### 2018-02-22 Working Draft/Meta-Analysis on Sexual Selection and Population Fitness.Rmd
Add files via upload

---
title: "Effects of sexual selection on non-sexual fitness components: a meta-analysis"
subtitle: Supplementary Material
author: "Justin Cally, University of Melbourne"
output: html_notebook
---

```{r warning=FALSE, message=FALSE}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(MuMIn)
library(glmulti)
library(cowplot)
library(ggrepel)
library(reshape2)
```

# Methods

Our aim was to investigate the effects of sexual selection on population fitness by conducting a meta-analysis on studies that measured fitness related outcomes after experimentally evolving a population under varying levels of opportunity for sexual selection. Here we describe the process of the literature search, data extraction, effect size calculation, formulation of multilevel models and assessing publication bias.

##Literature Search (Extended methods from paper)

**The literature search was conducted under the following conditions:**

1. We searched ISI Web of Science and Scopus on 9th June 2017. Notably, these resulted in a different set of returns (**PRISMA Figure**).

2. Studies were restricted to those from peer-reviewed and in the English language.

3. We devised a search strategy that sought to find studies which manipulated the presence or strength of sexual selection using experimental evolution, and then measured some proxy of population fitness. As such the search terms were as follows:

####_ISI Web of Science_

Topic (TS) = “Sexual Selection” OR Promisc* OR Monogam* OR Polygam* OR Polyandr* OR Polygyn* OR “Mate choice”

AND

Topic (TS) = Fitness OR “Population Fitness” OR Deleterious OR “Male Strength” OR Fecund* OR Viability OR Productiv* OR “Reproductive Success” OR “Reproductive Rate” OR Surviv* OR | “Development Rate” OR Extinct* OR “Competitive Success” OR Mortality OR Mass OR “Body Size” OR “Wing Size” OR Emergence OR Mating Rate OR “Mating Propensity” OR Adapt* OR “Novel | Environment” OR “Sexual Conflict” OR “Sexual Antagonis*”

AND

Topic (TS) = Generations OR “Experimental evolution” OR “mutation load”

AND

Research Area (SU) = “Evolutionary Biology”

####_Scopus_

TITLE-ABS-KEY = “Sexual Selection” OR Promisc* OR Monogam* OR Polygam* OR Polyandr* OR Polygyn* OR “Mate choice”

AND

TITLE-ABS-KEY = Fitness OR “Population Fitness” OR Deleterious OR “Male Strength” OR Fecund* OR Viability OR Productiv* OR “Reproductive Success” OR “Reproductive Rate” OR Surviv* | OR “Development Rate” OR Extinct* OR “Competitive Success” OR Mortality OR Mass OR “Body Size” OR “Wing Size” OR Emergence OR Mating Rate OR “Mating Propensity” OR Adapt* OR | “Novel Environment” OR “Sexual Conflict” OR “Sexual Antagonis*”

AND

TITLE-ABS-KEY = Generations OR “Experimental evolution” OR “mutation load”

In addition to studies found from the literature search we also included three relevant studies that were identified during scoping but not picked up in the subsequent formal searches (Partridge 1980; Price et al. 2010; Savic Veselinovic et al. 2013) that were missed by the database searches (**PRISMA Figure**).

4. After removing duplicates, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution). This left 130 papers, for which we read the full text and applied the following selection criteria:

  + **(1: Study Design)** The study was an experimental evolution study lasting >1 generation
  + **(1: Population)** a) The study was conducted using an animal species that was b) diecious
  + **(1: Intervention and Control)** The study experimentally manipulated the strength of sexual selection (e.g. via enforced monogamy or an altered sex ratio)
  + **(1: Outcomes)** The study measured a trait that we judged to be a potential correlate of population fitness.

This latter criterion is likely to be contentious, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness. We therefore relied on our best judgement when deciding which studies to exclude (see Table XXX). The inclusion/exlusion critera as applied to each study are detailed in an accompaning spreadsheet.

```{r}
Eligibility.criteria <- read.csv('Eligibility Workbook(22.02).csv', fileEncoding="UTF-8")
Eligibility.criteria %>% pander(split.cell = 20, split.table = 250, style = "grid")
```

##Data Extraction

The raw extracted data table is presented in the accompanying data folder. It details the type of data collected for each study (arithmatic means, SD, n, F-statistic, chi-squared, proportion etc.). The rules utilised were as follows:

1. Arithmatic means, standard deviations/errors and sample sizes were extracted from a paper, supplementary material or a linked data repository (e.g. Data Dryad). This was possible when means and SD were reported in text or in a table. We would preferentially extract data for each experimental evolution line/replicat/family if possible and only extract data for the final reported generation (which was noted down).

2. If we could not find the means and SD in text format we used web-plot digitizer (v.3.12) to extract data from graphs.

3. If means were not reported then we ecxtracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package. Summary statistics included _F_, _z_, _t_ and _chi^2^_. These conversions still required providing sample sizes for each treatment so these needed to be extractable from the study. Some summary statistics were obtained from generalized linear model summary tabels, others from straight forward ANOVAs and then some from more complex analysis such as proportional hazards statistical tests.

4. The covariates collected were extensive (**DATA TABLE**) and are discussed later. They were all regarded as potentially explaining trends in effect size or bias and hence were collected.

##Effect Size Calculation

> Not sure what to do about these calculations. I did not really lay them out neatly and the compute.es does not really return neat values. My calculations were done in a clunkier manual way. And are shown below.

**SS- will be group one with increased SS being group two**

####Almbro and Simmons 2014**

######Brood Number (No Distinction) 
```{r}
mes(15.4, 18, 10.071, 10.071, 207, 207, dig = 3)
```

######Strength (Stressed) 
```{r}
mes(0.047, 0.094, 0.05724, 0.16217, 91, 91, dig = 3)
```

##The Meta-Analysis Dataset

### Setup

Read in csv file 
```{r}
prelim.data <- read.csv('Preliminary data frame 22.2.18.csv')
kable(prelim.data)
```

###Explanation of Dataframe:

**Study ID**: An ID given to the published paper the effect size is sourced from

**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup

**Species and Species ID**: Same thing

**SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment

**Ratio Category**: A three level category for the ratio of males to females (high, medium, low).

**Density Category**: A three level category for the density of males to females (high, medium, low).

**SSS.Categorical**: A three level category for the **density & the ratio** of males to females (high medium, low).

**Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)

**Blind**: Whether the study was blind or not

**Generations** The number of generations run before fitness outcomes were measured

**Enforced Monogamy**: Whether the study had the low sexual selection treatment as enforced monogamy (YES) or not (NO). Not all studies compared enforced monogamy and SS+ treatments. Some used FB vs MB, where FB is the SS (low intensity).

**Sex**: Whether the fitness outcome was measured for females (F), males (M) or both (B). Studies that reported 'both' would pool results from males and females.

**Ambiguous**: Is the fitness outcome ambiguous (YES) or not ambigous (NO). Ambiguous outcomes may be those that may not necessarily be directional, that is to say they may be a life history trait.

**Outcome Class**: Grouped as Direct, Indirect or Ambiguous.

**Environment**: In the methods of the papers included in this study it was usually stated whether additional modifications to the experimental lines were made. Briefly, this was usually a modification that made conditions more stressful such as using a novel food source or elevated mutation load, the effect sizes from these experimental lines are labelled as 'Stressed'. If it was clearly stated that there was no such modification it is labelled 'Unstressed'. However, sometimes the paper was ambiguous in what lines had added stress or the results from stressed and unstressed lines were pooled together, in this case we label it as 'Not Stated'.

**g**: Hedge's g calculated using the compute.es package

**var.g**: The within study variance associated with the effect size, g

**mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance). Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.)

**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.

_______________________________________________

### Factor and level data

A lot of the covariates are categorical, so here we assign them as factors and relevel them.

```{r}
prelim.data$Study.ID <- prelim.data$Study.ID %>% factor
prelim.data$Taxon <- prelim.data$Taxon %>% factor
prelim.data$Experiment.ID <- prelim.data$Experiment.ID %>% factor 
prelim.data$Authors <- prelim.data$Authors %>% factor
prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor
prelim.data$Species <- prelim.data$Species %>% factor
#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor %>% relevel(ref="Indirect")
prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor %>% relevel(ref="NO")
prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor %>% relevel(ref="0")
prelim.data$Post.cop <- prelim.data$Post.cop %>% factor %>% relevel(ref="0")
prelim.data$Ratio.Category <- prelim.data$Ratio.Category %>% factor %>% relevel(ref="Low")
prelim.data$Density.Category <- prelim.data$Density.Category %>% factor %>% relevel(ref="Low")
prelim.data$SSS.Categorical <- prelim.data$SSS.Categorical %>% factor %>% relevel(ref="Low")
prelim.data$Blinding <- prelim.data$Blinding %>% factor
```

________________________________________________

###The Effect Size Dataset

The number of effect sizes, publications, blind experiments, effect sizes in stressed conditions, male, female and both measures and different species used, with the number of effect sizes per taxon also reported.

```{r}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
n.stressed.ones <- 
prelim.data %>% summarise(Effect_sizes = n(), 
                       Publications = prelim.data$Study.ID %>% unique %>% length,
                       Blind_experiments = n.blind.ones,
                       Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
                       Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
                       Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
                       Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
                       Different_species =  prelim.data$Species %>% unique %>% length,
                       Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
                       Effect_sizes_.Flyq = sum(Taxon == "Fly"),
                       Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
                       Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
                       Effect_sizes_.Miteq = sum(Taxon == "Mite"),
                       Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
                       Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% pander(split.cell = 40, split.table = Inf)
```

###Forest plot using ggplot

Here we show the residual effect sizes for each outcome measured. The following forest plot is based on the residual effect sizes. The model is an intercept only model with the same multilevel random effects structure as we use later when investigating environment and sex

> Although I am not sure whether having the raw values would be better. In addition whether it is worth it to add in summary polygons (effect sizes) for a grouped outcome

Using ggplot the forest plot is grouped according to environment and sex, with multiple effect sizes on one row for a given study

```{r, fig.height=30, fig.width=22.5}
#Create model we later establish and analyse but not restricted
forest.model <- rma.mv(g, var.g, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, method = "REML", data = prelim.data)

#Obtain residuals
resstandards <- (rstandard.rma.mv(forest.model, type="response"))

#Create new df with residuals replacing raw
df.forest.model <- prelim.data
df.forest.model$g <- resstandards$resid
df.forest.model$sei <- resstandards$se

#Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
df.forest.model$Outcome_f = factor(df.forest.model$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

#define upper and lower bounds
df.forest.model$lowerci <- df.forest.model$g - 1.96*((df.forest.model$sei))
df.forest.model$upperci <- df.forest.model$g + 1.96*((df.forest.model$sei))

#Get author and year in one
df.forest.model$AuthorYear = paste(df.forest.model$Authors, df.forest.model$Year, sep=" ")

#Generate a plot
p.meta <- ggplot(df.forest.model, aes(y=reorder(AuthorYear, -g), x=g, xmin=lowerci, xmax=upperci, shape=Sex, color = Outcome.Class)) +
 #Add data points and color them black
geom_point(size=2)+
geom_errorbarh(data=df.forest.model, aes(xmin= lowerci, xmax = upperci) ,height=.1)+
  #Specify the limits of the x-axis and relabel it to something more meaningful
  scale_x_continuous(limits=c(-5,5), name='Standardized Mean Difference (g)')+
  #Give y-axis a meaningful label
  ylab('Reference')+
  #Add a vertical dashed line indicating an effect size of zero, for reference
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  #Create sub-plots (i.e., facets) based on levels of setting
  #And allow them to have their own unique axes (so authors don't redundantly repeat)
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
p.meta
```

___________________
###Effect size of subgroups

>The following documents how i could run individual models for each outcome or outcome.class of interest and then plot them. This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment)

There is not really enough direct outcomes to analyse by itself so hence we combine with indirect later
```{r}
#Ambiguous outcomes

model.Ambiguous <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Ambiguous"), intercept = T ,data = prelim.data)

summary(model.Ambiguous)
```

```{r}
#Indirect outcomes

model.Indirect <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Indirect"), intercept = T ,data = prelim.data)

summary(model.Indirect)
```

```{r}
#Direct outcomes

model.Direct <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Direct"), data = prelim.data)

summary(model.Direct)
```

Now let's combine into a data frame and plot. The following plot could then be added to the large forest plot as summary polygons or summary points with error bars.

```{r}
#Data frame
Outcome.category <- c('Ambiguous', 'Indirect', 'Direct')
Estimate <- c(model.Ambiguous$b, model.Indirect$b, model.Direct$b)
l.ci <- c(model.Ambiguous$ci.lb, model.Indirect$ci.lb, model.Direct$ci.lb)
u.ci <- c(model.Ambiguous$ci.ub, model.Indirect$ci.ub, model.Direct$ci.ub)
data.1 <- data.frame(Outcome.category, Estimate, l.ci, u.ci)

#plot

data.1 %>% ggplot(aes(x = Estimate, y= Outcome.category)) + 
  geom_point() +
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, size=1) +
  ylab("Outcome Category")+
  xlab("Effect Size")+
  xlim(-.2, .5)+
  ggtitle('Meta-Analysis Results')
```

From the previous forest plot and models we see that overall sexual selection is beneficial towards population fitness. Although this is heavily modulated by the individual outcome and the outcome class. We explore heterogeneity in more depth later in this document.

__________________________________

###Model predictions

####Does the effect of sexual selection differ between species?

First run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes or environments that were not stated whether they were stressed or unstressed. In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.

```{r}
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), Environment = as.character(Environment), Outcome.Class.2 = as.character(Outcome.Class), Enforced.Monogamy = as.character(Enforced.Monogamy))

#RWe need to make sure the factors are leveled in the same order as we write our prediction function (below)
restricted.data$Environment <- restricted.data$Environment %>% factor %>% relevel(ref="Unstressed")
restricted.data$Sex <- restricted.data$Sex %>% factor %>% relevel(ref="M")
restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor %>% relevel(ref="Indirect")

#run model again with restricted data 
model.complete <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex + Environment + Taxon + Sex:Environment, 
                         random = ~ 1 | Study.ID/Outcome, 
                         method = "REML", 
                         data = restricted.data)

#Note that the data is subsetted
summary(model.complete)

```

The result is a model with estimates for various taxa, species, sexes and environments. To make sense of these estimates we should obtain average predictions for each moderator variable class of interest. We can do that by using a modified version version of a function used by Holman 2017. Here it alows us to cluster predictions for the different moderators of interest: Sex, environment, taxon etc. This is done by obtaining predictions using the base ``predict()`` function for the ``rma.mv()`` objects that have been previously created
```{r}
# function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
get.predictions.complete <- function(newdata){
  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Unstressed<-1
  if(newdata[3] == "Cricket") Cricket<-1
  if(newdata[3] == "Fly") Fly<-1
  if(newdata[3] == "Guppy") Guppy<-1
  if(newdata[3] == "Mite") Mite<-1
  if(newdata[3] == "Mouse") Mouse<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, interaction1=interaction1, interaction2=interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed"),
                           Taxon = c("Cricket", "Fly", "Guppy", "Mite", "Mouse")))
predictions.complete <- cbind(predictions.complete, do.call("rbind", apply(predictions.complete, 1, get.predictions.complete))) %>%
  select(Sex, Environment, Taxon, pred, se, ci.lb, ci.ub) 
for(i in 4:7) predictions.complete[,i] <- unlist(predictions.complete[,i])
```

Note that to get vertical position dodge to use in the ggplot meta-analysis we need to utilise a vertical position dodge. We can obtain this formula from the following github page by Jared Lander: https://github.com/jaredlander/coefplot/blob/master/R/position.r
```{r include=FALSE}
# Detect and prevent collisions.
# Powers dodging, stacking and filling.
collidev <- function(data, height = NULL, name, strategy, check.height = TRUE) {
    # Determine height
    if (!is.null(height)) {
        # height set manually
        if (!(all(c("ymin", "ymax") %in% names(data)))) {
            data$ymin <- data$y - height / 2
            data$ymax <- data$y + height / 2
        }
    } else {
        if (!(all(c("ymin", "ymax") %in% names(data)))) {
            data$ymin <- data$y
            data$ymax <- data$y
        }

        # height determined from data, must be floating point constant
        heights <- unique(data$ymax - data$ymin)
        heights <- heights[!is.na(heights)]

        #   # Suppress warning message since it's not reliable
        #     if (!zero_range(range(heights))) {
        #       warning(name, " requires constant height: output may be incorrect",
        #         call. = FALSE)
        #     }
        height <- heights[1]
    }

    # Reorder by x position, relying on stable sort to preserve existing
    # ordering, which may be by group or order.
    data <- data[order(data$ymin), ]

    # Check for overlap
    intervals <- as.numeric(t(unique(data[c("ymin", "ymax")])))
    intervals <- intervals[!is.na(intervals)]

    if (length(unique(intervals)) > 1 & any(diff(scale(intervals)) < -1e-6)) {
        warning(name, " requires non-overlapping y intervals", call. = FALSE)
        # This is where the algorithm from [L. Wilkinson. Dot plots.
        # The American Statistician, 1999.] should be used
    }

    if (!is.null(data$xmax)) {
        plyr::ddply(data, "ymin", strategy, height = height)
    } else if (!is.null(data$x)) {
        data$xmax <- data$x
        data <- plyr::ddply(data, "ymin", strategy, height = height)
        data$x <- data$xmax
        data
    } else {
        stop("Neither x nor xmax defined")
    }
}

# Stack overlapping intervals.
# Assumes that each set has the same horizontal position
pos_stackv <- function(df, height) {
    if (nrow(df) == 1) return(df)

    n <- nrow(df) + 1
    x <- ifelse(is.na(df$x), 0, df$x)
    if (all(is.na(df$y))) {
        heights <- rep(NA, n)
    } else {
        heights <- c(0, cumsum(x))
    }

    df$xmin <- heights[-n]
    df$xmax <- heights[-1]
    df$x <- df$xmax
    df
}

# Stack overlapping intervals and set height to 1.
# Assumes that each set has the same horizontal position.
pos_fillv <- function(df, height) {
    stacked <- pos_stackv(df, height)
    stacked$xmin <- stacked$xmin / max(stacked$xmax)
    stacked$xmax <- stacked$xmax / max(stacked$xmax)
    stacked$x <- stacked$xmax
    stacked
}

# Dodge overlapping interval.
# Assumes that each set has the same horizontal position.
pos_dodgev <- function(df, height) {
    n <- length(unique(df$group))
    if (n == 1) return(df)

    if (!all(c("ymin", "ymax") %in% names(df))) {
        df$ymin <- df$y
        df$ymax <- df$y
    }

    d_height <- max(df$ymax - df$ymin)

    # df <- data.frame(n = c(2:5, 10, 26), div = c(4, 3, 2.666666,  2.5, 2.2, 2.1))
    # ggplot(df, aes(n, div)) + geom_point()

    # Have a new group index from 1 to number of groups.
    # This might be needed if the group numbers in this set don't include all of 1:n
    groupidy <- match(df$group, sort(unique(df$group)))

    # Find the center for each group, then use that to calculate xmin and xmax
    df$y <- df$y + height * ((groupidy - 0.5) / n - .5)
    df$ymin <- df$y - d_height / n / 2
    df$ymax <- df$y + d_height / n / 2

    df
}

#' Adjust position by dodging overlaps to the side.
#'
#' @inheritParams ggplot2::position_identity
#' @param height Dodging height, when different to the height of the individual
#'   elements. This is useful when you want to align narrow geoms with wider
#'   geoms. See the examples for a use case.
#' @family position adjustments
#' @export
#' @examples
#' ggplot(mtcars, aes(factor(cyl), fill = factor(vs))) +
#'   geom_bar(position = "dodge")
#'
#' ggplot(diamonds, aes(price, fill = cut)) +
#'   geom_histogram(position="dodge")
#' # see ?geom_boxplot and ?geom_bar for more examples
#'
#' # To dodge items with different heights, you need to be explicit
#' df <- data.frame(x=c("a","a","b","b"), y=2:5, g = rep(1:2, 2))
#' p <- ggplot(df, aes(x, y, group = g)) +
#'   geom_bar(
#'     stat = "identity", position = "dodge",
#'     fill = "grey50", colour = "black"
#'   )
#' p
#'
#' # A line range has no height:
#' p + geom_linerange(aes(ymin = y-1, ymax = y+1), position = "dodge")
#' # You need to explicitly specify the height for dodging
#' p + geom_linerange(aes(ymin = y-1, ymax = y+1),
#'   position = position_dodge(width = 0.9))
#'
#' # Similarly with error bars:
#' p + geom_errorbar(aes(ymin = y-1, ymax = y+1), width = 0.2,
#'   position = "dodge")
#' p + geom_errorbar(aes(ymin = y-1, ymax = y+1, height = 0.2),
#'   position = position_dodge(width = 0.90))
#'
position_dodgev <- function(height = NULL) {
    ggproto(NULL, PositionDodgeV, height = height)
}

PositionDodgeV <- ggproto("PositionDodgeV", Position,
                          required_aes = "y",
                          height = NULL,
                          setup_params = function(self, data) {
                              if (is.null(data$ymin) && is.null(data$ymax) && is.null(self$height)) {
                                  warning("height not defined. Set with `position_dodgev(height = ?)`",
                                          call. = FALSE)
                              }
                              list(height = self$height)
                          },

                          compute_panel = function(data, params, scales) {
                              collidev(data, params$height, "position_dodgev", pos_dodgev, check.height = FALSE)
                          }
)
```

Third, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.

> I would liker to know how to join a table with mean, and CI values to the forest plots I am generating.

```{r, fig.height= 7, fig.width=10}
pd <- position_dodgev(height = .7)
predictions.complete %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, xmax = predictions.complete$ci.ub), height = 0, position = pd) +
  geom_point(position = pd, size=2) + 
  facet_grid(Taxon ~.)+
  ylab("Environment")+
  xlab("Model Prediction (Hedges g)")+
  xlim(-2, 2)+
  ggtitle('Effects of Sex, Stress and Outcome Class \non Population Fitness for Each Taxon')
```

This model indicates quite a bit of heterogeneity between taxon. More so that that confidence limits increase, rather than radically changing direction of effect. However we can se from this that under stressed environments, females twnd to

____________

####Does sexual selection benefit populations in stressed environments more than unstressed environments? **AND** Do the benefits of sexual selection accrue more for female fitness components?

Here we run a three level model where the outcome is nested within a study (Study.ID). Other potential random effects include Species and Group.ID. However the estimate (variance from random effect) of these two other potential random effects tended towards zero and were dropped from the model. Additionally the model could be run with just Study.ID, but from our exploration of heterogeneity (below) we see that there is sufficient correlation (but not ICC = 1) between outcomes to include it as a random effect within the model.

```{r}
#run model without taxon: 3 level model with outcomes within a study
model.complete2 <- rma.mv(g, var.g, 
                          mods = ~ 1 + Sex + Environment + Sex:Environment, 
                          random = ~ 1 | Study.ID/Outcome, 
                          method = "REML", 
                          data = restricted.data)
summary(model.complete2)
```

```{r, fig.height= 7, fig.width=10}

#Generate predictions without taxon utilising the previously described function

get.predictions.complete2 <- function(newdata){
  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Unstressed<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

  predict(model.complete2, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete2 <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed")))
predictions.complete2 <- cbind(predictions.complete2, do.call("rbind", apply(predictions.complete2, 1, get.predictions.complete2))) %>%
  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
for(i in 3:6) predictions.complete2[,i] <- unlist(predictions.complete2[,i])

#And plot the results

pd <- position_dodgev(height = .3)
predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, xmax = predictions.complete2$ci.ub), height = 0, position = pd) +
  geom_point(position = pd) + 
  ylab("Environment")+
  xlab("Effect Size (Hedges g)")+
  xlim(-.75, .75)+
  ggtitle('Effects of Sex, Stress \non Population Fitness')
```

__________________________________
###Estimating Heterogeneity using _I^2^_ and exploring correlations

Let's obtain a _I^2^_ statistic using the formulas presented here: http://www.metafor-project.org/doku.php/tips:i2_multilevel_multivariate

There are different methods to obtain estimates of _I^2^_, they should be pretty similar though. Here we obtain an overall value of _I^2^_ that is weighted based on variance where estimates of heterogeneity are sourced from sigma^2^ of the respective models. 
```{r}
#There are two estimates of heterogeneity: A between cluster (between studies) and a within-cluster (outcomes within a study)

#This is for the model with outcome within study
W <- diag(1/restricted.data$var.g)
X <- model.matrix(model.complete2)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
```
This is a reasonably high _I^2^_ value but is relatively common in Ecology and Evolution (Nakagawa 2017).

To investigate the sources of heterogeneity we can obtain a breakdown of the heterogeneity for the three level model.
```{r}
100 * model.complete2$sigma2 / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
```

This indicates that 24.3 % of total heterogeneity is due to the between study heterogeneity and 68.275 % for within study heterogeneity between different outcomes. With the remaining 7.5 % due to sampling variance. Interestingly this might indicate that _I^2^_ would be largely reduced for a model restricted to a single outcome... Let's test this with our most common outcome...Reproductive Success

```{r}
#Reproductive Success Restriction 
restricted.dataRS <- restricted.data %>% filter(restricted.data$Outcome == "Reproductive Success")

#Run reproductive success only model 
model.completeRS <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ 1 | Study.ID, method = "REML", data = restricted.dataRS)

#Run estimate of heterogeneity
W2 <- diag(1/restricted.dataRS$var.g)
X2 <- model.matrix(model.completeRS)
P2 <- W2 - W2 %*% X2 %*% solve(t(X2) %*% W2 %*% X2) %*% t(X2) %*% W2
100 * sum(model.completeRS$sigma2) / (sum(model.completeRS$sigma2) + (model.completeRS$k-model.completeRS$p)/sum(diag(P2)))
```

So if we look at an individual outcomes such as reproductive success our I^2 is lower (79.53 %). Which is still high as it comes from 39 studies but lower than others. If we wanted to run models independently we could do it for those with a large enough sample size (k>10).

Furthermore, we can obtain estimates of the intra-class correlation (ICC) within a study via: 
```{r}
round(model.complete2$sigma2[1] / sum(model.complete2$sigma2), 3)
```

This means that within a study, between different outcomes, there is a correlation of 26.2 % (low-medium). This justifies including outcome as a level, as without it we would be assuming ICC = 1. We can also gain an estimate of the total heterogeniety, as the sum of the sigma componenets: 
```{r}
round(sum(model.complete2$sigma2), 3)
```

#### Multilevel model using metafors alternative random effect structure

> This inner, outer factor stuff from the metafor package is a bit strange. There is a goodish description in ``?rma.mv()`` but still unsure how it differs from the above model. It seems that it is useful to breakdown variance-covariance matrix but unsure how that would benefit our analysis.

```{r}
#Just to check, how about with outcome as the inner factor 
model.complete2.2 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ factor(Outcome) | Study.ID, method = "REML", data = restricted.data)

summary(model.complete2.2)

#Now with a slightly different structure (HCS)

model.complete2.3 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ Outcome | Study.ID, struct = "HCS", method = "REML", data = restricted.data)

summary(model.complete2.3)
```

```{r, fig.height= 7, fig.width=10}
#Generate predictions without taxon

get.predictions.complete2 <- function(newdata){
  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Unstressed<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

  predict(model.complete2.2, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete2 <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed")))
predictions.complete2 <- cbind(predictions.complete2, do.call("rbind", apply(predictions.complete2, 1, get.predictions.complete2))) %>%
  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
for(i in 3:6) predictions.complete2[,i] <- unlist(predictions.complete2[,i])

#And plot the results

pd <- position_dodgev(height = .3)
predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, xmax = predictions.complete2$ci.ub), height = 0, position = pd) +
  geom_point(position = pd) + 
  ylab("Environment")+
  xlab("Effect Size (Hedges g)")+
  xlim(-.75, .75)+
  ggtitle('Effects of Sex, Stress \non Population Fitness (OUTCOME = INNER FACTOR)')
```

____________________

## Meta-Analysis on Variance

This meta-analysis on variation utilises previously described and utilised methods devoleped (Nakagawa et al. 2015; Senior et al. 2016). Our goal is to determine whether the phenotypic variance in fitness related traits is impacted by sexual selection. We would assume that if selection is occuring not only would the trait mean shift in a certain direction but the variance associated with those changes to the mean would also decrease. In this case we use an effect size statistic known as the natural log of the coefficient of variation ratio (lnCVR)

First, we setup our calculation by creating a a restricted dataset with only unabmiguous fitness outcomes and running the functions developed by Nakagawa et al. 2015:

```{r}
#Setup restricted data
prelim.data2 <- (prelim.data %>% filter(Outcome.Class != "Ambiguous"))

#Run function for lnCVR and associated variance of lnCVR

#for lnCVR

Calc.lnCVR<-function(CMean, CSD, CN, EMean, ESD, EN){

	ES<-log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))

	return(ES)

}

#for variance of lnCVR

Calc.var.lnCVR<-function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T){

	if(Equal.E.C.Corr==T){

		mvcorr<-cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate

		S2<- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))

	}
	else{

		Cmvcorr<-cor.test(log(CMean), log(CSD))$estimate
		Emvcorr<-cor.test(log(EMean), (ESD))$estimate

		S2<- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))

	}
	return(S2)

}

```

Secondly, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes. Noting that not all of the dataset has means, SD and n; some were calculated from summary statistics and are not able to have lnCVR calculated. Once we obtain these lnCVR estimates we can run subsetted models that use as the response variable:

Now utilise function with existing data frame 
```{r, fig.height= 7, fig.width=10}
#foe lnCVR
prelim.data2$lnCVr <- Calc.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high)

#for variance in lnCVR
prelim.data2$var.lnCVr <- Calc.var.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high, Equal.E.C.Corr=F)

#Run simple models subsetted for each environment/sex (this is perhaps a clunky way so we also use predictions shown below)

# For stressed environment and females
varSF <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID, subset = (Environment == "Stressed" & Sex == "F"))

# For stressed environment and females
varSM <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID, subset = (Environment == "Stressed" & Sex == "M"))

# For stressed environment and females
varSB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID, subset = (Environment == "Stressed" & Sex == "B"))

#For Benign environment and females
varUF<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID, subset = (Environment == "Unstressed" & Sex == "F"))

#For Benign environment and males
varUM<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID, subset = (Environment == "Unstressed" & Sex == "M"))

#For Benign environment and both
varUB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID, subset = (Environment == "Unstressed" & Sex == "B"))

#Create dataframe of estimates and confidence intervals
lnCVR <- c(varSF$b, varSM$b, varSB$b, varUF$b, varUM$b, varUB$b)
l.ci <- c(varSF$ci.lb, varSM$ci.lb, varSB$ci.lb, varUF$ci.lb, varUM$ci.lb, varUB$ci.lb)
u.ci <- c(varSF$ci.ub, varSM$ci.ub, varSB$ci.ub, varUF$ci.ub, varUM$ci.ub, varUB$ci.ub)
Environment <- c("Stressed", "Stressed", "Stressed", "Unstressed", "Unstressed", "Unstressed")
Sex <- c("Female", "Male", "Both", "Female", "Male", "Both")
k <- c(varSF$k, varSM$k, varSB$k, varUF$k, varUM$k, varUB$k)

var.data <- data.frame(lnCVR, l.ci, u.ci, Environment, Sex, k)

#Releveling the factors to make sure it aligns with other formatted graphs
var.data$Environment <- var.data$Environment %>% factor %>% relevel(ref="Unstressed")
var.data$Sex <- var.data$Sex %>% factor %>% relevel(ref="Male")

#Plot subseted model estimates

var.data %>% ggplot(aes(x=lnCVR, y = Environment, colour = Sex))+ 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, position = pd) +
  geom_point(position = pd) + 
  ylab("Environment")+
  xlab("lnCVR")+
  xlim(-.75, .75)+
  ggtitle('Meta-Analysis of Variance (Using Subsetting)')

```

Here we see that Stressed environments tend to reduce phenotypic variance (if anything). However, perhaps a better way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously. This can be done be utilising the same predict function but for lnCVR and var.lnCVR.

Multilevel-model using lnCVR:

```{r}
#Now try with multilevel model 
variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ 1 | Study.ID/Outcome, method = "REML", data = prelim.data2 %>% filter(Environment != "Not Stated"))
summary(variance.model)
```

Plotted predictions of lnCVR for various moderators:

```{r, fig.height= 7, fig.width=10}

#Generate predictions
get.predictions.variance <- function(newdata){
  F<-0; M<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "F") F<-1 
  if(newdata[1] == "M") M<-1 
  if(newdata[2] == "Stressed") Unstressed<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "M" & newdata[2] == "Stressed") interaction2<-1

  predict(variance.model, newmods=c(F, M, Stressed, interaction1=interaction1, interaction2=interaction2))
}
# Get the predictions for each combination of moderators
predictions.variance <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed")))
predictions.variance <- cbind(predictions.variance, do.call("rbind", apply(predictions.variance, 1, get.predictions.variance))) %>%
  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
for(i in 3:6) predictions.variance[,i] <- unlist(predictions.variance[,i])

#And plot the results

pd <- position_dodgev(height = .3)
predictions.variance %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.variance$ci.lb, xmax = predictions.variance$ci.ub), height = 0, position = pd) +
  geom_point(position = pd) + 
  ylab("Environment")+
  xlab("lnCVR")+
  xlim(-1.2, 1.2)+
  ggtitle('Meta-Analysis of Variance (Using Model Predictions)')
```

From these predictions we see that environmental stress has a large impact on phenotypic variance, whereby phenotypic variance is lower for females than for males and under stressful conditions the phenotypic variance of females decreases. Indicating there is a narrowing of phenotypic variance under selection.

____________________
##Bias

###Funnel plots indicate potential but small amounts of publication bias

Checking for biases with a funnell plot. Note that the trim and fill method does not work with rma.mv objects. However we can perform Eggers test using the ``ragtest()`` function. This tests for asymmetry via assessing relationships between effect size and a specified predictor. See ``?ragtest()`` for more information. Also the eggers test does not work for rma.mv objects. 
```{r}
funnel.rma(model.Ambiguous)
regtest(model.Ambiguous, predictor = "vi")
funnel.rma(model.Indirect)
regtest(model.Indirect)
funnel.rma(model.Direct)
regtest(model.Direct)
funnel.rma(model.complete2)
```

>Now use ggplot for funnel plot. This is pretty clunky and unlike the ``funnel.rma`` it does not use residuals but raw effect sizes, we could of course add residuals, so it depends on how much customization you think these plots should have. The outline taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

```{r, fig.height= 7, fig.width=10}
#Funnel plot for indirect model

#Make restricted data for indirect

prelim.data.Indirect <- prelim.data %>% filter(Outcome.Class == "Indirect")

#read in apatheme
#My APA-format theme
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        text=element_text(family='Times'),
        legend.position='none')

#Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
estimate = model.Indirect$b
se = model.Indirect$se

#Store a vector of values that spans the range from 0
#to the max value of impression (standard error) in your dataset.
#Make the increment (the final value) small enough (I choose 0.001)
#to ensure your whole range of data is captured
se.seq=seq(0, max(sqrt(prelim.data.Indirect$var.g)), 0.001)

#Now, compute vectors of the lower-limit and upper limit values for
#the 95% CI region, using the range of SE that you generated in the previous step, and the stored value of your meta-analytic estimate.
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)

#You can do this for a 99% CI region too
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)

#And finally, do the same thing except now calculating the confidence interval
#for your meta-analytic estimate based on the stored value of its standard error
meanll95 = estimate-(1.96*se)
meanul95 = estimate+(1.96*se)

#Now, smash all of those calculated values into one data frame (called 'dfCI').
#You might get a warning about '...row names were found from a short variable...'
#You can ignore it.
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

#Now we can actually make the funnel plot.
#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
fp = ggplot(prelim.data.Indirect, aes_string(x = sqrt(prelim.data.Indirect$var.g), y =prelim.data.Indirect$g)) +
#Add your data-points to the scatterplot
  geom_point(shape = 1) +
#Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('g')+
#Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
#to the lower and upper limits of your 95% CI region,
#And dashed lines corresponding to your 99% CI region
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
#Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
#at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse()+
#Specify the range and interval for the tick-marks of the y-axis (Zr);
#Choose values that work for you based on your data
  scale_y_continuous(breaks=seq(-1.25,2,0.25))+
#And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
#Finally, apply my APA-format theme (see code at end of post).
#You could, alternatively, specify theme_bw() instead.
  apatheme

#Call the pretty funnel plot
fp
```

###Other tests of publication bias suggest there is little evidence for publication bias

If we see a positive trend with effect size and Journal Impact Factor it may represent publication bias whereby significant (positive) results are published more readily and in more circulated journals. Our journal impact factor dataset is not evenly distributed as several publications in Nature (JIF ~ 40) are much larger than the next highest JIF (~11)

```{r}
prelim.data %>% ggplot(aes(x=JIF, y=(g), size = 1/sqrt(var.g)))+
  geom_jitter()+
  geom_hline(yintercept=0, linetype = 'dotted')+
  geom_smooth(method = 'lm')
```

> I think it may also be interesting to plot the maximum effect size for each study and then plot the results as many studies measure a suite of traits.

We can also look at the time-lag bias, which suggests effect size decreases over time. Again, because one publication from 1980 is well before the next publication in the late 1990s we see a very uneven distribution.

```{r}
prelim.data %>% ggplot(aes(x=Year, y=g, size = (1/(var.g))))+
  geom_jitter()+
  geom_hline(yintercept=0, linetype = 'dotted')+
  geom_smooth(method='lm')+
  labs(size = 'weight')
```

From these graphs, we see a small trend for larger effect sizes to be published in higher impact journals as well as for effect size to decrease over successive years. Additionally to publication bias, other forms of bias may exist within studies. We initially collected data on whether studies were blind or not. Although not enough studies were blind for us to include it as a fixed effect within the model we can test whether blinding affects the raw effect size:

```{r}
df.forest.model %>% ggplot(aes(x=Blinding, y=g, color = Outcome.Class))+
  geom_boxplot()+
  geom_hline(yintercept=0, linetype = 'dotted')
```

### 2018-02-27 Working Draft/Meta-Analysis on Sexual Selection and Population Fitness.Rmd
Add files via upload

@@
 prelim.data$Taxon <- prelim.data$Taxon %>% factor
-prelim.data$Experiment.ID <- prelim.data$Experiment.ID %>% factor 
+prelim.data$Group.ID <- prelim.data$Group.ID %>% factor 
 prelim.data$Authors <- prelim.data$Authors %>% factor
@@
                        Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
+                       Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
                        Different_species =  prelim.data$Species %>% unique %>% length,
@@
 The following forest plot is based on the residual effect sizes.
-The model is an intercept only model with the same multilevel random effects structure as we use later when investigating environment and sex
+The model is an intercept only model with standard random effects structure.
 
@@
 ```{r, fig.height=30, fig.width=22.5}
-#Create model we later establish and analyse but not restricted
-forest.model <- rma.mv(g, var.g, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, method = "REML", data = prelim.data)
+#Create standard random effectrs model
+forest.model <- rma(g, var.g, mods = ~ 1, method = "REML", data = prelim.data)
 
 #Obtain residuals
-resstandards <- (rstandard.rma.mv(forest.model, type="response"))
+resstandards <- (rstandard.rma.uni(forest.model, type="response"))
 
@@
 
-pd <- position_dodgev(height = .3)
+pd <- position_dodgev(height = .5)
 predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
@@
 
+We see that female fitness in stressed environments is greater than the other measurements.
+For outcomes that were measured for both female and males we see a greater uncertainty in the estimate.
+It is not obviously clear why this is.
+The 'both' outcomes are restricted to extinction rate, offspring viability, mutant frequency and reproductive success.
+However, the shift from 'both' being ns in unstressed to significant in stressed may reflect the dampening of the negative correlations (sexual antagonism).
+
+```{r}
+table(restricted.data$Outcome, restricted.data$Sex)
+```
+
 __________________________________
@@
 
+____________
+
 #### Multilevel model using metafors alternative random effect structure
@@
 > This inner, outer factor stuff from the metafor package is a bit strange.
-There is a goodish description in ``?rma.mv()`` but still unsure how it differs from the above model.
+There is a description in ``?rma.mv()`` but still unsure how it differs from the above model.
 It seems that it is useful to breakdown variance-covariance matrix but unsure how that would benefit our analysis.
@@
 # For stressed environment and females
-varSF <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID, subset = (Environment == "Stressed" & Sex == "F"))
+varSF <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "F"))
 
 # For stressed environment and females
-varSM <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID, subset = (Environment == "Stressed" & Sex == "M"))
+varSM <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "M"))
 
 # For stressed environment and females
-varSB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID, subset = (Environment == "Stressed" & Sex == "B"))
+varSB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "B"))
 
 #For Benign environment and females
-varUF<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID, subset = (Environment == "Unstressed" & Sex == "F"))
+varUF<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "F"))
 
 #For Benign environment and males
-varUM<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID, subset = (Environment == "Unstressed" & Sex == "M"))
+varUM<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "M"))
 
 #For Benign environment and both
-varUB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID, subset = (Environment == "Unstressed" & Sex == "B"))
+varUB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "B"))
 
@@
 ```{r}
-funnel.rma(model.Ambiguous)
+trim.ambig <- trimfill.rma.uni(model.Ambiguous)
+funnel.rma(trim.ambig)
 regtest(model.Ambiguous, predictor = "vi")
 funnel.rma(model.Indirect)
-regtest(model.Indirect)
+regtest(model.Indirect, predictor = "vi")
 funnel.rma(model.Direct)
-regtest(model.Direct)
-funnel.rma(model.complete2)
+regtest(model.Direct, predictor = "vi")
+funnel.rma(model.complete2, type="rstandard", yaxis = "sei")
 ```
@@
 
+####Journal Impact Factor
+
 If we see a positive trend with effect size and Journal Impact Factor it may represent publication bias whereby significant (positive) results are published more readily and in more circulated journals.
-Our journal impact factor dataset is not evenly distributed as several publications in Nature (JIF ~ 40) are much larger than the next highest JIF (~11)
-
-```{r}
-prelim.data %>% ggplot(aes(x=JIF, y=(g), size = 1/sqrt(var.g)))+
-  geom_jitter()+
+Our journal impact factor dataset is not evenly distributed as several publications in Nature (JIF ~ 40) are much larger than the next highest JIF (~11).
+
+```{r}
+
+```
+
+```{r, fig.width=10, fig.height=8}
+prelim.data %>% ggplot(aes(x=JIF, y=(g)))+
+  geom_jitter(color='darkgreen', alpha=.3, aes(size = (1/(var.g))))+
   geom_hline(yintercept=0, linetype = 'dotted')+
-  geom_smooth(method = 'lm')
+  geom_smooth(method='lm', color='black')+
+  labs(size = 'weight')
 ```
@@
 > I think it may also be interesting to plot the maximum effect size for each study and then plot the results as many studies measure a suite of traits.
+
+####Time-lag Bias
 
@@
 
-```{r}
-prelim.data %>% ggplot(aes(x=Year, y=g, size = (1/(var.g))))+
-  geom_jitter()+
+```{r, fig.width=7.50, fig.height=6}
+prelim.data %>% ggplot(aes(x=Year, y=g))+
+  geom_jitter(color='orange', alpha=.3, aes(size = (1/(var.g))))+
   geom_hline(yintercept=0, linetype = 'dotted')+
-  geom_smooth(method='lm')+
+  geom_smooth(method='lm', color='black')+
   labs(size = 'weight')
 ```
+
+####Blinding
 
@@
 
-```{r}
-df.forest.model %>% ggplot(aes(x=Blinding, y=g, color = Outcome.Class))+
+```{r, fig.width=10, fig.height=8}
+df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
   geom_boxplot()+
+  geom_jitter(aes(color=Blinding))+
   geom_hline(yintercept=0, linetype = 'dotted')
 ```
+
+####Sample Size
+
+We also collected sample sizes for each of the effect sizes calculated.
+Because we are dealing withj different taxa some studies are not suited to have sample sizes in the 1000's.
+We can simply inspect the sample size ande effect sizes through the following plot:
+```{r, fig.width=5, fig.height=10}
+prelim.data %>% ggplot(aes(x=(n), y = g))+
+  geom_point()+
+  xlim(0,2100)+
+  facet_grid(Taxon~., scales='free')+
+  ylim(-3.5,3.5)+
+  geom_hline(yintercept=0, linetype="dashed")
+```
+
+(Promislow 1998 has one sample size of >10,000) and is not shown here.
+From these plots we can see that with increased sample size the effect sizes are closer to zero.
+Thistrend should be taken into account as meta-analytic models are wighted by 1/variance.
+
+####Generations
+
+We recorded the number of generations of experimental exolution each study used. The number of generations proved a negligable predictor in the meta-analytic models and can be seen here:
+
+```{r, fig.width=8, fig.height=7}
+prelim.data %>% ggplot(aes(x=Generations, y=g, color=Taxon))+
+  geom_point()+
+  ylim(-3.5,3.5)+
+  geom_hline(yintercept=0, linetype="dashed")
+```

### 2018-02-28 meta_analysis_sexual_selection_pop_fitness.Rmd
Luke initial work

--- 2018-02-27 Working Draft/Meta-Analysis on Sexual Selection and Population Fitness.Rmd
@@
 ---
-title: "Effects of sexual selection on non-sexual fitness components: a meta-analysis"
+title: 'Effects of sexual selection on non-sexual fitness components: a meta-analysis'
+author: "Justin Cally, University of Melbourne"
 subtitle: Supplementary Material
-author: "Justin Cally, University of Melbourne"
-output: html_notebook
+output:
+  html_document:
+    toc: true # table of content true
+    toc_float: true # make 
+    depth: 3  # upto three depths of headings (specified by #, ## and ###)
+    number_sections: false  ## if you want number sections at each table header
+    theme: yeti # lovely fonts and colours
+    code_folding: hide # awesome buttons to show/hide the code
+  pdf_document: default
 ---
 
-```{r warning=FALSE, message=FALSE}
+```{r warning=FALSE, message=FALSE, results='hide'}
 library(knitr)
@@
 library(reshape2)
-```
-
-# Methods
+source("Vdodge_function.R") # nice function for ggplot
+```
+
+```{r echo=FALSE, results='hide'}
+library(knitr) # set up cacheing to save time when re-building the html document
+```
+`r opts_chunk$set(cache=TRUE)`
+
+## Supplementary Methods
 
@@
 
-##Literature Search (Extended methods from paper)
+### Literature Search
 
@@
 
-1. We searched ISI Web of Science and Scopus on 9th June 2017. Notably, these resulted in a different set of returns (**PRISMA Figure**).
+1. We searched ISI Web of Science and Scopus on 9th June 2017. The two search engines produded a somewhat different set of papers (**PRISMA Figure**).
 
@@
 
+We used the following search on ISI Web of Science:
+
 Topic (TS) = “Sexual Selection” OR Promisc* OR Monogam* OR Polygam* OR Polyandr* OR Polygyn* OR “Mate choice”
@@
 
+We used the following search on Scopus:
+
 TITLE-ABS-KEY = “Sexual Selection” OR Promisc* OR Monogam* OR Polygam* OR Polyandr* OR Polygyn* OR “Mate choice”
@@
 
-In addition to studies found from the literature search we also included three relevant studies that were identified during scoping but not picked up in the subsequent formal searches (Partridge 1980; Price et al.
+### Additions to the literature search
+
+In addition to studies found from the literature search we also included three relevant studies that we found, which were not picked up in the subsequent formal searches (Partridge 1980; Price et al.
 2010; Savic Veselinovic et al.
-2013) that were missed by the database searches (**PRISMA Figure**).
-
-4.
-After removing duplicates, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution).
+2013; **PRISMA Figure**).
+
+### Data extraction
+
+After removing duplicates papers recovered from both ISI and Scopus, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution).
 This left 130 papers, for which we read the full text and applied the following selection criteria:
@@
 We therefore relied on our best judgement when deciding which studies to exclude (see Table XXX).
-The inclusion/exlusion critera as applied to each study are detailed in an accompaning spreadsheet.
-
-```{r}
-Eligibility.criteria <- read.csv('Eligibility Workbook(22.02).csv', fileEncoding="UTF-8")
-Eligibility.criteria %>% pander(split.cell = 20, split.table = 250, style = "grid")
-```
-
-##Data Extraction
-
-The raw extracted data table is presented in the accompanying data folder.
+The inclusion/exlusion critera as applied to each study are detailed in **Table S1**.
+
+**Table S1:** WRITE TABLE LEGEND.
+ <br/><br/> 
+<input type=button class=hideshow></input>
+```{r}
+Eligibility.criteria <- read.csv('data/Eligibility Workbook(22.02).csv', 
+                                 fileEncoding="UTF-8")
+Eligibility.criteria %>% 
+  pander(split.cell = 40, split.table = Inf)
+```
+
+### Effect Size Calculation
+
+A spreadsheet describing the data that was extracted from each of the included studies is included as supplementary material.
 It details the type of data collected for each study (arithmatic means, SD, n, F-statistic, chi-squared, proportion etc.).
@@
 3.
-If means were not reported then we ecxtracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package.
+If means were not reported then we extracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package.
 Summary statistics included _F_, _z_, _t_ and _chi^2^_.
@@
 
-4. The covariates collected were extensive (**DATA TABLE**) and are discussed later. They were all regarded as potentially explaining trends in effect size or bias and hence were collected.
-
-##Effect Size Calculation
-
-> Not sure what to do about these calculations.
-I did not really lay them out neatly and the compute.es does not really return neat values.
-My calculations were done in a clunkier manual way.
-And are shown below.
-
-**SS- will be group one with increased SS being group two**
-
-####Almbro and Simmons 2014**
-
-######Brood Number (No Distinction) 
-```{r}
-mes(15.4, 18, 10.071, 10.071, 207, 207, dig = 3)
-```
-
-######Strength (Stressed) 
-```{r}
-mes(0.047, 0.094, 0.05724, 0.16217, 91, 91, dig = 3)
-```
-
-##The Meta-Analysis Dataset
-
-### Setup
-
-Read in csv file 
-```{r}
-prelim.data <- read.csv('Preliminary data frame 22.2.18.csv')
-kable(prelim.data)
-```
-
-###Explanation of Dataframe:
+4. We also collected various covariates for some of the studies (**DATA TABLE**), which are discussed later.
+
+## The effect size dataset
+
+### Table of effect sizes
+
+**Table S2:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
+ <br/><br/> 
+<input type=button class=hideshow></input>
+```{r}
+# Load the data and clean up the variable formats
+prelim.data <- read.csv('data/Preliminary data frame 22.2.18.csv')
+prelim.data$Study.ID <- prelim.data$Study.ID %>% factor()
+prelim.data$Taxon <- prelim.data$Taxon %>% factor()
+prelim.data$Group.ID <- prelim.data$Group.ID %>% factor()
+prelim.data$Authors <- prelim.data$Authors %>% factor()
+prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
+prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
+prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor()
+prelim.data$Species <- prelim.data$Species %>% factor()
+#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
+prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
+prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor() %>% relevel(ref="NO")
+prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor() %>% relevel(ref="0")
+prelim.data$Post.cop <- prelim.data$Post.cop %>% factor() %>% relevel(ref="0")
+prelim.data$Ratio.Category <- prelim.data$Ratio.Category %>% factor() %>% relevel(ref="Low")
+prelim.data$Density.Category <- prelim.data$Density.Category %>% factor() %>% relevel(ref="Low")
+prelim.data$SSS.Categorical <- prelim.data$SSS.Categorical %>% factor() %>% relevel(ref="Low")
+prelim.data$Blinding <- prelim.data$Blinding %>% factor()
+
+prelim.data %>% pander(split.cell = 40, split.table = Inf)
+```
 
 **Study ID**: An ID given to the published paper the effect size is sourced from
-
 **Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup
-
 **Species and Species ID**: Same thing
-
 **SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment
-
 **Ratio Category**: A three level category for the ratio of males to females (high, medium, low).
-
 **Density Category**: A three level category for the density of males to females (high, medium, low).
-
 **SSS.Categorical**: A three level category for the **density & the ratio** of males to females (high medium, low). 
-
 **Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)
-
 **Blind**: Whether the study was blind or not
-
 **Generations** The number of generations run before fitness outcomes were measured
-
 **Enforced Monogamy**: Whether the study had the low sexual selection treatment as enforced monogamy (YES) or not (NO).
@@
 Some used FB vs MB, where FB is the SS (low intensity).
-
 **Sex**: Whether the fitness outcome was measured for females (F), males (M) or both (B). Studies that reported 'both' would pool results from males and females.
-
 **Ambiguous**: Is the fitness outcome ambiguous (YES) or not ambigous (NO). Ambiguous outcomes may be those that may not necessarily be directional, that is to say they may be a life history trait. 
-
 **Outcome Class**: Grouped as Direct, Indirect or Ambiguous.
-
 **Environment**: In the methods of the papers included in this study it was usually stated whether additional modifications to the experimental lines were made.
@@
 However, sometimes the paper was ambiguous in what lines had added stress or the results from stressed and unstressed lines were pooled together, in this case we label it as 'Not Stated'.
-
 **g**: Hedge's g calculated using the compute.es package
-
 **var.g**: The within study variance associated with the effect size, g
-
 **mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance).
 Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.)
-
 **JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.
 
-_______________________________________________
-
-### Factor and level data
-
-A lot of the covariates are categorical, so here we assign them as factors and relevel them.
-
-```{r}
-prelim.data$Study.ID <- prelim.data$Study.ID %>% factor
-prelim.data$Taxon <- prelim.data$Taxon %>% factor
-prelim.data$Group.ID <- prelim.data$Group.ID %>% factor 
-prelim.data$Authors <- prelim.data$Authors %>% factor
-prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
-prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
-prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor
-prelim.data$Species <- prelim.data$Species %>% factor
-#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
-prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor %>% relevel(ref="Indirect")
-prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor %>% relevel(ref="NO")
-prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor %>% relevel(ref="0")
-prelim.data$Post.cop <- prelim.data$Post.cop %>% factor %>% relevel(ref="0")
-prelim.data$Ratio.Category <- prelim.data$Ratio.Category %>% factor %>% relevel(ref="Low")
-prelim.data$Density.Category <- prelim.data$Density.Category %>% factor %>% relevel(ref="Low")
-prelim.data$SSS.Categorical <- prelim.data$SSS.Categorical %>% factor %>% relevel(ref="Low")
-prelim.data$Blinding <- prelim.data$Blinding %>% factor
-```
-
 ________________________________________________
 
-###The Effect Size Dataset
+### Table of sample sizes
 
@@
 
-```{r}
+**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
+ <br/><br/> 
+<input type=button class=hideshow></input>
+```{r message=FALSE}
 n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
-n.stressed.ones <- 
-prelim.data %>% summarise(Effect_sizes = n(), 
-                       Publications = prelim.data$Study.ID %>% unique %>% length,
+prelim.data %>% 
+  summarise(
+    Effect_sizes_.Totalq = n(), 
+    Publications = prelim.data$Study.ID %>% unique() %>% length(),
     Blind_experiments = n.blind.ones,
@@
     Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
-                       Different_species =  prelim.data$Species %>% unique %>% length,
+    Different_species =  prelim.data$Species %>% unique() %>% length(),
     Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
@@
     Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
-                       Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt %>%
+    Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt() %>%
   mutate(variable = gsub("_", " ", variable),
@@
          variable = gsub("q", ")", variable)) %>% 
-  rename_("n" = "value", " " = "variable") %>% pander(split.cell = 40, split.table = Inf)
-```
-
-###Forest plot using ggplot
+  rename_("n" = "value", " " = "variable") %>% 
+  pander(split.cell = 40, split.table = Inf)
+```
+
+### Forest plot
 
@@
 
-Using ggplot the forest plot is grouped according to environment and sex, with multiple effect sizes on one row for a given study
-
-```{r, fig.height=30, fig.width=22.5}
-#Create standard random effectrs model
+> Luke says: if you are plotting RESIDUAL effect sizes, doesn't that mean this plots shows each effect size, relative to the grand mean effect size?
+Like, -0.05 means it is below average, but the effect is still positive since the grand mean is +0.1.
+This is probably not what we want.
+
+> I have modified the code below so that it plots the resid + the grand mean.
+But I think since model is intercept only, this might be the same thing as the raw data...
+not sure.
+Have a think, or just plot all the raw effect sizes +/- their 95% CIs, instead of the residuals.
+
+> Also try to make it clear what positive g means (I guess positive g means higher fitness when SS is present/strong?)
+
+```{r, fig.height=25, fig.width=10}
+# Run standard random effects model
 forest.model <- rma(g, var.g, mods = ~ 1, method = "REML", data = prelim.data)
 
-#Obtain residuals
+# Obtain residuals
 resstandards <- (rstandard.rma.uni(forest.model, type="response"))
 
-#Create new df with residuals replacing raw
-df.forest.model <- prelim.data
-df.forest.model$g <- resstandards$resid
+# Obtain grand mean effect size    <- ADDED BY LUKE
+grand.mean <- as.numeric(forest.model$b)
+
+# Create new df with residuals replacing raw
+df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
+df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
 df.forest.model$sei <- resstandards$se
 
-#Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
+# Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
 df.forest.model$Outcome_f = factor(df.forest.model$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
 
-#define upper and lower bounds
+# define upper and lower bounds
 df.forest.model$lowerci <- df.forest.model$g - 1.96*((df.forest.model$sei))
@@
 
-#Get author and year in one
-df.forest.model$AuthorYear = paste(df.forest.model$Authors, df.forest.model$Year, sep=" ")
+# Get author and year in one
+short.author.names <- data.frame(long = df.forest.model$Authors %>% unique(),
+                                 short = df.forest.model$Authors %>% unique() %>% 
+  as.character() %>% 
+  strsplit(split = ",") %>% 
+  sapply(FUN=function(x) x[1])) %>%
+  left_join(df.forest.model %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
+  mutate(suffix = "")
+
+# Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
+dups <- with(short.author.names, table(short, Year)) %>% melt()
+dups <- dups[dups$value > 1, ]
+for(i in 1:nrow(dups)){
+  short.author.names$suffix[
+    short.author.names$short == dups$short[i] &
+      short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
+}
+
+# Add the AuthorYear column to the dataframe of effect sizes
+short.author.names <- short.author.names %>%
+  mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
+  select(long, AuthorYear)
+df.forest.model <- df.forest.model %>% 
+  left_join(short.author.names, by = c("Authors" = "long"))
 
 #Generate a plot
-p.meta <- ggplot(df.forest.model, aes(y=reorder(AuthorYear, -g), x=g, xmin=lowerci, xmax=upperci, shape=Sex, color = Outcome.Class)) +
- #Add data points and color them black
-geom_point(size=2)+
-geom_errorbarh(data=df.forest.model, aes(xmin= lowerci, xmax = upperci) ,height=.1)+
-  #Specify the limits of the x-axis and relabel it to something more meaningful
-  scale_x_continuous(limits=c(-5,5), name='Standardized Mean Difference (g)')+
-  #Give y-axis a meaningful label
-  ylab('Reference')+
-  #Add a vertical dashed line indicating an effect size of zero, for reference
+p.meta <- df.forest.model %>% 
+  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female")) %>%
+  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
+  geom_errorbarh(aes(xmin = lowerci, xmax = upperci), height = 0.1) +
+  geom_point(size = 2) +  #Add data points and color them black
+  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
+  scale_color_discrete(name = "Relationship\nto fitness") + 
+  ylab('Reference') + 
   geom_vline(xintercept=0, color='black', linetype='dashed')+
-  #Create sub-plots (i.e., facets) based on levels of setting
-  #And allow them to have their own unique axes (so authors don't redundantly repeat)
   facet_grid(Outcome_f~., scales= 'free', space='free')+
   theme(strip.text.y = element_text(angle = 0))
+ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
 p.meta
 ```
+<br></br>
+**Figure 1:** Forest plot of effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
+Rows with multiple data points denote studies that provided multiple effect sizes.
 
 ___________________
-###Effect size of subgroups
-
->The following documents how i could run individual models for each outcome or outcome.class of interest and then plot them.
+
+### Effect size differs depending on the response variable
+
+>The following documents how I could run individual models for each outcome or outcome.class of interest and then plot them.
 This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment)
 
-There is not really enough direct outcomes to analyse by itself so hence we combine with indirect later
-```{r}
-#Ambiguous outcomes
-
-model.Ambiguous <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Ambiguous"), intercept = T ,data = prelim.data)
-
-summary(model.Ambiguous)
-```
-
-```{r}
-#Indirect outcomes
-
-model.Indirect <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Indirect"), intercept = T ,data = prelim.data)
-
-summary(model.Indirect)
-```
-
-```{r}
-#Direct outcomes
-
-model.Direct <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Direct"), data = prelim.data)
-
-summary(model.Direct)
-```
-
-Now let's combine into a data frame and plot. The following plot could then be added to the large forest plot as summary polygons or summary points with error bars.
-
-```{r}
-#Data frame
-Outcome.category <- c('Ambiguous', 'Indirect', 'Direct')
-Estimate <- c(model.Ambiguous$b, model.Indirect$b, model.Direct$b)
-l.ci <- c(model.Ambiguous$ci.lb, model.Indirect$ci.lb, model.Direct$ci.lb)
-u.ci <- c(model.Ambiguous$ci.ub, model.Indirect$ci.ub, model.Direct$ci.ub)
-data.1 <- data.frame(Outcome.category, Estimate, l.ci, u.ci)
-
-#plot
-
-data.1 %>% ggplot(aes(x = Estimate, y= Outcome.category)) + 
+> Nice idea, but I think the correct way to do this is to fit Outcome.class as a moderator, and then use predict() to find the average effect size within each of the 3 levels, as you have done below.
+I coded something below, but it's wrong:
+
+```{r}
+model.outcome.class <- rma(g, var.g,
+                           mods = ~ Outcome.Class, 
+                           method = "REML", 
+                           intercept = TRUE, 
+                           data = prelim.data)
+
+# Get the intercept (i.e. the grand mean for 'ambiguous', and the effects for the others)
+mod.table <- do.call("cbind", model.outcome.class[names(model.outcome.class) %in% c("b", "ci.lb", "ci.ub")])
+
+data.frame(Outcome.class = c("Ambiguous", "Direct", "Indirect"),
+           mod.table) %>%
+  ggplot(aes(y = Outcome.class, x = V1))  +
+  geom_vline(xintercept = 0, linetype = 2) +
+  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height=0) +
   geom_point() + 
-  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
-  geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, size=1) +
-  ylab("Outcome Category")+
-  xlab("Effect Size")+
-  xlim(-.2, .5)+
-  ggtitle('Meta-Analysis Results')
-```
+  xlab("Effect size and 95% CIs")
+```
+
+<!-- There is not really enough direct outcomes to analyse by itself so hence we combine with indirect later -->
+<!-- ```{r} -->
+<!-- #Ambiguous outcomes -->
+
+<!-- model.Ambiguous <- rma(g, var.g, -->
+<!--                        mods = ~ 1,  -->
+<!--                        method = "REML",  -->
+<!--                        subset = (Outcome.Class == "Ambiguous"),  -->
+<!--                        intercept = TRUE,  -->
+<!--                        data = prelim.data) -->
+
+<!-- summary(model.Ambiguous) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- #Indirect outcomes -->
+
+<!-- model.Indirect <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Indirect"), intercept = T ,data = prelim.data) -->
+
+<!-- summary(model.Indirect) -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- #Direct outcomes -->
+
+<!-- model.Direct <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Direct"), data = prelim.data) -->
+
+<!-- summary(model.Direct) -->
+<!-- ``` -->
+
+<!-- Now let's combine into a data frame and plot. The following plot could then be added to the large forest plot as summary polygons or summary points with error bars.  -->
+
+<!-- ```{r} -->
+<!-- #Data frame -->
+<!-- Outcome.category <- c('Ambiguous', 'Indirect', 'Direct') -->
+<!-- Estimate <- c(model.Ambiguous$b, model.Indirect$b, model.Direct$b) -->
+<!-- l.ci <- c(model.Ambiguous$ci.lb, model.Indirect$ci.lb, model.Direct$ci.lb) -->
+<!-- u.ci <- c(model.Ambiguous$ci.ub, model.Indirect$ci.ub, model.Direct$ci.ub) -->
+<!-- data.1 <- data.frame(Outcome.category, Estimate, l.ci, u.ci) -->
+
+<!-- #plot -->
+
+<!-- data.1 %>% ggplot(aes(x = Estimate, y= Outcome.category)) +  -->
+<!--   geom_point() + -->
+<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
+<!--   geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, size=1) + -->
+<!--   ylab("Outcome Category")+ -->
+<!--   xlab("Effect Size")+ -->
+<!--   xlim(-.2, .5)+ -->
+<!--   ggtitle('Meta-Analysis Results') -->
+<!-- ``` -->
 
@@
 
-###Model predictions
-
-####Does the effect of sexual selection differ between species?
+### Effect size differs between taxa
 
@@
   filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
-  mutate(Sex = as.character(Sex), Environment = as.character(Environment), Outcome.Class.2 = as.character(Outcome.Class), Enforced.Monogamy = as.character(Enforced.Monogamy))
-
-#RWe need to make sure the factors are leveled in the same order as we write our prediction function (below)
+  mutate(Sex = as.character(Sex), 
+         Environment = as.character(Environment), 
+         Outcome.Class.2 = as.character(Outcome.Class), 
+         Enforced.Monogamy = as.character(Enforced.Monogamy))
+
+# Make sure the factors are leveled in the same order as we write our prediction function (below)
 restricted.data$Environment <- restricted.data$Environment %>% factor %>% relevel(ref="Unstressed")
@@
 
-#run model again with restricted data 
+# run meta-analysis using the restricted data, and moderators
 model.complete <- rma.mv(g, var.g, 
@@
 
-#Note that the data is subsetted
 summary(model.complete) 
-
 ```
@@
 
-Note that to get vertical position dodge to use in the ggplot meta-analysis we need to utilise a vertical position dodge.
-We can obtain this formula from the following github page by Jared Lander: https://github.com/jaredlander/coefplot/blob/master/R/position.r
-```{r include=FALSE}
-# Detect and prevent collisions.
-# Powers dodging, stacking and filling.
-collidev <- function(data, height = NULL, name, strategy, check.height = TRUE) {
-    # Determine height
-    if (!is.null(height)) {
-        # height set manually
-        if (!(all(c("ymin", "ymax") %in% names(data)))) {
-            data$ymin <- data$y - height / 2
-            data$ymax <- data$y + height / 2
-        }
-    } else {
-        if (!(all(c("ymin", "ymax") %in% names(data)))) {
-            data$ymin <- data$y
-            data$ymax <- data$y
-        }
-
-        # height determined from data, must be floating point constant
-        heights <- unique(data$ymax - data$ymin)
-        heights <- heights[!is.na(heights)]
-
-        #   # Suppress warning message since it's not reliable
-        #     if (!zero_range(range(heights))) {
-        #       warning(name, " requires constant height: output may be incorrect",
-        #         call. = FALSE)
-        #     }
-        height <- heights[1]
-    }
-
-    # Reorder by x position, relying on stable sort to preserve existing
-    # ordering, which may be by group or order.
-    data <- data[order(data$ymin), ]
-
-    # Check for overlap
-    intervals <- as.numeric(t(unique(data[c("ymin", "ymax")])))
-    intervals <- intervals[!is.na(intervals)]
-
-    if (length(unique(intervals)) > 1 & any(diff(scale(intervals)) < -1e-6)) {
-        warning(name, " requires non-overlapping y intervals", call. = FALSE)
-        # This is where the algorithm from [L. Wilkinson. Dot plots.
-        # The American Statistician, 1999.] should be used
-    }
-
-    if (!is.null(data$xmax)) {
-        plyr::ddply(data, "ymin", strategy, height = height)
-    } else if (!is.null(data$x)) {
-        data$xmax <- data$x
-        data <- plyr::ddply(data, "ymin", strategy, height = height)
-        data$x <- data$xmax
-        data
-    } else {
-        stop("Neither x nor xmax defined")
-    }
-}
-
-# Stack overlapping intervals.
-# Assumes that each set has the same horizontal position
-pos_stackv <- function(df, height) {
-    if (nrow(df) == 1) return(df)
-
-    n <- nrow(df) + 1
-    x <- ifelse(is.na(df$x), 0, df$x)
-    if (all(is.na(df$y))) {
-        heights <- rep(NA, n)
-    } else {
-        heights <- c(0, cumsum(x))
-    }
-
-    df$xmin <- heights[-n]
-    df$xmax <- heights[-1]
-    df$x <- df$xmax
-    df
-}
-
-# Stack overlapping intervals and set height to 1.
-# Assumes that each set has the same horizontal position.
-pos_fillv <- function(df, height) {
-    stacked <- pos_stackv(df, height)
-    stacked$xmin <- stacked$xmin / max(stacked$xmax)
-    stacked$xmax <- stacked$xmax / max(stacked$xmax)
-    stacked$x <- stacked$xmax
-    stacked
-}
-
-# Dodge overlapping interval.
-# Assumes that each set has the same horizontal position.
-pos_dodgev <- function(df, height) {
-    n <- length(unique(df$group))
-    if (n == 1) return(df)
-
-    if (!all(c("ymin", "ymax") %in% names(df))) {
-        df$ymin <- df$y
-        df$ymax <- df$y
-    }
-
-    d_height <- max(df$ymax - df$ymin)
-
-    # df <- data.frame(n = c(2:5, 10, 26), div = c(4, 3, 2.666666,  2.5, 2.2, 2.1))
-    # ggplot(df, aes(n, div)) + geom_point()
-
-    # Have a new group index from 1 to number of groups.
-    # This might be needed if the group numbers in this set don't include all of 1:n
-    groupidy <- match(df$group, sort(unique(df$group)))
-
-    # Find the center for each group, then use that to calculate xmin and xmax
-    df$y <- df$y + height * ((groupidy - 0.5) / n - .5)
-    df$ymin <- df$y - d_height / n / 2
-    df$ymax <- df$y + d_height / n / 2
-
-    df
-}
-
-#' Adjust position by dodging overlaps to the side.
-#'
-#' @inheritParams ggplot2::position_identity
-#' @param height Dodging height, when different to the height of the individual
-#'   elements. This is useful when you want to align narrow geoms with wider
-#'   geoms. See the examples for a use case.
-#' @family position adjustments
-#' @export
-#' @examples
-#' ggplot(mtcars, aes(factor(cyl), fill = factor(vs))) +
-#'   geom_bar(position = "dodge")
-#'
-#' ggplot(diamonds, aes(price, fill = cut)) +
-#'   geom_histogram(position="dodge")
-#' # see ?geom_boxplot and ?geom_bar for more examples
-#'
-#' # To dodge items with different heights, you need to be explicit
-#' df <- data.frame(x=c("a","a","b","b"), y=2:5, g = rep(1:2, 2))
-#' p <- ggplot(df, aes(x, y, group = g)) +
-#'   geom_bar(
-#'     stat = "identity", position = "dodge",
-#'     fill = "grey50", colour = "black"
-#'   )
-#' p
-#'
-#' # A line range has no height:
-#' p + geom_linerange(aes(ymin = y-1, ymax = y+1), position = "dodge")
-#' # You need to explicitly specify the height for dodging
-#' p + geom_linerange(aes(ymin = y-1, ymax = y+1),
-#'   position = position_dodge(width = 0.9))
-#'
-#' # Similarly with error bars:
-#' p + geom_errorbar(aes(ymin = y-1, ymax = y+1), width = 0.2,
-#'   position = "dodge")
-#' p + geom_errorbar(aes(ymin = y-1, ymax = y+1, height = 0.2),
-#'   position = position_dodge(width = 0.90))
-#'
-position_dodgev <- function(height = NULL) {
-    ggproto(NULL, PositionDodgeV, height = height)
-}
-
-PositionDodgeV <- ggproto("PositionDodgeV", Position,
-                          required_aes = "y",
-                          height = NULL,
-                          setup_params = function(self, data) {
-                              if (is.null(data$ymin) && is.null(data$ymax) && is.null(self$height)) {
-                                  warning("height not defined. Set with `position_dodgev(height = ?)`",
-                                          call. = FALSE)
-                              }
-                              list(height = self$height)
-                          },
-
-                          compute_panel = function(data, params, scales) {
-                              collidev(data, params$height, "position_dodgev", pos_dodgev, check.height = FALSE)
-                          }
-)
-```
-
 Third, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.
 
-> I would liker to know how to join a table with mean, and CI values to the forest plots I am generating.
+> I would like to know how to join a table with mean, and CI values to the forest plots I am generating.
+
+> You can make tables with ggplot, and bind them to graphs using the grid and gridExtra packages. It's pretty hard! See ?gridExtra::tableGrob. 
+> Honestly might be easier to do it manually with e.g. Inkscape or Illustrator.
 
@@
 More so that that confidence limits increase, rather than radically changing direction of effect.
-However we can se from this that under stressed environments, females twnd to
+However we can see from this that under stressed environments, females tend to
 
@@
 Note that the trim and fill method does not work with rma.mv objects.
-However we can perform Eggers test using the ``ragtest()`` function.
+However we can perform Eggers test using the ``regtest()`` function.
 This tests for asymmetry via assessing relationships between effect size and a specified predictor.
-See ``?ragtest()`` for more information.
+See ``?regtest`` for more information.
 Also the eggers test does not work for rma.mv objects.
 ```{r}
-trim.ambig <- trimfill.rma.uni(model.Ambiguous)
-funnel.rma(trim.ambig)
-regtest(model.Ambiguous, predictor = "vi")
-funnel.rma(model.Indirect)
-regtest(model.Indirect, predictor = "vi")
-funnel.rma(model.Direct)
-regtest(model.Direct, predictor = "vi")
-funnel.rma(model.complete2, type="rstandard", yaxis = "sei")
+regtest(forest.model, predictor = "vi")
+
+# I cut all these out, since the trime-and-fill doesn't work, and those sub-models probably don't make sense
+# trim.ambig <- trimfill.rma.uni(model.Ambiguous)
+# funnel.rma(trim.ambig)
+# regtest(model.Ambiguous, predictor = "vi")
+# funnel.rma(model.Indirect)
+# regtest(model.Indirect, predictor = "vi")
+# funnel.rma(model.Direct)
+# regtest(model.Direct, predictor = "vi")
+# funnel.rma(model.complete2, type="rstandard", yaxis = "sei")
 ```
@@
 
+> Luke re-wrote this into a function, for neatness. You can replace 'dataset' and 'model' with whatever to save copy-pasting the code.
+
 ```{r, fig.height= 7, fig.width=10}
-#Funnel plot for indirect model
-
-#Make restricted data for indirect
-
-prelim.data.Indirect <- prelim.data %>% filter(Outcome.Class == "Indirect")
-
-#read in apatheme
-#My APA-format theme
-apatheme=theme_bw()+
+#Funnel plot for all outcome classes
+
+make.funnel <- function(dataset, model){
+
+  apatheme <- theme_bw() +  #My APA-format theme
     theme(panel.grid.major=element_blank(),
@@
 
-#Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
-estimate = model.Indirect$b
-se = model.Indirect$se
-
-#Store a vector of values that spans the range from 0
-#to the max value of impression (standard error) in your dataset.
-#Make the increment (the final value) small enough (I choose 0.001)
-#to ensure your whole range of data is captured
-se.seq=seq(0, max(sqrt(prelim.data.Indirect$var.g)), 0.001)
-
-#Now, compute vectors of the lower-limit and upper limit values for
-#the 95% CI region, using the range of SE that you generated in the previous step, and the stored value of your meta-analytic estimate.
-ll95 = estimate-(1.96*se.seq)
-ul95 = estimate+(1.96*se.seq)
-
-#You can do this for a 99% CI region too
-ll99 = estimate-(3.29*se.seq)
-ul99 = estimate+(3.29*se.seq)
-
-#And finally, do the same thing except now calculating the confidence interval
-#for your meta-analytic estimate based on the stored value of its standard error
-meanll95 = estimate-(1.96*se)
-meanul95 = estimate+(1.96*se)
-
-#Now, smash all of those calculated values into one data frame (called 'dfCI').
-#You might get a warning about '...row names were found from a short variable...'
-#You can ignore it.
-dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
+  estimate <- model$b
+  SE <- model$se
+  se.seq <- seq(0, max(sqrt(dataset$var.g)), 0.001)
+  dfCI <- data.frame(ll95 = estimate - (1.96 * se.seq), 
+                     ul95 = estimate + (1.96 * se.seq), 
+                     ll99 = estimate - (3.29 * se.seq), 
+                     ul99 = estimate + (3.29 * se.seq), 
+                     se.seq = se.seq, 
+                     meanll95 = estimate - (1.96 * SE), 
+                     meanul95 = estimate + (1.96 * SE))
 
   #Now we can actually make the funnel plot.
-#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
-fp = ggplot(prelim.data.Indirect, aes_string(x = sqrt(prelim.data.Indirect$var.g), y =prelim.data.Indirect$g)) +
-#Add your data-points to the scatterplot
+  ggplot(dataset, aes(x = sqrt(var.g), y = g)) +
     geom_point(shape = 1) +
-#Give the x- and y- axes informative labels
-  xlab('Standard Error') + ylab('g')+
-#Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
-#to the lower and upper limits of your 95% CI region,
-#And dashed lines corresponding to your 99% CI region
-  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
+    xlab("Standard Error") + ylab("Effect size (Hedges' g)") +
+    geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) + # confidence lines
     geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
@@
     #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-#at the top of the figure once we swap the x- and y-axes...
-  scale_x_reverse()+
-#Specify the range and interval for the tick-marks of the y-axis (Zr);
-#Choose values that work for you based on your data
-  scale_y_continuous(breaks=seq(-1.25,2,0.25))+
-#And now we flip the axes so that SE is on y- and Zr is on x-
-  coord_flip()+
-#Finally, apply my APA-format theme (see code at end of post).
-#You could, alternatively, specify theme_bw() instead.
-  apatheme
-
-#Call the pretty funnel plot
-fp
+    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI, colour = "red") +
+    geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI, colour = "red") +
+    scale_x_reverse() +
+    # scale_y_continuous(breaks = seq(-1.25,2,0.25)) + #Choose values that work for you based on your data
+    coord_flip() +
+    theme_classic()
+    # apatheme
+}
+
+make.funnel(prelim.data, forest.model)
 ```
@@
 ```
+
+<!-- Some JavaScript to control the buttons to show/hide the big tables -->
+<script>
+$( "input.hideshow" ).each( function ( index, button ) {
+  button.value = 'Hide Output';
+  $( button ).click( function () {
+    var target = this.nextSibling ? this : this.parentNode;
+     target = target.nextSibling.nextSibling.nextSibling.nextSibling.nextSibling;
+    if ( target.style.display == 'block' || target.style.display == '' ) {
+      target.style.display = 'none';
+      this.value = 'Show Output';
+    } else {
+      target.style.display = 'block';
+      this.value = 'Hide Output';
+    }
+  } );
+} );
+</script>

### 2018-03-01 meta_analysis_sexual_selection_pop_fitness.Rmd
Luke and Justin meeting

@@
 library(reshape2)
+library(RColorBrewer)
 source("Vdodge_function.R") # nice function for ggplot
@@
 **Study ID**: An ID given to the published paper the effect size is sourced from
+
 **Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup
+
 **Species and Species ID**: Same thing
+
 **SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment
+
 **Ratio Category**: A three level category for the ratio of males to females (high, medium, low).
+
 **Density Category**: A three level category for the density of males to females (high, medium, low).
+
 **SSS.Categorical**: A three level category for the **density & the ratio** of males to females (high medium, low).
+
 **Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)
@@
 # Make sure the factors are leveled in the same order as we write our prediction function (below)
-restricted.data$Environment <- restricted.data$Environment %>% factor %>% relevel(ref="Unstressed")
-restricted.data$Sex <- restricted.data$Sex %>% factor %>% relevel(ref="M")
-restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor %>% relevel(ref="Indirect")
-
-# run meta-analysis using the restricted data, and moderators
+restricted.data$Environment <- restricted.data$Environment %>% factor() %>% relevel(ref="Unstressed")
+restricted.data$Sex <- restricted.data$Sex %>% factor() %>% relevel(ref="M")
+restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
+restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Mouse")
+
 model.complete <- rma.mv(g, var.g, 
-                         mods = ~ 1 + Sex + Environment + Taxon + Sex:Environment, 
-                         random = ~ 1 | Study.ID/Outcome, 
+                         mods = ~ 1 + Sex * Environment, # << ----- Add big model, then cull predictors to this one
+                         random = list(~ 1 | Study.ID, 
+                                       ~ 1 | Outcome), 
                          method = "REML", 
@@
 
-# I cut all these out, since the trime-and-fill doesn't work, and those sub-models probably don't make sense
+# I cut all these out, since the trim-and-fill doesn't work, and those sub-models probably don't make sense
 # trim.ambig <- trimfill.rma.uni(model.Ambiguous)
@@
   apatheme <- theme_bw() +  #My APA-format theme
-    theme(panel.grid.major=element_blank(),
-          panel.grid.minor=element_blank(),
-          panel.border=element_blank(),
-          axis.line=element_line(),
-          text=element_text(family='Times'),
-          legend.position='none')
+    theme(panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.border = element_blank(),
+          axis.line = element_line(),
+          text = element_text(family = 'Times'),
+          legend.position = 'none')
 
@@
 
-  #Now we can actually make the funnel plot.
   ggplot(dataset, aes(x = sqrt(var.g), y = g)) +
-    geom_point(shape = 1) +
+    geom_point(alpha = 0.4) +
     xlab("Standard Error") + ylab("Effect size (Hedges' g)") +
@@
     #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI, colour = "red") +
-    geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI, colour = "red") +
+    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI, colour = "tomato") +
+    geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI, colour = "tomato") +
     scale_x_reverse() +
@@
     # apatheme
+
 }
@@
 
-```{r}
-
-```
-
 ```{r, fig.width=10, fig.height=8}
-prelim.data %>% ggplot(aes(x=JIF, y=(g)))+
+prelim.data %>% ggplot(aes(x=log10(JIF), y=(g)))+
   geom_jitter(color='darkgreen', alpha=.3, aes(size = (1/(var.g))))+
@@
 
-####Time-lag Bias
+#### Time-lag Bias
 
@@
 ```{r, fig.width=7.50, fig.height=6}
-prelim.data %>% ggplot(aes(x=Year, y=g))+
+prelim.data %>% 
+  ggplot(aes(x=Year, y=g))+
   geom_jitter(color='orange', alpha=.3, aes(size = (1/(var.g))))+
@@
 
-####Blinding
+#### Blinding
 
@@
   geom_jitter(aes(color=Blinding))+
-  geom_hline(yintercept=0, linetype = 'dotted')
+  geom_hline(yintercept=0, linetype = 'dotted') + 
+  theme(legend.position = "none")
 ```
@@
 ```{r, fig.width=5, fig.height=10}
-prelim.data %>% ggplot(aes(x=(n), y = g))+
+prelim.data %>% ggplot(aes(x=n, y = g))+
   geom_point()+
-  xlim(0,2100)+
+  scale_x_log10(breaks = c(10, 100, 1000, 10000)) + 
+  #xlim(0,2100)+
   facet_grid(Taxon~., scales='free')+
@@
 
-####Generations
+#### Generations
 
@@
 ```{r, fig.width=8, fig.height=7}
-prelim.data %>% ggplot(aes(x=Generations, y=g, color=Taxon))+
-  geom_point()+
+prelim.data %>% ggplot(aes(x=Generations, y=g, fill=Taxon))+
+  geom_point(shape=21, color = "grey20")+
   ylim(-3.5,3.5)+
-  geom_hline(yintercept=0, linetype="dashed")
+  geom_hline(yintercept=0, linetype="dashed") + 
+  scale_fill_brewer(palette = "Set3")
 ```

### 2018-03-01 meta_analysis_sexual_selection_pop_fitness.Rmd
Spellingz
1/3 Post meeting update

@@
 library(ggplot2)
+library(kableExtra)
 library(MuMIn)
@@
 
-**Table S1:** WRITE TABLE LEGEND.
+**Table S1:** An eligibility criteria was based on four features a study needed to include (discussed above), to be eligable for inclusion in the meta-analysis the study needed to satisfy all criteria.
+Here we applied a step-wise process to the studies that had their full-text read and excluded them when they first failed to meet the criteria.
+Additional notes documenting reasons behind exclusion were also taken.
  <br/><br/> 
@@
                                  fileEncoding="UTF-8")
-Eligibility.criteria %>% 
-  pander(split.cell = 40, split.table = Inf)
+kable(Eligibility.criteria, "html") %>%
+  kable_styling() %>%
+  scroll_box(width = "800px", height = "500px")
 ```
@@
 prelim.data$Post.cop <- prelim.data$Post.cop %>% factor() %>% relevel(ref="0")
-prelim.data$Ratio.Category <- prelim.data$Ratio.Category %>% factor() %>% relevel(ref="Low")
-prelim.data$Density.Category <- prelim.data$Density.Category %>% factor() %>% relevel(ref="Low")
-prelim.data$SSS.Categorical <- prelim.data$SSS.Categorical %>% factor() %>% relevel(ref="Low")
 prelim.data$Blinding <- prelim.data$Blinding %>% factor()
 
-prelim.data %>% pander(split.cell = 40, split.table = Inf)
+kable(prelim.data, "html") %>%
+  kable_styling() %>%
+  scroll_box(width = "800px", height = "500px")
 ```
@@
 
-**Ratio Category**: A three level category for the ratio of males to females (high, medium, low).
-
-**Density Category**: A three level category for the density of males to females (high, medium, low).
-
-**SSS.Categorical**: A three level category for the **density & the ratio** of males to females (high medium, low).
-
 **Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)
+
 **Blind**: Whether the study was blind or not
+
 **Generations** The number of generations run before fitness outcomes were measured
+
 **Enforced Monogamy**: Whether the study had the low sexual selection treatment as enforced monogamy (YES) or not (NO).
@@
 Some used FB vs MB, where FB is the SS (low intensity).
+
 **Sex**: Whether the fitness outcome was measured for females (F), males (M) or both (B). Studies that reported 'both' would pool results from males and females.
+
 **Ambiguous**: Is the fitness outcome ambiguous (YES) or not ambigous (NO). Ambiguous outcomes may be those that may not necessarily be directional, that is to say they may be a life history trait.
+
 **Outcome Class**: Grouped as Direct, Indirect or Ambiguous.
+
 **Environment**: In the methods of the papers included in this study it was usually stated whether additional modifications to the experimental lines were made.
@@
 However, sometimes the paper was ambiguous in what lines had added stress or the results from stressed and unstressed lines were pooled together, in this case we label it as 'Not Stated'.
-**g**: Hedge's g calculated using the compute.es package
-**var.g**: The within study variance associated with the effect size, g
+
+**g**: Hedge's g calculated using the compute.es package.
+
+**var.g**: The within study variance associated with the effect size, g.
+
 **mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance).
-Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.)
+Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.).
+
 **JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.
@@
 
-**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
+**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
  <br/><br/> 
@@
 ```
+ <br/><br/> 
+**Table S4:** Table of fitness outcomes included in our meta-analysis by sex.
+ <br/><br/> 
+<input type=button class=hideshow></input>
+```{r}
+Outcome_and_sex <- table(prelim.data$Outcome, prelim.data$Sex) %>%
+  pander(split.cell = 40, split.table = Inf)
+```
 
@@
 # Run standard random effects model
-forest.model <- rma(g, var.g, mods = ~ 1, method = "REML", data = prelim.data)
-
-# Obtain residuals
-resstandards <- (rstandard.rma.uni(forest.model, type="response"))
-
-# Obtain grand mean effect size    <- ADDED BY LUKE
-grand.mean <- as.numeric(forest.model$b)
-
-# Create new df with residuals replacing raw
-df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
-df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
-df.forest.model$sei <- resstandards$se
+# forest.model <- rma.mv(g, var.g, 
+#                        mods = ~ 1 + Sex * Environment + Taxon,
+#                        random = list(~ 1 | Study.ID, 
+#                                        ~ 1 | Outcome),
+#                        method = "REML", 
+#                        data = prelim.data)
+# 
+# # Obtain residuals
+# resstandards <- (rstandard.rma.mv(forest.model, 
+#                                    type="response"))
+# 
+# # Obtain grand mean effect size    <- ADDED BY LUKE
+# grand.mean <- as.numeric(forest.model$b)
+# 
+# # Create new df with residuals replacing raw
+# df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
+# df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
+# df.forest.model$sei <- resstandards$se
 
 # Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
-df.forest.model$Outcome_f = factor(df.forest.model$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
+prelim.data$Outcome_f = factor(prelim.data$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
 
 # define upper and lower bounds
-df.forest.model$lowerci <- df.forest.model$g - 1.96*((df.forest.model$sei))
-df.forest.model$upperci <- df.forest.model$g + 1.96*((df.forest.model$sei))
+prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
+prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))
 
 # Get author and year in one
-short.author.names <- data.frame(long = df.forest.model$Authors %>% unique(),
-                                 short = df.forest.model$Authors %>% unique() %>% 
+short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
+                                 short = prelim.data$Authors %>% unique() %>% 
   as.character() %>% 
@@
   sapply(FUN=function(x) x[1])) %>%
-  left_join(df.forest.model %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
+  left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
   mutate(suffix = "")
@@
   select(long, AuthorYear)
-df.forest.model <- df.forest.model %>% 
+prelim.data <- prelim.data %>% 
   left_join(short.author.names, by = c("Authors" = "long"))
@@
 #Generate a plot
-p.meta <- df.forest.model %>% 
+p.meta <- prelim.data %>% 
   mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
@@
   ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
-  geom_errorbarh(aes(xmin = lowerci, xmax = upperci), height = 0.1) +
-  geom_point(size = 2) +  #Add data points and color them black
+  geom_errorbarh(aes(xmin = lowerci, 
+                     xmax = upperci), height = 0.1) +
+  geom_point(size = 3) +  #Add data points and color them black
   scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
@@
   facet_grid(Outcome_f~., scales= 'free', space='free')+
-  theme(strip.text.y = element_text(angle = 0))
+  theme(strip.text.y = element_text(angle = 0))+
 ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
@@
 <br></br>
-**Figure 1:** Forest plot of effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
+**Figure 1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
 Rows with multiple data points denote studies that provided multiple effect sizes.
@@
 
->The following documents how I could run individual models for each outcome or outcome.class of interest and then plot them.
-This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment)
-
-> Nice idea, but I think the correct way to do this is to fit Outcome.class as a moderator, and then use predict() to find the average effect size within each of the 3 levels, as you have done below.
-I coded something below, but it's wrong:
-
-```{r}
-model.outcome.class <- rma(g, var.g,
-                           mods = ~ Outcome.Class, 
-                           method = "REML", 
-                           intercept = TRUE, 
-                           data = prelim.data)
-
-# Get the intercept (i.e. the grand mean for 'ambiguous', and the effects for the others)
-mod.table <- do.call("cbind", model.outcome.class[names(model.outcome.class) %in% c("b", "ci.lb", "ci.ub")])
-
-data.frame(Outcome.class = c("Ambiguous", "Direct", "Indirect"),
-           mod.table) %>%
-  ggplot(aes(y = Outcome.class, x = V1))  +
-  geom_vline(xintercept = 0, linetype = 2) +
-  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height=0) +
-  geom_point() + 
-  xlab("Effect size and 95% CIs")
-```
+> Let's just run one big model then cull from there
+
+<!-- >The following documents how I could run individual models for each outcome or outcome.class of interest and then plot them.
+This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment) -->
+
+<!-- > Nice idea, but I think the correct way to do this is to fit Outcome.class as a moderator, and then use predict() to find the average effect size within each of the 3 levels, as you have done below.
+I coded something below, but it's wrong: -->
+
+<!-- ```{r} -->
+<!-- model.outcome.class <- rma(g, var.g, -->
+<!--                            mods = ~ Outcome.Class,  -->
+<!--                            method = "REML",  -->
+<!--                            intercept = TRUE,  -->
+<!--                            data = prelim.data) -->
+
+<!-- # Get the intercept (i.e. the grand mean for 'ambiguous', and the effects for the others) -->
+<!-- mod.table <- do.call("cbind", model.outcome.class[names(model.outcome.class) %in% c("b", "ci.lb", "ci.ub")]) -->
+
+<!-- data.frame(Outcome.class = c("Ambiguous", "Direct", "Indirect"), -->
+<!--            mod.table) %>% -->
+<!--   ggplot(aes(y = Outcome.class, x = V1))  + -->
+<!--   geom_vline(xintercept = 0, linetype = 2) + -->
+<!--   geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height=0) + -->
+<!--   geom_point() +  -->
+<!--   xlab("Effect size and 95% CIs") -->
+<!-- ``` -->
 
@@
 
-From the previous forest plot and models we see that overall sexual selection is beneficial towards population fitness.
+<!-- From the previous forest plot and models we see that overall sexual selection is beneficial towards population fitness.
 Although this is heavily modulated by the individual outcome and the outcome class.
 We explore heterogeneity in more depth later in this document.
+-->
+
+### Exploring our data with the large set of covariates
+
+We collected data from fitness components that were deemed ambiguous as well as unambiguous.
+The ambiguous outcomes are likely to add in heterogeneity to the models and not help us in answering questions of fitness effects of sexual selection.
+A model utilising our complete dataset with many moderator variables would thus be:
+
+```{r}
+model.preliminary <- rma.mv(g, var.g, 
+                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + Generations + Blinding, # << ----- Add big model, then cull predictors to this one
+                         random = list(~ 1 | Study.ID, 
+                                       ~ 1 | Outcome), 
+                         method = "REML", 
+                         data = prelim.data)
+
+summary(model.preliminary)
+
+```
+<br></br>
+**A note on random effects** Here we utilise crossed random effects of Study.ID and Outcome.
+Nesting Outcomes within Study.ID can also be achieved through ``random = ~ 1 | Study.ID/Outcome``.
+However given that the same outcome is expected to be measured in the same/very similar way between studies we used a crossed random effects design.
+
+From this model we can see that there are several redundant moderators: Blinding, Generations and the Outcome class (direct, indirect and ambiguous) show little effect and are not key to our research question (like sex and environment are).
+However, because taxa is a likely source of heterogeneity and effect size could reasonably be expected to differ between taxa, we investigate this fixed effect further...
 
@@
 
-### Effect size differs between taxa
-
-First run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes or environments that were not stated whether they were stressed or unstressed.
+### Effect size differ slightly between taxa
+
+First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes or environments that were not stated whether they were stressed or unstressed (confusing and confounding).
 In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.
@@
 ```{r}
+#Restrict the dataset for unambiguous outcomes and environments 
 restricted.data <- prelim.data %>% 
@@
 restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
-restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Mouse")
+restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Beetle")
 
 model.complete <- rma.mv(g, var.g, 
-                         mods = ~ 1 + Sex * Environment, # << ----- Add big model, then cull predictors to this one
+                         mods = ~ 1 + Sex * Environment + Taxon, # << ----- Add big model, then cull predictors to this one
                          random = list(~ 1 | Study.ID, 
@@
                            Environment = c("Unstressed", "Stressed"),
-                           Taxon = c("Cricket", "Fly", "Guppy", "Mite", "Mouse")))
+                           Taxon = c("Beetle", "Cricket", "Fly", "Guppy", "Mite", "Mouse")))
 predictions.complete <- cbind(predictions.complete, do.call("rbind", apply(predictions.complete, 1, get.predictions.complete))) %>%
@@
 
-Third, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.
-
-> I would like to know how to join a table with mean, and CI values to the forest plots I am generating.
-
-> You can make tables with ggplot, and bind them to graphs using the grid and gridExtra packages. It's pretty hard! See ?gridExtra::tableGrob. 
-> Honestly might be easier to do it manually with e.g. Inkscape or Illustrator.
-
-```{r, fig.height= 7, fig.width=10}
+Thirdly, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.
+
+<!-- > I would like to know how to join a table with mean, and CI values to the forest plots I am generating. -->
+
+<!-- > You can make tables with ggplot, and bind them to graphs using the grid and gridExtra packages. It's pretty hard! See ?gridExtra::tableGrob.  -->
+<!-- > Honestly might be easier to do it manually with e.g. Inkscape or Illustrator.	 -->
+
+```{r, fig.height= 5, fig.width=7.5}
 pd <- position_dodgev(height = .7)
-predictions.complete %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
+Taxon.metaanlysis <- predictions.complete %>% ggplot(aes(x = pred, 
+                                                         y= Environment, 
+                                                         fill = Sex)) + 
   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
-  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, xmax = predictions.complete$ci.ub), height = 0, position = pd) +
-  geom_point(position = pd, size=2) + 
+  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
+                     xmax = predictions.complete$ci.ub,
+                     color= Sex), 
+                 height = 0, position = pd) +
+  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
   facet_grid(Taxon ~.)+
-  ylab("Environment")+
-  xlab("Model Prediction (Hedges g)")+
+  ylab("Environment \n")+
+  xlab("\nModel Prediction (Hedges g)")+
   xlim(-2, 2)+
-  ggtitle('Effects of Sex, Stress and Outcome Class \non Population Fitness for Each Taxon')
+  ggtitle('Effects of Sex, Stress and Outcome Class \non Population Fitness for Each Taxon')+
+  scale_fill_brewer(palette = "Set1")+
+  scale_color_brewer(palette = "Set1")
+
+ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 5, width = 7.5)
+Taxon.metaanlysis
 ```
@@
 This model indicates quite a bit of heterogeneity between taxon.
-More so that that confidence limits increase, rather than radically changing direction of effect.
-However we can see from this that under stressed environments, females tend to
+However, more striking is that confidence bands increase for taxa with low sample size.
+As previously shown, the beetle and fly taxa are the most heavily sampled and in the above figure have the narrowest confidence bands.
+The overall direction of effect does not change, although guppies and mice show effect sizes ~ 0.
+We can see from this that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.
 
@@
 ```{r}
-#run model without taxon: 3 level model with outcomes within a study
+#run model without taxon: same random effects as above
 model.complete2 <- rma.mv(g, var.g, 
                           mods = ~ 1 + Sex + Environment + Sex:Environment, 
-                          random = ~ 1 | Study.ID/Outcome, 
+                          random = list(~ 1 | Study.ID, 
+                                       ~ 1 | Outcome), 
                           method = "REML", 
@@
 
-```{r, fig.height= 7, fig.width=10}
+```{r, fig.height= 5, fig.width=7.5}
 
@@
 #And plot the results
-
 pd <- position_dodgev(height = .5)
-predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
+EnvSex.metaanalysis <- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
-  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, xmax = predictions.complete2$ci.ub), height = 0, position = pd) +
-  geom_point(position = pd) + 
-  ylab("Environment")+
-  xlab("Effect Size (Hedges g)")+
+  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, 
+                     xmax = predictions.complete2$ci.ub,
+                     color = Sex), height = 0, position = pd) +
+  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
+  ylab("Environment\n")+
+  xlab("\nEffect Size (Hedges g)")+
   xlim(-.75, .75)+
-  ggtitle('Effects of Sex, Stress \non Population Fitness')
+  ggtitle('Effects of Sex, Stress \non Population Fitness')+
+  scale_fill_brewer(palette = "Set1")+
+  scale_color_brewer(palette = "Set1")
+
+ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 5, width = 7.5)
+EnvSex.metaanalysis
 ```
@@
 The 'both' outcomes are restricted to extinction rate, offspring viability, mutant frequency and reproductive success.
-However, the shift from 'both' being ns in unstressed to significant in stressed may reflect the dampening of the negative correlations (sexual antagonism).
-
-```{r}
-table(restricted.data$Outcome, restricted.data$Sex)
-```
+However, the shift from 'both' being not significant in unstressed to significant in stressed may reflect the dampening of the negative correlations (sexual antagonism).
 
@@
 
-To investigate the sources of heterogeneity we can obtain a breakdown of the heterogeneity for the three level model.
+To investigate the sources of heterogeneity we can obtain a breakdown of the heterogeneity for the model.
 ```{r}
@@
 
-This indicates that 24.3 % of total heterogeneity is due to the between study heterogeneity and 68.275 % for within study heterogeneity between different outcomes.
+This indicates that 32.37 % of total heterogeneity is due to the **between study** heterogeneity and 68.275 % for **between outcome** heterogeneity between different outcomes.
 With the remaining 7.5 % due to sampling variance.
@@
 
-So if we look at an individual outcomes such as reproductive success our I^2 is lower (79.53 %).
+So if we look at an individual outcomes such as reproductive success our I^2 is lower (80.97 %).
 Which is still high as it comes from 39 studies but lower than others.
 If we wanted to run models independently we could do it for those with a large enough sample size (k>10).
+
+> Justin Says:  I am no longer sure we can use ICC as the model is not nested now, instead the random effects are crossed
 
@@
 
-#### Multilevel model using metafors alternative random effect structure
-
-> This inner, outer factor stuff from the metafor package is a bit strange.
+<!-- #### Multilevel model using metafors alternative random effect structure  -->
+
+<!-- > This inner, outer factor stuff from the metafor package is a bit strange.
 There is a description in ``?rma.mv()`` but still unsure how it differs from the above model.
 It seems that it is useful to breakdown variance-covariance matrix but unsure how that would benefit our analysis.
-
-```{r}
-#Just to check, how about with outcome as the inner factor 
-model.complete2.2 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ factor(Outcome) | Study.ID, method = "REML", data = restricted.data)
-
-summary(model.complete2.2)
-
-#Now with a slightly different structure (HCS)
-
-model.complete2.3 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ Outcome | Study.ID, struct = "HCS", method = "REML", data = restricted.data)
-
-summary(model.complete2.3)
-```
-
-```{r, fig.height= 7, fig.width=10}
-#Generate predictions without taxon
-
-get.predictions.complete2 <- function(newdata){
-  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
-  if(newdata[1] == "B") B<-1 
-  if(newdata[1] == "F") F<-1 
-  if(newdata[2] == "Stressed") Unstressed<-1
-  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
-  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1
-
-  predict(model.complete2.2, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
-}
-# Get the predictions for each combination of moderators
-predictions.complete2 <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
-                           Environment = c("Unstressed", "Stressed")))
-predictions.complete2 <- cbind(predictions.complete2, do.call("rbind", apply(predictions.complete2, 1, get.predictions.complete2))) %>%
-  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
-for(i in 3:6) predictions.complete2[,i] <- unlist(predictions.complete2[,i])
-
-#And plot the results
-
-pd <- position_dodgev(height = .3)
-predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
-  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
-  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, xmax = predictions.complete2$ci.ub), height = 0, position = pd) +
-  geom_point(position = pd) + 
-  ylab("Environment")+
-  xlab("Effect Size (Hedges g)")+
-  xlim(-.75, .75)+
-  ggtitle('Effects of Sex, Stress \non Population Fitness (OUTCOME = INNER FACTOR)')
-```
+-->
+
+<!-- ```{r} -->
+<!-- #Just to check, how about with outcome as the inner factor  -->
+<!-- model.complete2.2 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ factor(Outcome) | Study.ID, method = "REML", data = restricted.data) -->
+
+<!-- summary(model.complete2.2) -->
+
+<!-- #Now with a slightly different structure (HCS) -->
+
+<!-- model.complete2.3 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ Outcome | Study.ID, struct = "HCS", method = "REML", data = restricted.data) -->
+
+<!-- summary(model.complete2.3) -->
+<!-- ``` -->
+
+<!-- ```{r, fig.height= 7, fig.width=10} -->
+<!-- #Generate predictions without taxon -->
+
+<!-- get.predictions.complete2 <- function(newdata){ -->
+<!--   B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0 -->
+<!--   if(newdata[1] == "B") B<-1  -->
+<!--   if(newdata[1] == "F") F<-1  -->
+<!--   if(newdata[2] == "Stressed") Unstressed<-1 -->
+<!--   if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1 -->
+<!--   if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1 -->
+
+<!--   predict(model.complete2.2, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2)) -->
+<!-- } -->
+<!-- # Get the predictions for each combination of moderators -->
+<!-- predictions.complete2 <- as.data.frame(expand.grid(Sex = c("M", "B", "F"), -->
+<!--                            Environment = c("Unstressed", "Stressed"))) -->
+<!-- predictions.complete2 <- cbind(predictions.complete2, do.call("rbind", apply(predictions.complete2, 1, get.predictions.complete2))) %>% -->
+<!--   select(Sex, Environment, pred, se, ci.lb, ci.ub)  -->
+<!-- for(i in 3:6) predictions.complete2[,i] <- unlist(predictions.complete2[,i]) -->
+
+<!-- #And plot the results -->
+
+<!-- pd <- position_dodgev(height = .3) -->
+<!-- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) +  -->
+<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
+<!--   geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, xmax = predictions.complete2$ci.ub), height = 0, position = pd) + -->
+<!--   geom_point(position = pd) +  -->
+<!--   ylab("Environment")+ -->
+<!--   xlab("Effect Size (Hedges g)")+ -->
+<!--   xlim(-.75, .75)+ -->
+<!--   ggtitle('Effects of Sex, Stress \non Population Fitness (OUTCOME = INNER FACTOR)') -->
+<!-- ``` -->
 
@@
 #Setup restricted data
-prelim.data2 <- (prelim.data %>% filter(Outcome.Class != "Ambiguous"))
+prelim.data2 <- (prelim.data %>% filter(Outcome.Class != "Ambiguous",  Environment != "Not Stated"))
 
@@
 
+> Justin Says: Scrap subsetting, just use exact same model as we used for Hedges' g
+
 Secondly, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes.
-Noting that not all of the dataset has means, SD and n; some were calculated from summary statistics and are not able to have lnCVR calculated.
-Once we obtain these lnCVR estimates we can run subsetted models that use as the response variable:
-
-Now utilise function with existing data frame 
-```{r, fig.height= 7, fig.width=10}
-#foe lnCVR
+Noting that not all of the dataset has means, SD and n; some were calculated from summary statistics and are not able to have lnCVR calculated:
+
+```{r}
+#Calculate lnCVr and var.lnCVr
+#for lnCVR
 prelim.data2$lnCVr <- Calc.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high)
@@
 prelim.data2$var.lnCVr <- Calc.var.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high, Equal.E.C.Corr=F)
-
-#Run simple models subsetted for each environment/sex (this is perhaps a clunky way so we also use predictions shown below)
-
-# For stressed environment and females
-varSF <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "F"))
-
-# For stressed environment and females
-varSM <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "M"))
-
-# For stressed environment and females
-varSB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "B"))
-
-#For Benign environment and females
-varUF<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "F"))
-
-#For Benign environment and males
-varUM<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "M"))
-
-#For Benign environment and both
-varUB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "B"))
-
-#Create dataframe of estimates and confidence intervals
-lnCVR <- c(varSF$b, varSM$b, varSB$b, varUF$b, varUM$b, varUB$b)
-l.ci <- c(varSF$ci.lb, varSM$ci.lb, varSB$ci.lb, varUF$ci.lb, varUM$ci.lb, varUB$ci.lb)
-u.ci <- c(varSF$ci.ub, varSM$ci.ub, varSB$ci.ub, varUF$ci.ub, varUM$ci.ub, varUB$ci.ub)
-Environment <- c("Stressed", "Stressed", "Stressed", "Unstressed", "Unstressed", "Unstressed")
-Sex <- c("Female", "Male", "Both", "Female", "Male", "Both")
-k <- c(varSF$k, varSM$k, varSB$k, varUF$k, varUM$k, varUB$k)
-
-var.data <- data.frame(lnCVR, l.ci, u.ci, Environment, Sex, k)
-
-#Releveling the factors to make sure it aligns with other formatted graphs
-var.data$Environment <- var.data$Environment %>% factor %>% relevel(ref="Unstressed")
-var.data$Sex <- var.data$Sex %>% factor %>% relevel(ref="Male")
-
-#Plot subseted model estimates
-
-var.data %>% ggplot(aes(x=lnCVR, y = Environment, colour = Sex))+ 
-  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
-  geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, position = pd) +
-  geom_point(position = pd) + 
-  ylab("Environment")+
-  xlab("lnCVR")+
-  xlim(-.75, .75)+
-  ggtitle('Meta-Analysis of Variance (Using Subsetting)')
-
-```
-
-Here we see that Stressed environments tend to reduce phenotypic variance (if anything).
-However, perhaps a better way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously.
+```
+
+<!-- #Run simple models subsetted for each environment/sex (this is perhaps a clunky way so we also use predictions shown below) -->
+
+<!-- # For stressed environment and females -->
+<!-- varSF <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "F")) -->
+
+<!-- # For stressed environment and females -->
+<!-- varSM <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "M")) -->
+
+<!-- # For stressed environment and females -->
+<!-- varSB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "B")) -->
+
+<!-- #For Benign environment and females -->
+<!-- varUF<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "F")) -->
+
+<!-- #For Benign environment and males -->
+<!-- varUM<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "M")) -->
+
+<!-- #For Benign environment and both -->
+<!-- varUB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "B")) -->
+
+<!-- #Create dataframe of estimates and confidence intervals -->
+<!-- lnCVR <- c(varSF$b, varSM$b, varSB$b, varUF$b, varUM$b, varUB$b) -->
+<!-- l.ci <- c(varSF$ci.lb, varSM$ci.lb, varSB$ci.lb, varUF$ci.lb, varUM$ci.lb, varUB$ci.lb) -->
+<!-- u.ci <- c(varSF$ci.ub, varSM$ci.ub, varSB$ci.ub, varUF$ci.ub, varUM$ci.ub, varUB$ci.ub) -->
+<!-- Environment <- c("Stressed", "Stressed", "Stressed", "Unstressed", "Unstressed", "Unstressed") -->
+<!-- Sex <- c("Female", "Male", "Both", "Female", "Male", "Both") -->
+<!-- k <- c(varSF$k, varSM$k, varSB$k, varUF$k, varUM$k, varUB$k) -->
+
+<!-- var.data <- data.frame(lnCVR, l.ci, u.ci, Environment, Sex, k) -->
+
+<!-- #Releveling the factors to make sure it aligns with other formatted graphs -->
+<!-- var.data$Environment <- var.data$Environment %>% factor %>% relevel(ref="Unstressed") -->
+<!-- var.data$Sex <- var.data$Sex %>% factor %>% relevel(ref="Male") -->
+
+<!-- #Plot subseted model estimates -->
+
+<!-- var.data %>% ggplot(aes(x=lnCVR, y = Environment, colour = Sex))+ -->
+<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + -->
+<!--   geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, position = pd) + -->
+<!--   geom_point(position = pd) + -->
+<!--   ylab("Environment")+ -->
+<!--   xlab("lnCVR")+ -->
+<!--   xlim(-.75, .75)+ -->
+<!--   ggtitle('Meta-Analysis of Variance (Using Subsetting)') -->
+
+Although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously.
 This can be done be utilising the same predict function but for lnCVR and var.lnCVR.
@@
 #Now try with multilevel model 
-variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ 1 | Study.ID/Outcome, method = "REML", data = prelim.data2 %>% filter(Environment != "Not Stated"))
+variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex + Environment + Sex:Environment, 
+                         random = ~ 1 | Study.ID/Outcome, 
+                         method = "REML", data = prelim.data2)
 summary(variance.model)
@@
 pd <- position_dodgev(height = .3)
-predictions.variance %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
+var.plot <- predictions.variance %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
-  geom_errorbarh(aes(xmin = predictions.variance$ci.lb, xmax = predictions.variance$ci.ub), height = 0, position = pd) +
-  geom_point(position = pd) + 
-  ylab("Environment")+
-  xlab("lnCVR")+
+  geom_errorbarh(aes(xmin = predictions.variance$ci.lb, 
+                     xmax = predictions.variance$ci.ub,
+                     color = Sex), 
+                 height = 0, position = pd) +
+  geom_point(position = pd, size=3, shape = 21, color= "grey20") + 
+  ylab("Environment\n")+
+  xlab("\nlnCVR")+
   xlim(-1.2, 1.2)+
-  ggtitle('Meta-Analysis of Variance (Using Model Predictions)')
+  ggtitle('Meta-Analysis of Variance (Using Model Predictions)')+
+  scale_fill_brewer(palette = "Set1")+
+  scale_color_brewer(palette = "Set1")
+
+ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 5, width = 7.5)
+var.plot
 ```
@@
 ```{r}
-regtest(forest.model, predictor = "vi")
+#regtest(forest.model, predictor = "vi")
 
@@
 
-make.funnel(prelim.data, forest.model)
+#make.funnel(restricted.data, model.complete2)
 ```
@@
 
-```{r, fig.width=10, fig.height=8}
+```{r, fig.width=5, fig.height=7.5}
 prelim.data %>% ggplot(aes(x=log10(JIF), y=(g)))+
@@
 
-```{r, fig.width=7.50, fig.height=6}
+```{r, fig.width=5, fig.height=7.5}
 prelim.data %>% 
@@
 
-```{r, fig.width=10, fig.height=8}
+```{r, fig.width=5, fig.height=7.5}
 df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
@@
 
-We recorded the number of generations of experimental exolution each study used. The number of generations proved a negligable predictor in the meta-analytic models and can be seen here:
+We recorded the number of generations of experimental exolution each study used. The number of generations proved a negligible predictor in the meta-analytic models and can be seen here:
 

### 2018-03-02 meta_analysis_sexual_selection_pop_fitness.Rmd
2/3 Edit

@@
 ```{r}
-Outcome_and_sex <- table(prelim.data$Outcome, prelim.data$Sex) %>%
-  pander(split.cell = 40, split.table = Inf)
+Outcome_and_sex <- as.data.frame.matrix(table(prelim.data$Outcome, prelim.data$Sex))
+colnames(Outcome_and_sex) <- cbind("Both", "Male", "Female")
+
+Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)
+
 ```
@@
   facet_grid(Outcome_f~., scales= 'free', space='free')+
-  theme(strip.text.y = element_text(angle = 0))+
+  theme(strip.text.y = element_text(angle = 0))
 ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
@@
 summary(model.preliminary)
-
 ```
@@
 
-```{r, fig.height= 5, fig.width=7.5}
+```{r, fig.height= 7.5, fig.width=10}
 pd <- position_dodgev(height = .7)
@@
   xlim(-2, 2)+
-  ggtitle('Effects of Sex, Stress and Outcome Class \non Population Fitness for Each Taxon')+
+  ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
   scale_fill_brewer(palette = "Set1")+
@@
 
-ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 5, width = 7.5)
+ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 7.5, width = 10)
 Taxon.metaanlysis
@@
 
-```{r, fig.height= 5, fig.width=7.5}
+```{r, fig.height= 7.5, fig.width=10}
 
@@
   xlim(-.75, .75)+
-  ggtitle('Effects of Sex, Stress \non Population Fitness')+
+  ggtitle('Effects of Sex and Stress \non Population Fitness')+
   scale_fill_brewer(palette = "Set1")+
@@
 
-ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 5, width = 7.5)
+ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 7.5, width = 10)
 EnvSex.metaanalysis
@@
 
-ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 5, width = 7.5)
+ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 7.5, width = 10)
 var.plot
@@
 
-```{r, fig.height= 7, fig.width=10}
-#Funnel plot for all outcome classes
+```{r, fig.height= 7.5, fig.width=10}
+
+#Using residuals for the funnel plot means that we need to generate residuals (intercept only)
+
+forest.model <- rma.mv(g, var.g,
+                       mods = ~ 1,
+                       random = list(~ 1 | Study.ID,
+                                       ~ 1 | Outcome),
+                       method = "REML",
+                       data = prelim.data)
+
+# Obtain residuals
+resstandards <- (rstandard.rma.mv(forest.model,
+                                   type="response"))
+
+# Obtain grand mean effect size    <- ADDED BY LUKE
+grand.mean <- as.numeric(forest.model$b)
+
+# Create new df with residuals replacing raw
+df.forest.model <- prelim.data
+df.forest.model$g <- resstandards$resid + grand.mean 
+df.forest.model$sei <- resstandards$se
+
+# Funnel plot for all outcome classes
 
@@
   ggplot(dataset, aes(x = sqrt(var.g), y = g)) +
-    geom_point(alpha = 0.4) +
+    geom_point(size=1, shape = 21, color= "grey20") +
     xlab("Standard Error") + ylab("Effect size (Hedges' g)") +
@@
     coord_flip() +
+    scale_fill_brewer(palette = "Set1")+
     theme_classic()
@@
 
-#make.funnel(restricted.data, model.complete2)
+funnel.plot <- make.funnel(df.forest.model, forest.model)
+
+ggsave(plot = funnel.plot, filename = "figures/funnel_plot.eps", height = 7.5, width = 10)
+funnel.plot
+
 ```
@@
 
-```{r, fig.width=5, fig.height=7.5}
-prelim.data %>% ggplot(aes(x=log10(JIF), y=(g)))+
-  geom_jitter(color='darkgreen', alpha=.3, aes(size = (1/(var.g))))+
+```{r, fig.height= 7.5, fig.width=10}
+prelim.data %>% ggplot(aes(x=JIF, y=g))+
+  geom_jitter(color='darkgreen', alpha=.3, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
   geom_hline(yintercept=0, linetype = 'dotted')+
   geom_smooth(method='lm', color='black')+
-  labs(size = 'weight')
-```
-
-> I think it may also be interesting to plot the maximum effect size for each study and then plot the results as many studies measure a suite of traits.
+  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Journal Impact Factor')
+```
+
+> Is this graph ok how it is?
 
@@
 
-```{r, fig.width=5, fig.height=7.5}
+```{r, fig.height= 7.5, fig.width=10}
 prelim.data %>% 
   ggplot(aes(x=Year, y=g))+
-  geom_jitter(color='orange', alpha=.3, aes(size = (1/(var.g))))+
+  geom_jitter(color='darkorange', alpha=.5, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
   geom_hline(yintercept=0, linetype = 'dotted')+
   geom_smooth(method='lm', color='black')+
-  labs(size = 'weight')
+  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Year')
 ```
@@
 We initially collected data on whether studies were blind or not.
-Although not enough studies were blind for us to include it as a fixed effect within the model we can test whether blinding affects the raw effect size:
-
-```{r, fig.width=5, fig.height=7.5}
+Although not enough studies (n=8) used blinding for us to include it as a fixed effect within the model we can test whether blinding affects the raw effect size:
+
+```{r, fig.height= 7.5, fig.width=10}
 df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
-  geom_boxplot()+
-  geom_jitter(aes(color=Blinding))+
+  geom_boxplot(outlier.shape = NA)+
+  geom_jitter(aes(fill=Blinding), shape=21, color='grey20', size=1.7)+
   geom_hline(yintercept=0, linetype = 'dotted') + 
-  theme(legend.position = "none")
+  theme(legend.position = "none")+
+  scale_fill_brewer(palette = "Set2")+
+  labs(y='Effect size (Hedges g)', x= 'Blinding')
 ```
@@
 We can simply inspect the sample size ande effect sizes through the following plot:
-```{r, fig.width=5, fig.height=10}
+
+```{r, fig.height= 10, fig.width=5}
 prelim.data %>% ggplot(aes(x=n, y = g))+
-  geom_point()+
+  geom_point(fill="grey", color="grey20", shape=21)+
   scale_x_log10(breaks = c(10, 100, 1000, 10000)) + 
@@
   ylim(-3.5,3.5)+
-  geom_hline(yintercept=0, linetype="dashed")
+  geom_hline(yintercept=0, linetype="dashed")+
+  labs(y='Effect size (Hedges g)', x= 'Sample Size (n) [logscale]')
 ```
@@
 From these plots we can see that with increased sample size the effect sizes are closer to zero.
-Thistrend should be taken into account as meta-analytic models are wighted by 1/variance.
+This trend should be taken into account as meta-analytic models are wighted by 1/variance.
 
@@
 
-```{r, fig.width=8, fig.height=7}
+```{r, fig.height= 7.5, fig.width=10}
 prelim.data %>% ggplot(aes(x=Generations, y=g, fill=Taxon))+
-  geom_point(shape=21, color = "grey20")+
+  geom_point(shape=21, color = "grey20", size=2)+
   ylim(-3.5,3.5)+
   geom_hline(yintercept=0, linetype="dashed") + 
-  scale_fill_brewer(palette = "Set3")
+  scale_fill_brewer(palette = "Set3")+
+  labs(y='Effect size (Hedges g)', x= 'Generations')
 ```

### 2018-03-05 meta_analysis_sexual_selection_pop_fitness.Rmd
5/3 Getting close :)

@@
 title: 'Effects of sexual selection on non-sexual fitness components: a meta-analysis'
-author: "Justin Cally, University of Melbourne"
+author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
 subtitle: Supplementary Material
@@
 library(kableExtra)
-library(MuMIn)
-library(glmulti)
-library(cowplot)
 library(ggrepel)
@@
 
-####_ISI Web of Science_
+<br></br>
+
+**_ISI Web of Science_**
 
@@
 
-####_Scopus_
+<br></br>
+
+**_Scopus_**
 
@@
 
-### Additions to the literature search
+### Additions to the Literature Search
 
@@
 This latter criterion is likely to be contentious, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness.
-We therefore relied on our best judgement when deciding which studies to exclude (see Table XXX).
+We therefore relied on our best judgement when deciding which studies to exclude (see Table **XXX**).
 The inclusion/exlusion critera as applied to each study are detailed in **Table S1**.
@@
 
-4. We also collected various covariates for some of the studies (**DATA TABLE**), which are discussed later.
-
-## The effect size dataset
-
-### Table of effect sizes
+4. We also collected various covariates for some of the studies (**Table S2**), which are discussed later.
+
+______________
+
+## The Effect Size Dataset
+
+### Table of Effect Sizes
+
+>Justin Says: I think I need to clean up some of the notes and make them more readable
 
@@
 ```
+<br></br>
 
@@
 
-**SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment
+**SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment [Was not used in any analysis]
 
@@
 **JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.
-
-________________________________________________
+<br></br>
 
@@
 <input type=button class=hideshow></input>
-```{r message=FALSE}
+```{r message=FALSE, warning=FALSE}
 n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
@@
                      xmax = upperci), height = 0.1) +
-  geom_point(size = 3) +  #Add data points and color them black
+  geom_point(size = 1.5) +
   scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
@@
 <br></br>
-**Figure 1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
+**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
 Rows with multiple data points denote studies that provided multiple effect sizes.
@@
 
-### Effect size differs depending on the response variable
+## Multilevel Meta-Analysis
 
@@
 
-### Exploring our data with the large set of covariates
+### Models With Many Covariates
 
@@
 
-### Effect size differ slightly between taxa
-
-First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes or environments that were not stated whether they were stressed or unstressed (confusing and confounding).
+### Sexual Selection Amongst Taxa
+
+First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding).
 In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.
 
-```{r}
+```{r, warning=FALSE}
 #Restrict the dataset for unambiguous outcomes and environments 
@@
 pd <- position_dodgev(height = .7)
-Taxon.metaanlysis <- predictions.complete %>% ggplot(aes(x = pred, 
-                                                         y= Environment, 
-                                                         fill = Sex)) + 
+Taxon.metaanlysis <- predictions.complete %>% 
+    mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female")) %>%
+  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
@@
                      color= Sex), 
-                 height = 0, position = pd) +
+                 height = 0, position = pd, show.legend = F) +
   geom_point(position = pd, size=3, shape=21, color = "grey20") + 
@@
   scale_fill_brewer(palette = "Set1")+
-  scale_color_brewer(palette = "Set1")
+  scale_color_brewer(palette = "Set1")+
+  guides(fill = guide_legend(reverse=T))
 
@@
 ```
-
-This model indicates quite a bit of heterogeneity between taxon.
-However, more striking is that confidence bands increase for taxa with low sample size.
+<br></br>
+**Figure S2:** The predictions from this model indicate some heterogeneity between taxon.
+However, the most apparent difference between taxa is that confidence bands increase for taxa with low sample size.
 As previously shown, the beetle and fly taxa are the most heavily sampled and in the above figure have the narrowest confidence bands.
-The overall direction of effect does not change, although guppies and mice show effect sizes ~ 0.
-We can see from this that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.
+Importantly, the overall direction of effect does not change between taxon, although guppies and mice show near zero effect sizes.
+Here we see that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.
 
@@
 
-####Does sexual selection benefit populations in stressed environments more than unstressed environments? **AND** Do the benefits of sexual selection accrue more for female fitness components?
-
-Here we run a three level model where the outcome is nested within a study (Study.ID).
+###Sexual Selection, Environment and Sex
+
+Here we ask two key questions: Does sexual selection benefit populations in stressed environments more than unstressed environments?
+**AND** Do the benefits of sexual selection accrue more for female fitness components?
+
+We run a three level model where the outcome is nested within a study (Study.ID).
 Other potential random effects include Species and Group.ID.
@@
 pd <- position_dodgev(height = .5)
-EnvSex.metaanalysis <- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
+EnvSex.metaanalysis <- predictions.complete2 %>% 
+      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female")) %>%
+  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
@@
                      xmax = predictions.complete2$ci.ub,
-                     color = Sex), height = 0, position = pd) +
+                     color = Sex), height = 0, position = pd, show.legend = F) +
   geom_point(position = pd, size=3, shape=21, color = "grey20") + 
@@
 ```
+<br></br>
+**Figure S3:** Sexual selection generally increases population fitness, especially for females under stressed conditions.
+The benefits of sexual selection on fitness for females under stressed conditions are small-medium according to Cohen's interperetation of effect sizes.
 
@@
 __________________________________
-###Estimating Heterogeneity using _I^2^_ and exploring correlations
-
-Let's obtain a _I^2^_ statistic using the formulas presented here: http://www.metafor-project.org/doku.php/tips:i2_multilevel_multivariate
+###Estimating Heterogeneity Using _I^2^_
+
+Let's obtain a _I^2^_ statistic for the model above using the formulas presented here: http://www.metafor-project.org/doku.php/tips:i2_multilevel_multivariate
 
@@
 ```{r}
-#There are two estimates of heterogeneity: A between cluster (between studies) and a within-cluster (outcomes within a study)
-
-#This is for the model with outcome within study
+#This is for the model with outcome and study as crossed random effects
 W <- diag(1/restricted.data$var.g)
@@
 
-This indicates that 32.37 % of total heterogeneity is due to the **between study** heterogeneity and 68.275 % for **between outcome** heterogeneity between different outcomes.
-With the remaining 7.5 % due to sampling variance.
+This indicates that 32.37 % of total heterogeneity is due to the **between study** heterogeneity and 62.17 % for **between outcome** heterogeneity between different outcomes.
+With the remaining 5.5 % due to sampling variance.
 Interestingly this might indicate that _I^2^_ would be largely reduced for a model restricted to a single outcome...
@@
 ```
-
-____________
 
@@
 
-## Meta-Analysis on Variance
+## Multilevel Meta-Analysis on Variance
 
@@
 
-First, we setup our calculation by creating a a restricted dataset with only unabmiguous fitness outcomes and running the functions developed by Nakagawa et al. 2015:
+**Firstly**, we setup our calculation by creating a a restricted dataset with only unabmiguous fitness outcomes and running the functions developed by Nakagawa et al. 2015:
 
@@
 
-Secondly, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes.
+**Secondly**, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes.
 Noting that not all of the dataset has means, SD and n; some were calculated from summary statistics and are not able to have lnCVR calculated:
@@
 
-Although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously.
+**Thirdly**, although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously, that way we retain the same methodology in model structure and test the same hypotheses.
 This can be done be utilising the same predict function but for lnCVR and var.lnCVR.
@@
 
-```{r}
+```{r, warning=FALSE}
 #Now try with multilevel model 
-variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex + Environment + Sex:Environment, 
-                         random = ~ 1 | Study.ID/Outcome, 
+variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex*Environment, 
+                          random = list(~ 1 | Study.ID, 
+                                       ~ 1 | Outcome), 
                          method = "REML", data = prelim.data2)
@@
 pd <- position_dodgev(height = .3)
-var.plot <- predictions.variance %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
+var.plot <- predictions.variance %>% 
+ mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+        Sex = replace(Sex, Sex == "M", "Male"),
+        Sex = replace(Sex, Sex == "F", "Female")) %>%
+  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
@@
                      color = Sex), 
-                 height = 0, position = pd) +
+                 height = 0, position = pd, show.legend = F) +
   geom_point(position = pd, size=3, shape = 21, color= "grey20") + 
@@
 ```
-
-From these predictions we see that environmental stress has a large impact on phenotypic variance, whereby phenotypic variance is lower for females than for males and under stressful conditions the phenotypic variance of females decreases.
-Indicating there is a narrowing of phenotypic variance under selection.
+<br></br>
+**Figure S4:** Phenotypic variation changes under sexual selection in stressful environments.
+For stressed females, phenotypic variation decreases (narrows).
+While for males in stressed environments it increases.
+For outcomes that measured both males and females (both) phenotypic variation did not change **or** changed for males and females in opposite directions and thus cancels out when measured together.
 
 ____________________
-##Bias
-
-###Funnel plots indicate potential but small amounts of publication bias
-
-Checking for biases with a funnell plot.
+##Publication Bias
+
+###Funnel plots and Egger's Test
+
+Checking for biases with a funnel plot.
 Note that the trim and fill method does not work with rma.mv objects.
@@
 See ``?regtest`` for more information.
-Also the eggers test does not work for rma.mv objects.
-```{r}
-#regtest(forest.model, predictor = "vi")
-
-# I cut all these out, since the trim-and-fill doesn't work, and those sub-models probably don't make sense
-# trim.ambig <- trimfill.rma.uni(model.Ambiguous)
-# funnel.rma(trim.ambig)
-# regtest(model.Ambiguous, predictor = "vi")
-# funnel.rma(model.Indirect)
-# regtest(model.Indirect, predictor = "vi")
-# funnel.rma(model.Direct)
-# regtest(model.Direct, predictor = "vi")
-# funnel.rma(model.complete2, type="rstandard", yaxis = "sei")
-```
-
->Now use ggplot for funnel plot.
-This is pretty clunky and unlike the ``funnel.rma`` it does not use residuals but raw effect sizes, we could of course add residuals, so it depends on how much customization you think these plots should have.
+Because the Eggers test does not work for ``rma.mv`` objects we remove the random effects and run with Sex * Environment as moderators.
+```{r}
+standard.model <- rma(g, var.g, 
+                      mods = ~ 1 + Sex * Environment, 
+                      data=prelim.data)
+regtest(standard.model)
+```
+
+We can use ggplot for creating a funnel plot.
+The code is pretty clunky and unlike the ``funnel.rma`` it does not use automatically plot residuals so we have to generate them independently.
 The outline taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
@@
 
-```{r, fig.height= 7.5, fig.width=10}
+```{r, fig.height= 7.5, fig.width=10, warning=FALSE, message=FALSE}
 
@@
 # Obtain grand mean effect size    <- ADDED BY LUKE
-grand.mean <- as.numeric(forest.model$b)
+grand.mean <- as.numeric(forest.model$b) #WHAT about weightings?
 
@@
     coord_flip() +
-    scale_fill_brewer(palette = "Set1")+
-    theme_classic()
+    scale_fill_brewer(palette = "Set1")
+    # theme_classic()
     # apatheme
@@
 ```
-
-###Other tests of publication bias suggest there is little evidence for publication bias
-
-####Journal Impact Factor
-
-If we see a positive trend with effect size and Journal Impact Factor it may represent publication bias whereby significant (positive) results are published more readily and in more circulated journals.
+<br></br>
+**Figure S5:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 7.2671, p < .0001).
+The asymmetry appears to be sourced from a spread of positive effect sizes outside the funnel and of varying degrees of precision.
+Counter to expectations of publication bias these positive studies are not just 'low precision, large effect' results.
+Funnel plot asymmetry may also be due to heterogeneity, which in this study is high due to the many species and outcomes measured.
+
+###Journal Impact Factor
+
+If we see a positive trend with effect size and Journal Impact Factor (JIF) it may represent publication bias whereby significant (positive) results are published more readily and in more circulated journals and non-confirmitory or negative results are not published or publiushed in lower impact journals.
 Our journal impact factor dataset is not evenly distributed as several publications in Nature (JIF ~ 40) are much larger than the next highest JIF (~11).
 
-```{r, fig.height= 7.5, fig.width=10}
-prelim.data %>% ggplot(aes(x=JIF, y=g))+
+```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
+JIF.plot <- prelim.data %>% ggplot(aes(x=JIF, y=g))+
   geom_jitter(color='darkgreen', alpha=.3, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
@@
   geom_smooth(method='lm', color='black')+
+  scale_x_continuous(breaks = c(0,10,20,30,40), limits = c(2,42.5))+
   labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Journal Impact Factor')
-```
-
-> Is this graph ok how it is?
-
-#### Time-lag Bias
+
+ggsave(plot = JIF.plot, filename = "figures/JIF_plot.eps", height = 7.5, width = 10)
+JIF.plot
+```
+<br></br>
+**Figure S6:** Journal impact factor does not show a noticable correlation with effect size.
+The positive slope shown here is due to several effect sizes published in a high impact journal.
+Most papers were published in discipline specific journals such as _Evolution_ and _Journal of Evolutionary Biology_.
+
+### Time-lag Bias
 
 We can also look at the time-lag bias, which suggests effect size decreases over time.
-Again, because one publication from 1980 is well before the next publication in the late 1990s we see a very uneven distribution.
-
-```{r, fig.height= 7.5, fig.width=10}
-prelim.data %>% 
+Again, because one publication from 1980 is well before the next publication in the late 1990s we see a very uneven distribution of data points.
+
+```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
+time.plot <- prelim.data %>% 
   ggplot(aes(x=Year, y=g))+
@@
   labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Year')
-```
-
-#### Blinding
-
-From these graphs, we see a small trend for larger effect sizes to be published in higher impact journals as well as for effect size to decrease over successive years.
-Additionally to publication bias, other forms of bias may exist within studies.
-We initially collected data on whether studies were blind or not.
-Although not enough studies (n=8) used blinding for us to include it as a fixed effect within the model we can test whether blinding affects the raw effect size:
-
-```{r, fig.height= 7.5, fig.width=10}
-df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
-  geom_boxplot(outlier.shape = NA)+
-  geom_jitter(aes(fill=Blinding), shape=21, color='grey20', size=1.7)+
-  geom_hline(yintercept=0, linetype = 'dotted') + 
-  theme(legend.position = "none")+
-  scale_fill_brewer(palette = "Set2")+
-  labs(y='Effect size (Hedges g)', x= 'Blinding')
-```
-
-####Sample Size
+
+ggsave(plot = time.plot, filename = "figures/time_plot.eps", height = 7.5, width = 10)
+time.plot
+```
+<br></br>
+**Figure S7:** The effect size dataset shows little to no signs of the time-lag bias as the average effect sizes from published studies remains consistent across the previous two decades.
+
+###Sample Size
 
@@
 ```{r, fig.height= 10, fig.width=5}
-prelim.data %>% ggplot(aes(x=n, y = g))+
+samplesize.plot <- prelim.data %>% ggplot(aes(x=n, y = g))+
   geom_point(fill="grey", color="grey20", shape=21)+
@@
   labs(y='Effect size (Hedges g)', x= 'Sample Size (n) [logscale]')
-```
-
-(Promislow 1998 has one sample size of >10,000) and is not shown here.
+
+ggsave(plot = samplesize.plot, filename = "figures/samplesize_plot.eps", height = 10, width = 5)
+samplesize.plot
+```
+<br></br>
+**Figure S8:** Variation in size does not appear to have unexpected trends in any taxons, with greater variation in effect size for those studies utilising a lower sample size.
+
 From these plots we can see that with increased sample size the effect sizes are closer to zero.
-This trend should be taken into account as meta-analytic models are wighted by 1/variance.
-
-#### Generations
-
-We recorded the number of generations of experimental exolution each study used. The number of generations proved a negligible predictor in the meta-analytic models and can be seen here:
+This trend is taken into account as meta-analytic models and are wighted by 1/variance.
+**Note** Promislow (1998) has one sample size of >10,000 in flies and is not shown here to avoid making radical changes to the scale.
+
+________________
+
+##Other Moderators
+
+### Blinding
+
+In addition to publication bias, other forms of bias may exist within studies.
+We initially collected data on whether studies were blind or not.
+Although not many studies (n=8) used blinding there was multiple effect sizes reported in these studies, thus we can visualise whether blinding affects the effect sizes from the model.
+Blinding was regarded as a redundant predictor in the model (estimate = 0.0287, p = 0.8974) and was dropped.
 
 ```{r, fig.height= 7.5, fig.width=10}
-prelim.data %>% ggplot(aes(x=Generations, y=g, fill=Taxon))+
-  geom_point(shape=21, color = "grey20", size=2)+
+blind.plot <- df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
+  geom_boxplot(outlier.shape = NA)+
+  geom_jitter(aes(fill=Blinding, size = (1/(var.g))/sum((1/(var.g)))*100), shape=21, color='grey20')+
+  geom_hline(yintercept=0, linetype = 'dotted') + 
+  scale_fill_brewer(palette = "Set2")+
+  labs(y='Effect size (Hedges g)', x= 'Blinding', size = 'Weight (%)')+
+  guides(fill=FALSE)
+
+ggsave(plot = blind.plot, filename = "figures/blind_plot.eps", height = 7.5, width = 10)
+blind.plot
+```
+<br></br>
+**Figure S9:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
+However, this should not be viewed as evidence against the validity of blinding as a research method.
+
+### Generations
+
+We recorded the number of generations of experimental exolution each study used.
+The number of generations proved a negligible predictor in the meta-analytic models (estimate = 0.0019, p = 0.2341).
+The effect sizes are plotted against the generation at which the effect size was extracted.
+
+```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
+generations.plot <- df.forest.model %>% ggplot(aes(x=Generations, y=g))+
+  geom_point(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
   ylim(-3.5,3.5)+
@@
   scale_fill_brewer(palette = "Set3")+
-  labs(y='Effect size (Hedges g)', x= 'Generations')
+  geom_smooth(method = 'lm', color='black')+
+  labs(y='Effect size (Hedges g)', x= 'Generations', size= 'Weight (%)')
+
+ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
+generations.plot
+```
+<br></br>
+**Figure S10:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
+
+________________
+
+##R Session Information
+
+This section shows the operating system and R packages attached during the production of this document
+
+```{r}
+sessionInfo() %>% pander
 ```

### 2018-03-06 meta_analysis_sexual_selection_pop_fitness.Rmd
6/3 Update with more supp tables

@@
 This latter criterion is likely to be contentious, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness.
-We therefore relied on our best judgement when deciding which studies to exclude (see Table **XXX**).
-The inclusion/exlusion critera as applied to each study are detailed in **Table S1**.
-
-**Table S1:** An eligibility criteria was based on four features a study needed to include (discussed above), to be eligable for inclusion in the meta-analysis the study needed to satisfy all criteria.
+We therefore relied on our best judgement when deciding which studies to exclude (see **Table S1**).
+The inclusion/exlusion critera as applied to each study are detailed in **Table S2**.
+
+**Table S1:** We classed each of the twenty fitness related outcomes into three broad groups of direct, indirect and ambiguous based on the established link with population fitness, the directionality of the measure.
+Here we detailed how these outcomes were measured in the studies of this meta-analysis.
+In the accompanying box we provide a legend to the references cited in the table.
+
+ <br/><br/>
+```{r, warning=FALSE}
+outcome.descriptions <- read.csv('data/outcome.descriptions.csv', 
+                                 fileEncoding="UTF-8")
+kable(outcome.descriptions, "html") %>%
+  kable_styling() %>%
+  scroll_box(width = "800px", height = "500px")
+```
+  <br/><br/> 
+<input type=button class=hideshow></input>
+```{r, warning=FALSE}
+outcome.references <- read.csv('data/references.tableS1.csv', 
+                                 fileEncoding="UTF-8")
+kable(outcome.references, "html") %>%
+  kable_styling() %>%
+  scroll_box(width = "800px", height = "250px")
+```
+  <br/><br/>
+
+**Table S2:** An eligibility criteria was based on four features a study needed to include (discussed above), to be eligable for inclusion in the meta-analysis the study needed to satisfy all criteria.
 Here we applied a step-wise process to the studies that had their full-text read and excluded them when they first failed to meet the criteria.
@@
 
-4. We also collected various covariates for some of the studies (**Table S2**), which are discussed later.
+4. We also collected various covariates for some of the studies (**Table S3**), which are discussed later.
 
@@
 
-**Table S2:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
+**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
  <br/><br/> 
@@
 
-**Study ID**: An ID given to the published paper the effect size is sourced from
-
-**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup
-
-**Species and Species ID**: Same thing
+**Study ID**: An ID given to the published paper the effect size is sourced from (n=65).
+
+**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup. [Was not use in analysis]
+
+**Species**: The species used in the experimental evolution procedure (n = 15).
+
+**Taxon**: The taxon to which the species belongs. One of the following: Beetle, fly, mouse, nematode, guppy, mite and cricket (taxa were selected arbitrarily based on the available data).
 
@@
 
-**Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)
-
-**Blind**: Whether the study was blind or not
-
-**Generations** The number of generations run before fitness outcomes were measured
+**Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0).
+
+**Blinding**: A binary classification, describing whether blind protocols were used during the experiment. Papers were assumed to be not blind unless declared otherwise.
+
+**Generations**: The number of generations that the species was subject to differing levels of sexual selection, ranging from 1 to 162.
 
@@
 
-**Sex**: Whether the fitness outcome was measured for females (F), males (M) or both (B). Studies that reported 'both' would pool results from males and females.
+**n**: Pooled sample size of the paired treatments.
+
+**Outcome**: The fitness related outcome that was measured, e.g.
+fecundity, survival, or mating success (see Table S1 for all 20 categories).
+We applied our own classifications rather than relying on those provided by the authors, because different papers sometimes used different names for the same trait.
+
+**Outcome Class**: To help guide analysis the outcomes were classed into three categories; ambiguous, indirect and direct (see Table S1).
+
+**Sex**: A moderator variable with three levels, describing whether the effect size in question comes from a measurement of males (M), females (F), or individuals of both sexes (B).
 
 **Ambiguous**: Is the fitness outcome ambiguous (YES) or not ambigous (NO). Ambiguous outcomes may be those that may not necessarily be directional, that is to say they may be a life history trait.
-
-**Outcome Class**: Grouped as Direct, Indirect or Ambiguous.
 
@@
 
+**Positive Fitness**: Whether the measurment used in the study is beneficial for fitness (1) or not (0). Note that g has already been multiplied by this column.
+
 **mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance).
@@
 
-**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.
+**JIF**: Journal Impact factor at year of publication.
+Several impact factors were unable to be determined/found and are NA.We obtained the journal impact factor for each effect size at the time of publication using InCites Journal Citation Reports.
 <br></br>
@@
 
-**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
+**Table S4:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
  <br/><br/> 
@@
  <br/><br/> 
-**Table S4:** Table of fitness outcomes included in our meta-analysis by sex.
+**Table S5:** Table of fitness outcomes included in our meta-analysis by sex.
  <br/><br/> 
@@
 Outcome_and_sex <- as.data.frame.matrix(table(prelim.data$Outcome, prelim.data$Sex))
-colnames(Outcome_and_sex) <- cbind("Both", "Male", "Female")
+colnames(Outcome_and_sex) <- cbind("Both", "Female", "Male")
 
@@
 Rows with multiple data points denote studies that provided multiple effect sizes.
+
+###Quantitative Summary Mean
+
+We can obtain a bootstrap weighted mean for the entire dataset. Although this does not take into account any moderator variables it does provide a rough guide on where most of the datapoints sit:
+
+```{r}
+#Run function
+get.CIs.for.weighted.mean <- function(x, weights){
+  total.resamples <- 10000
+  num.chunks <- ceiling(length(x)*total.resamples / 10^7) # To be nice to RAM, let's keep these to ten million or less 
+  if(num.chunks == 1){
+    rand <- sample(length(x), length(x)*total.resamples, replace = TRUE)
+    resampled.weighted.means <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:total.resamples, each = length(x))) %>% 
+      group_by(replicate) %>% 
+      summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean
+  }
+
+  else{
+    resampled.weighted.means <- vector(mode = "list", length = 0)
+    number.of.resamples <- floor(total.resamples/num.chunks)
+    final.chunk.size <- total.resamples - number.of.resamples * (num.chunks-1)
+    for(i in 1:num.chunks){
+      if(i == num.chunks) number.of.resamples <- final.chunk.size
+      rand <- sample(length(x), length(x) * number.of.resamples, replace = TRUE)
+      resampled.weighted.means[[i]] <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:number.of.resamples, each = length(x))) %>% 
+        group_by(replicate) %>% 
+        summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean
+    }
+    resampled.weighted.means <- unlist(resampled.weighted.means)
+  }
+
+  data.frame(w.mean = median(resampled.weighted.means),
+             lowerCI = quantile(resampled.weighted.means, probs = 0.025) %>% as.numeric(),
+             upperCI = quantile(resampled.weighted.means, probs = 0.975) %>% as.numeric())
+}
+
+#Get weights
+prelim.data$Standard.weights <- (1/prelim.data$var.g)
+
+#Run function with weights
+get.CIs.for.weighted.mean(prelim.data$g, prelim.data$Standard.weights) %>% pander()
+```
+
+>Could this be used as a line in the forest plot showing the average (or as a polygon at the bottom)
 
@@
 model.complete2 <- rma.mv(g, var.g, 
-                          mods = ~ 1 + Sex + Environment + Sex:Environment, 
+                          mods = ~ 1 + Sex * Environment, 
                           random = list(~ 1 | Study.ID, 
@@
 
+Using an anova we can test to see if a female in a stressed environment gains significantly greater fitness benefits than in an unstressed environment:
+
+```{r}
+anova(model.complete2, L=c(0, 0, 1, -1, 0, 0)) 
+```
+
+```{r}
+anova(model.complete2, L=c(0, 1, 0, -1, 0, 0)) 
+```
+
 __________________________________

### 2018-03-07 meta_analysis_sexual_selection_pop_fitness.Rmd
7/3 Update

@@
   geom_point(size = 1.5) +
-  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
+  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
   scale_color_discrete(name = "Relationship\nto fitness") + 
@@
 Rows with multiple data points denote studies that provided multiple effect sizes.
-
-###Quantitative Summary Mean
+Positive values indicate fitness benefits of sexual selection.
+
+###Quantitative summary using bootstrapped means
 
@@
 
->Could this be used as a line in the forest plot showing the average (or as a polygon at the bottom)
+>Could this be used as a line in the forest plot showing the average (or as a polygon at the bottom), or done for each outcome?
 
@@
 
+**Comparisons of Stress vs Unstresss through anovas**
+
 Using an anova we can test to see if a female in a stressed environment gains significantly greater fitness benefits than in an unstressed environment:

### 2018-04-12 meta_analysis_sexual_selection_pop_fitness.Rmd
12/4/18 update

@@
 
-```{r warning=FALSE, message=FALSE, results='hide'}
-library(knitr)
+```{r, warning=FALSE, message=FALSE, results='hide'}
 library(pander)
@@
   <br/><br/>
+
+```{r}
+head(outcome.descriptions)
+```
 
@@
 **Figure S10:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
+<br></br>
+
+Kawecki et al.(2012) reviewed the field of experimental evolution and noted that changes to variation may need longer generations to become apparent.
+The following graph looks at the relationship between number of generations and lnCVr
+
+```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
+generations.plot.var <- prelim.data2 %>% ggplot(aes(x=Generations, y=lnCVr))+
+  geom_point(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
+  ylim(-3.5,3.5)+
+  geom_hline(yintercept=0, linetype="dashed") + 
+  scale_fill_brewer(palette = "Set3")+
+  geom_smooth(method = 'lm', color='black')+
+  labs(y='Effect size (lnCVR)', x= 'Generations', size= 'Weight (%)')
+
+# ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
+generations.plot.var
+```
+
+**Figure S11:** WRITE HERE
 

### 2018-04-12 meta_analysis_sexual_selection_pop_fitness.Rmd
12/4/18 update

@@
 prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))
-
-# Get author and year in one
-short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
-                                 short = prelim.data$Authors %>% unique() %>% 
-  as.character() %>% 
-  strsplit(split = ",") %>% 
-  sapply(FUN=function(x) x[1])) %>%
-  left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
-  mutate(suffix = "")
-
-# Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
-dups <- with(short.author.names, table(short, Year)) %>% melt()
-dups <- dups[dups$value > 1, ]
-for(i in 1:nrow(dups)){
-  short.author.names$suffix[
-    short.author.names$short == dups$short[i] &
-      short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
-}
-
-# Add the AuthorYear column to the dataframe of effect sizes
-short.author.names <- short.author.names %>%
-  mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
-  select(long, AuthorYear)
-prelim.data <- prelim.data %>% 
-  left_join(short.author.names, by = c("Authors" = "long"))
+# 
+# # Get author and year in one
+# short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
+#                                  short = prelim.data$Authors %>% unique() %>% 
+#   as.character() %>% 
+#   strsplit(split = ",") %>% 
+#   sapply(FUN=function(x) x[1])) %>%
+#   left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
+#   mutate(suffix = "")
+# 
+# # Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
+# dups <- with(short.author.names, table(short, Year)) %>% melt()
+# dups <- dups[dups$value > 1, ]
+# for(i in 1:nrow(dups)){
+#   short.author.names$suffix[
+#     short.author.names$short == dups$short[i] &
+#       short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
+# }
+# 
+# # Add the AuthorYear column to the dataframe of effect sizes
+# short.author.names <- short.author.names %>%
+#   mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
+#   select(long, AuthorYear)
+# prelim.data <- prelim.data %>% 
+#   left_join(short.author.names, by = c("Authors" = "long"))
 
@@
 >Could this be used as a line in the forest plot showing the average (or as a polygon at the bottom), or done for each outcome?
+
+Or we could run the models as subsets (one for each outcome)
+
+```{r}
+outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
+names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+outcome.models <-  llply(outcome.list, function(x) rma(g, var.g, 
+                          mods = ~ 1, 
+                          method = "REML",
+                          subset = (Outcome_f == x),
+                          data = prelim.data))
+
+df.list <- as.data.frame(do.call("rbind", outcome.models)) # data frame of model results
+
+simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "I2"))
+outcome.frame <- format(simple.frame, digits = 2)
+outcome.frame <- add_rownames(outcome.frame, "Outcome")
+outcome.frame$b <- as.numeric(outcome.frame$b)
+outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
+outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
+outcome.frame %>% pander
+```
+
+Check the results on a plot
+```{r}
+outcome.frame %>% ggplot(aes(x = b, y=Outcome)) + 
+  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
+  geom_errorbarh(aes(xmin = ci.lb, 
+                     xmax = ci.ub), height = 0, position = pd, show.legend = F) +
+  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
+  ylab("Outcome\n")+
+  xlab("\nEffect Size (Hedges g)")+
+  xlim(-2.5, 2.5)+
+  ggtitle('Effects of Sex and Stress \non Population Fitness')
+```
 

### 2018-04-19 meta_analysis_sexual_selection_pop_fitness.Rmd
19/4 update

--- 2018-03-07 meta_analysis_sexual_selection_pop_fitness.Rmd
@@
 
-```{r warning=FALSE, message=FALSE, results='hide'}
-library(knitr)
+```{r, warning=FALSE, message=FALSE, results='hide'}
 library(pander)
+library(tidyr)
 library(compute.es)
 library(metafor)
+library(plyr)
 library(dplyr)
@@
 library(ggplot2)
+library(ggthemes)
 library(kableExtra)
@@
 
-### Data extraction
+###Inclusion/Exclusion criteria
 
@@
 ### Table of Effect Sizes
-
->Justin Says: I think I need to clean up some of the notes and make them more readable
 
@@
 **mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance).
-Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.).
+Rows without these values (NA) had hedges g' derived from summary statistics (F, z, chi-square etc.).
 
@@
 
-> Although I am not sure whether having the raw values would be better. In addition whether it is worth it to add in summary polygons (effect sizes) for a grouped outcome
-
-> Luke says: if you are plotting RESIDUAL effect sizes, doesn't that mean this plots shows each effect size, relative to the grand mean effect size?
-Like, -0.05 means it is below average, but the effect is still positive since the grand mean is +0.1.
-This is probably not what we want.
-
-> I have modified the code below so that it plots the resid + the grand mean.
-But I think since model is intercept only, this might be the same thing as the raw data...
-not sure.
-Have a think, or just plot all the raw effect sizes +/- their 95% CIs, instead of the residuals.
-
-> Also try to make it clear what positive g means (I guess positive g means higher fitness when SS is present/strong?)
-
-```{r, fig.height=25, fig.width=10}
+```{r, fig.height=18, fig.width=12}
 # Run standard random effects model
@@
 prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))
-
-# Get author and year in one
-short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
-                                 short = prelim.data$Authors %>% unique() %>% 
-  as.character() %>% 
-  strsplit(split = ",") %>% 
-  sapply(FUN=function(x) x[1])) %>%
-  left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
-  mutate(suffix = "")
-
-# Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
-dups <- with(short.author.names, table(short, Year)) %>% melt()
-dups <- dups[dups$value > 1, ]
-for(i in 1:nrow(dups)){
-  short.author.names$suffix[
-    short.author.names$short == dups$short[i] &
-      short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
-}
-
-# Add the AuthorYear column to the dataframe of effect sizes
-short.author.names <- short.author.names %>%
-  mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
-  select(long, AuthorYear)
-prelim.data <- prelim.data %>% 
-  left_join(short.author.names, by = c("Authors" = "long"))
-
+# 
+# # Get author and year in one
+# short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
+#                                  short = prelim.data$Authors %>% unique() %>% 
+#   as.character() %>% 
+#   strsplit(split = ",") %>% 
+#   sapply(FUN=function(x) x[1])) %>%
+#   left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
+#   mutate(suffix = "")
+# 
+# # Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
+# dups <- with(short.author.names, table(short, Year)) %>% melt()
+# dups <- dups[dups$value > 1, ]
+# for(i in 1:nrow(dups)){
+#   short.author.names$suffix[
+#     short.author.names$short == dups$short[i] &
+#       short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
+# }
+# 
+# # Add the AuthorYear column to the dataframe of effect sizes
+# short.author.names <- short.author.names %>%
+#   mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
+#   select(long, AuthorYear)
+# prelim.data <- prelim.data %>% 
+#   left_join(short.author.names, by = c("Authors" = "long")) 
+library(ggthemes)
 #Generate a plot
@@
          Sex = replace(Sex, Sex == "F", "Female")) %>%
-  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
+
+  ggplot(aes(y=reorder(AuthorYear, -g), x = g)) +
+
+  scale_color_brewer(name = "Relationship\nto fitness", 
+                    palette = "Set1", 
+                    breaks=c("Ambiguous","Indirect","Direct"))+
+
+  scale_shape_manual(values=c(21,22,24))+
+
+  scale_fill_brewer(name = "Relationship\nto fitness", 
+                    palette = "Set1", 
+                    breaks=c("Ambiguous","Indirect","Direct"))+
+
   geom_errorbarh(aes(xmin = lowerci, 
-                     xmax = upperci), height = 0.1) +
-  geom_point(size = 1.5) +
-  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
-  scale_color_discrete(name = "Relationship\nto fitness") + 
+                     xmax = upperci,
+                     color = Outcome.Class), height = 0.1, show.legend = FALSE) +
+
+  geom_point(aes(shape = Sex,
+                 fill = Outcome.Class), 
+             size = 1.75, 
+             color = "grey20") +
+
+  scale_x_continuous(limits=c(-3.35, 12), 
+                     breaks = c(-3, -2, -1, 0, 1, 2, 3), 
+                     name='                              Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
+
   ylab('Reference') +
-  geom_vline(xintercept=0, color='black', linetype='dashed')+
-  facet_grid(Outcome_f~., scales= 'free', space='free')+
-  theme(strip.text.y = element_text(angle = 0))
-ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
+
+  geom_vline(xintercept=0, 
+             color='black', 
+             linetype='dashed')+
+
+  facet_grid(Outcome_f~.,
+             labeller = label_wrap_gen(width=23),
+             scales= 'free', 
+             space='free')+
+
+  guides(fill = guide_legend(override.aes = list(shape = 21, colour = "grey20")))+
+
+  # scale_color_discrete(breaks=c("Ambiguous","Indirect","Direct"))+
+  theme_bw()+
+
+  theme(strip.text.y = element_text(angle = 0, size = 8, margin = margin(t=15, r=15, b=15, l=15)), 
+        strip.background = element_rect(colour = NULL,
+                                        linetype = "blank",
+                                        fill = "gray90"),
+        text = element_text(size=11),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=12), 
+        legend.title=element_text(size=12, 
+                                  face = "bold"),
+        axis.title.x = element_text(hjust = 0, size = 12))
+
+ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 18, width = 12)
 p.meta
+
+# svg("figures/Big_forest_plot.svg", width=12, height=18)
+# p.meta
+# dev.off()
 ```
@@
 
-###Quantitative summary using bootstrapped means
-
-We can obtain a bootstrap weighted mean for the entire dataset. Although this does not take into account any moderator variables it does provide a rough guide on where most of the datapoints sit:
-
-```{r}
-#Run function
-get.CIs.for.weighted.mean <- function(x, weights){
-  total.resamples <- 10000
-  num.chunks <- ceiling(length(x)*total.resamples / 10^7) # To be nice to RAM, let's keep these to ten million or less 
-  if(num.chunks == 1){
-    rand <- sample(length(x), length(x)*total.resamples, replace = TRUE)
-    resampled.weighted.means <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:total.resamples, each = length(x))) %>% 
-      group_by(replicate) %>% 
-      summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean
-  }
-
-  else{
-    resampled.weighted.means <- vector(mode = "list", length = 0)
-    number.of.resamples <- floor(total.resamples/num.chunks)
-    final.chunk.size <- total.resamples - number.of.resamples * (num.chunks-1)
-    for(i in 1:num.chunks){
-      if(i == num.chunks) number.of.resamples <- final.chunk.size
-      rand <- sample(length(x), length(x) * number.of.resamples, replace = TRUE)
-      resampled.weighted.means[[i]] <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:number.of.resamples, each = length(x))) %>% 
-        group_by(replicate) %>% 
-        summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean
-    }
-    resampled.weighted.means <- unlist(resampled.weighted.means)
-  }
-
-  data.frame(w.mean = median(resampled.weighted.means),
-             lowerCI = quantile(resampled.weighted.means, probs = 0.025) %>% as.numeric(),
-             upperCI = quantile(resampled.weighted.means, probs = 0.975) %>% as.numeric())
-}
-
-#Get weights
-prelim.data$Standard.weights <- (1/prelim.data$var.g)
-
-#Run function with weights
-get.CIs.for.weighted.mean(prelim.data$g, prelim.data$Standard.weights) %>% pander()
-```
-
->Could this be used as a line in the forest plot showing the average (or as a polygon at the bottom), or done for each outcome?
+<!-- ###Quantitative summary using bootstrapped means -->
+
+<!-- We can obtain a bootstrap weighted mean for the entire dataset.
+Although this does not take into account any moderator variables it does provide a rough guide on where most of the datapoints sit:  -->
+
+<!-- ```{r} -->
+<!-- #Run function -->
+<!-- get.CIs.for.weighted.mean <- function(x, weights){ -->
+<!--   total.resamples <- 10000 -->
+<!--   num.chunks <- ceiling(length(x)*total.resamples / 10^7) # To be nice to RAM, let's keep these to ten million or less  -->
+<!--   if(num.chunks == 1){ -->
+<!--     rand <- sample(length(x), length(x)*total.resamples, replace = TRUE) -->
+<!--     resampled.weighted.means <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:total.resamples, each = length(x))) %>%  -->
+<!--       group_by(replicate) %>%  -->
+<!--       summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean -->
+<!--   } -->
+
+<!--   else{ -->
+<!--     resampled.weighted.means <- vector(mode = "list", length = 0) -->
+<!--     number.of.resamples <- floor(total.resamples/num.chunks) -->
+<!--     final.chunk.size <- total.resamples - number.of.resamples * (num.chunks-1) -->
+<!--     for(i in 1:num.chunks){ -->
+<!--       if(i == num.chunks) number.of.resamples <- final.chunk.size -->
+<!--       rand <- sample(length(x), length(x) * number.of.resamples, replace = TRUE) -->
+<!--       resampled.weighted.means[[i]] <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:number.of.resamples, each = length(x))) %>%  -->
+<!--         group_by(replicate) %>%  -->
+<!--         summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean -->
+<!--     } -->
+<!--     resampled.weighted.means <- unlist(resampled.weighted.means) -->
+<!--   } -->
+
+<!--   data.frame(w.mean = median(resampled.weighted.means), -->
+<!--              lowerCI = quantile(resampled.weighted.means, probs = 0.025) %>% as.numeric(), -->
+<!--              upperCI = quantile(resampled.weighted.means, probs = 0.975) %>% as.numeric()) -->
+<!-- } -->
+
+<!-- #Get weights -->
+<!-- prelim.data$Standard.weights <- (1/prelim.data$var.g) -->
+
+<!-- #Run function with weights -->
+<!-- get.CIs.for.weighted.mean(prelim.data$g, prelim.data$Standard.weights) %>% pander() -->
+<!-- ``` -->
+
+###Meta-analysis of individual outcomes
+
+We can run individual standard random effects models for each outcome.
+From the intercept only model we can obtain a mean (beta) and confidence intervals.
+Following that we can obtain estimates for _I^2^_, the % of residual heterogeneity for each given outcome.
+
+**Table S6** Summary of individual model results, including _I^2^_, for all outcomes with n>3 (fix this).
+
+```{r, warning = FALSE}
+outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
+names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
+                          mods = ~ 1, 
+                          method = "REML",
+                          random = ~ 1 + Study.ID,
+                          subset = (Outcome_f == x),
+                          data = prelim.data))
+
+df.list <- as.data.frame(do.call("rbind", outcome.models)) # data frame of model results
+
+simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))
+# simple.frame$vi <- as.matrix(simple.frame$vi)
+# simple.frame$W <- diag(1/(simple.frame$vi))
+# 
+# XO <- model.matrix(model.complete2)
+# PO <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+# 100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
+
+#I couldn't get mapply to work when calculating I2 so I calculated them manually.
+
+#Body Size 
+restricted.dataBS <- prelim.data %>% filter(prelim.data$Outcome == "Body Size")
+
+#Run estimate of heterogeneity
+WBS = diag(1/restricted.dataBS$var.g)
+XBS = model.matrix(outcome.models[["Body Size"]])
+PBS = WBS - WBS %*% XBS %*% solve(t(XBS) %*% WBS %*% XBS) %*% t(XBS) %*% WBS
+BodySizeI2 <- 100 * sum(outcome.models[["Body Size"]]$sigma2) / (sum(outcome.models[["Body Size"]]$sigma2) + (outcome.models[["Body Size"]]$k-outcome.models[["Body Size"]]$p)/sum(diag(PBS)))
+
+#Development Rate 
+restricted.dataDR <- prelim.data %>% filter(prelim.data$Outcome == "Development Rate")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataDR$var.g)
+X = model.matrix(outcome.models[["Development Rate"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+DevelopmentRateI2 <- 100 * sum(outcome.models[["Development Rate"]]$sigma2) / (sum(outcome.models[["Development Rate"]]$sigma2) + (outcome.models[["Development Rate"]]$k-outcome.models[["Development Rate"]]$p)/sum(diag(P)))
+
+#Early Fecundity 
+restricted.dataEF <- prelim.data %>% filter(prelim.data$Outcome == "Early Fecundity")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataEF$var.g)
+X = model.matrix(outcome.models[["Early Fecundity"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+EarlyFecundityI2 <- 100 * sum(outcome.models[["Early Fecundity"]]$sigma2) / (sum(outcome.models[["Early Fecundity"]]$sigma2) + (outcome.models[["Early Fecundity"]]$k-outcome.models[["Early Fecundity"]]$p)/sum(diag(P)))
+
+#Immunity
+restricted.dataI <- prelim.data %>% filter(prelim.data$Outcome == "Immunity")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataI$var.g)
+X = model.matrix(outcome.models[["Immunity"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+ImmunityI2 <- 100 * sum(outcome.models[["Immunity"]]$sigma2) / (sum(outcome.models[["Immunity"]]$sigma2) + (outcome.models[["Immunity"]]$k-outcome.models[["Immunity"]]$p)/sum(diag(P)))
+
+#Mating Duration
+restricted.dataMD <- prelim.data %>% filter(prelim.data$Outcome == "Mating Duration")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMD$var.g)
+X = model.matrix(outcome.models[["Mating Duration"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MatingDurationI2 <- 100 * sum(outcome.models[["Mating Duration"]]$sigma2) / (sum(outcome.models[["Mating Duration"]]$sigma2) + (outcome.models[["Mating Duration"]]$k-outcome.models[["Mating Duration"]]$p)/sum(diag(P)))
+
+#Mutant Frequency
+restricted.dataMF <- prelim.data %>% filter(prelim.data$Outcome == "Mutant Frequency")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMF$var.g)
+X = model.matrix(outcome.models[["Mutant Frequency"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MutantFrequencyI2 <- 100 * sum(outcome.models[["Mutant Frequency"]]$sigma2) / (sum(outcome.models[["Mutant Frequency"]]$sigma2) + (outcome.models[["Mutant Frequency"]]$k-outcome.models[["Mutant Frequency"]]$p)/sum(diag(P)))
+
+#Fitness Senescence
+restricted.dataFS <- prelim.data %>% filter(prelim.data$Outcome == "Fitness Senescence")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataFS$var.g)
+X = model.matrix(outcome.models[["Fitness Senescence"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+FitnessSenescenceI2 <- 100 * sum(outcome.models[["Fitness Senescence"]]$sigma2) / (sum(outcome.models[["Fitness Senescence"]]$sigma2) + (outcome.models[["Fitness Senescence"]]$k-outcome.models[["Fitness Senescence"]]$p)/sum(diag(P)))
+
+#Lifespan
+restricted.dataL <- prelim.data %>% filter(prelim.data$Outcome == "Lifespan")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataL$var.g)
+X = model.matrix(outcome.models[["Lifespan"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+LifespanI2 <- 100 * sum(outcome.models[["Lifespan"]]$sigma2) / (sum(outcome.models[["Lifespan"]]$sigma2) + (outcome.models[["Lifespan"]]$k-outcome.models[["Lifespan"]]$p)/sum(diag(P)))
+
+#Male Attractiveness
+restricted.dataMA <- prelim.data %>% filter(prelim.data$Outcome == "Male Attractiveness")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMA$var.g)
+X = model.matrix(outcome.models[["Male Attractiveness"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MaleAttractivenessI2 <- 100 * sum(outcome.models[["Male Attractiveness"]]$sigma2) / (sum(outcome.models[["Male Attractiveness"]]$sigma2) + (outcome.models[["Male Attractiveness"]]$k-outcome.models[["Male Attractiveness"]]$p)/sum(diag(P)))
+
+#Mating Frequency
+restricted.dataMF <- prelim.data %>% filter(prelim.data$Outcome == "Mating Frequency")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMF$var.g)
+X = model.matrix(outcome.models[["Mating Frequency"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MatingFrequencyI2 <- 100 * sum(outcome.models[["Mating Frequency"]]$sigma2) / (sum(outcome.models[["Mating Frequency"]]$sigma2) + (outcome.models[["Mating Frequency"]]$k-outcome.models[["Mating Frequency"]]$p)/sum(diag(P)))
+
+#Mating Latency
+restricted.dataML <- prelim.data %>% filter(prelim.data$Outcome == "Mating Latency")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataML$var.g)
+X = model.matrix(outcome.models[["Mating Latency"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MatingLatencyI2 <- 100 * sum(outcome.models[["Mating Latency"]]$sigma2) / (sum(outcome.models[["Mating Latency"]]$sigma2) + (outcome.models[["Mating Latency"]]$k-outcome.models[["Mating Latency"]]$p)/sum(diag(P)))
+
+#Mating Success
+restricted.dataMS <- prelim.data %>% filter(prelim.data$Outcome == "Mating Success")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMS$var.g)
+X = model.matrix(outcome.models[["Mating Success"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MatingSuccessI2 <- 100 * sum(outcome.models[["Mating Success"]]$sigma2) / (sum(outcome.models[["Mating Success"]]$sigma2) + (outcome.models[["Mating Success"]]$k-outcome.models[["Mating Success"]]$p)/sum(diag(P)))
+
+#Ejaculate Quality and Production
+restricted.dataEQ <- prelim.data %>% filter(prelim.data$Outcome == "Ejaculate Quality and Production")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataEQ$var.g)
+X = model.matrix(outcome.models[["Ejaculate Quality and Production"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+EjaculateQualityI2 <- 100 * sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) / (sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) + (outcome.models[["Ejaculate Quality and Production"]]$k-outcome.models[["Ejaculate Quality and Production"]]$p)/sum(diag(P)))
+
+#Extinction Rate
+restricted.dataER <- prelim.data %>% filter(prelim.data$Outcome == "Extinction Rate")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataER$var.g)
+X = model.matrix(outcome.models[["Extinction Rate"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+ExtinctionRateI2 <- 100 * sum(outcome.models[["Extinction Rate"]]$sigma2) / (sum(outcome.models[["Extinction Rate"]]$sigma2) + (outcome.models[["Extinction Rate"]]$k-outcome.models[["Extinction Rate"]]$p)/sum(diag(P)))
+
+#Offspring Viability
+restricted.dataOV <- prelim.data %>% filter(prelim.data$Outcome == "Offspring Viability")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataOV$var.g)
+X = model.matrix(outcome.models[["Offspring Viability"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+OffspringViabilityI2 <- 100 * sum(outcome.models[["Offspring Viability"]]$sigma2) / (sum(outcome.models[["Offspring Viability"]]$sigma2) + (outcome.models[["Offspring Viability"]]$k-outcome.models[["Offspring Viability"]]$p)/sum(diag(P)))
+
+#Reproductive Success
+restricted.dataRS <- prelim.data %>% filter(prelim.data$Outcome == "Reproductive Success")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataRS$var.g)
+X = model.matrix(outcome.models[["Reproductive Success"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+ReproductiveSuccessI2 <- 100 * sum(outcome.models[["Reproductive Success"]]$sigma2) / (sum(outcome.models[["Reproductive Success"]]$sigma2) + (outcome.models[["Reproductive Success"]]$k-outcome.models[["Reproductive Success"]]$p)/sum(diag(P)))
+
+simple.frame$I2 <- c(NA, BodySizeI2, DevelopmentRateI2, EarlyFecundityI2, ImmunityI2, MatingDurationI2, NA, MutantFrequencyI2, FitnessSenescenceI2, LifespanI2, MaleAttractivenessI2, MatingFrequencyI2, MatingLatencyI2, MatingSuccessI2, NA, EjaculateQualityI2, ExtinctionRateI2, OffspringViabilityI2, ReproductiveSuccessI2)
+
+outcome.frame <- format(simple.frame, digits = 2)
+outcome.frame <- add_rownames(outcome.frame, "Outcome")
+outcome.frame$b <- as.numeric(outcome.frame$b)
+outcome.frame$k <- as.numeric(outcome.frame$k)
+outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
+outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
+outcome.frame$I2 <- as.numeric(outcome.frame$I2)
+
+outcome.frame %>% pander(split.cell = 40, split.table = Inf)
+
+#Can't get the llply or mapply to work on the list of outcomes
+
+# I2df <- llply(outcome.models, function(x) {
+#   prelim.data %>% filter(prelim.data$Outcome == outcome.list)
+# })
+#   #Run estimate of heterogeneity
+# Wlist <- llply(outcome.list, function(x) {diag(1/I2df[[x]]$var.g)}) #X
+# 
+# Xlist <- llply(outcome.list, function(x) {model.matrix(outcome.models[[x]])}) #Y
+# 
+# Pfunc <- Map(function(X,Y,Z) {
+#   X[[Z]] - X[[Z]] %*% Y[[Z]] %*% solve(t(Y[[Z]]) %*% X[[Z]] %*% Y[[Z]]) %*% t(Y[[Z]]) %*% X[[Z]]},
+#   X=Wlist, Y=Xlist, Z=1:19)
+# 
+# llply()
+# 
+# I2list <- llply(outcome.list, function(x) {100 * sum(outcome.models[[x]]$sigma2) / (sum(outcome.models[[x]]$sigma2) + (outcome.models[[x]]$k-outcome.models[[x]]$p)/sum(diag(Wlist - Wlist %*% Xlist %*% solve(t(Xlist) %*% Wlist %*% Xlist) %*% t(Xlist) %*% x)))})
+# 
+# matrix(outcome.list)
+```
+
+<!-- Check the results on a plot -->
+<!-- ```{r} -->
+<!-- pd <- position_dodgev(height = .7) -->
+<!-- outcome.frame %>% ggplot(aes(x = b, y= Outcome)) +  -->
+<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
+<!--   geom_errorbarh(aes(xmin = ci.lb,  -->
+<!--                      xmax = ci.ub), height = 0, position = pd, show.legend = F) + -->
+<!--   geom_point(position = pd, color = "grey20") +  -->
+<!--   ylab("Outcome\n")+ -->
+<!--   xlab("\nEffect Size (Hedges g)")+ -->
+<!--   xlim(-2.5, 2.5)+ -->
+<!--   ggtitle('Standard Random Effects Model') -->
+<!-- ``` -->
 
@@
 ## Multilevel Meta-Analysis
-
-> Let's just run one big model then cull from there
 
@@
 
+<input type=button class=hideshow></input>
 ```{r}
@@
 <br></br>
-**A note on random effects** Here we utilise crossed random effects of Study.ID and Outcome.
-Nesting Outcomes within Study.ID can also be achieved through ``random = ~ 1 | Study.ID/Outcome``.
-However given that the same outcome is expected to be measured in the same/very similar way between studies we used a crossed random effects design.
 
@@
 
+<input type=button class=hideshow></input>
 ```{r, warning=FALSE}
@@
 This is done by obtaining predictions using the base ``predict()`` function for the ``rma.mv()`` objects that have been previously created
-```{r}
+```{r, warning=FALSE}
 # function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
@@
   if(newdata[1] == "F") F<-1 
-  if(newdata[2] == "Stressed") Unstressed<-1
+  if(newdata[2] == "Stressed") Stressed<-1
   if(newdata[3] == "Cricket") Cricket<-1
@@
 for(i in 4:7) predictions.complete[,i] <- unlist(predictions.complete[,i])
+
+countpred = count_(restricted.data, c("Sex", "Environment", "Taxon"))
+
+predictions.complete <- left_join(predictions.complete, countpred, by = c("Sex", "Environment", "Taxon"))
+
+countpred = count_(restricted.data, c("Sex", "Environment", "Taxon"))
+
+predictions.complete <- left_join(predictions.complete, countpred, by = c("Sex", "Environment", "Taxon"))
 ```
@@
 
-```{r, fig.height= 7.5, fig.width=10}
-pd <- position_dodgev(height = .7)
+```{r, fig.height= 6, fig.width=8}
+pd <- position_dodgev(0.5)
+
 Taxon.metaanlysis <- predictions.complete %>% 
@@
   ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
-  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
+  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
   geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
@@
                  height = 0, position = pd, show.legend = F) +
-  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
+  geom_point(position = pd, size=2, shape=21, color = "grey20") + 
   facet_grid(Taxon ~.)+
@@
   xlab("\nModel Prediction (Hedges g)")+
-  xlim(-2, 2)+
+  xlim(-1, 2)+
   ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
@@
   scale_color_brewer(palette = "Set1")+
-  guides(fill = guide_legend(reverse=T))
-
-ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 7.5, width = 10)
+  guides(fill = guide_legend(reverse=T))+
+    theme_bw()+
+
+  theme(strip.text.y = element_text(angle = 0, size = 14, margin = margin(r=20, l=20)), 
+        strip.background = element_rect(colour = NULL,
+                                        linetype = "blank",
+                                        fill = "gray90"),
+        text = element_text(size=14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=14), 
+        legend.title=element_text(size=14, 
+                                  face = "bold"),
+        axis.title.x = element_text(hjust = 0.3, size = 14),
+        axis.title.y = element_text(size = 14),
+        plot.title = element_text(size = 14))
+
+ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 6, width = 8)
 Taxon.metaanlysis
@@
 Here we see that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.
+
+**Table S7** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.
+
+```{r}
+colnames(predictions.complete) <- c("Sex", "Environment", "Taxon", "Prediction", "SE", "CI.lb", "CI.ub", "n")
+predictions.complete <- format(predictions.complete, digits = 2)
+predictions.complete[[9]] <- NULL
+predictions.complete %>% pander()
+```
 
@@
 ```
-
-```{r, fig.height= 7.5, fig.width=10}
+<br></br>
+
+Now plot the model predictions using a similar function to the one used in the above section with taxon.
+
+```{r, fig.height= 6, fig.width=6}
 
@@
   if(newdata[1] == "F") F<-1 
-  if(newdata[2] == "Stressed") Unstressed<-1
+  if(newdata[2] == "Stressed") Stressed<-1
   if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
@@
 
+countpred <- count_(restricted.data, c("Sex", "Environment"))
+
+predictions.complete2 <- left_join(predictions.complete2, countpred, by = c("Sex", "Environment"))
+
 #And plot the results
-pd <- position_dodgev(height = .5)
+pd <- position_dodgev(height = 0.65)
 EnvSex.metaanalysis <- predictions.complete2 %>% 
@@
   ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
-  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
+  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
   geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, 
@@
                      color = Sex), height = 0, position = pd, show.legend = F) +
-  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
+  geom_point(aes(size=nn), position = pd, shape=21, color = "grey20") + 
+  scale_size(guide = 'none')+
   ylab("Environment\n")+
-  xlab("\nEffect Size (Hedges g)")+
-  xlim(-.75, .75)+
-  ggtitle('Effects of Sex and Stress \non Population Fitness')+
+  xlab("\nEffect Size (Hedges' g)")+
   scale_fill_brewer(palette = "Set1")+
   scale_color_brewer(palette = "Set1")+
-  guides(fill = guide_legend(reverse=T))
-
-ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 7.5, width = 10)
+  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
+  scale_x_continuous(limits = c(-0.2, 1), breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1))+
+
+  theme_bw()+
+
+  theme(panel.spacing = unit(0.5, "lines"),
+        text = element_text(size=14),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=14), 
+        legend.title=element_text(size=14, 
+                                  face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+        axis.title.y = element_text(size = 14),
+        axis.text.y = element_text(angle = 90),
+        plot.title = element_text(size = 14))
+
+ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 6, width = 6)
 EnvSex.metaanalysis
+
+# svg("figures/fEnvironment_Sex_metaanalysis_plot.svg", width=6, height=6)
+# EnvSex.metaanalysis
+# dev.off()
 ```
@@
 The benefits of sexual selection on fitness for females under stressed conditions are small-medium according to Cohen's interperetation of effect sizes.
+Circle size is proportional to sample size.
+
+**Table S8**
+```{r}
+colnames(predictions.complete2) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
+predictions.complete2 <- format(predictions.complete2, digits = 2)
+predictions.complete2 %>% pander()
+```
 
@@
 ```{r}
-anova(model.complete2, L=c(0, 0, 1, -1, 0, 0)) 
+anova(model.complete2, L=c(0, 0, 0, 1, 0, -1)) 
 ```
@@
 anova(model.complete2, L=c(0, 1, 0, -1, 0, 0)) 
+```
+
+From these anovas we see that a stressed environment leads to a significantly greater increase in fitness components for "female"" but NOT "both" sexes.
+
+We can also test if there is a difference between males and females in unstressed and stressed conditions:
+
+```{r}
+#anova where you specify the values based on the list of moderators
+anova(model.complete2, L=c(1, 0, -1, 0, 0, 0)) 
+```
+
+Or both in stressed vs unstressed:
+
+```{r}
+anova(model.complete2, L=c(0, 1, 0, 0, -1, 0)) 
+```
+
+Or males in stressed vs unstressed:
+
+```{r}
+anova(model.complete2, L=c(1, 0, 0, -1, 0, 0)) 
 ```
@@
 ```
-This is a reasonably high _I^2^_ value but is relatively common in Ecology and Evolution (Nakagawa 2017).
+95 % is a reasonably high _I^2^_ value but is relatively common in Ecology and Evolution (Nakagawa 2017).
 
@@
 
-This indicates that 32.37 % of total heterogeneity is due to the **between study** heterogeneity and 62.17 % for **between outcome** heterogeneity between different outcomes.
+This indicates that 61 % of total heterogeneity is due to the **between study** heterogeneity and 34 % for **between outcome** heterogeneity between different outcomes.
 With the remaining 5.5 % due to sampling variance.
-Interestingly this might indicate that _I^2^_ would be largely reduced for a model restricted to a single outcome...
-Let's test this with our most common outcome...Reproductive Success
-
-```{r}
-#Reproductive Success Restriction 
-restricted.dataRS <- restricted.data %>% filter(restricted.data$Outcome == "Reproductive Success")
-
-#Run reproductive success only model 
-model.completeRS <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ 1 | Study.ID, method = "REML", data = restricted.dataRS)
-
-#Run estimate of heterogeneity
-W2 <- diag(1/restricted.dataRS$var.g)
-X2 <- model.matrix(model.completeRS)
-P2 <- W2 - W2 %*% X2 %*% solve(t(X2) %*% W2 %*% X2) %*% t(X2) %*% W2
-100 * sum(model.completeRS$sigma2) / (sum(model.completeRS$sigma2) + (model.completeRS$k-model.completeRS$p)/sum(diag(P2)))
-```
-
-So if we look at an individual outcomes such as reproductive success our I^2 is lower (80.97 %).
-Which is still high as it comes from 39 studies but lower than others.
-If we wanted to run models independently we could do it for those with a large enough sample size (k>10).
-
-> Justin Says:  I am no longer sure we can use ICC as the model is not nested now, instead the random effects are crossed
-
-Furthermore, we can obtain estimates of the intra-class correlation (ICC) within a study via: 
-```{r}
-round(model.complete2$sigma2[1] / sum(model.complete2$sigma2), 3)
-```
-
-This means that within a study, between different outcomes, there is a correlation of 26.2 % (low-medium).
+Interestingly this might indicate that _I^2^_ would be largely reduced for a model restricted to a single outcome.
+The _I^2^_ values for individual outcomes were presented earlier in this document and presented alongside the forest plot.
+
+<!-- Furthermore, we can obtain estimates of the intra-class correlation (ICC) within a study via:  -->
+<!-- ```{r} -->
+<!-- round(model.complete2$sigma2[1] / sum(model.complete2$sigma2), 3) -->
+<!-- ``` -->
+
+<!-- This means that within a study, between different outcomes, there is a correlation of 26.2 % (low-medium).
 This justifies including outcome as a level, as without it we would be assuming ICC = 1.
-We can also gain an estimate of the total heterogeniety, as the sum of the sigma componenets:
-```{r}
-round(sum(model.complete2$sigma2), 3)
-```
+We can also gain an estimate of the total heterogeniety, as the sum of the sigma componenets:  -->
+<!-- ```{r} -->
+<!-- round(sum(model.complete2$sigma2), 3) -->
+<!-- ``` -->
 
@@
 
-> Justin Says: Scrap subsetting, just use exact same model as we used for Hedges' g
-
 **Secondly**, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes.
@@
 prelim.data2$var.lnCVr <- Calc.var.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high, Equal.E.C.Corr=F)
+
+prelim.data2 <- prelim.data2 %>% drop_na(lnCVr)
 ```
@@
 ```
-
-Plotted predictions of lnCVR for various moderators:
-
-```{r, fig.height= 7.5, fig.width=10}
+<br></br>
+**Fourthly**, we can plot predictions of lnCVR for various moderators:
+
+```{r, fig.height= 6, fig.width=6, warning = FALSE}
 
@@
   if(newdata[1] == "M") M<-1 
-  if(newdata[2] == "Stressed") Unstressed<-1
+  if(newdata[2] == "Stressed") Stressed<-1
   if(newdata[1] == "F" & newdata[2] == "Stressed") interaction1<-1
@@
 
+countpred = count_(prelim.data2, c("Sex", "Environment"))
+
+predictions.variance <- left_join(predictions.variance, countpred, by = c("Sex", "Environment"))
+
 #And plot the results
 
-pd <- position_dodgev(height = .3)
 var.plot <- predictions.variance %>% 
@@
         Sex = replace(Sex, Sex == "F", "Female")) %>%
-  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
-  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
+  ggplot(aes(x = pred, y= reorder(Environment, -pred), fill = Sex)) + 
+  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
   geom_errorbarh(aes(xmin = predictions.variance$ci.lb, 
@@
                  height = 0, position = pd, show.legend = F) +
-  geom_point(position = pd, size=3, shape = 21, color= "grey20") + 
+  geom_point(aes(size = nn), position = pd, shape = 21, color= "grey20") + 
+  scale_size(guide = 'none')+
   ylab("Environment\n")+
-  xlab("\nlnCVR")+
-  xlim(-1.2, 1.2)+
-  ggtitle('Meta-Analysis of Variance (Using Model Predictions)')+
+  xlab("\nPhenotypic Variance (lnCVR)")+
+  scale_x_continuous(limits = c(-1.6, 1.2), breaks = c(-1.5, -1, -0.5, 0, 0.5, 1))+
   scale_fill_brewer(palette = "Set1")+
   scale_color_brewer(palette = "Set1")+
-  guides(fill = guide_legend(reverse=T))
-
-ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 7.5, width = 10)
+  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
+
+  theme_bw()+
+
+  theme(panel.spacing = unit(0.5, "lines"),
+        text = element_text(size=14),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=14), 
+        legend.title=element_text(size=14, 
+                                  face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+        axis.title.y = element_text(size = 14),
+        axis.text.y = element_text(angle = 90))
+
+ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 4, width = 8)
 var.plot
+
+# svg("figures/Variance_plot.svg", width=6, height=6)
+# var.plot
+# dev.off()
 ```
@@
 For outcomes that measured both males and females (both) phenotypic variation did not change **or** changed for males and females in opposite directions and thus cancels out when measured together.
+Circle size is proportional to sample size.
+
+**Table S9** The above figure is based off the following dataframe:
+```{r}
+colnames(predictions.variance) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
+predictions.variance <- format(predictions.variance, digits = 2)
+predictions.variance %>% pander()
+```
+
+Briefly, we can test whether the stressed female and the stressed both are different:
+
+```{r}
+anova(variance.model, L=c(0, 0, 0, 1, -1, 0))
+```
 
@@
 
-> Luke re-wrote this into a function, for neatness. You can replace 'dataset' and 'model' with whatever to save copy-pasting the code.
-
-```{r, fig.height= 7.5, fig.width=10, warning=FALSE, message=FALSE}
+```{r, fig.height= 6, fig.width=8, warning=FALSE, message=FALSE}
 
@@
   ggplot(dataset, aes(x = sqrt(var.g), y = g)) +
-    geom_point(size=1, shape = 21, color= "grey20") +
-    xlab("Standard Error") + ylab("Effect size (Hedges' g)") +
+    geom_point(size=1.5, shape = 21, color= "grey20") +
+    xlab("Standard Error") + ylab("Effect Size (Hedges' g)") +
     geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) + # confidence lines
@@
     #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI, colour = "tomato") +
-    geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI, colour = "tomato") +
+    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotdash', data=dfCI, colour = "tomato",size =0.75) +
+    geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotdash', data=dfCI, colour = "tomato",size=0.75) +
     scale_x_reverse() +
@@
     coord_flip() +
-    scale_fill_brewer(palette = "Set1")
-    # theme_classic()
-    # apatheme
+    scale_fill_brewer(palette = "Set1")+
+
+    theme_bw()+
+
+    theme(panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        text = element_text(size=14),
+        axis.line=element_line(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.text = element_text(size=12),
+        legend.title=element_text(size=12,
+                                  face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 12),
+        axis.title.y = element_text(size = 12))
 
@@
 
+# svg("figures/funnel_plot.svg", width=8, height=6)
+# funnel.plot
+# dev.off()
 ```
@@
 
-```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
-JIF.plot <- prelim.data %>% ggplot(aes(x=JIF, y=g))+
-  geom_jitter(color='darkgreen', alpha=.3, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
+```{r, fig.height= 4, fig.width=8, warning=FALSE}
+JIFlm <- (lm(g ~ 1 + JIF, data = prelim.data))
+
+# cairo_ps("figures/JIF_Plot.eps", width=10, height=7.5)
+
+JIF.plot <- ggplot(data = prelim.data, aes(x=JIF, y=g))+
+  geom_jitter(color='darkgreen', alpha=0.4, aes(size = (1/(var.g))/sum((1/(var.g)))*100), show.legend = FALSE)+
   geom_hline(yintercept=0, linetype = 'dotted')+
-  geom_smooth(method='lm', color='black')+
-  scale_x_continuous(breaks = c(0,10,20,30,40), limits = c(2,42.5))+
-  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Journal Impact Factor')
-
-ggsave(plot = JIF.plot, filename = "figures/JIF_plot.eps", height = 7.5, width = 10)
+  geom_smooth(method='lm', color='black', linetype="solid")+
+  scale_x_log10(limits = c(-5,40), breaks = c(0, 1, 2, 5, 10, 20, 40))+
+  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Journal Impact Factor (logarithmic scale)')+
+
+  theme_bw()+
+
+    theme(panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        text = element_text(size=14),
+        axis.line=element_line(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.text = element_text(size=12),
+        legend.title=element_text(size=12,
+                                  face = "bold"),
+        axis.title.x = element_text(size = 12),
+        axis.title.y = element_text(size = 12))
+
+# dev.off()
+# 
+# svg("figures/JIF_Plot.svg", width=4, height=4)
+# JIF.plot
+# dev.off()
+
 JIF.plot
+
 ```
@@
 Most papers were published in discipline specific journals such as _Evolution_ and _Journal of Evolutionary Biology_.
+Circle size is proportional to weight (%) of study.
+
+We can test the effect of JIF on ES with a simple linear model: 
+```{r}
+JIFlm <- lm(g ~ log(JIF), data = prelim.data)
+summary(JIFlm)
+```
+
+This shows that JIF does not have a significant effect on effect sizes from the published study
 
@@
 
-```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
+```{r, fig.height= 4, fig.width=8, warning=FALSE}
 time.plot <- prelim.data %>% 
   ggplot(aes(x=Year, y=g))+
-  geom_jitter(color='darkorange', alpha=.5, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
+  geom_jitter(color='darkorange', alpha=.5, aes(size = (1/(var.g))/sum((1/(var.g)))*100), show.legend = FALSE)+
   geom_hline(yintercept=0, linetype = 'dotted')+
   geom_smooth(method='lm', color='black')+
-  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Year')
-
-ggsave(plot = time.plot, filename = "figures/time_plot.eps", height = 7.5, width = 10)
+  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Year')+
+    theme_bw()+
+    theme(panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(),
+        text = element_text(size=14),
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.text = element_text(size=12),
+        legend.title=element_text(size=12,
+                                  face = "bold"),
+        axis.title.x = element_text(size = 12),
+        axis.title.y = element_text(size = 12))
+
 time.plot
+
+# svg("figures/Time_Plot.svg", width=4, height=4)
+# time.plot
+# dev.off()
 ```
@@
 **Figure S7:** The effect size dataset shows little to no signs of the time-lag bias as the average effect sizes from published studies remains consistent across the previous two decades.
-
-###Sample Size
-
-We also collected sample sizes for each of the effect sizes calculated.
+Circle size is proportional to weight of study (%).
+
+We can also test the effect of publication year on ES with a simple linear model (similar to the one for JIF: 
+```{r}
+Yearlm <- lm(g ~ Year, data = prelim.data)
+summary(Yearlm)
+```
+
+This shows that publication year does not have a significant effect on effect sizes from the published study
+
+<!-- ###Sample Size -->
+
+<!-- We also collected sample sizes for each of the effect sizes calculated.
 Because we are dealing withj different taxa some studies are not suited to have sample sizes in the 1000's.
-We can simply inspect the sample size ande effect sizes through the following plot:
-
-```{r, fig.height= 10, fig.width=5}
-samplesize.plot <- prelim.data %>% ggplot(aes(x=n, y = g))+
-  geom_point(fill="grey", color="grey20", shape=21)+
-  scale_x_log10(breaks = c(10, 100, 1000, 10000)) + 
-  #xlim(0,2100)+
-  facet_grid(Taxon~., scales='free')+
-  ylim(-3.5,3.5)+
-  geom_hline(yintercept=0, linetype="dashed")+
-  labs(y='Effect size (Hedges g)', x= 'Sample Size (n) [logscale]')
-
-ggsave(plot = samplesize.plot, filename = "figures/samplesize_plot.eps", height = 10, width = 5)
-samplesize.plot
-```
-<br></br>
-**Figure S8:** Variation in size does not appear to have unexpected trends in any taxons, with greater variation in effect size for those studies utilising a lower sample size.
-
-From these plots we can see that with increased sample size the effect sizes are closer to zero.
+We can simply inspect the sample size ande effect sizes through the following plot: -->
+
+<!-- ```{r, fig.height= 10, fig.width=5} -->
+<!-- samplesize.plot <- prelim.data %>% ggplot(aes(x=n, y = g))+ -->
+<!--   geom_point(fill="grey", color="grey20", shape=21)+ -->
+<!--   scale_x_log10(breaks = c(10, 100, 1000, 10000)) +  -->
+<!--   #xlim(0,2100)+ -->
+<!--   facet_grid(Taxon~., scales='free')+ -->
+<!--   ylim(-3.5,3.5)+ -->
+<!--   geom_hline(yintercept=0, linetype="dashed")+ -->
+<!--   labs(y='Effect size (Hedges g)', x= 'Sample Size (n) [logscale]') -->
+
+<!-- ggsave(plot = samplesize.plot, filename = "figures/samplesize_plot.eps", height = 10, width = 5) -->
+<!-- samplesize.plot -->
+<!-- ``` -->
+<!-- <br></br> -->
+<!-- **Figure S8:** Variation in size does not appear to have unexpected trends in any taxons, with greater variation in effect size for those studies utilising a lower sample size.  -->
+
+<!-- From these plots we can see that with increased sample size the effect sizes are closer to zero.
 This trend is taken into account as meta-analytic models and are wighted by 1/variance.
 **Note** Promislow (1998) has one sample size of >10,000 in flies and is not shown here to avoid making radical changes to the scale.
+-->
 
@@
   labs(y='Effect size (Hedges g)', x= 'Blinding', size = 'Weight (%)')+
-  guides(fill=FALSE)
+  guides(fill=FALSE)+
+  theme_bw()+
+  theme(panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(),
+        text = element_text(size=14),
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.text = element_text(size=12),
+        legend.title=element_text(size=12,
+                                  face = "bold"),
+        axis.title.x = element_text(size = 12),
+        axis.title.y = element_text(size = 12))
 
@@
   geom_smooth(method = 'lm', color='black')+
-  labs(y='Effect size (Hedges g)', x= 'Generations', size= 'Weight (%)')
+  labs(y='Effect size (Hedges g)', x= 'Generations', size= 'Weight (%)')+
+  theme_bw()+
+  theme(panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(),
+        text = element_text(size=14),
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.text = element_text(size=12),
+        legend.title=element_text(size=12,
+                                  face = "bold"),
+        axis.title.x = element_text(size = 12),
+        axis.title.y = element_text(size = 12))
 
@@
 generations.plot
+
+# svg("figures/Generations_Plot.svg", width=10, height=7.5)
+# generations.plot
+# dev.off()
 ```
@@
 **Figure S10:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
+<br></br>
+
+Kawecki et al.(2012) reviewed the field of experimental evolution and noted that changes to variation may need longer generations to become apparent.
+The following graph looks at the relationship between number of generations and lnCVr
+
+```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
+generations.plot.var <- prelim.data2 %>% ggplot(aes(x=Generations, y=lnCVr))+
+  geom_point(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
+  ylim(-3.5,3.5)+
+  geom_hline(yintercept=0, linetype="dashed") + 
+  scale_fill_brewer(palette = "Set3")+
+  geom_smooth(method = 'lm', color='black')+
+  labs(y='Effect size (lnCVR)', x= 'Generations', size= 'Weight (%)')+
+  theme_bw()+
+  theme(panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        text = element_text(size=14),
+        axis.line=element_line(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.text = element_text(size=12),
+        legend.title=element_text(size=12,
+                                  face = "bold"),
+        axis.title.x = element_text(size = 12),
+        axis.title.y = element_text(size = 12))
+
+# ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
+generations.plot.var
+```
+
+**Figure S11:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran.
+
+```{r}
+summary(lm(lnCVr ~ Generations, data = prelim.data2))
+```
 

### 2018-05-04 meta_analysis_sexual_selection_pop_fitness.Rmd
4/5 update

@@
 <br></br>
-**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
+**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
 Rows with multiple data points denote studies that provided multiple effect sizes.
@@
 outcome.frame$I2 <- as.numeric(outcome.frame$I2)
+outcome.frame$Class <- c("Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Direct", "Direct", "Direct")
 
@@
 
-**Table S8**
+**Table S8** The predictions in the plot above use the following dataframe
 ```{r}
@@
 
+Both (unstressed vs stressed)
 ```{r}
@@
 
-We can also test if there is a difference between males and females in unstressed and stressed conditions:
+We can also test if there is a difference between males and females in unstressed conditions:
 

### 2018-05-15 meta_analysis_sexual_selection_pop_fitness.Rmd
brms add

@@
 ```
+__________________________________
+
+###Bayesian models using _brms_ package
+
+We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
+```{r}
+library(rstan) #Note that installation requires some effort
+library(brms) 
+library(backports) #seems to be a dependency
+
+#Use brm to create a model similar to the one used in the REML approach. 
+meta.brms <- brm(g | se(sqrt(var.g), sigma = TRUE) ~ 1 + Sex * Environment 
+                + (1|Study.ID) 
+                + (1|Outcome),
+                control = list(adapt_delta = 0.95),
+                data = restricted.data)
+
+summary(meta.brms)
+```
+
+Plot summart of model
+```{r}
+plot(meta.brms)
+```
+
+Obtain marginal effects plots
+```{r}
+marginal_effects(meta.brms)
+```
 

### 2018-05-18 meta_analysis_sexual_selection_pop_fitness.Rmd
Bayesian update

--- 2018-05-04 meta_analysis_sexual_selection_pop_fitness.Rmd
@@
 library(RColorBrewer)
+library(ggridges)
 source("Vdodge_function.R") # nice function for ggplot
@@
 ```
+__________________________________
+
+###Bayesian models using _brms_ package
+
+We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
+```{r, warning=FALSE}
+library(rstan) #Note that installation requires some effort
+library(brms) 
+library(backports) #seems to be a dependency
+```
+
+```{r, warning = FALSE, results='hide', message=FALSE}
+#Use brm to create a model similar to the one used in the REML approach. 
+#Use brm to create a model similar to the one used in the REML approach. 
+meta.brms <- brm(g| se(sqrt(var.g), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (sqrt(var.g)) with sex and environment as moderators
+                + (1|Study.ID) #group level effect #1
+                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
+                family = "gaussian", #default
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.99),
+                data = restricted.data)
+```
+
+```{r}
+summary(meta.brms)
+```
+
+Plot summary of the model estimates
+```{r}
+plot(meta.brms)
+```
+
+We can also obtain marginal effects plots
+
+> Are these like the predictions?
+
+```{r}
+marginaleffects <- marginal_effects(meta.brms)
+```
+
+Obtain fitted values: **Note that the fitted values obtained here have much smaller error than the predict values, which blow out**
+
+```{r}
+#obtain average variance of each group in the prediction
+av.var.g <- as.numeric(c(restricted.data %>% filter (Sex == 'M' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
+              restricted.data %>% filter (Sex == 'B' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
+              restricted.data %>% filter (Sex == 'F' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
+              restricted.data %>% filter (Sex == 'M' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
+              restricted.data %>% filter (Sex == 'B' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
+              restricted.data %>% filter (Sex == 'F' & Environment == "Stressed") %>% summarise(mean = mean(var.g))))
+
+#Expand grid for environment and sex
+brms.newdata <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
+                           Environment = c("Unstressed", "Stressed")))
+#Add variance
+brms.newdata$var.g <- av.var.g
+
+#Add predictions
+brms.predict <- fitted(meta.brms, newdata = brms.newdata, re_formula = NA)
+brms.predict <- as.data.frame(brms.predict)
+brms.predictions <- data.frame(brms.newdata$Sex, brms.newdata$Environment, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)
+
+#Add sample size 
+brms.predictions$n <- as.numeric(predictions.complete2$n)
+
+#Name columns
+colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI", "n")
+```
+
+Plot results for brms prediction using the same ggplot code as for the metafor model predictions
+
+```{r, fig.height=6, fig.width = 6}
+EnvSex.metaanalysis.brms <- brms.predictions %>% 
+      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female")) %>%
+  ggplot(aes(x = Estimate, y= Environment, fill = Sex)) + 
+  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
+  geom_errorbarh(aes(xmin = brms.predictions$LCI, 
+                     xmax = brms.predictions$UCI,
+                     color = Sex), height = 0, position = pd, show.legend = F) +
+  geom_point(aes(size=n), position = pd, shape=21, color = "grey20") + 
+  scale_size(guide = 'none')+
+  ylab("Environment\n")+
+  xlab("\nEffect Size (Hedges' g)")+
+  scale_fill_brewer(palette = "Set1")+
+  scale_color_brewer(palette = "Set1")+
+  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
+  scale_x_continuous(limits = c(-0.2, 1), breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1))+
+
+  theme_bw()+
+
+  theme(panel.spacing = unit(0.5, "lines"),
+        text = element_text(size=14),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=14), 
+        legend.title=element_text(size=14, 
+                                  face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+        axis.title.y = element_text(size = 14),
+        axis.text.y = element_text(angle = 90),
+        plot.title = element_text(size = 14))
+
+EnvSex.metaanalysis.brms
+```
+<br></br>
+**Figure X** Bayesian fitted values for effect size using a comprable model to the one used in the REML approach
+
+Let's get the distribution of posterior fitted values and plot with ggridges
+
+```{r}
+#Obtain posterior fitted values and transform
+posterior_fit <- data.frame(t(posterior_linpred(meta.brms, newdata = brms.newdata, re_formula = NA)))
+
+#Add columns for Environment and Sex
+posterior_fit$Sex <- c("Male", "Both", "Female", "Male", "Both", "Female")
+posterior_fit$Environment <- c("Benign_Male", "Benign_Both", "Benign_Female", "Stressful_Male", "Stressful_Both", "Stressful_Female")
+
+#Clean up dataframe
+posterior_fit <- melt(posterior_fit, id = c("Sex", "Environment"))
+posterior_fit$variable <- NULL
+```
+
+```{r, fig.height=8, fig.width=8}
+posterior_fit %>% ggplot(aes(x=value, y = Environment, fill = Sex))+
+  geom_density_ridges2(alpha = 0.75)+
+  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
+    ylab("Environment\n")+
+  xlab("\nPosterior Effect Size (Hedges' g)")+
+  scale_fill_brewer(palette = "Set1")+
+  scale_color_brewer(palette = "Set1")+
+  guides(fill = guide_legend(reverse=T, override.aes = list(size = 0.5)))+
+  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+
+
+  theme_bw()+
+
+  theme(panel.spacing = unit(0.5, "lines"),
+        text = element_text(size=14),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=14), 
+        legend.title=element_text(size=14, 
+                                  face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+        axis.title.y = element_text(size = 14),
+        axis.text.y = element_text(angle = 0),
+        plot.title = element_text(size = 14))
+
+```
+<br></br>
+**Figure X** Posterior fitted values for Hedges' g using the same model as above
 

### 2018-05-20 meta_analysis_sexual_selection_pop_fitness.Rmd
plot with both bayesian and frenq

@@
 pd <- position_dodgev(height = 0.65)
-EnvSex.metaanalysis <- predictions.complete2 %>% 
+predictions.complete2 <- predictions.complete2 %>% 
       mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
@@
          Sex = replace(Sex, Sex == "F", "Female")) %>%
-  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
+  mutate(Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
+         Environment = replace(Environment, Environment == "Unstressed", "Benign"))
+ EnvSex.metaanalysis <- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
   geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
@@
 We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
-```{r, warning=FALSE}
+```{r, warning=FALSE, message = FALSE}
 library(rstan) #Note that installation requires some effort
@@
 library(backports) #seems to be a dependency
+devtools::install_github("mvuorre/brmstools")
+library(brmstools) 
 ```
@@
 posterior_fit$Sex <- c("Male", "Both", "Female", "Male", "Both", "Female")
-posterior_fit$Environment <- c("Benign_Male", "Benign_Both", "Benign_Female", "Stressful_Male", "Stressful_Both", "Stressful_Female")
+posterior_fit$Environment <- c("Benign", "Benign", "Benign", "Stressful", "Stressful", "Stressful")
 
@@
 
-```{r, fig.height=8, fig.width=8}
-posterior_fit %>% ggplot(aes(x=value, y = Environment, fill = Sex))+
-  geom_density_ridges2(alpha = 0.75)+
+```{r, fig.height=5, fig.width=5}
+
+pd <- position_dodgev(height = 0.3)
+posterior.plot <- posterior_fit %>% ggplot()+
+  geom_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10)+
   geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
@@
 
-  theme(panel.spacing = unit(0.5, "lines"),
+  theme(panel.spacing = unit(0.1, "lines"),
         text = element_text(size=14),
@@
 
+both.plots <- posterior.plot + 
+  geom_point(data = predictions.complete2, 
+             aes(x = pred, y = Environment, size=nn, fill = Sex), 
+             shape=21, color = "grey20", position = pd, show.legend = F) +
+
+  geom_errorbarh(data = predictions.complete2, 
+                 aes(x= pred, xmin = predictions.complete2$ci.lb,
+                     xmax = predictions.complete2$ci.ub, y = Environment,
+                     color = Sex), 
+                 height = 0, show.legend = F, position = pd)+
+    scale_y_discrete(expand=c(0.075,0))
+
+both.plots
+
+svg("figures/both_plot.svg", width=6, height=6)
+both.plots
+dev.off()
 ```

### 2018-05-24 meta_analysis_sexual_selection_pop_fitness.Rmd
Luke brms changes

@@
 prelim.data$Study.ID <- prelim.data$Study.ID %>% factor()
-prelim.data$Taxon <- prelim.data$Taxon %>% factor()
 prelim.data$Group.ID <- prelim.data$Group.ID %>% factor()
-prelim.data$Authors <- prelim.data$Authors %>% factor()
-prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
-prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
-prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor()
-prelim.data$Species <- prelim.data$Species %>% factor()
+prelim.data$Environment <- prelim.data$Environment %>% relevel(ref="Unstressed")
+prelim.data$Sex <- prelim.data$Sex %>% relevel(ref="B")
+
 #Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
-prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
-prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor() %>% relevel(ref="NO")
+prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% relevel(ref="Indirect")
+prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% relevel(ref="NO")
 prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor() %>% relevel(ref="0")
@@
 Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)
-
 ```
@@
 model.preliminary <- rma.mv(g, var.g, 
-                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + Generations + Blinding, # << ----- Add big model, then cull predictors to this one
+                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + log(Generations) + Blinding, # << ----- Add big model, then cull predictors to this one
                          random = list(~ 1 | Study.ID, 
@@
 summary(model.preliminary)
+
+brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding 
+                + (1|Study.ID) #group level effect #1
+                + (1|Outcome)
+                + (1|Taxon), 
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.99, max_treedepth = 15),
+                data = prelim.data %>% mutate(SE = sqrt(var.g)))
+
+bayesplot::mcmc_areas(posterior_samples(brms.preliminary)[,1:11]) + geom_vline(xintercept = 0, linetype = 2)
+
+new.data <- prelim.data %>% 
+  mutate(SE = sqrt(var.g)) %>% 
+  select(Sex, Environment, Blinding, Generations, SE) %>% 
+  mutate(Generations = mean(log(Generations)), Blinding = "Blind", SE = 0) %>% 
+  distinct() %>% arrange(Sex, Environment)
+predictions <- data.frame(new.data, predict(brms.preliminary, newdata = new.data, re_formula = NA))
+
+pd <- position_dodge(0.2)
+predictions %>% ggplot(aes(Sex, Estimate, group = Environment)) + 
+  geom_errorbar(aes(ymin = X2.5.ile, ymax = X97.5.ile), position = pd, width = 0) +
+  geom_point(position = pd) +
+  coord_flip()
 ```
@@
 restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Beetle") 
+restricted.data$Outcome <- restricted.data$Outcome %>% factor()
 
@@
 summary(model.complete)
+
+brms.complete <- brm(g | se(SE)  ~ 1 + Sex * Environment + Taxon + Outcome
+                + (1|Study.ID), #group level effect #1
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                data = restricted.data %>% mutate(SE = sqrt(var.g)))
+
+brms.complete2 <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding + 
+                + (1|Taxon) #group level effect #1
+                + (1|Outcome) #group level effect #1
+                + (1|Study.ID), #group level effect #1
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.9999, max_treedepth = 15),
+                data = restricted.data %>% mutate(SE = sqrt(var.g)))
+
+bayesplot::mcmc_areas(posterior_samples(brms.complete)[,1:24]) + geom_vline(xintercept = 0, linetype = 2)
+bayesplot::mcmc_areas(posterior_samples(brms.complete2) %>% select(-starts_with("r"), -lp__)) + geom_vline(xintercept = 0, linetype = 2)
+
+post <- (posterior_samples(brms.complete, 
+                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
+                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
+                                    "b_SexF:EnvironmentStressed", "b_OutcomeReproductiveSuccess")) %>%
+  mutate(both_benign = b_Intercept + b_SexB + b_OutcomeReproductiveSuccess,
+         both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed` + b_OutcomeReproductiveSuccess,
+         male_benign = b_Intercept + b_OutcomeReproductiveSuccess,
+         male_stressful = b_Intercept + b_EnvironmentStressed + b_OutcomeReproductiveSuccess,
+         female_benign = b_Intercept + b_SexF + b_OutcomeReproductiveSuccess,
+         female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed` + b_OutcomeReproductiveSuccess))[,-(1:7)]
+
+post2 <- (posterior_samples(brms.complete, 
+                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
+                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
+                                    "b_SexF:EnvironmentStressed")) %>%
+  mutate(both_benign = b_Intercept + b_SexB,
+         both_stressful = b_Intercept + b_SexB + `b_SexB:EnvironmentStressed`,
+         male_benign = b_Intercept,
+         male_stressful = b_Intercept + b_EnvironmentStressed ,
+         female_benign = b_Intercept + b_SexF ,
+         female_stressful = b_Intercept + b_SexF + `b_SexF:EnvironmentStressed` ))[,-(1:6)]
+
+bayesplot::mcmc_areas(post) + geom_vline(xintercept = 0, linetype = 2)
+
+new.data <- restricted.data %>% 
+  mutate(SE = sqrt(var.g)) %>% 
+  select(Sex, Environment, Blinding, Generations, SE, Taxon) %>% 
+  mutate(Generations = mean(log(Generations)), 
+         Blinding = "Blind", 
+         Taxon = "Fly",
+         Outcome = "Reproductive Success",
+         SE = 0) %>% 
+  distinct() %>% arrange(Sex, Environment)
+predictions.complete <- data.frame(new.data, fitted(brms.complete, newdata = new.data, re_formula = NA))
+
+pd <- position_dodge(0.2)
+predictions.complete %>% ggplot(aes(Sex, Estimate, group = Environment, colour = Environment)) + 
+  geom_errorbar(aes(ymin = X2.5.ile, ymax = X97.5.ile), position = pd, width = 0) +
+  geom_point(position = pd) +
+  coord_flip()
 ```

### 2018-05-24 meta_analysis_sexual_selection_pop_fitness.Rmd
Justin Previous Bayesian Explore

--- 2018-05-20 meta_analysis_sexual_selection_pop_fitness.Rmd
@@
 predictions.complete2 <- format(predictions.complete2, digits = 2)
+predictions.complete2$Prediction = as.numeric(predictions.complete2$Prediction)
+predictions.complete2$CI.lb = as.numeric(predictions.complete2$CI.lb)
+predictions.complete2$CI.ub = as.numeric(predictions.complete2$CI.ub)
+predictions.complete2$n = as.numeric(predictions.complete2$n)
+
 predictions.complete2 %>% pander()
@@
 library(backports) #seems to be a dependency
-devtools::install_github("mvuorre/brmstools")
+#devtools::install_github("mvuorre/brmstools")
 library(brmstools) 
@@
 #Use brm to create a model similar to the one used in the REML approach. 
-meta.brms <- brm(g| se(sqrt(var.g), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (sqrt(var.g)) with sex and environment as moderators
+meta.brms <- brm(g| se(sqrt(var.g), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (sqrt(var.g)) with sex, environment and their interaction as moderators
                 + (1|Study.ID) #group level effect #1
@@
 
-```{r, fig.height=5, fig.width=5}
+```{r, fig.height=5.5, fig.width=5.5}
 
@@
 posterior.plot <- posterior_fit %>% ggplot()+
-  geom_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10)+
+  geom_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F)+
   geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
-    ylab("Environment\n")+
-  xlab("\nPosterior Effect Size (Hedges' g)")+
+    ylab("Environment")+
+  xlab("\nEffect Size (Hedges' g)")+
   scale_fill_brewer(palette = "Set1")+
   scale_color_brewer(palette = "Set1")+
-  guides(fill = guide_legend(reverse=T, override.aes = list(size = 0.5)))+
   scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+
@@
   theme(panel.spacing = unit(0.1, "lines"),
-        text = element_text(size=14),
+        text = element_text(size=16),
         panel.border= element_blank(),
@@
         panel.grid.minor.x = element_blank(), 
-        legend.text = element_text(size=14), 
-        legend.title=element_text(size=14, 
+        legend.text = element_text(size=16), 
+        legend.title=element_text(size=16, 
                                   face = "bold"),
         axis.title.x = element_text(hjust = 0.5, size = 14),
-        axis.title.y = element_text(size = 14),
+        axis.title.y = element_text(size = 16, hjust = 0.35, margin = margin(r=-10)),
         axis.text.y = element_text(angle = 0),
-        plot.title = element_text(size = 14))
+        plot.title = element_text(size = 16))
 
@@
   geom_point(data = predictions.complete2, 
-             aes(x = pred, y = Environment, size=nn, fill = Sex), 
-             shape=21, color = "grey20", position = pd, show.legend = F) +
+             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
+             shape=21, color = "grey20", position = pd) +
+
+    guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
+    scale_size(guide = 'none')+
 
   geom_errorbarh(data = predictions.complete2, 
-                 aes(x= pred, xmin = predictions.complete2$ci.lb,
-                     xmax = predictions.complete2$ci.ub, y = Environment,
+                 aes(x= Prediction, xmin = predictions.complete2$CI.lb,
+                     xmax = predictions.complete2$CI.ub, y = Environment,
                      color = Sex), 
@@
 
-svg("figures/both_plot.svg", width=6, height=6)
-both.plots
-dev.off()
+# svg("figures/both_plot.svg", width=5.5, height=5.5)
+# both.plots
+# dev.off()
+# 
+# pdf("figures/both_plot.pdf",  width = 5.5, height = 5.5)
+# both.plots
+# dev.off()
 ```

### 2018-05-28 meta_analysis_sexual_selection_pop_fitness.Rmd
Bayesian plots for Hedges' g and lnCVR

--- 2018-05-24 meta_analysis_sexual_selection_pop_fitness.Rmd
@@
 library(ggridges)
+library(rstan) #Note that installation requires some effort
+library(brms) 
+library(backports) #seems to be a dependency
+library(bayesplot)
+#devtools::install_github("mvuorre/brmstools")
+library(brmstools) 
 source("Vdodge_function.R") # nice function for ggplot
@@
 ```{r, fig.height=18, fig.width=12}
-# Run standard random effects model
-# forest.model <- rma.mv(g, var.g, 
-#                        mods = ~ 1 + Sex * Environment + Taxon,
-#                        random = list(~ 1 | Study.ID, 
-#                                        ~ 1 | Outcome),
-#                        method = "REML", 
-#                        data = prelim.data)
-# 
-# # Obtain residuals
-# resstandards <- (rstandard.rma.mv(forest.model, 
-#                                    type="response"))
-# 
-# # Obtain grand mean effect size    <- ADDED BY LUKE
-# grand.mean <- as.numeric(forest.model$b)
-# 
-# # Create new df with residuals replacing raw
-# df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
-# df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
-# df.forest.model$sei <- resstandards$se
 
@@
 prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))
-# 
-# # Get author and year in one
-# short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
-#                                  short = prelim.data$Authors %>% unique() %>% 
-#   as.character() %>% 
-#   strsplit(split = ",") %>% 
-#   sapply(FUN=function(x) x[1])) %>%
-#   left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
-#   mutate(suffix = "")
-# 
-# # Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
-# dups <- with(short.author.names, table(short, Year)) %>% melt()
-# dups <- dups[dups$value > 1, ]
-# for(i in 1:nrow(dups)){
-#   short.author.names$suffix[
-#     short.author.names$short == dups$short[i] &
-#       short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
-# }
-# 
-# # Add the AuthorYear column to the dataframe of effect sizes
-# short.author.names <- short.author.names %>%
-#   mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
-#   select(long, AuthorYear)
-# prelim.data <- prelim.data %>% 
-#   left_join(short.author.names, by = c("Authors" = "long")) 
+
 library(ggthemes)
@@
 Positive values indicate fitness benefits of sexual selection.
-
-<!-- ###Quantitative summary using bootstrapped means -->
-
-<!-- We can obtain a bootstrap weighted mean for the entire dataset.
-Although this does not take into account any moderator variables it does provide a rough guide on where most of the datapoints sit:  -->
-
-<!-- ```{r} -->
-<!-- #Run function -->
-<!-- get.CIs.for.weighted.mean <- function(x, weights){ -->
-<!--   total.resamples <- 10000 -->
-<!--   num.chunks <- ceiling(length(x)*total.resamples / 10^7) # To be nice to RAM, let's keep these to ten million or less  -->
-<!--   if(num.chunks == 1){ -->
-<!--     rand <- sample(length(x), length(x)*total.resamples, replace = TRUE) -->
-<!--     resampled.weighted.means <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:total.resamples, each = length(x))) %>%  -->
-<!--       group_by(replicate) %>%  -->
-<!--       summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean -->
-<!--   } -->
-
-<!--   else{ -->
-<!--     resampled.weighted.means <- vector(mode = "list", length = 0) -->
-<!--     number.of.resamples <- floor(total.resamples/num.chunks) -->
-<!--     final.chunk.size <- total.resamples - number.of.resamples * (num.chunks-1) -->
-<!--     for(i in 1:num.chunks){ -->
-<!--       if(i == num.chunks) number.of.resamples <- final.chunk.size -->
-<!--       rand <- sample(length(x), length(x) * number.of.resamples, replace = TRUE) -->
-<!--       resampled.weighted.means[[i]] <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:number.of.resamples, each = length(x))) %>%  -->
-<!--         group_by(replicate) %>%  -->
-<!--         summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean -->
-<!--     } -->
-<!--     resampled.weighted.means <- unlist(resampled.weighted.means) -->
-<!--   } -->
-
-<!--   data.frame(w.mean = median(resampled.weighted.means), -->
-<!--              lowerCI = quantile(resampled.weighted.means, probs = 0.025) %>% as.numeric(), -->
-<!--              upperCI = quantile(resampled.weighted.means, probs = 0.975) %>% as.numeric()) -->
-<!-- } -->
-
-<!-- #Get weights -->
-<!-- prelim.data$Standard.weights <- (1/prelim.data$var.g) -->
-
-<!-- #Run function with weights -->
-<!-- get.CIs.for.weighted.mean(prelim.data$g, prelim.data$Standard.weights) %>% pander() -->
-<!-- ``` -->
 
@@
 
-<!-- Check the results on a plot -->
-<!-- ```{r} -->
-<!-- pd <- position_dodgev(height = .7) -->
-<!-- outcome.frame %>% ggplot(aes(x = b, y= Outcome)) +  -->
-<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
-<!--   geom_errorbarh(aes(xmin = ci.lb,  -->
-<!--                      xmax = ci.ub), height = 0, position = pd, show.legend = F) + -->
-<!--   geom_point(position = pd, color = "grey20") +  -->
-<!--   ylab("Outcome\n")+ -->
-<!--   xlab("\nEffect Size (Hedges g)")+ -->
-<!--   xlim(-2.5, 2.5)+ -->
-<!--   ggtitle('Standard Random Effects Model') -->
-<!-- ``` -->
-
 ___________________
@@
 ## Multilevel Meta-Analysis
-
-<!-- >The following documents how I could run individual models for each outcome or outcome.class of interest and then plot them.
-This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment) -->
-
-<!-- > Nice idea, but I think the correct way to do this is to fit Outcome.class as a moderator, and then use predict() to find the average effect size within each of the 3 levels, as you have done below.
-I coded something below, but it's wrong: -->
-
-<!-- ```{r} -->
-<!-- model.outcome.class <- rma(g, var.g, -->
-<!--                            mods = ~ Outcome.Class,  -->
-<!--                            method = "REML",  -->
-<!--                            intercept = TRUE,  -->
-<!--                            data = prelim.data) -->
-
-<!-- # Get the intercept (i.e. the grand mean for 'ambiguous', and the effects for the others) -->
-<!-- mod.table <- do.call("cbind", model.outcome.class[names(model.outcome.class) %in% c("b", "ci.lb", "ci.ub")]) -->
-
-<!-- data.frame(Outcome.class = c("Ambiguous", "Direct", "Indirect"), -->
-<!--            mod.table) %>% -->
-<!--   ggplot(aes(y = Outcome.class, x = V1))  + -->
-<!--   geom_vline(xintercept = 0, linetype = 2) + -->
-<!--   geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height=0) + -->
-<!--   geom_point() +  -->
-<!--   xlab("Effect size and 95% CIs") -->
-<!-- ``` -->
-
-<!-- There is not really enough direct outcomes to analyse by itself so hence we combine with indirect later -->
-<!-- ```{r} -->
-<!-- #Ambiguous outcomes -->
-
-<!-- model.Ambiguous <- rma(g, var.g, -->
-<!--                        mods = ~ 1,  -->
-<!--                        method = "REML",  -->
-<!--                        subset = (Outcome.Class == "Ambiguous"),  -->
-<!--                        intercept = TRUE,  -->
-<!--                        data = prelim.data) -->
-
-<!-- summary(model.Ambiguous) -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- #Indirect outcomes -->
-
-<!-- model.Indirect <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Indirect"), intercept = T ,data = prelim.data) -->
-
-<!-- summary(model.Indirect) -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- #Direct outcomes -->
-
-<!-- model.Direct <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Direct"), data = prelim.data) -->
-
-<!-- summary(model.Direct) -->
-<!-- ``` -->
-
-<!-- Now let's combine into a data frame and plot. The following plot could then be added to the large forest plot as summary polygons or summary points with error bars.  -->
-
-<!-- ```{r} -->
-<!-- #Data frame -->
-<!-- Outcome.category <- c('Ambiguous', 'Indirect', 'Direct') -->
-<!-- Estimate <- c(model.Ambiguous$b, model.Indirect$b, model.Direct$b) -->
-<!-- l.ci <- c(model.Ambiguous$ci.lb, model.Indirect$ci.lb, model.Direct$ci.lb) -->
-<!-- u.ci <- c(model.Ambiguous$ci.ub, model.Indirect$ci.ub, model.Direct$ci.ub) -->
-<!-- data.1 <- data.frame(Outcome.category, Estimate, l.ci, u.ci) -->
-
-<!-- #plot -->
-
-<!-- data.1 %>% ggplot(aes(x = Estimate, y= Outcome.category)) +  -->
-<!--   geom_point() + -->
-<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
-<!--   geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, size=1) + -->
-<!--   ylab("Outcome Category")+ -->
-<!--   xlab("Effect Size")+ -->
-<!--   xlim(-.2, .5)+ -->
-<!--   ggtitle('Meta-Analysis Results') -->
-<!-- ``` -->
-
-<!-- From the previous forest plot and models we see that overall sexual selection is beneficial towards population fitness.
-Although this is heavily modulated by the individual outcome and the outcome class.
-We explore heterogeneity in more depth later in this document.
--->
 
@@
 summary(model.preliminary)
+
+#Also use bayesian model
+
+brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding 
+                + (1|Study.ID) #group level effect #1
+                + (1|Outcome)
+                + (1|Taxon), 
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                data = prelim.data %>% mutate(SE = sqrt(var.g)))
+
+#Plot model results
+prelim.results.bayesplot <- bayesplot::mcmc_areas(posterior_samples(brms.preliminary)[,1:11]) + 
+  geom_vline(xintercept = 0, linetype = 2)
+
+prelim.results.bayesplot
+
 ```
@@
 summary(model.complete)
+
+#Have taxon as fixed effects
+brms.complete <- brm(g | se(SE)  ~ 1 + Sex * Environment + Taxon
+                + (1|Study.ID) #group level effect #1
+                + (1|Outcome), #group level effect #2 
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                data = restricted.data %>% mutate(SE = sqrt(var.g)))
+
+bayesplot::mcmc_areas(posterior_samples(brms.complete)[,1:13]) +
+  geom_vline(xintercept = 0, linetype = 2)
+
+# new.data <- restricted.data %>% 
+#   mutate(SE = sqrt(var.g)) %>% 
+#   select(Sex, Environment, Blinding, Generations, SE, Taxon) %>% 
+#   mutate(Generations = mean(log(Generations)), 
+#          Blinding = "Blind", 
+#          Taxon = "Fly",
+#          Outcome = "Reproductive Success",
+#          SE = 0) %>% 
+#   distinct() %>% arrange(Sex, Environment)
+# predictions.complete <- data.frame(new.data, fitted(brms.complete, newdata = new.data, re_formula = NA))
+# 
+# pd <- position_dodge(0.2)
+# predictions.complete %>% ggplot(aes(Sex, Estimate, group = Environment, colour = Environment)) + 
+#   geom_errorbar(aes(ymin = X2.5.ile, ymax = X97.5.ile), position = pd, width = 0) +
+#   geom_point(position = pd) +
+#   coord_flip()
 ```
@@
 We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above.
-```{r, warning=FALSE, message = FALSE}
-library(rstan) #Note that installation requires some effort
-library(brms) 
-library(backports) #seems to be a dependency
-#devtools::install_github("mvuorre/brmstools")
-library(brmstools) 
-```
 
@@
 #Use brm to create a model similar to the one used in the REML approach. 
-#Use brm to create a model similar to the one used in the REML approach. 
-meta.brms <- brm(g| se(sqrt(var.g), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (sqrt(var.g)) with sex, environment and their interaction as moderators
+meta.brms <- brm(g| se((SE), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (SE), sex, environment and their interaction are moderators
                 + (1|Study.ID) #group level effect #1
@@
                 cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
-                control = list(adapt_delta = 0.99),
-                data = restricted.data)
-```
-
-```{r}
+                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                data = restricted.data %>% mutate(SE = sqrt(var.g)))
+
 summary(meta.brms)
-```
-
-Plot summary of the model estimates
-```{r}
-plot(meta.brms)
-```
-
-We can also obtain marginal effects plots
-
-> Are these like the predictions?
-
-```{r}
-marginaleffects <- marginal_effects(meta.brms)
-```
-
-Obtain fitted values: **Note that the fitted values obtained here have much smaller error than the predict values, which blow out**
-
-```{r}
-#obtain average variance of each group in the prediction
-av.var.g <- as.numeric(c(restricted.data %>% filter (Sex == 'M' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
-              restricted.data %>% filter (Sex == 'B' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
-              restricted.data %>% filter (Sex == 'F' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
-              restricted.data %>% filter (Sex == 'M' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
-              restricted.data %>% filter (Sex == 'B' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
-              restricted.data %>% filter (Sex == 'F' & Environment == "Stressed") %>% summarise(mean = mean(var.g))))
+
+#You can obtain a posterior sampling through the ``fitted.brmsfit`` function, which gives the same posterior values as doing it manually (see below).**Note that the fitted values obtained here have much smaller error than the predict values, which blow out**
+
+# #obtain average variance of each group in the prediction
+# av.var.g <- as.numeric(c(restricted.data %>% filter (Sex == 'M' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
+#               restricted.data %>% filter (Sex == 'B' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
+#               restricted.data %>% filter (Sex == 'F' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
+#               restricted.data %>% filter (Sex == 'M' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
+#               restricted.data %>% filter (Sex == 'B' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
+#               restricted.data %>% filter (Sex == 'F' & Environment == "Stressed") %>% summarise(mean = mean(var.g))))
 
 #Expand grid for environment and sex
-brms.newdata <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
-                           Environment = c("Unstressed", "Stressed")))
-#Add variance
-brms.newdata$var.g <- av.var.g
-
-#Add predictions
-brms.predict <- fitted(meta.brms, newdata = brms.newdata, re_formula = NA)
-brms.predict <- as.data.frame(brms.predict)
-brms.predictions <- data.frame(brms.newdata$Sex, brms.newdata$Environment, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)
-
-#Add sample size 
-brms.predictions$n <- as.numeric(predictions.complete2$n)
-
-#Name columns
-colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI", "n")
-```
-
-Plot results for brms prediction using the same ggplot code as for the metafor model predictions
-
-```{r, fig.height=6, fig.width = 6}
-EnvSex.metaanalysis.brms <- brms.predictions %>% 
-      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
-         Sex = replace(Sex, Sex == "M", "Male"),
-         Sex = replace(Sex, Sex == "F", "Female")) %>%
-  ggplot(aes(x = Estimate, y= Environment, fill = Sex)) + 
-  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
-  geom_errorbarh(aes(xmin = brms.predictions$LCI, 
-                     xmax = brms.predictions$UCI,
-                     color = Sex), height = 0, position = pd, show.legend = F) +
-  geom_point(aes(size=n), position = pd, shape=21, color = "grey20") + 
-  scale_size(guide = 'none')+
-  ylab("Environment\n")+
-  xlab("\nEffect Size (Hedges' g)")+
-  scale_fill_brewer(palette = "Set1")+
-  scale_color_brewer(palette = "Set1")+
-  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
-  scale_x_continuous(limits = c(-0.2, 1), breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1))+
-
-  theme_bw()+
-
-  theme(panel.spacing = unit(0.5, "lines"),
-        text = element_text(size=14),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
-        panel.grid.major.x = element_blank(),
-        panel.grid.major.y = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(), 
-        legend.text = element_text(size=14), 
-        legend.title=element_text(size=14, 
-                                  face = "bold"),
-        axis.title.x = element_text(hjust = 0.5, size = 14),
-        axis.title.y = element_text(size = 14),
-        axis.text.y = element_text(angle = 90),
-        plot.title = element_text(size = 14))
-
-EnvSex.metaanalysis.brms
-```
-<br></br>
-**Figure X** Bayesian fitted values for effect size using a comprable model to the one used in the REML approach
+# brms.newdata <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
+#                            Environment = c("Unstressed", "Stressed")))
+# #Add variance
+# brms.newdata$var.g <- av.var.g
+# 
+# #Add predictions
+# brms.predict <- fitted(meta.brms, newdata = brms.newdata, re_formula = NA)
+# brms.predict <- as.data.frame(brms.predict)
+# brms.predictions <- data.frame(brms.newdata$Sex, brms.newdata$Environment, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)
+# 
+# #Name columns
+# colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI", "n")
+```
 
@@
 ```{r}
+post <- (posterior_samples(meta.brms, 
+                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
+                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
+                                    "b_SexF:EnvironmentStressed")) %>%
+         mutate(both_benign = b_Intercept + b_SexB,
+         both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed`,
+         male_benign = b_Intercept,
+         male_stressful = b_Intercept + b_EnvironmentStressed,
+         female_benign = b_Intercept + b_SexF,
+         female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed`))[,-(1:6)]
+
 #Obtain posterior fitted values and transform
-posterior_fit <- data.frame(t(posterior_linpred(meta.brms, newdata = brms.newdata, re_formula = NA)))
+# posterior_fit <- data.frame(t(posterior_linpred(meta.brms, newdata = brms.newdata, re_formula = NA)))
 
 #Add columns for Environment and Sex
-posterior_fit$Sex <- c("Male", "Both", "Female", "Male", "Both", "Female")
-posterior_fit$Environment <- c("Benign", "Benign", "Benign", "Stressful", "Stressful", "Stressful")
+post <- as.data.frame(t(post))
+post$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
+post$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")
 
 #Clean up dataframe
-posterior_fit <- melt(posterior_fit, id = c("Sex", "Environment"))
-posterior_fit$variable <- NULL
+post <- melt(post, id = c("Sex", "Environment"))
+post$variable <- NULL
 ```
@@
 pd <- position_dodgev(height = 0.3)
-posterior.plot <- posterior_fit %>% ggplot()+
-  geom_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F)+
+posterior.plot <- post %>% ggplot()+
+  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
   geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
@@
 
-# svg("figures/both_plot.svg", width=5.5, height=5.5)
+# svg("figures/both_plot.svg", width=6, height=6)
 # both.plots
@@
 <br></br>
-**Figure X** Posterior fitted values for Hedges' g using the same model as above
+**Figure X** Posterior fitted values for Hedges' g alongside the predictions from metafor
 
@@
 The _I^2^_ values for individual outcomes were presented earlier in this document and presented alongside the forest plot.
-
-<!-- Furthermore, we can obtain estimates of the intra-class correlation (ICC) within a study via:  -->
-<!-- ```{r} -->
-<!-- round(model.complete2$sigma2[1] / sum(model.complete2$sigma2), 3) -->
-<!-- ``` -->
-
-<!-- This means that within a study, between different outcomes, there is a correlation of 26.2 % (low-medium).
-This justifies including outcome as a level, as without it we would be assuming ICC = 1.
-We can also gain an estimate of the total heterogeniety, as the sum of the sigma componenets:  -->
-<!-- ```{r} -->
-<!-- round(sum(model.complete2$sigma2), 3) -->
-<!-- ``` -->
-
-<!-- #### Multilevel model using metafors alternative random effect structure  -->
-
-<!-- > This inner, outer factor stuff from the metafor package is a bit strange.
-There is a description in ``?rma.mv()`` but still unsure how it differs from the above model.
-It seems that it is useful to breakdown variance-covariance matrix but unsure how that would benefit our analysis.
--->
-
-<!-- ```{r} -->
-<!-- #Just to check, how about with outcome as the inner factor  -->
-<!-- model.complete2.2 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ factor(Outcome) | Study.ID, method = "REML", data = restricted.data) -->
-
-<!-- summary(model.complete2.2) -->
-
-<!-- #Now with a slightly different structure (HCS) -->
-
-<!-- model.complete2.3 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ Outcome | Study.ID, struct = "HCS", method = "REML", data = restricted.data) -->
-
-<!-- summary(model.complete2.3) -->
-<!-- ``` -->
-
-<!-- ```{r, fig.height= 7, fig.width=10} -->
-<!-- #Generate predictions without taxon -->
-
-<!-- get.predictions.complete2 <- function(newdata){ -->
-<!--   B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0 -->
-<!--   if(newdata[1] == "B") B<-1  -->
-<!--   if(newdata[1] == "F") F<-1  -->
-<!--   if(newdata[2] == "Stressed") Unstressed<-1 -->
-<!--   if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1 -->
-<!--   if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1 -->
-
-<!--   predict(model.complete2.2, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2)) -->
-<!-- } -->
-<!-- # Get the predictions for each combination of moderators -->
-<!-- predictions.complete2 <- as.data.frame(expand.grid(Sex = c("M", "B", "F"), -->
-<!--                            Environment = c("Unstressed", "Stressed"))) -->
-<!-- predictions.complete2 <- cbind(predictions.complete2, do.call("rbind", apply(predictions.complete2, 1, get.predictions.complete2))) %>% -->
-<!--   select(Sex, Environment, pred, se, ci.lb, ci.ub)  -->
-<!-- for(i in 3:6) predictions.complete2[,i] <- unlist(predictions.complete2[,i]) -->
-
-<!-- #And plot the results -->
-
-<!-- pd <- position_dodgev(height = .3) -->
-<!-- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) +  -->
-<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
-<!--   geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, xmax = predictions.complete2$ci.ub), height = 0, position = pd) + -->
-<!--   geom_point(position = pd) +  -->
-<!--   ylab("Environment")+ -->
-<!--   xlab("Effect Size (Hedges g)")+ -->
-<!--   xlim(-.75, .75)+ -->
-<!--   ggtitle('Effects of Sex, Stress \non Population Fitness (OUTCOME = INNER FACTOR)') -->
-<!-- ``` -->
 
@@
 #for lnCVR
-prelim.data2$lnCVr <- Calc.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high)
+restricted.data$lnCVr <- Calc.lnCVR(restricted.data$mean.low, restricted.data$sd.low, restricted.data$n.low, restricted.data$mean.high, restricted.data$sd.high, restricted.data$n.high)
 
 #for variance in lnCVR
-prelim.data2$var.lnCVr <- Calc.var.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high, Equal.E.C.Corr=F)
-
-prelim.data2 <- prelim.data2 %>% drop_na(lnCVr)
-```
-
-<!-- #Run simple models subsetted for each environment/sex (this is perhaps a clunky way so we also use predictions shown below) -->
-
-<!-- # For stressed environment and females -->
-<!-- varSF <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "F")) -->
-
-<!-- # For stressed environment and females -->
-<!-- varSM <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "M")) -->
-
-<!-- # For stressed environment and females -->
-<!-- varSB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "B")) -->
-
-<!-- #For Benign environment and females -->
-<!-- varUF<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "F")) -->
-
-<!-- #For Benign environment and males -->
-<!-- varUM<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "M")) -->
-
-<!-- #For Benign environment and both -->
-<!-- varUB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "B")) -->
-
-<!-- #Create dataframe of estimates and confidence intervals -->
-<!-- lnCVR <- c(varSF$b, varSM$b, varSB$b, varUF$b, varUM$b, varUB$b) -->
-<!-- l.ci <- c(varSF$ci.lb, varSM$ci.lb, varSB$ci.lb, varUF$ci.lb, varUM$ci.lb, varUB$ci.lb) -->
-<!-- u.ci <- c(varSF$ci.ub, varSM$ci.ub, varSB$ci.ub, varUF$ci.ub, varUM$ci.ub, varUB$ci.ub) -->
-<!-- Environment <- c("Stressed", "Stressed", "Stressed", "Unstressed", "Unstressed", "Unstressed") -->
-<!-- Sex <- c("Female", "Male", "Both", "Female", "Male", "Both") -->
-<!-- k <- c(varSF$k, varSM$k, varSB$k, varUF$k, varUM$k, varUB$k) -->
-
-<!-- var.data <- data.frame(lnCVR, l.ci, u.ci, Environment, Sex, k) -->
-
-<!-- #Releveling the factors to make sure it aligns with other formatted graphs -->
-<!-- var.data$Environment <- var.data$Environment %>% factor %>% relevel(ref="Unstressed") -->
-<!-- var.data$Sex <- var.data$Sex %>% factor %>% relevel(ref="Male") -->
-
-<!-- #Plot subseted model estimates -->
-
-<!-- var.data %>% ggplot(aes(x=lnCVR, y = Environment, colour = Sex))+ -->
-<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + -->
-<!--   geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, position = pd) + -->
-<!--   geom_point(position = pd) + -->
-<!--   ylab("Environment")+ -->
-<!--   xlab("lnCVR")+ -->
-<!--   xlim(-.75, .75)+ -->
-<!--   ggtitle('Meta-Analysis of Variance (Using Subsetting)') -->
+restricted.data$var.lnCVr <- Calc.var.lnCVR(restricted.data$mean.low, restricted.data$sd.low, restricted.data$n.low, restricted.data$mean.high, restricted.data$sd.high, restricted.data$n.high, Equal.E.C.Corr=F)
+
+restricted.data <- restricted.data %>% drop_na(lnCVr)
+```
 
@@
 This can be done be utilising the same predict function but for lnCVR and var.lnCVR.
+For the brms model we can obtain predictions manually or through the ``fitted.brmsfit``.
 
@@
                                        ~ 1 | Outcome), 
-                         method = "REML", data = prelim.data2)
+                         method = "REML", data = restricted.data)
 summary(variance.model)
+
+#Now with brms
+
+#Use brm to create a model similar to the one used in the REML approach. 
+variance.brms <- brm(lnCVr| se((SE.v), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (SE), sex, environment and their interaction are moderators
+                + (1|Study.ID) #group level effect #1
+                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
+                family = "gaussian", #default
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                data = restricted.data %>% mutate(SE.v = sqrt(var.lnCVr)))
+
+summary(variance.brms)
+
+post.variance <- (posterior_samples(variance.brms, 
+                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
+                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
+                                    "b_SexF:EnvironmentStressed")) %>%
+         mutate(both_benign = b_Intercept + b_SexB,
+         both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed`,
+         male_benign = b_Intercept,
+         male_stressful = b_Intercept + b_EnvironmentStressed,
+         female_benign = b_Intercept + b_SexF,
+         female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed`))[,-(1:6)]
+
+#Add columns for Environment and Sex
+post.variance <- as.data.frame(t(post.variance))
+post.variance$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
+post.variance$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")
+
+#Clean up dataframe
+post.variance <- melt(post.variance, id = c("Sex", "Environment"))
+post.variance$variable <- NULL
 ```
@@
 
-```{r, fig.height= 6, fig.width=6, warning = FALSE}
+```{r, fig.height= 5.5, fig.width=5.5, warning = FALSE}
 
@@
 get.predictions.variance <- function(newdata){
-  F<-0; M<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
+  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
+  if(newdata[1] == "B") B<-1 
   if(newdata[1] == "F") F<-1 
-  if(newdata[1] == "M") M<-1 
   if(newdata[2] == "Stressed") Stressed<-1
-  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction1<-1
-  if(newdata[1] == "M" & newdata[2] == "Stressed") interaction2<-1
-
-  predict(variance.model, newmods=c(F, M, Stressed, interaction1=interaction1, interaction2=interaction2))
+  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
+  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1
+
+  predict(variance.model, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
 }
@@
 
-#And plot the results
-
-var.plot <- predictions.variance %>% 
+#Change names to make them more clear
+predictions.variance <- predictions.variance %>% 
       mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
@@
          Sex = replace(Sex, Sex == "F", "Female")) %>%
-  ggplot(aes(x = pred, y= reorder(Environment, -pred), fill = Sex)) + 
+  mutate(Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
+         Environment = replace(Environment, Environment == "Unstressed", "Benign"))
+
+colnames(predictions.variance) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
+
+#And plot the results, first for the posterior results of the brms model then for the metafor predictions
+
+var.plot.posterior <- post.variance %>% ggplot()+
+  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
   geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
-  geom_errorbarh(aes(xmin = predictions.variance$ci.lb, 
-                     xmax = predictions.variance$ci.ub,
-                     color = Sex), 
-                 height = 0, position = pd, show.legend = F) +
-  geom_point(aes(size = nn), position = pd, shape = 21, color= "grey20") + 
-  scale_size(guide = 'none')+
   ylab("Environment\n")+
@@
   scale_color_brewer(palette = "Set1")+
-  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
 
@@
 
-  theme(panel.spacing = unit(0.5, "lines"),
-        text = element_text(size=14),
+  theme(panel.spacing = unit(0.1, "lines"),
+        text = element_text(size=16),
         panel.border= element_blank(),
@@
         panel.grid.minor.x = element_blank(), 
-        legend.text = element_text(size=14), 
-        legend.title=element_text(size=14, 
+        legend.text = element_text(size=16), 
+        legend.title=element_text(size=16, 
                                   face = "bold"),
         axis.title.x = element_text(hjust = 0.5, size = 14),
-        axis.title.y = element_text(size = 14),
-        axis.text.y = element_text(angle = 90))
-
-ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 4, width = 8)
-var.plot
-
-# svg("figures/Variance_plot.svg", width=6, height=6)
+        axis.title.y = element_text(size = 16, hjust = 0.35, margin = margin(r=-10)),
+        axis.text.y = element_text(angle = 0),
+        plot.title = element_text(size = 16))
+
+both.var.plots <- var.plot.posterior +
+  geom_point(data = predictions.variance, 
+             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
+             shape=21, color = "grey20", position = pd) +
+  guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
+  scale_size(guide = 'none')+
+
+  geom_errorbarh(data = predictions.variance, 
+                 aes(x = Prediction, xmin = predictions.variance$CI.lb, 
+                     xmax = predictions.variance$CI.ub, y = Environment,
+                     color = Sex), 
+                 height = 0, position = pd, show.legend = F) +
+  scale_y_discrete(expand=c(0.075,0))
+
+# ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 4, width = 8)
 # var.plot
+
+both.var.plots
+# svg("figures/both.var.plots.svg", width=6, height=6)
+# both.var.plots
+# dev.off()
+
+# pdf("figures/both.var.plots.pdf",  width = 5.5, height = 5.5)
+# both.var.plots
 # dev.off()
@@
 ```{r}
-colnames(predictions.variance) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
 predictions.variance <- format(predictions.variance, digits = 2)
@@
 ```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
-generations.plot.var <- prelim.data2 %>% ggplot(aes(x=Generations, y=lnCVr))+
+generations.plot.var <- restricted.data %>% ggplot(aes(x=Generations, y=lnCVr))+
   geom_point(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
@@
 ```{r}
-summary(lm(lnCVr ~ Generations, data = prelim.data2))
+summary(lm(lnCVr ~ Generations, data = restricted.data))
 ```

### 2018-06-06 meta_analysis_sexual_selection_pop_fitness.Rmd
6/6 Update

@@
 library(lme4)
+library(car)
 library(forestplot)
@@
 library(ggridges)
-library(rstan) #Note that installation requires some effort
+library(rstan) #Note that installation requires some effort: dependency for brms
 library(brms) 
@@
 source("Vdodge_function.R") # nice function for ggplot
-```
-
-```{r echo=FALSE, results='hide'}
+source("Tidy_functions_for_brms.R") #Tidy functions for making model tables for brms
+```
+
+```{r echo=FALSE, results='hide', warning=FALSE}
 library(knitr) # set up cacheing to save time when re-building the html document
@@
 Several impact factors were unable to be determined/found and are NA.We obtained the journal impact factor for each effect size at the time of publication using InCites Journal Citation Reports.
-<br></br>
+
+_________
 
@@
 ```
-<br></br>
+
+____________
 
@@
 ```{r, fig.height=18, fig.width=12}
-
 # Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
@@
          Sex = replace(Sex, Sex == "M", "Male"),
-         Sex = replace(Sex, Sex == "F", "Female")) %>%
+         Sex = replace(Sex, Sex == "F", "Female"),
+         Outcome.Class = factor(Outcome.Class, levels = c("Ambiguous", "Indirect", "Direct"))) %>%
 
@@
 
-  scale_color_brewer(name = "Relationship\nto fitness", 
-                    palette = "Set1", 
-                    breaks=c("Ambiguous","Indirect","Direct"))+
+  scale_color_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
+                    name = "Relationship\nto fitness")+
 
@@
 
-  scale_fill_brewer(name = "Relationship\nto fitness", 
-                    palette = "Set1", 
-                    breaks=c("Ambiguous","Indirect","Direct"))+
+  scale_fill_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
+                    name = "Relationship\nto fitness")+
 
@@
 
-  guides(fill = guide_legend(override.aes = list(shape = 21, colour = "grey20")))+
+  guides(fill = guide_legend(override.aes = list(shape = 21, colour = "grey20", size = 6)),
+         shape = guide_legend(override.aes = list(size = 4.5)))+
 
@@
 
-ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 18, width = 12)
 p.meta
+
+### We can save the file in several vector graphics forms
+
+#ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 18, width = 12)
 
@@
 # dev.off()
+# 
+# pdf("figures/Big_forest_plot.pdf", width=12, height=18)
+# p.meta
+# dev.off()
 ```
@@
 
+___________
+
 ###Meta-analysis of individual outcomes
@@
 
-**Table S6** Summary of individual model results, including _I^2^_, for all outcomes with n>3 (fix this).
-
+**Table S6** Summary of individual model results, including _I^2^_, for all outcomes with n>3. 
+<input type=button class=hideshow></input>
 ```{r, warning = FALSE}
@@
 simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))
-# simple.frame$vi <- as.matrix(simple.frame$vi)
-# simple.frame$W <- diag(1/(simple.frame$vi))
-# 
-# XO <- model.matrix(model.complete2)
-# PO <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-# 100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
-
-#I couldn't get mapply to work when calculating I2 so I calculated them manually.
+
+#There is no simple way to get I2 for multilevel models in metafor, so we can obtain them manually for each outcome
 
@@
 
-outcome.frame %>% pander(split.cell = 40, split.table = Inf)
-
-#Can't get the llply or mapply to work on the list of outcomes
-
-# I2df <- llply(outcome.models, function(x) {
-#   prelim.data %>% filter(prelim.data$Outcome == outcome.list)
-# })
-#   #Run estimate of heterogeneity
-# Wlist <- llply(outcome.list, function(x) {diag(1/I2df[[x]]$var.g)}) #X
-# 
-# Xlist <- llply(outcome.list, function(x) {model.matrix(outcome.models[[x]])}) #Y
-# 
-# Pfunc <- Map(function(X,Y,Z) {
-#   X[[Z]] - X[[Z]] %*% Y[[Z]] %*% solve(t(Y[[Z]]) %*% X[[Z]] %*% Y[[Z]]) %*% t(Y[[Z]]) %*% X[[Z]]},
-#   X=Wlist, Y=Xlist, Z=1:19)
-# 
-# llply()
-# 
-# I2list <- llply(outcome.list, function(x) {100 * sum(outcome.models[[x]]$sigma2) / (sum(outcome.models[[x]]$sigma2) + (outcome.models[[x]]$k-outcome.models[[x]]$p)/sum(diag(Wlist - Wlist %*% Xlist %*% solve(t(Xlist) %*% Wlist %*% Xlist) %*% t(Xlist) %*% x)))})
-# 
-# matrix(outcome.list)
-```
-
-___________________
+#Only present subset model results for outcomes with 4 or more effect sizes
+
+outcome.frame %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)
+```
+
+______________
 
@@
 
-summary(model.preliminary)
-
+summary(model.preliminary, digits = 2)
+
+```
+<br></br>
+
+Here we can also run a bayesian model alongside the restricted maximum likelihood model (metafor)
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
 #Also use bayesian model
-
-brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding 
-                + (1|Study.ID) #group level effect #1
+brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
+                + (1|Study.ID) #group level effects
                 + (1|Outcome)
@@
 
+```
+<br></br>
+
+```{r}
 #Plot model results
 prelim.results.bayesplot <- bayesplot::mcmc_areas(posterior_samples(brms.preliminary)[,1:11]) + 
-  geom_vline(xintercept = 0, linetype = 2)
+  geom_vline(xintercept = 0, linetype = 2) +
+
+  theme_bw()+
+
+  theme(panel.spacing = unit(0.1, "lines"),
+        text = element_text(size=16),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=16), 
+        legend.title=element_text(size=16, 
+                                  face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+        axis.title.y = element_text(size = 16, hjust = 0.35, margin = margin(r=-10)),
+        axis.text.y = element_text(angle = 0),
+        plot.title = element_text(size = 16))
 
@@
 
-```
-<br></br>
-
-From this model we can see that there are several redundant moderators: Blinding, Generations and the Outcome class (direct, indirect and ambiguous) show little effect and are not key to our research question (like sex and environment are).
-However, because taxa is a likely source of heterogeneity and effect size could reasonably be expected to differ between taxa, we investigate this fixed effect further...
-
-__________________________________
+make_text_summary(brms.preliminary) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
+```
+**Figure S2 & Table S7:** Bayesian model results for a preliminary model that explores many covariates collected in the dataset.
+
+From these models we can see that there are several redundant moderators: Blinding and Generations show little effect and are not key to our research question (like sex and environment are).
+However, because taxa is a likely source of heterogeneity and effect size could reasonably be expected to differ between taxa, we investigate taxa as a fixed effect.
+
+____________________
 
@@
 First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding).
-In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.
+In this model we use Sex, Environment, Taxon and the interaction between sex and environment.
 
 <input type=button class=hideshow></input>
-```{r, warning=FALSE}
+```{r, results='hide', message=FALSE, error = FALSE, warning=FALSE}
 #Restrict the dataset for unambiguous outcomes and environments 
@@
 
-model.complete <- rma.mv(g, var.g, 
+model.complete <- rma.mv(g, V = var.g, 
                          mods = ~ 1 + Sex * Environment + Taxon, # << ----- Add big model, then cull predictors to this one
@@
 
-summary(model.complete)
-
-#Have taxon as fixed effects
-brms.complete <- brm(g | se(SE)  ~ 1 + Sex * Environment + Taxon
-                + (1|Study.ID) #group level effect #1
-                + (1|Outcome), #group level effect #2 
-                family = "gaussian", 
-                seed = 1,
-                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
-                control = list(adapt_delta = 0.999, max_treedepth = 15),
-                data = restricted.data %>% mutate(SE = sqrt(var.g)))
-
-bayesplot::mcmc_areas(posterior_samples(brms.complete)[,1:13]) +
-  geom_vline(xintercept = 0, linetype = 2)
-
-# new.data <- restricted.data %>% 
-#   mutate(SE = sqrt(var.g)) %>% 
-#   select(Sex, Environment, Blinding, Generations, SE, Taxon) %>% 
-#   mutate(Generations = mean(log(Generations)), 
-#          Blinding = "Blind", 
-#          Taxon = "Fly",
-#          Outcome = "Reproductive Success",
-#          SE = 0) %>% 
-#   distinct() %>% arrange(Sex, Environment)
-# predictions.complete <- data.frame(new.data, fitted(brms.complete, newdata = new.data, re_formula = NA))
-# 
-# pd <- position_dodge(0.2)
-# predictions.complete %>% ggplot(aes(Sex, Estimate, group = Environment, colour = Environment)) + 
-#   geom_errorbar(aes(ymin = X2.5.ile, ymax = X97.5.ile), position = pd, width = 0) +
-#   geom_point(position = pd) +
-#   coord_flip()
+summary(model.complete, digits = 2)
 ```
@@
 This is done by obtaining predictions using the base ``predict()`` function for the ``rma.mv()`` objects that have been previously created
-```{r, warning=FALSE}
+```{r, warning=FALSE, fig.height= 8, fig.width=8}
 # function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
@@
 predictions.complete <- left_join(predictions.complete, countpred, by = c("Sex", "Environment", "Taxon"))
-```
-
-Thirdly, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.
-
-<!-- > I would like to know how to join a table with mean, and CI values to the forest plots I am generating. -->
-
-<!-- > You can make tables with ggplot, and bind them to graphs using the grid and gridExtra packages. It's pretty hard! See ?gridExtra::tableGrob.  -->
-<!-- > Honestly might be easier to do it manually with e.g. Inkscape or Illustrator.	 -->
-
-```{r, fig.height= 6, fig.width=8}
-pd <- position_dodgev(0.5)
+
+#Thirdly, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.
+
+pd <- position_dodgev(0.6)
 
@@
          Sex = replace(Sex, Sex == "M", "Male"),
-         Sex = replace(Sex, Sex == "F", "Female")) %>%
+         Sex = replace(Sex, Sex == "F", "Female"),
+         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
+         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
+         Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>%
   ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
@@
   ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
-  scale_fill_brewer(palette = "Set1")+
-  scale_color_brewer(palette = "Set1")+
-  guides(fill = guide_legend(reverse=T))+
+  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  guides(fill = guide_legend(reverse=T, override.aes = list(size = 4.5)))+
+
     theme_bw()+
@@
 
-ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 6, width = 8)
+#ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.svg", height = 8, width = 8)
 Taxon.metaanlysis
@@
 <br></br>
-**Figure S2:** The predictions from this model indicate some heterogeneity between taxon.
+**Figure S3:** The predictions from this model indicate some heterogeneity between taxon.
 However, the most apparent difference between taxa is that confidence bands increase for taxa with low sample size.
@@
 
-**Table S7** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.
+**Table S8** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.
 
@@
 
+Given that none of categories of taxa significantly impact effect size we can incorporate them as random/group level effects in later models.
+
 ____________
@@
 
-Here we ask two key questions: Does sexual selection benefit populations in stressed environments more than unstressed environments?
-**AND** Do the benefits of sexual selection accrue more for female fitness components?
-
-We run a three level model where the outcome is nested within a study (Study.ID).
-Other potential random effects include Species and Group.ID.
-However the estimate (variance from random effect) of these two other potential random effects tended towards zero and were dropped from the model.
-Additionally the model could be run with just Study.ID, but from our exploration of heterogeneity (below) we see that there is sufficient correlation (but not ICC = 1) between outcomes to include it as a random effect within the model.
-
-```{r}
-#run model without taxon: same random effects as above
-model.complete2 <- rma.mv(g, var.g, 
+Here we ask two key questions: Does sexual selection benefit populations in stressed environments more than benign environments? **AND** Do the benefits of sexual selection differ between the sexes?
+
+We can run a model where the outcome is crossed with study (Study.ID) and Taxon as random effects and environment, sex and their interactions are fized effects.
+
+```{r}
+#run model with taxon as a random effect
+model.complete2 <- rma.mv(g, V = var.g, 
                           mods = ~ 1 + Sex * Environment, 
                           random = list(~ 1 | Study.ID, 
-                                       ~ 1 | Outcome), 
+                                       ~ 1 | Outcome,
+                                       ~ 1 | Taxon), 
                           method = "REML", 
                           data = restricted.data)
-summary(model.complete2)
-```
-<br></br>
-
-Now plot the model predictions using a similar function to the one used in the above section with taxon.
-
-```{r, fig.height= 6, fig.width=6}
-
-#Generate predictions without taxon utilising the previously described function
-
-get.predictions.complete2 <- function(newdata){
-  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
-  if(newdata[1] == "B") B<-1 
-  if(newdata[1] == "F") F<-1 
-  if(newdata[2] == "Stressed") Stressed<-1
-  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
-  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1
-
-  predict(model.complete2, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
-}
-# Get the predictions for each combination of moderators
-predictions.complete2 <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
-                           Environment = c("Unstressed", "Stressed")))
-predictions.complete2 <- cbind(predictions.complete2, do.call("rbind", apply(predictions.complete2, 1, get.predictions.complete2))) %>%
-  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
-for(i in 3:6) predictions.complete2[,i] <- unlist(predictions.complete2[,i])
-
-countpred <- count_(restricted.data, c("Sex", "Environment"))
-
-predictions.complete2 <- left_join(predictions.complete2, countpred, by = c("Sex", "Environment"))
-
-#And plot the results
-pd <- position_dodgev(height = 0.65)
-predictions.complete2 <- predictions.complete2 %>% 
-      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
-         Sex = replace(Sex, Sex == "M", "Male"),
-         Sex = replace(Sex, Sex == "F", "Female")) %>%
-  mutate(Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
-         Environment = replace(Environment, Environment == "Unstressed", "Benign"))
- EnvSex.metaanalysis <- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
-  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
-  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, 
-                     xmax = predictions.complete2$ci.ub,
-                     color = Sex), height = 0, position = pd, show.legend = F) +
-  geom_point(aes(size=nn), position = pd, shape=21, color = "grey20") + 
-  scale_size(guide = 'none')+
-  ylab("Environment\n")+
-  xlab("\nEffect Size (Hedges' g)")+
-  scale_fill_brewer(palette = "Set1")+
-  scale_color_brewer(palette = "Set1")+
-  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
-  scale_x_continuous(limits = c(-0.2, 1), breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1))+
-
-  theme_bw()+
-
-  theme(panel.spacing = unit(0.5, "lines"),
-        text = element_text(size=14),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
-        panel.grid.major.x = element_blank(),
-        panel.grid.major.y = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(), 
-        legend.text = element_text(size=14), 
-        legend.title=element_text(size=14, 
-                                  face = "bold"),
-        axis.title.x = element_text(hjust = 0.5, size = 14),
-        axis.title.y = element_text(size = 14),
-        axis.text.y = element_text(angle = 90),
-        plot.title = element_text(size = 14))
-
-ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 6, width = 6)
-EnvSex.metaanalysis
-
-# svg("figures/fEnvironment_Sex_metaanalysis_plot.svg", width=6, height=6)
-# EnvSex.metaanalysis
-# dev.off()
-```
-<br></br>
-**Figure S3:** Sexual selection generally increases population fitness, especially for females under stressed conditions.
-The benefits of sexual selection on fitness for females under stressed conditions are small-medium according to Cohen's interperetation of effect sizes.
-Circle size is proportional to sample size.
-
-**Table S8** The predictions in the plot above use the following dataframe
-```{r}
-colnames(predictions.complete2) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
-predictions.complete2 <- format(predictions.complete2, digits = 2)
-predictions.complete2$Prediction = as.numeric(predictions.complete2$Prediction)
-predictions.complete2$CI.lb = as.numeric(predictions.complete2$CI.lb)
-predictions.complete2$CI.ub = as.numeric(predictions.complete2$CI.ub)
-predictions.complete2$n = as.numeric(predictions.complete2$n)
-
-predictions.complete2 %>% pander()
-```
-
-We see that female fitness in stressed environments is greater than the other measurements.
-For outcomes that were measured for both female and males we see a greater uncertainty in the estimate.
-It is not obviously clear why this is.
-The 'both' outcomes are restricted to extinction rate, offspring viability, mutant frequency and reproductive success.
-However, the shift from 'both' being not significant in unstressed to significant in stressed may reflect the dampening of the negative correlations (sexual antagonism).
-
-**Comparisons of Stress vs Unstresss through anovas**
-
-Using an anova we can test to see if a female in a stressed environment gains significantly greater fitness benefits than in an unstressed environment:
-
-```{r}
-anova(model.complete2, L=c(0, 0, 0, 1, 0, -1)) 
-```
-
-Both (unstressed vs stressed)
-```{r}
-anova(model.complete2, L=c(0, 1, 0, -1, 0, 0)) 
-```
-
-From these anovas we see that a stressed environment leads to a significantly greater increase in fitness components for "female"" but NOT "both" sexes.
-
-We can also test if there is a difference between males and females in unstressed conditions:
+summary(model.complete2, digits = 2)
+```
+
+______________
+
+####Comparisons of environment and Sex Conditions REML model through anovas
+
+**Table S9** Using the ``anova.rma`` function we can conduct hypothesis tests between two categorical groups in the model.
+Here we conduct 5 tests testing relative effects of sexual selection between the sexes and in different environments.
 
@@
 #anova where you specify the values based on the list of moderators
-anova(model.complete2, L=c(1, 0, -1, 0, 0, 0)) 
-```
-
-Or both in stressed vs unstressed:
-
-```{r}
-anova(model.complete2, L=c(0, 1, 0, 0, -1, 0)) 
-```
-
-Or males in stressed vs unstressed:
-
-```{r}
-anova(model.complete2, L=c(1, 0, 0, -1, 0, 0)) 
-```
-__________________________________
-
-###Bayesian models using _brms_ package
-
-We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above.
-
-```{r, warning = FALSE, results='hide', message=FALSE}
-#Use brm to create a model similar to the one used in the REML approach. 
-meta.brms <- brm(g| se((SE), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (SE), sex, environment and their interaction are moderators
-                + (1|Study.ID) #group level effect #1
-                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
-                family = "gaussian", #default
+anova.1 = anova(model.complete2, L=c(1, 0, -1, 0, 0, 0)) 
+anova.2 = anova(model.complete2, L=c(0, 0, 0, 1, 0, -1))
+anova.3 = anova(model.complete2, L=c(0, 0, 1, 0, 0, -1))
+anova.4 = anova(model.complete2, L=c(1, 0, 0, -1, 0, 0))
+anova.5 = anova(model.complete2, L=c(0, 1, 0, 0, -1, 0))
+
+anova.list <- list(anova.1, anova.2, anova.3, anova.4, anova.5)
+
+anova.frame <- t(data.frame(lapply(anova.list, function(x) {
+  data.frame(x[["hyp"]],
+  x[["Lb"]],
+  x[["se"]],
+  x[["Lb"]] - 1.96*x[["se"]],
+  x[["Lb"]] + 1.96*x[["se"]],
+  x[["pval"]])
+})))
+anova.frame <- as.data.frame(split(anova.frame, rep(1:6)))
+colnames(anova.frame) <- c("Hypothesis", "Estimate", "Est.Error", "CI.Lower", "CI.Upper", "pval")
+anova.frame$Estimate <- as.numeric(levels(anova.frame$Estimate))[anova.frame$Estimate]
+anova.frame$Est.Error <- as.numeric(levels(anova.frame$Est.Error))[anova.frame$Est.Error]
+anova.frame$CI.Lower <- as.numeric(levels(anova.frame$CI.Lower))[anova.frame$CI.Lower]
+anova.frame$CI.Upper <- as.numeric(levels(anova.frame$CI.Upper))[anova.frame$CI.Upper]
+anova.frame$pval <- as.numeric(levels(anova.frame$pval))[anova.frame$pval]
+anova.frame <- format(anova.frame, digits = 2)
+anova.frame$star <- c("", "*", "*", "*", "")
+colnames(anova.frame)[colnames(anova.frame)=="star"] <- " "
+anova.frame$pval <- NULL
+anova.frame %>% pander(split.table = Inf)
+```
+<br></br>
+From these anovas we see that a stressful environment leads to a significantly greater increase in fitness components for "female"" but NOT "both" sexes, while significantly decreasing male fitness.
+We can also test if there is a difference between males and females in stressful but not benign conditions.
+
+______________
+
+###Bayesian model on the effects of environment and sex
+
+We can run a bayesian model using the brms package.
+The model has the same moderators as the REML approach used above.
+The ``brms`` package sets standard priors that are selected to be 'weakly informative'.
+The _R^2^_ of this Bayesian model was 0.35 (95% CIs = 0.31-0.39).
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+#Use brms to create a model similar to the one used in the REML approach. 
+brms.complete2 <- brm(g | se(SE)  ~ 1 + Sex * Environment #se(SE, sigma = TRUE) gives differnt results
+                + (1|Taxon) #group level effect #1
+                + (1|Study.ID) #group level effect #2
+                + (1|Outcome), #group level effect #3 
+                family = "gaussian", 
                 seed = 1,
-                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
-                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.9999, max_treedepth = 15),
                 data = restricted.data %>% mutate(SE = sqrt(var.g)))
 
-summary(meta.brms)
-
-#You can obtain a posterior sampling through the ``fitted.brmsfit`` function, which gives the same posterior values as doing it manually (see below).**Note that the fitted values obtained here have much smaller error than the predict values, which blow out**
+```
+<br></br>
+We can then get the distribution of posterior fitted values and examine the model summary
+
+**Table S10** Model estimate summary table for the Bayesian model investigating the effect of environment and sex (alongside sexual selection) on fitness. 
+```{r}
+#You can obtain a posterior sampling through the ``fitted.brmsfit`` function, which gives the same posterior values as doing it manually (see below).**Note that the fitted values obtained here have much smaller error than the predict values**
 
@@
 # #Name columns
-# colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI", "n")
-```
-
-Let's get the distribution of posterior fitted values and plot with ggridges
-
-```{r}
-post <- (posterior_samples(meta.brms, 
+# colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI")
+
+post <- (posterior_samples(brms.complete2, 
                            pars = c("b_Intercept", "b_SexB", "b_SexF", 
@@
 post$variable <- NULL
-```
-
-```{r, fig.height=5.5, fig.width=5.5}
+
+make_text_summary(brms.complete2) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
+```
+<br></br>
+Like with the REML approach, from these model results we can test several hypotheses between the categories of environment and sex.
+For instance, the first hypothesis in the table below tests whether there is a difference between male and female fitness increase under sexual selection in benign conditions.
+With the answer stating that they largely overlap in their predictions and are the same, to 95 % confidence.
+
+**Table S11** Hypothesis tests for the Bayesian model are similar to the REML model (Table S9), with slight differences to CIs.
+```{r}
+#Obtain hypothesis estimates
+brms.hypothesis <- hypothesis(brms.complete2, c("Intercept = SexF",
+                             "EnvironmentStressed = SexF:EnvironmentStressed",
+                             "SexF = SexF:EnvironmentStressed",
+                             "Intercept = EnvironmentStressed",
+                             "SexB = SexB:EnvironmentStressed"))
+#Format into dataframe
+brms.hypothesis.table <- 
+  data.frame(brms.hypothesis[["hypothesis"]][["Hypothesis"]],
+             brms.hypothesis[["hypothesis"]][["Estimate"]],
+             brms.hypothesis[["hypothesis"]][["Est.Error"]],
+             brms.hypothesis[["hypothesis"]][["CI.Lower"]],
+             brms.hypothesis[["hypothesis"]][["CI.Upper"]],
+             brms.hypothesis[["hypothesis"]][["Star"]])
+colnames(brms.hypothesis.table) <- c("Hypothesis", "Estimate", "Est.Error", "CI.Lower", "CI.Upper", " ")
+brms.hypothesis.table <- format(brms.hypothesis.table, digits = 2)
+brms.hypothesis.table %>% pander(split.table = Inf)
+```
+<br></br>
+Using predictions from both REML and Bayesian models we can obtain a figure that plots the mean/median predictions as well as distribution density (Bayesian) and 95 % CI (REML).
+
+```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE, error = FALSE}
+#Generate predictions without taxon utilising the previously described function
+
+get.predictions.complete2 <- function(newdata){
+  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
+  if(newdata[1] == "B") B<-1 
+  if(newdata[1] == "F") F<-1 
+  if(newdata[2] == "Stressed") Stressed<-1
+  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
+  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1
+
+  predict(model.complete2, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
+}
+# Get the predictions for each combination of moderators
+predictions.complete2 <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
+                           Environment = c("Unstressed", "Stressed")))
+predictions.complete2 <- cbind(predictions.complete2, do.call("rbind", apply(predictions.complete2, 1, get.predictions.complete2))) %>%
+  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
+for(i in 3:6) predictions.complete2[,i] <- unlist(predictions.complete2[,i])
+
+countpred <- count_(restricted.data, c("Sex", "Environment"))
+
+predictions.complete2 <- left_join(predictions.complete2, countpred, by = c("Sex", "Environment"))
+colnames(predictions.complete2) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
+predictions.complete2 <- predictions.complete2 %>%
+      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female"),
+         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
+         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
+         Sex = factor(Sex, levels = c("Male", "Both", "Female")))
 
 pd <- position_dodgev(height = 0.3)
-posterior.plot <- post %>% ggplot()+
-  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
+posterior.plot <- post %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
+  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
   geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
@@
   xlab("\nEffect Size (Hedges' g)")+
-  scale_fill_brewer(palette = "Set1")+
-  scale_color_brewer(palette = "Set1")+
-  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+
+  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_x_continuous(limits = c(-0.75, 1.5), breaks = c(-1, -.5, 0, 0.5, 1, 1.5))+
 
@@
 both.plots <- posterior.plot + 
-  geom_point(data = predictions.complete2, 
-             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
-             shape=21, color = "grey20", position = pd) +
-
-    guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
-    scale_size(guide = 'none')+
-
-  geom_errorbarh(data = predictions.complete2, 
+  geom_errorbarh(data = predictions.complete2 %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
                  aes(x= Prediction, xmin = predictions.complete2$CI.lb,
@@
                  height = 0, show.legend = F, position = pd)+
+
+  geom_point(data = predictions.complete2 %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
+             shape=21, color = "grey20", position = pd) +
+
+    guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
+    scale_size(guide = 'none')+
+
     scale_y_discrete(expand=c(0.075,0))
@@
 # dev.off()
-# 
-# pdf("figures/both_plot.pdf",  width = 5.5, height = 5.5)
+# #
+# pdf("figures/both_plot.pdf",  width = 6, height = 6)
 # both.plots
@@
 <br></br>
-**Figure X** Posterior fitted values for Hedges' g alongside the predictions from metafor
-
-__________________________________
+**Figure S3:** Sexual selection generally increases population fitness, especially for females under stressful conditions.
+The benefits of sexual selection on fitness for females under stressful conditions are small-medium according to Cohen's interperetation of effect sizes.
+Circle size is proportional to sample size (shown below).
+
+**Table S12** The predictions in the plot above use the following dataframe
+```{r}
+predictions.complete2 <- format(predictions.complete2, digits = 2)
+predictions.complete2$Prediction = as.numeric(predictions.complete2$Prediction)
+predictions.complete2$CI.lb = as.numeric(predictions.complete2$CI.lb)
+predictions.complete2$CI.ub = as.numeric(predictions.complete2$CI.ub)
+predictions.complete2$n = as.numeric(predictions.complete2$n)
+
+predictions.complete2 %>% pander()
+```
+
+____________________
+
 ###Estimating Heterogeneity Using _I^2^_
@@
 We would assume that if selection is occuring not only would the trait mean shift in a certain direction but the variance associated with those changes to the mean would also decrease.
-In this case we use an effect size statistic known as the natural log of the coefficient of variation ratio (lnCVR)
-
-**Firstly**, we setup our calculation by creating a a restricted dataset with only unabmiguous fitness outcomes and running the functions developed by Nakagawa et al. 2015:
-
-```{r}
-#Setup restricted data
-prelim.data2 <- (prelim.data %>% filter(Outcome.Class != "Ambiguous",  Environment != "Not Stated"))
-
-#Run function for lnCVR and associated variance of lnCVR
-
-#for lnCVR
-
+In this case we use an effect size statistic known as the natural log of the coefficient of variation ratio (lnCVR).
+
+```{r}
+# Firstly, we setup our calculation by creating a a restricted dataset with only unabmiguous fitness outcomes and running the functions developed by Nakagawa et al. 2015: 
 Calc.lnCVR<-function(CMean, CSD, CN, EMean, ESD, EN){
@@
 
-```
-
-**Secondly**, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes.
+# Secondly, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes.
 Noting that not all of the dataset has means, SD and n; some were calculated from summary statistics and are not able to have lnCVR calculated:
 
-```{r}
 #Calculate lnCVr and var.lnCVr
@@
 #for variance in lnCVR
-restricted.data$var.lnCVr <- Calc.var.lnCVR(restricted.data$mean.low, restricted.data$sd.low, restricted.data$n.low, restricted.data$mean.high, restricted.data$sd.high, restricted.data$n.high, Equal.E.C.Corr=F)
-
-restricted.data <- restricted.data %>% drop_na(lnCVr)
-```
-
-**Thirdly**, although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously, that way we retain the same methodology in model structure and test the same hypotheses.
+restricted.data$var.lnCVr <- Calc.var.lnCVR(restricted.data$mean.low, restricted.data$sd.low, restricted.data$n.low, restricted.data$mean.high, restricted.data$sd.high, restricted.data$n.high, Equal.E.C.Corr=T) #Equal.E.C.Corr = T assumes that the correlaiton between mean and sd (Taylor's Law) is equal for the mean and control groups
+
+restricted.data2 <- restricted.data 
+```
+
+Although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously, that way we retain the same methodology in model structure and test the same hypotheses.
 This can be done be utilising the same predict function but for lnCVR and var.lnCVR.
@@
 
-Multilevel-model using lnCVR:
+Multilevel-model using lnCVR and REML:
 
@@
 #Now try with multilevel model 
-variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex*Environment, 
-                          random = list(~ 1 | Study.ID, 
+variance.model <- rma.mv(lnCVr, V = var.lnCVr, mods = ~ 1 + Sex*Environment, 
+                          random = list(~ 1 | Taxon,
+                                        ~ 1 | Study.ID,
                                         ~ 1 | Outcome), 
-                         method = "REML", data = restricted.data)
-summary(variance.model)
-
-#Now with brms
-
+                         method = "REML", data = restricted.data2)
+summary(variance.model, digits = 2)
+```
+
+Again, we use ``brms`` to obtain Bayesian model estimates. For this model the _R^2^_ is 0.34 (95% CIs = 0.32-0.36).
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
+#When knitting this markdown this model stalls
 #Use brm to create a model similar to the one used in the REML approach. 
-variance.brms <- brm(lnCVr| se((SE.v), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (SE), sex, environment and their interaction are moderators
-                + (1|Study.ID) #group level effect #1
-                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
+variance.brms <- brm(lnCVr| se(SE.v)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (SE), sex, environment and their interaction are moderators
+                + (1|Taxon) #group level effects
+                + (1|Study.ID)
+                + (1|Outcome),
                 family = "gaussian", #default
@@
                 control = list(adapt_delta = 0.999, max_treedepth = 15),
-                data = restricted.data %>% mutate(SE.v = sqrt(var.lnCVr)))
-
-summary(variance.brms)
-
-post.variance <- (posterior_samples(variance.brms, 
+                data = restricted.data2 %>% mutate(SE.v = sqrt(var.lnCVr)))
+```
+
+**Table S13** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
+```{r}
+var.brms <- readRDS(file = "data/variance.brms.rds") #Avoid re-running model above
+post.variance <- (posterior_samples(var.brms, 
                            pars = c("b_Intercept", "b_SexB", "b_SexF", 
@@
 post.variance$variable <- NULL
-```
-<br></br>
-**Fourthly**, we can plot predictions of lnCVR for various moderators:
-
-```{r, fig.height= 5.5, fig.width=5.5, warning = FALSE}
+
+make_text_summary(var.brms) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
+```
+<br></br>
+Predictions based on the REML and Bayesian model can then be generated in the same way as for Hedges'g.
+Here, lower values of lnCVR indicate a narrowing (decrease) in phenotypic variance as a result of sexual selection.
+
+```{r, fig.height=6, fig.width=6, warning =FALSE, message=FALSE, error = FALSE}
 
@@
 
-countpred = count_(prelim.data2, c("Sex", "Environment"))
+countpred = count_(restricted.data2, c("Sex", "Environment"))
 
@@
 
-var.plot.posterior <- post.variance %>% ggplot()+
-  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
+var.plot.posterior <- post.variance %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
+  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
   geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
@@
   xlab("\nPhenotypic Variance (lnCVR)")+
-  scale_x_continuous(limits = c(-1.6, 1.2), breaks = c(-1.5, -1, -0.5, 0, 0.5, 1))+
-  scale_fill_brewer(palette = "Set1")+
-  scale_color_brewer(palette = "Set1")+
+  scale_x_continuous(limits = c(-2.1, 1.2), breaks = c(-2, -1.5, -1, -0.5, 0, 0.5, 1))+
+  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
 
@@
 both.var.plots <- var.plot.posterior +
-  geom_point(data = predictions.variance, 
+  geom_errorbarh(data = predictions.variance %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+                 aes(x = Prediction, xmin = predictions.variance$CI.lb, 
+                     xmax = predictions.variance$CI.ub, y = Environment,
+                     color = Sex), 
+                 height = 0, position = pd, show.legend = F) +
+  geom_point(data = predictions.variance %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
              aes(x = Prediction, y = Environment, size=n, fill = Sex), 
@@
 
-  geom_errorbarh(data = predictions.variance, 
-                 aes(x = Prediction, xmin = predictions.variance$CI.lb, 
-                     xmax = predictions.variance$CI.ub, y = Environment,
-                     color = Sex), 
-                 height = 0, position = pd, show.legend = F) +
   scale_y_discrete(expand=c(0.075,0))
 
-# ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 4, width = 8)
-# var.plot
-
 both.var.plots
+
 # svg("figures/both.var.plots.svg", width=6, height=6)
@@
 # dev.off()
-
-# pdf("figures/both.var.plots.pdf",  width = 5.5, height = 5.5)
+# 
+# pdf("figures/both.var.plots.pdf",  width = 6, height = 6)
 # both.var.plots
@@
 
-**Table S9** The above figure is based off the following dataframe:
+**Table S14** The above figure is based off the following dataframe:
 ```{r}
@@
 
-Briefly, we can test whether the stressed female and the stressed both are different:
-
-```{r}
-anova(variance.model, L=c(0, 0, 0, 1, -1, 0))
-```
-
-____________________
+_________
+
 ##Publication Bias
@@
 This tests for asymmetry via assessing relationships between effect size and a specified predictor.
-See ``?regtest`` for more information.
 Because the Eggers test does not work for ``rma.mv`` objects we remove the random effects and run with Sex * Environment as moderators.
@@
 standard.model <- rma(g, var.g, 
-                      mods = ~ 1 + Sex * Environment, 
+                      mods = ~ Sex * Environment, 
                       data=prelim.data)
@@
 The code is pretty clunky and unlike the ``funnel.rma`` it does not use automatically plot residuals so we have to generate them independently.
-The outline taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
+The outline taken from is taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
 
@@
 ```{r, fig.height= 4, fig.width=8, warning=FALSE}
-JIFlm <- (lm(g ~ 1 + JIF, data = prelim.data))
-
-# cairo_ps("figures/JIF_Plot.eps", width=10, height=7.5)
 
@@
 
-```{r, fig.height= 7.5, fig.width=10}
+```{r, fig.height= 6, fig.width=8}
 blind.plot <- df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
@@
   scale_fill_brewer(palette = "Set2")+
-  labs(y='Effect size (Hedges g)', x= 'Blinding', size = 'Weight (%)')+
-  guides(fill=FALSE)+
+  labs(y="Effect size (Hedges' g)", x= 'Blinding', size = 'Weight (%)')+
+  guides(fill=FALSE, size = guide_legend(override.aes = list(fill = "#66c2a5")))+
   theme_bw()+
@@
 
-ggsave(plot = blind.plot, filename = "figures/blind_plot.eps", height = 7.5, width = 10)
+ggsave(plot = blind.plot, filename = "figures/blind_plot.eps", height = 6, width = 8)
 blind.plot
@@
 However, this should not be viewed as evidence against the validity of blinding as a research method.
+
+____________
 
@@
 
-```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
+```{r, fig.height= 6, fig.width=8, warning=FALSE}
 generations.plot <- df.forest.model %>% ggplot(aes(x=Generations, y=g))+
@@
   geom_smooth(method = 'lm', color='black')+
-  labs(y='Effect size (Hedges g)', x= 'Generations', size= 'Weight (%)')+
+  labs(y="Effect size (Hedges' g)", x= 'Generations', size= 'Weight (%)')+
   theme_bw()+
@@
 ```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
-generations.plot.var <- restricted.data %>% ggplot(aes(x=Generations, y=lnCVr))+
+generations.plot.var <- restricted.data2 %>% ggplot(aes(x=Generations, y=lnCVr))+
   geom_point(shape=21, color = "grey20", size=2, aes(fill=Taxon))+

### 2018-06-06 Tidy_functions_for_brms.R

@@ -1,0 +1,23 @@
+
+# Helper function for making supplementary tables of model results
+make_text_summary <- function(model){
+  posterior_samples(model) %>% 
+    select(parnames(model), -starts_with("r"), -lp__) %>%
+    as.mcmc() %>% posterior_summary() %>%
+    round(3) %>% as.data.frame()
+}
+
+# For adding stars to the tables when the 95% CIs don't overlap zero
+add_significance_stars <- function(posterior){
+  posterior$xx <- " "
+  posterior$xx[posterior[,3] < 0 & posterior[,4] < 0] <- "*"
+  posterior$xx[posterior[,3] > 0 & posterior[,4] > 0] <- "*"
+  names(posterior)[names(posterior) == "xx"] <- " "
+  posterior
+}
+
+# Get the Bayes R^2 for a model, and it's 95% CIs, and neaten them for printing
+neat.R2 <- function(model){
+  R2 <- bayes_R2(model) %>% round(2)
+  paste(R2[1,1], " (95% CIs = ", R2[1,3], "-", R2[1,4], ")", sep = "")
+}

### 2018-06-06 meta_analysis_sexual_selection_pop_fitness.Rmd
6/6 Update

@@
 ---
-title: 'Effects of sexual selection on non-sexual fitness components: a meta-analysis'
+title: 'Sexual selection improves fitness: a meta-analysis'
 author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
@@
 
-Here we show the residual effect sizes for each outcome measured.
-The following forest plot is based on the residual effect sizes.
-The model is an intercept only model with standard random effects structure.
+Here we show the raw effect sizes for each fitness component measured.
 

### 2018-06-20 meta_analysis_sexual_selection_pop_fitness.Rmd
20/6 Update

@@
 ---
-title: 'Sexual selection improves fitness: a meta-analysis'
+title: 'Sexual selection improves population fitness: a meta-analysis'
 author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
 subtitle: Supplementary Material
+bibliography: bibliography_meta_analysis.bib
 output:
@@
 library(brmstools)
+library(metaAidR)
+source("I2_function.R") #Adapted function for obtaining I2 with CIs
 source("Vdodge_function.R") # nice function for ggplot
@@
 Here we describe the process of the literature search, data extraction, effect size calculation, formulation of multilevel models and assessing publication bias.
+We used the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) as a guide during this meta-analysis.
 
@@
 
-1. We searched ISI Web of Science and Scopus on 9th June 2017. The two search engines produded a somewhat different set of papers (**PRISMA Figure**).
+1. We searched ISI Web of Science and Scopus on 9th June 2017. The two search engines produded a somewhat different set of papers (**see PRISMA Figure in manuscript**).
 
@@
 
-In addition to studies found from the literature search we also included three relevant studies that we found, which were not picked up in the subsequent formal searches (Partridge 1980; Price et al.
-2010; Savic Veselinovic et al.
-2013; **PRISMA Figure**).
+In addition to studies found from the literature search we also included three relevant studies that we found, which were not picked up in the subsequent formal searches [@Partridge_1980; @Price_2010; @Savic_2013] **see PRISMA Figure in manuscript**.
 
@@
 
-After removing duplicates papers recovered from both ISI and Scopus, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution).
+After removing duplicates papers recovered from both _Web of Science_ and _Scopus_, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution).
 This left 130 papers, for which we read the full text and applied the following selection criteria:
@@
   + **(1: Study Design)** The study was an experimental evolution study lasting >1 generation
-  + **(1: Population)** a) The study was conducted using an animal species that was b) diecious
-  + **(1: Intervention and Control)** The study experimentally manipulated the strength of sexual selection (e.g. via enforced monogamy or an altered sex ratio)
-  + **(1: Outcomes)** The study measured a trait that we judged to be a potential correlate of population fitness.
+  + **(2: Population)** a) The study was conducted using an animal species that was b) dioecious
+  + **(3: Intervention and Control)** The study experimentally manipulated the strength of sexual selection for at least one generation (e.g. via enforced monogamy or an altered sex ratio)
+  + **(4: Outcomes)** The study measured a trait that we judged to be a potential correlate of population fitness.
 
@@
   kable_styling() %>%
-  scroll_box(width = "800px", height = "500px")
+  scroll_box(width = "100%", height = "500px")
 ```
@@
   kable_styling() %>%
-  scroll_box(width = "800px", height = "250px")
+  scroll_box(width = "100%", height = "250px")
 ```
@@
 3.
-If means were not reported then we extracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package.
+If means were not reported then we extracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package [@compute_es].
 Summary statistics included _F_, _z_, _t_ and _chi^2^_.
@@
 
-**Positive Fitness**: Whether the measurment used in the study is beneficial for fitness (1) or not (0). Note that g has already been multiplied by this column.
+**Positive Fitness**: Whether the measurment used in the study is beneficial for fitness (1) or not (0).
+Note that g has already been multiplied by this column.
+We inverted all of the effect sizes pertaining to fitness outcomes that are expected to be negatively related to fitness by multiplying the effect size by -1.
 
@@
 
-### Table of sample sizes
-
-The number of effect sizes, publications, blind experiments, effect sizes in stressed conditions, male, female and both measures and different species used, with the number of effect sizes per taxon also reported.
+### Tables of Sample Sizes
+
+Here we present the number of effect sizes, publications, blind experiments, effect sizes in stresful conditions, male, female and both measures and different species used.
 
@@
  <br/><br/> 
-<input type=button class=hideshow></input>
 ```{r message=FALSE, warning=FALSE}
@@
     Blind_experiments = n.blind.ones,
+    Effect_sizes_.Enforced_monogamyq = (sum(prelim.data$Enforced.Monogamy == "YES")),
+    Effect_sizes_.Ambiguousq = (sum(prelim.data$Outcome.Class == "Ambiguous")),
+    Effect_sizes_.Indirectq = (sum(prelim.data$Outcome.Class == "Indirect")),
+    Effect_sizes_.Directq = (sum(prelim.data$Outcome.Class == "Direct")),
     Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
@@
  <br/><br/> 
-<input type=button class=hideshow></input>
 ```{r}
@@
 
-### Forest plot
-
-Here we show the raw effect sizes for each fitness component measured.
+### Forest Plot
 
@@
 
-  # scale_color_discrete(breaks=c("Ambiguous","Indirect","Direct"))+
+  #Add theme specifying text size, margins, lines etc.
   theme_bw()+
@@
 
-p.meta
-
 ### We can save the file in several vector graphics forms
@@
 # dev.off()
+
+p.meta
 ```
@@
 
-___________
-
-###Meta-analysis of individual outcomes
-
-We can run individual standard random effects models for each outcome.
-From the intercept only model we can obtain a mean (beta) and confidence intervals.
-Following that we can obtain estimates for _I^2^_, the % of residual heterogeneity for each given outcome.
-
-**Table S6** Summary of individual model results, including _I^2^_, for all outcomes with n>3. 
-<input type=button class=hideshow></input>
+______________
+
+## Meta-Analysis
+
+###Overall effect of sexual selection on fitness
+
+We can obtain an overall weghted grand mean and confidence intervals with a simple intercept only for both Bayesian and REML models.
+Notably, in both models the estimates are approximately the same, with Bayesian estimates being marginally wider.
+
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
+grand.mean.bayes <- brm(g | se(SE)  ~ 1 #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
+                + (1|Study.ID)
+                + (1|Outcome), 
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.9999, max_treedepth = 15),
+                data = prelim.data %>% mutate(SE = sqrt(var.g)))
+
+```
+
+```{r}
+grand.mean.bayes <- readRDS("data/grand.mean.bayes.rds")
+
+#Run REML model 
+forest.model <- rma.mv(g, var.g,
+                       mods = ~ 1,
+                       random = list(~ 1 | Study.ID,
+                                      ~ 1 | Outcome),
+                       method = "REML",
+                       data = prelim.data)
+
+#Manually imput bayesian results
+mean = c(forest.model$b, 0.22)
+LCI = c(forest.model$ci.lb, 0.01)
+UCI = c(forest.model$ci.ub, 0.43)
+grand.means.df <- data.frame(rbind(mean, LCI, UCI))
+colnames(grand.means.df) = c("REML", "Bayesian")
+grand.means.df %>% pander(digits = 2)
+```
+
+____________________
+
+###Effect of Sexual Selection for different fitness components
+
+Instead of running individual models for each fitness component we can run a model with the fitness components as predictors.
+In this case we maintain all of our fitness components and include study.id as a group level effect (to account for within study correlations in effect size).
+Using the ``brms`` package we can run a Bayesian model and generate fitted values for each fitness component.
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
+model.fitness.components.bayes <- brm(g | se(SE)  ~ Outcome #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
+                + (1|Study.ID), 
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                data = prelim.data %>% mutate(SE = sqrt(var.g)))
+
+make_text_summary(model.fitness.components.bayes) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander(split.cell = 40, split.table = Inf)
+```
+
+**Table S6** Summary of model predictions for 20 fitness components. In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot).
+
 ```{r, warning = FALSE}
-outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
-names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
-outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
-                          mods = ~ 1, 
-                          method = "REML",
-                          random = ~ 1 + Study.ID,
-                          subset = (Outcome_f == x),
-                          data = prelim.data))
-
-df.list <- as.data.frame(do.call("rbind", outcome.models)) # data frame of model results
-
-simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))
-
-#There is no simple way to get I2 for multilevel models in metafor, so we can obtain them manually for each outcome
-
-#Body Size 
-restricted.dataBS <- prelim.data %>% filter(prelim.data$Outcome == "Body Size")
-
-#Run estimate of heterogeneity
-WBS = diag(1/restricted.dataBS$var.g)
-XBS = model.matrix(outcome.models[["Body Size"]])
-PBS = WBS - WBS %*% XBS %*% solve(t(XBS) %*% WBS %*% XBS) %*% t(XBS) %*% WBS
-BodySizeI2 <- 100 * sum(outcome.models[["Body Size"]]$sigma2) / (sum(outcome.models[["Body Size"]]$sigma2) + (outcome.models[["Body Size"]]$k-outcome.models[["Body Size"]]$p)/sum(diag(PBS)))
-
-#Development Rate 
-restricted.dataDR <- prelim.data %>% filter(prelim.data$Outcome == "Development Rate")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataDR$var.g)
-X = model.matrix(outcome.models[["Development Rate"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-DevelopmentRateI2 <- 100 * sum(outcome.models[["Development Rate"]]$sigma2) / (sum(outcome.models[["Development Rate"]]$sigma2) + (outcome.models[["Development Rate"]]$k-outcome.models[["Development Rate"]]$p)/sum(diag(P)))
-
-#Early Fecundity 
-restricted.dataEF <- prelim.data %>% filter(prelim.data$Outcome == "Early Fecundity")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataEF$var.g)
-X = model.matrix(outcome.models[["Early Fecundity"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-EarlyFecundityI2 <- 100 * sum(outcome.models[["Early Fecundity"]]$sigma2) / (sum(outcome.models[["Early Fecundity"]]$sigma2) + (outcome.models[["Early Fecundity"]]$k-outcome.models[["Early Fecundity"]]$p)/sum(diag(P)))
-
-#Immunity
-restricted.dataI <- prelim.data %>% filter(prelim.data$Outcome == "Immunity")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataI$var.g)
-X = model.matrix(outcome.models[["Immunity"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-ImmunityI2 <- 100 * sum(outcome.models[["Immunity"]]$sigma2) / (sum(outcome.models[["Immunity"]]$sigma2) + (outcome.models[["Immunity"]]$k-outcome.models[["Immunity"]]$p)/sum(diag(P)))
-
-#Mating Duration
-restricted.dataMD <- prelim.data %>% filter(prelim.data$Outcome == "Mating Duration")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataMD$var.g)
-X = model.matrix(outcome.models[["Mating Duration"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-MatingDurationI2 <- 100 * sum(outcome.models[["Mating Duration"]]$sigma2) / (sum(outcome.models[["Mating Duration"]]$sigma2) + (outcome.models[["Mating Duration"]]$k-outcome.models[["Mating Duration"]]$p)/sum(diag(P)))
-
-#Mutant Frequency
-restricted.dataMF <- prelim.data %>% filter(prelim.data$Outcome == "Mutant Frequency")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataMF$var.g)
-X = model.matrix(outcome.models[["Mutant Frequency"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-MutantFrequencyI2 <- 100 * sum(outcome.models[["Mutant Frequency"]]$sigma2) / (sum(outcome.models[["Mutant Frequency"]]$sigma2) + (outcome.models[["Mutant Frequency"]]$k-outcome.models[["Mutant Frequency"]]$p)/sum(diag(P)))
-
-#Fitness Senescence
-restricted.dataFS <- prelim.data %>% filter(prelim.data$Outcome == "Fitness Senescence")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataFS$var.g)
-X = model.matrix(outcome.models[["Fitness Senescence"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-FitnessSenescenceI2 <- 100 * sum(outcome.models[["Fitness Senescence"]]$sigma2) / (sum(outcome.models[["Fitness Senescence"]]$sigma2) + (outcome.models[["Fitness Senescence"]]$k-outcome.models[["Fitness Senescence"]]$p)/sum(diag(P)))
-
-#Lifespan
-restricted.dataL <- prelim.data %>% filter(prelim.data$Outcome == "Lifespan")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataL$var.g)
-X = model.matrix(outcome.models[["Lifespan"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-LifespanI2 <- 100 * sum(outcome.models[["Lifespan"]]$sigma2) / (sum(outcome.models[["Lifespan"]]$sigma2) + (outcome.models[["Lifespan"]]$k-outcome.models[["Lifespan"]]$p)/sum(diag(P)))
-
-#Male Attractiveness
-restricted.dataMA <- prelim.data %>% filter(prelim.data$Outcome == "Male Attractiveness")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataMA$var.g)
-X = model.matrix(outcome.models[["Male Attractiveness"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-MaleAttractivenessI2 <- 100 * sum(outcome.models[["Male Attractiveness"]]$sigma2) / (sum(outcome.models[["Male Attractiveness"]]$sigma2) + (outcome.models[["Male Attractiveness"]]$k-outcome.models[["Male Attractiveness"]]$p)/sum(diag(P)))
-
-#Mating Frequency
-restricted.dataMF <- prelim.data %>% filter(prelim.data$Outcome == "Mating Frequency")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataMF$var.g)
-X = model.matrix(outcome.models[["Mating Frequency"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-MatingFrequencyI2 <- 100 * sum(outcome.models[["Mating Frequency"]]$sigma2) / (sum(outcome.models[["Mating Frequency"]]$sigma2) + (outcome.models[["Mating Frequency"]]$k-outcome.models[["Mating Frequency"]]$p)/sum(diag(P)))
-
-#Mating Latency
-restricted.dataML <- prelim.data %>% filter(prelim.data$Outcome == "Mating Latency")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataML$var.g)
-X = model.matrix(outcome.models[["Mating Latency"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-MatingLatencyI2 <- 100 * sum(outcome.models[["Mating Latency"]]$sigma2) / (sum(outcome.models[["Mating Latency"]]$sigma2) + (outcome.models[["Mating Latency"]]$k-outcome.models[["Mating Latency"]]$p)/sum(diag(P)))
-
-#Mating Success
-restricted.dataMS <- prelim.data %>% filter(prelim.data$Outcome == "Mating Success")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataMS$var.g)
-X = model.matrix(outcome.models[["Mating Success"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-MatingSuccessI2 <- 100 * sum(outcome.models[["Mating Success"]]$sigma2) / (sum(outcome.models[["Mating Success"]]$sigma2) + (outcome.models[["Mating Success"]]$k-outcome.models[["Mating Success"]]$p)/sum(diag(P)))
-
-#Ejaculate Quality and Production
-restricted.dataEQ <- prelim.data %>% filter(prelim.data$Outcome == "Ejaculate Quality and Production")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataEQ$var.g)
-X = model.matrix(outcome.models[["Ejaculate Quality and Production"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-EjaculateQualityI2 <- 100 * sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) / (sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) + (outcome.models[["Ejaculate Quality and Production"]]$k-outcome.models[["Ejaculate Quality and Production"]]$p)/sum(diag(P)))
-
-#Extinction Rate
-restricted.dataER <- prelim.data %>% filter(prelim.data$Outcome == "Extinction Rate")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataER$var.g)
-X = model.matrix(outcome.models[["Extinction Rate"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-ExtinctionRateI2 <- 100 * sum(outcome.models[["Extinction Rate"]]$sigma2) / (sum(outcome.models[["Extinction Rate"]]$sigma2) + (outcome.models[["Extinction Rate"]]$k-outcome.models[["Extinction Rate"]]$p)/sum(diag(P)))
-
-#Offspring Viability
-restricted.dataOV <- prelim.data %>% filter(prelim.data$Outcome == "Offspring Viability")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataOV$var.g)
-X = model.matrix(outcome.models[["Offspring Viability"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-OffspringViabilityI2 <- 100 * sum(outcome.models[["Offspring Viability"]]$sigma2) / (sum(outcome.models[["Offspring Viability"]]$sigma2) + (outcome.models[["Offspring Viability"]]$k-outcome.models[["Offspring Viability"]]$p)/sum(diag(P)))
-
-#Reproductive Success
-restricted.dataRS <- prelim.data %>% filter(prelim.data$Outcome == "Reproductive Success")
-
-#Run estimate of heterogeneity
-W = diag(1/restricted.dataRS$var.g)
-X = model.matrix(outcome.models[["Reproductive Success"]])
-P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-ReproductiveSuccessI2 <- 100 * sum(outcome.models[["Reproductive Success"]]$sigma2) / (sum(outcome.models[["Reproductive Success"]]$sigma2) + (outcome.models[["Reproductive Success"]]$k-outcome.models[["Reproductive Success"]]$p)/sum(diag(P)))
-
-simple.frame$I2 <- c(NA, BodySizeI2, DevelopmentRateI2, EarlyFecundityI2, ImmunityI2, MatingDurationI2, NA, MutantFrequencyI2, FitnessSenescenceI2, LifespanI2, MaleAttractivenessI2, MatingFrequencyI2, MatingLatencyI2, MatingSuccessI2, NA, EjaculateQualityI2, ExtinctionRateI2, OffspringViabilityI2, ReproductiveSuccessI2)
-
-outcome.frame <- format(simple.frame, digits = 2)
-outcome.frame <- add_rownames(outcome.frame, "Outcome")
-outcome.frame$b <- as.numeric(outcome.frame$b)
-outcome.frame$k <- as.numeric(outcome.frame$k)
-outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
-outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
-outcome.frame$I2 <- as.numeric(outcome.frame$I2)
-outcome.frame$Class <- c("Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Direct", "Direct", "Direct")
-
-#Only present subset model results for outcomes with 4 or more effect sizes
-
-outcome.frame %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)
-```
-
-______________
-
-## Multilevel Meta-Analysis
+components.brms <- readRDS(file = "data/components.brms.rds") #Avoid re-running model above
+
+#Expand grid for environment and sex
+brms.newdata <- as.data.frame(expand.grid(Outcome = unique(prelim.data$Outcome)))
+
+#Get average SE: useful if using predict, but not fitted
+av.se.g <- prelim.data %>% group_by(Outcome) %>% summarise(mean = mean(sqrt(var.g)))
+brms.newdata$SE <- av.se.g$mean
+
+#Add predictions/fitted values
+brms.predict <- fitted(components.brms, newdata = brms.newdata, re_formula = NA)
+brms.predict <- as.data.frame(brms.predict)
+brms.predictions <- data.frame(brms.newdata$Outcome, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)
+
+#Name columns
+colnames(brms.predictions) <- c("Fitness Component", "Estimate", "Error", "LCI", "UCI")
+
+outcome.list.factor <-  c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+
+brms.predictions <- brms.predictions[match(outcome.list.factor, brms.predictions$`Fitness Component`),]
+rownames(brms.predictions) <- NULL
+sample.sizes.outcomes <- as.data.frame(table(prelim.data$Outcome))
+colnames(sample.sizes.outcomes) <- c("Fitness Component", "n")
+fitness.component.predictions <- left_join(brms.predictions, sample.sizes.outcomes, by = "Fitness Component")
+fitness.component.predictions %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
+```
+
+____________________
 
@@
 We collected data from fitness components that were deemed ambiguous as well as unambiguous.
-The ambiguous outcomes are likely to add in heterogeneity to the models and not help us in answering questions of fitness effects of sexual selection.
-A model utilising our complete dataset with many moderator variables would thus be:
+The ambiguous outcomes are likely to add in heterogeneity to the models and may not help us in answering questions of the fitness effects of sexual selection.
+A REML model utilising our complete dataset with many moderator variables would thus be:
 
@@
 <br></br>
-
-Here we can also run a bayesian model alongside the restricted maximum likelihood model (metafor)
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+Here we can also run a Bayesian model alongside the REML model (metafor). The _R^2^_ for this model is 0.36 (95% CIs = 0.33-0.4). 
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
 #Also use bayesian model
@@
 <br></br>
-
-```{r}
+<input type=button class=hideshow></input>
+```{r}
+brms.preliminary <- readRDS(file = "data/brms.preliminary.rds") #Avoid re-running model above
 #Plot model results
@@
 First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding).
+Notably, with the ambiguous measures included we already see a positive effect of sexual selection and thus removing these fitness components is not an attempt to obtain a significant answer, rather it restricts the data to traits that are less contentious and thus we believe this approach is conservative.
 In this model we use Sex, Environment, Taxon and the interaction between sex and environment.
@@
 <input type=button class=hideshow></input>
-```{r, results='hide', message=FALSE, error = FALSE, warning=FALSE}
+```{r, message=FALSE, error = FALSE, warning=FALSE}
 #Restrict the dataset for unambiguous outcomes and environments 
@@
 To make sense of these estimates we should obtain average predictions for each moderator variable class of interest.
-We can do that by using a modified version version of a function used by Holman 2017.
+We can do that by using a modified version version of a function used by @Holman_2018.
 Here it alows us to cluster predictions for the different moderators of interest: Sex, environment, taxon etc.
@@
 
-Given that none of categories of taxa significantly impact effect size we can incorporate them as random/group level effects in later models.
+Given that none of categories of taxa significantly impact effect size, and many categories are unsamples (Table S8) we can incorporate them as random/group level effects in models henceforth.
 
@@
 
-###Sexual Selection, Environment and Sex
-
-Here we ask two key questions: Does sexual selection benefit populations in stressed environments more than benign environments? **AND** Do the benefits of sexual selection differ between the sexes?
-
-We can run a model where the outcome is crossed with study (Study.ID) and Taxon as random effects and environment, sex and their interactions are fized effects.
-
-```{r}
-#run model with taxon as a random effect
+###REML: Effects of Environment and Sex
+
+Here we ask two key questions: Does sexual selection benefit populations in stressful environments more than benign environments? **AND** Do the benefits of sexual selection differ between the sexes?
+
+```{r}
+#We can run a model where the outcome is crossed with study (Study.ID) and Taxon as random effects and environment, sex and their interactions are fixed effects.
 model.complete2 <- rma.mv(g, V = var.g, 
@@
 
-______________
-
-####Comparisons of environment and Sex Conditions REML model through anovas
+We conducted hypothesis tests on the above model to investigate the effective difference between two groups.
+Depending on the package this method is also refered to as linear hypothesis or anova (metafor).
 
@@
 #anova where you specify the values based on the list of moderators
-anova.1 = anova(model.complete2, L=c(1, 0, -1, 0, 0, 0)) 
-anova.2 = anova(model.complete2, L=c(0, 0, 0, 1, 0, -1))
-anova.3 = anova(model.complete2, L=c(0, 0, 1, 0, 0, -1))
-anova.4 = anova(model.complete2, L=c(1, 0, 0, -1, 0, 0))
-anova.5 = anova(model.complete2, L=c(0, 1, 0, 0, -1, 0))
+anova.1 = anova(model.complete2, L=c(0, 0, -1, 0, 0, 0)) 
+anova.2 = anova(model.complete2, L=c(0, 0, -1, 0, 0, -1))
+anova.3 = anova(model.complete2, L=c(0, 0, 0, -1, 0, -1))
+anova.4 = anova(model.complete2, L=c(0, 0, 0, -1, 0, 0))
+anova.5 = anova(model.complete2, L=c(0, 0, 0, -1, -1, 0))
 
@@
 anova.frame$pval <- NULL
+rownames(anova.frame) <- c("M vs F, Benign", "M vs F, Stressful", "Benign vs Stressful, Female", "Benign vs Stressful, Male", "Benign vs Stressful, Both")
 anova.frame %>% pander(split.table = Inf)
@@
 From these anovas we see that a stressful environment leads to a significantly greater increase in fitness components for "female"" but NOT "both" sexes, while significantly decreasing male fitness.
-We can also test if there is a difference between males and females in stressful but not benign conditions.
+We also see there is a difference between the sexes in stressful environments (females with larger mean) but not in benign environments (marginal).
 
@@
 
-###Bayesian model on the effects of environment and sex
-
-We can run a bayesian model using the brms package.
+###Bayesian: Effects of Environment and Sex
+
+We can run a Bayesian model using the ``brms`` package.
 The model has the same moderators as the REML approach used above.
@@
 The _R^2^_ of this Bayesian model was 0.35 (95% CIs = 0.31-0.39).
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+Additionally, we can obtain the distribution of posterior fitted values and examine the model summary
+
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
 #Use brms to create a model similar to the one used in the REML approach. 
@@
 <br></br>
-We can then get the distribution of posterior fitted values and examine the model summary
 
@@
 ```{r}
+brms.complete2 <- readRDS(file = "data/brms.complete2.rds") #Avoid re-running model above
+
 #You can obtain a posterior sampling through the ``fitted.brmsfit`` function, which gives the same posterior values as doing it manually (see below).**Note that the fitted values obtained here have much smaller error than the predict values**
@@
 
+#Alternatively you can obtain posterior samples manually.
 post <- (posterior_samples(brms.complete2, 
@@
 Like with the REML approach, from these model results we can test several hypotheses between the categories of environment and sex.
-For instance, the first hypothesis in the table below tests whether there is a difference between male and female fitness increase under sexual selection in benign conditions.
-With the answer stating that they largely overlap in their predictions and are the same, to 95 % confidence.
 
@@
 #Obtain hypothesis estimates
-brms.hypothesis <- hypothesis(brms.complete2, c("Intercept = SexF",
-                             "EnvironmentStressed = SexF:EnvironmentStressed",
-                             "SexF = SexF:EnvironmentStressed",
-                             "Intercept = EnvironmentStressed",
-                             "SexB = SexB:EnvironmentStressed"))
+brms.hypothesis <- hypothesis(brms.complete2, c("0 = SexF",
+                             "0 = SexF + SexF:EnvironmentStressed",
+                             "0 = SexF:EnvironmentStressed + EnvironmentStressed",
+                             "0 = EnvironmentStressed",
+                             "0 = SexB:EnvironmentStressed + EnvironmentStressed"))
 #Format into dataframe
@@
 brms.hypothesis.table <- format(brms.hypothesis.table, digits = 2)
+rownames(brms.hypothesis.table) <- c("M vs F, Benign", "M vs F, Stressful", "Benign vs Stressful, Female", "Benign vs Stressful, Male", "Benign vs Stressful, Both")
 brms.hypothesis.table %>% pander(split.table = Inf)
@@
 }
+
 # Get the predictions for each combination of moderators
@@
 
+#Plot the posterior values from the Bayesian model as density ridges
 pd <- position_dodgev(height = 0.3)
@@
 
+#Add the REML predictions as circles with error bars
 both.plots <- posterior.plot + 
@@
   scale_y_discrete(expand=c(0.075,0))
-
-both.plots
 
@@
 # dev.off()
+
+both.plots
 ```
@@
 Circle size is proportional to sample size (shown below).
-
-**Table S12** The predictions in the plot above use the following dataframe
+The REML predictions are shown as circles with error bars and the Bayesian predictions as density ridges.
+This figure can also be found in the main manuscript.
+
+**Table S12** The REML predictions in the plot above use the following dataframe
 ```{r}
@@
 
-###Estimating Heterogeneity Using _I^2^_
-
-Let's obtain a _I^2^_ statistic for the model above using the formulas presented here: http://www.metafor-project.org/doku.php/tips:i2_multilevel_multivariate
-
-There are different methods to obtain estimates of _I^2^_, they should be pretty similar though.
-Here we obtain an overall value of _I^2^_ that is weighted based on variance where estimates of heterogeneity are sourced from sigma^2^ of the respective models.
-```{r}
-#This is for the model with outcome and study as crossed random effects
-W <- diag(1/restricted.data$var.g)
-X <- model.matrix(model.complete2)
-P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
-```
-95 % is a reasonably high _I^2^_ value but is relatively common in Ecology and Evolution (Nakagawa 2017).
-
-To investigate the sources of heterogeneity we can obtain a breakdown of the heterogeneity for the model.
-```{r}
-100 * model.complete2$sigma2 / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
-```
-
-This indicates that 61 % of total heterogeneity is due to the **between study** heterogeneity and 34 % for **between outcome** heterogeneity between different outcomes.
-With the remaining 5.5 % due to sampling variance.
-Interestingly this might indicate that _I^2^_ would be largely reduced for a model restricted to a single outcome.
-The _I^2^_ values for individual outcomes were presented earlier in this document and presented alongside the forest plot.
+###Estimating Hedges' g Heterogeneity Using _I^2^_
+
+Using an adapted function from https://github.com/daniel1noble/metaAidR we can obtain confidence intervals for total _I^2^_ and the individual components of the random effects.
+There are different methods to obtain estimates of _I^2^_.
+Here we obtain an overall value of _I^2^_ that is weighted based on variance and where estimates of heterogeneity are sourced from sigma^2^ of the respective models.
+The values are based on the REML models.
+
+```{r}
+I2(model.complete2, restricted.data$var.g) %>% pander(digits = 3)
+```
+These values indicate that 61.5 % of total heterogeneity is due to the **between study** heterogeneity and 33.5 % for **between outcome** heterogeneity between different outcomes.
+The total _I^2^_  is 95 %, a reasonably high _I^2^_ value.
+However this is relatively common in Ecology and Evolution total.
 
@@
 
-## Multilevel Meta-Analysis on Variance
-
-This meta-analysis on variation utilises previously described and utilised methods devoleped (Nakagawa et al.
-2015; Senior et al.
-2016).
+##Meta-Analysis on Variance
+
+###Obtaining lnCVR and Meta-Analysis Models
+
+This meta-analysis on variation utilises previously described and utilised methods devoleped [@Nakagawa_2015; @Senior_2016].
 Our goal is to determine whether the phenotypic variance in fitness related traits is impacted by sexual selection.
@@
 ```{r, warning=FALSE}
-#Now try with multilevel model 
 variance.model <- rma.mv(lnCVr, V = var.lnCVr, mods = ~ 1 + Sex*Environment, 
@@
 ```
-
 **Table S13** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
@@
 Predictions based on the REML and Bayesian model can then be generated in the same way as for Hedges'g.
-Here, lower values of lnCVR indicate a narrowing (decrease) in phenotypic variance as a result of sexual selection.
+Here, negative values of lnCVR indicate a narrowing (decrease) in phenotypic variance as a result of sexual selection.
 
@@
 
-both.var.plots
-
 # svg("figures/both.var.plots.svg", width=6, height=6)
@@
 # dev.off()
+
+both.var.plots
 ```
@@
 **Figure S4:** Phenotypic variation changes under sexual selection in stressful environments.
-For stressed females, phenotypic variation decreases (narrows).
-While for males in stressed environments it increases.
-For outcomes that measured both males and females (both) phenotypic variation did not change **or** changed for males and females in opposite directions and thus cancels out when measured together.
+For females under stressful conditions phenotypic variation decreases (narrows).
+While for males in stressful environments it increases.
+For outcomes that measured a mix of both males and females (pooled samples) in stressful environments phenotypic variation decreased slightly.
+The REML predictions are shown as circles with error bars and the Bayesian predictions as density ridges.
 Circle size is proportional to sample size.
 
-**Table S14** The above figure is based off the following dataframe:
+**Table S14** The REML predictions in the plot above use the following dataframe.
 ```{r}
@@
 
+____________________
+
+###Hypothesis Tests For Phenotypic Variation Model
+
+Like we did for Hedges g' we can also conduct hypothesis tests between categorical groups to inform us if there is a difference between two groups of interest (e.g.
+females in benign and females in stressful environments).
+Here we present Bayesian and REML hypothesis predictions.
+Positive values indivate the first term in the hypothesis is larger (which would be male for rows 1-2 or benign for rows 3-5).
+
+**Table S15** Bayesian hypothesis tests between categorical groups for phenotypic variation (lnCVR)
+```{r}
+#Obtain hypothesis estimates
+brms.hypothesis.var <- hypothesis(var.brms, c("0 = SexF",
+                             "0 = SexF + SexF:EnvironmentStressed",
+                             "0 = SexF:EnvironmentStressed + EnvironmentStressed",
+                             "0 = EnvironmentStressed",
+                             "0 = SexB:EnvironmentStressed + EnvironmentStressed"))
+#Format into dataframe
+brms.hypothesis.table.var <- 
+  data.frame(brms.hypothesis.var[["hypothesis"]][["Hypothesis"]],
+             brms.hypothesis.var[["hypothesis"]][["Estimate"]],
+             brms.hypothesis.var[["hypothesis"]][["Est.Error"]],
+             brms.hypothesis.var[["hypothesis"]][["CI.Lower"]],
+             brms.hypothesis.var[["hypothesis"]][["CI.Upper"]],
+             brms.hypothesis.var[["hypothesis"]][["Star"]])
+colnames(brms.hypothesis.table.var) <- c("Hypothesis", "Estimate", "Est.Error", "CI.Lower", "CI.Upper", " ")
+row.names(brms.hypothesis.table.var) <- c("M vs F, Benign", "M vs F, Stressful", "Benign vs Stressful, Female", "Benign vs Stressful, Male", "Benign vs Stressful, Both")
+brms.hypothesis.table.var <- format(brms.hypothesis.table.var, digits = 2)
+brms.hypothesis.table.var %>% pander(split.table = Inf)
+```
+
+**Table S16** REML hypothesis tests between categorical groups for phenotypic variation (lnCVR)
+```{r}
+#anova where you specify the values based on the list of moderators
+anova.1 = anova(variance.model, L=c(0, 0, -1, 0, 0, 0)) 
+anova.2 = anova(variance.model, L=c(0, 0, -1, 0, 0, -1))
+anova.3 = anova(variance.model, L=c(0, 0, 0, -1, 0, -1))
+anova.4 = anova(variance.model, L=c(0, 0, 0, -1, 0, 0))
+anova.5 = anova(variance.model, L=c(0, 0, 0, -1, -1, 0))
+
+anova.list.var <- list(anova.1, anova.2, anova.3, anova.4, anova.5)
+
+anova.frame.var <- t(data.frame(lapply(anova.list.var, function(x) {
+  data.frame(x[["hyp"]],
+  x[["Lb"]],
+  x[["se"]],
+  x[["Lb"]] - 1.96*x[["se"]],
+  x[["Lb"]] + 1.96*x[["se"]],
+  x[["pval"]])
+})))
+anova.frame.var <- as.data.frame(split(anova.frame.var, rep(1:6)))
+colnames(anova.frame.var) <- c("Hypothesis", "Estimate", "Est.Error", "CI.Lower", "CI.Upper", "pval")
+anova.frame.var$Estimate <- as.numeric(levels(anova.frame.var$Estimate))[anova.frame.var$Estimate]
+anova.frame.var$Est.Error <- as.numeric(levels(anova.frame.var$Est.Error))[anova.frame.var$Est.Error]
+anova.frame.var$CI.Lower <- as.numeric(levels(anova.frame.var$CI.Lower))[anova.frame.var$CI.Lower]
+anova.frame.var$CI.Upper <- as.numeric(levels(anova.frame.var$CI.Upper))[anova.frame.var$CI.Upper]
+anova.frame.var$pval <- as.numeric(levels(anova.frame.var$pval))[anova.frame.var$pval]
+anova.frame.var <- format(anova.frame.var, digits = 2)
+anova.frame.var$star <- c("*", "*", "*", "*", "*")
+colnames(anova.frame.var)[colnames(anova.frame.var)=="star"] <- " "
+anova.frame.var$pval <- NULL
+row.names(anova.frame.var) <- c("M vs F, Benign", "M vs F, Stressful", "Benign vs Stressful, Female", "Benign vs Stressful, Male", "Benign vs Stressful, Both")
+anova.frame.var %>% pander(split.table = Inf)
+```
+
+____________________
+
+###Estimating lnCVR Heterogeneity Using _I^2^_
+
+Similar to the meta-analysis on Hedges' g we can obtain _I^2^_ for lnCVR REML model.
+In this case (compared to Hedges' g) we see Taxon has more of a variable effect on overall _I^2^_ estimates, although the overall _I^2^_ remains relatively similar (95.4 %).
+
+```{r}
+I2(variance.model, restricted.data2$var.g) %>% pander(digits = 3)
+```
 _________
@@
 
-Checking for biases with a funnel plot.
-Note that the trim and fill method does not work with rma.mv objects.
-However we can perform Eggers test using the ``regtest()`` function.
+Here we check for publication bias with a funnel plot.
+Note that the trim and fill or Eggers test method does not work with rma.mv objects.
+We can perform Eggers test using the ``regtest()`` function.
 This tests for asymmetry via assessing relationships between effect size and a specified predictor.
@@
 
-We can use ggplot for creating a funnel plot.
-The code is pretty clunky and unlike the ``funnel.rma`` it does not use automatically plot residuals so we have to generate them independently.
-The outline taken from is taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
+We can use ggplot for creating a funnel plot. The outline taken from is taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
 
@@
 
-# Obtain grand mean effect size    <- ADDED BY LUKE
-grand.mean <- as.numeric(forest.model$b) #WHAT about weightings?
+# Obtain grand mean effect size 
+grand.mean <- as.numeric(forest.model$b)
 
@@
 <br></br>
-**Figure S5:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 7.2671, p < .0001).
+**Figure S5:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.2210, p < .0001).
 The asymmetry appears to be sourced from a spread of positive effect sizes outside the funnel and of varying degrees of precision.
@@
 
-This shows that publication year does not have a significant effect on effect sizes from the published study
-
-<!-- ###Sample Size -->
-
-<!-- We also collected sample sizes for each of the effect sizes calculated.
-Because we are dealing withj different taxa some studies are not suited to have sample sizes in the 1000's.
-We can simply inspect the sample size ande effect sizes through the following plot: -->
-
-<!-- ```{r, fig.height= 10, fig.width=5} -->
-<!-- samplesize.plot <- prelim.data %>% ggplot(aes(x=n, y = g))+ -->
-<!--   geom_point(fill="grey", color="grey20", shape=21)+ -->
-<!--   scale_x_log10(breaks = c(10, 100, 1000, 10000)) +  -->
-<!--   #xlim(0,2100)+ -->
-<!--   facet_grid(Taxon~., scales='free')+ -->
-<!--   ylim(-3.5,3.5)+ -->
-<!--   geom_hline(yintercept=0, linetype="dashed")+ -->
-<!--   labs(y='Effect size (Hedges g)', x= 'Sample Size (n) [logscale]') -->
-
-<!-- ggsave(plot = samplesize.plot, filename = "figures/samplesize_plot.eps", height = 10, width = 5) -->
-<!-- samplesize.plot -->
-<!-- ``` -->
-<!-- <br></br> -->
-<!-- **Figure S8:** Variation in size does not appear to have unexpected trends in any taxons, with greater variation in effect size for those studies utilising a lower sample size.  -->
-
-<!-- From these plots we can see that with increased sample size the effect sizes are closer to zero.
-This trend is taken into account as meta-analytic models and are wighted by 1/variance.
-**Note** Promislow (1998) has one sample size of >10,000 in flies and is not shown here to avoid making radical changes to the scale.
--->
+This shows that publication year does not have a significant effect on effect sizes from the published study.
 
@@
 
-ggsave(plot = blind.plot, filename = "figures/blind_plot.eps", height = 6, width = 8)
+#ggsave(plot = blind.plot, filename = "figures/blind_plot.eps", height = 6, width = 8)
 blind.plot
@@
 
-ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
-generations.plot
+#ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
 
@@
 # dev.off()
+
+generations.plot
 ```
@@
 
-Kawecki et al.(2012) reviewed the field of experimental evolution and noted that changes to variation may need longer generations to become apparent.
+@Kawecki_2012 reviewed the field of experimental evolution and noted that changes to variation may need longer generations to become apparent.
 The following graph looks at the relationship between number of generations and lnCVr
@@
 
+________________
+
+##References
+ <br/><br/> 
 <!-- Some JavaScript to control the buttons to show/hide the big tables -->

### 2018-06-20 I2_function.R

@@ -1,0 +1,92 @@
+#Script for I2, taken and modified from Dan Nobles MetaAidR on github
+
+
+round_df <- function(x, digits) {
+  numeric_columns <- sapply(x, class) == 'numeric'
+  x[numeric_columns] <-  round(x[numeric_columns], digits)
+  x
+}
+
+I2 <- function(model, v, ME = FALSE, sims = 1500, phylo = FALSE){
+  
+  if(class(model) != "MCMCglmm" && class(model) != "rma.mv" && class(model) != "rma"){
+    stop("The model object is not of class 'MCMCglmm' or 'metafor'")
+  }
+  
+  wi <- 1/v  #weight
+  Vw <- sum((wi) * (length(wi) - 1))  / (((sum(wi)^2) - sum((wi)^2)))
+  
+  if("MCMCglmm" %in% class(model)){
+    # Get posterior distribution
+    # TO DO : NEED TO MAKE THIS WORK WITH ginverse in MCMCglmm. Added a bit, but needs work.
+    if(ME == FALSE){
+      post <- model$VCV[,-match(c("sqrt(mev):sqrt(mev).meta"), colnames(model$VCV))]
+    } else{
+      post <- model$VCV[,-match(ME, colnames(model$VCV))]
+    }
+    #Calculate total variance
+    VT <- rowSums(Matrix::cBind(post, Vw))
+    Vt <- rowSums(post)  # remove Vw
+    
+    # For each variance component divide by the total variance. Note this needs to be fixed for phylo, but does deal with variable random effects.
+    I2_re <- post / VT
+    I2_total  <- Vt / VT
+    
+    if(phylo == FALSE){
+      tmpMatrix <- Matrix::cBind(I2_re, total = I2_total)
+    }else{
+      I2_phylo <- post[,match(phylo, colnames(post))] / Vt
+      tmpMatrix <- Matrix::cBind(I2_re, I2_phylo, total = I2_total)
+    }
+    
+    mode <- MCMCglmm::posterior.mode(coda::as.mcmc(tmpMatrix))
+    CI <- coda::HPDinterval(coda::as.mcmc(tmpMatrix))
+    colnames(CI) <- c("2.5% CI", "97.5% CI")
+    
+    I2_Table <- as.data.frame(Matrix::cBind(I2_Est. = mode[-match("units", names(mode))], CI[-match("units", rownames(CI)),]))
+    class(I2_Table) <- c("metaAidR", "data.frame")
+    
[…]

### 2018-06-20 Tidy_functions_for_brms.R

@@ -21,3 +21,12 @@ neat.R2 <- function(model){
   R2 <- bayes_R2(model) %>% round(2)
   paste(R2[1,1], " (95% CIs = ", R2[1,3], "-", R2[1,4], ")", sep = "")
 }
+
+# For adding stars to the tables when the 95% CIs don't overlap zero
+add_significance_stars2 <- function(prediction){
+  prediction$xx <- " "
+  prediction$xx[prediction[,4] < 0 & prediction[,5] < 0] <- "*"
+  prediction$xx[prediction[,4] > 0 & prediction[,5] > 0] <- "*"
+  names(prediction)[names(prediction) == "xx"] <- " "
+  prediction
+}

### 2018-06-21 meta_analysis_sexual_selection_pop_fitness.Rmd
21/6 update

@@
 ```{r, fig.height= 6, fig.width=8, warning=FALSE}
-generations.plot <- df.forest.model %>% ggplot(aes(x=Generations, y=g))+
-  geom_point(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
+generations.plot <- restricted.data %>% ggplot(aes(x=Generations, y=g))+
+  geom_jitter(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
   ylim(-3.5,3.5)+
@@
 <br></br>
+A linear model shows next to no effect of generations on effect size: 
+```{r}
+summary(lm(g ~ Generations, data = restricted.data))
+```
 
 @Kawecki_2012 reviewed the field of experimental evolution and noted that changes to variation may need longer generations to become apparent.
-The following graph looks at the relationship between number of generations and lnCVr
+The following graph looks at the relationship between number of generations and lnCVr:
 
@@
 generations.plot.var <- restricted.data2 %>% ggplot(aes(x=Generations, y=lnCVr))+
-  geom_point(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
+  geom_jitter(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
   ylim(-3.5,3.5)+
@@
 
-**Figure S11:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran.
-
-```{r}
-summary(lm(lnCVr ~ Generations, data = restricted.data))
+**Figure S11:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
+
+```{r}
+summary(lm(lnCVr ~ Generations, data = restricted.data2))
 ```

### 2018-06-21 meta_analysis_sexual_selection_pop_fitness.Rmd
21/6 Update 2

@@
 
-### Effect Size Calculation
-
-A spreadsheet describing the data that was extracted from each of the included studies is included as supplementary material.
-It details the type of data collected for each study (arithmatic means, SD, n, F-statistic, chi-squared, proportion etc.).
-The rules utilised were as follows:
+### Data Extraction and Effect Size Calculation
+
+The rules utilised during the data extraction and effect size calculation were as follows:
 

### 2018-08-09 meta_analysis_sexual_selection_pop_fitness.Rmd
July Update
Former-commit-id: e74e4243afdb2d1711123ba6f45a5cc82486c246

@@
 title: 'Sexual selection improves population fitness: a meta-analysis'
-author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
+author: "Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
 subtitle: Supplementary Material
@@
 We used the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) as a guide during this meta-analysis.
+The repository used to formulate this document can be found here: https://github.com/JustinCally/SexualSelection
 
@@
     Effect_sizes_.Directq = (sum(prelim.data$Outcome.Class == "Direct")),
-    Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
-    Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
+    Effect_sizes_.Stressfulq = (sum(prelim.data$Environment == "Stressed")),
+    Effect_sizes_.Benignq = (sum(prelim.data$Environment == "Unstressed")),         
     Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
@@
 Notably, in both models the estimates are approximately the same, with Bayesian estimates being marginally wider.
+The priors for ``brms`` are set from a weakly non-informative student t-distribution: ``student_t(3, 0, 10)``.
+Notew that narrowing the prior (e.g.
+standard normal distribution: ``normal(0,1)``) has negligible effects on the model results.
 
@@
                 + (1|Study.ID)
-                + (1|Outcome), 
+                + (1|Outcome)
+                + (1|Taxon), 
                 family = "gaussian", 
@@
 
-```
-
-```{r}
+saveRDS(grand.mean.bayes, "data/grand.mean.bayes.rds") #Save to avoid re-running during knit
+```
+
+```{r}
+#Inspect this for details of random/group level effects
 grand.mean.bayes <- readRDS("data/grand.mean.bayes.rds")
@@
                        random = list(~ 1 | Study.ID,
-                                      ~ 1 | Outcome),
+                                      ~ 1 | Outcome,
+                                      ~ 1 | Taxon),
                        method = "REML",
@@
 
-#Manually imput bayesian results
-mean = c(forest.model$b, 0.22)
-LCI = c(forest.model$ci.lb, 0.01)
-UCI = c(forest.model$ci.ub, 0.43)
-grand.means.df <- data.frame(rbind(mean, LCI, UCI))
+#Manually imput bayesian results: brms model object difficult to extract from
+mean = c(forest.model$b, 0.23) #Values for Bayesian can be obtained from grand.mean.bayes model object
+LCI = c(forest.model$ci.lb, -0.06)
+UCI = c(forest.model$ci.ub, 0.51)
+Stat = c(forest.model$pval, 18.09) #BF can be obtained with: hypothesis(grand.mean.bayes, "Intercept > 0")
+grand.means.df <- data.frame(rbind(mean, LCI, UCI, Stat))
 colnames(grand.means.df) = c("REML", "Bayesian")
@@
 model.fitness.components.bayes <- brm(g | se(SE)  ~ Outcome #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
-                + (1|Study.ID), 
+                + (1|Study.ID)
+                + (1|Taxon), 
                 family = "gaussian", 
@@
 make_text_summary(model.fitness.components.bayes) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander(split.cell = 40, split.table = Inf)
-```
-
-**Table S6** Summary of model predictions for 20 fitness components. In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot).
+
+saveRDS(model.fitness.components.bayes, "data/components.brms.rds") #Save to avoid re-running during knit
+```
+
+**Table S6** Summary of model predictions for 20 fitness components.
+In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot).
+Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0.
+Where values greater than 1 correspond to higher likelihood of the effect size being positive and values less than 1 suggest that the effect size is more likely to be negative.
 
@@
 fitness.component.predictions <- left_join(brms.predictions, sample.sizes.outcomes, by = "Fitness Component")
-fitness.component.predictions %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
+
+#Obtain Bayes Factor of likelihood that the outcome is greater than 0
+BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+#Obtain BF for all components
+Hypotheses <- list()
+BFs <- list()
+Hypotheses[["Behavioural Plasticity"]] <- hypothesis(components.brms, "Intercept > 0") #Intercept in model, need to do it by itself
+BFs[["Behavioural Plasticity"]] <- Hypotheses[["Behavioural Plasticity"]][["hypothesis"]][["Evid.Ratio"]]
+for (i in BF.outcome.list){
+Hypotheses[[i]] <- hypothesis(components.brms, paste("Intercept + Outcome",i," > 0", sep = ""))
+BFs[[i]] <- Hypotheses[[i]][["hypothesis"]][["Evid.Ratio"]]
+} #Loop for all fitness compoinents
+fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
 ```
@@
 summary(model.preliminary, digits = 2)
-
 ```

### 2018-08-09 meta_analysis_sexual_selection_pop_fitness.Rmd
July Update 2
Former-commit-id: b36ca7cd53a41a1312d6526493c85c9fd656bf11

@@
 } #Loop for all fitness compoinents
+
 fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)

### 2018-08-09 meta_analysis_sexual_selection_pop_fitness.Rmd
July Update 3
Remove rownames Table S6

@@
 
-fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
+fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% `row.names<-`(NULL) %>% pander(split.cell = 40, split.table = Inf, digits = 2)
 ```

### 2018-09-14 meta_analysis_sexual_selection_pop_fitness.Rmd
REML estimates for outcomes table

--- 2018-08-09 meta_analysis_sexual_selection_pop_fitness.Rmd
@@
 **Table S6** Summary of model predictions for 20 fitness components.
-In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot).
+In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot) using the Bayesian values.
 Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0.
 Where values greater than 1 correspond to higher likelihood of the effect size being positive and values less than 1 suggest that the effect size is more likely to be negative.
+The right side of the table provides the REML estimates with SE and CIs.
 
@@
 #Name columns
-colnames(brms.predictions) <- c("Fitness Component", "Estimate", "Error", "LCI", "UCI")
+colnames(brms.predictions) <- c("Fitness Component", "Bayes Pred.", "Bayes SE", "Bayes LCI", "Bayes UCI")
 
@@
 
-fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
+#Now for REML
+model.fitness.components.REML <- rma.mv(g, var.g, mods = ~ 1 + Outcome,
+                         random = list(~ 1 | Study.ID,
+                                       ~ 1 | Taxon),
+                         method = "REML",
+                         data = prelim.data)
+
+get.predictions.outcomes <- function(newdata){
+  `Body Condition`<-0; `Body Size`<-0; `Development Rate`<-0; `Early Fecundity`<-0; `Ejaculate Quality and Production`<-0; `Extinction Rate`<-0; `Fitness Senescence`<-0; Immunity<-0; Lifespan<-0; `Male Attractiveness`<-0; `Mating Duration`<-0; `Mating Frequency`<-0; `Mating Latency`<-0; `Mating Success`<-0; `Mutant Frequency`<-0; `Offspring Viability`<-0; `Pesticide Resistance`<-0; `Reproductive Success`<-0; Strength<-0
+  if(newdata[1] == 'Body Size') `Body Size`<-1
+  if(newdata[1] == 'Development Rate') `Development Rate`<-1
+  if(newdata[1] == 'Early Fecundity') `Early Fecundity`<-1
+  if(newdata[1] == 'Immunity')Immunity<-1
+  if(newdata[1] == 'Mating Duration')`Mating Duration`<-1
+  if(newdata[1] == 'Pesticide Resistance')`Pesticide Resistance`<-1
+  if(newdata[1] == 'Mutant Frequency')`Mutant Frequency`<-1
+  if(newdata[1] == 'Body Condition')`Body Condition`<-1
+  if(newdata[1] == 'Fitness Senescence')`Fitness Senescence`<-1
+  if(newdata[1] == 'Lifespan')Lifespan<-1
+  if(newdata[1] == 'Male Attractiveness')`Male Attractiveness`<-1
+  if(newdata[1] == 'Mating Frequency')`Mating Frequency`<-1
+  if(newdata[1] == 'Mating Latency')`Mating Latency`<-1
+  if(newdata[1] == 'Mating Success')`Mating Success`<-1
+  if(newdata[1] == 'Strength')Strength<-1
+  if(newdata[1] == 'Ejaculate Quality and Production')`Ejaculate Quality and Production`<-1
+  if(newdata[1] == 'Extinction Rate')`Extinction Rate`<-1
+  if(newdata[1] == 'Offspring Viability')`Offspring Viability`<-1
+  if(newdata[1] == 'Reproductive Success')`Reproductive Success`<-1
+
+  predict(model.fitness.components.REML, newmods=c(`Body Condition`, `Body Size`, `Development Rate`, `Early Fecundity`, `Ejaculate Quality and Production`, `Extinction Rate`, `Fitness Senescence`, Immunity, Lifespan, `Male Attractiveness`, `Mating Duration`, `Mating Frequency`, `Mating Latency`, `Mating Success`, `Mutant Frequency`, `Offspring Viability`, `Pesticide Resistance`, `Reproductive Success`, Strength))
+}
+# Get the predictions for each combination of moderators
+predictions.outcomes <- as.data.frame(expand.grid(Outcome = outcome.list.factor))
+predictions.outcomes <- cbind(predictions.outcomes, do.call("rbind", apply(predictions.outcomes, 1, get.predictions.outcomes))) %>%
+  select(Outcome, pred, se, ci.lb, ci.ub) 
+for(i in 2:5) predictions.complete[,i] <- unlist(predictions.complete[,i])
+
+colnames(predictions.outcomes) <- c("Fitness Component", "REML Prediction", "REML SE", "REML LCI", "REML UCI")
+predictions.outcomes <- format(predictions.outcomes, digits = 2)
+
+fitness.component.predictions <- fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% `row.names<-`(NULL) %>% format(digits = 2)
+
+left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component") %>% pander(split.table = Inf, digits = 2)
+
+```
+
+```{r}
+
 ```
@@
   ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
-  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
-  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
   guides(fill = guide_legend(reverse=T, override.aes = list(size = 4.5)))+
@@
 #Generate predictions without taxon utilising the previously described function
-
 get.predictions.complete2 <- function(newdata){
@@
   xlab("\nEffect Size (Hedges' g)")+
-  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
-  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  # scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  # scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
   scale_x_continuous(limits = c(-0.75, 1.5), breaks = c(-1, -.5, 0, 0.5, 1, 1.5))+
@@
   scale_x_continuous(limits = c(-2.1, 1.2), breaks = c(-2, -1.5, -1, -0.5, 0, 0.5, 1))+
-  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
-  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
 

### 2018-09-19 meta_analysis_sexual_selection_pop_fitness.Rmd
Hide_names add REML

@@
 title: 'Sexual selection improves population fitness: a meta-analysis'
-author: "Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
+author: #"Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
 subtitle: Supplementary Material
@@
 library(metaAidR)
+library(cowplot)
 source("I2_function.R") #Adapted function for obtaining I2 with CIs
@@
 We used the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) as a guide during this meta-analysis.
-The repository used to formulate this document can be found here: https://github.com/JustinCally/SexualSelection
+The repository used to formulate this document can be found here: **hidden for double-blid peer review**
 
@@
   select(Outcome, pred, se, ci.lb, ci.ub) 
-for(i in 2:5) predictions.complete[,i] <- unlist(predictions.complete[,i])
+for(i in 2:5) predictions.outcomes[,i] <- unlist(predictions.outcomes[,i])
 
@@
 left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component") %>% pander(split.table = Inf, digits = 2)
-
-```
-
-```{r}
 
@@
 predictions.variance <- format(predictions.variance, digits = 2)
-predictions.variance %>% pander()
+predictions.variance %>% pander(digits = 2)
 ```

### 2018-09-19 Manuscripts/Manuscript_MetaAnalysis.Rmd
Added Manuscripts

---
title: "Sexual selection improves population fitness: a meta-analysis"
author: 
- #Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
- 
- #'\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
output:
  pdf_document: default
  html_document: default
  word_document:
      pandoc_args: ["--smart"]
bibliography: Bibliography/Bibliography.bib
csl: Bibliography/NComms.csl
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual selection improves fitness} \usepackage{titlefoot}
  \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\onehalfspacing
abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict theoretically. A powerful means to test whether sexual selection increases or decreases population fitness is to manipulate the opportunity for sexual selection in two or more populations, allow evolution to proceed, and then compare the average fitness between the treatment groups. Here, we synthesise 459 effect sizes from 65 experimental evolution studies that tested for effects of sexual selection on adaptation. We find that sexual selection tends to elevate the mean and reduce the variance for many fitness traits; especially for females evolving under stressful conditions. We conclude that the beneficial population-level consequences of sexual selection are typically stronger than the harmful ones, and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments. We discuss the implications of these results for conservation and evolutionary biology.
---
<!-- \maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.} -->

\newpage
```{r, echo = F, warning=F, message = F}
library(knitr)
library(kableExtra)
library(dplyr)

```

Sexual selection, defined as selection resulting from competition for mates or their gametes[@RN139], is a ubiquitous evolutionary force that has profoundly shaped the natural world. As far back as Darwin[@RN310], researchers have theorised that sexual selection can change the average absolute fitness of individuals in a population (henceforth termed ‘population fitness’[@RN269; @RN268]). However, opinion is divided over whether the net effect on population fitness is positive or negative[@RN42; @RN25; @RN116; @RN95]. _Prima facie_, one might predict that sexual selection would have no effect on population fitness, since it does not matter which individuals of the faster-reproducing sex (typically males) succeed in mating, so long as some do[@RN142]. However, when genotypes with high mating or fertilisation success also have superior breeding values for traits that affect population fitness (e.g. survival, parental care, female fecundity, or success in interspecific competition), sexual selection is predicted to elevate population fitness by causing a correlated response in these other traits[@RN95]. In essence, the demographically-limiting sex (typically females) benefits from a gene pool that has been purged of harmful alleles through sexual selection on the non-limiting sex (typically males), with the benefit to population fitness potentially large[@RN94; @RN198; @RN58].

Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness (intralocus sexual conflict)[@RN187; @RN146; @RN237; @RN147]. Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males[@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care (interlocus sexual conflict)[@RN314; @RN276; @RN315]. Given these conflicting theoretical expectations and empirical results, it remains unclear whether sexual selection tends to have a net benefit or cost to population fitness[@RN42; @RN25; @RN116; @RN95].

Researchers have investigated the population-level consequences of sexual selection using a range of approaches including macro-evolutionary studies[@RN56; @RN51; @RN55], analysis of the fossil record[@RN270], quantitative genetics[@RN187; @RN200; @RN115; @RN254; @RN257] and especially experimental evolution. In particular, many experimental evolution studies have manipulated the intensity of sexual selection in captive populations, allowed evolution to proceed, and then measured population fitness components such as lifespan, fecundity, population extinction rate and mutation load. This approach facilitates direct measurement of the net effect of sexual selection on population fitness, at least in the specific populations and ecological conditions under study.

Theoretical and empirical work has highlighted a number of factors that affect the relationship between sexual selection and population fitness. For example, the genetic correlation between female fecundity and male mating/fertilisation success varies in sign and magnitude between species[@RN298] and even between conspecific populations[@RN201], implying that sexual selection on males increases mean female fitness in some species and populations but not others. These inconsistencies could derive from differences in allele frequencies, or environmental differences that alter how genotype relates to fitness. Importantly, several studies have hypothesised that populations should display a more positive genetic correlation between male and female fitness – and thus potentially between mating/fertilisation success and population fitness – in novel or fluctuating environments, relative to stable environments[@RN187; @RN173; @RN74; @RN257]. These predictions arise because stable environments create consistent selection, preferentially eroding genetic variation at sexually-concordant loci (i.e. loci where the fittest genotype is the same in both sexes) and leaving behind variation at sexually antagonistic loci. Although there are several systematic reviews of the effects of sexual selection on offspring fitness (see ref.[@RN183]), none that we know of have addressed whether sexual selection is more beneficial to population fitness in stressful conditions or novel environments, despite the relevance of this question to conservation biology.

Here, we synthesise the empirical literature on sexual selection and population fitness using formal meta-analysis. We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection, and then measured some fitness component, since these provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations. Our principle aims were to measure the average net effect of sexual selection on the population-level mean and variance for various fitness components, and to test whether this effect varies between stressful and benign environments.

#Results

##The effect size dataset

We retrieved 459 effect sizes from 65 studies. 94 effect sizes were collected from populations evolving under stressful conditions, while 335 were measured for those evolving in benign conditions. 189 of the effect sizes came from measurements made on males, 219 on females, and the remaining 51 from measurements of a mixed-sex sample of individuals. Most effect sizes in our dataset came from studies that manipulated sexual selection by completely removing it in one treatment via enforced random monogamy (*n* = 241); other effect sizes (*n* = 218) derived from alternative manipulations, such as changing the adult sex ratio. In total, we obtained effect sizes for 20 different fitness traits, with reproductive success (*n* = 156) and offspring viability (*n* = 56) being the most commonly-measured traits. We classified 216 effect sizes as direct measures of fitness, 147 as indirect, and the remaining 96 effect sizes as ambiguous (see Methods, Fig. 1 and Table S1). Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, reproductive success, offspring viability and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration and early fecundity). Tables S4-S5 give a detailed description of our dataset.

##Sexual selection is associated with higher mean values for most fitness components

The grand mean for all effect sizes was positive (REML $\beta$ = 0.23, 95 % CIs: 0.01 to 0.44, *p* = 0.038; Bayesian $\beta$ = 0.23, 95 % CIs: -0.06 to 0.51, $BF_{>0}$ = 18), indicating that sexual selection typically had a net positive effect on the majority of populations and fitness components so far studied. Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits. Sexual selection had a beneficial effect on most fitness traits, including all of the fitness traits that we classified as being ‘direct’ measurements of population fitness: extinction rate (REML $\beta$ = 0.37, 95 % CIs: 0.01 to 0.73; Bayesian $\beta$ = 0.37, 95 % CIs: -0.02 to 0.79, $BF_{>0}$ = 30.13; *n* = 4), offspring viability (REML $\beta$ = 0.20, 95 % CIs: 0.042 to 0.36; Bayesian $\beta$ = 0.21, 95 % CIs: -0.04 to 0.47, $BF_{>0}$ = 24.89; *n* = 56) and reproductive success (REML $\beta$ = 0.17, 95 % CIs: 0.013 to 0.32; Bayesian $\beta$ = 0.18, 95 % CIs: -0.06 to 0.44, $BF_{>0}$ = 15.53; *n* = 156; Fig. 1; Table S6). Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.49, 95 % CIs: -0.72 to -0.26; Bayesian $\beta$ = -0.49, 95 % CIs: -0.78 to -0.19, $BF_{>0}$ = 0.0054; *n* = 35) and body condition (REML $\beta$ = -1.3, 95 % CIs: -1.9 to -0.67; Bayesian $\beta$ = -1.3, 95 % CIs: -1.9 to -0.63, $BF_{>0}$ = 0.00025, *n* = 1). Fig. 1 presents Bayesian estimates for each fitness component and Table S6 contains both Bayesian and REML predictions with sample sizes and BF’s.

##The roles of environmental stress and sex

We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect fitness (Table 1, 2).  Sexual selection significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (e.g. a food source to which they were not well-adapted) than under benign conditions (Fig. 2a, Table 2). Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (Fig. 2a, Table 2). Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (Fig. 2a, Table 2). Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.

Other moderator variables that we examined had minimal impacts on effect size (Fig. S2 and Table S7). Specifically, effect size did not depend on whether or not the study was conducted blind (Fig. S9), nor on the number of generations for which the experimental evolution study was run (Fig. S10 and Fig. S11).

The effect size estimates we recovered were highly heterogeneous ($I^2$ = 94.9 %, 95 % CIs: 93 to 96%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208]. Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 61.5 %, 95 % CIs: 42.9 % to 78.9 %), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 33.5 %, 95 % CIs: 15.8 % to 52.7 %). The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model implied a non-zero effect ($\sigma^2$ = 0.145 [0.006-0.517]; Table S10). Variation among taxa is explored further in the Supplementary Material, (Figure S3 and Table S8).

##Sexual selection reduces phenotypic variance, for female traits in stressful environments

By applying meta-analysis to log coefficient of variation ratios (*lnCVRs*)[@RN177], we found that sexual selection reduces phenotypic variation under certain conditions (Fig. 2b). Specifically, phenotypic variance was significantly reduced by sexual selection for fitness components measured in females under stressful conditions (*lnCVR* = -1.0, 95% CIs: -1.4 to -0.69). By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (Fig. 2b; Tables S13-S16). However, as expected from the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.44, 95% CIs: -0.80 to -0.081; Fig. 2b).

As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 95.4 %, 95 % CIs: 93 % to 97.1 %). Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 40.1 %, 95 % CIs: 23.5 % to 60.2 %), fitness components ($I^2_{fitness\:components}$ = 38.7 %, 95 % CIs: 17.1 % to 60.7 %) and taxon ($I^2_{taxon}$ = 16.6 %, 95 % CIs: 3.1 % to 37.2 %).
<!-- We don't use Bayesian predictions for lnCVR, which is inconsistent with previous results -->

##Publication bias

The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (Fig. 3a; Egger’s test: *z* = 6.2, *p* < 0.0001). Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection. There was no significant relationship between effect size and journal impact factor (Fig. 3b; $t_{437}$ = 1.2, *p* = 0.25) or year of publication (Fig. 3c; $t_{437}$ = -1.0, *p* = 0.31); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured[@RN216; @RN217].

```{r, echo = FALSE, fig.cap="Forest plot showing the effect of manipulation of sexual selection, for 20 fitness components from 65 studies. Effect sizes (*n* = 459) varied between fitness components, and were more often positive than negative. Predicted average values are presented alongside each fitness component; those in bold have 95 % confidence intervals that do not cross zero. The estimates presented here are Bayesian predictions, which appear slightly more conservative than REML predictions (Table S6)."}
knitr::include_graphics("Figures/ForestPlot_edit3.pdf") #Not relative path
```

```{r, echo = FALSE, fig.cap="(**a**) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions. (**b**) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals. The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Tables S12 and S14). Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median."}
knitr::include_graphics("Figures/environment_variance_edit5.pdf") #Not relative path
```

```{r, echo = FALSE, fig.cap="Tests of publication bias are mixed and suggest publication bias may be present. (**a**) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies. (**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias. For (**b**) and (**c**) circle size is proportional to the weight (%) of the study, which is inversely proportional to the variance of the effect size."}
knitr::include_graphics("Figures/publicationbias.pdf") #Not relative path
```
\newpage

**Table 1:**Results for the multilevel meta-analysis model testing the effects of sexual selection in different environments and between sexes. Moderator variables whose 95% confidence intervals do not cross zero are shown in bold.
```{r, echo = F}
options(knitr.kable.NA = ' ')

table1 <- read.csv('table1.csv') %>% 
  mutate(
    Estimate = cell_spec(Estimate, "latex", bold = ifelse(LCI*UCI > 0, T, F)),
    Parameters = cell_spec(Parameters, "latex", bold = ifelse(LCI*UCI > 0, T, F))
  )

kable(table1, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
  kable_styling(latex_options = c("scale_down", "striped"), full_width = F) %>%
  row_spec(0, bold = TRUE) %>%
  group_rows("REML Model", 1, 6) %>%
  group_rows("Bayesian Model", 7, 12)
```

**Table 2:** Hypothesis tests using restricted maximum likelihood (REML) or Bayesian methods, illustrating how sex and environmental stress interact to modulate effect size. Tests whose 95% confidence intervals do not cross zero are shown in bold.
```{r, echo = F}
options(knitr.kable.NA = ' ')

table2 <- read.csv('table2.csv') %>% rename('Statistical Approach' = Statistical.Approach) %>%
  mutate(
    Estimate = cell_spec(Estimate, "latex", bold = ifelse(LCI*UCI > 0, T, F)),
    `Statistical Approach` = cell_spec(`Statistical Approach`, "latex", bold = ifelse(LCI*UCI > 0, T, F))
  )

kable(table2, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
  kable_styling(latex_options = c("scale_down"), full_width = F) %>%
  row_spec(0, bold = TRUE) %>%
  collapse_rows(columns = 1:2, latex_hline = "major")
```

\newpage

#Discussion

Our meta-analysis revealed that populations evolving under sexual selection often have higher values for multiple fitness traits, relative to populations where sexual selection was experimentally removed or weakened. Notably, sexual selection had small but beneficial effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced) and the proportion of viable offspring. Fitness traits related to immunocompetence were an exception: sexual selection typically resulted in weaker immunity. The negative effect on immunity is interesting in light of the hypothesised trade-off between sexually-selected phenotypes and immunity, for example due to immunosuppressive effects of sex hormones[@RN323; @RN324]. Furthermore, the overall benefit of sexual selection was greater for females than males and this sex difference was magnified in stressful environments. Consistent with stronger selection on female fitness under stress, female phenotypic variance was substantially reduced under these conditions. These results suggest that sexual selection may be a key factor in population persistence under stressful conditions, such as fluctuating environmental change[@RN173] or spatial variability[@RN189]. Under such conditions, female reproductive output often acts as the limiting factor in staving off extinction[@RN188].

The results of the meta-analysis support predictions that sexual selection can improve population fitness and hence aid adaptation[@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58]. Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been ‘purged’ of deleterious alleles through intense selection on males[@RN94; @RN198; @RN95]. What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males. Below we discuss possible explanations for this result, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection[@RN317; @RN318].

Firstly, the response of male fitness to sexual selection may be constrained in species where the heritability of male fitness is influenced by the sex determination system. Males are heterogametic in many of the species in our sample (e.g. in species with XY or XO sex determination systems); this can reduce father-to-son heritability relative to mother-to-daughter, since sons never inherit the larger sex chromosome from their fathers[@RN340; @RN262; @RN147; @RN263]. This imbalance of male phenotypes that depend on X-linked loci should slow adaptation relative to rapidly adapting female phenotypes[@RN263; @RN259]. However,  X-linkage is also likely to inflate the contribution of X-linked genes to fitness variance in the heterogametic sex. Under this view, X-linkage facilitates adaptation by increasing the efficacy of selection against recessive deleterious alleles and selection for rare (and recessive) beneficial alleles [@RN341; @RN339]. Given these countering viewpoints, there is no clear consensus on sex-based differences in heritability. For instance, a systematic review found no difference in mean heritability between male and female traits, however there was a male-biased skew in heritability of reproductive traits, which are more likely to be tied to fitness[@RN342]. Conversely, a recent GWAS in humans found a number of traits with higher heritability in females than males[@RN325].

Secondly, selection on males might be weaker than selection on females, resulting in slower adaptation following experimental manipulation of sexual selection. This explanation may initially seem implausible, because net selection on males is generally thought to be stronger than on females due to the cumulative effects of sexual and natural selection[@RN304; @RN303; @RN337; @RN338]. However, an oft-overlooked aspect is that selection might frequently be ‘softer’ on males and ‘harder’ on females[@RN319], because the local competitive environment is usually more important for males than it is for females. For instance, a mediocre male genotype can have high fitness provided it outcompetes its local rivals, while low-fitness female genotypes are likely to produce few offspring even when competing with other low-fitness females. Therefore, improvements in genetic quality should have stronger diminishing returns in males, possibly contributing to our finding that the genetic consequences of sexual selection lead to greater fitness benefits to females. Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the nature of selection, relative to expectations for large, natural populations[@RN322; @RN277; @RN112]. For example, many studies[@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then randomly mixed to create the next generation; this ensures that successful males simply needed to outcompete their rival(s) in the same sub-population, while successful females needed to outcompete all other females in the entire population.

Our results suggest that the greater benefit of sexual selection to females than males is magnified in stressful environments. Recent work has emphasised that environmental stress should reduce the strength of sexually antagonistic selection relative to selection that is concordant between sexes. Theoretical models reaching this conclusion[@RN67; @RN173] have been supported by empirical studies[@RN187; @RN74; @RN243]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress[@RN74]. However, other quantitative genetic studies have shown that stressful conditions do not always reduce sexual antagonism[@RN297; @RN200; @RN257]. Variation in effects of sexual selection in stressful environments may be due to potentially variable responses amongst taxa[@RN298] and environments. Notably, Connallon and Hall (2016)[@RN173] predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it. Our meta-analysis suggests that under directional selection generally imposed by environmental stress, sexual antagonism is likely dampened; allowing sexual selection to facilitate adaptation and persistence.

Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as commonly is the case for studies in ecology and evolution[@RN208]. Most of the heterogeneity was explained by ‘study’ and how fitness was measured (fitness component); whereas the taxon, number of generations and use of blinding showed less impact on effect size. Taxonomic diversity is limited in experimental evolution studies, which generally use lab-suitable invertebrates with similar mating systems and sex determination. However, a meta-analysis of macro-evolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates (fish, insects, birds, spiders, reptiles, mammals)[@RN165]. Despite this, taxonomic differences in the effects of sexual selection on fitness or patterns of diversity are often expected due to differences in mating systems[@RN277] and sex-determination systems[@RN262]. For example, mate choice is more prevalent in taxa with high levels of parental care[@RN196], affecting the strength and nature of sexual selection. Furthermore, male heterogametic taxa, including those commonly used in experimental evolution such as flies (Diptera), beetles (Coleoptera) and mice (Mammalia), are likely to have higher heritability of fitness from mothers to daughters. Our results – which show greater fitness effects accruing to females – align with this hypothesis.

Our findings have implications for fundamental and applied research. For example, the beneficial population-level consequences of sexual selection have been proposed as one possible resolution to the long-standing evolutionary puzzle presented by sexual reproduction[@RN309]. If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants that arise in their midst[@RN94; @RN308; @RN198]. Sexual selection is also important for conservation (reviewed in ref.[@RN25]) and captive breeding programs (reviewed in ref.[@RN117]). Within captive breeding programs, genetic diversity is often managed through the enforced monogamy of a strategically selected (genetically diverse) breeding pair[@RN117]. Captive breeding programs may benefit from allowing sexual selection of  ‘good genes’ or more compatible genes[@RN294], or by increasing maternal investment by females paired with ‘attractive’ males[@RN291; @RN292; @RN293]. Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution could reduce the genetic quality of the population, and potentially compromise its long-term persistence[@RN332; @RN331; @RN47; @RN333; @RN330]. Equally, our results support recent evidence that human activities that directly counteract sexual selection, such as selective harvesting of the largest or most ornamented males, can lower population fitness[@RN334]. Based on the weight of evidence from experimental evolution, we suggest that sexually-selected populations may be more resilient to environmental change, including anthropogenic environmental pressures, over relevant time scales.

#Materials and methods

##Literature search

We searched *ISI Web of Science* and *Scopus* on 9^th^ June 2017 for peer-reviewed, English language studies that manipulated the presence or strength of sexual selection using experimental evolution, and then measured some proxy of population fitness. A detailed list of search terms is given in the Electronic Supplementary Material (ESM).

After removing duplicates, we read the titles and abstracts of the remaining 1015 papers and removed those that did not fit our inclusion criteria (typically because they did not present primary experimental evolution data). This left 130 papers, for which we read the full text and applied the inclusion criteria outlined in the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) diagram (Fig. 4). Briefly, we included studies that 1) were conducted in a dioecious animal species, 2) experimentally manipulated the strength of sexual selection (e.g. via experimentally-enforced random monogamy or an altered sex ratio) for at least one generation, and 3) measured a trait that we judged to be a potential correlate of population fitness. This third criterion is the most subjective, because there is rarely enough data to determine whether a particular trait is (or is not) correlated with population fitness. We therefore relied on our best judgement when deciding what outcomes were correlated with population fitness. We categorised the fitness outcomes into three categories: ambiguous, indirect and direct (detailed in Table S1). Briefly, ambiguous measures of fitness were those that are reported to have an unclear or variable association with fitness (e.g. body size, mating duration and early fecundity). Indirect fitness components were those that are often used as a proxy of fitness but do not directly measure aspects of success in reproduction or population viability (e.g. lifespan, mating success and ejaculate quality/production). Finally, direct measures of fitness (reproductive success, offspring viability and extinction rate) are those that measure fitness through components of reproduction or long-term viability. The ESM describes why specific papers recovered in the literature search were included or excluded (Table S2).

Of the 130 papers subjected to detailed screening, 62 were excluded based on the PRISMA criteria (Fig. 4). Additionally, three papers presented insufficient information to calculate effect size. In these cases, we contacted the authors and attempted to obtain the missing data, with partial success. The final meta-analysis covered data from 65 papers.

##Data extraction

From each paper, we first attempted to extract the arithmetic means, standard deviations and sample sizes of each of the different treatment groups, which facilitate calculation of effect size (see below). Typically, there were two or three treatments, which varied in the strength of sexual selection. For some papers, summary statistics were not written down, but were presented in a figure such as a bar chart: in these cases, we extracted the data using *WebPlotDigitizer* v.3.12[@RN195]. If the treatment means were not reported (and the raw data were unavailable), we instead calculated effect size from test statistics comparing treatment means (*e.g.*, $F$, $t$, $z$ or $\chi^2$ values), which we used to estimate effect size using several formulae (see below).

Where possible, we extracted data for each independent replicate or experimental evolution line within a study; otherwise, we used pooled treatment means. For studies that repeatedly measured the same population across multiple generations, we only extracted data for the last reported generation.

In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see Table S3 and associated ESM). The moderators were selected due to their ready availability, and because we hypothesised that they might explain some of the observed heterogeneity in effect size. A key moderator was whether the environmental conditions that a population evolved under were stressful (*e.g.*, elevated mutation load, novel/sub-optimal food source, increased sub-lethal temperatures). Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), blinding of researchers to treatments and number of generations a treatment group underwent experimentally evolution. In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the ESM (Table S3).

```{r, echo = FALSE, fig.cap="Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets."}
knitr::include_graphics("Figures/PRISMA\ Chart.pdf ") #Not relative path
```

\newpage

##Effect size calculation

For each measurement of each pair of treatments, we estimated the standardised effect size Hedges’ *g*[@RN204]. Similar to Cohen’s *d*, Hedges’ *g* expresses the difference in means in terms of standard deviations (making it dimensionless), but it is more robust to unequal sampling and small sample sizes[@RN209]. For comparisons of extracted treatment means, we calculated Hedges’ *g* using the ``mes`` function in the *compute.es* R package[@RN179]. To calculate Hedges' *g* from test statistics, we used the ``fes``, ``chies``, and ``tes`` functions in the *compute.es* package (for $F$, $\chi^2$ and $t$ statistics, respectively). The ``propes`` function was used to calculate effect size from a difference in proportions; in two cases[@RN327; @RN329], a proportion was equal to one (producing infinite effect sizes), and so we subtracted one from the numerator when estimating Hedges’ g. In all cases, we selected a direction for the effect size calculation such that in our meta-analysis, negative effect sizes indicate that the removal of sexual selection was associated with higher fitness trait values, and positive effect sizes indicate higher fitness when sexual selection was elevated or left intact. We also inverted the sign of effect sizes pertaining to measurements that are expected to be negatively related to population fitness (e.g. parasite load, mutation load, extinction risk/rate, mating duration (females), mating latency (males), and rate of senescence). Because many of our 65 papers measured multiple fitness outcomes, studied multiple replicate populations, or had three or more sexual selection treatments, we calculated a total of 459 effect sizes.

For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*)[@RN177]. The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups[@RN177; @RN190], and so we were only able to calculate lnCVR for 356 of 459 comparisons.

##Meta-analysis models

Firstly, we obtained a weighted mean effect size (Hedges’ *g*) for the entire dataset using both Bayesian and restricted maximum likelihood (REML) approaches for completeness. The weighted mean was obtained by fitting a model with no fixed moderator variables, but fitness component (*e.g.*, body size, female fecundity), study and taxon as random/group-level effects. That is, we separately model correlations between different effect sizes sourced from the same study, taxon, or pertaining to the same fitness component, and account for these interdependencies when estimating the overall effect. Given the small number of phylogenetically diverse species, we did not utilise phylogenetic corrections within the models.

Secondly, we fixed fitness component as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the 20 fitness components, using the relevant ``predict`` functions for each of the ``R`` packages used (see below). Additionally, we report Bayes Factor ($BF$) values, which estimates the likelihood ratio that the respective effect size is greater than zero ($BF_{>0}$). Further details on model parameters can be found within the ESM.

Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g* and *lnCVR*) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed effects meta-analyses. These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (i.e. those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g n* = 336; *lnCVR n* = 277). We again fit study, fitness component, and taxon as random/group level effects. The effects of other moderators such as generations and blinding are explored in the ESM.

Meta-analyses fit by REML were implemented in the *metafor* ``R`` package (v. 2.0)[@RN212], while their Bayesian equivalents used the *brms* ``R`` package (v. 2.3.1)[@RN290] to specify and run models in the Stan programming language. The modelling approaches are detailed in the ESM including the use of weakly informative priors.

##Publication bias

We tested for publication bias via funnel plots, using Egger’s test to quantify plot asymmetry[@RN213; @RN214]. However, funnel plot asymmetry does not necessarily indicate publication bias; asymmetry can arise simply through between-study heterogeneity[@RN215]. Thus, we utilised several other methods for checking publication bias. We investigated whether the time-lag bias[@RN216] – where effect size magnitudes decrease over successive years – is present. Additionally, we assessed a potential source of publication bias through the correlation between effect size and journal impact factor[@RN217], which can arise if null or countervailing results are more difficult to publish. The Journal impact factor for each effect size at the time of publication was obtained using *InCites Journal Citation Reports*.

##Code and data availability

The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (**link hidden for double bind review**). The repository (**link hidden for double bind review**) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results.

#Acknowledgements
We are very grateful to Paco Garcia-Gonzalez for sharing a collection of literature that helped to guide our study, and to Tim Connallon for comments on the manuscript.

\newpage
# References
<div id="refs"></div>

### 2018-09-19 Manuscripts/Manuscript_MetaAnalysis.Rmd
Figure 3 Caption Update (was empty before)

@@
 library(dplyr)
-
 ```
@@
 
-```{r, echo = FALSE, fig.cap="Tests of publication bias are mixed and suggest publication bias may be present.
+```{r, echo = FALSE, fig.cap= "Tests of publication bias are mixed and suggest publication bias may be present.
 (**a**) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies.
@@
 ```
+
+<!-- Appears to be a problem having two captions -->
 \newpage

### 2018-09-24 meta_analysis_sexual_selection_pop_fitness.Rmd

@@
 library(brmstools)
-library(metaAidR)
+library(metaAidR) # install.packages("metaAidR")
 library(cowplot)
@@
 We used the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) as a guide during this meta-analysis.
-The repository used to formulate this document can be found here: **hidden for double-blid peer review**
+The repository used to formulate this document can be found here: **hidden for double-blind peer review**
 
@@
 
-This latter criterion is likely to be contentious, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness.
+Criterion 4 is somewhat subjective, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness.
 We therefore relied on our best judgement when deciding which studies to exclude (see **Table S1**).
@@
 
-**Table S1:** We classed each of the twenty fitness related outcomes into three broad groups of direct, indirect and ambiguous based on the established link with population fitness, the directionality of the measure.
-Here we detailed how these outcomes were measured in the studies of this meta-analysis.
-In the accompanying box we provide a legend to the references cited in the table.
-
- <br/><br/>
+**Table S1:** We classified each of the twenty fitness outcomes into three broad groups -- direct, indirect and ambiguous -- based on the established link with population fitness, the directionality of the measure.
+Here we detailed how these outcomes were measured in the primary studies.
+
 ```{r, warning=FALSE}
-outcome.descriptions <- read.csv('data/outcome.descriptions.csv', 
-                                 fileEncoding="UTF-8")
-kable(outcome.descriptions, "html") %>%
-  kable_styling() %>%
+read.csv('data/outcome.descriptions.csv', fileEncoding="UTF-8") %>%
+  kable("html") %>% kable_styling() %>%
   scroll_box(width = "100%", height = "500px")
 ```
-  <br/><br/> 
-<input type=button class=hideshow></input>
+<br></br>
+
+#### References for Table S1
 ```{r, warning=FALSE}
-outcome.references <- read.csv('data/references.tableS1.csv', 
-                                 fileEncoding="UTF-8")
-kable(outcome.references, "html") %>%
-  kable_styling() %>%
+read.csv('data/references.tableS1.csv', fileEncoding="UTF-8") %>%
+  kable("html") %>% kable_styling() %>%
   scroll_box(width = "100%", height = "250px")
 ```
-  <br/><br/>
-
-**Table S2:** An eligibility criteria was based on four features a study needed to include (discussed above), to be eligable for inclusion in the meta-analysis the study needed to satisfy all criteria.
-Here we applied a step-wise process to the studies that had their full-text read and excluded them when they first failed to meet the criteria.
-Additional notes documenting reasons behind exclusion were also taken.
- <br/><br/> 
-<input type=button class=hideshow></input>
-```{r}
-Eligibility.criteria <- read.csv('data/Eligibility Workbook(22.02).csv', 
-                                 fileEncoding="UTF-8")
-kable(Eligibility.criteria, "html") %>%
-  kable_styling() %>%
+<br></br>
+
+**Table S2:** A study was deemed eligible for inclusion in the meta-analysis if it met all four criteria discussed above (referred to by their numbers, 1-4, in this table).
+We went through these four criteria in a step-wise fashion, for each of the 130 studies for which we read the full text, and noted the first criterion that was failed (if any).
+The table provides notes on our inclusion/exclusion decisions.
+
+```{r}
+read.csv('data/Eligibility Workbook(22.02).csv', fileEncoding="UTF-8") %>%
+  kable("html") %>% kable_styling() %>%
   scroll_box(width = "100%", height = "500px")
 ```
+<br></br>
 
@@
  <br/><br/> 
-<input type=button class=hideshow></input>
-```{r}
-# Load the data and clean up the variable formats
-prelim.data <- read.csv('data/Preliminary data frame 22.2.18.csv')
-prelim.data$Study.ID <- prelim.data$Study.ID %>% factor()
-prelim.data$Group.ID <- prelim.data$Group.ID %>% factor()
-prelim.data$Environment <- prelim.data$Environment %>% relevel(ref="Unstressed")
-prelim.data$Sex <- prelim.data$Sex %>% relevel(ref="B")
-
-#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
-prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% relevel(ref="Indirect")
-prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% relevel(ref="NO")
-prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor() %>% relevel(ref="0")
-prelim.data$Post.cop <- prelim.data$Post.cop %>% factor() %>% relevel(ref="0")
-prelim.data$Blinding <- prelim.data$Blinding %>% factor()
-
-kable(prelim.data, "html") %>%
+```{r}
+# Load the data and format the variables
+full_dataset <- read.csv('data/meta_analysis_dataset.csv') %>%
+  mutate(Study.ID = factor(Study.ID),
+         Group.ID = factor(Group.ID),
+         Environment = relevel(factor(Environment), ref = "Unstressed"),
+         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"),
+         Pre.cop = relevel(factor(Pre.cop), ref = "0"),
+         Post.cop = relevel(factor(Post.cop), ref = "0"),
+         Blinding = factor(Blinding))
+
+kable(full_dataset, "html") %>%
   kable_styling() %>%
@@
 **Table S4:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
- <br/><br/> 
 ```{r message=FALSE, warning=FALSE}
-n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
-prelim.data %>% 
+n.blind.ones <- (sum(full_dataset$Blind == "Blind"))
+full_dataset %>% 
   summarise(
     Effect_sizes_.Totalq = n(), 
-    Publications = prelim.data$Study.ID %>% unique() %>% length(),
+    Publications = Study.ID %>% unique() %>% length(),
     Blind_experiments = n.blind.ones,
-    Effect_sizes_.Enforced_monogamyq = (sum(prelim.data$Enforced.Monogamy == "YES")),
-    Effect_sizes_.Ambiguousq = (sum(prelim.data$Outcome.Class == "Ambiguous")),
-    Effect_sizes_.Indirectq = (sum(prelim.data$Outcome.Class == "Indirect")),
-    Effect_sizes_.Directq = (sum(prelim.data$Outcome.Class == "Direct")),
-    Effect_sizes_.Stressfulq = (sum(prelim.data$Environment == "Stressed")),
-    Effect_sizes_.Benignq = (sum(prelim.data$Environment == "Unstressed")),         
-    Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
-    Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
-    Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
-    Different_species =  prelim.data$Species %>% unique() %>% length(),
+    Effect_sizes_.Enforced_monogamyq = (sum(Enforced.Monogamy == "YES")),
+    Effect_sizes_.Ambiguousq = (sum(Outcome.Class == "Ambiguous")),
+    Effect_sizes_.Indirectq = (sum(Outcome.Class == "Indirect")),
+    Effect_sizes_.Directq = (sum(Outcome.Class == "Direct")),
+    Effect_sizes_.Stressfulq = (sum(Environment == "Stressed")),
+    Effect_sizes_.Benignq = (sum(Environment == "Unstressed")),         
+    Effect_sizes_.Maleq = (sum(Sex == "M")),
+    Effect_sizes_.Femaleq = (sum(Sex == "F")),
+    Effect_sizes_.Both_sexesq = (sum(Sex == "B")),
+    Different_species =  Species %>% unique() %>% length(),
     Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
@@
  <br/><br/>
+
 **Table S5:** Table of fitness outcomes included in our meta-analysis by sex.
- <br/><br/> 
-```{r}
-Outcome_and_sex <- as.data.frame.matrix(table(prelim.data$Outcome, prelim.data$Sex))
+```{r}
+Outcome_and_sex <- as.data.frame.matrix(table(full_dataset$Outcome, full_dataset$Sex))
 colnames(Outcome_and_sex) <- cbind("Both", "Female", "Male")
-
 Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)
@@
 # Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
-prelim.data$Outcome_f = factor(prelim.data$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
+full_dataset$Outcome_f = factor(full_dataset$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
 
 # define upper and lower bounds
-prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
-prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))
-
-library(ggthemes)
-#Generate a plot
-p.meta <- prelim.data %>% 
+full_dataset$lowerci <- full_dataset$g - 1.96*(sqrt(full_dataset$var.g))
+full_dataset$upperci <- full_dataset$g + 1.96*(sqrt(full_dataset$var.g))
+
+p.meta <- full_dataset %>% 
   mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
@@
   ggplot(aes(y=reorder(AuthorYear, -g), x = g)) +
-
   scale_color_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
                      name = "Relationship\nto fitness")+
-
   scale_shape_manual(values=c(21,22,24))+
-
   scale_fill_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
                     name = "Relationship\nto fitness")+
-
   geom_errorbarh(aes(xmin = lowerci, 
@@
 
-### We can save the file in several vector graphics forms
-
-#ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 18, width = 12)
-
-# svg("figures/Big_forest_plot.svg", width=12, height=18)
-# p.meta
-# dev.off()
-# 
-# pdf("figures/Big_forest_plot.pdf", width=12, height=18)
-# p.meta
-# dev.off()
-
 p.meta
@@
 
-###Overall effect of sexual selection on fitness
+### Overall effect of sexual selection on fitness
 
@@
 The priors for ``brms`` are set from a weakly non-informative student t-distribution: ``student_t(3, 0, 10)``.
-Notew that narrowing the prior (e.g.
-standard normal distribution: ``normal(0,1)``) has negligible effects on the model results.
-
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
-grand.mean.bayes <- brm(g | se(SE)  ~ 1 #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
+We also tested that using a stronger prior (e.g.
+standard normal distribution: ``normal(0, 1)``) has negligible effects on the model results.
+
+#### Run the Bayesian meta-analysis to get the overall effect
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/grand.mean.bayes.rds")){
+  grand.mean.bayes <- brm(g | se(SE)  ~ 1 # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                           + (1|Study.ID)
@@
                           control = list(adapt_delta = 0.9999, max_treedepth = 15),
-                data = prelim.data %>% mutate(SE = sqrt(var.g)))
-
-saveRDS(grand.mean.bayes, "data/grand.mean.bayes.rds") #Save to avoid re-running during knit
-```
-
-```{r}
-#Inspect this for details of random/group level effects
+                          data = full_dataset %>% mutate(SE = sqrt(var.g)))
+
+  saveRDS(grand.mean.bayes, "data/grand.mean.bayes.rds") # Save to avoid re-running during knit
+}
 grand.mean.bayes <- readRDS("data/grand.mean.bayes.rds")
-
-#Run REML model 
+```
+
+#### Run the REML meta-analysis to get the overall effect
+```{r}
 forest.model <- rma.mv(g, var.g,
@@
                        method = "REML",
-                       data = prelim.data)
-
-#Manually imput bayesian results: brms model object difficult to extract from
-mean = c(forest.model$b, 0.23) #Values for Bayesian can be obtained from grand.mean.bayes model object
-LCI = c(forest.model$ci.lb, -0.06)
-UCI = c(forest.model$ci.ub, 0.51)
-Stat = c(forest.model$pval, 18.09) #BF can be obtained with: hypothesis(grand.mean.bayes, "Intercept > 0")
-grand.means.df <- data.frame(rbind(mean, LCI, UCI, Stat))
-colnames(grand.means.df) = c("REML", "Bayesian")
-grand.means.df %>% pander(digits = 2)
+                       data = full_dataset)
+```
+
+#### Inspect the effect sizes esimates from these two models
+
+These estimates are presented in the text of the Results section. The test statistic is either the p-value (REML) or Bayes factor comparing the effect size to zero (Bayesian).
+```{r}
+pander(data.frame(
+  Method = c("REML", "Bayesian"),
+  Grand_mean_effect_size_g = c(forest.model$b, summary(grand.mean.bayes)$fixed[,"Estimate"]),
+  Lower_95_CI = c(forest.model$ci.lb, summary(grand.mean.bayes)$fixed[,"l-95% CI"]),
+  Upper_95_CI = c(forest.model$ci.ub, summary(grand.mean.bayes)$fixed[,"u-95% CI"]),
+  Test_statistic = c(forest.model$pval, hypothesis(grand.mean.bayes, "Intercept > 0")$hypothesis$Evid.Ratio)), digits = 2) 
 ```
@@
 
-###Effect of Sexual Selection for different fitness components
+### Effect of Sexual Selection for different fitness components
 
 Instead of running individual models for each fitness component we can run a model with the fitness components as predictors.
-In this case we maintain all of our fitness components and include study.id as a group level effect (to account for within study correlations in effect size).
-Using the ``brms`` package we can run a Bayesian model and generate fitted values for each fitness component.
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
-model.fitness.components.bayes <- brm(g | se(SE)  ~ Outcome #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
+In this case we maintain all of our fitness components and include `study.id` as a group level effect (to account for within study correlations in effect size).
+Using the `brms` package we can run a Bayesian model and generate fitted values for each fitness component.
+
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/components.brms.rds")){
+  components.brms <- 
+    brm(g | se(SE)  ~ Outcome #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
         + (1|Study.ID)
@@
         control = list(adapt_delta = 0.999, max_treedepth = 15),
-                data = prelim.data %>% mutate(SE = sqrt(var.g)))
-
-make_text_summary(model.fitness.components.bayes) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander(split.cell = 40, split.table = Inf)
-
-saveRDS(model.fitness.components.bayes, "data/components.brms.rds") #Save to avoid re-running during knit
+        data = full_dataset %>% mutate(SE = sqrt(var.g)))
+
+  saveRDS(components.brms, "data/components.brms.rds") 
+}
+
+components.brms <- readRDS(file = "data/components.brms.rds")
+
+make_text_summary(components.brms) %>% 
+  add_significance_stars() %>% 
+  tibble::rownames_to_column("Model Parameter") %>% 
+  pander(split.cell = 40, split.table = Inf)
 ```
@@
 ```{r, warning = FALSE}
-components.brms <- readRDS(file = "data/components.brms.rds") #Avoid re-running model above
-
-#Expand grid for environment and sex
-brms.newdata <- as.data.frame(expand.grid(Outcome = unique(prelim.data$Outcome)))
-
-#Get average SE: useful if using predict, but not fitted
-av.se.g <- prelim.data %>% group_by(Outcome) %>% summarise(mean = mean(sqrt(var.g)))
+# Define new data for prediction
+brms.newdata <- as.data.frame(expand.grid(Outcome = unique(full_dataset$Outcome)))
+
+# Get average SE: useful if using predict, but not fitted
+av.se.g <- full_dataset %>% group_by(Outcome) %>% summarise(mean = mean(sqrt(var.g)))
 brms.newdata$SE <- av.se.g$mean
 
-#Add predictions/fitted values
-brms.predict <- fitted(components.brms, newdata = brms.newdata, re_formula = NA)
-brms.predict <- as.data.frame(brms.predict)
+# Find the fitted values (i.e. predictions from the linear mixed model fit by brms)
+brms.predict <- fitted(components.brms, newdata = brms.newdata, re_formula = NA) %>% as.data.frame()
 brms.predictions <- data.frame(brms.newdata$Outcome, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)
@@
 #Name columns
-colnames(brms.predictions) <- c("Fitness Component", "Bayes Pred.", "Bayes SE", "Bayes LCI", "Bayes UCI")
+colnames(brms.predictions) <- c("Fitness Component", "Bayes Prediction", "Bayes SE", "Bayes L_95_CI", "Bayes U_95_CI")
 
@@
 rownames(brms.predictions) <- NULL
-sample.sizes.outcomes <- as.data.frame(table(prelim.data$Outcome))
+sample.sizes.outcomes <- as.data.frame(table(full_dataset$Outcome))
 colnames(sample.sizes.outcomes) <- c("Fitness Component", "n")
@@
 
-#Obtain Bayes Factor of likelihood that the outcome is greater than 0
+# Obtain Bayes Factor of likelihood that the outcome is greater than 0
 BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
-#Obtain BF for all components
+# Obtain BF for all components
 Hypotheses <- list()
@@
 for (i in BF.outcome.list){
-Hypotheses[[i]] <- hypothesis(components.brms, paste("Intercept + Outcome",i," > 0", sep = ""))
+  Hypotheses[[i]] <- hypothesis(components.brms, paste("Intercept + Outcome", i," > 0", sep = ""))
   BFs[[i]] <- Hypotheses[[i]][["hypothesis"]][["Evid.Ratio"]]
-} #Loop for all fitness compoinents
-
-#Now for REML
+} #Loop over all fitness compoinents
+
+# Now for REML. Not easy because the predict function for rma.mv has an odd interface
 model.fitness.components.REML <- rma.mv(g, var.g, mods = ~ 1 + Outcome,
@@
                          method = "REML",
-                         data = prelim.data)
+                         data = full_dataset)
 
@@
 left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component") %>% pander(split.table = Inf, digits = 2)
-
 ```
@@
 
-### Models With Many Covariates
+### Meta-analyses including many moderator variables
 
 We collected data from fitness components that were deemed ambiguous as well as unambiguous.
-The ambiguous outcomes are likely to add in heterogeneity to the models and may not help us in answering questions of the fitness effects of sexual selection.
+The ambiguous outcomes are likely to add heterogeneity to the models and may not help us in answering questions of the fitness effects of sexual selection.
 A REML model utilising our complete dataset with many moderator variables would thus be:
 
-<input type=button class=hideshow></input>
 ```{r}
 model.preliminary <- rma.mv(g, var.g, 
-                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + log(Generations) + Blinding, # << ----- Add big model, then cull predictors to this one
+                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + log(Generations) + Blinding, 
                          random = list(~ 1 | Study.ID, 
@@
                          method = "REML", 
-                         data = prelim.data)
+                         data = full_dataset)
 
@@
 <br></br>
+
 Here we can also run a Bayesian model alongside the REML model (metafor). The _R^2^_ for this model is 0.36 (95% CIs = 0.33-0.4). 
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
-#Also use bayesian model
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/brms.preliminary.rds")){
   brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
@@
                 control = list(adapt_delta = 0.999, max_treedepth = 15),
-                data = prelim.data %>% mutate(SE = sqrt(var.g)))
-
-```
-<br></br>
-<input type=button class=hideshow></input>
-```{r}
-brms.preliminary <- readRDS(file = "data/brms.preliminary.rds") #Avoid re-running model above
+                data = full_dataset %>% mutate(SE = sqrt(var.g)))
+  saveRDS(brms.preliminary, file = "data/brms.preliminary.rds") 
+}
+brms.preliminary <- readRDS(file = "data/brms.preliminary.rds") # Avoid re-running model above
+```
+<br></br>
+
+```{r}
 #Plot model results
@@
 
-make_text_summary(brms.preliminary) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
+make_text_summary(brms.preliminary) %>% 
+  add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
 ```
@@
 
-From these models we can see that there are several redundant moderators: Blinding and Generations show little effect and are not key to our research question (like sex and environment are).
-However, because taxa is a likely source of heterogeneity and effect size could reasonably be expected to differ between taxa, we investigate taxa as a fixed effect.
+From these models we can see that the moderators `Blinding` and `Generations` have little effect on effect size, and they are also tangential to our research question (unlike e.g.
+`sex` and `environment`).
 
@@
 
-### Sexual Selection Amongst Taxa
-
-First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding).
-Notably, with the ambiguous measures included we already see a positive effect of sexual selection and thus removing these fitness components is not an attempt to obtain a significant answer, rather it restricts the data to traits that are less contentious and thus we believe this approach is conservative.
-In this model we use Sex, Environment, Taxon and the interaction between sex and environment.
-
-<input type=button class=hideshow></input>
+### Restricted analysis to just the higher-quality data
+
+The models and plots above all use the full dataset (called `full_dataset` in the R code).
+However, some of the variables included in that dataset are not clearly related to population fitness (these were scored as "Ambiguous" in the "Outcome.Class" column), or it was unclear whether the environmental conditions could be termed "Stressful" or "Benign".
+To check whether our findings are robust to the inclusion of the ambiguous results, and to properly evaluate the effects of environmental stress, we next restricted the dataset to exclude these unclear cases (called `strict_dataset` in the R code).
+We also focus on the model containing the fixed effects Sex, Environment, Taxon and the interaction between sex and environment, as these are key to our research question.
+
 ```{r, message=FALSE, error = FALSE, warning=FALSE}
-#Restrict the dataset for unambiguous outcomes and environments 
-restricted.data <- prelim.data %>% 
+strict_dataset <- full_dataset %>% 
   filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>% 
-  mutate(Sex = as.character(Sex), 
-         Environment = as.character(Environment), 
-         Outcome.Class.2 = as.character(Outcome.Class), 
-         Enforced.Monogamy = as.character(Enforced.Monogamy))
-
-# Make sure the factors are leveled in the same order as we write our prediction function (below)
-restricted.data$Environment <- restricted.data$Environment %>% factor() %>% relevel(ref="Unstressed")
-restricted.data$Sex <- restricted.data$Sex %>% factor() %>% relevel(ref="M")
-restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
-restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Beetle") 
-restricted.data$Outcome <- restricted.data$Outcome %>% factor()
+  mutate(Sex = relevel(Sex, ref = "M"),
+         Environment = relevel(Environment, ref = "Unstressed"),
+         Taxon = relevel(Taxon, ref = "Beetle"),
+         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))
 
 model.complete <- rma.mv(g, V = var.g, 
-                         mods = ~ 1 + Sex * Environment + Taxon, # << ----- Add big model, then cull predictors to this one
+                         mods = ~ 1 + Sex * Environment + Taxon, 
                          random = list(~ 1 | Study.ID, 
@@
                          method = "REML", 
-                         data = restricted.data)
+                         data = strict_dataset)
 
@@
 
-The result is a model with estimates for various taxa, species, sexes and environments.
-To make sense of these estimates we should obtain average predictions for each moderator variable class of interest.
-We can do that by using a modified version version of a function used by @Holman_2018.
-Here it alows us to cluster predictions for the different moderators of interest: Sex, environment, taxon etc.
-This is done by obtaining predictions using the base ``predict()`` function for the ``rma.mv()`` objects that have been previously created
+The result is a model with estimates for various taxa, species, sexes and environments. We again write a function to predict the average effect size for each sub-group in the data.
+
 ```{r, warning=FALSE, fig.height= 8, fig.width=8}
@@
 
-countpred = count_(restricted.data, c("Sex", "Environment", "Taxon"))
-
+countpred <- count_(strict_dataset, c("Sex", "Environment", "Taxon"))
 predictions.complete <- left_join(predictions.complete, countpred, by = c("Sex", "Environment", "Taxon"))
-
-countpred = count_(restricted.data, c("Sex", "Environment", "Taxon"))
-
+countpred <- count_(strict_dataset, c("Sex", "Environment", "Taxon"))
 predictions.complete <- left_join(predictions.complete, countpred, by = c("Sex", "Environment", "Taxon"))
 
-#Thirdly, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.
+# plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.
 
@@
 
-Given that none of categories of taxa significantly impact effect size, and many categories are unsamples (Table S8) we can incorporate them as random/group level effects in models henceforth.
+Given that none of the levels of `Taxon` have a particularly strong impact on effect size, and many categories are incompletely sampled with regards to Sex and Environment (Table S8), we elected to treat `Taxon` as a random/group level effect in all subsequent models.
 
@@
 
-###REML: Effects of Environment and Sex
-
-Here we ask two key questions: Does sexual selection benefit populations in stressful environments more than benign environments? **AND** Do the benefits of sexual selection differ between the sexes?
-
-```{r}
-#We can run a model where the outcome is crossed with study (Study.ID) and Taxon as random effects and environment, sex and their interactions are fixed effects.
+### REML: Effects of Environment and Sex
+
+Here we ask two key questions: Does sexual selection benefit populations in stressful environments more than benign environments?
+**AND** Do the benefits of sexual selection differ between the sexes?
+The only difference to the previous model is that `Taxon` is now treated as a random effect.
+
+```{r}
 model.complete2 <- rma.mv(g, V = var.g, 
@@
                           method = "REML", 
-                          data = restricted.data)
+                          data = strict_dataset)
 summary(model.complete2, digits = 2)
@@
 
-We conducted hypothesis tests on the above model to investigate the effective difference between two groups.
-Depending on the package this method is also refered to as linear hypothesis or anova (metafor).
+Next, we conducted planned contrasts on `model.complete2` to investigate the difference in effect size between groups, using the anova method from `metafor`.
 
 **Table S9** Using the ``anova.rma`` function we can conduct hypothesis tests between two categorical groups in the model.
-Here we conduct 5 tests testing relative effects of sexual selection between the sexes and in different environments.
+Here we conduct 5 tests comparing the relative effect of sexual selection between the sexes, and in different environments.
 
@@
 <br></br>
-From these anovas we see that a stressful environment leads to a significantly greater increase in fitness components for "female"" but NOT "both" sexes, while significantly decreasing male fitness.
-We also see there is a difference between the sexes in stressful environments (females with larger mean) but not in benign environments (marginal).
 
@@
 
-###Bayesian: Effects of Environment and Sex
-
-We can run a Bayesian model using the ``brms`` package.
-The model has the same moderators as the REML approach used above.
-The ``brms`` package sets standard priors that are selected to be 'weakly informative'.
-The _R^2^_ of this Bayesian model was 0.35 (95% CIs = 0.31-0.39).
-Additionally, we can obtain the distribution of posterior fitted values and examine the model summary
-
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
-#Use brms to create a model similar to the one used in the REML approach. 
-brms.complete2 <- brm(g | se(SE)  ~ 1 + Sex * Environment #se(SE, sigma = TRUE) gives differnt results
-                + (1|Taxon) #group level effect #1
-                + (1|Study.ID) #group level effect #2
-                + (1|Outcome), #group level effect #3 
+### Bayesian model: Effects of Environment and Sex
+
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/brms.complete2.rds")){
+  brms.complete2 <- brm(g | se(SE)  ~ 1 + Sex * Environment 
+                        + (1|Taxon) 
+                        + (1|Study.ID) 
+                        + (1|Outcome), 
                         family = "gaussian", 
                         seed = 1,
-                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                        cores = 4, chains = 4, iter = 4000, 
                         control = list(adapt_delta = 0.9999, max_treedepth = 15),
-                data = restricted.data %>% mutate(SE = sqrt(var.g)))
-
+                        data = strict_dataset %>% mutate(SE = sqrt(var.g)))
+  saveRDS(brms.complete2, file = "data/brms.complete2.rds")
+}
+brms.complete2 <- readRDS(file = "data/brms.complete2.rds") 
 ```
@@
 ```{r}
-brms.complete2 <- readRDS(file = "data/brms.complete2.rds") #Avoid re-running model above
-
-#You can obtain a posterior sampling through the ``fitted.brmsfit`` function, which gives the same posterior values as doing it manually (see below).**Note that the fitted values obtained here have much smaller error than the predict values**
-
-# #obtain average variance of each group in the prediction
-# av.var.g <- as.numeric(c(restricted.data %>% filter (Sex == 'M' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
-#               restricted.data %>% filter (Sex == 'B' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
-#               restricted.data %>% filter (Sex == 'F' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
-#               restricted.data %>% filter (Sex == 'M' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
-#               restricted.data %>% filter (Sex == 'B' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
-#               restricted.data %>% filter (Sex == 'F' & Environment == "Stressed") %>% summarise(mean = mean(var.g))))
-
-#Expand grid for environment and sex
-# brms.newdata <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
-#                            Environment = c("Unstressed", "Stressed")))
-# #Add variance
-# brms.newdata$var.g <- av.var.g
-# 
-# #Add predictions
-# brms.predict <- fitted(meta.brms, newdata = brms.newdata, re_formula = NA)
-# brms.predict <- as.data.frame(brms.predict)
-# brms.predictions <- data.frame(brms.newdata$Sex, brms.newdata$Environment, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)
-# 
-# #Name columns
-# colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI")
-
-#Alternatively you can obtain posterior samples manually.
+# lternatively you can obtain posterior samples manually.
 post <- (posterior_samples(brms.complete2, 
@@
 
-#Obtain posterior fitted values and transform
-# posterior_fit <- data.frame(t(posterior_linpred(meta.brms, newdata = brms.newdata, re_formula = NA)))
-
-#Add columns for Environment and Sex
+# Add columns for Environment and Sex
 post <- as.data.frame(t(post))
@@
 <br></br>
-Like with the REML approach, from these model results we can test several hypotheses between the categories of environment and sex.
 
@@
 
-countpred <- count_(restricted.data, c("Sex", "Environment"))
+countpred <- count_(strict_dataset, c("Sex", "Environment"))
 
@@
         legend.text = element_text(size=16), 
-        legend.title=element_text(size=16, 
-                                  face = "bold"),
+        legend.title=element_text(size=16, face = "bold"),
         axis.title.x = element_text(hjust = 0.5, size = 14),
@@
   geom_errorbarh(data = predictions.complete2 %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
-                 aes(x= Prediction, xmin = predictions.complete2$CI.lb,
+                 aes(xmin = predictions.complete2$CI.lb,
                      xmax = predictions.complete2$CI.ub, y = Environment,
@@
 
-  scale_y_discrete(expand=c(0.075,0))
-
-# svg("figures/both_plot.svg", width=6, height=6)
-# both.plots
-# dev.off()
-# #
-# pdf("figures/both_plot.pdf",  width = 6, height = 6)
-# both.plots
-# dev.off()
+  scale_y_discrete(expand=c(0.075, 0))
 
@@
 ```{r}
-I2(model.complete2, restricted.data$var.g) %>% pander(digits = 3)
+I2(model.complete2, strict_dataset$var.g) %>% pander(digits = 3)
 ```
@@
 
-##Meta-Analysis on Variance
-
-###Obtaining lnCVR and Meta-Analysis Models
+## Meta-Analysis on Variance
+
+### Obtaining lnCVR and Meta-Analysis Models
 
@@
 # Firstly, we setup our calculation by creating a a restricted dataset with only unabmiguous fitness outcomes and running the functions developed by Nakagawa et al. 2015: 
-Calc.lnCVR<-function(CMean, CSD, CN, EMean, ESD, EN){
-
-	ES<-log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
-
+Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN){
+	ES <- log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
 	return(ES)
@@
 
-#for variance of lnCVR
-
-Calc.var.lnCVR<-function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T){
+# Function to find the variance of lnCVR
+# Equal.E.C.Corr = T assumes that the correlaiton between mean and sd (Taylor's Law) is equal for the mean and control groups
+Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr = TRUE){
 
@@
 
-		mvcorr<-cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate
-
-		S2<- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
+		mvcorr <- cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate
+
+		S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
 
@@
 
-		S2<- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
+		S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
 
@@
 	return(S2)
-
 }
@@
 #Calculate lnCVr and var.lnCVr
-#for lnCVR
-restricted.data$lnCVr <- Calc.lnCVR(restricted.data$mean.low, restricted.data$sd.low, restricted.data$n.low, restricted.data$mean.high, restricted.data$sd.high, restricted.data$n.high)
-
-#for variance in lnCVR
-restricted.data$var.lnCVr <- Calc.var.lnCVR(restricted.data$mean.low, restricted.data$sd.low, restricted.data$n.low, restricted.data$mean.high, restricted.data$sd.high, restricted.data$n.high, Equal.E.C.Corr=T) #Equal.E.C.Corr = T assumes that the correlaiton between mean and sd (Taylor's Law) is equal for the mean and control groups
-
-restricted.data2 <- restricted.data 
-```
-
-Although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously, that way we retain the same methodology in model structure and test the same hypotheses.
-This can be done be utilising the same predict function but for lnCVR and var.lnCVR.
-For the brms model we can obtain predictions manually or through the ``fitted.brmsfit``.
-
-Multilevel-model using lnCVR and REML:
+strict_dataset$lnCVr     <- with(strict_dataset, Calc.lnCVR (mean.low, sd.low, n.low, mean.high, sd.high, n.high))
+strict_dataset$var.lnCVr <- with(strict_dataset, Calc.var.lnCVR (mean.low, sd.low, n.low, mean.high, sd.high, n.high))
+```
+
+#### Meta-analysis of lnCVR using REML
 
@@
                                         ~ 1 | Outcome), 
-                         method = "REML", data = restricted.data2)
+                         method = "REML", data = strict_dataset)
 summary(variance.model, digits = 2)
@@
 
+#### Bayesian meta-analysis of lnCVR
 Again, we use ``brms`` to obtain Bayesian model estimates. For this model the _R^2^_ is 0.34 (95% CIs = 0.32-0.36).
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
-#When knitting this markdown this model stalls
-#Use brm to create a model similar to the one used in the REML approach. 
-variance.brms <- brm(lnCVr| se(SE.v)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (SE), sex, environment and their interaction are moderators
-                + (1|Taxon) #group level effects
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/variance.brms.rds")){
+  variance.brms <- brm(lnCVr| se(SE.v)  ~ 1 + Sex * Environment 
+                + (1|Taxon) 
                 + (1|Study.ID)
                 + (1|Outcome),
-                family = "gaussian", #default
+                family = "gaussian", 
                 seed = 1,
-                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
+                cores = 4, chains = 4, iter = 4000, 
                 control = list(adapt_delta = 0.999, max_treedepth = 15),
-                data = restricted.data2 %>% mutate(SE.v = sqrt(var.lnCVr)))
-```
+                data = strict_dataset %>% mutate(SE.v = sqrt(var.lnCVr)))
+  saveRDS(variance.brms, "data/variance.brms.rds")
+}
+var.brms <- readRDS(file = "data/variance.brms.rds") #Avoid re-running model above
+```
+
 **Table S13** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
 ```{r}
-var.brms <- readRDS(file = "data/variance.brms.rds") #Avoid re-running model above
 post.variance <- (posterior_samples(var.brms, 
@@
 
-make_text_summary(var.brms) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
+make_text_summary(var.brms) %>% 
+  add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
 ```
@@
 
-countpred = count_(restricted.data2, c("Sex", "Environment"))
+countpred <- count_(strict_dataset, c("Sex", "Environment"))
 
@@
 
-var.plot.posterior <- post.variance %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
+var.plot.posterior <- post.variance %>% 
+  mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% 
+  ggplot() +
   stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
@@
 both.var.plots <- var.plot.posterior +
-  geom_errorbarh(data = predictions.variance %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
-                 aes(x = Prediction, xmin = predictions.variance$CI.lb, 
+  geom_errorbarh(data = predictions.variance %>% 
+                   mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+                 aes(xmin = predictions.variance$CI.lb, 
                      xmax = predictions.variance$CI.ub, y = Environment,
@@
                  height = 0, position = pd, show.legend = F) +
-  geom_point(data = predictions.variance %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+  geom_point(data = predictions.variance %>% 
+               mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
              aes(x = Prediction, y = Environment, size=n, fill = Sex), 
@@
   scale_size(guide = 'none')+  
-
   scale_y_discrete(expand=c(0.075,0))
-
-# svg("figures/both.var.plots.svg", width=6, height=6)
-# both.var.plots
-# dev.off()
-# 
-# pdf("figures/both.var.plots.pdf",  width = 6, height = 6)
-# both.var.plots
-# dev.off()
 
@@
 
-###Hypothesis Tests For Phenotypic Variation Model
-
-Like we did for Hedges g' we can also conduct hypothesis tests between categorical groups to inform us if there is a difference between two groups of interest (e.g.
-females in benign and females in stressful environments).
-Here we present Bayesian and REML hypothesis predictions.
+### Hypothesis tests For models of lnCVR
+
+As we did for Hedges' $g$, we here conduct hypothesis tests between categorical groups, to identify groups that differ significantly in how much sexual selection affects the phenotypic variance.
 Positive values indivate the first term in the hypothesis is larger (which would be male for rows 1-2 or benign for rows 3-5).
@@
 ```{r}
-I2(variance.model, restricted.data2$var.g) %>% pander(digits = 3)
+I2(variance.model, strict_dataset$var.g) %>% pander(digits = 3)
 ```
@@
 
-##Publication Bias
-
-###Funnel plots and Egger's Test
+## Publication Bias
+
+### Funnel plots and Egger's Test
 
@@
                       mods = ~ Sex * Environment, 
-                      data=prelim.data)
+                      data = full_dataset)
 regtest(standard.model)
@@
 
-We can use ggplot for creating a funnel plot. The outline taken from is taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
+We can use ggplot to create a nice funnel plot. The following code takes inspiration from [John K. Sakaluk](https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/).
 
 ```{r, fig.height= 6, fig.width=8, warning=FALSE, message=FALSE}
-
 #Using residuals for the funnel plot means that we need to generate residuals (intercept only)
-
 forest.model <- rma.mv(g, var.g,
@@
                        method = "REML",
-                       data = prelim.data)
+                       data = full_dataset)
 
 # Obtain residuals
-resstandards <- (rstandard.rma.mv(forest.model,
-                                   type="response"))
+resstandards <- rstandard.rma.mv(forest.model, type = "response")
 
@@
 # Create new df with residuals replacing raw
-df.forest.model <- prelim.data
+df.forest.model <- full_dataset
 df.forest.model$g <- resstandards$resid + grand.mean 
@@
 
-  apatheme <- theme_bw() +  #My APA-format theme
+  apatheme <- theme_bw() +  
     theme(panel.grid.major = element_blank(),
@@
 
-  estimate <- model$b
+  estimate <- model$b %>% as.numeric()
   SE <- model$se
@@
     geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
-    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotdash', data=dfCI, colour = "tomato",size =0.75) +
+    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotdash', data=dfCI, colour = "tomato", size =0.75) +
     geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotdash', data=dfCI, colour = "tomato",size=0.75) +
     scale_x_reverse() +
-    # scale_y_continuous(breaks = seq(-1.25,2,0.25)) + #Choose values that work for you based on your data
     coord_flip() +
@@
 funnel.plot
-
-# svg("figures/funnel_plot.svg", width=8, height=6)
-# funnel.plot
-# dev.off()
-```
-<br></br>
-**Figure S5:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.2210, p < .0001).
-The asymmetry appears to be sourced from a spread of positive effect sizes outside the funnel and of varying degrees of precision.
+```
+<br></br>
+**Figure S5:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001).
+The asymmetry appears to come from a spread of positive effect sizes outside the funnel and of varying degrees of precision.
 Counter to expectations of publication bias these positive studies are not just 'low precision, large effect' results.
-Funnel plot asymmetry may also be due to heterogeneity, which in this study is high due to the many species and outcomes measured.
-
-###Journal Impact Factor
+Funnel plot asymmetry may also be due to genuine heterogeneity in effect sizes between studies, which is high in the present meta-analysis because it covers many species, outcome measurements, and experimental designs.
+
+### Journal Impact Factor
 
@@
 ```{r, fig.height= 4, fig.width=8, warning=FALSE}
-
-JIF.plot <- ggplot(data = prelim.data, aes(x=JIF, y=g))+
-  geom_jitter(color='darkgreen', alpha=0.4, aes(size = (1/(var.g))/sum((1/(var.g)))*100), show.legend = FALSE)+
+JIF.plot <- ggplot(data = full_dataset, aes(x=JIF, y=g))+
+  geom_jitter(color='darkgreen', alpha = 0.4, aes(size = 1 / var.g), show.legend = FALSE)+
   geom_hline(yintercept=0, linetype = 'dotted')+
   geom_smooth(method='lm', color='black', linetype="solid")+
-  scale_x_log10(limits = c(-5,40), breaks = c(0, 1, 2, 5, 10, 20, 40))+
+  scale_x_log10(limits = c(-5, 40), breaks = c(0, 1, 2, 5, 10, 20, 40))+
   labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Journal Impact Factor (logarithmic scale)')+ 
-
   theme_bw()+
-
   theme(panel.spacing = unit(0.5, "lines"),
@@
         legend.text = element_text(size=12),
-        legend.title=element_text(size=12,
-                                  face = "bold"),
+        legend.title=element_text(size=12,face = "bold"),
         axis.title.x = element_text(size = 12),
@@
 
-# dev.off()
-# 
-# svg("figures/JIF_Plot.svg", width=4, height=4)
-# JIF.plot
-# dev.off()
-
 JIF.plot
-
-```
-<br></br>
-**Figure S6:** Journal impact factor does not show a noticable correlation with effect size.
-The positive slope shown here is due to several effect sizes published in a high impact journal.
-Most papers were published in discipline specific journals such as _Evolution_ and _Journal of Evolutionary Biology_.
-Circle size is proportional to weight (%) of study.
-
-We can test the effect of JIF on ES with a simple linear model: 
-```{r}
-JIFlm <- lm(g ~ log(JIF), data = prelim.data)
+```
+<br></br>
+**Figure S6:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
+
+Testing the effect of JIF on effect size with a simple linear model (slope = +0.1, p = 0.25): 
+```{r}
+JIFlm <- lm(g ~ log(JIF), data = full_dataset)
 summary(JIFlm)
 ```
-
-This shows that JIF does not have a significant effect on effect sizes from the published study
 
@@
 ```{r, fig.height= 4, fig.width=8, warning=FALSE}
-time.plot <- prelim.data %>% 
+time.plot <- full_dataset %>% 
   ggplot(aes(x=Year, y=g))+
@@
 time.plot
-
-# svg("figures/Time_Plot.svg", width=4, height=4)
-# time.plot
-# dev.off()
-```
-<br></br>
-**Figure S7:** The effect size dataset shows little to no signs of the time-lag bias as the average effect sizes from published studies remains consistent across the previous two decades.
-Circle size is proportional to weight of study (%).
-
-We can also test the effect of publication year on ES with a simple linear model (similar to the one for JIF: 
-```{r}
-Yearlm <- lm(g ~ Year, data = prelim.data)
+```
+<br></br>
+**Figure S7:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
+Point size is proportional to the precision of the effect size.
+
+Again, a linear model for the regression line in the plot shows no effect (slope = -0.007, p = 0.3):
+```{r}
+Yearlm <- lm(g ~ Year, data = full_dataset)
 summary(Yearlm)
@@
 
-This shows that publication year does not have a significant effect on effect sizes from the published study.
-
 ________________
 
-##Other Moderators
+## Other Moderators
 
@@
 blind.plot <- df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
-  geom_boxplot(outlier.shape = NA)+
-  geom_jitter(aes(fill=Blinding, size = (1/(var.g))/sum((1/(var.g)))*100), shape=21, color='grey20')+
+  geom_jitter(aes(fill=Blinding, size = 1/var.g), shape=21, color='grey20')+
+  geom_boxplot(outlier.shape = NA, fill = NA)+
   geom_hline(yintercept=0, linetype = 'dotted') + 
@@
         legend.text = element_text(size=12),
-        legend.title=element_text(size=12,
-                                  face = "bold"),
+        legend.title=element_text(size=12, face = "bold"),
         axis.title.x = element_text(size = 12),
@@
 
-#ggsave(plot = blind.plot, filename = "figures/blind_plot.eps", height = 6, width = 8)
+# ggsave(plot = blind.plot, filename = "figures/blind_plot.eps", height = 6, width = 8)
 blind.plot
@@
 ```{r, fig.height= 6, fig.width=8, warning=FALSE}
-generations.plot <- restricted.data %>% ggplot(aes(x=Generations, y=g))+
+generations.plot <- strict_dataset %>% ggplot(aes(x=Generations, y=g))+
   geom_jitter(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
@@
 
-# svg("figures/Generations_Plot.svg", width=10, height=7.5)
-# generations.plot
-# dev.off()
-
 generations.plot
@@
 **Figure S10:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
-<br></br>
+
 A linear model shows next to no effect of generations on effect size: 
 ```{r}
-summary(lm(g ~ Generations, data = restricted.data))
+summary(lm(g ~ Generations, data = strict_dataset))
 ```
@@
 ```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
-generations.plot.var <- restricted.data2 %>% ggplot(aes(x=Generations, y=lnCVr))+
+generations.plot.var <- strict_dataset %>% ggplot(aes(x=Generations, y=lnCVr))+
   geom_jitter(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
@@
 ```
-
+<br></br>
 **Figure S11:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
@@
 ```{r}
-summary(lm(lnCVr ~ Generations, data = restricted.data2))
+summary(lm(lnCVr ~ Generations, data = strict_dataset))
 ```
@@
 
-##R Session Information
+## R Session Information
 
@@
 
-##References
- <br/><br/> 
-<!-- Some JavaScript to control the buttons to show/hide the big tables -->
-<script>
-$( "input.hideshow" ).each( function ( index, button ) {
-  button.value = 'Hide Output';
-  $( button ).click( function () {
-    var target = this.nextSibling ? this : this.parentNode;
-     target = target.nextSibling.nextSibling.nextSibling.nextSibling.nextSibling;
-    if ( target.style.display == 'block' || target.style.display == '' ) {
-      target.style.display = 'none';
-      this.value = 'Show Output';
-    } else {
-      target.style.display = 'block';
-      this.value = 'Hide Output';
-    }
-  } );
-} );
-</script>
+## References

### 2018-09-26 Manuscripts/Manuscript_MetaAnalysis.Rmd
Luke changes to MS

@@
   \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\onehalfspacing
-abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict theoretically.
-A powerful means to test whether sexual selection increases or decreases population fitness is to manipulate the opportunity for sexual selection in two or more populations, allow evolution to proceed, and then compare the average fitness between the treatment groups.
-Here, we synthesise 459 effect sizes from 65 experimental evolution studies that tested for effects of sexual selection on adaptation.
-We find that sexual selection tends to elevate the mean and reduce the variance for many fitness traits; especially for females evolving under stressful conditions.
-We conclude that the beneficial population-level consequences of sexual selection are typically stronger than the harmful ones, and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
+abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict from first principles.
+Instead, one can empirically determine whether sexual selection increases or decreases population fitness by  manipulating the opportunity for sexual selection in replicate populations, allow evolution to proceed, and then comparing the evolved average fitness between the treatment groups.
+Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis.
+We find that sexual selection tends to elevate the mean and reduce the variance for many fitness traits, especially in females, and for populations evolving under stressful conditions.
+We conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones, and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
 We discuss the implications of these results for conservation and evolutionary biology.
+\vspace{5mm} \par\noindent \textbf{Keywords:} Adaptation, Gender load, Monogamy, Mutation load, Sexual conflict.
+\vspace{5mm} \par\noindent \textbf{Word count:} XXXX in main text.
 ---
@@
 survival, parental care, female fecundity, or success in interspecific competition), sexual selection is predicted to elevate population fitness by causing a correlated response in these other traits[@RN95].
-In essence, the demographically-limiting sex (typically females) benefits from a gene pool that has been purged of harmful alleles through sexual selection on the non-limiting sex (typically males), with the benefit to population fitness potentially large[@RN94; @RN198; @RN58].
+In essence, the demographically-limiting sex (typically females) benefits from a gene pool that has been purged of harmful alleles through sexual selection on the non-limiting sex (typically males).
+Theoretically, the benefit to population fitness might could be large[@RN94; @RN198; @RN58].
 
-Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness (intralocus sexual conflict)[@RN187; @RN146; @RN237; @RN147].
-Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males[@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care (interlocus sexual conflict)[@RN314; @RN276; @RN315].
+Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus sexual conflict[@RN187; @RN146; @RN237; @RN147].
+Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males[@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care (\textit{inter}locus sexual conflict)[@RN314; @RN276; @RN315].
 Given these conflicting theoretical expectations and empirical results, it remains unclear whether sexual selection tends to have a net benefit or cost to population fitness[@RN42; @RN25; @RN116; @RN95].
@@
 
-Theoretical and empirical work has highlighted a number of factors that affect the relationship between sexual selection and population fitness.
-For example, the genetic correlation between female fecundity and male mating/fertilisation success varies in sign and magnitude between species[@RN298] and even between conspecific populations[@RN201], implying that sexual selection on males increases mean female fitness in some species and populations but not others.
-These inconsistencies could derive from differences in allele frequencies, or environmental differences that alter how genotype relates to fitness.
-Importantly, several studies have hypothesised that populations should display a more positive genetic correlation between male and female fitness – and thus potentially between mating/fertilisation success and population fitness – in novel or fluctuating environments, relative to stable environments[@RN187; @RN173; @RN74; @RN257].
-These predictions arise because stable environments create consistent selection, preferentially eroding genetic variation at sexually-concordant loci (i.e.
+A number of factors might influence the strength and sign of the correlation between sexual selection and population fitness.
+First, the genetic correlation between female fecundity and male mating/fertilisation success varies in sign and magnitude between species[@RN298] and even between conspecific populations[@RN201], implying that sexual selection on males increases mean female fitness in some species and populations but not others.
+These inconsistencies could derive from differences in allele frequencies, or environmental differences that alter how genotype relates to phenotype and fitness.
+Second, it has been hypothesised that populations should display a more positive genetic correlation between male and female fitness – and thus potentially between mating/fertilisation success and population fitness – in novel or fluctuating environments, relative to stable environments[@RN187; @RN173; @RN74; @RN257].
+This is because stable environments create consistent selection, preferentially eroding genetic variation at sexually-concordant loci (i.e.
 loci where the fittest genotype is the same in both sexes) and leaving behind variation at sexually antagonistic loci.
-Although there are several systematic reviews of the effects of sexual selection on offspring fitness (see ref.[@RN183]), none that we know of have addressed whether sexual selection is more beneficial to population fitness in stressful conditions or novel environments, despite the relevance of this question to conservation biology.
+We know of no systematic reviews testing this latter theory, though it is has motivated several recent empirical tests (e.g.[@RN187; @RN200; @RN254]), and is relevant to conservation genetics.
 
@@
 We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection, and then measured some fitness component, since these provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations.
-Our principle aims were to measure the average net effect of sexual selection on the population-level mean and variance for various fitness components, and to test whether this effect varies between stressful and benign environments.
+Our principle aims were to measure the average net effect of sexual selection on the population-level mean and variance for various fitness components, to test whether this effect varies between stressful and benign environments, and identify key moderators of the effect size of sexual selection treatment.
 
@@
 189 of the effect sizes came from measurements made on males, 219 on females, and the remaining 51 from measurements of a mixed-sex sample of individuals.
-Most effect sizes in our dataset came from studies that manipulated sexual selection by completely removing it in one treatment via enforced random monogamy (*n* = 241); other effect sizes (*n* = 218) derived from alternative manipulations, such as changing the adult sex ratio.
-In total, we obtained effect sizes for 20 different fitness traits, with reproductive success (*n* = 156) and offspring viability (*n* = 56) being the most commonly-measured traits.
+Most effect sizes in our dataset came from studies that manipulated sexual selection by completely removing it in one treatment via enforced random monogamy ($n$ = 241); other effect sizes ($n$ = 218) derived from alternative manipulations, such as changing the adult sex ratio.
+In total, we obtained effect sizes for 20 different fitness traits, with reproductive success ($n$ = 156) and offspring viability ($n$ = 56) being the most commonly-measured traits.
 We classified 216 effect sizes as direct measures of fitness, 147 as indirect, and the remaining 96 effect sizes as ambiguous (see Methods, Fig.
@@
 
-The grand mean for all effect sizes was positive (REML $\beta$ = 0.23, 95 % CIs: 0.01 to 0.44, *p* = 0.038; Bayesian $\beta$ = 0.23, 95 % CIs: -0.06 to 0.51, $BF_{>0}$ = 18), indicating that sexual selection typically had a net positive effect on the majority of populations and fitness components so far studied.
+The grand mean for all effect sizes was positive (REML $\beta$ = 0.23, 95% CIs: 0.01 to 0.44, $p$ = 0.038; Bayesian $\beta$ = 0.23, 95% CIs: -0.06 to 0.51, $BF_{>0}$ = 18), indicating that sexual selection typically had a net positive effect on the majority of populations and fitness components so far studied.
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
-Sexual selection had a beneficial effect on most fitness traits, including all of the fitness traits that we classified as being ‘direct’ measurements of population fitness: extinction rate (REML $\beta$ = 0.37, 95 % CIs: 0.01 to 0.73; Bayesian $\beta$ = 0.37, 95 % CIs: -0.02 to 0.79, $BF_{>0}$ = 30.13; *n* = 4), offspring viability (REML $\beta$ = 0.20, 95 % CIs: 0.042 to 0.36; Bayesian $\beta$ = 0.21, 95 % CIs: -0.04 to 0.47, $BF_{>0}$ = 24.89; *n* = 56) and reproductive success (REML $\beta$ = 0.17, 95 % CIs: 0.013 to 0.32; Bayesian $\beta$ = 0.18, 95 % CIs: -0.06 to 0.44, $BF_{>0}$ = 15.53; *n* = 156; Fig.
+Sexual selection had a beneficial effect on most fitness traits, including all of the fitness traits that we classified as being ‘direct’ measurements of population fitness: extinction rate (REML $\beta$ = 0.37, 95% CIs: 0.01 to 0.73; Bayesian $\beta$ = 0.37, 95% CIs: -0.02 to 0.79, $BF_{>0}$ = 30.13; $n$ = 4), offspring viability (REML $\beta$ = 0.20, 95% CIs: 0.042 to 0.36; Bayesian $\beta$ = 0.21, 95% CIs: -0.04 to 0.47, $BF_{>0}$ = 24.89; $n$ = 56) and reproductive success (REML $\beta$ = 0.17, 95% CIs: 0.013 to 0.32; Bayesian $\beta$ = 0.18, 95% CIs: -0.06 to 0.44, $BF_{>0}$ = 15.53; $n$ = 156; Fig.
 1; Table S6).
-Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.49, 95 % CIs: -0.72 to -0.26; Bayesian $\beta$ = -0.49, 95 % CIs: -0.78 to -0.19, $BF_{>0}$ = 0.0054; *n* = 35) and body condition (REML $\beta$ = -1.3, 95 % CIs: -1.9 to -0.67; Bayesian $\beta$ = -1.3, 95 % CIs: -1.9 to -0.63, $BF_{>0}$ = 0.00025, *n* = 1).
+Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.49, 95% CIs: -0.72 to -0.26; Bayesian $\beta$ = -0.49, 95% CIs: -0.78 to -0.19, $BF_{>0}$ = 0.0054; $n$ = 35) and body condition (REML $\beta$ = -1.3, 95% CIs: -1.9 to -0.67; Bayesian $\beta$ = -1.3, 95% CIs: -1.9 to -0.63, $BF_{>0}$ = 0.00025, $n$ = 1).
 Fig.
-1 presents Bayesian estimates for each fitness component and Table S6 contains both Bayesian and REML predictions with sample sizes and BF’s.
+1 presents Bayesian estimates for each fitness component and Table S6 contains both Bayesian and REML estimates, with sample sizes and test statistics.
 
@@
 
-The effect size estimates we recovered were highly heterogeneous ($I^2$ = 94.9 %, 95 % CIs: 93 to 96%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208].
-Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 61.5 %, 95 % CIs: 42.9 % to 78.9 %), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 33.5 %, 95 % CIs: 15.8 % to 52.7 %).
+The effect size estimates we recovered were highly heterogeneous ($I^2$ = 94.9%, 95% CIs: 93-96%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208].
+Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 61.5%, 95% CIs: 42.9-78.9%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 33.5%, 95% CIs: 15.8-52.7%).
 The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model implied a non-zero effect ($\sigma^2$ = 0.145 [0.006-0.517]; Table S10).
@@
 
-By applying meta-analysis to log coefficient of variation ratios (*lnCVRs*)[@RN177], we found that sexual selection reduces phenotypic variation under certain conditions (Fig.
+By applying meta-analysis to log coefficient of variation ratios (*lnCVRs*)[@RN177], we found evidence that sexual selection reduces phenotypic variation under certain conditions (Fig.
 2b).
@@
 
-As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 95.4 %, 95 % CIs: 93 % to 97.1 %).
-Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 40.1 %, 95 % CIs: 23.5 % to 60.2 %), fitness components ($I^2_{fitness\:components}$ = 38.7 %, 95 % CIs: 17.1 % to 60.7 %) and taxon ($I^2_{taxon}$ = 16.6 %, 95 % CIs: 3.1 % to 37.2 %).
+As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 95.4%, 95% CIs: 93-97%).
+Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 40.1 %, 95% CIs: 23.5 % to 60.2 %), fitness components ($I^2_{fitness\:components}$ = 38.7%, 95% CIs: 17.1-60.7%) and taxon ($I^2_{taxon}$ = 16.6, 95% CIs: 3.1-37.2%).
 <!-- We don't use Bayesian predictions for lnCVR, which is inconsistent with previous results -->
@@
 The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (Fig.
-3a; Egger’s test: *z* = 6.2, *p* < 0.0001).
+3a; Egger’s test: *z* = 6.2, $p$ < 0.0001).
 Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection.
 There was no significant relationship between effect size and journal impact factor (Fig.
-3b; $t_{437}$ = 1.2, *p* = 0.25) or year of publication (Fig.
-3c; $t_{437}$ = -1.0, *p* = 0.31); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured[@RN216; @RN217].
+3b; $t_{437}$ = 1.2, $p$ = 0.25) or year of publication (Fig.
+3c; $t_{437}$ = -1.0, $p$ = 0.31); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured[@RN216; @RN217].
 
 ```{r, echo = FALSE, fig.cap="Forest plot showing the effect of manipulation of sexual selection, for 20 fitness components from 65 studies.
-Effect sizes (*n* = 459) varied between fitness components, and were more often positive than negative.
-Predicted average values are presented alongside each fitness component; those in bold have 95 % confidence intervals that do not cross zero.
-The estimates presented here are Bayesian predictions, which appear slightly more conservative than REML predictions (Table S6)."}
+Effect sizes ($n$ = 459) varied between fitness components, and were more often positive than negative.
+Predicted average values are presented alongside each fitness component; those in bold have 95% confidence intervals that do not cross zero.
+The estimates presented here are Bayesian predictions, which were slightly more conservative than the REML predictions (Table S6)."}
 knitr::include_graphics("Figures/ForestPlot_edit3.pdf") #Not relative path
@@
 (**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias.
-For (**b**) and (**c**) circle size is proportional to the weight (%) of the study, which is inversely proportional to the variance of the effect size."}
+For (**b**) and (**c**) point size is proportional to the precision of the effect size (i.e.
+the inverse of its variance)."}
 knitr::include_graphics("Figures/publicationbias.pdf") #Not relative path
@@
 Fitness traits related to immunocompetence were an exception: sexual selection typically resulted in weaker immunity.
-The negative effect on immunity is interesting in light of the hypothesised trade-off between sexually-selected phenotypes and immunity, for example due to immunosuppressive effects of sex hormones[@RN323; @RN324].
-Furthermore, the overall benefit of sexual selection was greater for females than males and this sex difference was magnified in stressful environments.
-Consistent with stronger selection on female fitness under stress, female phenotypic variance was substantially reduced under these conditions.
-These results suggest that sexual selection may be a key factor in population persistence under stressful conditions, such as fluctuating environmental change[@RN173] or spatial variability[@RN189].
-Under such conditions, female reproductive output often acts as the limiting factor in staving off extinction[@RN188].
+This result is interesting in light of the hypothesised trade-off between sexually-selected phenotypes and immunity, for example due to immunosuppressive effects of sex hormones[@RN323; @RN324].
+Furthermore, the overall benefit of sexual selection was greater for females than males, and this sex difference was magnified in stressful environments.
+Consistent with stronger selection on female fitness under stress, female phenotypic variance was substantially reduced when sexual selection was applied under stressful as opposed to benign conditions.
+These results suggest that sexual selection may contribute to population persistence under stressful conditions, such as fluctuating environmental change[@RN173] or spatial variability[@RN189], particularly since female reproductive output is often a limiting factor in population growth[@RN188].
 
-The results of the meta-analysis support predictions that sexual selection can improve population fitness and hence aid adaptation[@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
-Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been ‘purged’ of deleterious alleles through intense selection on males[@RN94; @RN198; @RN95].
-What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males.
+The results of the meta-analysis support predictions that sexual selection can improve population fitness and accelerate adaptation[@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
+Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles through selection on males[@RN94; @RN198; @RN95].
+What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest).
 Below we discuss possible explanations for this result, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection[@RN317; @RN318].
@@
 Males are heterogametic in many of the species in our sample (e.g.
-in species with XY or XO sex determination systems); this can reduce father-to-son heritability relative to mother-to-daughter, since sons never inherit the larger sex chromosome from their fathers[@RN340; @RN262; @RN147; @RN263].
-This imbalance of male phenotypes that depend on X-linked loci should slow adaptation relative to rapidly adapting female phenotypes[@RN263; @RN259].
+in species with XY or XO sex determination systems); this can reduce father-to-son heritability relative to mother-to-daughter, since sons never inherit the larger sex chromosome from their fathers[@RN340; @RN262; @RN147; @RN263], which might slow adaptation in male relative to female traits[@RN263; @RN259].
 However,  X-linkage is also likely to inflate the contribution of X-linked genes to fitness variance in the heterogametic sex.
 Under this view, X-linkage facilitates adaptation by increasing the efficacy of selection against recessive deleterious alleles and selection for rare (and recessive) beneficial alleles [@RN341; @RN339].
-Given these countering viewpoints, there is no clear consensus on sex-based differences in heritability.
-For instance, a systematic review found no difference in mean heritability between male and female traits, however there was a male-biased skew in heritability of reproductive traits, which are more likely to be tied to fitness[@RN342].
-Conversely, a recent GWAS in humans found a number of traits with higher heritability in females than males[@RN325].
+Perhaps as a result of these conflicting predictions, there seems to be no clear consensus regarding sex-based differences in heritability.
+For instance, a systematic review found no difference in mean heritability between male and female traits, although there was a male-biased skew in heritability of reproductive traits[@RN342].
+Conversely, a recent association study in humans found a number of traits showing higher heritability in females than males[@RN325].
 
 Secondly, selection on males might be weaker than selection on females, resulting in slower adaptation following experimental manipulation of sexual selection.
-This explanation may initially seem implausible, because net selection on males is generally thought to be stronger than on females due to the cumulative effects of sexual and natural selection[@RN304; @RN303; @RN337; @RN338].
+This explanation may initially seem implausible, because net selection on males is generally assumed to be stronger than on females, due to the (actual or hypothesised) sex difference in sexual selection strength and inter-individual variance in fitness[@RN304; @RN303; @RN337; @RN338].
 However, an oft-overlooked aspect is that selection might frequently be ‘softer’ on males and ‘harder’ on females[@RN319], because the local competitive environment is usually more important for males than it is for females.
@@
 Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the nature of selection, relative to expectations for large, natural populations[@RN322; @RN277; @RN112].
-For example, many studies[@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then randomly mixed to create the next generation; this ensures that successful males simply needed to outcompete their rival(s) in the same sub-population, while successful females needed to outcompete all other females in the entire population.
+For example, many studies[@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then mixed and randomly sampled to create the next generation; this design ensures that successful males simply needed to outcompete their rival(s) in the same sub-population, while each female's reproductive output is measured against the entire female population.
 
@@
 Variation in effects of sexual selection in stressful environments may be due to potentially variable responses amongst taxa[@RN298] and environments.
-Notably, Connallon and Hall (2016)[@RN173] predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it.
-Our meta-analysis suggests that under directional selection generally imposed by environmental stress, sexual antagonism is likely dampened; allowing sexual selection to facilitate adaptation and persistence.
+Notably, Connallon and Hall[@RN173] predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it.
+Our meta-analysis suggests that under directional selection imposed by environmental stress, sexual antagonism is likely dampened; allowing sexual selection to facilitate adaptation and persistence.
 
 Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as commonly is the case for studies in ecology and evolution[@RN208].
-Most of the heterogeneity was explained by ‘study’ and how fitness was measured (fitness component); whereas the taxon, number of generations and use of blinding showed less impact on effect size.
-Taxonomic diversity is limited in experimental evolution studies, which generally use lab-suitable invertebrates with similar mating systems and sex determination.
-However, a meta-analysis of macro-evolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates (fish, insects, birds, spiders, reptiles, mammals)[@RN165].
+Most of the heterogeneity was explained by study and the fitness component that was measured, while the taxon, number of generations of evolution, and use of blinding showed less impact on effect size.
+Taxonomic diversity is limited in experimental evolution studies, which mostly use lab-suitable invertebrates with similar mating systems and sex determination.
+However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates (fish, insects, birds, spiders, reptiles, mammals)[@RN165].
 Despite this, taxonomic differences in the effects of sexual selection on fitness or patterns of diversity are often expected due to differences in mating systems[@RN277] and sex-determination systems[@RN262].
-For example, mate choice is more prevalent in taxa with high levels of parental care[@RN196], affecting the strength and nature of sexual selection.
+For example, mate choice is thought to be more prevalent in taxa with well-developed parental care[@RN196], affecting the strength and nature of sexual selection.
 Furthermore, male heterogametic taxa, including those commonly used in experimental evolution such as flies (Diptera), beetles (Coleoptera) and mice (Mammalia), are likely to have higher heritability of fitness from mothers to daughters.
-Our results – which show greater fitness effects accruing to females – align with this hypothesis.
+Our results -- which show greater fitness effects accruing to females -- align with this hypothesis.
 
@@
 If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants that arise in their midst[@RN94; @RN308; @RN198].
-Sexual selection is also important for conservation (reviewed in ref.[@RN25]) and captive breeding programs (reviewed in ref.[@RN117]).
+Sexual selection is also important for conservation[@RN25] and captive breeding programs[@RN117].
 Within captive breeding programs, genetic diversity is often managed through the enforced monogamy of a strategically selected (genetically diverse) breeding pair[@RN117].
-Captive breeding programs may benefit from allowing sexual selection of  ‘good genes’ or more compatible genes[@RN294], or by increasing maternal investment by females paired with ‘attractive’ males[@RN291; @RN292; @RN293].
-Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution could reduce the genetic quality of the population, and potentially compromise its long-term persistence[@RN332; @RN331; @RN47; @RN333; @RN330].
+Captive breeding programs may benefit from allowing sexual selection of 'good genes' or more compatible genes[@RN294], or by increasing maternal investment by females paired with 'attractive' males[@RN291; @RN292; @RN293].
+Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution, could reduce the genetic quality of the population, and potentially compromise its long-term persistence[@RN332; @RN331; @RN47; @RN333; @RN330].
 Equally, our results support recent evidence that human activities that directly counteract sexual selection, such as selective harvesting of the largest or most ornamented males, can lower population fitness[@RN334].
@@
 
-##Meta-analysis models
+## Mixed effects meta-analysis
 
-Firstly, we obtained a weighted mean effect size (Hedges’ *g*) for the entire dataset using both Bayesian and restricted maximum likelihood (REML) approaches for completeness.
-The weighted mean was obtained by fitting a model with no fixed moderator variables, but fitness component (*e.g.*, body size, female fecundity), study and taxon as random/group-level effects.
+Firstly, we obtained a weighted mean effect size (Hedges’ *g*) for the entire dataset, using both Bayesian and restricted maximum likelihood (REML) approaches for completeness.
+The weighted mean was obtained by fitting a model with no moderator variables (i.e.
+fixed effects), but fitness component (*e.g.*, body size, female fecundity), study ID, and taxon as random/group-level effects.
 That is, we separately model correlations between different effect sizes sourced from the same study, taxon, or pertaining to the same fitness component, and account for these interdependencies when estimating the overall effect.
@@
 Secondly, we fixed fitness component as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the 20 fitness components, using the relevant ``predict`` functions for each of the ``R`` packages used (see below).
-Additionally, we report Bayes Factor ($BF$) values, which estimates the likelihood ratio that the respective effect size is greater than zero ($BF_{>0}$).
+Additionally, we report Bayes Factors ($BF$), giving the likelihood ratio that the focal effect size differs from zero.
 Further details on model parameters can be found within the ESM.
 
-Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g* and *lnCVR*) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed effects meta-analyses.
+Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g* and *lnCVR*) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
 These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (i.e.
 those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g n* = 336; *lnCVR n* = 277).
-We again fit study, fitness component, and taxon as random/group level effects.
-The effects of other moderators such as generations and blinding are explored in the ESM.
+We again fit study ID, fitness component, and taxon as random/group level effects.
+Models investigating other moderators such as number of generations and blinding are presented in the ESM.
 
@@
 2.3.1)[@RN290] to specify and run models in the Stan programming language.
-The modelling approaches are detailed in the ESM including the use of weakly informative priors.
 
@@
 Additionally, we assessed a potential source of publication bias through the correlation between effect size and journal impact factor[@RN217], which can arise if null or countervailing results are more difficult to publish.
-The Journal impact factor for each effect size at the time of publication was obtained using *InCites Journal Citation Reports*.
+The journal impact factor for each effect size at the time of publication was obtained using *InCites Journal Citation Reports*.
 

### 2018-09-26 Manuscripts/Manuscript_MetaAnalysis.Rmd
spelling

@@
 output:
-  pdf_document: default
-  html_document: default
   word_document:
       pandoc_args: ["--smart"]
+  html_document: default
+  pdf_document: default
 bibliography: Bibliography/Bibliography.bib
@@
 abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict from first principles.
-Instead, one can empirically determine whether sexual selection increases or decreases population fitness by  manipulating the opportunity for sexual selection in replicate populations, allow evolution to proceed, and then comparing the evolved average fitness between the treatment groups.
+Instead, one can empirically determine whether sexual selection increases or decreases population fitness by  manipulating the opportunity for sexual selection in replicate populations, allow evolution to proceed, and then compare the evolved average fitness between the treatment groups.
 Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis.
@@
 In essence, the demographically-limiting sex (typically females) benefits from a gene pool that has been purged of harmful alleles through sexual selection on the non-limiting sex (typically males).
-Theoretically, the benefit to population fitness might could be large[@RN94; @RN198; @RN58].
+Theoretically, the benefit to population fitness could be large[@RN94; @RN198; @RN58].
 
@@
 Researchers have investigated the population-level consequences of sexual selection using a range of approaches including macro-evolutionary studies[@RN56; @RN51; @RN55], analysis of the fossil record[@RN270], quantitative genetics[@RN187; @RN200; @RN115; @RN254; @RN257] and especially experimental evolution.
-In particular, many experimental evolution studies have manipulated the intensity of sexual selection in captive populations, allowed evolution to proceed, and then measured population fitness components such as lifespan, fecundity, population extinction rate and mutation load.
+In particular, many experimental evolution studies have manipulated the intensity of sexual selection in captive populations, allowed evolution to proceed, and then measured population fitness components such as lifespan, reproductive success, population extinction rate and mutation load.
 This approach facilitates direct measurement of the net effect of sexual selection on population fitness, at least in the specific populations and ecological conditions under study.
@@
 For instance, a mediocre male genotype can have high fitness provided it outcompetes its local rivals, while low-fitness female genotypes are likely to produce few offspring even when competing with other low-fitness females.
-Therefore, improvements in genetic quality should have stronger diminishing returns in males, possibly contributing to our finding that the genetic consequences of sexual selection lead to greater fitness benefits to females.
+Therefore, improvements in genetic quality should have stronger diminishing returns in males, possibly contributing to our finding that the genetic consequences of sexual selection lead to greater fitness benefits for females.
 Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the nature of selection, relative to expectations for large, natural populations[@RN322; @RN277; @RN112].
@@
 4).
-Briefly, we included studies that 1) were conducted in a dioecious animal species, 2) experimentally manipulated the strength of sexual selection (e.g.
-via experimentally-enforced random monogamy or an altered sex ratio) for at least one generation, and 3) measured a trait that we judged to be a potential correlate of population fitness.
+Briefly, we included studies that 1) were conducted in a dioecious animal species, 2) experimentally manipulated the strength of sexual selection (*e.g.*, via experimentally-enforced random monogamy or an altered sex ratio) for at least one generation, and 3) measured a trait that we judged to be a potential correlate of population fitness.
 This third criterion is the most subjective, because there is rarely enough data to determine whether a particular trait is (or is not) correlated with population fitness.
@@
 We categorised the fitness outcomes into three categories: ambiguous, indirect and direct (detailed in Table S1).
-Briefly, ambiguous measures of fitness were those that are reported to have an unclear or variable association with fitness (e.g.
-body size, mating duration and early fecundity).
-Indirect fitness components were those that are often used as a proxy of fitness but do not directly measure aspects of success in reproduction or population viability (e.g.
-lifespan, mating success and ejaculate quality/production).
+Briefly, ambiguous measures of fitness were those that are reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration and early fecundity).
+Indirect fitness components were those that are often used as a proxy of fitness but do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production).
 Finally, direct measures of fitness (reproductive success, offspring viability and extinction rate) are those that measure fitness through components of reproduction or long-term viability.
@@
 Firstly, we obtained a weighted mean effect size (Hedges’ *g*) for the entire dataset, using both Bayesian and restricted maximum likelihood (REML) approaches for completeness.
-The weighted mean was obtained by fitting a model with no moderator variables (i.e.
-fixed effects), but fitness component (*e.g.*, body size, female fecundity), study ID, and taxon as random/group-level effects.
+The weighted mean was obtained by fitting a model with no moderator variables (*i.e.* fixed effects), but fitness component (*e.g.*, body size, female fecundity), study ID, and taxon as random/group-level effects.
 That is, we separately model correlations between different effect sizes sourced from the same study, taxon, or pertaining to the same fitness component, and account for these interdependencies when estimating the overall effect.
@@
 Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g* and *lnCVR*) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
-These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (i.e.
-those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g n* = 336; *lnCVR n* = 277).
+These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g*: *n* = 336; *lnCVR*: *n* = 277).
 We again fit study ID, fitness component, and taxon as random/group level effects.

### 2018-09-27 Manuscripts/Manuscript_MetaAnalysis.Rmd
Format for NComms

@@
 output:
+  pdf_document: default
+  html_document: default
   word_document:
       pandoc_args: ["--smart"]
-  html_document: default
-  pdf_document: default
 bibliography: Bibliography/Bibliography.bib
@@
 \vspace{5mm} \par\noindent \textbf{Keywords:} Adaptation, Gender load, Monogamy, Mutation load, Sexual conflict.
-\vspace{5mm} \par\noindent \textbf{Word count:} XXXX in main text.
+\vspace{5mm} \par\noindent \textbf{Word count:} 4,370 in main text.
 ---
@@
 
-#Acknowledgements
-We are very grateful to Paco Garcia-Gonzalez for sharing a collection of literature that helped to guide our study, and to Tim Connallon for comments on the manuscript.
+<!-- #Acknowledgements -->
+<!-- We are very grateful to Paco Garcia-Gonzalez for sharing a collection of literature that helped to guide our study, and to Tim Connallon for comments on the manuscript. -->
 

### 2018-09-27 meta_analysis_sexual_selection_pop_fitness.Rmd
Format for NComms

@@
 output:
+  pdf_document: default
   html_document:
@@
     code_folding: hide # awesome buttons to show/hide the code
-  pdf_document: default
 ---

### 2018-10-02 meta_analysis_sexual_selection_pop_fitness.Rmd
Fixed Blind Plot weights

@@
 blind.plot <- df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
-  geom_jitter(aes(fill=Blinding, size = 1/var.g), shape=21, color='grey20')+
+  geom_jitter(aes(fill=Blinding, size = ((1/var.g)/27708.14)*100), shape=21, color='grey20')+ #total 1/var.g
   geom_boxplot(outlier.shape = NA, fill = NA)+

### 2018-10-02 meta_analysis_sexual_selection_pop_fitness.Rmd
Update Blind Fig Weights

@@
 output:
-  pdf_document: default
   html_document:
@@
     code_folding: hide # awesome buttons to show/hide the code
+  pdf_document: default
 ---

### 2018-10-19 Manuscripts/Manuscript_MetaAnalysis.Rmd
Edits to thesis manuscript

@@
 author: 
-- #Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
+- Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
 - 
-- #'\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
+- '\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
 output:
@@
 ---
-<!-- \maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.} -->
+\maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.}
 

### 2018-10-20 meta_analysis_sexual_selection_pop_fitness.Rmd
Names added back to supp mat

@@
 title: 'Sexual selection improves population fitness: a meta-analysis'
-author: #"Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
+author: "Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
 subtitle: Supplementary Material
@@
 We used the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) as a guide during this meta-analysis.
-The repository used to formulate this document can be found here: **hidden for double-blind peer review**
+The repository used to formulate this document can be found here: https://github.com/JustinCally/SexualSelection
 

### 2018-11-26 Response_to_Nature_Comms.Rmd
Lots of changes to the data, supp and reviewer comments

---
title: "Sexual selection improves population fitness: a meta-analysis"
subtitle: "Response to Decision Letter"
output: pdf_document
---

```{r, warning=FALSE, message=FALSE, results='hide', echo = FALSE}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(car)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
library(rstan) #Note that installation requires some effort: dependency for brms
library(brms) 
library(backports) #seems to be a dependency
library(bayesplot)
#devtools::install_github("mvuorre/brmstools")
library(brmstools)
library(metaAidR) # install.packages("metaAidR")
library(cowplot)
library(gridExtra)
#setwd("~/Documents/Uni/metaanalysis/SexualSelection")
source("I2_function.R") #Adapted function for obtaining I2 with CIs
source("Vdodge_function.R") # nice function for ggplot
source("Tidy_functions_for_brms.R") #Tidy functions for making model tables for brms

#load(".RData")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Dear Dr. Jones and colleagues,

Many thanks for your time, and for the very helpful comments on our manuscript. We have considerably reworked the manuscript in light of the many insightful comments and suggestions provided by the reviewers. Please see below for a detailed list of responses to each of the reviewers' points. We also attach a revised manuscript and a revised copy of the supplementary material, as well as a copy of the revised manuscript in which the significant changes and additions have been highlighted. Please let us know if we can do anything further to assist you.

Yours Sincerely,

Justin Cally and co-authors

________________________________________________________

## Comments from Reviewer 1 (Prof. Jacek Radwan)

>*The manuscript presents results of a meta-analysis assessing the effect of sexual selection on population fitness. This topic has been increasingly studied over the past decade or so, and the time seems ripe for a synthesis. The authors have done good job searching the literature – it includes all relevant papers I could remember, and the results should be of interest to a broad range of evolutionary biologists. I cannot expertly judge on state-of-the-art methodology, but I do have several general concerns about how the analyses were performed.*

Many thanks for your time and this valuable feedback.

>*Firstly, it seems that several male traits like to be under sexual selection, but not related to population fitness were included. I don’t think this is correct given the question being asked (i.e. whether sexual selection increases population fitness). I think traits which are directly under sexual selection (eg. attractiveness, reproductive success) should not be pooled with traits which may respond to manipulation of sexual selection indirectly (eg. male development time, survival) and can affect population fitness. Distinguishing between both types of trait could actually be revealing – e.g. could expose trade-offs between sexually selected traits and fitness components unrelated to reproductive competition (see eg. Radwan et al. 2015 Evol Biol), a thus potentially explain lower effect of sexual selection on (pooled) male traits than on female traits.*

The reviewer is correct that several traits are likely under trade-offs with other traits as sexual selection not only affects mean fitness but alters life history traits (*i.e.* sexual selection may increase male body size or attractiveness, but decrease development rate). In essence this is why our meta-analysis sought to investigate the *net* effect of sexual selection on population fitness across many traits, rather than one that may be traded off in a given direction. Importantly, to account for the variable and uncertain relationships certain traits have with fitness (as raised by the reviewer). We provide an expacded table on how each trait is measured and why they are classed as ambiguous, indirect and direct in their relationship with fitness. Given that this information was in the Supplementary Material we have revised the manuscript to clarify the distinctions more thoroughly.

Additionally, the reviewers comment that male attractiveness may not be related to population fitness is correct. Because male attractiveness may be positively or negatively correlated with average fitness (although in many condition-dependent traits a positive association is assumed) we have re-classified *Male Attractiveness* as ambiguously related to fitness, rather than indirect. All subsequent models, statistics and figures now take into account this re-classification. However, given the small sample size for male attractiveness effect sizes (n = 6), **we find only marginal changes in the results and no key changes in the key findings of the study*.**

>*Secondly, looking at Figure 1, one notices apparent anomalies, for example significantly positive slope for male attractiveness, based on studies with average effect size close to zero. I think this (and few others) surprising estimates may result from fitting random terms across all trait types (fitted as a fixed factor, second model); I guess fitting interaction (random slopes) would not be feasible for some categories including few data points, but some of them could easily be pooled in wider categories.*

The reviewer raises questions of the analysis that produce seemingly suprising results. We agree that some of *significant* predictions in Figure 1 (whereby 95 % CIs do not overlap zero) appear surprising based on the distribution on effect sizes. In regards to the trait "male attractiveness", the 95 % CIs do not overlap zero. This is the case even though the higher weighted studies are very close to zero. However, this seeming anomoly can be explained by various reasons.

Firstly, althought the effect size prediction for the trait has 95 % CIs not overlapping zero, the overall magnitude of the effect size is small (see Table exerpt), and the Bayes Factor (an estimate of the likelihood that the effect size is actually positive) is also small. The full table for all predicted effect sizes used in Figure 1 can be seen in **SXXX**. Below we provide the exerpt of this table and forest plot for "Male attractiveness".

Secondly, the effect size predictions were made using a single model that incorperated all 459 effect sizes, thus model predictions for each trait have narrower confidence intervals as the fitted values do not incorperate measurement error. In regards to our analysis, this means that the predictions that appear in Figure 1 are sourced from using ``fitted.brmsfit`` as opposed to ``predict.brmsfit``. Given the reviewers comments we have clarified how we obtained model predictions used in our results. Additionally, some meta-analyses investigating the effect of a variable on more than one outcome model each outcome (in this case the *fitness component*) seperately. Arguably, this method provides more variable model estimates as models will always have lower power due to reduced sample sizes and the incorperation of measurement error in the predictions. We have added a table to the Supplementary Material where models are independently conducted on all fitness components where n > 3.

```{r}
left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component")  %>% filter(`Fitness Component` == "Male Attractiveness") %>% pander(split.table = Inf, digits = 2)
```

```{r, fig.width = 9, fig.height = 3}
pd <- position_dodgev(0.6)

p.meta.male.attract <- full_dataset %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female"),
         Outcome.Class = factor(Outcome.Class, levels = c("Ambiguous", "Indirect", "Direct"))) %>%
  filter(Outcome == "Male Attractiveness") %>%

  ggplot(aes(x=reorder(AuthorYear, -g), y = g)) +
  scale_color_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
                     name = "Relationship\nto fitness")+
  scale_shape_manual(values=c(21,22,24))+
  scale_fill_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
                    name = "Relationship\nto fitness")+
  geom_errorbar(aes(ymin = lowerci, 
                     ymax = upperci,
                     color = Outcome.Class,
                     group = g),
                width = 0, show.legend = FALSE) +

  geom_point(aes(shape = Sex,
                 fill = Outcome.Class),
             size = 1.75, 
             color = "grey20",
             position = position_dodge2(width = 0.2)) +

  coord_flip()+

  scale_y_continuous(limits=c(-3.1, 3.1), 
                     breaks = c(-3, -2, -1, 0, 1, 2, 3), 
                     name='                              Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +

  xlab('Reference') +

  geom_hline(yintercept=0, 
             color='black', 
             linetype='dashed')+

    geom_hline(yintercept=0.314, 
             color='#4daf4a', 
             linetype=1,
             size = 1)+

  geom_hline(yintercept=0.0302, 
             color='#4daf4a', 
             linetype=3)+

  geom_hline(yintercept=0.61, 
             color='#4daf4a', 
             linetype=3)+

  facet_grid(Outcome_f~.,
             labeller = label_wrap_gen(width=20),
             scales= 'free', 
             space='free')+

  guides(fill = guide_legend(override.aes = list(shape = 21, colour = "grey20", size = 6)),
         shape = F)+

  #Add theme specifying text size, margins, lines etc.
  theme_bw()+

  theme(strip.text.y = element_text(angle = 0, size = 8, margin = margin(t=15, r=15, b=15, l=15)), 
        strip.background = element_rect(colour = NULL,
                                        linetype = "blank",
                                        fill = "gray90"),
        text = element_text(size=11),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=12), 
        legend.title=element_text(size=12, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0, size = 12))

p.meta.male.attract
```

>*Thirdly, type of trait measured explained 35% variance, but the authors do not explore this any further. However, examination of Fig. 1 suggest that some indirect/ambiguous fitness measures account for much of this heterogeneity and they generally have higher average effect sizes that direct measures (except for immunity). I’d like to see if the authors recover their main result if they only direct measures.*

**Add section in discussion about the variability amongst traits and why some might be subject to trade offs (e.g. immunity).**

**Summarise results for direct, indirect and ambiguous**

The reviewer provides an accurate shortcoming of discussion on the observed heterogeneity between fitness components. We have extended certain parts of the discussion related to this aspect...

In regards to conducting a meta-analysis on just direct fitnesss components, the reviewer provids a valid question of our use of direct **and** indirect fitness components for the meta-analysis investigating the effects of sex and stress. To some degree the use of direct **and** indirect is arbitrary. But based on the question we asked we were interested in the effect of sexual selection on many components of fitness.

Nevertheless, we conducted our analysis using just direct fitness measures. We find the same key associations; that sexual selection generally elevates fitness, especially for females, with the effect magnified in stressful environments. Below we present the findings, which we have incorperated into our supplementary material and referenced within the manuscript and Figure 2 caption.

Additionally, in order to further distinguish the effects of sexual selection on ambiguous, indirect and direct fitness components, we have structured the second paragraph of the results to more consistently reflect our classification system.

```{r, warning=FALSE}
model.direct.only <- rma.mv(g, V = var.g, 
                          mods = ~ 1 + Sex * Environment, 
                          random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome,
                                       ~ 1 | Taxon), 
                          method = "REML", 
                          data = strict_dataset %>% filter(Outcome.Class == "Direct"))

#Generate predictions without taxon utilising the previously described function
get.predictions.direct <- function(newdata){
  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Stressed<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

  predict(model.direct.only, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
}

# Get the predictions for each combination of moderators
predictions.direct <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed")))
predictions.direct <- cbind(predictions.direct, do.call("rbind", apply(predictions.direct, 1, get.predictions.direct))) %>%
  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
for(i in 3:6) predictions.direct[,i] <- unlist(predictions.direct[,i])

countpred <- count_(strict_dataset %>% filter(Outcome.Class == "Direct"), c("Sex", "Environment"))

predictions.direct <- left_join(predictions.direct, countpred, by = c("Sex", "Environment"))
colnames(predictions.direct) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
predictions.direct <- predictions.direct %>%
      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female"),
         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
         Sex = factor(Sex, levels = c("Male", "Both", "Female")))

predictions.direct <- format(predictions.direct, digits = 2)
predictions.direct$Prediction = as.numeric(predictions.direct$Prediction)
predictions.direct$CI.lb = as.numeric(predictions.direct$CI.lb)
predictions.direct$CI.ub = as.numeric(predictions.direct$CI.ub)
predictions.direct$n = as.numeric(predictions.direct$n)

predictions.direct %>% pander(caption = "Model using only direct measures of fitness")
```

```{r, fig.height=4.5, fig.width=6.25, warning=FALSE, message=FALSE, error = FALSE, fig.align='center'}
if(!file.exists("data/brms.direct.rds")){
  brms.direct <- brm(g | se(SE)  ~ 1 + Sex * Environment 
                        + (1|Taxon) 
                        + (1|Study.ID) 
                        + (1|Outcome), 
                        family = "gaussian", 
                        seed = 1,
                        cores = 4, chains = 4, iter = 4000, 
                        control = list(adapt_delta = 0.9999, max_treedepth = 15),
                        data = strict_dataset %>% 
                          filter(Outcome.Class == "Direct") %>% 
                          mutate(SE = sqrt(var.g)))
  saveRDS(brms.direct, file = "data/brms.direct.rds")
}
brms.direct <- readRDS(file = "data/brms.direct.rds")

# lternatively you can obtain posterior samples manually.
post <- (posterior_samples(brms.direct, 
                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
                                    "b_SexF:EnvironmentStressed")) %>%
           mutate(both_benign = b_Intercept + b_SexB,
                  both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed`,
                  male_benign = b_Intercept,
                  male_stressful = b_Intercept + b_EnvironmentStressed,
                  female_benign = b_Intercept + b_SexF,
                  female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed`))[,-(1:6)]

# Add columns for Environment and Sex
post <- as.data.frame(t(post))
post$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
post$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")

#Clean up dataframe
post <- melt(post, id = c("Sex", "Environment"))
post$variable <- NULL

#Plot the posterior values from the Bayesian model as density ridges
pd <- position_dodgev(height = 0.3)
posterior.plot <- post %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  ylab("Environment\n")+
  xlab("\nEffect Size (Hedges' g)")+
  # scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  # scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
  scale_x_continuous(limits = c(-0.75, 1.5), breaks = c(-1, -.5, 0, 0.5, 1, 1.5))+

  theme_bw()+

  theme(panel.spacing = unit(0.1, "lines"),
        text = element_text(size=16),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=16), 
        legend.title=element_text(size=16, face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 14),
        axis.title.y = element_text(size = 16, hjust = 0.35, margin = margin(r=-10)),
        axis.text.y = element_text(angle = 0),
        plot.title = element_text(size = 16))

#Add the REML predictions as circles with error bars
both.plots <- posterior.plot + 
  geom_errorbarh(data = predictions.direct %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
                 aes(xmin = predictions.direct$CI.lb,
                     xmax = predictions.direct$CI.ub, y = Environment,
                     color = Sex), 
                 height = 0, show.legend = F, position = pd)+

  geom_point(data = predictions.direct %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
             shape=21, color = "grey20", position = pd) +

    guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
    scale_size(guide = 'none')+

  scale_y_discrete(expand=c(0.075, 0))

both.plots
```

```{r, warning=FALSE}
direct.only.data <- strict_dataset %>% filter(Outcome.Class == "Direct")
I2(model.direct.only, direct.only.data$var.g) %>% pander(digits = 3)
```

>*Another major problem I have with the manuscript concerns interpretation of the very intriguing finding that the response to manipulation of sexual selection was stronger for female traits compared to male traits. I’m confused by the authors’ explanation: do they assume sexual selection acted directly on females, and not only indirectly, via males? Only then things like mother to daughter heritability, or hard selection on females, should matter.*

Leave this for Luke

Good sugggestion!

>*Perhaps the effect on females is indeed direct, and results from stress imposed by polygamous treatment, which magnifies direct, hard selection on females? This would be an important finding, and perhaps the authors could test it with their dataset by contrasting middle-class-neighborhood-like studies from those which allowed for female evolution. But if correct, this explanation is not exactly the effect of sexual selection, but rather enhanced selection of females due to enhanced (male induced) stress, so the interpretation of results should change.*

Answer

**Other comments:**  
>*l. 30 – reviews on sexual conflict are OK to cite here, but there are empirical papers actually demonstrating correlation between male sexual selected traits (Harano et al. 2011; Plesnar et al. 2014) which should also be cited.*

Thank you, we now cite those papers as suggested in line 31. Additionally, they are especially pertenant to experimental evolution studies using species such as the bulb mite (*Rhizoglyphus robini*)[@Plesnar_2014] and flour beetles (*Gnatocerus cornutus*)[@Harano_2010].

>*l. 151 – the authors discuss beneficial effects of sexual selection on direct fitness measures such as reproductive success or offspring viability, but estimates for both of these measures actually overlapped zero! Perhaps joint analysis of direct fitness measures, as I suggested above, could support this conclusion, but currently this is an overstatement.*

The reviewer is correct in that the 95 % CI overlap zero for the three direct fitness components (extinction rate, offspring viability and reproductive success) have 95 % CI overlapping zero. Additionally, our analysis reveals that the predicted effect size for direct fitness components has 95 % CIs that overlap zero for Bayesian, but not REML models (REML $\beta$ = 0.15, 95% CIs: 0.033 to 0.27; Bayesian $\beta$ = 0.15, 95% CIs: -0.058 to 0.34, $BF_{>0}$ = 4.9). In this respect we have tapered and clarified our statement that we find some evidence that sexual selection increases mean values of traits directly related to fitness. However, we retain our statement that sexual selection generally elevates the mean of fitness components directly related to fitness as a two-way 95 % confidence limit is an arbitrary cut-off and the Bayes Factors suggest that their is a high likelihood that the effect size for direct fitness components is greater than zero.

**In the discussion the authors say they included the number of experimental evolution generations, but I could not find this information in methods.**

It is correct that we did not use the number of generations in our main analysis. Line 281 of the manuscript (Methods section) states that the number of generations. In the supplementary material we investigate the role of number of generations (the lineage is evolved for) has on fitness in the section *Meta-analyses including many moderator variables* as well as in Figure S10 and S11. Generations (specifically, log-Generations) had minimal effect on the effect sizes and was removed for the models that appeared in the main text.

**Fig. S1 is not referred to in the main texts, is it different from Fig. 2, except that the latter contains predicted average values for fitness components?**

No difference... kind of there for documentation on how we created it (transparency). What do you think we should do about this Luke?

________________________________________________________

## Comments from Reviewer 2

**This meta-analysis investigated the consequences of sexual selection experiments on trait mean and variance (comparing sexually selected groups vs control groups). Overall, the authors observe sexual selection usually increase mean and reduce variance (especially in females). The authors conclude sexual selection's benefits outweigh its detrimental effects. This meta-analysis is extremely well conducted (the use of both likelihood-based and Bayesian models for robustness), and although I am not an expert on this topic, I really enjoyed reading it, and it was very clear. Especially, I am impressed with the detailed supplement which showed the code and analysis. However, I have several comments regarding their analysis, which will increase the robustness of results and thus conclusions.**

Many thanks for your time and attention, and for the valuable feedback.

**1 --- The use of Hedges' $g$. I understand that Hedges' $g$ was probably used because it can take interval measurements as well as ratio measurements (lnCVR can only take ratio measurements). However, $g$ cannot really deal well with heterogeneity between two groups (i.e. experimental and control groups having different variances). This is why Hedges' $g$ (Cohen's $d$) was criticized earlier.**

Answer

**Osenberg, C. W., O. Sarnelle, and S. D. Cooper. 1997. Effect size in ecological experiments: the application of biological models in meta-analysis. \textit{American Naturalist} 150:798-812.**

Answer

**As a response, they come up with log response ratio (lnRR) - see**

**Hedges, L. V., J. Gurevitch, and P. S. Curtis. 1999. The meta-analysis of response ratios in experimental ecology. \textit{Ecology} 80:1150-1156.**

**I recommend that the authors use lnRR for their effect size for mean comparison as well as Hedge's $g$ to see the robustness of their conclusions for the mean.**

Reviewer 2 has rightly pointed out that the use of Hedge's *g* has been critisized for its ability to account for heterogeneity between the control and treatment groups **CITE**. We extended our meta-analysis by including the log response ratio (lnRR) as well as a modified version of Hedge's g that attempts to account for this heterogeneity, this modified statistic (**CITE**) can be derived from the ``metafor`` package for meta-analysis, where it is named SMDH (standardized mean difference with heteroscedastic population variances in the two groups). There are several key findings from the use of lnRR and SMDH:

*Firstly*, Hedge's g and SMDH are highly correlated. This suggests that unequal variance between the treatment and control groups (heteroscedasticity) is unlikely to impact the effect size of Hedge's g

```{r, warning=F}
#This function writes in the correlation value
panel.cor <- function(x, y, digits=2, prefix="", cex.cor, ...)
{
  usr <- par("usr"); on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- abs(cor(x, y, use="pairwise.complete.obs"))
  txt <- format(c(r, 0.123456789), digits=digits)[1]
  txt <- paste0(prefix, txt)
  if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
  text(0.5, 0.5, txt, cex = cex.cor * r)
}

es.correlation.df <- lnRR.data %>% left_join(SMD.data %>% rename(`Hedge's g` = SMD)) %>% left_join(SMDH.data)

pairs(es.correlation.df %>% select(`Hedge's g`, lnRR, SMDH), lower.panel=panel.smooth, upper.panel=panel.cor)
```

*Secondly*, The calculation of lnRR and SMDH can only be calculated for effect sizes where the study reported means, standard deviations and sample sizes (352 out of 459). This is a limitation as in our analysis we investigate the effects of sex and stress on a further restricted dataset (direct and indirect fitness traits only). Specifically, fewer effect sizes from stressful conditions are able to be calculated; making Hedge's g an advantageous effect size in comparison to lnRR.

```{r}
predictions.complete2 %>% select(Sex, Environment, `Hedge's g sample size` = n) %>% 
  left_join(predictions.lnRR %>% select(Sex, Environment, `lnRR sample size` = n), by = c("Sex", "Environment")) %>% pander()
```

*Thirdly*, if we conduct a meta-analysis using lnRR as the effect size we obtain very similar results with all major conclusions unchanged (keeping in mind that lnRR and Hedge's are on different scales):  
+ The effect of sexual selection on population fitness is generally positive.
+ This effect is magnified for females in stressful environments with a significantly positive interaction term (stress*females)

```{r, warning = F, fig.width=7, fig.height = 3.5, message = F}
grid.arrange(both.plots + 
               guides(fill = FALSE) + 
               ggtitle("Comparison between Hedge's g and lnRR effect sizes \n\n"), 
             lnRR.plots + ggtitle("\n\n"), nrow = 1)
```

For these reasons we have decided to use Hedge's g as the main effect size throughout the manuscript but reference and provide equivelant statistical analysis for lnRR in the supplementary material.

**2 --- The authors may consider also doing another set of meta-analyses using lnVR (log variability ratio - proposed in Nakagawa et al. 2015).**

**Nakagawa, S., R. Poulin, K. Mengersen, K. Reinhold, L. Engqvist, M. Lagisz, and A. M. Senior. 2015. Meta-analysis of variation: ecological and evolutionary applications and beyond. \textit{Methods in Ecology and Evolution} 6:143-152.**

Answer

**As one can see in Figure 2, the mean results (Hedges' $g$) are a mirror image of the variance results (this makes sense CV controls for means). I would like to see what the absolute change in variances. Probably the authors can put the analysis using lnVR in the supplement. The results of this analysis can be discussed. Also, the mean-variance relationship between mean and variance (sd) should be verified (e.g. plot log mean and log sd or log variance).**

The reviewer suggestions have been included in our meta-analysis in order to validate our conclusions. Several key points arise from the meta-analysis of variation:

*Firstly*, as the reviewer suggested we justify the use of lnCVR my assessing the mean-variance relationship. Given this finding the use of lnCVR is preferenced over lnVR, as lnVR does not account for the mean-variance relationship.

```{r, warning = F, message=F}
full_dataset %>% ggplot(aes(x = mean.high, y = sd.high))+
  geom_point()+
  scale_x_log10()+
  scale_y_log10()+
  xlab("Mean of Treatment Group")+
  ylab("Standard Deviation of Treatment Group") +
  geom_smooth(method = "lm", colour = "red")
```

*Secondly*, We conducted both Bayesian and REML meta-analyses for lnVR, which we present in the supplementary material and briefly discuss in the manuscript. We found similar trends for the meta-analysis of variance using lnCVR and the meta-analysis of variance using lnVR, These are:

+  In stressful environments sexual selection leads to a decrease in the variance for females, relative to benign environments
+  Bayesian models suggest that under stressful conditions elevated sexual selection causes a significant decrease in the variance. But this trend is not significant for REML models.

However, when using lnVR, the variability of fitness traits for males under sexual selection increased, while in the model using lnCVR it did not.

```{r, warning = F, fig.width=7, fig.height = 3.5, message = F}
grid.arrange(both.var.plots + 
               guides(fill = FALSE) + 
               ggtitle("Comparison between lnCVR and lnVR effect sizes \n\n"), 
             both.lnVR.plots + ggtitle("\n\n"), nrow = 1)
```

**3 --- $I^2$ needs to be explained. $I^2$ is proposed originally here:**

**Higgins, J., and S. Thompson. 2002. Quantifying heterogeneity in a meta-analysis. \textit{Statistics in Medicine} 21:1539 - 1558.**

**But later expanded in here for mixed models (hierarchical models)**

**Nakagawa, S., and E. S. A. Santos. 2012. Methodological issues and advances in biological meta-analysis. \textit{Evolutionary Ecology} 26:1253-1274.**

**This is what the authors use. Also, it will be good to put the degree in I^2 in the context. To do this see this paper:**

**Senior, A. M., C. E. Grueber, T. Kamiya, M. Lagisz, K. O'Dwyer, E. S. A. Santos, and S. Nakagawa. 2016. Heterogeneity in ecological and evolutionary meta-analyses: its magnitude and implications. \textit{Ecology} 97:3293-3299.**

Answer

**4 --- Publication tests have been conducted on, I think, "meta-analytic" residuals results as suggested in Nakagawa and Santos 2012. One could use such residuals to conduct the trim and fill method and see how much the mean could move (see Nakagawa and Santos 2012). One should remember the funnel asymmetry could be caused by the presece of heterogeniety. See:**

**Egger, M., G. Smith, M. Schneider, and C. Minder. 1997. Bias in metaanalysis detected by a simple, graphical test. \textit{Br Med J} 315:629 - 634.**

Answer

**5 --- Figure 3 - are these grey envelopes 95% CI?**

Answer

**6 --- the title - do the authors include "a systematic review" - so "a systematic reveiw and meta-analysis" - these two things are diferent - see:**

**Nakagawa, S., and R. Poulin. 2012. Meta-analytic insights into evolutionary ecology: an introduction and synthesis. \textit{Evolutionary Ecology} 26:1085-1099.**

Our mstudy does not involve a systematic review.

**Hope my comments are useful.**

They were extremely useful, many thanks!

________________________________________________________

## Comments from Reviewer 3

**This manuscript addresses the question of whether, on average, sexual selection has a net beneficial or detrimental effect on population fitness, using a meta-analysis of experimental evolution studies comparing the fitness of populations under different intensities of sexual selection. The analyses consider the effects of sexual selection on both the mean and variance of population fitness, and test whether these effects differ for stressful vs. benign environments, or depend on the measure of population fitness.**

**These are issues of longstanding interest, and as there is now quite a wealth of experimental evolution studies addressing these questions a meta-analysis synthesising their findings is timely.**

Many thanks for your time and attention, and for the valuable feedback.

**The results of this meta-analysis broadly concur with current theoretical predictions, and are likely to interest a wide readership. Across all studies, environment types and fitness measures there was a small positive effect of sexual selection on mean population fitness, although effect sizes varied with the fitness measure used. The positive effect of sexual selection on fitness was strongest for females in stressful environments, who also showed reduced variance in fitness under sexual selection.**

Answer

**The authors discuss these findings thoughtfully, although they focus more on the (weaker) effects found for ‘direct’ measures of fitness while somewhat neglecting the effects seen for ‘indirect’ fitness measures (e.g. of attractiveness, mating latency, lifespan, ejaculate traits). These potentially deserve more consideration, especially as many appear to be male-limited traits or measured mainly in males, that would appear to have a direct bearing on male mating success (if an indirect link to overall fitness), yet despite this the overall effect of sexual selection on male fitness is not significant.**

Need to answer this in a similar line to Jaceks comments.

**I have only a few more specific comments:**

**Does your approach consider variation in the intensity of sexual selection exclusively on males? This is worth noting (e.g. statements such as that on line 98-99 might be amended to “Sexual selection on males significantly improved female fitness.”)**

Answer

**Experiments manipulating the sex ratio to alter sexual selection might simultaneously decrease sexual selection on males while increasing sexual selection on females. Would this be classified as reduced sexual selection in your analyses? I don’t think you included this aspect of study design as a moderator variable in any of your analyses – given that close to half of the effects you include come from “alternative manipulations” (line 70) perhaps you could test whether this affects effect size?**

Answer

**It seems possible that sexual selection on females, and not only on males, could affect population fitness – potentially even more directly than sexual selection on males. And might differing extents of sexual selection in each sex interact with the differences you saw in fitness measured in males vs. females?**

Answer

**L111-118 It seems a little odd that there is no residual heterogeneity in your $I^2$ estimates. From the supplemental information it is not entirely clear to me how you have adapted the function that is under development in “metaAidR”, but can you double check that you have appropriately incorporated the residual variance into these estimates?**

Answer

**L307-311 Please clarify here that lnCVR was calculated as the ratio $ln(CVfitness_{SS}/CVfitness_{no SS})$**

Answer

**Fig. 3 Please explain the dashed red and black lines in the figure caption.**

Answer

**Tables 1, 2 Please check – the parameter estimates for ‘Female sex’ and test for ‘Female > Male’ are bolded inconsistently between the REML and Bayesian models where these estimates are identical.**

Answer

### 2018-11-26 Manuscripts/Manuscript_MetaAnalysis.Rmd
Lots of changes to the data, supp and reviewer comments

--- 2018-09-26 Manuscripts/Manuscript_MetaAnalysis.Rmd
@@
 ---
-title: "Sexual selection improves population fitness: a meta-analysis"
+title: '\huge{Sexual selection improves population fitness: a meta-analysis}'
 author: 
-- #Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
+- Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
 - 
-- #'\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
+- '\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
 output:
+  pdf_document: default
+  html_document: default
   word_document:
       pandoc_args: ["--smart"]
-  html_document: default
-  pdf_document: default
 bibliography: Bibliography/Bibliography.bib
+subparagraph: yes
 csl: Bibliography/NComms.csl
@@
   \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\onehalfspacing
+    \usepackage{titlesec} \titleformat{\section}{\normalfont\scshape\LARGE}{\thesection}{1em}{} \titleformat{\subsection}{\normalfont\Large}{\thesubsection}{1em}{} \titleformat{\subsubsection}{\normalfont\large}{\thesubsubsection}{1em}{} \usepackage{abstract} \renewcommand{\abstractnamefont}{\normalfont\Large}
+    \usepackage{hyperref}\hypersetup{colorlinks=false, linkcolor=blue, filecolor=blue, urlcolor=blue} 
+    \usepackage{color,soul}
+    \raggedbottom    
 abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict from first principles.
@@
 We find that sexual selection tends to elevate the mean and reduce the variance for many fitness traits, especially in females, and for populations evolving under stressful conditions.
-We conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones, and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
+We conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
 We discuss the implications of these results for conservation and evolutionary biology.
 \vspace{5mm} \par\noindent \textbf{Keywords:} Adaptation, Gender load, Monogamy, Mutation load, Sexual conflict.
-\vspace{5mm} \par\noindent \textbf{Word count:} XXXX in main text.
 ---
-<!-- \maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.} -->
+\maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.}
 
@@
 ```
+\phantomsection
 
-Sexual selection, defined as selection resulting from competition for mates or their gametes[@RN139], is a ubiquitous evolutionary force that has profoundly shaped the natural world.
-As far back as Darwin[@RN310], researchers have theorised that sexual selection can change the average absolute fitness of individuals in a population (henceforth termed ‘population fitness’[@RN269; @RN268]).
-However, opinion is divided over whether the net effect on population fitness is positive or negative[@RN42; @RN25; @RN116; @RN95].
-_Prima facie_, one might predict that sexual selection would have no effect on population fitness, since it does not matter which individuals of the faster-reproducing sex (typically males) succeed in mating, so long as some do[@RN142].
-However, when genotypes with high mating or fertilisation success also have superior breeding values for traits that affect population fitness (e.g.
-survival, parental care, female fecundity, or success in interspecific competition), sexual selection is predicted to elevate population fitness by causing a correlated response in these other traits[@RN95].
+#Introduction
+
+Sexual selection, defined as selection resulting from competition for mates or their gametes [@RN139], is a ubiquitous evolutionary force that has profoundly shaped the natural world.
+As far back as Darwin [@RN310], researchers have theorised that sexual selection can change the average absolute fitness of individuals in a population, henceforth termed ‘population fitness’ [@RN269; @RN268].
+However, opinion is divided over whether the net effect on population fitness is positive or negative [@RN42; @RN25; @RN116; @RN95].
+_Prima facie_, one might predict that sexual selection would have no effect on population fitness, since it does not matter which individuals of the faster-reproducing sex (typically males) succeed in mating, so long as some do [@RN142].
+However, when genotypes with high mating or fertilisation success also have superior breeding values for traits that affect population fitness (*e.g.*, survival, parental care, female fecundity, or success in interspecific competition), sexual selection is predicted to elevate population fitness by causing a correlated response in these other traits [@RN95].
 In essence, the demographically-limiting sex (typically females) benefits from a gene pool that has been purged of harmful alleles through sexual selection on the non-limiting sex (typically males).
-Theoretically, the benefit to population fitness could be large[@RN94; @RN198; @RN58].
+Theoretically, the benefit to population fitness could be large [@RN94; @RN198; @RN58].
 
-Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus sexual conflict[@RN187; @RN146; @RN237; @RN147].
-Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males[@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care (\textit{inter}locus sexual conflict)[@RN314; @RN276; @RN315].
-Given these conflicting theoretical expectations and empirical results, it remains unclear whether sexual selection tends to have a net benefit or cost to population fitness[@RN42; @RN25; @RN116; @RN95].
+Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus \hl{sexual conflict} [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014].
+Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males [@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care: \textit{inter}locus sexual conflict [@RN314; @RN276; @RN315].
+Given these conflicting theoretical expectations and empirical results, it remains unclear whether sexual selection tends to have a net benefit or cost to population fitness [@RN42; @RN25; @RN116; @RN95].
 
-Researchers have investigated the population-level consequences of sexual selection using a range of approaches including macro-evolutionary studies[@RN56; @RN51; @RN55], analysis of the fossil record[@RN270], quantitative genetics[@RN187; @RN200; @RN115; @RN254; @RN257] and especially experimental evolution.
+Researchers have investigated the population-level consequences of sexual selection using a range of approaches including macro-evolutionary studies [@RN56; @RN51; @RN55], analysis of the fossil record [@RN270], quantitative genetics [@RN187; @RN200; @RN115; @RN254; @RN257] and especially experimental evolution.
 In particular, many experimental evolution studies have manipulated the intensity of sexual selection in captive populations, allowed evolution to proceed, and then measured population fitness components such as lifespan, reproductive success, population extinction rate and mutation load.
@@
 A number of factors might influence the strength and sign of the correlation between sexual selection and population fitness.
-First, the genetic correlation between female fecundity and male mating/fertilisation success varies in sign and magnitude between species[@RN298] and even between conspecific populations[@RN201], implying that sexual selection on males increases mean female fitness in some species and populations but not others.
+First, the genetic correlation between female fecundity and male mating/fertilisation success varies in sign and magnitude between species [@RN298] and even between conspecific populations [@RN201], implying that sexual selection on males increases mean female fitness in some species and populations but not others.
 These inconsistencies could derive from differences in allele frequencies, or environmental differences that alter how genotype relates to phenotype and fitness.
-Second, it has been hypothesised that populations should display a more positive genetic correlation between male and female fitness – and thus potentially between mating/fertilisation success and population fitness – in novel or fluctuating environments, relative to stable environments[@RN187; @RN173; @RN74; @RN257].
-This is because stable environments create consistent selection, preferentially eroding genetic variation at sexually-concordant loci (i.e.
-loci where the fittest genotype is the same in both sexes) and leaving behind variation at sexually antagonistic loci.
-We know of no systematic reviews testing this latter theory, though it is has motivated several recent empirical tests (e.g.[@RN187; @RN200; @RN254]), and is relevant to conservation genetics.
+Second, it has been hypothesised that populations should display a more positive genetic correlation between male and female fitness – and thus potentially between mating/fertilisation success and population fitness – in novel or fluctuating environments, relative to stable environments [@RN187; @RN173; @RN74; @RN257].
+This is because stable environments create consistent selection, preferentially eroding genetic variation at sexually-concordant loci (*i.e.* loci where the fittest genotype is the same in both sexes) and leaving behind variation at sexually antagonistic loci.
+We know of no systematic reviews testing this latter theory, though it is has motivated several recent empirical tests [*e.g.* @RN187; @RN200; @RN254], and is relevant to conservation genetics.
 
@@
 Our principle aims were to measure the average net effect of sexual selection on the population-level mean and variance for various fitness components, to test whether this effect varies between stressful and benign environments, and identify key moderators of the effect size of sexual selection treatment.
+\phantomsection
 
 #Results
+\phantomsection
 
@@
 In total, we obtained effect sizes for 20 different fitness traits, with reproductive success ($n$ = 156) and offspring viability ($n$ = 56) being the most commonly-measured traits.
-We classified 216 effect sizes as direct measures of fitness, 147 as indirect, and the remaining 96 effect sizes as ambiguous (see Methods, Fig.
-1 and Table S1).
-Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, reproductive success, offspring viability and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration and early fecundity).
-Tables S4-S5 give a detailed description of our dataset.
+We classified 216 effect sizes as direct measures of fitness, 147 as indirect, and the remaining 96 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
+Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, reproductive success, offspring viability, and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, and early fecundity).
+\href{https://justincally.github.io/SexualSelection/#tables_of_sample_sizes}{Tables S4-S5} give a detailed description of our dataset.\phantomsection
 
-##Sexual selection is associated with higher mean values for most fitness components
+\subsection{Sexual selection is associated with higher mean values for most fitness \\components}
 
-The grand mean for all effect sizes was positive (REML $\beta$ = 0.23, 95% CIs: 0.01 to 0.44, $p$ = 0.038; Bayesian $\beta$ = 0.23, 95% CIs: -0.06 to 0.51, $BF_{>0}$ = 18), indicating that sexual selection typically had a net positive effect on the majority of populations and fitness components so far studied.
+The grand mean for all effect sizes (\hl{direct, indirect and ambiguous}) was positive (REML $\beta$ = 0.23, 95% CIs: 0.01 to 0.44, $p$ = 0.038; Bayesian $\beta$ = 0.23, 95% CIs: -0.06 to 0.51, $BF_{>0}$ = 18), indicating that sexual selection typically had a net positive effect on the majority of populations and fitness components so far studied.
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
-Sexual selection had a beneficial effect on most fitness traits, including all of the fitness traits that we classified as being ‘direct’ measurements of population fitness: extinction rate (REML $\beta$ = 0.37, 95% CIs: 0.01 to 0.73; Bayesian $\beta$ = 0.37, 95% CIs: -0.02 to 0.79, $BF_{>0}$ = 30.13; $n$ = 4), offspring viability (REML $\beta$ = 0.20, 95% CIs: 0.042 to 0.36; Bayesian $\beta$ = 0.21, 95% CIs: -0.04 to 0.47, $BF_{>0}$ = 24.89; $n$ = 56) and reproductive success (REML $\beta$ = 0.17, 95% CIs: 0.013 to 0.32; Bayesian $\beta$ = 0.18, 95% CIs: -0.06 to 0.44, $BF_{>0}$ = 15.53; $n$ = 156; Fig.
-1; Table S6).
+Sexual selection had a beneficial effect on most fitness traits, including all of the fitness traits that we classified as being ‘direct’ measurements of population fitness: extinction rate (REML $\beta$ = 0.37, 95% CIs: 0.01 to 0.73; Bayesian $\beta$ = 0.37, 95% CIs: -0.02 to 0.79, $BF_{>0}$ = 30.13; $n$ = 4), offspring viability (REML $\beta$ = 0.20, 95% CIs: 0.042 to 0.36; Bayesian $\beta$ = 0.21, 95% CIs: -0.04 to 0.47, $BF_{>0}$ = 24.89; $n$ = 56) and reproductive success (REML $\beta$ = 0.17, 95% CIs: 0.013 to 0.32; Bayesian $\beta$ = 0.18, 95% CIs: -0.06 to 0.44, $BF_{>0}$ = 15.53; $n$ = 156; \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6}).
 Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.49, 95% CIs: -0.72 to -0.26; Bayesian $\beta$ = -0.49, 95% CIs: -0.78 to -0.19, $BF_{>0}$ = 0.0054; $n$ = 35) and body condition (REML $\beta$ = -1.3, 95% CIs: -1.9 to -0.67; Bayesian $\beta$ = -1.3, 95% CIs: -1.9 to -0.63, $BF_{>0}$ = 0.00025, $n$ = 1).
-Fig.
-1 presents Bayesian estimates for each fitness component and Table S6 contains both Bayesian and REML estimates, with sample sizes and test statistics.
+\autoref{forest_plot} presents Bayesian estimates for each fitness component and \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6} contains both Bayesian and REML estimates, with sample sizes and test statistics.
+\phantomsection
 
@@
 
-We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect fitness (Table 1, 2).
-Sexual selection significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (e.g.
-a food source to which they were not well-adapted) than under benign conditions (Fig.
-2a, Table 2).
-Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (Fig.
-2a, Table 2).
-Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (Fig.
-2a, Table 2).
+We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect fitness (\hyperlink{page.13}{Table 1, 2}).
+Sexual selection significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
+Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
+Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
 
-Other moderator variables that we examined had minimal impacts on effect size (Fig.
-S2 and Table S7).
-Specifically, effect size did not depend on whether or not the study was conducted blind (Fig.
-S9), nor on the number of generations for which the experimental evolution study was run (Fig.
-S10 and Fig.
-S11).
+Other moderator variables that we examined had minimal impacts on effect size (\href{https://justincally.github.io/SexualSelection/#meta-analyses_including_many_moderator_variables}{Figure S2, Table S7}).
+Specifically, effect size did not depend on whether or not the study was conducted blind (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S9}), nor on the number of generations for which the experimental evolution study was run (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S10, S11}).
 
@@
 Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 61.5%, 95% CIs: 42.9-78.9%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 33.5%, 95% CIs: 15.8-52.7%).
-The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model implied a non-zero effect ($\sigma^2$ = 0.145 [0.006-0.517]; Table S10).
-Variation among taxa is explored further in the Supplementary Material, (Figure S3 and Table S8).
+The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model implied a non-zero effect ($\sigma^2$ = 0.145 [0.006-0.517]; \href{https://justincally.github.io/SexualSelection/#bayesian_model:_effects_of_environment_and_sex}{Table S10}).
+Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S3, Table S8}).
+\phantomsection
 
@@
 
-By applying meta-analysis to log coefficient of variation ratios (*lnCVRs*)[@RN177], we found evidence that sexual selection reduces phenotypic variation under certain conditions (Fig.
-2b).
+By applying meta-analysis to log coefficient of variation ratios [*lnCVR*; @RN177], we found evidence that sexual selection reduces phenotypic variation under certain conditions (\autoref{env_sex}b).
 Specifically, phenotypic variance was significantly reduced by sexual selection for fitness components measured in females under stressful conditions (*lnCVR* = -1.0, 95% CIs: -1.4 to -0.69).
-By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (Fig.
-2b; Tables S13-S16).
-However, as expected from the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.44, 95% CIs: -0.80 to -0.081; Fig.
-2b).
+By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (\autoref{env_sex}b; \href{https://justincally.github.io/SexualSelection/#obtaining_lncvr_and_meta-analysis_models}{Tables S13-S16}).
+However, as expected from the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.44, 95% CIs: -0.80 to -0.081; \autoref{env_sex}b).
 
@@
 Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 40.1 %, 95% CIs: 23.5 % to 60.2 %), fitness components ($I^2_{fitness\:components}$ = 38.7%, 95% CIs: 17.1-60.7%) and taxon ($I^2_{taxon}$ = 16.6, 95% CIs: 3.1-37.2%).
-<!-- We don't use Bayesian predictions for lnCVR, which is inconsistent with previous results -->
+\phantomsection
 
@@
 
-The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (Fig.
-3a; Egger’s test: *z* = 6.2, $p$ < 0.0001).
+The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (\autoref{publication_bias}a; Egger’s test: *z* = 6.2, $p$ < 0.0001).
 Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection.
-There was no significant relationship between effect size and journal impact factor (Fig.
-3b; $t_{437}$ = 1.2, $p$ = 0.25) or year of publication (Fig.
-3c; $t_{437}$ = -1.0, $p$ = 0.31); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured[@RN216; @RN217].
+There was no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.25) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.0, $p$ = 0.31); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
 
-```{r, echo = FALSE, fig.cap="Forest plot showing the effect of manipulation of sexual selection, for 20 fitness components from 65 studies.
+![Forest plot showing the effect of manipulation of sexual selection, for 20 fitness components from 65 studies.
 Effect sizes ($n$ = 459) varied between fitness components, and were more often positive than negative.
 Predicted average values are presented alongside each fitness component; those in bold have 95% confidence intervals that do not cross zero.
-The estimates presented here are Bayesian predictions, which were slightly more conservative than the REML predictions (Table S6)."}
-knitr::include_graphics("Figures/ForestPlot_edit3.pdf") #Not relative path
-```
+The estimates presented here are Bayesian predictions, which were slightly more conservative than the REML predictions (Table S6).\label{forest_plot}](Figures/ForestPlot_edit3.pdf)
 
-```{r, echo = FALSE, fig.cap="(**a**) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
+![(**a**) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
 (**b**) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals.
-The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Tables S12 and S14).
-Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median."}
-knitr::include_graphics("Figures/environment_variance_edit5.pdf") #Not relative path
-```
+The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Table S12 and S14).
+Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.\label{env_sex}](Figures/environment_variance_edit5.pdf)
 
-```{r, echo = FALSE, fig.cap= "Tests of publication bias are mixed and suggest publication bias may be present.
+![Tests of publication bias are mixed and suggest publication bias may be present.
 (**a**) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies.
 (**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias.
-For (**b**) and (**c**) point size is proportional to the precision of the effect size (i.e.
-the inverse of its variance)."}
-knitr::include_graphics("Figures/publicationbias.pdf") #Not relative path
-```
+For (**b**) and (**c**) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).\label{publication_bias}](Figures/publicationbias.pdf)
 
@@
 \newpage
+\nolinenumbers
 
-**Table 1:**Results for the multilevel meta-analysis model testing the effects of sexual selection in different environments and between sexes.
+**Table 1:** Results for the multilevel meta-analysis model testing the effects of sexual selection in different environments and between sexes.
 Moderator variables whose 95% confidence intervals do not cross zero are shown in bold.
+
 ```{r, echo = F}
@@
 
+\vspace{0.75 cm}
+
 **Table 2:** Hypothesis tests using restricted maximum likelihood (REML) or Bayesian methods, illustrating how sex and environmental stress interact to modulate effect size.
 Tests whose 95% confidence intervals do not cross zero are shown in bold.
+
 ```{r, echo = F}
@@
 \newpage
+\phantomsection
+\linenumbers
 
@@
 Fitness traits related to immunocompetence were an exception: sexual selection typically resulted in weaker immunity.
-This result is interesting in light of the hypothesised trade-off between sexually-selected phenotypes and immunity, for example due to immunosuppressive effects of sex hormones[@RN323; @RN324].
+This result is interesting in light of the hypothesised trade-off between sexually-selected phenotypes and immunity, for example, due to immunosuppressive effects of sex hormones [@RN323; @RN324].
 Furthermore, the overall benefit of sexual selection was greater for females than males, and this sex difference was magnified in stressful environments.
 Consistent with stronger selection on female fitness under stress, female phenotypic variance was substantially reduced when sexual selection was applied under stressful as opposed to benign conditions.
-These results suggest that sexual selection may contribute to population persistence under stressful conditions, such as fluctuating environmental change[@RN173] or spatial variability[@RN189], particularly since female reproductive output is often a limiting factor in population growth[@RN188].
+These results suggest that sexual selection may contribute to population persistence under stressful conditions, such as fluctuating environmental change [@RN173] or spatial variability [@RN189], particularly since female reproductive output is often a limiting factor in population growth [@RN188].
 
-The results of the meta-analysis support predictions that sexual selection can improve population fitness and accelerate adaptation[@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
-Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles through selection on males[@RN94; @RN198; @RN95].
+The results of the meta-analysis support predictions that sexual selection can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
+Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles through selection on males [@RN94; @RN198; @RN95].
 What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest).
-Below we discuss possible explanations for this result, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection[@RN317; @RN318].
+Below we discuss possible explanations for this result, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].
 
 Firstly, the response of male fitness to sexual selection may be constrained in species where the heritability of male fitness is influenced by the sex determination system.
-Males are heterogametic in many of the species in our sample (e.g.
-in species with XY or XO sex determination systems); this can reduce father-to-son heritability relative to mother-to-daughter, since sons never inherit the larger sex chromosome from their fathers[@RN340; @RN262; @RN147; @RN263], which might slow adaptation in male relative to female traits[@RN263; @RN259].
+Males are heterogametic in many of the species in our sample (*e.g.* in species with XY or XO sex determination systems); this can reduce father-to-son heritability relative to mother-to-daughter, since sons never inherit the larger sex chromosome from their fathers [@RN340; @RN262; @RN147; @RN263], which might slow adaptation in male relative to female traits [@RN263; @RN259].
 However, X-linkage is also likely to inflate the contribution of X-linked genes to fitness variance in the heterogametic sex.
@@
 Perhaps as a result of these conflicting predictions, there seems to be no clear consensus regarding sex-based differences in heritability.
-For instance, a systematic review found no difference in mean heritability between male and female traits, although there was a male-biased skew in heritability of reproductive traits[@RN342].
-Conversely, a recent association study in humans found a number of traits showing higher heritability in females than males[@RN325].
+For instance, a systematic review found no difference in mean heritability between male and female traits, although there was a male-biased skew in heritability of reproductive traits [@RN342].
+Conversely, a recent association study in humans found a number of traits showing higher heritability in females than males [@RN325].
 
 Secondly, selection on males might be weaker than selection on females, resulting in slower adaptation following experimental manipulation of sexual selection.
-This explanation may initially seem implausible, because net selection on males is generally assumed to be stronger than on females, due to the (actual or hypothesised) sex difference in sexual selection strength and inter-individual variance in fitness[@RN304; @RN303; @RN337; @RN338].
-However, an oft-overlooked aspect is that selection might frequently be ‘softer’ on males and ‘harder’ on females[@RN319], because the local competitive environment is usually more important for males than it is for females.
+This explanation may initially seem implausible, because net selection on males is generally assumed to be stronger than on females, due to the (actual or hypothesised) sex difference in sexual selection strength and inter-individual variance in fitness [@RN304; @RN303; @RN337; @RN338].
+However, an oft-overlooked aspect is that selection might frequently be ‘softer’ on males and ‘harder’ on females [@RN319], because the local competitive environment is usually more important for males than it is for females.
 For instance, a mediocre male genotype can have high fitness provided it outcompetes its local rivals, while low-fitness female genotypes are likely to produce few offspring even when competing with other low-fitness females.
 Therefore, improvements in genetic quality should have stronger diminishing returns in males, possibly contributing to our finding that the genetic consequences of sexual selection lead to greater fitness benefits for females.
-Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the nature of selection, relative to expectations for large, natural populations[@RN322; @RN277; @RN112].
-For example, many studies[@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then mixed and randomly sampled to create the next generation; this design ensures that successful males simply needed to outcompete their rival(s) in the same sub-population, while each female's reproductive output is measured against the entire female population.
+Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the nature of selection, relative to expectations for large, natural populations [@RN322; @RN277; @RN112].
+For example, many studies [@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then mixed and randomly sampled to create the next generation; this design ensures that successful males simply needed to outcompete their rival(s) in the same sub-population, while each female's reproductive output is measured against the entire female population.
 
@@
 Recent work has emphasised that environmental stress should reduce the strength of sexually antagonistic selection relative to selection that is concordant between sexes.
-Theoretical models reaching this conclusion[@RN67; @RN173] have been supported by empirical studies[@RN187; @RN74; @RN243]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress[@RN74].
-However, other quantitative genetic studies have shown that stressful conditions do not always reduce sexual antagonism[@RN297; @RN200; @RN257].
-Variation in effects of sexual selection in stressful environments may be due to potentially variable responses amongst taxa[@RN298] and environments.
-Notably, Connallon and Hall[@RN173] predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it.
+Theoretical models reaching this conclusion [@RN67; @RN173] have been supported by empirical studies [@RN187; @RN74; @RN243]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress [@RN74].
+However, other quantitative genetic studies have shown that stressful conditions do not always reduce sexual antagonism [@RN297; @RN200; @RN257].
+Variation in effects of sexual selection in stressful environments may be due to potentially variable responses amongst taxa [@RN298] and environments.
+Notably, @RN173 predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it.
 Our meta-analysis suggests that under directional selection imposed by environmental stress, sexual antagonism is likely dampened; allowing sexual selection to facilitate adaptation and persistence.
 
-Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as commonly is the case for studies in ecology and evolution[@RN208].
+Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as commonly is the case for studies in ecology and evolution [@RN208].
 Most of the heterogeneity was explained by study and the fitness component that was measured, while the taxon, number of generations of evolution, and use of blinding showed less impact on effect size.
 Taxonomic diversity is limited in experimental evolution studies, which mostly use lab-suitable invertebrates with similar mating systems and sex determination.
-However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates (fish, insects, birds, spiders, reptiles, mammals)[@RN165].
-Despite this, taxonomic differences in the effects of sexual selection on fitness or patterns of diversity are often expected due to differences in mating systems[@RN277] and sex-determination systems[@RN262].
-For example, mate choice is thought to be more prevalent in taxa with well-developed parental care[@RN196], affecting the strength and nature of sexual selection.
+However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates [fish, insects, birds, spiders, reptiles, mammals; @RN165].
+Despite this, taxonomic differences in the effects of sexual selection on fitness or patterns of diversity are often expected due to differences in mating systems [@RN277] and sex-determination systems [@RN262].
+For example, mate choice is thought to be more prevalent in taxa with well-developed parental care [@RN196], affecting the strength and nature of sexual selection.
 Furthermore, male heterogametic taxa, including those commonly used in experimental evolution such as flies (Diptera), beetles (Coleoptera) and mice (Mammalia), are likely to have higher heritability of fitness from mothers to daughters.
@@
 Our findings have implications for fundamental and applied research.
-For example, the beneficial population-level consequences of sexual selection have been proposed as one possible resolution to the long-standing evolutionary puzzle presented by sexual reproduction[@RN309].
-If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants that arise in their midst[@RN94; @RN308; @RN198].
-Sexual selection is also important for conservation[@RN25] and captive breeding programs[@RN117].
-Within captive breeding programs, genetic diversity is often managed through the enforced monogamy of a strategically selected (genetically diverse) breeding pair[@RN117].
-Captive breeding programs may benefit from allowing sexual selection of 'good genes' or more compatible genes[@RN294], or by increasing maternal investment by females paired with 'attractive' males[@RN291; @RN292; @RN293].
-Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution, could reduce the genetic quality of the population, and potentially compromise its long-term persistence[@RN332; @RN331; @RN47; @RN333; @RN330].
-Equally, our results support recent evidence that human activities that directly counteract sexual selection, such as selective harvesting of the largest or most ornamented males, can lower population fitness[@RN334].
+For example, the beneficial population-level consequences of sexual selection have been proposed as one possible resolution to the long-standing evolutionary puzzle presented by sexual reproduction [@RN309].
+If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants that arise in their midst [@RN94; @RN308; @RN198].
+Sexual selection is also important for conservation [@RN25] and captive breeding programs [@RN117].
+Within captive breeding programs, genetic diversity is often managed through the enforced monogamy of a strategically selected (genetically diverse) breeding pair [@RN117].
+Captive breeding programs may benefit from allowing sexual selection of 'good genes' or more compatible genes [@RN294], or by increasing maternal investment by females paired with 'attractive' males [@RN291; @RN292; @RN293].
+Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution, could reduce the genetic quality of the population, and potentially compromise its long-term persistence [@RN332; @RN331; @RN47; @RN333; @RN330].
+Equally, our results support recent evidence that human activities that directly counteract sexual selection, such as selective harvesting of the largest or most ornamented males, can lower population fitness [@RN334].
 Based on the weight of evidence from experimental evolution, we suggest that sexually-selected populations may be more resilient to environmental change, including anthropogenic environmental pressures, over relevant time scales.
+\phantomsection
 
 #Materials and methods
+\phantomsection
 
@@
 We searched *ISI Web of Science* and *Scopus* on 9^th^ June 2017 for peer-reviewed, English language studies that manipulated the presence or strength of sexual selection using experimental evolution, and then measured some proxy of population fitness.
-A detailed list of search terms is given in the Electronic Supplementary Material (ESM).
+A detailed list of search terms is given in the Electronic Supplementary Material (\href{https://justincally.github.io/SexualSelection/}{ESM}).
 
-After removing duplicates, we read the titles and abstracts of the remaining 1015 papers and removed those that did not fit our inclusion criteria (typically because they did not present primary experimental evolution data).
-This left 130 papers, for which we read the full text and applied the inclusion criteria outlined in the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) diagram (Fig.
-4).
+After removing duplicates, we read the titles and abstracts of the remaining 1,015 papers and removed those that did not fit our inclusion criteria (typically because they did not present primary experimental evolution data).
+This left 130 papers, for which we read the full text and applied the inclusion criteria outlined in the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) diagram (\autoref{prisma_flow}).
 Briefly, we included studies that 1) were conducted in a dioecious animal species, 2) experimentally manipulated the strength of sexual selection (*e.g.*, via experimentally-enforced random monogamy or an altered sex ratio) for at least one generation, and 3) measured a trait that we judged to be a potential correlate of population fitness.
@@
 We therefore relied on our best judgement when deciding what outcomes were correlated with population fitness.
-We categorised the fitness outcomes into three categories: ambiguous, indirect and direct (detailed in Table S1).
+We categorised the fitness outcomes into three categories: ambiguous, indirect and direct (detailed in \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
 Briefly, ambiguous measures of fitness were those that are reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration and early fecundity).
@@
 Finally, direct measures of fitness (reproductive success, offspring viability and extinction rate) are those that measure fitness through components of reproduction or long-term viability.
-The ESM describes why specific papers recovered in the literature search were included or excluded (Table S2).
+The ESM describes why specific papers recovered in the literature search were included or excluded (\href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S2}).
 
-Of the 130 papers subjected to detailed screening, 62 were excluded based on the PRISMA criteria (Fig.
-4).
+Of the 130 papers subjected to detailed screening, 62 were excluded based on the PRISMA criteria (\autoref{prisma_flow}).
 Additionally, three papers presented insufficient information to calculate effect size.
@@
 The final meta-analysis covered data from 65 papers.
+
+![Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.\label{prisma_flow}](Figures/PRISMA\ Chart.pdf)
+
+\phantomsection
 
@@
 Typically, there were two or three treatments, which varied in the strength of sexual selection.
-For some papers, summary statistics were not written down, but were presented in a figure such as a bar chart: in these cases, we extracted the data using *WebPlotDigitizer* v.3.12[@RN195].
+For some papers, summary statistics were not written down, but were presented in a figure such as a bar chart: in these cases, we extracted the data using *WebPlotDigitizer* v.3.12 [@RN195].
 If the treatment means were not reported (and the raw data were unavailable), we instead calculated effect size from test statistics comparing treatment means (*e.g.*, $F$, $t$, $z$ or $\chi^2$ values), which we used to estimate effect size using several formulae (see below).
@@
 
-In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see Table S3 and associated ESM).
+In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see \href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{Table S3} and associated ESM).
 The moderators were selected due to their ready availability, and because we hypothesised that they might explain some of the observed heterogeneity in effect size.
@@
 Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), blinding of researchers to treatments and number of generations a treatment group underwent experimentally evolution.
-In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the ESM (Table S3).
-
-```{r, echo = FALSE, fig.cap="Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets."}
-knitr::include_graphics("Figures/PRISMA\ Chart.pdf ") #Not relative path
-```
-
-\newpage
+In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the ESM (\href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{Table S3}).
+\phantomsection
 
@@
 
-For each measurement of each pair of treatments, we estimated the standardised effect size Hedges’ *g*[@RN204].
-Similar to Cohen’s *d*, Hedges’ *g* expresses the difference in means in terms of standard deviations (making it dimensionless), but it is more robust to unequal sampling and small sample sizes[@RN209].
-For comparisons of extracted treatment means, we calculated Hedges’ *g* using the ``mes`` function in the *compute.es* R package[@RN179].
+For each measurement of each pair of treatments, we estimated the standardised effect size Hedges’ *g* [@RN204].
+Similar to Cohen’s *d*, Hedges’ *g* expresses the difference in means in terms of standard deviations (making it dimensionless), but it is more robust to unequal sampling and small sample sizes [@RN209].
+For comparisons of extracted treatment means, we calculated Hedges’ *g* using the ``mes`` function in the *compute.es* R package [@RN179].
 To calculate Hedges' *g* from test statistics, we used the ``fes``, ``chies``, and ``tes`` functions in the *compute.es* package (for $F$, $\chi^2$ and $t$ statistics, respectively).
-The ``propes`` function was used to calculate effect size from a difference in proportions; in two cases[@RN327; @RN329], a proportion was equal to one (producing infinite effect sizes), and so we subtracted one from the numerator when estimating Hedges’ g.
+The ``propes`` function was used to calculate effect size from a difference in proportions; in two cases [@RN327; @RN329], a proportion was equal to one (producing infinite effect sizes), and so we subtracted one from the numerator when estimating Hedges’ g.
 In all cases, we selected a direction for the effect size calculation such that in our meta-analysis, negative effect sizes indicate that the removal of sexual selection was associated with higher fitness trait values, and positive effect sizes indicate higher fitness when sexual selection was elevated or left intact.
-We also inverted the sign of effect sizes pertaining to measurements that are expected to be negatively related to population fitness (e.g.
-parasite load, mutation load, extinction risk/rate, mating duration (females), mating latency (males), and rate of senescence).
+We also inverted the sign of effect sizes pertaining to measurements that are expected to be negatively related to population fitness (*e.g.*, parasite load, mutation load, extinction risk/rate, mating duration (females), mating latency (males), and rate of senescence).
 Because many of our 65 papers measured multiple fitness outcomes, studied multiple replicate populations, or had three or more sexual selection treatments, we calculated a total of 459 effect sizes.
 
-For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*)[@RN177].
-The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups[@RN177; @RN190], and so we were only able to calculate lnCVR for 356 of 459 comparisons.
+For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177].
+The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 356 of 459 comparisons.
+\phantomsection
 
-## Mixed effects meta-analysis
+##Mixed-effects meta-analysis
 
@@
 We again fit study ID, fitness component, and taxon as random/group level effects.
-Models investigating other moderators such as number of generations and blinding are presented in the ESM.
+Models investigating other moderators such as number of generations and blinding are presented in the \href{https://justincally.github.io/SexualSelection/}{ESM}.
 
-Meta-analyses fit by REML were implemented in the *metafor* ``R`` package (v.
-2.0)[@RN212], while their Bayesian equivalents used the *brms* ``R`` package (v.
-2.3.1)[@RN290] to specify and run models in the Stan programming language.
+Meta-analyses fit by REML were implemented in the *metafor* ``R`` package [v.
+2.0; @RN212], while their Bayesian equivalents used the *brms* ``R`` package [v.
+2.3.1; @RN290] to specify and run models in the Stan programming language.
+\phantomsection
 
@@
 
-We tested for publication bias via funnel plots, using Egger’s test to quantify plot asymmetry[@RN213; @RN214].
-However, funnel plot asymmetry does not necessarily indicate publication bias; asymmetry can arise simply through between-study heterogeneity[@RN215].
+We tested for publication bias via funnel plots, using Egger’s test to quantify plot asymmetry [@RN213; @RN214].
+However, funnel plot asymmetry does not necessarily indicate publication bias; asymmetry can arise simply through between-study heterogeneity [@RN215].
 Thus, we utilised several other methods for checking publication bias.
-We investigated whether the time-lag bias[@RN216] – where effect size magnitudes decrease over successive years – is present.
-Additionally, we assessed a potential source of publication bias through the correlation between effect size and journal impact factor[@RN217], which can arise if null or countervailing results are more difficult to publish.
-The journal impact factor for each effect size at the time of publication was obtained using *InCites Journal Citation Reports*.
+We investigated whether the time-lag bias [@RN216] – where effect size magnitudes decrease over successive years – is present.
+Additionally, we assessed a potential source of publication bias through the correlation between effect size and journal impact factor [@RN217], which can arise if null or countervailing results are more difficult to publish.
+The journal impact factor for each effect size at the time of publication was obtained using *InCites Journal Citation Reports*.\phantomsection
 
@@
 The repository (**link hidden for double bind review**) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results.
+\phantomsection
 
@@
 
-\newpage
+\newpage\phantomsection
+
 # References

### 2018-11-26 meta_analysis_sexual_selection_pop_fitness.Rmd
Lots of changes to the data, supp and reviewer comments

@@
 library(rstan) #Note that installation requires some effort: dependency for brms
+#devtools::install_github("paul-buerkner/brms")
 library(brms) 
@@
 library(cowplot)
+#devtools::install_github("eclarke/ggbeeswarm")
+library(ggbeeswarm)
 source("I2_function.R") #Adapted function for obtaining I2 with CIs
@@
 ```{r echo=FALSE, results='hide', warning=FALSE}
-library(knitr) # set up cacheing to save time when re-building the html document
+knitr::opts_knit$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
 ```
@@
 
-____________
-
-### Forest Plot
+______________
+
+## Meta-Analysis
+
+### Overall effect of sexual selection on fitness
+
+We can obtain an overall weghted grand mean and confidence intervals with a simple intercept only for both Bayesian and REML models.
+Notably, in both models the estimates are approximately the same, with Bayesian estimates being marginally wider.
+The priors for ``brms`` are set from a weakly non-informative student t-distribution: ``student_t(3, 0, 10)``.
+We also tested that using a stronger prior (e.g.
+standard normal distribution: ``normal(0, 1)``) has negligible effects on the model results.
+
+#### Run the Bayesian meta-analysis to get the overall effect
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/grand.mean.bayes.rds")){
+  grand.mean.bayes <- brm(g | se(SE)  ~ 1 # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
+                          + (1|Study.ID)
+                          + (1|Outcome)
+                          + (1|Taxon), 
+                          family = "gaussian", 
+                          seed = 1,
+                          cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                          control = list(adapt_delta = 0.999, max_treedepth = 15),
+                          data = full_dataset %>% mutate(SE = sqrt(var.g)))
+
+  saveRDS(grand.mean.bayes, "data/grand.mean.bayes.rds") # Save to avoid re-running during knit
+}
+grand.mean.bayes <- readRDS("data/grand.mean.bayes.rds")
+
+```
+
+#### Run the REML meta-analysis to get the overall effect
+```{r}
+forest.model <- rma.mv(g, var.g,
+                       mods = ~ 1,
+                       random = list(~ 1 | Study.ID,
+                                      ~ 1 | Outcome,
+                                      ~ 1 | Taxon),
+                       method = "REML",
+                       data = full_dataset)
+```
+
+#### Inspect the effect sizes esimates from these two models
+
+These estimates are presented in the text of the Results section. The test statistic is either the p-value (REML) or Bayes factor (BF) comparing the effect size to zero (Bayesian).
+```{r}
+pander(data.frame(
+  Method = c("REML", "Bayesian"),
+  Grand_mean_effect_size_g = c(forest.model$b, summary(grand.mean.bayes)$fixed[,"Estimate"]),
+  Lower_95_CI = c(forest.model$ci.lb, summary(grand.mean.bayes)$fixed[,"l-95% CI"]),
+  Upper_95_CI = c(forest.model$ci.ub, summary(grand.mean.bayes)$fixed[,"u-95% CI"]),
+  Test_statistic = c(forest.model$pval, hypothesis(grand.mean.bayes, "Intercept > 0")$hypothesis$Evid.Ratio)), digits = 2) 
+```
+
+### Effect of sexual selection on direct, indirect and ambiguous measures of fitness
+
+The mean effect size may also be calculated for each of the three fitness trait classes (Ambiguous, Indirect and Direct)
+
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/grand.mean.class.bayes.rds")){
+  grand.mean.class.bayes <- brm(g | se(SE)  ~ Outcome.Class # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
+                          + (1|Study.ID)
+                          + (1|Taxon), 
+                          family = "gaussian", 
+                          seed = 1,
+                          cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
+                          control = list(adapt_delta = 0.9999, max_treedepth = 15),
+                          data = full_dataset %>% mutate(SE = sqrt(var.g)))
+
+  saveRDS(grand.mean.class.bayes, "data/grand.mean.class.bayes.rds") # Save to avoid re-running during knit
+}
+grand.mean.class.bayes <- readRDS("data/grand.mean.class.bayes.rds")
+
+# Define new data for prediction
+brms.newdata.class <- as.data.frame(expand.grid(Outcome.Class = unique(full_dataset$Outcome.Class)))
+
+# Get average SE: useful if using predict, but not fitted
+av.se.g.class <- full_dataset %>% group_by(Outcome.Class) %>% summarise(mean = mean(sqrt(var.g)))
+brms.newdata.class$SE <- av.se.g.class$mean
+
+# Find the fitted values (i.e. predictions from the linear mixed model fit by brms)
+brms.predict.class <- fitted(grand.mean.class.bayes, newdata = brms.newdata.class, re_formula = NA) %>% as.data.frame()
+brms.predictions.class <- data.frame(brms.newdata.class$Outcome.Class, brms.predict.class$Estimate, brms.predict.class$Est.Error, brms.predict.class$Q2.5, brms.predict.class$Q97.5)
+
+#Name columns
+colnames(brms.predictions.class) <- c("Relationship to Fitness", "Bayes Prediction", "Bayes SE", "Bayes LCI", "Bayes UCI")
+
+outcome.list.factor.class <-  c('Indirect', 'Ambiguous', 'Direct')
+
+brms.predictions.class <- brms.predictions.class[match(outcome.list.factor.class, brms.predictions.class$`Relationship to Fitness`),]
+rownames(brms.predictions.class) <- NULL
+sample.sizes.outcome.class <- as.data.frame(table(full_dataset$Outcome.Class))
+colnames(sample.sizes.outcome.class) <- c("Relationship to Fitness", "n")
+fitness.class.predictions <- left_join(brms.predictions.class, sample.sizes.outcome.class, by = "Relationship to Fitness")
+
+# Obtain Bayes Factor of likelihood that the outcome is greater than 0
+BF.outcome.class.list <-  c('Ambiguous', 'Direct')
+# Obtain BF for all components
+Hypotheses <- list()
+BFs <- list()
+Hypotheses[["Indirect"]] <- hypothesis(grand.mean.class.bayes, "Intercept > 0") #Intercept in model, need to do it by itself
+BFs[["Indirect"]] <- Hypotheses[["Indirect"]][["hypothesis"]][["Evid.Ratio"]]
+for (i in BF.outcome.class.list){
+  Hypotheses[[i]] <- hypothesis(grand.mean.class.bayes, paste("Intercept + Outcome.Class", i," > 0", sep = ""))
+  BFs[[i]] <- Hypotheses[[i]][["hypothesis"]][["Evid.Ratio"]]
+} #Loop over all fitness compoinents
+
+# Now for REML. Not easy because the predict function for rma.mv has an odd interface
+model.fitness.class.REML <- rma.mv(g, var.g, mods = ~ 1 + Outcome.Class,
+                         random = list(~ 1 | Study.ID,
+                                       ~ 1 | Taxon),
+                         method = "REML",
+                         data = full_dataset)
+
+get.predictions.class <- function(newdata){
+  Indirect <- 0; Ambiguous <- 0; Direct <- 0
+  if(newdata[1] == 'Ambiguous') Ambiguous<-1
+  if(newdata[1] == 'Direct') Direct<-1
+
+  predict(model.fitness.class.REML, newmods=c(Ambiguous, Direct))
+}
+# Get the predictions for each combination of moderators
+predictions.class <- as.data.frame(expand.grid(Outcome.Class = outcome.list.factor.class))
+predictions.class <- cbind(predictions.class, do.call("rbind", apply(predictions.class, 1, get.predictions.class))) %>%
+  select(Outcome.Class, pred, se, ci.lb, ci.ub) 
+for(i in 2:5) predictions.class[,i] <- unlist(predictions.class[,i])
+
+colnames(predictions.class) <- c("Relationship to Fitness", "REML Prediction", "REML SE", "REML LCI", "REML UCI")
+predictions.class <- format(predictions.class, digits = 2)
+
+fitness.class.predictions <- fitness.class.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% `row.names<-`(NULL) %>% format(digits = 2)
+
+left_join(fitness.class.predictions, predictions.class, by = "Relationship to Fitness") %>% pander(split.table = Inf, digits = 2)
+
+```
+
+From this data we can generate a forest plot with the following:
+
+```{r}
+pd <- position_dodge(0.3)
+predictions.class[,2:5] <- sapply(predictions.class[,2:5], as.numeric)
+forest.plot.class <- predictions.class %>%
+  rename(Outcome.Class = "Relationship to Fitness",
+         Pred = 'REML Prediction',
+         LCI = 'REML LCI',
+         UCI = 'REML UCI') %>%
+  mutate(Outcome.Class = factor(Outcome.Class, levels = c("Direct", "Indirect", "Ambiguous"))) %>%
+  ggplot(aes(x = Outcome.Class, y = Pred, colour = Outcome.Class, fill = Outcome.Class)) + 
+  geom_hline(yintercept = 0, linetype = 2) + 
+  geom_hline(yintercept = 0.23, linetype = 2, colour = "steelblue", size = 1) +
+  geom_quasirandom(data = full_dataset %>% 
+  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female"),
+         Outcome.Class = factor(Outcome.Class, levels = c("Direct", "Indirect", "Ambiguous"))),
+                   aes(x = Outcome.Class, y = g), alpha=0.4) +
+  geom_errorbar(mapping = aes(ymin = LCI, ymax = UCI), width = 0, position = pd, size=1, colour = "grey10") + 
+  geom_point(position = pd, size=3.25, shape = 23, stroke = .75, color = "grey10") + 
+  ylab("Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]") +
+  theme_minimal(12) +
+  theme(panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(), legend.position = "none") +
+  scale_color_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
+                     name = "Relationship\nto fitness")+
+  scale_fill_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
+                     name = "Relationship\nto fitness")+
+  xlab("Relationship to Fitness")+
+  coord_flip()
+
+forest.plot.class
+```
+
+____________________
+
+### Effect of Sexual Selection for different fitness components
+
+#### Forest Plot
 
@@
 # Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
-full_dataset$Outcome_f = factor(full_dataset$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
+full_dataset$Outcome_f = factor(full_dataset$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
 
@@
 
-  scale_x_continuous(limits=c(-3.35, 12), 
+  scale_x_continuous(limits=c(-3.35, 4.25), 
                      breaks = c(-3, -2, -1, 0, 1, 2, 3), 
-                     name='                              Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
+                     name='Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
 
@@
                                   face = "bold"),
-        axis.title.x = element_text(hjust = 0, size = 12))
+        axis.title.x = element_text(hjust = 0.5, size = 14))
 
@@
 Positive values indicate fitness benefits of sexual selection.
-
-______________
-
-## Meta-Analysis
-
-### Overall effect of sexual selection on fitness
-
-We can obtain an overall weghted grand mean and confidence intervals with a simple intercept only for both Bayesian and REML models.
-Notably, in both models the estimates are approximately the same, with Bayesian estimates being marginally wider.
-The priors for ``brms`` are set from a weakly non-informative student t-distribution: ``student_t(3, 0, 10)``.
-We also tested that using a stronger prior (e.g.
-standard normal distribution: ``normal(0, 1)``) has negligible effects on the model results.
-
-#### Run the Bayesian meta-analysis to get the overall effect
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
-if(!file.exists("data/grand.mean.bayes.rds")){
-  grand.mean.bayes <- brm(g | se(SE)  ~ 1 # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
-                          + (1|Study.ID)
-                          + (1|Outcome)
-                          + (1|Taxon), 
-                          family = "gaussian", 
-                          seed = 1,
-                          cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
-                          control = list(adapt_delta = 0.9999, max_treedepth = 15),
-                          data = full_dataset %>% mutate(SE = sqrt(var.g)))
-
-  saveRDS(grand.mean.bayes, "data/grand.mean.bayes.rds") # Save to avoid re-running during knit
-}
-grand.mean.bayes <- readRDS("data/grand.mean.bayes.rds")
-```
-
-#### Run the REML meta-analysis to get the overall effect
-```{r}
-forest.model <- rma.mv(g, var.g,
-                       mods = ~ 1,
-                       random = list(~ 1 | Study.ID,
-                                      ~ 1 | Outcome,
-                                      ~ 1 | Taxon),
-                       method = "REML",
-                       data = full_dataset)
-```
-
-#### Inspect the effect sizes esimates from these two models
-
-These estimates are presented in the text of the Results section. The test statistic is either the p-value (REML) or Bayes factor comparing the effect size to zero (Bayesian).
-```{r}
-pander(data.frame(
-  Method = c("REML", "Bayesian"),
-  Grand_mean_effect_size_g = c(forest.model$b, summary(grand.mean.bayes)$fixed[,"Estimate"]),
-  Lower_95_CI = c(forest.model$ci.lb, summary(grand.mean.bayes)$fixed[,"l-95% CI"]),
-  Upper_95_CI = c(forest.model$ci.ub, summary(grand.mean.bayes)$fixed[,"u-95% CI"]),
-  Test_statistic = c(forest.model$pval, hypothesis(grand.mean.bayes, "Intercept > 0")$hypothesis$Evid.Ratio)), digits = 2) 
-```
-
-____________________
-
-### Effect of Sexual Selection for different fitness components
 
@@
 components.brms <- readRDS(file = "data/components.brms.rds") 
-
-make_text_summary(components.brms) %>% 
-  add_significance_stars() %>% 
-  tibble::rownames_to_column("Model Parameter") %>% 
-  pander(split.cell = 40, split.table = Inf)
 ```
@@
 Where values greater than 1 correspond to higher likelihood of the effect size being positive and values less than 1 suggest that the effect size is more likely to be negative.
-The right side of the table provides the REML estimates with SE and CIs.
+The right side of the table provides the REML estimates with SE and 95 % CIs.
 
@@
 #Name columns
-colnames(brms.predictions) <- c("Fitness Component", "Bayes Prediction", "Bayes SE", "Bayes L_95_CI", "Bayes U_95_CI")
-
-outcome.list.factor <-  c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+colnames(brms.predictions) <- c("Fitness Component", "Bayes Prediction", "Bayes SE", "Bayes LCI", "Bayes UCI")
+
+outcome.list.factor <-  c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
 
@@
 # Obtain Bayes Factor of likelihood that the outcome is greater than 0
-BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
 # Obtain BF for all components
@@
 left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component") %>% pander(split.table = Inf, digits = 2)
+```
+
+Individual Meta-analyses for each fitness related trait with n>3:
+
+```{r, warning = FALSE}
+outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
+names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
+                          mods = ~ 1, 
+                          method = "REML",
+                          random = list(~ 1 | Study.ID,
+                                       ~ 1 | Taxon),
+                          subset = (Outcome_f == x),
+                          data = full_dataset))
+
+df.list <- as.data.frame(do.call("rbind", outcome.models)) # data frame of model results
+
+simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))
+# simple.frame$vi <- as.matrix(simple.frame$vi)
+# simple.frame$W <- diag(1/(simple.frame$vi))
+# 
+# XO <- model.matrix(model.complete2)
+# PO <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+# 100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
+
+#I couldn't get mapply to work when calculating I2 so I calculated them manually.
+
+#Body Size 
+restricted.dataBS <- full_dataset %>% filter(full_dataset$Outcome == "Body Size")
+
+#Run estimate of heterogeneity
+WBS = diag(1/restricted.dataBS$var.g)
+XBS = model.matrix(outcome.models[["Body Size"]])
+PBS = WBS - WBS %*% XBS %*% solve(t(XBS) %*% WBS %*% XBS) %*% t(XBS) %*% WBS
+BodySizeI2 <- 100 * sum(outcome.models[["Body Size"]]$sigma2) / (sum(outcome.models[["Body Size"]]$sigma2) + (outcome.models[["Body Size"]]$k-outcome.models[["Body Size"]]$p)/sum(diag(PBS)))
+
+#Development Rate 
+restricted.dataDR <- full_dataset %>% filter(full_dataset$Outcome == "Development Rate")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataDR$var.g)
+X = model.matrix(outcome.models[["Development Rate"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+DevelopmentRateI2 <- 100 * sum(outcome.models[["Development Rate"]]$sigma2) / (sum(outcome.models[["Development Rate"]]$sigma2) + (outcome.models[["Development Rate"]]$k-outcome.models[["Development Rate"]]$p)/sum(diag(P)))
+
+#Early Fecundity 
+restricted.dataEF <- full_dataset %>% filter(full_dataset$Outcome == "Early Fecundity")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataEF$var.g)
+X = model.matrix(outcome.models[["Early Fecundity"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+EarlyFecundityI2 <- 100 * sum(outcome.models[["Early Fecundity"]]$sigma2) / (sum(outcome.models[["Early Fecundity"]]$sigma2) + (outcome.models[["Early Fecundity"]]$k-outcome.models[["Early Fecundity"]]$p)/sum(diag(P)))
+
+#Immunity
+restricted.dataI <- full_dataset %>% filter(full_dataset$Outcome == "Immunity")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataI$var.g)
+X = model.matrix(outcome.models[["Immunity"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+ImmunityI2 <- 100 * sum(outcome.models[["Immunity"]]$sigma2) / (sum(outcome.models[["Immunity"]]$sigma2) + (outcome.models[["Immunity"]]$k-outcome.models[["Immunity"]]$p)/sum(diag(P)))
+
+#Mating Duration
+restricted.dataMD <- full_dataset %>% filter(full_dataset$Outcome == "Mating Duration")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMD$var.g)
+X = model.matrix(outcome.models[["Mating Duration"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MatingDurationI2 <- 100 * sum(outcome.models[["Mating Duration"]]$sigma2) / (sum(outcome.models[["Mating Duration"]]$sigma2) + (outcome.models[["Mating Duration"]]$k-outcome.models[["Mating Duration"]]$p)/sum(diag(P)))
+
+#Mutant Frequency
+restricted.dataMF <- full_dataset %>% filter(full_dataset$Outcome == "Mutant Frequency")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMF$var.g)
+X = model.matrix(outcome.models[["Mutant Frequency"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MutantFrequencyI2 <- 100 * sum(outcome.models[["Mutant Frequency"]]$sigma2) / (sum(outcome.models[["Mutant Frequency"]]$sigma2) + (outcome.models[["Mutant Frequency"]]$k-outcome.models[["Mutant Frequency"]]$p)/sum(diag(P)))
+
+#Fitness Senescence
+restricted.dataFS <- full_dataset %>% filter(full_dataset$Outcome == "Fitness Senescence")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataFS$var.g)
+X = model.matrix(outcome.models[["Fitness Senescence"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+FitnessSenescenceI2 <- 100 * sum(outcome.models[["Fitness Senescence"]]$sigma2) / (sum(outcome.models[["Fitness Senescence"]]$sigma2) + (outcome.models[["Fitness Senescence"]]$k-outcome.models[["Fitness Senescence"]]$p)/sum(diag(P)))
+
+#Lifespan
+restricted.dataL <- full_dataset %>% filter(full_dataset$Outcome == "Lifespan")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataL$var.g)
+X = model.matrix(outcome.models[["Lifespan"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+LifespanI2 <- 100 * sum(outcome.models[["Lifespan"]]$sigma2) / (sum(outcome.models[["Lifespan"]]$sigma2) + (outcome.models[["Lifespan"]]$k-outcome.models[["Lifespan"]]$p)/sum(diag(P)))
+
+#Male Attractiveness
+restricted.dataMA <- full_dataset %>% filter(full_dataset$Outcome == "Male Attractiveness")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMA$var.g)
+X = model.matrix(outcome.models[["Male Attractiveness"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MaleAttractivenessI2 <- 100 * sum(outcome.models[["Male Attractiveness"]]$sigma2) / (sum(outcome.models[["Male Attractiveness"]]$sigma2) + (outcome.models[["Male Attractiveness"]]$k-outcome.models[["Male Attractiveness"]]$p)/sum(diag(P)))
+
+#Mating Frequency
+restricted.dataMF <- full_dataset %>% filter(full_dataset$Outcome == "Mating Frequency")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMF$var.g)
+X = model.matrix(outcome.models[["Mating Frequency"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MatingFrequencyI2 <- 100 * sum(outcome.models[["Mating Frequency"]]$sigma2) / (sum(outcome.models[["Mating Frequency"]]$sigma2) + (outcome.models[["Mating Frequency"]]$k-outcome.models[["Mating Frequency"]]$p)/sum(diag(P)))
+
+#Mating Latency
+restricted.dataML <- full_dataset %>% filter(full_dataset$Outcome == "Mating Latency")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataML$var.g)
+X = model.matrix(outcome.models[["Mating Latency"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MatingLatencyI2 <- 100 * sum(outcome.models[["Mating Latency"]]$sigma2) / (sum(outcome.models[["Mating Latency"]]$sigma2) + (outcome.models[["Mating Latency"]]$k-outcome.models[["Mating Latency"]]$p)/sum(diag(P)))
+
+#Mating Success
+restricted.dataMS <- full_dataset %>% filter(full_dataset$Outcome == "Mating Success")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMS$var.g)
+X = model.matrix(outcome.models[["Mating Success"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MatingSuccessI2 <- 100 * sum(outcome.models[["Mating Success"]]$sigma2) / (sum(outcome.models[["Mating Success"]]$sigma2) + (outcome.models[["Mating Success"]]$k-outcome.models[["Mating Success"]]$p)/sum(diag(P)))
+
+#Ejaculate Quality and Production
+restricted.dataEQ <- full_dataset %>% filter(full_dataset$Outcome == "Ejaculate Quality and Production")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataEQ$var.g)
+X = model.matrix(outcome.models[["Ejaculate Quality and Production"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+EjaculateQualityI2 <- 100 * sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) / (sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) + (outcome.models[["Ejaculate Quality and Production"]]$k-outcome.models[["Ejaculate Quality and Production"]]$p)/sum(diag(P)))
+
+#Extinction Rate
+restricted.dataER <- full_dataset %>% filter(full_dataset$Outcome == "Extinction Rate")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataER$var.g)
+X = model.matrix(outcome.models[["Extinction Rate"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+ExtinctionRateI2 <- 100 * sum(outcome.models[["Extinction Rate"]]$sigma2) / (sum(outcome.models[["Extinction Rate"]]$sigma2) + (outcome.models[["Extinction Rate"]]$k-outcome.models[["Extinction Rate"]]$p)/sum(diag(P)))
+
+#Offspring Viability
+restricted.dataOV <- full_dataset %>% filter(full_dataset$Outcome == "Offspring Viability")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataOV$var.g)
+X = model.matrix(outcome.models[["Offspring Viability"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+OffspringViabilityI2 <- 100 * sum(outcome.models[["Offspring Viability"]]$sigma2) / (sum(outcome.models[["Offspring Viability"]]$sigma2) + (outcome.models[["Offspring Viability"]]$k-outcome.models[["Offspring Viability"]]$p)/sum(diag(P)))
+
+#Reproductive Success
+restricted.dataRS <- full_dataset %>% filter(full_dataset$Outcome == "Reproductive Success")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataRS$var.g)
+X = model.matrix(outcome.models[["Reproductive Success"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+ReproductiveSuccessI2 <- 100 * sum(outcome.models[["Reproductive Success"]]$sigma2) / (sum(outcome.models[["Reproductive Success"]]$sigma2) + (outcome.models[["Reproductive Success"]]$k-outcome.models[["Reproductive Success"]]$p)/sum(diag(P)))
+
+simple.frame$I2 <- c(NA, BodySizeI2, DevelopmentRateI2, EarlyFecundityI2, ImmunityI2, MaleAttractivenessI2, MatingDurationI2, NA, MutantFrequencyI2, FitnessSenescenceI2, LifespanI2, MatingFrequencyI2, MatingLatencyI2, MatingSuccessI2, NA, EjaculateQualityI2, ExtinctionRateI2, OffspringViabilityI2, ReproductiveSuccessI2)
+
+outcome.frame <- format(simple.frame, digits = 2)
+outcome.frame <- add_rownames(outcome.frame, "Outcome")
+outcome.frame$b <- as.numeric(outcome.frame$b)
+outcome.frame$k <- as.numeric(outcome.frame$k)
+outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
+outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
+outcome.frame$I2 <- as.numeric(outcome.frame$I2)
+outcome.frame$Class <- c("Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Direct", "Direct", "Direct")
+
+outcome.frame %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)
+
 ```
@@
 
+##Meta-analysis using lnRR
+
+As per reviewers comments, we can use the log-response ratio instead of hedges g. Here we use the ``metafor`` function escalc.
+
+```{r}
+lnRR.data <- 
+escalc(measure = "ROM",
+       m1i = mean.high, 
+       m2i = mean.low,
+       sd1i = sd.high,
+       sd2i = sd.low,
+       n1i = n.high,
+       n2i = n.low,
+       vtype = "LS",
+       data = full_dataset, var.names=c("lnRR","lnRR_var"), digits=4) %>% 
+  filter(lnRR != "NA") %>% 
+  mutate(lnRR = round(lnRR, 3)*Positive.Fitness,
+         Sex = relevel(Sex, ref = "M"),
+         Environment = relevel(Environment, ref = "Unstressed"),
+         Taxon = relevel(Taxon, ref = "Beetle"),
+         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))
+
+SMD.data <- 
+  escalc(measure = "SMD",
+         m1i = mean.high, 
+         m2i = mean.low,
+         sd1i = sd.high,
+         sd2i = sd.low,
+         n1i = n.high,
+         n2i = n.low, 
+         vtype = "UB",
+         data = full_dataset, var.names=c("SMD","SMD_var"), digits=4) %>% 
+  filter(SMD != "NA") %>% 
+  mutate(SMD = round(SMD, 3)*Positive.Fitness,
+         Sex = relevel(Sex, ref = "M"),
+         Environment = relevel(Environment, ref = "Unstressed"),
+         Taxon = relevel(Taxon, ref = "Beetle"),
+         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))
+
+SMDH.data <- 
+  escalc(measure = "SMDH",
+         m1i = mean.high, 
+         m2i = mean.low,
+         sd1i = sd.high,
+         sd2i = sd.low,
+         n1i = n.high,
+         n2i = n.low, 
+         data = full_dataset, var.names=c("SMDH","SMDH_var"), digits=4) %>% 
+  filter(SMDH != "NA") %>% 
+  mutate(SMDH = round(SMDH, 3)*Positive.Fitness,
+         Sex = relevel(Sex, ref = "M"),
+         Environment = relevel(Environment, ref = "Unstressed"),
+         Taxon = relevel(Taxon, ref = "Beetle"),
+         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))
+
+lnRR.grandmean <- rma.mv(lnRR, lnRR_var,
+                       mods = ~ 1,
+                       random = list(~ 1 | Study.ID,
+                                      ~ 1 | Outcome,
+                                      ~ 1 | Taxon),
+                       method = "REML",
+                       data = lnRR.data)
+
+summary(lnRR.grandmean)
+
+SMD.grandmean <- rma.mv(SMD, SMD_var,
+                       mods = ~ 1,
+                       random = list(~ 1 | Study.ID,
+                                      ~ 1 | Outcome,
+                                      ~ 1 | Taxon),
+                       method = "REML",
+                       data = SMD.data)
+
+summary(SMD.grandmean)
+
+SMDH.grandmean <- rma.mv(SMDH, SMDH_var,
+                       mods = ~ 1,
+                       random = list(~ 1 | Study.ID,
+                                      ~ 1 | Outcome,
+                                      ~ 1 | Taxon),
+                       method = "REML",
+                       data = SMDH.data)
+
+summary(SMDH.grandmean)
+```
+
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/lnRR.brms.env.sex.rds")){
+  lnRR.brms.env.sex <- brm(lnRR | se(SE)  ~ 1 + Sex * Environment 
+                        + (1|Taxon) 
+                        + (1|Study.ID) 
+                        + (1|Outcome), 
+                        family = "gaussian", 
+                        seed = 1,
+                        cores = 4, chains = 4, iter = 4000, 
+                        control = list(adapt_delta = 0.9999, max_treedepth = 15),
+                        data = lnRR.data %>% mutate(SE = sqrt(lnRR_var)) %>% 
+                          filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
+  saveRDS(lnRR.brms.env.sex, file = "data/lnRR.brms.env.sex.rds")
+}
+lnRR.brms.env.sex <- readRDS(file = "data/lnRR.brms.env.sex.rds")
+
+# lternatively you can obtain posterior samples manually.
+lnRR.post <- (posterior_samples(lnRR.brms.env.sex, 
+                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
+                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
+                                    "b_SexF:EnvironmentStressed")) %>%
+           mutate(both_benign = b_Intercept + b_SexB,
+                  both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed`,
+                  male_benign = b_Intercept,
+                  male_stressful = b_Intercept + b_EnvironmentStressed,
+                  female_benign = b_Intercept + b_SexF,
+                  female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed`))[,-(1:6)]
+
+# Add columns for Environment and Sex
+lnRR.post <- as.data.frame(t(lnRR.post))
+lnRR.post$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
+lnRR.post$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")
+
+#Clean up dataframe
+lnRR.post <- melt(lnRR.post, id = c("Sex", "Environment"))
+lnRR.post$variable <- NULL
+
+lnRR.env.sex.model <- rma.mv(lnRR, V = lnRR_var, 
+                          mods = ~ 1 + Sex * Environment, 
+                          random = list(~ 1 | Study.ID, 
+                                       ~ 1 | Outcome,
+                                       ~ 1 | Taxon), 
+                          method = "REML", 
+                          data = lnRR.data %>% filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
+summary(lnRR.env.sex.model, digits = 2)
+
+#Generate predictions without taxon utilising the previously described function
+get.predictions.lnRR <- function(newdata){
+  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
+  if(newdata[1] == "B") B<-1 
+  if(newdata[1] == "F") F<-1 
+  if(newdata[2] == "Stressed") Stressed<-1
+  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
+  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1
+
+  predict(lnRR.env.sex.model, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
+}
+
+# Get the predictions for each combination of moderators
+predictions.lnRR <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
+                           Environment = c("Unstressed", "Stressed")))
+predictions.lnRR <- cbind(predictions.lnRR, do.call("rbind", apply(predictions.lnRR, 1, get.predictions.lnRR))) %>%
+  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
+for(i in 3:6) predictions.lnRR[,i] <- unlist(predictions.lnRR[,i])
+
+countpred <- count_(lnRR.data %>% filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"), c("Sex", "Environment"))
+
+predictions.lnRR <- left_join(predictions.lnRR, countpred, by = c("Sex", "Environment"))
+colnames(predictions.lnRR) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
+predictions.lnRR <- predictions.lnRR %>%
+      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female"),
+         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
+         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
+         Sex = factor(Sex, levels = c("Male", "Both", "Female")))
+
+predictions.lnRR <- format(predictions.lnRR, digits = 2)
+predictions.lnRR$Prediction = as.numeric(predictions.lnRR$Prediction)
+predictions.lnRR$CI.lb = as.numeric(predictions.lnRR$CI.lb)
+predictions.lnRR$CI.ub = as.numeric(predictions.lnRR$CI.ub)
+predictions.lnRR$n = as.numeric(predictions.lnRR$n)
+
+predictions.lnRR %>% pander()
+
+summary(lnRR.brms.env.sex)
+summary(lnRR.env.sex.model)
+```
+
+```{r}
+#Plot the posterior values from the Bayesian model as density ridges
+pd <- position_dodgev(height = 0.3)
+posterior.lnRR.plot <- lnRR.post %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
+  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
+  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
+  ylab("Environment")+
+  xlab("\nEffect Size (lnRR)")+
+  # scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  # scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-1, -.5, 0, 0.5, 1, 1.5))+
+
+  theme_bw()+
+
+  theme(panel.spacing = unit(0.1, "lines"),
+        text = element_text(size=16),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=16), 
+        legend.title=element_text(size=16, face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+        axis.title.y = element_text(size = 16, hjust = 0.35, margin = margin(r=-10)),
+        axis.text.y = element_text(angle = 0),
+        plot.title = element_text(size = 16))
+
+#Add the REML predictions as circles with error bars
+lnRR.plots <- posterior.lnRR.plot + 
+  geom_errorbarh(data = predictions.lnRR %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+                 aes(xmin = predictions.lnRR$CI.lb,
+                     xmax = predictions.lnRR$CI.ub, y = Environment,
+                     color = Sex), 
+                 height = 0, show.legend = F, position = pd)+
+
+  geom_point(data = predictions.lnRR %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
+             shape=21, color = "grey20", position = pd) +
+
+    guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
+    scale_size(guide = 'none')+
+
+  scale_y_discrete(expand=c(0.075, 0))
+
+lnRR.plots
+```
+
+```{r}
+env.sex.mean.only <- rma.mv(g, V = var.g, 
+                          mods = ~ 1 + Sex * Environment, 
+                          random = list(~ 1 | Study.ID, 
+                                       ~ 1 | Outcome,
+                                       ~ 1 | Taxon), 
+                          method = "REML", 
+                          data = strict_dataset %>% filter(mean.low != "NA"))
+summary(env.sex.mean.only, digits = 2)
+```
+
 ## Meta-Analysis on Variance
@@
 
-countpred <- count_(strict_dataset, c("Sex", "Environment"))
+countpred <- count_(strict_dataset %>% filter(lnCVr != "NA" ), c("Sex", "Environment"))
 
@@
 _________
+
+#lnVr
+
+```{r}
+lnVR.data <- 
+escalc(measure = "VR",
+       m1i = mean.high, 
+       m2i = mean.low,
+       sd1i = sd.high,
+       sd2i = sd.low,
+       n1i = n.high,
+       n2i = n.low,
+       vtype = "LS",
+       data = full_dataset, var.names=c("lnVR","lnVR_var"), digits=4) %>% 
+  filter(lnVR != "NA") %>% 
+  mutate(lnVR = round(lnVR, 3),
+         Sex = relevel(Sex, ref = "M"),
+         Environment = relevel(Environment, ref = "Unstressed"),
+         Taxon = relevel(Taxon, ref = "Beetle"),
+         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))
+
+lnCVR.data <- 
+escalc(measure = "CVR",
+       m1i = mean.high, 
+       m2i = mean.low,
+       sd1i = sd.high,
+       sd2i = sd.low,
+       n1i = n.high,
+       n2i = n.low,
+       vtype = "LS",
+       data = full_dataset, var.names=c("lnCVR","lnCVR_var"), digits=4) %>% 
+  filter(lnCVR != "NA") %>% 
+  mutate(lnCVR = round(lnCVR, 3),
+         Sex = relevel(Sex, ref = "M"),
+         Environment = relevel(Environment, ref = "Unstressed"),
+         Taxon = relevel(Taxon, ref = "Beetle"),
+         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))
+
+Variability.data <- left_join(lnVR.data, lnCVR.data)
+
+Variability.data %>% ggplot(aes(x = lnVR, y = lnCVR)) + geom_point()
+
+cor(Variability.data$lnVR, Variability.data$lnCVR, use = "complete.obs")
+```
+
+```{r}
+#MA on lnVR
+lnVR.model <- rma.mv(lnVR, V = lnVR_var, mods = ~ 1 + Sex*Environment, 
+                          random = list(~ 1 | Taxon,
+                                        ~ 1 | Study.ID,
+                                        ~ 1 | Outcome), 
+                         method = "REML", data = lnVR.data %>% filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
+summary(lnVR.model, digits = 2)
+
+#Generate predictions
+get.predictions.lnVR <- function(newdata){
+  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
+  if(newdata[1] == "B") B<-1 
+  if(newdata[1] == "F") F<-1 
+  if(newdata[2] == "Stressed") Stressed<-1
+  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
+  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1
+
+  predict(lnVR.model, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
+}
+# Get the predictions for each combination of moderators
+predictions.lnVR <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
+                           Environment = c("Unstressed", "Stressed")))
+predictions.lnVR <- cbind(predictions.lnVR, do.call("rbind", apply(predictions.lnVR, 1, get.predictions.lnVR))) %>%
+  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
+for(i in 3:6) predictions.lnVR[,i] <- unlist(predictions.lnVR[,i])
+
+countpred <- count_(lnVR.data, c("Sex", "Environment"))
+
+predictions.lnVR <- left_join(predictions.lnVR, countpred, by = c("Sex", "Environment"))
+
+#Change names to make them more clear
+predictions.lnVR <- predictions.lnVR %>% 
+      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female")) %>%
+  mutate(Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
+         Environment = replace(Environment, Environment == "Unstressed", "Benign"))
+
+colnames(predictions.lnVR) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
+
+predictions.lnVR %>% pander(digits = 2) 
+```
+
+```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+if(!file.exists("data/lnVR.brms.rds")){
+  lnVR.brms <- brm(lnVR| se(lnVR_var)  ~ 1 + Sex * Environment 
+                + (1|Taxon) 
+                + (1|Study.ID)
+                + (1|Outcome),
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, 
+                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                data =  lnVR.data %>% filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
+  saveRDS(lnVR.brms, "data/lnVR.brms.rds")
+}
+lnVR.brms <- readRDS(file = "data/lnVR.brms.rds") #Avoid re-running model above
+```
+
+**Table S13** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
+```{r}
+post.lnVR <- (posterior_samples(lnVR.brms, 
+                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
+                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
+                                    "b_SexF:EnvironmentStressed")) %>%
+         mutate(both_benign = b_Intercept + b_SexB,
+         both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed`,
+         male_benign = b_Intercept,
+         male_stressful = b_Intercept + b_EnvironmentStressed,
+         female_benign = b_Intercept + b_SexF,
+         female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed`))[,-(1:6)]
+
+#Add columns for Environment and Sex
+post.lnVR <- as.data.frame(t(post.lnVR))
+post.lnVR$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
+post.lnVR$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")
+
+#Clean up dataframe
+post.lnVR <- melt(post.lnVR, id = c("Sex", "Environment"))
+post.lnVR$variable <- NULL
+
+#And plot the results, first for the posterior results of the brms model then for the metafor predictions
+
+lnVR.plot.posterior <- post.lnVR %>% 
+  mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% 
+  ggplot() +
+  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
+  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
+  ylab("Environment\n")+
+  xlab("\nPhenotypic Variance (lnVR)")+
+  scale_x_continuous(limits = c(-1.6, 1.75), breaks = c(-2, -1.5, -1, -0.5, 0, 0.5, 1))+
+  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+
+  theme_bw()+
+
+  theme(panel.spacing = unit(0.1, "lines"),
+        text = element_text(size=16),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=16), 
+        legend.title=element_text(size=16, face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+        axis.title.y = element_text(size = 16, hjust = 0.35, margin = margin(r=-10)),
+        axis.text.y = element_text(angle = 0),
+        plot.title = element_text(size = 16))
+
+both.lnVR.plots <- lnVR.plot.posterior +
+  geom_errorbarh(data = predictions.lnVR %>% 
+                   mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+                 aes(xmin = predictions.lnVR$CI.lb, 
+                     xmax = predictions.lnVR$CI.ub, y = Environment,
+                     color = Sex), 
+                 height = 0, position = pd, show.legend = F) +
+  geom_point(data = predictions.lnVR %>% 
+               mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
+             shape=21, color = "grey20", position = pd) +
+  guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
+  scale_size(guide = 'none')+  
+  scale_y_discrete(expand=c(0.075,0))
+
+both.lnVR.plots
+```
 

### 2018-11-30 Response_to_Nature_Comms.Rmd
Furhter changes based on reviewers comments

@@
 Firstly, althought the effect size prediction for the trait has 95 % CIs not overlapping zero, the overall magnitude of the effect size is small (see Table exerpt), and the Bayes Factor (an estimate of the likelihood that the effect size is actually positive) is also small.
-The full table for all predicted effect sizes used in Figure 1 can be seen in **SXXX**.
+The full table for all predicted effect sizes used in Figure 1 can be seen in **S8**.
 Below we provide the exerpt of this table and forest plot for "Male attractiveness".
@@
 Arguably, this method provides more variable model estimates as models will always have lower power due to reduced sample sizes and the incorperation of measurement error in the predictions.
-We have added a table to the Supplementary Material where models are independently conducted on all fitness components where n > 3.
+We have added a table to the Supplementary Material where models are independently conducted on all fitness components where n > 3 (**Table S9**).
 

### 2018-11-30 Manuscripts/Manuscript_MetaAnalysis.Rmd
Furhter changes based on reviewers comments

@@
 library(dplyr)
+library(brms)
+
+source("../Tidy_functions_for_brms.R") #Tidy functions for making model tables for brms
 ```
@@
 
-Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus \hl{sexual conflict} [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014].
+Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus **sexual conflict** [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014].
 Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males [@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care: \textit{inter}locus sexual conflict [@RN314; @RN276; @RN315].
@@
 We retrieved 459 effect sizes from 65 studies.
-94 effect sizes were collected from populations evolving under stressful conditions, while 335 were measured for those evolving in benign conditions.
+92 effect sizes were collected from populations evolving under stressful conditions, while 337 were measured for those evolving in benign conditions.
 189 of the effect sizes came from measurements made on males, 219 on females, and the remaining 51 from measurements of a mixed-sex sample of individuals.
@@
 In total, we obtained effect sizes for 20 different fitness traits, with reproductive success ($n$ = 156) and offspring viability ($n$ = 56) being the most commonly-measured traits.
-We classified 216 effect sizes as direct measures of fitness, 147 as indirect, and the remaining 96 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
+We classified 216 effect sizes as direct measures of fitness, 141 as indirect, and the remaining 102 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
 Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, reproductive success, offspring viability, and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, and early fecundity).
@@
 
-The grand mean for all effect sizes (\hl{direct, indirect and ambiguous}) was positive (REML $\beta$ = 0.23, 95% CIs: 0.01 to 0.44, $p$ = 0.038; Bayesian $\beta$ = 0.23, 95% CIs: -0.06 to 0.51, $BF_{>0}$ = 18), indicating that sexual selection typically had a net positive effect on the majority of populations and fitness components so far studied.
+The grand mean for all effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.25, 95% CIs: 0.06 to 0.43, $p$ = 0.008; Bayesian $\beta$ = 0.25, 95% CIs: -0.02 to 0.52, $BF_{>0}$ = 32), indicating that sexual selection typically had a net positive effect on the majority of populations and fitness components so far studied.
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
-Sexual selection had a beneficial effect on most fitness traits, including all of the fitness traits that we classified as being ‘direct’ measurements of population fitness: extinction rate (REML $\beta$ = 0.37, 95% CIs: 0.01 to 0.73; Bayesian $\beta$ = 0.37, 95% CIs: -0.02 to 0.79, $BF_{>0}$ = 30.13; $n$ = 4), offspring viability (REML $\beta$ = 0.20, 95% CIs: 0.042 to 0.36; Bayesian $\beta$ = 0.21, 95% CIs: -0.04 to 0.47, $BF_{>0}$ = 24.89; $n$ = 56) and reproductive success (REML $\beta$ = 0.17, 95% CIs: 0.013 to 0.32; Bayesian $\beta$ = 0.18, 95% CIs: -0.06 to 0.44, $BF_{>0}$ = 15.53; $n$ = 156; \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6}).
-Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.49, 95% CIs: -0.72 to -0.26; Bayesian $\beta$ = -0.49, 95% CIs: -0.78 to -0.19, $BF_{>0}$ = 0.0054; $n$ = 35) and body condition (REML $\beta$ = -1.3, 95% CIs: -1.9 to -0.67; Bayesian $\beta$ = -1.3, 95% CIs: -1.9 to -0.63, $BF_{>0}$ = 0.00025, $n$ = 1).
-\autoref{forest_plot} presents Bayesian estimates for each fitness component and \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6} contains both Bayesian and REML estimates, with sample sizes and test statistics.
+Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6}).
+**Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.23, 95% CIs: 0.12 to 0.35; Bayesian $\beta$ = 0.23, 95% CIs: 0.03 to 0.41, $BF_{>0}$ = 55, $n$ = 102) and an indirect relationship to fitness (REML $\beta$ = 0.25, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.04 to 0.42, $BF_{>0}$ = 68, $n$ = 141).
+Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.02 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.07 to 0.3, $BF_{>0}$ = 14, $n$ = 216).
+An extensive forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed in model prediction and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
+Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.16, $BF_{>0}$ = 0.0021; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.8 to -0.61, $BF_{>0}$ = 0.00013, $n$ = 1).
 \phantomsection
@@
 
-We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect fitness (\hyperlink{page.13}{Table 1, 2}).
-Sexual selection significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
-Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
-Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
+We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect fitness (\hyperlink{page.18}{Table 1, 2}).
+Sexual selection significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
+Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
+Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, **with a small but significant difference** between benign versus stressful conditions (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
+**When the lnRR (log Response Ratio) effect size was used to conduct the meta-analysis, the results corroborate those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S4 and Table S16).**
 
-Other moderator variables that we examined had minimal impacts on effect size (\href{https://justincally.github.io/SexualSelection/#meta-analyses_including_many_moderator_variables}{Figure S2, Table S7}).
+Other moderator variables that we examined had minimal impacts on effect size (\href{https://justincally.github.io/SexualSelection/#meta-analyses_including_many_moderator_variables}{Figure S2, Table S10}).
 Specifically, effect size did not depend on whether or not the study was conducted blind (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S9}), nor on the number of generations for which the experimental evolution study was run (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S10, S11}).
@@
 
-![Forest plot showing the effect of manipulation of sexual selection, for 20 fitness components from 65 studies.
-Effect sizes ($n$ = 459) varied between fitness components, and were more often positive than negative.
-Predicted average values are presented alongside each fitness component; those in bold have 95% confidence intervals that do not cross zero.
-The estimates presented here are Bayesian predictions, which were slightly more conservative than the REML predictions (Table S6).\label{forest_plot}](Figures/ForestPlot_edit3.pdf)
+<!-- Appears to be a problem having two captions -->
 
-![(**a**) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
-(**b**) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals.
-The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Table S12 and S14).
-Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.\label{env_sex}](Figures/environment_variance_edit5.pdf)
-
-![Tests of publication bias are mixed and suggest publication bias may be present.
-(**a**) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies.
-(**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias.
-For (**b**) and (**c**) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).\label{publication_bias}](Figures/publicationbias.pdf)
-
-<!-- Appears to be a problem having two captions -->
 \newpage
-\nolinenumbers
-
-**Table 1:** Results for the multilevel meta-analysis model testing the effects of sexual selection in different environments and between sexes.
-Moderator variables whose 95% confidence intervals do not cross zero are shown in bold.
-
-```{r, echo = F}
-options(knitr.kable.NA = ' ')
-
-table1 <- read.csv('table1.csv') %>% 
-  mutate(
-    Estimate = cell_spec(Estimate, "latex", bold = ifelse(LCI*UCI > 0, T, F)),
-    Parameters = cell_spec(Parameters, "latex", bold = ifelse(LCI*UCI > 0, T, F))
-  )
-
-kable(table1, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
-  kable_styling(latex_options = c("scale_down", "striped"), full_width = F) %>%
-  row_spec(0, bold = TRUE) %>%
-  group_rows("REML Model", 1, 6) %>%
-  group_rows("Bayesian Model", 7, 12)
-```
-
-\vspace{0.75 cm}
-
-**Table 2:** Hypothesis tests using restricted maximum likelihood (REML) or Bayesian methods, illustrating how sex and environmental stress interact to modulate effect size.
-Tests whose 95% confidence intervals do not cross zero are shown in bold.
-
-```{r, echo = F}
-options(knitr.kable.NA = ' ')
-
-table2 <- read.csv('table2.csv') %>% rename('Statistical Approach' = Statistical.Approach) %>%
-  mutate(
-    Estimate = cell_spec(Estimate, "latex", bold = ifelse(LCI*UCI > 0, T, F)),
-    `Statistical Approach` = cell_spec(`Statistical Approach`, "latex", bold = ifelse(LCI*UCI > 0, T, F))
-  )
-
-kable(table2, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
-  kable_styling(latex_options = c("scale_down"), full_width = F) %>%
-  row_spec(0, bold = TRUE) %>%
-  collapse_rows(columns = 1:2, latex_hline = "major")
-```
 
@@
 
-![Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.\label{prisma_flow}](Figures/PRISMA\ Chart.pdf)
-
 \phantomsection
@@
 <div id="refs"></div>
+
+\newpage
+\phantomsection
+\nolinenumbers
+
+#Tables and Figures
+
+**Table 1:** Results for the multilevel meta-analysis model testing the effects of sexual selection in different environments and between sexes.
+Moderator variables whose 95% confidence intervals do not cross zero are shown in bold.
+
+```{r, echo = F}
+model.complete2 <- readRDS('../data/model.complete2.rds')
+brms.complete2 <- readRDS('../data/brms.complete2.rds')
+
+table1 <- data.frame(round(as.numeric(model.complete2[["beta"]]), digits = 2))  %>% rename(Estimate = 1)
+table1$SE <- as.numeric(model.complete2[["se"]])
+table1$LCI <- as.numeric(model.complete2[["ci.lb"]])
+table1$UCI <- as.numeric(model.complete2[["ci.ub"]])
+table1$z <- as.numeric(model.complete2[["zval"]])
+table1$p <- as.numeric(model.complete2[["pval"]])
+
+brms.model.table <- make_text_summary(brms.complete2) %>% add_significance_stars()
+brms.model.table$z <- NA
+brms.model.table$p <- NA
+brms.model.table <- brms.model.table[1:6,]
+
+table1 <- rbind(table1, brms.model.table %>% select(Estimate, SE = Est.Error, LCI = Q2.5, UCI = Q97.5, z, p)) %>% tibble::rownames_to_column("Parameters")
+table1$Parameters <- c("Intercept", "Both Sexes", "Female Sex", "Stressed Environment", "Both Sexes x Stressed Environment", "Female Sex x Stressed Environment", "Intercept", "Both Sexes", "Female Sex", "Stressed Environment", "Both Sexes x Stressed Environment", "Female Sex x Stressed Environment")
+
+options(knitr.kable.NA = ' ')
+
+table1 <- table1 %>% 
+  mutate(
+    Estimate = cell_spec(Estimate, "latex", bold = ifelse(LCI*UCI > 0, T, F)),
+    Parameters = cell_spec(Parameters, "latex", bold = ifelse(LCI*UCI > 0, T, F))
+  )
+
+kable(table1, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
+  kable_styling(latex_options = c("scale_down", "striped"), full_width = F) %>%
+  row_spec(0, bold = TRUE) %>%
+  group_rows("REML Model", 1, 6) %>%
+  group_rows("Bayesian Model", 7, 12)
+```
+
+\vspace{0.75 cm}
+
+**Table 2:** Hypothesis tests using restricted maximum likelihood (REML) or Bayesian methods, illustrating how sex and environmental stress interact to modulate effect size.
+Tests whose 95% confidence intervals do not cross zero are shown in bold.
+
+```{r, echo = F}
+options(knitr.kable.NA = ' ')
+
+table2 <- read.csv('table2.csv') %>% rename('Statistical Approach' = Statistical.Approach) %>%
+  mutate(
+    Estimate = cell_spec(Estimate, "latex", bold = ifelse(LCI*UCI > 0, T, F)),
+    `Statistical Approach` = cell_spec(`Statistical Approach`, "latex", bold = ifelse(LCI*UCI > 0, T, F))
+  )
+
+kable(table2, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
+  kable_styling(latex_options = c("scale_down"), full_width = F) %>%
+  row_spec(0, bold = TRUE) %>%
+  collapse_rows(columns = 1:2, latex_hline = "major")
+```
+
+\newpage
+
+![The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness.
+Overall, effect sizes were more often positive than negative.
+Predicted average values are presented as a diamond for each fitness-relationship category.
+The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line.
+Predictions from both Bayesian and REML models can be found in Table S7).\label{forest_plot}](Figures/forest.plot.class.pdf)
+
+![(**a**) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
+(**b**) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals.
+The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Table S12 and S14).
+Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.\label{env_sex}](Figures/environment_variance_edit5.pdf)
+
+![Tests of publication bias are mixed and suggest publication bias may be present.
+(**a**) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies.
+(**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias.
+For (**b**) and (**c**) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).\label{publication_bias}](Figures/publicationbias.pdf)
+
+![Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.\label{prisma_flow}](Figures/PRISMA\ Chart.pdf)

### 2018-11-30 meta_analysis_sexual_selection_pop_fitness.Rmd
Furhter changes based on reviewers comments

@@
 ```{r, warning=FALSE, message=FALSE, results='hide'}
+library(knitr)
 library(pander)
@@
 
-```{r echo=FALSE, results='hide', warning=FALSE}
-knitr::opts_knit$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
-```
-`r opts_chunk$set(cache=TRUE)`
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
+```
 
@@
 colnames(Outcome_and_sex) <- cbind("Both", "Female", "Male")
-Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)
+Outcome_and_sex %>% tibble::rownames_to_column("Parameters") %>% mutate(Total = Both+Female+Male) %>% pander(split.cell = 40, split.table = Inf)
 ```
@@
 
+**Table S6**
 These estimates are presented in the text of the Results section. The test statistic is either the p-value (REML) or Bayes factor (BF) comparing the effect size to zero (Bayesian).
-```{r}
+```{r, warning = F}
 pander(data.frame(
@@
 ### Effect of sexual selection on direct, indirect and ambiguous measures of fitness
+
+**Table S7**
 
@@
   ylab("Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]") +
-  theme_minimal(12) +
-  theme(panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(), legend.position = "none") +
+  theme_minimal(14) +
+  theme(panel.grid.major.y = element_blank(), 
+        panel.grid.minor.y = element_blank(), 
+        legend.position = "none",
+        axis.text.y = element_text(size = 13, hjust = 1)) +
   scale_color_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
@@
                      name = "Relationship\nto fitness")+
-  xlab("Relationship to Fitness")+
+  xlab("Relationship to Fitness\n")+
   coord_flip()
-
-forest.plot.class
 ```
@@
 
-  scale_x_continuous(limits=c(-3.35, 4.25), 
+  scale_x_continuous(limits=c(-3.35, 10), 
                      breaks = c(-3, -2, -1, 0, 1, 2, 3), 
@@
         axis.title.x = element_text(hjust = 0.5, size = 14))
-
-p.meta
-```
+```
+
+<img src="figures/ForestPlot_size_reduced.pdf" alt=" "  width="1650" height="2100">
 <br></br>
@@
 
-**Table S6** Summary of model predictions for 20 fitness components.
-In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot) using the Bayesian values.
+**Table S8** Summary of model predictions for 20 fitness components.
+In Figure S1 these values are presented as a text overlay on Figure 1 (Forest Plot) using the Bayesian values.
 Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0.
@@
 
-Individual Meta-analyses for each fitness related trait with n>3:
+**Table S9** In some instances it may be beneficial to the reader to obtain average effect sizes of each fitness trait **entirely independent** of other traits.
+For this reason we present a summary of independent model estimates for 16 fitness components with a sample size greater than 3 effect sizes (n>3).
+Unlike above where estimates were generated based on predictions from a single model, here we run individual meta-analyses for each fitness related trait.
+Independent models generally reduce the power and significance of some of the estimates with 'Extinction rate' and 'Ejaculate quality and production' the only two traits with p-values < 0.05.
 
@@
 
+**Table S10:** Bayesian model results for a preliminary model that explores many covariates collected in the dataset.
+
 ```{r}
@@
 
-prelim.results.bayesplot
-
 make_text_summary(brms.preliminary) %>% 
@@
 ```
-**Figure S2 & Table S7:** Bayesian model results for a preliminary model that explores many covariates collected in the dataset.
 
@@
 <br></br>
-**Figure S3:** The predictions from this model indicate some heterogeneity between taxon.
+**Figure S2:** The predictions from this model indicate some heterogeneity between taxon.
 However, the most apparent difference between taxa is that confidence bands increase for taxa with low sample size.
@@
 
-**Table S8** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.
+**Table S11** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.
 
@@
 
-Given that none of the levels of `Taxon` have a particularly strong impact on effect size, and many categories are incompletely sampled with regards to Sex and Environment (Table S8), we elected to treat `Taxon` as a random/group level effect in all subsequent models.
+Given that none of the levels of `Taxon` have a particularly strong impact on effect size, and many categories are incompletely sampled with regards to Sex and Environment (Table S11), we elected to treat `Taxon` as a random/group level effect in all subsequent models.
 
@@
                           data = strict_dataset)
+saveRDS(model.complete2, 'data/model.complete2.rds')
 summary(model.complete2, digits = 2)
@@
 
-**Table S9** Using the ``anova.rma`` function we can conduct hypothesis tests between two categorical groups in the model.
+**Table S12** Using the ``anova.rma`` function we can conduct hypothesis tests between two categorical groups in the model.
 Here we conduct 5 tests comparing the relative effect of sexual selection between the sexes, and in different environments.
@@
 
-**Table S10** Model estimate summary table for the Bayesian model investigating the effect of environment and sex (alongside sexual selection) on fitness. 
+**Table S13** Model estimate summary table for the Bayesian model investigating the effect of environment and sex (alongside sexual selection) on fitness. 
 ```{r}
@@
 
-**Table S11** Hypothesis tests for the Bayesian model are similar to the REML model (Table S9), with slight differences to CIs.
+**Table S14** Hypothesis tests for the Bayesian model are similar to the REML model (Table S9), with slight differences to CIs.
 ```{r}
@@
 
-**Table S12** The REML predictions in the plot above use the following dataframe
+**Table S15** The REML predictions in the plot above use the following dataframe
 ```{r}
@@
 
-As per reviewers comments, we can use the log-response ratio instead of hedges g. Here we use the ``metafor`` function escalc.
-
-```{r}
+As per reviewers comments, we can use the log-response ratio (lnRR) instead of Hedges' g as the effect size (response variable in meta-analysis models).
+To calculate lnRR we use the ``metafor`` function ``escalc``.
+
+```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE, error = FALSE}
 lnRR.data <- 
@@
 
-summary(lnRR.grandmean)
-
 SMD.grandmean <- rma.mv(SMD, SMD_var,
@@
 
-summary(SMD.grandmean)
-
 SMDH.grandmean <- rma.mv(SMDH, SMDH_var,
@@
 
-summary(SMDH.grandmean)
-```
-
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
 if(!file.exists("data/lnRR.brms.env.sex.rds")){
@@
                           data = lnRR.data %>% filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
-summary(lnRR.env.sex.model, digits = 2)
 
@@
 
-predictions.lnRR %>% pander()
-
-summary(lnRR.brms.env.sex)
-summary(lnRR.env.sex.model)
-```
-
-```{r}
 #Plot the posterior values from the Bayesian model as density ridges
@@
 
-```{r}
-env.sex.mean.only <- rma.mv(g, V = var.g, 
-                          mods = ~ 1 + Sex * Environment, 
-                          random = list(~ 1 | Study.ID, 
-                                       ~ 1 | Outcome,
-                                       ~ 1 | Taxon), 
-                          method = "REML", 
-                          data = strict_dataset %>% filter(mean.low != "NA"))
-summary(env.sex.mean.only, digits = 2)
+**Figure S4:** Using an alternative effect size (lnRR) sexual selection also increases population fitness.
+Circle size is proportional to sample size (shown below).
+The REML predictions are shown as circles with error bars and the Bayesian predictions as density ridges.
+Note that the magnitude of the effect sizes presented here should not be directly compared with those using Hedges' g as lnRR is a log-transformed value.
+
+**Table S16** The REML predictions for the meta-analysis using lnRR (plotted above) are formulated from the following model and predictions.
+
+```{r}
+summary(lnRR.env.sex.model)
+predictions.lnRR %>% pander()
 ```
@@
 
-**Table S13** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
+**Table S17** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
 ```{r}
@@
 
-**Table S14** The REML predictions in the plot above use the following dataframe.
+**Table S18** The REML predictions in the plot above use the following dataframe.
 ```{r}
@@
 
-**Table S15** Bayesian hypothesis tests between categorical groups for phenotypic variation (lnCVR)
+**Table S19** Bayesian hypothesis tests between categorical groups for phenotypic variation (lnCVR)
 ```{r}
@@
 
-**Table S16** REML hypothesis tests between categorical groups for phenotypic variation (lnCVR)
+**Table S20** REML hypothesis tests between categorical groups for phenotypic variation (lnCVR)
 ```{r}
@@
 
-#lnVr
-
-```{r}
+###lnVr Effect Size of Variance
+
+In this meta-analysis we used the the log-coefficient of variaince ratio (lnCVR) as the response variable when investigating the impact of sexual selection on the variation in the distribution of traits associated with fitness.
+The lnCVR was used over the log-variance ration (lnVR) because lnVR does not account for the mean-variance relationship  [@Nakagawa_2015; @Senior_2016] seen in this meta-analysis (see below).
+However, for completeness we present a similar style meta-analysis for lnVR to investigate the effects of environment
+
+```{r, warning = F, message=F}
+full_dataset %>% ggplot(aes(x = mean.high, y = sd.high))+
+  geom_point()+
+  scale_x_log10()+
+  scale_y_log10()+
+  xlab("Mean of Treatment Group")+
+  ylab("Standard Deviation of Treatment Group") +
+  geom_smooth(method = "lm", colour = "red")
+```
+
+**Figure S5** The use of lnCVR (as opposed to lnVR) is justified in this meta-analysis due to the strong mean-variance relationship.
+In this case the standard deviation from the treatment group is compared to the means of the treatment group on a log-scale.
+
+```{r, warning = FALSE}
 lnVR.data <- 
@@
 
-Variability.data <- left_join(lnVR.data, lnCVR.data)
-
-Variability.data %>% ggplot(aes(x = lnVR, y = lnCVR)) + geom_point()
-
-cor(Variability.data$lnVR, Variability.data$lnCVR, use = "complete.obs")
-```
-
-```{r}
 #MA on lnVR
@@
                          method = "REML", data = lnVR.data %>% filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
-summary(lnVR.model, digits = 2)
 
@@
 
-predictions.lnVR %>% pander(digits = 2) 
-```
-
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
 if(!file.exists("data/lnVR.brms.rds")){
-  lnVR.brms <- brm(lnVR| se(lnVR_var)  ~ 1 + Sex * Environment 
+  lnVR.brms <- brm(lnVR| se(SE.lnVR)  ~ 1 + Sex * Environment 
                 + (1|Taxon) 
@@
                 control = list(adapt_delta = 0.999, max_treedepth = 15),
-                data =  lnVR.data %>% filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
+                data =  lnVR.data %>% mutate(SE.lnVR = sqrt(lnVR_var)) %>% filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated"))
   saveRDS(lnVR.brms, "data/lnVR.brms.rds")
@@
 
-**Table S13** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
-```{r}
+```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE, error = FALSE}
 post.lnVR <- (posterior_samples(lnVR.brms, 
@@
 
+**Figure S6:** The effects of sexual selection on the log-variance ratio (lnVR).
+Without accounting for the mean variance relationship (lnCVR) sexual selection has different effects on the variance measure.
+
+**Table S21** The points in the above plot are based on the following REML model and predictions.
+While the predicted effects of sexual selection on lnVR in stressful conditions is non-significantly negative, there is still a negative significant interaction between stressful environments and the female sex.
+```{r}
+summary(lnVR.model, digits = 2)
+predictions.lnVR %>% pander(digits = 2) 
+```
+
+_______________________
+
 ## Publication Bias
@@
                        random = list(~ 1 | Study.ID,
-                                       ~ 1 | Outcome),
+                                      ~ 1 | Outcome,
+                                      ~ 1 | Taxon),
                        method = "REML",
@@
 <br></br>
-**Figure S5:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001).
+**Figure S7:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001).
 The asymmetry appears to come from a spread of positive effect sizes outside the funnel and of varying degrees of precision.
@@
 ```{r, fig.height= 4, fig.width=8, warning=FALSE}
-JIF.plot <- ggplot(data = full_dataset, aes(x=JIF, y=g))+
-  geom_jitter(color='darkgreen', alpha = 0.4, aes(size = 1 / var.g), show.legend = FALSE)+
+JIF.plot <- ggplot(data = full_dataset, aes(x=JIF, y=g, size = 1 / var.g))+
+  geom_point(fill='darkgreen', shape = 21, colour = 'grey20', alpha = 0.75)+
   geom_hline(yintercept=0, linetype = 'dotted')+
-  geom_smooth(method='lm', color='black', linetype="solid")+
+  geom_smooth(method='lm', color='darkgreen', linetype="solid")+
   scale_x_log10(limits = c(-5, 40), breaks = c(0, 1, 2, 5, 10, 20, 40))+
-  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Journal Impact Factor (logarithmic scale)')+ 
+  labs(size = 'Weight (%)', y="Effect size (Hedges' g)", x= 'Journal Impact Factor (log-scale)')+ 
+  guides(size = F)+
   theme_bw()+
@@
 <br></br>
-**Figure S6:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
+**Figure S8:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
 
@@
 time.plot <- full_dataset %>% 
-  ggplot(aes(x=Year, y=g))+
-  geom_jitter(color='darkorange', alpha=.5, aes(size = (1/(var.g))/sum((1/(var.g)))*100), show.legend = FALSE)+
+  ggplot(aes(x=Year, y=g, size = 1/(var.g)))+
+  geom_jitter(fill='darkorange', alpha=.75, shape = 21, colour ='grey20')+
   geom_hline(yintercept=0, linetype = 'dotted')+
-  geom_smooth(method='lm', color='black')+
-  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Year')+
+  guides(size = F)+
+  geom_smooth(method='lm', color='darkorange')+
+  labs(y="Effect size (Hedges' g)", x= 'Year')+
     theme_bw()+
@@
 <br></br>
-**Figure S7:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
+**Figure S9:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
 Point size is proportional to the precision of the effect size.
@@
 <br></br>
-**Figure S9:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
+**Figure S10:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
 However, this should not be viewed as evidence against the validity of blinding as a research method.
@@
 <br></br>
-**Figure S10:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
+**Figure S11:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
 
@@
 <br></br>
-**Figure S11:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
+**Figure S12:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
 

### 2018-12-05 Response_to_Nature_Comms.Rmd
More changes to reviewers comments

@@
 
-#load(".RData")
+load(".RData")
 ```
@@
 Please let us know if we can do anything further to assist you.
+
+In addition to the changes suggested by reviewers, the peer-review process highlighted some human errors on our behalf in the dataset with respect to effect size calculation, these were issues to a select few effect sizes.
+As such, we have thoroughly rechecked our dataset and re-ran the analyses.
+Ultimately the corrections to the dataset have altered our conclusions.
 
@@
 Importantly, to account for the variable and uncertain relationships certain traits have with fitness (as raised by the reviewer).
-We provide an expacded table on how each trait is measured and why they are classed as ambiguous, indirect and direct in their relationship with fitness.
-Given that this information was in the Supplementary Material we have revised the manuscript to clarify the distinctions more thoroughly.
+We provide a table on how each trait is measured and their relationship with fitness.
+Given that this information was in the Supplementary Material we have **revised the manuscript to clarify the distinctions more thoroughly**.
 
@@
 All subsequent models, statistics and figures now take into account this re-classification.
-However, given the small sample size for male attractiveness effect sizes (n = 6), **we find only marginal changes in the results and no key changes in the key findings of the study*.**
+However, given the small sample size for male attractiveness effect sizes (n = 6), we find only marginal changes in the results and no key changes in the key findings of the study.
 
@@
 Firstly, althought the effect size prediction for the trait has 95 % CIs not overlapping zero, the overall magnitude of the effect size is small (see Table exerpt), and the Bayes Factor (an estimate of the likelihood that the effect size is actually positive) is also small.
-The full table for all predicted effect sizes used in Figure 1 can be seen in **S8**.
+The full table for all predicted effect sizes used in Figure S1 can be seen in **S8**.
 Below we provide the exerpt of this table and forest plot for "Male attractiveness".
@@
 In regards to our analysis, this means that the predictions that appear in Figure 1 are sourced from using ``fitted.brmsfit`` as opposed to ``predict.brmsfit``.
-Given the reviewers comments we have clarified how we obtained model predictions used in our results.
 Additionally, some meta-analyses investigating the effect of a variable on more than one outcome model each outcome (in this case the *fitness component*) seperately.
@@
 We have added a table to the Supplementary Material where models are independently conducted on all fitness components where n > 3 (**Table S9**).
+
+Given, the confusion with regards to Figure 1 as it originally appeared within the manuscript we have altered the figure to a generalized forest plot by grouping the effect sizes from each of the fitness classes (ambiguous, indirect and direct).
+The previous Figure 1 has now been moved to the Supplementry Material with corresponding tables.
 
@@
 
-```{r, fig.width = 9, fig.height = 3}
+```{r, fig.height=3}
 pd <- position_dodgev(0.6)
@@
                     name = "Relationship\nto fitness")+
-  geom_errorbar(aes(ymin = lowerci, 
+  geom_linerange(aes(ymin = lowerci, 
                    ymax = upperci,
+                   x = reorder(AuthorYear, -g),
                      color = Outcome.Class,
-                     group = g),
-                width = 0, show.legend = FALSE) +
+                     group = "identity"),
+               show.legend = FALSE,
+               position = position_dodge2(width = 0.2, preserve = "single")) +
 
@@
              color = "grey20",
-             position = position_dodge2(width = 0.2)) +
+             position = position_dodge2(width = 0.2),
+             show.legend = F) +
 
@@
                      breaks = c(-3, -2, -1, 0, 1, 2, 3), 
-                     name='                              Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
+                     name='Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
 
@@
   facet_grid(Outcome_f~.,
-             labeller = label_wrap_gen(width=20),
+             labeller = label_wrap_gen(width=10),
              scales= 'free', 
@@
 
-  theme(strip.text.y = element_text(angle = 0, size = 8, margin = margin(t=15, r=15, b=15, l=15)), 
+  theme(strip.text.y = element_text(angle = 0, size = 12, margin = margin(t=15, r=15, b=15, l=15)), 
         strip.background = element_rect(colour = NULL,
@@
                                         fill = "gray90"),
-        text = element_text(size=11),
+        text = element_text(size=13),
         panel.spacing = unit(0.5, "lines"),
@@
                                   face = "bold"),
-        axis.title.x = element_text(hjust = 0, size = 12))
+        axis.title.x = element_text(hjust = 0.5, size = 12))
 
@@
 
-**Summarise results for direct, indirect and ambiguous**
+The reviewer provides an accurate shortcoming of discussion on the observed heterogeneity between fitness components.
+The sixth paragraph of our discussion is raises some potential reasons why heterogeneity may be high within our meta-analysis.
+Additionally, it may please the reviewer to find an addition to our Supplementary Material (Table S9), now conducts independent meta-analyses and obtains $I^2$ for each of these traits.
+Even when metanalyses are conducted on a single trait, heterogeneity ($I^2$) is still high > 90 %.
 
-The reviewer provides an accurate shortcoming of discussion on the observed heterogeneity between fitness components. We have extended certain parts of the discussion related to this aspect...
-
-In regards to conducting a meta-analysis on just direct fitnesss components, the reviewer provids a valid question of our use of direct **and** indirect fitness components for the meta-analysis investigating the effects of sex and stress.
-To some degree the use of direct **and** indirect is arbitrary.
-But based on the question we asked we were interested in the effect of sexual selection on many components of fitness.
+In regards to conducting a meta-analysis on just direct fitnesss components, the reviewer provides a valid question of our use of direct **and** indirect fitness components for the meta-analysis investigating the effects of sex and stress.
+Based on the question we asked we were interested in the effect of sexual selection on many components of fitness.
 
@@
 We find the same key associations; that sexual selection generally elevates fitness, especially for females, with the effect magnified in stressful environments.
-Below we present the findings, which we have incorperated into our supplementary material and referenced within the manuscript and Figure 2 caption.
+Below we present the findings.
+**should we put this in the supp?**
 
@@
 
-```{r, warning=FALSE}
+```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 10}
 model.direct.only <- rma.mv(g, V = var.g, 
@@
 
-predictions.direct %>% pander(caption = "Model using only direct measures of fitness")
-```
-
-```{r, fig.height=4.5, fig.width=6.25, warning=FALSE, message=FALSE, error = FALSE, fig.align='center'}
 if(!file.exists("data/brms.direct.rds")){
@@
 # lternatively you can obtain posterior samples manually.
-post <- (posterior_samples(brms.direct, 
+post.direct <- (posterior_samples(brms.direct, 
                            pars = c("b_Intercept", "b_SexB", "b_SexF", 
@@
 # Add columns for Environment and Sex
-post <- as.data.frame(t(post))
-post$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
-post$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")
+post.direct <- as.data.frame(t(post.direct))
+post.direct$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
+post.direct$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")
 
 #Clean up dataframe
-post <- melt(post, id = c("Sex", "Environment"))
-post$variable <- NULL
+post.direct <- melt(post.direct, id = c("Sex", "Environment"))
+post.direct$variable <- NULL
 
@@
 pd <- position_dodgev(height = 0.3)
-posterior.plot <- post %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
+posterior.direct.plot <- post.direct %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
   stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
@@
 #Add the REML predictions as circles with error bars
-both.plots <- posterior.plot + 
+both.direct.plots <- posterior.direct.plot + 
   geom_errorbarh(data = predictions.direct %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
@@
 
-both.plots
+grid.arrange(both.plots + 
+               guides(fill = FALSE)+
+               ggtitle("Indirect And Direct\n")+ theme(plot.title = element_text(size = 18, face = "bold", colour = "Red")),
+             both.direct.plots + ggtitle("Direct Only\n")+
+               theme(axis.title.y = element_blank(), 
+                     plot.title = element_text(size = 18, face = "bold", colour = "Red")), 
+             nrow = 1, 
+             widths = c(3,4))
 ```
@@
 ```{r, warning=FALSE}
-direct.only.data <- strict_dataset %>% filter(Outcome.Class == "Direct")
-I2(model.direct.only, direct.only.data$var.g) %>% pander(digits = 3)
+predictions.direct %>% pander(caption = "Model using only direct measures of fitness")
 ```
@@
 But if correct, this explanation is not exactly the effect of sexual selection, but rather enhanced selection of females due to enhanced (male induced) stress, so the interpretation of results should change.*
+
+Not too sure what he means.
 
@@
 The reviewer is correct in that the 95 % CI overlap zero for the three direct fitness components (extinction rate, offspring viability and reproductive success) have 95 % CI overlapping zero.
-Additionally, our analysis reveals that the predicted effect size for direct fitness components has 95 % CIs that overlap zero for Bayesian, but not REML models (REML $\beta$ = 0.15, 95% CIs: 0.033 to 0.27; Bayesian $\beta$ = 0.15, 95% CIs: -0.058 to 0.34, $BF_{>0}$ = 4.9).
+Additionally, our analysis reveals that the predicted effect size for direct fitness components has 95 % CIs that overlap zero for Bayesian, but not REML models (REML $\beta$ = 0.13, 95% CIs: 0.022 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.068 to 0.30, $BF_{>0}$ = 4.9).
 In this respect we have tapered and clarified our statement that we find some evidence that sexual selection increases mean values of traits directly related to fitness.
@@
 
-**In the discussion the authors say they included the number of experimental evolution generations, but I could not find this information in methods.**
+>*In the discussion the authors say they included the number of experimental evolution generations, but I could not find this information in methods.*
 
 It is correct that we did not use the number of generations in our main analysis.
-Line 281 of the manuscript (Methods section) states that the number of generations.
-In the supplementary material we investigate the role of number of generations (the lineage is evolved for) has on fitness in the section *Meta-analyses including many moderator variables* as well as in Figure S10 and S11.
+The manuscript (Methods section) states that the number of generations.
+In the supplementary material we investigate the role of number of generations (the lineage is evolved for) has on fitness in the section *Meta-analyses including many moderator variables* as well as in Figure S12 and S13.
 Generations (specifically, log-Generations) had minimal effect on the effect sizes and was removed for the models that appeared in the main text.
 
-**Fig. S1 is not referred to in the main texts, is it different from Fig. 2, except that the latter contains predicted average values for fitness components?**
+>*Fig. S1 is not referred to in the main texts, is it different from Fig. 2, except that the latter contains predicted average values for fitness components?*
 
-No difference... kind of there for documentation on how we created it (transparency). What do you think we should do about this Luke?
+**No difference... kind of there for documentation on how we created it (transparency). What do you think we should do about this Luke?**
 
@@
 
-**This meta-analysis investigated the consequences of sexual selection experiments on trait mean and variance (comparing sexually selected groups vs control groups).
+>*This meta-analysis investigated the consequences of sexual selection experiments on trait mean and variance (comparing sexually selected groups vs control groups).
 Overall, the authors observe sexual selection usually increase mean and reduce variance (especially in females).
@@
 Especially, I am impressed with the detailed supplement which showed the code and analysis.
-However, I have several comments regarding their analysis, which will increase the robustness of results and thus conclusions.**
+However, I have several comments regarding their analysis, which will increase the robustness of results and thus conclusions.*
 
@@
 
-**1 --- The use of Hedges' $g$.
+>*1 --- The use of Hedges' $g$.
 I understand that Hedges' $g$ was probably used because it can take interval measurements as well as ratio measurements (lnCVR can only take ratio measurements).
@@
 experimental and control groups having different variances).
-This is why Hedges' $g$ (Cohen's $d$) was criticized earlier.**
+This is why Hedges' $g$ (Cohen's $d$) was criticized earlier.*
 
-Answer
+>Osenberg, C. W., O. Sarnelle, and S. D. Cooper. 1997. Effect size in ecological experiments: the application of biological models in meta-analysis. \textit{American Naturalist} 150:798-812.
 
-**Osenberg, C. W., O. Sarnelle, and S. D. Cooper. 1997. Effect size in ecological experiments: the application of biological models in meta-analysis. \textit{American Naturalist} 150:798-812.**
+>*As a response, they come up with log response ratio (lnRR) - see*
 
-Answer
+>Hedges, L. V., J. Gurevitch, and P. S. Curtis. 1999. The meta-analysis of response ratios in experimental ecology. \textit{Ecology} 80:1150-1156.
 
-**As a response, they come up with log response ratio (lnRR) - see**
-
-**Hedges, L. V., J. Gurevitch, and P. S. Curtis. 1999. The meta-analysis of response ratios in experimental ecology. \textit{Ecology} 80:1150-1156.**
-
-**I recommend that the authors use lnRR for their effect size for mean comparison as well as Hedge's $g$ to see the robustness of their conclusions for the mean.**
+>*I recommend that the authors use lnRR for their effect size for mean comparison as well as Hedge's $g$ to see the robustness of their conclusions for the mean.*
 
@@
                ggtitle("Comparison between Hedge's g and lnRR effect sizes \n\n"), 
-             lnRR.plots + ggtitle("\n\n"), nrow = 1)
+             lnRR.plots + ggtitle("\n\n"), nrow = 1, widths = c(3,4))
+```
+
+*Fourthly*, Hedges' g appears more normally distributed than lnRR, which to some extent may come as a surprise as **some literature** says lnRR should usually be more normal.
+A normal distribution of the response variable is anticipated to increase model fit.
+
+```{r}
+grid.arrange(ggplot(data = lnRR.data, aes(x = lnRR))+
+  geom_density(),
+
+ggplot(lnRR.data, aes(sample = lnRR)) + 
+  stat_qq() + 
+  stat_qq_line() +
+  labs(x = 'theoretical quantiles', y = "lnRR sample"),
+
+ggplot(data = full_dataset, aes(x = g))+
+  geom_density()+
+  xlab("Hedges' g"),
+
+ggplot(full_dataset, aes(sample = g)) + 
+  stat_qq() + 
+  stat_qq_line() +
+  labs(x = 'theoretical quantiles', y = "Hedges' g sample"))
 ```
@@
 
-**2 --- The authors may consider also doing another set of meta-analyses using lnVR (log variability ratio - proposed in Nakagawa et al. 2015).**
+>*2 --- The authors may consider also doing another set of meta-analyses using lnVR (log variability ratio - proposed in Nakagawa et al. 2015).*
 
-**Nakagawa, S., R.
+>Nakagawa, S., R.
 Poulin, K.
@@
 Meta-analysis of variation: ecological and evolutionary applications and beyond.
-\textit{Methods in Ecology and Evolution} 6:143-152.**
+\textit{Methods in Ecology and Evolution} 6:143-152.
 
-Answer
-
-**As one can see in Figure 2, the mean results (Hedges' $g$) are a mirror image of the variance results (this makes sense CV controls for means).
+>*As one can see in Figure 2, the mean results (Hedges' $g$) are a mirror image of the variance results (this makes sense CV controls for means).
 I would like to see what the absolute change in variances.
@@
 Also, the mean-variance relationship between mean and variance (sd) should be verified (e.g.
-plot log mean and log sd or log variance).**
+plot log mean and log sd or log variance).*
 
@@
 
-```{r, warning = F, message=F}
+```{r, warning = F, message=F, fig.width=6, fig.height=3}
+grid.arrange(full_dataset %>% ggplot(aes(x = mean.low, y = sd.low))+
+  geom_point()+
+  scale_x_log10()+
+  scale_y_log10()+
+  xlab("Mean of Control Group")+
+  ylab("Standard Deviation of Control Group") +
+  geom_smooth(method = "lm", colour = "red"),
+
   full_dataset %>% ggplot(aes(x = mean.high, y = sd.high))+
@@
   ylab("Standard Deviation of Treatment Group") +
-  geom_smooth(method = "lm", colour = "red")
+  geom_smooth(method = "lm", colour = "red"), nrow = 1)
 ```
@@
 *Secondly*, We conducted both Bayesian and REML meta-analyses for lnVR, which we present in the supplementary material and briefly discuss in the manuscript.
-We found similar trends for the meta-analysis of variance using lnCVR and the meta-analysis of variance using lnVR, These are:
+We found a similar trend for the meta-analysis of variance using lnCVR and the meta-analysis of variance using lnVR, These are:
 
 +  In stressful environments sexual selection leads to a decrease in the variance for females, relative to benign environments
-+  Bayesian models suggest that under stressful conditions elevated sexual selection causes a significant decrease in the variance. But this trend is not significant for REML models.
++  Sexual selection reduces variance in females compared to males.
 
-However, when using lnVR, the variability of fitness traits for males under sexual selection increased, while in the model using lnCVR it did not.
+However, when using lnVR, the variability of fitness traits for males under sexual selection increased, lnVR for females in stressful environments was not statistically different from zero, and sexual selection in benign environments increased phenotypic variance for females.
 

### 2018-12-05 Manuscripts/Manuscript_MetaAnalysis.Rmd
More changes to reviewers comments

@@
 
-Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus **sexual conflict** [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014].
+Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus **sexual conflict [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014]**.
 Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males [@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care: \textit{inter}locus sexual conflict [@RN314; @RN276; @RN315].
@@
 Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
-Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, **with a small but significant difference** between benign versus stressful conditions (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
+Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
-**When the lnRR (log Response Ratio) effect size was used to conduct the meta-analysis, the results corroborate those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S4 and Table S16).**
+**When the lnRR (log Response Ratio) effect size was used to conduct the meta-analysis investigating the impact of sex and environment, the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S4 and Table S16).**
 
@@
 
-The effect size estimates we recovered were highly heterogeneous ($I^2$ = 94.9%, 95% CIs: 93-96%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208].
-Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 61.5%, 95% CIs: 42.9-78.9%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 33.5%, 95% CIs: 15.8-52.7%).
-The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model implied a non-zero effect ($\sigma^2$ = 0.145 [0.006-0.517]; \href{https://justincally.github.io/SexualSelection/#bayesian_model:_effects_of_environment_and_sex}{Table S10}).
-Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S3, Table S8}).
+The effect size estimates we recovered were highly heterogeneous ($I^2$ = 94.7%, 95% CIs: 92.4-96.4%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208].
+Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 57.4%, 95% CIs: 38.1-76.5%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 37.4%, 95% CIs: 16.9-57.6%).
+The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model **suggested a probable non-zero effect** ($\sigma^2$ = 0.13 [0-0.46]).
+Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
 \phantomsection
@@
 By applying meta-analysis to log coefficient of variation ratios [*lnCVR*; @RN177], we found evidence that sexual selection reduces phenotypic variation under certain conditions (\autoref{env_sex}b).
-Specifically, phenotypic variance was significantly reduced by sexual selection for fitness components measured in females under stressful conditions (*lnCVR* = -1.0, 95% CIs: -1.4 to -0.69).
+Specifically, phenotypic variance was significantly reduced by sexual selection for fitness components measured in females under stressful conditions (*lnCVR* = -0.75, 95% CIs: -1.13 to -0.36).
 By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (\autoref{env_sex}b; \href{https://justincally.github.io/SexualSelection/#obtaining_lncvr_and_meta-analysis_models}{Tables S13-S16}).
-However, as expected from the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.44, 95% CIs: -0.80 to -0.081; \autoref{env_sex}b).
+However, similar to the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.77, 95% CIs: -1.16 to -0.38; \autoref{env_sex}b).
 
-As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 95.4%, 95% CIs: 93-97%).
-Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 40.1 %, 95% CIs: 23.5 % to 60.2 %), fitness components ($I^2_{fitness\:components}$ = 38.7%, 95% CIs: 17.1-60.7%) and taxon ($I^2_{taxon}$ = 16.6, 95% CIs: 3.1-37.2%).
+As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 95.8%, 95% CIs: 93.4-97.5%).
+Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 34.8 %, 95% CIs: 18.8 % to 56.1 %), fitness components ($I^2_{fitness\:components}$ = 48.8%, 95% CIs: 23.3-70.1%) and taxon ($I^2_{taxon}$ = 12.2, 95% CIs: 2.07-29.8%).
 \phantomsection
@@
 
-The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (\autoref{publication_bias}a; Egger’s test: *z* = 6.2, $p$ < 0.0001).
+The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (\autoref{publication_bias}a; Egger’s test: *z* = 5.9, $p$ < 0.0001).
 Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection.
-There was no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.25) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.0, $p$ = 0.31); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
+There was no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.23) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.2, $p$ = 0.24); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
 
@@
 Our meta-analysis revealed that populations evolving under sexual selection often have higher values for multiple fitness traits, relative to populations where sexual selection was experimentally removed or weakened.
-Notably, sexual selection had small but beneficial effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced) and the proportion of viable offspring.
+**Sexual selection had beneficial effects for traits that were ambiguously or indirectly related to fitness, but had smaller, variable effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced) and the proportion of viable offspring**.
 Fitness traits related to immunocompetence were an exception: sexual selection typically resulted in weaker immunity.
@@
 Furthermore, the overall benefit of sexual selection was greater for females than males, and this sex difference was magnified in stressful environments.
-Consistent with stronger selection on female fitness under stress, female phenotypic variance was substantially reduced when sexual selection was applied under stressful as opposed to benign conditions.
+Consistent with stronger selection on female fitness under stress, **female and mixed-sex samples showed substantially reduced phenotypic variance** when sexual selection was applied under stressful as opposed to benign conditions.
 These results suggest that sexual selection may contribute to population persistence under stressful conditions, such as fluctuating environmental change [@RN173] or spatial variability [@RN189], particularly since female reproductive output is often a limiting factor in population growth [@RN188].
@@
 In all cases, we selected a direction for the effect size calculation such that in our meta-analysis, negative effect sizes indicate that the removal of sexual selection was associated with higher fitness trait values, and positive effect sizes indicate higher fitness when sexual selection was elevated or left intact.
-We also inverted the sign of effect sizes pertaining to measurements that are expected to be negatively related to population fitness (*e.g.*, parasite load, mutation load, extinction risk/rate, mating duration (females), mating latency (males), and rate of senescence).
+We also inverted the sign of effect sizes pertaining to measurements that are expected to be negatively related to population fitness **(*e.g.*, parasite load, mutation load, extinction risk/rate, mating latency (males), and rate of senescence)**.
 Because many of our 65 papers measured multiple fitness outcomes, studied multiple replicate populations, or had three or more sexual selection treatments, we calculated a total of 459 effect sizes.
 
-For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177].
-The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 356 of 459 comparisons.
+**Additionally, using studies that presented means, standard deviations and sample sizes (n = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) CITE.
+The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homodescdandsavn).** However, lnRR was not able to be calculated from studies that
+
+For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177].**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (FIG SXX).
+As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 352 of 459 comparisons.
 \phantomsection
@@
 Given the small number of phylogenetically diverse species, we did not utilise phylogenetic corrections within the models.
+**In our meta-analyses we report Bayes Factors ($BF$), giving the likelihood ratio that the focal effect size differs from zero $BF_{>0}$.**
 
-Secondly, we fixed fitness component as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the 20 fitness components, using the relevant ``predict`` functions for each of the ``R`` packages used (see below).
-Additionally, we report Bayes Factors ($BF$), giving the likelihood ratio that the focal effect size differs from zero.
+**Secondly, we fixed the relationship to fitness class (Ambiguous, Indirect or Direct) as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the three fitness-relationship classes, using the relevant ``predict`` functions for each of the ``R`` packages used (see below).
+This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and reproductive success); predictions for this model on the 20 fitness components were derived as above.
+Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (n = 16); subset for each fitness trait with more than three effect sizes.
+These models were were intercept only REML models with study and taxon as group-level effects**.
 Further details on model parameters can be found within the ESM.
 
-Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g* and *lnCVR*) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
-These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g*: *n* = 336; *lnCVR*: *n* = 277).
+Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g*, *lnRR* and *lnCVR*) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
+These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g*: *n* = 330; *lnRR* & *lnCVR*: *n* = 269).
 We again fit study ID, fitness component, and taxon as random/group level effects.
@@
 
-**Table 1:** Results for the multilevel meta-analysis model testing the effects of sexual selection in different environments and between sexes.
+**Table 1:** Results for the multilevel meta-analysis model testing the effects of sexual selection on fitness (**measured by Hedges' _g_**) in different environments and between sexes.
 Moderator variables whose 95% confidence intervals do not cross zero are shown in bold.

### 2018-12-05 meta_analysis_sexual_selection_pop_fitness.Rmd
More changes to reviewers comments

@@
 library(ggbeeswarm)
+library(gridExtra)
 source("I2_function.R") #Adapted function for obtaining I2 with CIs
@@
 
-**Table S7**
-
-The mean effect size may also be calculated for each of the three fitness trait classes (Ambiguous, Indirect and Direct)
-
-```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
+**Table S7** The predicted effect size for each of the three fitness trait classes (Ambiguous, Indirect and Direct) that are presented in Figure 1 in the manuscript.
+This table presents both Bayesian and REML predictions with some discrepencies in the estimated error margins.
+Figure 1 within the manuscript uses REML predictions.
+
+```{r, warning = FALSE, message=FALSE, error = FALSE}
 if(!file.exists("data/grand.mean.class.bayes.rds")){
@@
 
-```{r}
+```{r, include = FALSE}
 pd <- position_dodge(0.3)
@@
 <img src="figures/ForestPlot_size_reduced.pdf" alt=" "  width="1650" height="2100">
-<br></br>
+
+<br></br>
+
 **Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
@@
 
-outcome.frame %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)
-
+outcome.frame %>% rename(beta = b, n = k) %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)
 ```
@@
 #And plot the results, first for the posterior results of the brms model then for the metafor predictions
-
+pd <- position_dodgev(height = 0.3)
 var.plot.posterior <- post.variance %>% 
@@
 <br></br>
-**Figure S4:** Phenotypic variation changes under sexual selection in stressful environments.
+**Figure S5:** Phenotypic variation changes under sexual selection in stressful environments.
 For females under stressful conditions phenotypic variation decreases (narrows).
@@
 
-**Figure S5** The use of lnCVR (as opposed to lnVR) is justified in this meta-analysis due to the strong mean-variance relationship.
+**Figure S6** The use of lnCVR (as opposed to lnVR) is justified in this meta-analysis due to the strong mean-variance relationship.
 In this case the standard deviation from the treatment group is compared to the means of the treatment group on a log-scale.
@@
 
-**Figure S6:** The effects of sexual selection on the log-variance ratio (lnVR).
+**Figure S7:** The effects of sexual selection on the log-variance ratio (lnVR).
 Without accounting for the mean variance relationship (lnCVR) sexual selection has different effects on the variance measure.
@@
 <br></br>
-**Figure S7:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001).
+**Figure S8:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001).
 The asymmetry appears to come from a spread of positive effect sizes outside the funnel and of varying degrees of precision.
@@
 <br></br>
-**Figure S8:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
+**Figure S9:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
 
@@
 <br></br>
-**Figure S9:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
+**Figure S10:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
 Point size is proportional to the precision of the effect size.
@@
 <br></br>
-**Figure S10:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
+**Figure S11:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
 However, this should not be viewed as evidence against the validity of blinding as a research method.
@@
 <br></br>
-**Figure S11:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
+**Figure S12:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
 
@@
 <br></br>
-**Figure S12:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
+**Figure S13:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
 

### 2018-12-07 Response_to_Nature_Comms.Rmd
Response to reviewers comments

@@
 ---
-title: "Sexual selection improves population fitness: a meta-analysis"
-subtitle: "Response to Decision Letter"
-output: pdf_document
+title: 'Sexual selection improves population fitness: a meta-analysis'
+output:
+  pdf_document: default
+  word_document: default
+subtitle: Response to Decision Letter
+bibliography: Manuscripts/Bibliography/Bibliography.bib
 ---
@@
 library(gridExtra)
+library(janitor)
 #setwd("~/Documents/Uni/metaanalysis/SexualSelection")
@@
 Importantly, to account for the variable and uncertain relationships certain traits have with fitness (as raised by the reviewer).
-We provide a table on how each trait is measured and their relationship with fitness.
-Given that this information was in the Supplementary Material we have **revised the manuscript to clarify the distinctions more thoroughly**.
+We provide a table (Table S1) on how each trait is measured and their relationship with fitness.
+Given that this information was in the Supplementary Material we have **revised the manuscript to clarify the distinctions more thoroughly...
+Probably need to check this again**.
 
@@
 All subsequent models, statistics and figures now take into account this re-classification.
-However, given the small sample size for male attractiveness effect sizes (n = 6), we find only marginal changes in the results and no key changes in the key findings of the study.
+However, given the small sample size for male attractiveness effect sizes (*n* = 6), we find only marginal changes in the results and no key changes in the key findings of the study.
 
@@
 
-Firstly, althought the effect size prediction for the trait has 95 % CIs not overlapping zero, the overall magnitude of the effect size is small (see Table exerpt), and the Bayes Factor (an estimate of the likelihood that the effect size is actually positive) is also small.
+Firstly, although the effect size prediction for the trait has 95 % CIs not overlapping zero, the overall magnitude of the effect size is small (see Table exerpt), and the Bayes Factor (an estimate of the likelihood that the effect size is actually positive) is also small.
 The full table for all predicted effect sizes used in Figure S1 can be seen in **S8**.
@@
 Secondly, the effect size predictions were made using a single model that incorperated all 459 effect sizes, thus model predictions for each trait have narrower confidence intervals as the fitted values do not incorperate measurement error.
-In regards to our analysis, this means that the predictions that appear in Figure 1 are sourced from using ``fitted.brmsfit`` as opposed to ``predict.brmsfit``.
-Additionally, some meta-analyses investigating the effect of a variable on more than one outcome model each outcome (in this case the *fitness component*) seperately.
-Arguably, this method provides more variable model estimates as models will always have lower power due to reduced sample sizes and the incorperation of measurement error in the predictions.
+In regards to our R code and analysis, this means that the predictions that appeared in Figure 1 are sourced from using ``fitted.brmsfit`` as opposed to ``predict.brmsfit``.
+In order to clarify this seeming anomaly in model predictions, some meta-analyses investigating the effect of a variable on more than one outcome model each outcome (in this case the *fitness component*) separately.
+Arguably, this method provides more variable model estimates as models will always have lower power due to reduced sample sizes and the incorporation of measurement error in the predictions.
 We have added a table to the Supplementary Material where models are independently conducted on all fitness components where n > 3 (**Table S9**).
+This may be of particular value for researchers using our meta-analysis as a research tool, whereby they are interested in the effect sizes from only a single trait (as opposed to our focus on population fitness as a whole).
 
 Given, the confusion with regards to Figure 1 as it originally appeared within the manuscript we have altered the figure to a generalized forest plot by grouping the effect sizes from each of the fitness classes (ambiguous, indirect and direct).
-The previous Figure 1 has now been moved to the Supplementry Material with corresponding tables.
+The previous Figure 1 has now been moved to the Supplementary Material with corresponding tables.
 
@@
 
-```{r, fig.height=3}
+```{r, fig.height=2.5, fig.width=6}
 pd <- position_dodgev(0.6)
@@
                show.legend = FALSE,
-               position = position_dodge2(width = 0.2, preserve = "single")) +
+               position = position_dodge2(width = 0.5, preserve = "single")) +
 
@@
              color = "grey20",
-             position = position_dodge2(width = 0.2),
+             position = position_dodge2(width = 0.5),
              show.legend = F) +
@@
 
+When the effect sizes (n = 6) for male attractiveness are viewed isolated from others, one can see that the large effect size (Nelson 2013) shifts the overall predicted effect size to be marginally positive.
+
 >*Thirdly, type of trait measured explained 35% variance, but the authors do not explore this any further.
@@
 
-**Add section in discussion about the variability amongst traits and why some might be subject to trade offs (e.g. immunity).**
+**Add more in discussion about the variability amongst traits and why some might be subject to trade offs (e.g.
+immunity): We do kind of talk about this and an earlier draft had some of Jaceks work with regards to sexual conflict maintaing genetic variance through trade-offs.
+Should we add this back in?**
 
@@
 
-In regards to conducting a meta-analysis on just direct fitnesss components, the reviewer provides a valid question of our use of direct **and** indirect fitness components for the meta-analysis investigating the effects of sex and stress.
+In regards to conducting a meta-analysis on just direct fitness components, the reviewer provides a valid question of our use of direct **and** indirect fitness components for the meta-analysis investigating the effects of sex and stress.
 Based on the question we asked we were interested in the effect of sexual selection on many components of fitness.
@@
 
-```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 10}
+```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 10, fig.height=6}
 model.direct.only <- rma.mv(g, V = var.g, 
@@
 
-Good sugggestion!
+Good suggestion!
 
@@
 **Other comments:**
+
 >*l.
@@
 
-**No difference... kind of there for documentation on how we created it (transparency). What do you think we should do about this Luke?**
+**No difference...
+kind of there for documentation on how we created it (transparency).
+We now get rid of the forest plot in the manuscript.
+However our supp info has a few plots that are in the manuscript.
+I think it is good to show the code we used to create it...
+for reproducibility**
 
@@
 
-Reviewer 2 has rightly pointed out that the use of Hedge's *g* has been critisized for its ability to account for heterogeneity between the control and treatment groups **CITE**.
-We extended our meta-analysis by including the log response ratio (lnRR) as well as a modified version of Hedge's g that attempts to account for this heterogeneity, this modified statistic (**CITE**) can be derived from the ``metafor`` package for meta-analysis, where it is named SMDH (standardized mean difference with heteroscedastic population variances in the two groups).
+Reviewer 2 has rightly pointed out that the use of Hedge's *g* has been critisized for its ability to account for heterogeneity between the control and treatment groups [Osenberg_1997].
+We extended our meta-analysis by including the log response ratio (*lnRR*) as well as a modified version of Hedge's g that attempts to account for this heterogeneity, this modified statistic [@bonett2009meta] can be derived from the ``metafor`` package for meta-analysis [@RN212], where it is named SMDH (standardized mean difference with heteroscedastic population variances in the two groups).
 There are several key findings from the use of lnRR and SMDH:
 
-*Firstly*, Hedge's g and SMDH are highly correlated.
-This suggests that unequal variance between the treatment and control groups (heteroscedasticity) is unlikely to impact the effect size of Hedge's g
+*Firstly*, Hedge's g and SMDH are highly correlated (in means and variance).
+This suggests that unequal variance between the treatment and control groups (heteroscedasticity) is unlikely to impact the effect size of Hedges' g.
 
-```{r, warning=F}
+```{r, warning=FALSE, message = FALSE, error=FALSE}
 #This function writes in the correlation value
@@
   usr <- par("usr"); on.exit(par(usr))
-  par(usr = c(0, 1, 0, 1))
-  r <- abs(cor(x, y, use="pairwise.complete.obs"))
+  par(usr = c(-2.5, 2.5, -2.5, 2.5))
+  r <- cor(x, y, use="pairwise.complete.obs")
   txt <- format(c(r, 0.123456789), digits=digits)[1]
@@
   if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
-  text(0.5, 0.5, txt, cex = cex.cor * r)
+  text(0, 0, txt, cex = cex.cor * 2*r)
 }
@@
 pairs(es.correlation.df %>% select(`Hedge's g`, lnRR, SMDH), lower.panel=panel.smooth, upper.panel=panel.cor)
+# pairs(es.correlation.df %>% select(SMD_var, SMDH_var), lower.panel=panel.smooth, upper.panel=panel.cor)
 ```
@@
 This is a limitation as in our analysis we investigate the effects of sex and stress on a further restricted dataset (direct and indirect fitness traits only).
-Specifically, fewer effect sizes from stressful conditions are able to be calculated; making Hedge's g an advantageous effect size in comparison to lnRR.
+Specifically, fewer effect sizes from stressful conditions are able to be calculated; making Hedges' g an advantageous effect size in comparison to lnRR.
 
-```{r}
+```{r, warning=FALSE, message = FALSE, error=FALSE}
 predictions.complete2 %>% select(Sex, Environment, `Hedge's g sample size` = n) %>% 
-  left_join(predictions.lnRR %>% select(Sex, Environment, `lnRR sample size` = n), by = c("Sex", "Environment")) %>% pander()
+  left_join(predictions.lnRR %>% select(Sex, Environment, `lnRR sample size` = n), by = c("Sex", "Environment")) %>%
+  adorn_totals("row") %>% pander()
 ```
 
-*Thirdly*, if we conduct a meta-analysis using lnRR as the effect size we obtain very similar results with all major conclusions unchanged (keeping in mind that lnRR and Hedge's are on different scales):
+*Thirdly*, if we conduct a meta-analysis using lnRR as the effect size we obtain very similar results with all major conclusions unchanged, keeping in mind that lnRR and Hedge's are on different scales; (further model results can be found within the Supplementary Material):
 + The effect of sexual selection on population fitness is generally positive.
-+ This effect is magnified for females in stressful environments with a significantly positive interaction term (stress*females)
++ This effect is magnified for females in stressful environments with a significantly positive interaction term (stress*females).
 
-```{r, warning = F, fig.width=7, fig.height = 3.5, message = F}
+```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 10, fig.height=6}
 grid.arrange(both.plots + 
                guides(fill = FALSE) + 
-               ggtitle("Comparison between Hedge's g and lnRR effect sizes \n\n"), 
-             lnRR.plots + ggtitle("\n\n"), nrow = 1, widths = c(3,4))
+               ggtitle("Comparison between Hedge's g \nand lnRR effect sizes \n"), 
+             lnRR.plots + ggtitle("\n\n") + xlim(-0.5,0.75), nrow = 1, widths = c(3,4))
 ```
 
-*Fourthly*, Hedges' g appears more normally distributed than lnRR, which to some extent may come as a surprise as **some literature** says lnRR should usually be more normal.
-A normal distribution of the response variable is anticipated to increase model fit.
+*Fourthly*, Hedges' g appears more normally distributed than lnRR, which to some extent may come as a surprise as *lnRR* should usually be more normally distributed around zero.
+However, given that our meta-analysis combines multiple traits, with different scales of magnitude lnRR may lead to some erroneous and biased effect sizes.
+Specifically, @Lajeunesse_2015 showed that *lnRR* is problematic when quantifying the outcome of studies with small sample sizes, and can yield unsuitable variance estimates when the parameter scale of the study are close to zero.
+The more normal distribution of the Hedges' *g* is anticipated to increase model fit.
 
@@
 
-For these reasons we have decided to use Hedge's g as the main effect size throughout the manuscript but reference and provide equivelant statistical analysis for lnRR in the supplementary material.
+The lnRR is a commonly used effect size when the trait of interest has a natural zero point. Given that we did not extract the data with this in mind, it may be a further limitation of *lnRR*.
+
+For these reasons we have decided to use Hedges' *g* as the main effect size throughout the manuscript but reference and provide equivelant statistical analysis for *lnRR* in the supplementary material.
 
@@
 
-The reviewer suggestions have been included in our meta-analysis in order to validate our conclusions. Several key points arise from the meta-analysis of variation:
+The reviewer suggestions have been included in our meta-analysis as Supplementary Material in order to maintain transparency in our conclusions.
+Several key points arise from the meta-analysis of variation:
 
-*Firstly*, as the reviewer suggested we justify the use of lnCVR my assessing the mean-variance relationship.
-Given this finding the use of lnCVR is preferenced over lnVR, as lnVR does not account for the mean-variance relationship.
+*Firstly*, as the reviewer suggested we justify the use of *lnCVR* my assessing the mean-variance relationship.
+The major limitation of lnVR is that it does not account for the mean-variance relationship and that is why lnCVR was suggested as the favourable correction [@RN177].
+Given this finding the use of *lnCVR* is preferenced over *lnVR*, as *lnVR* does not account for the mean-variance relationship.
 
-```{r, warning = F, message=F, fig.width=6, fig.height=3}
+```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 8, fig.height=3.75}
 grid.arrange(full_dataset %>% ggplot(aes(x = mean.low, y = sd.low))+
@@
 
-*Secondly*, We conducted both Bayesian and REML meta-analyses for lnVR, which we present in the supplementary material and briefly discuss in the manuscript.
-We found a similar trend for the meta-analysis of variance using lnCVR and the meta-analysis of variance using lnVR, These are:
+*Secondly*, We conducted both Bayesian and REML meta-analyses for *lnVR*, which we present in the supplementary material and briefly discuss in the manuscript.
+We found a similar trend for the meta-analysis of variance using *lnCVR* and the meta-analysis of variance using *lnVR*, These are:
 
-+  In stressful environments sexual selection leads to a decrease in the variance for females, relative to benign environments
++  In stressful environments sexual selection leads to a decrease in the variance for females, relative to benign environments.  
 +  Sexual selection reduces variance in females compared to males.
 
-However, when using lnVR, the variability of fitness traits for males under sexual selection increased, lnVR for females in stressful environments was not statistically different from zero, and sexual selection in benign environments increased phenotypic variance for females.
+However, when using *lnVR*, the variability of fitness traits for males under sexual selection increased, *lnVR* for females in stressful environments was not statistically different from zero, and sexual selection in benign environments increased phenotypic variance for females.
+Model results and predictions (from the REML model) can be cound within the Supplementary Material.
 
-```{r, warning = F, fig.width=7, fig.height = 3.5, message = F}
+```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 10, fig.height=6}
 grid.arrange(both.var.plots + 
                guides(fill = FALSE) + 
-               ggtitle("Comparison between lnCVR and lnVR effect sizes \n\n"), 
-             both.lnVR.plots + ggtitle("\n\n"), nrow = 1)
+               ggtitle("Comparison between lnCVR \nand lnVR effect sizes \n"), 
+             both.lnVR.plots + ggtitle("\n\n"), nrow = 1, widths = c(3,4))
 ```
 
-**3 --- $I^2$ needs to be explained. $I^2$ is proposed originally here:**
+>*3 --- $I^2$ needs to be explained. $I^2$ is proposed originally here:*
 
-**Higgins, J., and S. Thompson. 2002. Quantifying heterogeneity in a meta-analysis. \textit{Statistics in Medicine} 21:1539 - 1558.**
+>Higgins, J., and S. Thompson. 2002. Quantifying heterogeneity in a meta-analysis. \textit{Statistics in Medicine} 21:1539 - 1558.
 
-**But later expanded in here for mixed models (hierarchical models)**
+>*But later expanded in here for mixed models (hierarchical models)*
 
-**Nakagawa, S., and E. S. A. Santos. 2012. Methodological issues and advances in biological meta-analysis. \textit{Evolutionary Ecology} 26:1253-1274.**
+>Nakagawa, S., and E. S. A. Santos. 2012. Methodological issues and advances in biological meta-analysis. \textit{Evolutionary Ecology} 26:1253-1274.
 
-**This is what the authors use. Also, it will be good to put the degree in I^2 in the context. To do this see this paper:**
+>*This is what the authors use. Also, it will be good to put the degree in I^2 in the context. To do this see this paper:*
 
-**Senior, A.
+>Senior, A.
 M., C.
@@
 Heterogeneity in ecological and evolutionary meta-analyses: its magnitude and implications.
-\textit{Ecology} 97:3293-3299.**
+\textit{Ecology} 97:3293-3299.
 
-Answer
+We value the reviewers feedback and have incorperated all the suggestions within a paragraph within the methods of our manuscript.
 
-**4 --- Publication tests have been conducted on, I think, "meta-analytic" residuals results as suggested in Nakagawa and Santos 2012.
+>*4 --- Publication tests have been conducted on, I think, "meta-analytic" residuals results as suggested in Nakagawa and Santos 2012.
 One could use such residuals to conduct the trim and fill method and see how much the mean could move (see Nakagawa and Santos 2012).
 One should remember the funnel asymmetry could be caused by the presece of heterogeniety.
-See:**
+See:*
 
-**Egger, M., G. Smith, M. Schneider, and C. Minder. 1997. Bias in metaanalysis detected by a simple, graphical test. \textit{Br Med J} 315:629 - 634.**
+>Egger, M., G. Smith, M. Schneider, and C. Minder. 1997. Bias in metaanalysis detected by a simple, graphical test. \textit{Br Med J} 315:629 - 634.
 
-Answer
+**No in-buit functionality for trim-and-fill for rma.mv in metafor... could figure out a way to do it I suppose, not sure if worth it**
 
-**5 --- Figure 3 - are these grey envelopes 95% CI?**
+>*5 --- Figure 3 - are these grey envelopes 95% CI?*
 
-Answer
+Yes they are, we have now included this information in the figure caption. Thank you for highlighting this.
 
-**6 --- the title - do the authors include "a systematic review" - so "a systematic reveiw and meta-analysis" - these two things are diferent - see:**
+>*6 --- the title - do the authors include "a systematic review" - so "a systematic reveiw and meta-analysis" - these two things are diferent - see:*
 
-**Nakagawa, S., and R. Poulin. 2012. Meta-analytic insights into evolutionary ecology: an introduction and synthesis. \textit{Evolutionary Ecology} 26:1085-1099.**
+>Nakagawa, S., and R. Poulin. 2012. Meta-analytic insights into evolutionary ecology: an introduction and synthesis. \textit{Evolutionary Ecology} 26:1085-1099.
 
-Our mstudy does not involve a systematic review.
+Our study does not involve a systematic review.
+The scope of a systematic review was larger than this meta-analysis entailed.
+However, we did use a systematic literature search strategy and PRISMA framework of inclusion/exclusion.
+**I think thewre is some unsureness here on what counts as a systematic review...
+I remember in medicine a meta-analysis MUST be part of a systematic review, but I guess ecology and evolution is more flexible**.
 
-**Hope my comments are useful.**
+>*Hope my comments are useful.*
 
@@
 Answer
+
+# References
+<div id="refs"></div>

### 2018-12-07 Manuscripts/Manuscript_MetaAnalysis.Rmd
Response to reviewers comments

@@
 
-The effect size estimates we recovered were highly heterogeneous ($I^2$ = 94.7%, 95% CIs: 92.4-96.4%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208].
+The effect size estimates we recovered were highly heterogeneous ($I^2$ = 94.7%, 95% CIs: 92.4-96.4%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016].
 Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 57.4%, 95% CIs: 38.1-76.5%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 37.4%, 95% CIs: 16.9-57.6%).
@@
 
-As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 95.8%, 95% CIs: 93.4-97.5%).
-Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 34.8 %, 95% CIs: 18.8 % to 56.1 %), fitness components ($I^2_{fitness\:components}$ = 48.8%, 95% CIs: 23.3-70.1%) and taxon ($I^2_{taxon}$ = 12.2, 95% CIs: 2.07-29.8%).
+As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 99.2%, 95% CIs: 98.8-99.6%).
+Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 36.1 %, 95% CIs: 19.3 % to 59 %), fitness components ($I^2_{fitness\:components}$ = 50.4%, 95% CIs: 24.2-72.1%) and taxon ($I^2_{taxon}$ = 12.7, 95% CIs: 2.14-31%).
 \phantomsection
@@
 **Additionally, using studies that presented means, standard deviations and sample sizes (n = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) CITE.
-The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homodescdandsavn).** However, lnRR was not able to be calculated from studies that
+The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that
 
@@
 
-Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g*, *lnRR* and *lnCVR*) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
-These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g*: *n* = 330; *lnRR* & *lnCVR*: *n* = 269).
+Thirdly, we measured the impact of environment, sex and their interaction on the effect size **(Hedges’ *g*, *lnRR*, *lnCVR* and *lnVR* in the ESM)** associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
+These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign **(Hedges' *g*: *n* = 330; *lnRR*, *lnCVR* & *lnVR*: *n* = 269)**.
 We again fit study ID, fitness component, and taxon as random/group level effects.
 Models investigating other moderators such as number of generations and blinding are presented in the \href{https://justincally.github.io/SexualSelection/}{ESM}.
+
+**For our meta-analysis investigating the effects of environment and sex on the magnitude and variance of fitness-related traits (*Hedges' g* and *lnCVR*) we provide estimates of heterogenity present in the dataset.
+We use the $I^2$ statistic as an estimate of the proportion of total variation in study estimates that is due to heterogeneity [@Higgins_2002].
+$I^2$ is prefered over other statistics as it is independent of sample size, is easily interperatable (pecentage) and can be partitioned between random effects [@RN208].
+Within ecology and evolution heterogeneity in datasets is often high, with the mean $I^2$ from 86 studies above 90 % [@Senior_I2_2016].**
 
@@
 (**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias.
-For (**b**) and (**c**) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).\label{publication_bias}](Figures/publicationbias.pdf)
+For (**b**) and (**c**) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).
+Grey envelopes in (**b**) and (**c**) represent the 95 % CI of the linear regression.\label{publication_bias}](Figures/publicationbias.pdf)
 

### 2018-12-07 meta_analysis_sexual_selection_pop_fitness.Rmd
Response to reviewers comments

@@
 
-From this data we can generate a forest plot with the following:
-
 ```{r, include = FALSE}
@@
         axis.title.x = element_text(hjust = 0.5, size = 14))
-```
-
-<img src="figures/ForestPlot_size_reduced.pdf" alt=" "  width="1650" height="2100">
+
+knitr::include_graphics(path = "figures/ForestPlot_size_reduced.png") 
+```
 
@@
 ```
-These values indicate that 61.5 % of total heterogeneity is due to the **between study** heterogeneity and 33.5 % for **between outcome** heterogeneity between different outcomes.
-The total _I^2^_  is 95 %, a reasonably high _I^2^_ value.
-However this is relatively common in Ecology and Evolution total.
+These values indicate that 57.4 % of total heterogeneity is due to the **between study** heterogeneity and 37.4 % for **between outcome** heterogeneity between different outcomes.
+The total _I^2^_  is 94.7 %, a reasonably high _I^2^_ value.
+However this is relatively common in Ecology and Evolution total [@Senior_I2_2016].
 
@@
 Similar to the meta-analysis on Hedges' g we can obtain _I^2^_ for lnCVR REML model.
-In this case (compared to Hedges' g) we see Taxon has more of a variable effect on overall _I^2^_ estimates, although the overall _I^2^_ remains relatively similar (95.4 %).
-
-```{r}
-I2(variance.model, strict_dataset$var.g) %>% pander(digits = 3)
+In this case (compared to Hedges' g) we see Taxon has more of a variable effect on overall _I^2^_ estimates and the total _I^2^_ is larger.
+
+```{r}
+I2(variance.model, na.omit(strict_dataset$var.lnCVr)) %>% pander(digits = 3)
 ```

### 2018-12-19 Response_to_Nature_Comms.Rmd
luke letter edits

@@
 Please see below for a detailed list of responses to each of the reviewers' points.
+
 We also attach a revised manuscript and a revised copy of the supplementary material, as well as a copy of the revised manuscript in which the significant changes and additions have been highlighted.
@@
 
-In addition to the changes suggested by reviewers, the peer-review process highlighted some human errors on our behalf in the dataset with respect to effect size calculation, these were issues to a select few effect sizes.
-As such, we have thoroughly rechecked our dataset and re-ran the analyses.
-Ultimately the corrections to the dataset have altered our conclusions.
+Finally, in addition to the changes suggested by reviewers, we discovered a small number of errors in our original analysis, related to how effect sizes were calculated from certain primary studies in our meta-analysis.
+As such, we have thoroughly rechecked our dataset and re-ran the analyses with all errors corrected.
+**XXXXXXXXX**
 
@@
 
-Thank you, we now cite those papers as suggested in line 31.
-Additionally, they are especially pertenant to experimental evolution studies using species such as the bulb mite (*Rhizoglyphus robini*)[@Plesnar_2014] and flour beetles (*Gnatocerus cornutus*)[@Harano_2010].
+Thank you, we have added citations of those papers as suggested.
 
@@
 
-The reviewer is correct in that the 95 % CI overlap zero for the three direct fitness components (extinction rate, offspring viability and reproductive success) have 95 % CI overlapping zero.
-Additionally, our analysis reveals that the predicted effect size for direct fitness components has 95 % CIs that overlap zero for Bayesian, but not REML models (REML $\beta$ = 0.13, 95% CIs: 0.022 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.068 to 0.30, $BF_{>0}$ = 4.9).
-In this respect we have tapered and clarified our statement that we find some evidence that sexual selection increases mean values of traits directly related to fitness.
-However, we retain our statement that sexual selection generally elevates the mean of fitness components directly related to fitness as a two-way 95 % confidence limit is an arbitrary cut-off and the Bayes Factors suggest that their is a high likelihood that the effect size for direct fitness components is greater than zero.
+Thank you for catching this -- we have tempered our conclusions in the relevant section of the Discussion, since the results provide only moderate evidence for a positive effect of sexual selection on these traits.
 
@@
 
-It is correct that we did not use the number of generations in our main analysis.
-The manuscript (Methods section) states that the number of generations.
-In the supplementary material we investigate the role of number of generations (the lineage is evolved for) has on fitness in the section *Meta-analyses including many moderator variables* as well as in Figure S12 and S13.
-Generations (specifically, log-Generations) had minimal effect on the effect sizes and was removed for the models that appeared in the main text.
+This information could be found in the supplementary material in the section *Meta-analyses including many moderator variables* as well as in Figure S12 and S13.
+Generations (specifically, log-Generations) had minimal effect on the effect sizes and so was removed for the "minimum adequate models" that we presented in the main text.
+**We now clarify this in the main text JUSTIN, MAYBE REFERENCE THOSE FIGURES WHEN SAYING IT'S NON-SIG OR SOMETHING LIKE THAT**.
 
@@
 
-**No difference...
-kind of there for documentation on how we created it (transparency).
-We now get rid of the forest plot in the manuscript.
-However our supp info has a few plots that are in the manuscript.
-I think it is good to show the code we used to create it...
-for reproducibility**
+Our supplementary material does indeed contain all of our main figures, in order to show the data and code used to generate them.
+We have now made sure that e.g.
+Figure 2 in the HTML supplement is correctly labelled as Figure 2, to make it clear that it is not a different figure.
+**A JOB FOR JUSTIN HERE**
 
@@
 
-Reviewer 2 has rightly pointed out that the use of Hedge's *g* has been critisized for its ability to account for heterogeneity between the control and treatment groups [Osenberg_1997].
-We extended our meta-analysis by including the log response ratio (*lnRR*) as well as a modified version of Hedge's g that attempts to account for this heterogeneity, this modified statistic [@bonett2009meta] can be derived from the ``metafor`` package for meta-analysis [@RN212], where it is named SMDH (standardized mean difference with heteroscedastic population variances in the two groups).
-There are several key findings from the use of lnRR and SMDH:
+Reviewer 2 is correct that Hedges' *g* is imperfect, and so we extended our meta-analysis to include two alternative measures of effect size.
+Firstly, we present the log response ratio (*lnRR*) as suggested by this reviewer.
+Secondly, we present a modified version of Hedges' *g* that attempts to account for this heterogeneity issue [@bonett2009meta], named SMDH (standardized mean difference with heteroscedastic population variances in the two groups).
+There are several key findings from our new analyses using lnRR and SMDH:
 
-*Firstly*, Hedge's g and SMDH are highly correlated (in means and variance).
-This suggests that unequal variance between the treatment and control groups (heteroscedasticity) is unlikely to impact the effect size of Hedges' g.
+*Firstly*, Hedges' *g* and SMDH are highly correlated (in means and variance).
+This suggests that unequal variance between the treatment and control groups (heteroscedasticity) in the primary studies we examined is probably too small to greatly influence Hedges' *g*, which is interesting for the interpretation of earlier meta-analyses using Hedges' *g*.
 
@@
 
-*Secondly*, The calculation of lnRR and SMDH can only be calculated for effect sizes where the study reported means, standard deviations and sample sizes (352 out of 459).
-This is a limitation as in our analysis we investigate the effects of sex and stress on a further restricted dataset (direct and indirect fitness traits only).
-Specifically, fewer effect sizes from stressful conditions are able to be calculated; making Hedges' g an advantageous effect size in comparison to lnRR.
+*Secondly*, we note that lnRR and SMDH can only be calculated in cases where the primary study reported means, standard deviations and sample sizes (352 out of 459).
+This is a limitation, as we must discard roughly 25% of the data in order to use lnRR and SMDH, and so we think it is worthwhile to focus primarily on Hedges' *g* despite its minor limitations in the main manuscript, and use lnRR and SMDH for sensitivity analysis (to verify that the results are qualitatively the same as those produced by Hedges' *g*).
 
@@
 
-*Thirdly*, if we conduct a meta-analysis using lnRR as the effect size we obtain very similar results with all major conclusions unchanged, keeping in mind that lnRR and Hedge's are on different scales; (further model results can be found within the Supplementary Material):
+*Thirdly*, if we conduct a meta-analysis using lnRR as the effect size we obtain very similar results with all our main conclusions unchanged, keeping in mind that lnRR and Hedge's are on different scales (see the revised Supplementary Material).
+Specifically,
 + The effect of sexual selection on population fitness is generally positive.
@@
 
-*Fourthly*, Hedges' g appears more normally distributed than lnRR, which to some extent may come as a surprise as *lnRR* should usually be more normally distributed around zero.
-However, given that our meta-analysis combines multiple traits, with different scales of magnitude lnRR may lead to some erroneous and biased effect sizes.
-Specifically, @Lajeunesse_2015 showed that *lnRR* is problematic when quantifying the outcome of studies with small sample sizes, and can yield unsuitable variance estimates when the parameter scale of the study are close to zero.
-The more normal distribution of the Hedges' *g* is anticipated to increase model fit.
+*Fourthly*, the distribution of the lnRR effect sizes is non-normal (notably moreso than the distribution of Hedges' *g*), perhaps because one can get extreme values when taking a ratio (e.g.
+when the denominator is close to zero).
+Accordingly, @Lajeunesse_2015 showed that *lnRR* is problematic when quantifying the outcome of primary studies with small sample sizes, and can yield unsuitable variance estimates when the parameter scale of the study are close to zero.
+So, Hedges' *g* has the possible practical advantage of increasing model fit in our meta-analysis.
 
@@
 ```
-
-The lnRR is a commonly used effect size when the trait of interest has a natural zero point. Given that we did not extract the data with this in mind, it may be a further limitation of *lnRR*.
-
-For these reasons we have decided to use Hedges' *g* as the main effect size throughout the manuscript but reference and provide equivelant statistical analysis for *lnRR* in the supplementary material.
 
@@
 
-The reviewer suggestions have been included in our meta-analysis as Supplementary Material in order to maintain transparency in our conclusions.
-Several key points arise from the meta-analysis of variation:
+Many thanks -- we have now also present a meta-analysis of variation using lnVR in addition to one using lnCVR. We have the following comments on this new analysis:
 
-*Firstly*, as the reviewer suggested we justify the use of *lnCVR* my assessing the mean-variance relationship.
-The major limitation of lnVR is that it does not account for the mean-variance relationship and that is why lnCVR was suggested as the favourable correction [@RN177].
-Given this finding the use of *lnCVR* is preferenced over *lnVR*, as *lnVR* does not account for the mean-variance relationship.
+*Firstly*, as the reviewer suggested, we now justify our use of lnCVR as opposed to lnVR, by assessing the mean-variance relationship in our data.
+The major limitation of lnVR is that it does not account for the mean-variance relationship; indeed this is why lnCVR was suggested as the favourable correction [@RN177].
+We indeed found a strong positive correlation between mean and variance, suggesting our original use of lnCVR was justified.
 
@@
 
-*Secondly*, We conducted both Bayesian and REML meta-analyses for *lnVR*, which we present in the supplementary material and briefly discuss in the manuscript.
+*Secondly*, We conducted new Bayesian and REML meta-analyses for *lnVR*, which we present in the supplementary material and briefly discuss in the manuscript.
 We found a similar trend for the meta-analysis of variance using *lnCVR* and the meta-analysis of variance using *lnVR*, These are:
@@
 
-We value the reviewers feedback and have incorperated all the suggestions within a paragraph within the methods of our manuscript.
+Many thanks for this feedback -- we have incorporated all the suggestions within a paragraph in the Methods section.
 
@@
 
-**No in-buit functionality for trim-and-fill for rma.mv in metafor... could figure out a way to do it I suppose, not sure if worth it**
+Thanks -- we now remind the reader that funnel plot asymmetry is not decisive evidence for publicaiton bias, because it can also result from unexplained heterogeneity in the original effect sizes.
+We have elected not to implement trim-and-fill since the method seems to have fallen into disfavour among many readers, and because we are unsure how to correctly implement it using the REML- and Bayesian methods we used.
+NB that there is no method for trim-and-fill in mixed meta-analysis in the popular R package `metafor` (which we used), suggesting the method is not simple to implement.
 
@@
 
-Yes they are, we have now included this information in the figure caption. Thank you for highlighting this.
+Yes, and we have now included this information in the figure caption. Thank you for highlighting this.
 
@@
 
-Our study does not involve a systematic review.
-The scope of a systematic review was larger than this meta-analysis entailed.
+We think that the scope of a true systematic review (in the sense used by e.g.
+Cochrane reviews) is larger than our study entails.
 However, we did use a systematic literature search strategy and PRISMA framework of inclusion/exclusion.
-**I think thewre is some unsureness here on what counts as a systematic review...
-I remember in medicine a meta-analysis MUST be part of a systematic review, but I guess ecology and evolution is more flexible**.
+With this in mind, we have left our paper's title as "meta-analysis" rather than calling it a systematic review.
 
@@
 The positive effect of sexual selection on fitness was strongest for females in stressful environments, who also showed reduced variance in fitness under sexual selection.**
-
-Answer
 

### 2018-12-28 Response_to_Nature_Comms.Rmd
changes on plane

@@
 Many thanks for your time, and for the very helpful comments on our manuscript.
-We have considerably reworked the manuscript in light of the many insightful comments and suggestions provided by the reviewers.
-Please see below for a detailed list of responses to each of the reviewers' points.
+We have made many changes in light of the three reviewers' detailed feedback, and we feel that the manuscript has been greatly improved.
+Please see the letter below for our detailed responses to each of the reviewers' points.
+In addition to the revised manuscript and revised supplementary material, we attach a copy of the revised manuscript in which the significant changes and additions have been highlighted.
 
-We also attach a revised manuscript and a revised copy of the supplementary material, as well as a copy of the revised manuscript in which the significant changes and additions have been highlighted.
-Please let us know if we can do anything further to assist you.
-
-Finally, in addition to the changes suggested by reviewers, we discovered a small number of errors in our original analysis, related to how effect sizes were calculated from certain primary studies in our meta-analysis.
-As such, we have thoroughly rechecked our dataset and re-ran the analyses with all errors corrected.
+Finally, while working on the revisions we discovered a small number of errors, namely that we had miscalculated effect size from certain types of primary data.
+As such, we have thoroughly rechecked our dataset and re-ran all analyses with the errors corrected.
 **XXXXXXXXX**
@@
 
-Many thanks for your time and this valuable feedback.
+Many thanks for your time and for you very helpful feedback.
 
@@
 
-The reviewer is correct that several traits are likely under trade-offs with other traits as sexual selection not only affects mean fitness but alters life history traits (*i.e.* sexual selection may increase male body size or attractiveness, but decrease development rate).
-In essence this is why our meta-analysis sought to investigate the *net* effect of sexual selection on population fitness across many traits, rather than one that may be traded off in a given direction.
-Importantly, to account for the variable and uncertain relationships certain traits have with fitness (as raised by the reviewer).
-We provide a table (Table S1) on how each trait is measured and their relationship with fitness.
-Given that this information was in the Supplementary Material we have **revised the manuscript to clarify the distinctions more thoroughly...
-Probably need to check this again**.
-
-Additionally, the reviewers comment that male attractiveness may not be related to population fitness is correct.
-Because male attractiveness may be positively or negatively correlated with average fitness (although in many condition-dependent traits a positive association is assumed) we have re-classified *Male Attractiveness* as ambiguously related to fitness, rather than indirect.
-All subsequent models, statistics and figures now take into account this re-classification.
-However, given the small sample size for male attractiveness effect sizes (*n* = 6), we find only marginal changes in the results and no key changes in the key findings of the study.
+We completely agree that male attractiveness does not affect population fitness directly, and it is important that this is reflected in the meta-analysis.
+In the study, we took this belief into account.
+Specifically, we recorded effect size estimates relating to attractiveness (for completeness, and because it is possible that attractiveness is genetically correlated with traits that *do* affect population fitness).
+However, we classified male attractiveness as having an "indirect" relationship with population fitness (we did the same for other traits too, such as body condition and life span; see Table S1 for a full breakdown).
+However on reflection, we think that attractiveness is even more tenuously linked to population fitness, and so we have re-classified it as "ambiguous", along with traits like "Immunity" and "Development rate".
+Our main analysis excludes all of the ambiguous traits, and so our main results are now not derived from any effect sizes relating to male attractiveness.
+The exclusion of the n = 6 attractiveness effect sizes did not qualitatively change the results.
 
@@
 
-The reviewer raises questions of the analysis that produce seemingly suprising results.
-We agree that some of *significant* predictions in Figure 1 (whereby 95 % CIs do not overlap zero) appear surprising based on the distribution on effect sizes.
-In regards to the trait "male attractiveness", the 95 % CIs do not overlap zero.
-This is the case even though the higher weighted studies are very close to zero.
-However, this seeming anomoly can be explained by various reasons.
-
-Firstly, although the effect size prediction for the trait has 95 % CIs not overlapping zero, the overall magnitude of the effect size is small (see Table exerpt), and the Bayes Factor (an estimate of the likelihood that the effect size is actually positive) is also small.
-The full table for all predicted effect sizes used in Figure S1 can be seen in **S8**.
-Below we provide the exerpt of this table and forest plot for "Male attractiveness".
-
-Secondly, the effect size predictions were made using a single model that incorperated all 459 effect sizes, thus model predictions for each trait have narrower confidence intervals as the fitted values do not incorperate measurement error.
-In regards to our R code and analysis, this means that the predictions that appeared in Figure 1 are sourced from using ``fitted.brmsfit`` as opposed to ``predict.brmsfit``.
-In order to clarify this seeming anomaly in model predictions, some meta-analyses investigating the effect of a variable on more than one outcome model each outcome (in this case the *fitness component*) separately.
-Arguably, this method provides more variable model estimates as models will always have lower power due to reduced sample sizes and the incorporation of measurement error in the predictions.
-We have added a table to the Supplementary Material where models are independently conducted on all fitness components where n > 3 (**Table S9**).
-This may be of particular value for researchers using our meta-analysis as a research tool, whereby they are interested in the effect sizes from only a single trait (as opposed to our focus on population fitness as a whole).
-
-Given, the confusion with regards to Figure 1 as it originally appeared within the manuscript we have altered the figure to a generalized forest plot by grouping the effect sizes from each of the fitness classes (ambiguous, indirect and direct).
-The previous Figure 1 has now been moved to the Supplementary Material with corresponding tables.
+For reference, we here present the result for male attractiveness that the reviewer mentioned.
+The table shows the estimate from the meta-analysis, and the figure shows the n = 6 effect sizes that underlie it, with the mean effect size plotted as vertical lines.
 
@@
 ```
+
+We agree that alone, these 6 studies do not provide strong evidence the mean is positive, though note that the very precisely measured effect sizes are mostly positive.
+However the model of the full dataset contains many other effect sizes, with are primarily positive, and so
+
+The reviewer raises questions of the analysis that produce seemingly suprising results.
+We agree that some of *significant* predictions in Figure 1 (whereby 95 % CIs do not overlap zero) appear surprising based on the distribution on effect sizes.
+In regards to the trait "male attractiveness", the 95 % CIs do not overlap zero.
+This is the case even though the higher weighted studies are very close to zero.
+However, this seeming anomoly can be explained by various reasons.
+
+Firstly, although the effect size prediction for the trait has 95 % CIs not overlapping zero, the overall magnitude of the effect size is small (see Table exerpt), and the Bayes Factor (an estimate of the likelihood that the effect size is actually positive) is also small.
+The full table for all predicted effect sizes used in Figure S1 can be seen in **S8**.
+Below we provide the exerpt of this table and forest plot for "Male attractiveness".
+
+Secondly, the effect size predictions were made using a single model that incorperated all 459 effect sizes, thus model predictions for each trait have narrower confidence intervals as the fitted values do not incorperate measurement error.
+In regards to our R code and analysis, this means that the predictions that appeared in Figure 1 are sourced from using ``fitted.brmsfit`` as opposed to ``predict.brmsfit``.
+In order to clarify this seeming anomaly in model predictions, some meta-analyses investigating the effect of a variable on more than one outcome model each outcome (in this case the *fitness component*) separately.
+Arguably, this method provides more variable model estimates as models will always have lower power due to reduced sample sizes and the incorporation of measurement error in the predictions.
+We have added a table to the Supplementary Material where models are independently conducted on all fitness components where n > 3 (**Table S9**).
+This may be of particular value for researchers using our meta-analysis as a research tool, whereby they are interested in the effect sizes from only a single trait (as opposed to our focus on population fitness as a whole).
+
+Given, the confusion with regards to Figure 1 as it originally appeared within the manuscript we have altered the figure to a generalized forest plot by grouping the effect sizes from each of the fitness classes (ambiguous, indirect and direct).
+The previous Figure 1 has now been moved to the Supplementary Material with corresponding tables.
 

### 2018-12-29 Response_to_Nature_Comms.Rmd
change on desktop

--- 2018-12-19 Response_to_Nature_Comms.Rmd
@@
 
-Leave this for Luke
+We agree that this section could have been much clearer, and have made some changes in light of this comment to clarify what we meant.
+We believe that experiments that manipuate sexual selection on males will alter female fitness traits, even in species where females experience no sexual selection, because of mechanisms such as intra- and inter-locus sexual conflict.
+That is, evolution in males will almost always have pleiotropic consequences for females, or change how males males affect females (i.e.
+sexual selection on males causes of evolution of males' indirect genetic effects on females).
 
-Good suggestion!
+Consider for example the classic Holland and Rice-style experiment, where one removes sexual selection by enforcing random monogamy in a species like _Drosophila_ with 'traditional sex roles'.
+The males in these experiments are predicted to evolve to be less harmful to females, and they are also predicted to evolve a more female-like overall phenotype, due to the removal of selection on male-specific functions involved in sexual selection.
+Both of these male adaptations are expected to cause a genetically-based change in female traits: the former as a result of inter-locus coevolution (e.g.
+female resistance should evolve in response to decreased male harm), and the latter as a result of pleiotropy between the sexes.
+We thus might predict that females would adapt even more than males if female traits have more genetic variation, or if selection is 'harder' on females than males.
+These explanations are speculative and _post hoc_, and so in the revision we are careful to identify them as such.
+This result is arguably opposite to what one would predict, since the removal of sexual selection on males appears to be a more drastic change for males than for females, and we now spell this out as well.
 
@@
 
-Thank you for catching this -- we have tempered our conclusions in the relevant section of the Discussion, since the results provide only moderate evidence for a positive effect of sexual selection on these traits.
+Thank you for catching this -- we have tempered our conclusions in the relevant section of the Discussion, since the results provide only moderate evidence for a positive effect.
 
@@
 
-This information could be found in the supplementary material in the section *Meta-analyses including many moderator variables* as well as in Figure S12 and S13.
-Generations (specifically, log-Generations) had minimal effect on the effect sizes and so was removed for the "minimum adequate models" that we presented in the main text.
-**We now clarify this in the main text JUSTIN, MAYBE REFERENCE THOSE FIGURES WHEN SAYING IT'S NON-SIG OR SOMETHING LIKE THAT**.
+For relevant results, please see the section of the results that reads "Other moderator variables that we examined had minimal impacts on effect size (Figure S2, Table S10).
+Specifically, effect size did not depend on whether or not the study was conducted blind (Figure S9), nor on the number of generations for which the experimental evolution study was run (Figure S10, S11)." In the methods, we wrote "Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), blinding of researchers to treatments and number of generations a treatment group underwent experimentally evolution."
 
@@
 Our supplementary material does indeed contain all of our main figures, in order to show the data and code used to generate them.
-We have now made sure that e.g.
-Figure 2 in the HTML supplement is correctly labelled as Figure 2, to make it clear that it is not a different figure.
+We have changed the numbering of the supplementary figures, so that e.g.
+Figure 2 in the HTML supplement is correctly labelled as Figure 2 and not as Fig.
+S1, to make it clear that it is the same figure.
 **A JOB FOR JUSTIN HERE**
@@
 *Fourthly*, the distribution of the lnRR effect sizes is non-normal (notably moreso than the distribution of Hedges' *g*), perhaps because one can get extreme values when taking a ratio (e.g.
-when the denominator is close to zero).
+if the denominator is close to zero).
 Accordingly, @Lajeunesse_2015 showed that *lnRR* is problematic when quantifying the outcome of primary studies with small sample sizes, and can yield unsuitable variance estimates when the parameter scale of the study are close to zero.
@@
 *Firstly*, as the reviewer suggested, we now justify our use of lnCVR as opposed to lnVR, by assessing the mean-variance relationship in our data.
-The major limitation of lnVR is that it does not account for the mean-variance relationship; indeed this is why lnCVR was suggested as the favourable correction [@RN177].
+The major limitation of lnVR is that it does not account for the mean-variance relationship; indeed this is why lnCVR has been recommended over lnVR [@RN177].
 We indeed found a strong positive correlation between mean and variance, suggesting our original use of lnCVR was justified.
@@
 However, when using *lnVR*, the variability of fitness traits for males under sexual selection increased, *lnVR* for females in stressful environments was not statistically different from zero, and sexual selection in benign environments increased phenotypic variance for females.
-Model results and predictions (from the REML model) can be cound within the Supplementary Material.
+Model results and predictions (from the REML model) can be cound in the Supplementary Material.
 
@@
 
-Thanks -- we now remind the reader that funnel plot asymmetry is not decisive evidence for publicaiton bias, because it can also result from unexplained heterogeneity in the original effect sizes.
+Thanks -- we now **remind the reader that funnel plot asymmetry is not decisive evidence** for publication bias, because it can also result from unexplained heterogeneity in the original effect sizes.
 We have elected not to implement trim-and-fill since the method seems to have fallen into disfavour among many readers, and because we are unsure how to correctly implement it using the REML- and Bayesian methods we used.
@@
 
-We think that the scope of a true systematic review (in the sense used by e.g.
-Cochrane reviews) is larger than our study entails.
-However, we did use a systematic literature search strategy and PRISMA framework of inclusion/exclusion.
-With this in mind, we have left our paper's title as "meta-analysis" rather than calling it a systematic review.
+We agree, and we have changed the title to "Sexual selection improves population fitness: a systematic review and meta-analysis".  **DO THIS**
 
@@
 
-They were extremely useful, many thanks!
+Very useful, thank you!
 

### 2018-12-29 Response_to_Nature_Comms.Rmd
luke changes

@@
 
-Finally, while working on the revisions we discovered a small number of errors, namely that we had miscalculated effect size from certain types of primary data.
-As such, we have thoroughly rechecked our dataset and re-ran all analyses with the errors corrected.
-**XXXXXXXXX**
-
 Yours Sincerely,
@@
 
-We completely agree that male attractiveness does not affect population fitness directly, and it is important that this is reflected in the meta-analysis.
-In the study, we took this belief into account.
-Specifically, we recorded effect size estimates relating to attractiveness (for completeness, and because it is possible that attractiveness is genetically correlated with traits that *do* affect population fitness).
-However, we classified male attractiveness as having an "indirect" relationship with population fitness (we did the same for other traits too, such as body condition and life span; see Table S1 for a full breakdown).
-However on reflection, we think that attractiveness is even more tenuously linked to population fitness, and so we have re-classified it as "ambiguous", along with traits like "Immunity" and "Development rate".
+We completely agree that male attractiveness does not affect population fitness directly, and it is important to separate this trait from the "true" measures of population fitness in the meta-analysis.
+We do this more carefully in the revised meta-analysis.
+Specifically, in the original study, we classified male attractiveness as having an "indirect" relationship with population fitness (this is also how we classified traits such as body condition and life span; see Table S1 for a full breakdown).
+However on reflection, we think that attractiveness is only tenuously linked to population fitness, and so we have re-classified its relationship with population fitness as "ambiguous", along with traits like "Immunity" and "Development rate".
 Our main analysis excludes all of the ambiguous traits, and so our main results are now not derived from any effect sizes relating to male attractiveness.
 The exclusion of the n = 6 attractiveness effect sizes did not qualitatively change the results.
+
+**Additionally, we have split the trait "Reproductive success" into "Female reproductive success" and "Male reproductive success", in recognition of the facts that these two fitness components are maximised very differently, and are likely to have differentially related to population fitness.**
+
+Effect on the results...
 
@@
 ```{r}
-left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component")  %>% filter(`Fitness Component` == "Male Attractiveness") %>% pander(split.table = Inf, digits = 2)
+left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component") %>% 
+  filter(`Fitness Component` == "Male Attractiveness") %>% pander(split.table = Inf, digits = 2)
 ```
@@
 
-We agree that alone, these 6 studies do not provide strong evidence the mean is positive, though note that the very precisely measured effect sizes are mostly positive.
-However the model of the full dataset contains many other effect sizes, with are primarily positive, and so
+We agree that alone, these 6 studies do not provide strong evidence the mean is positive, although we note that some of the precisely measured effect sizes, and one of the imprecise ones, are positive, so this borderline significant result is not too anomalous.
 
-The reviewer raises questions of the analysis that produce seemingly suprising results.
-We agree that some of *significant* predictions in Figure 1 (whereby 95 % CIs do not overlap zero) appear surprising based on the distribution on effect sizes.
-In regards to the trait "male attractiveness", the 95 % CIs do not overlap zero.
-This is the case even though the higher weighted studies are very close to zero.
-However, this seeming anomoly can be explained by various reasons.
-
-Firstly, although the effect size prediction for the trait has 95 % CIs not overlapping zero, the overall magnitude of the effect size is small (see Table exerpt), and the Bayes Factor (an estimate of the likelihood that the effect size is actually positive) is also small.
-The full table for all predicted effect sizes used in Figure S1 can be seen in **S8**.
-Below we provide the exerpt of this table and forest plot for "Male attractiveness".
-
-Secondly, the effect size predictions were made using a single model that incorperated all 459 effect sizes, thus model predictions for each trait have narrower confidence intervals as the fitted values do not incorperate measurement error.
-In regards to our R code and analysis, this means that the predictions that appeared in Figure 1 are sourced from using ``fitted.brmsfit`` as opposed to ``predict.brmsfit``.
-In order to clarify this seeming anomaly in model predictions, some meta-analyses investigating the effect of a variable on more than one outcome model each outcome (in this case the *fitness component*) separately.
-Arguably, this method provides more variable model estimates as models will always have lower power due to reduced sample sizes and the incorporation of measurement error in the predictions.
-We have added a table to the Supplementary Material where models are independently conducted on all fitness components where n > 3 (**Table S9**).
-This may be of particular value for researchers using our meta-analysis as a research tool, whereby they are interested in the effect sizes from only a single trait (as opposed to our focus on population fitness as a whole).
-
-Given, the confusion with regards to Figure 1 as it originally appeared within the manuscript we have altered the figure to a generalized forest plot by grouping the effect sizes from each of the fitness classes (ambiguous, indirect and direct).
-The previous Figure 1 has now been moved to the Supplementary Material with corresponding tables.
-
-When the effect sizes (n = 6) for male attractiveness are viewed isolated from others, one can see that the large effect size (Nelson 2013) shifts the overall predicted effect size to be marginally positive.
+Secondly, the effect size predictions were made using a single model that incorporated hundreds of other effect sizes, which allows the model is allowed to 'share information' between the different fitness measures.
+For example, if the overall mean effect size is positive, then smaller subsets of the dataset (like the attractiveness subset, with n = 6 studies) will tend to be made slightly more positive.
+That is, in the absence of precise information about the true average effect size for studies of attractiveness, the model uses some information provided by the global average.
 
@@
 
-**Add more in discussion about the variability amongst traits and why some might be subject to trade offs (e.g.
-immunity): We do kind of talk about this and an earlier draft had some of Jaceks work with regards to sexual conflict maintaing genetic variance through trade-offs.
-Should we add this back in?**
+In the revision, we have now replaced our main analysis in light of this comment, and reassuringly we obtained qualitatively the same result.
+In the original, we culled the dataset to only include the "direct" and "indirect" measures of popualtion fitness (this decision was taken to maximise the use of the data).
+In the revision, we have eliminated the "indirect" measures, leaving n = **XX** "direct" effect sizes in our main analysis.
+To facilitate easy comparison, we present the new and old results below: one can see that nothing has changed (in terms of statistical significance).
+To avoid reader fatigue in our manuscript (since we already chop and change the dataset in many different ways), we have changed this analysis to include only the "direct" measures, i.e.
+the graph on the right, and the table below, rather than presenting both versions.
 
-The reviewer provides an accurate shortcoming of discussion on the observed heterogeneity between fitness components.
+<!-- **Add more in discussion about the variability amongst traits and why some might be subject to trade offs (e.g.
+immunity): We do kind of talk about this and an earlier draft had some of Jaceks work with regards to sexual conflict maintaining genetic variance through trade-offs.
+Should we add this back in?** -->
+
+<!-- The reviewer provides an accurate shortcoming of discussion on the observed heterogeneity between fitness components.
 The sixth paragraph of our discussion is raises some potential reasons why heterogeneity may be high within our meta-analysis.
@@
 Even when metanalyses are conducted on a single trait, heterogeneity ($I^2$) is still high > 90 %.
+-->
 
-In regards to conducting a meta-analysis on just direct fitness components, the reviewer provides a valid question of our use of direct **and** indirect fitness components for the meta-analysis investigating the effects of sex and stress.
+<!-- In regards to conducting a meta-analysis on just direct fitness components, the reviewer provides a valid question of our use of direct **and** indirect fitness components for the meta-analysis investigating the effects of sex and stress.
 Based on the question we asked we were interested in the effect of sexual selection on many components of fitness.
+-->
 
-Nevertheless, we conducted our analysis using just direct fitness measures.
+<!-- Nevertheless, we conducted our analysis using just direct fitness measures.
 We find the same key associations; that sexual selection generally elevates fitness, especially for females, with the effect magnified in stressful environments.
 Below we present the findings.
-**should we put this in the supp?**
+-->
+<!-- **should we put this in the supp?** -->
 
-Additionally, in order to further distinguish the effects of sexual selection on ambiguous, indirect and direct fitness components, we have structured the second paragraph of the results to more consistently reflect our classification system.
+<!-- Additionally, in order to further distinguish the effects of sexual selection on ambiguous, indirect and direct fitness components, we have structured the second paragraph of the results to more consistently reflect our classification system.
+-->
 
@@
 
-Consider for example the classic Holland and Rice-style experiment, where one removes sexual selection by enforcing random monogamy in a species like _Drosophila_ with 'traditional sex roles'.
-The males in these experiments are predicted to evolve to be less harmful to females, and they are also predicted to evolve a more female-like overall phenotype, due to the removal of selection on male-specific functions involved in sexual selection.
+Consider for example the classic Holland and Rice-style experiment, where one removes sexual selection by enforcing random monogamy in a species with 'traditional sex roles', such as _Drosophila_.
+Males are predicted to evolve to be less harmful to females in these experiments, and they are also predicted to evolve a more female-like overall phenotype, due to the removal of selection on male-specific functions involved in sexual selection.
 Both of these male adaptations are expected to cause a genetically-based change in female traits: the former as a result of inter-locus coevolution (e.g.
-female resistance should evolve in response to decreased male harm), and the latter as a result of pleiotropy between the sexes.
+female resistance should evolve in response to the reduction in male-induced harm), and the latter as a result of pleiotropy between the sexes.
 We thus might predict that females would adapt even more than males if female traits have more genetic variation, or if selection is 'harder' on females than males.
 These explanations are speculative and _post hoc_, and so in the revision we are careful to identify them as such.
-This result is arguably opposite to what one would predict, since the removal of sexual selection on males appears to be a more drastic change for males than for females, and we now spell this out as well.
+Our result is arguably opposite to what one would predict, because naively one would expect sexual selection to have greater effects on the phenotype of males, and we now spell this out as well.
 
@@
 
-Not too sure what he means.
-
-Answer
+Unfortunately, too few studies have manipulated sexual selection (independently of _all_ selection) using the middle class neighborhood design for a reliable test.
+However we did collect data on how sexual selection was manipulated: many studies imposed random monogamy, but other studies instead manipulated the adult sex ratio (e.g.
+3 males 1 female, 2 of each, or 3 females 1 male).
+In the revised manuscript we now included "manipulation type" as a two-level moderator.
+We find no effect of manipulation type on effect size, suggestion that both ways of removing sexual selection had a similar effect on population fitness traits.
+**See the revised Table SX.**
 
@@
 
-Reviewer 2 is correct that Hedges' *g* is imperfect, and so we extended our meta-analysis to include two alternative measures of effect size.
+After reading htose references, we agree that Hedges' *g* is imperfect, and so we checked the robustness of our meta-analysis using two alternative measures of effect size.
 Firstly, we present the log response ratio (*lnRR*) as suggested by this reviewer.
@@
 
-*Firstly*, Hedges' *g* and SMDH are highly correlated (in means and variance).
+*Firstly*, we found that Hedges' *g* and SMDH are highly correlated (in means and variance).
 This suggests that unequal variance between the treatment and control groups (heteroscedasticity) in the primary studies we examined is probably too small to greatly influence Hedges' *g*, which is interesting for the interpretation of earlier meta-analyses using Hedges' *g*.
@@
 
-*Secondly*, we note that lnRR and SMDH can only be calculated in cases where the primary study reported means, standard deviations and sample sizes (352 out of 459).
-This is a limitation, as we must discard roughly 25% of the data in order to use lnRR and SMDH, and so we think it is worthwhile to focus primarily on Hedges' *g* despite its minor limitations in the main manuscript, and use lnRR and SMDH for sensitivity analysis (to verify that the results are qualitatively the same as those produced by Hedges' *g*).
+*Secondly*, we note that lnRR and SMDH can only be calculated in cases where the primary study reported means, standard deviations and sample sizes (352 out of 459 primary effect sizes).
+This is a limitation of lnRR and SMDH, as we must discard roughly 25% of the data in order to use them instead of Hedges' *g*.
+We therefore think it is best to focus primarily on Hedges' *g* despite its minor limitations, and to use lnRR and SMDH for sensitivity analysis in the online supplementary material.
 
@@
 The major limitation of lnVR is that it does not account for the mean-variance relationship; indeed this is why lnCVR has been recommended over lnVR [@RN177].
-We indeed found a strong positive correlation between mean and variance, suggesting our original use of lnCVR was justified.
+We indeed found a strong positive correlation between mean and variance, suggesting that we should indeed lnCVR and not lnVR.
 
@@
 
-*Secondly*, We conducted new Bayesian and REML meta-analyses for *lnVR*, which we present in the supplementary material and briefly discuss in the manuscript.
-We found a similar trend for the meta-analysis of variance using *lnCVR* and the meta-analysis of variance using *lnVR*, These are:
-
-+  In stressful environments sexual selection leads to a decrease in the variance for females, relative to benign environments.  
-+  Sexual selection reduces variance in females compared to males.
-
-However, when using *lnVR*, the variability of fitness traits for males under sexual selection increased, *lnVR* for females in stressful environments was not statistically different from zero, and sexual selection in benign environments increased phenotypic variance for females.
-Model results and predictions (from the REML model) can be cound in the Supplementary Material.
+Although we think that *lnVR* is not preferable due to this positive relationship, we ran our meta-analyses using *lnVR* in the interests of completeness.
+**We present this new result in the supplementary material and briefly discuss it in the manuscript**.
+To summarise, we found very similar patterns, although the statistical significance of one of the results disappeared; see the following figure:
 
@@
 
-Many thanks for this feedback -- we have incorporated all the suggestions within a paragraph in the Methods section.
+Many thanks for this feedback -- we have **incorporated all these suggestions in the Methods section**.
 
@@
 
-**The results of this meta-analysis broadly concur with current theoretical predictions, and are likely to interest a wide readership.
+>*The results of this meta-analysis broadly concur with current theoretical predictions, and are likely to interest a wide readership.
 Across all studies, environment types and fitness measures there was a small positive effect of sexual selection on mean population fitness, although effect sizes varied with the fitness measure used.
-The positive effect of sexual selection on fitness was strongest for females in stressful environments, who also showed reduced variance in fitness under sexual selection.**
+The positive effect of sexual selection on fitness was strongest for females in stressful environments, who also showed reduced variance in fitness under sexual selection.*
 
-**The authors discuss these findings thoughtfully, although they focus more on the (weaker) effects found for ‘direct’ measures of fitness while somewhat neglecting the effects seen for ‘indirect’ fitness measures (e.g.
+>*The authors discuss these findings thoughtfully, although they focus more on the (weaker) effects found for ‘direct’ measures of fitness while somewhat neglecting the effects seen for ‘indirect’ fitness measures (e.g.
 of attractiveness, mating latency, lifespan, ejaculate traits).
-These potentially deserve more consideration, especially as many appear to be male-limited traits or measured mainly in males, that would appear to have a direct bearing on male mating success (if an indirect link to overall fitness), yet despite this the overall effect of sexual selection on male fitness is not significant.**
+These potentially deserve more consideration, especially as many appear to be male-limited traits or measured mainly in males, that would appear to have a direct bearing on male mating success (if an indirect link to overall fitness), yet despite this the overall effect of sexual selection on male fitness is not significant.*
 
-Need to answer this in a similar line to Jaceks comments.
+Please see our earlier response to Prof.
+Radwan: we do not consider male mating success (and related traits) to be correlates of population fitness, which is why the results differ between our strict analysis and the one that includes all the traits.
+Additionally, we chose to spend more time writing about the "direct" effects because our main focus is on population fitness.
+We agree that our secondary results are interesting as well, but we wanted to keep the manuscript focused and concise.
+Also, there is no theoretical controversy over how sexual selection should affect traits like male mating success; by contrast, the relationship between sexual selection and population fitness is contentious.
 
-**I have only a few more specific comments:**
+>*I have only a few more specific comments:*
 
-**Does your approach consider variation in the intensity of sexual selection exclusively on males?
+>*Does your approach consider variation in the intensity of sexual selection exclusively on males?
 This is worth noting (e.g.
-statements such as that on line 98-99 might be amended to “Sexual selection on males significantly improved female fitness.”)**
+statements such as that on line 98-99 might be amended to “Sexual selection on males significantly improved female fitness.”)*
 
-Answer
+>*Experiments manipulating the sex ratio to alter sexual selection might simultaneously decrease sexual selection on males while increasing sexual selection on females.
+Would this be classified as reduced sexual selection in your analyses?
+I don’t think you included this aspect of study design as a moderator variable in any of your analyses – given that close to half of the effects you include come from “alternative manipulations” (line 70) perhaps you could test whether this affects effect size?*
 
-**Experiments manipulating the sex ratio to alter sexual selection might simultaneously decrease sexual selection on males while increasing sexual selection on females.
-Would this be classified as reduced sexual selection in your analyses?
-I don’t think you included this aspect of study design as a moderator variable in any of your analyses – given that close to half of the effects you include come from “alternative manipulations” (line 70) perhaps you could test whether this affects effect size?**
+Some of the studies used the enforced monogamy design (as in Holland and Rice 2002), where one compares monogamous family groups with polyandrous ones (i.e.
+multiple males and one female), and so these manipulate sexual selection on males only, and eliminate sexual selection on females.
+Others instead manipulated the adult sex ratio (e.g.
+3 males 1 female, 2 of each, or 3 females 1 male); these studies manipulate sexual selection on both sexes simultaneously.
+For the latter type, we considered the strength of sexual selection on males to be variable of interest, though it is confounded with the strength of sexual seleciton on females.
+To test if there was any difference in the effect sizes induced by these two types of manipulation, we now include "manipulation type" as a moderator variable: there was no effect (see above comment to Reviewer 1).
+**We now also stress that we consider sexual selection on males, as suggested.**
 
-Answer
+>*It seems possible that sexual selection on females, and not only on males, could affect population fitness – potentially even more directly than sexual selection on males.
+And might differing extents of sexual selection in each sex interact with the differences you saw in fitness measured in males vs.
+females?*
 
-**It seems possible that sexual selection on females, and not only on males, could affect population fitness – potentially even more directly than sexual selection on males.
-And might differing extents of sexual selection in each sex interact with the differences you saw in fitness measured in males vs.
-females?**
+It is possible that sexual selection on females on affects population fitness, although to our knowledge no-one has considered or modelled this before.
+Also, we are not a aware of any experiments that have manipulated the opportunity for sexual selection on females independently of any other factors (e.g.
+sexual selection on males; see above comment).
+So, we have opted not to discuss or analyse this further, as we think the data do not yet allow for a robust test.
 
-Answer
+>*L111-118 It seems a little odd that there is no residual heterogeneity in your $I^2$ estimates.
+From the supplemental information it is not entirely clear to me how you have adapted the function that is under development in “metaAidR”, but can you double check that you have appropriately incorporated the residual variance into these estimates?*
 
-**L111-118 It seems a little odd that there is no residual heterogeneity in your $I^2$ estimates.
-From the supplemental information it is not entirely clear to me how you have adapted the function that is under development in “metaAidR”, but can you double check that you have appropriately incorporated the residual variance into these estimates?**
+**Check this please Justin - I could not see what you changed in the R script**
 
-Answer
+>*L307-311 Please clarify here that lnCVR was calculated as the ratio $ln(CVfitness_{SS}/CVfitness_{no SS})$*
 
-**L307-311 Please clarify here that lnCVR was calculated as the ratio $ln(CVfitness_{SS}/CVfitness_{no SS})$**
+**We now clarify this as suggested.**
 
-Answer
+>*Fig. 3 Please explain the dashed red and black lines in the figure caption.*
 
-**Fig. 3 Please explain the dashed red and black lines in the figure caption.**
+**We now clarify this as suggested.**
 
-Answer
+>*Tables 1, 2 Please check – the parameter estimates for ‘Female sex’ and test for ‘Female > Male’ are bolded inconsistently between the REML and Bayesian models where these estimates are identical.*
 
-**Tables 1, 2 Please check – the parameter estimates for ‘Female sex’ and test for ‘Female > Male’ are bolded inconsistently between the REML and Bayesian models where these estimates are identical.**
-
-Answer
+**Please check and answer this Justin**
 

### 2018-12-29 Manuscripts/Manuscript_MetaAnalysis.Rmd
luke changes

@@
 This is because stable environments create consistent selection, preferentially eroding genetic variation at sexually-concordant loci (*i.e.* loci where the fittest genotype is the same in both sexes) and leaving behind variation at sexually antagonistic loci.
-We know of no systematic reviews testing this latter theory, though it is has motivated several recent empirical tests [*e.g.* @RN187; @RN200; @RN254], and is relevant to conservation genetics.
+We know of no systematic reviews of this latter theory, though it is has motivated several recent empirical tests [*e.g.* @RN187; @RN200; @RN254], and is relevant to conservation genetics.
 
@@
 In total, we obtained effect sizes for 20 different fitness traits, with reproductive success ($n$ = 156) and offspring viability ($n$ = 56) being the most commonly-measured traits.
-We classified 216 effect sizes as direct measures of fitness, 141 as indirect, and the remaining 102 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
+We classified **216 effect sizes as direct measures of fitness, 141 as indirect, and the remaining 102 effect sizes as ambiguous** (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
 Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, reproductive success, offspring viability, and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, and early fecundity).

### 2018-12-29 meta_analysis_sexual_selection_pop_fitness.Rmd
luke changes

@@
 knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
+knitr::opts_chunk$set(warning=FALSE, message=FALSE) # Suppress warnings in the HTML output
+
 ```
@@
 
-**Study ID**: An ID given to the published paper the effect size is sourced from (n=65).
-
-**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup. [Was not use in analysis]
+**Study ID**: An ID given to the published paper the effect size is sourced from (n = 69).
+
+**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup. [Was not used in analysis]
 
@@
 
-**Table S9** In some instances it may be beneficial to the reader to obtain average effect sizes of each fitness trait **entirely independent** of other traits.
+**Table S9** In some instances it may be beneficial to the reader to obtain average effect sizes of each fitness trait **entirely independently** of other traits.
 For this reason we present a summary of independent model estimates for 16 fitness components with a sample size greater than 3 effect sizes (n>3).
@@
 
-### Restricted analysis to just the higher-quality data
+### Restricted analysis of just the higher-quality data
 
@@
 
+<!-- Note to Justin: here, I changed to just the 'direct' measures, and added the "Enforced Monogamy" predictor.
+You'll need to add the Bayesian equivalent, and alter the code for the figure etc.
+I think it's better this way, and the results don't appear to change in any major way -->
+
 ```{r, message=FALSE, error = FALSE, warning=FALSE}
+# strict_dataset <- full_dataset %>% 
+#   filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>% 
+#   mutate(Sex = relevel(Sex, ref = "M"),
+#          Environment = relevel(factor(Environment), ref = "Unstressed"),
+#          Taxon = relevel(factor(Taxon), ref = "Beetle"))
+
 strict_dataset <- full_dataset %>% 
-  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>% 
+  filter(Outcome.Class == "Direct" & Environment != "Not Stated")  %>% 
   mutate(Sex = relevel(Sex, ref = "M"),
-         Environment = relevel(Environment, ref = "Unstressed"),
-         Taxon = relevel(Taxon, ref = "Beetle"),
-         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))
+         Environment = relevel(factor(Environment), ref = "Unstressed"),
+         Taxon = relevel(factor(Taxon), ref = "Beetle"))
 
 model.complete <- rma.mv(g, V = var.g, 
-                         mods = ~ 1 + Sex * Environment + Taxon, 
+                         mods = ~ 1 + Sex * Environment + Taxon + Enforced.Monogamy, 
                          random = list(~ 1 | Study.ID, 
@@
 ```
+
+<!-- Bayesian equivalent is something like: -->
+
+<!-- ```{r} -->
+<!-- model.complete.bayesian <- brm(g | se(SE)  ~ 1 + Sex * Environment * Taxon + Enforced.Monogamy -->
+<!--                   + (1|Study.ID)  -->
+<!--                   + (1|Outcome),  -->
+<!--                   family = "gaussian",  -->
+<!--                   seed = 1, -->
+<!--                   cores = 1, chains = 4, iter = 4000,  -->
+<!--                   control = list(adapt_delta = 0.9999, max_treedepth = 15), -->
+<!--                   data = strict_dataset %>% mutate(SE = sqrt(var.g))) -->
+<!-- ``` -->
 
@@
 
-  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, interaction1=interaction1, interaction2=interaction2))
+  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, 1, interaction1, interaction2))
 }
@@
 The only difference to the previous model is that `Taxon` is now treated as a random effect.
+Note that this analysis again uses the strict dataset, containing only "direct" fitness measures and those where we were able to score the presence/absence of environmental stress.
 
@@
 
-```{r}
+```{r warning=FALSE}
 I2(model.complete2, strict_dataset$var.g) %>% pander(digits = 3)

### 2019-01-02 Response_to_Nature_Comms.Rmd
Updated Reproductive Success

@@
 
-**Additionally, we have split the trait "Reproductive success" into "Female reproductive success" and "Male reproductive success", in recognition of the facts that these two fitness components are maximised very differently, and are likely to have differentially related to population fitness.**
+Additionally, we have split the trait "Reproductive success" into "Female Reproductive Success", "Male Reproductive Success" and "Both Reproductive Success", the latter from studies where offspring number was measured from a given male-female pair interaction.
+We have made this reclassification in recognition of the facts that these two fitness components are maximised very differently, and are likely to have differentially related to population fitness.
+Specifically, we maintain "Female Reproductive Success" and "Both Reproductive Success" as direct measures of fitness but class "Male Reproductive Success" as an ambiguous measure of fitness.
 

### 2019-01-02 meta_analysis_sexual_selection_pop_fitness.Rmd
Updated Reproductive Success

@@
 # Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
-full_dataset$Outcome_f = factor(full_dataset$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
+full_dataset$Outcome_f = factor(full_dataset$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Male Reproductive Success', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Both Reproductive Success', 'Extinction Rate', 'Female Reproductive Success', 'Offspring Viability'))
 
@@
 
-knitr::include_graphics(path = "figures/ForestPlot_size_reduced.png") 
+#knitr::include_graphics(path = "figures/ForestPlot_size_reduced.png") 
 ```
@@
 
-outcome.list.factor <-  c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+outcome.list.factor <-  c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Male Reproductive Success', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Both Reproductive Success', 'Extinction Rate', 'Female Reproductive Success', 'Offspring Viability')
 
@@
 # Obtain Bayes Factor of likelihood that the outcome is greater than 0
-BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Male Reproductive Success', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Both Reproductive Success', 'Extinction Rate', 'Female Reproductive Success', 'Offspring Viability')
 # Obtain BF for all components
@@
 get.predictions.outcomes <- function(newdata){
-  `Body Condition`<-0; `Body Size`<-0; `Development Rate`<-0; `Early Fecundity`<-0; `Ejaculate Quality and Production`<-0; `Extinction Rate`<-0; `Fitness Senescence`<-0; Immunity<-0; Lifespan<-0; `Male Attractiveness`<-0; `Mating Duration`<-0; `Mating Frequency`<-0; `Mating Latency`<-0; `Mating Success`<-0; `Mutant Frequency`<-0; `Offspring Viability`<-0; `Pesticide Resistance`<-0; `Reproductive Success`<-0; Strength<-0
+  `Body Condition`<-0; `Body Size`<-0; `Development Rate`<-0; `Early Fecundity`<-0; `Ejaculate Quality and Production`<-0; `Extinction Rate`<-0; `Fitness Senescence`<-0; Immunity<-0; Lifespan<-0; `Male Attractiveness`<-0; `Male Reproductive Success`<-0; `Mating Duration`<-0; `Mating Frequency`<-0; `Mating Latency`<-0; `Mating Success`<-0; `Mutant Frequency`<-0; `Offspring Viability`<-0; `Pesticide Resistance`<-0; `Female Reproductive Success`<-0; `Both Reproductive Success`<-0; Strength<-0
   if(newdata[1] == 'Body Size') `Body Size`<-1
@@
   if(newdata[1] == 'Male Attractiveness')`Male Attractiveness`<-1
+  if(newdata[1] == 'Male Reproductive Success')`Male Reproductive Success`<-1
   if(newdata[1] == 'Mating Frequency')`Mating Frequency`<-1
@@
   if(newdata[1] == 'Offspring Viability')`Offspring Viability`<-1
-  if(newdata[1] == 'Reproductive Success')`Reproductive Success`<-1
-
-  predict(model.fitness.components.REML, newmods=c(`Body Condition`, `Body Size`, `Development Rate`, `Early Fecundity`, `Ejaculate Quality and Production`, `Extinction Rate`, `Fitness Senescence`, Immunity, Lifespan, `Male Attractiveness`, `Mating Duration`, `Mating Frequency`, `Mating Latency`, `Mating Success`, `Mutant Frequency`, `Offspring Viability`, `Pesticide Resistance`, `Reproductive Success`, Strength))
+  if(newdata[1] == 'Female Reproductive Success')`Female Reproductive Success`<-1
+  if(newdata[1] == 'Both Reproductive Success')`Both Reproductive Success`<-1
+
+  predict(model.fitness.components.REML, newmods=c(`Body Condition`, `Body Size`, `Development Rate`, `Early Fecundity`, `Ejaculate Quality and Production`, `Extinction Rate`, `Fitness Senescence`, Immunity, Lifespan, `Male Attractiveness`, `Male Reproductive Success`, `Mating Duration`, `Mating Frequency`, `Mating Latency`, `Mating Success`, `Mutant Frequency`, `Offspring Viability`, `Pesticide Resistance`, `Female Reproductive Success`, `Both Reproductive Success`, Strength))
 }
@@
 ```{r, warning = FALSE}
-outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
-names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
+#Excluding those with 3 or less effect sizes.
+
+outcome.list <- as.list(c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Male Reproductive Success', 'Mating Duration', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Ejaculate Quality and Production', 'Both Reproductive Success', 'Extinction Rate', 'Female Reproductive Success', 'Offspring Viability'))
+names(outcome.list) <- c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Male Reproductive Success', 'Mating Duration', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Ejaculate Quality and Production', 'Both Reproductive Success', 'Extinction Rate', 'Female Reproductive Success', 'Offspring Viability')
 outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
@@
 
+#Male Reproductive Success
+restricted.dataMRS <- full_dataset %>% filter(full_dataset$Outcome == "Male Reproductive Success")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataMRS$var.g)
+X = model.matrix(outcome.models[["Male Reproductive Success"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+MaleReproductiveSuccessI2 <- 100 * sum(outcome.models[["Male Reproductive Success"]]$sigma2) / (sum(outcome.models[["Male Reproductive Success"]]$sigma2) + (outcome.models[["Male Reproductive Success"]]$k-outcome.models[["Male Reproductive Success"]]$p)/sum(diag(P)))
+
 #Mating Frequency
@@
 
-#Reproductive Success
-restricted.dataRS <- full_dataset %>% filter(full_dataset$Outcome == "Reproductive Success")
+#Both Reproductive Success
+restricted.dataBRS <- full_dataset %>% filter(full_dataset$Outcome == "Both Reproductive Success")
 
 #Run estimate of heterogeneity
-W = diag(1/restricted.dataRS$var.g)
-X = model.matrix(outcome.models[["Reproductive Success"]])
+W = diag(1/restricted.dataBRS$var.g)
+X = model.matrix(outcome.models[["Both Reproductive Success"]])
 P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-ReproductiveSuccessI2 <- 100 * sum(outcome.models[["Reproductive Success"]]$sigma2) / (sum(outcome.models[["Reproductive Success"]]$sigma2) + (outcome.models[["Reproductive Success"]]$k-outcome.models[["Reproductive Success"]]$p)/sum(diag(P)))
-
-simple.frame$I2 <- c(NA, BodySizeI2, DevelopmentRateI2, EarlyFecundityI2, ImmunityI2, MaleAttractivenessI2, MatingDurationI2, NA, MutantFrequencyI2, FitnessSenescenceI2, LifespanI2, MatingFrequencyI2, MatingLatencyI2, MatingSuccessI2, NA, EjaculateQualityI2, ExtinctionRateI2, OffspringViabilityI2, ReproductiveSuccessI2)
+BothReproductiveSuccessI2 <- 100 * sum(outcome.models[["Both Reproductive Success"]]$sigma2) / (sum(outcome.models[["Both Reproductive Success"]]$sigma2) + (outcome.models[["Both Reproductive Success"]]$k-outcome.models[["Both Reproductive Success"]]$p)/sum(diag(P)))
+
+#Female Reproductive Success
+restricted.dataFRS <- full_dataset %>% filter(full_dataset$Outcome == "Female Reproductive Success")
+
+#Run estimate of heterogeneity
+W = diag(1/restricted.dataFRS$var.g)
+X = model.matrix(outcome.models[["Female Reproductive Success"]])
+P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+FemaleReproductiveSuccessI2 <- 100 * sum(outcome.models[["Female Reproductive Success"]]$sigma2) / (sum(outcome.models[["Female Reproductive Success"]]$sigma2) + (outcome.models[["Female Reproductive Success"]]$k-outcome.models[["Female Reproductive Success"]]$p)/sum(diag(P)))
+
+simple.frame$I2 <- c(BodySizeI2, DevelopmentRateI2, EarlyFecundityI2, ImmunityI2, MaleAttractivenessI2, MaleReproductiveSuccessI2, MatingDurationI2, MutantFrequencyI2, FitnessSenescenceI2, LifespanI2, MatingFrequencyI2, MatingLatencyI2, MatingSuccessI2, EjaculateQualityI2, BothReproductiveSuccessI2, ExtinctionRateI2, FemaleReproductiveSuccessI2, OffspringViabilityI2)
 
@@
 outcome.frame$I2 <- as.numeric(outcome.frame$I2)
-outcome.frame$Class <- c("Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Direct", "Direct", "Direct")
+outcome.frame$Class <- c("Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Direct", "Direct", "Direct", "Direct")
 
@@
 model.preliminary <- rma.mv(g, var.g, 
-                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + log(Generations) + Blinding, 
+                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + log(Generations) + Blinding + Enforced.Monogamy, 
                          random = list(~ 1 | Study.ID, 
@@
 if(!file.exists("data/brms.preliminary.rds")){
-  brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
+  brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding + Enforced.Monogamy #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                 + (1|Study.ID) #group level effects

### 2019-01-03 Response_to_Nature_Comms.Rmd
updated supp info

@@
 ---
-title: 'Sexual selection improves population fitness: a meta-analysis'
+title: 'Sexual selection improves population fitness: a systematic review and meta-analysis'
 output:
@@
 
-In the revision, we have now replaced our main analysis in light of this comment, and reassuringly we obtained qualitatively the same result.
-In the original, we culled the dataset to only include the "direct" and "indirect" measures of popualtion fitness (this decision was taken to maximise the use of the data).
-In the revision, we have eliminated the "indirect" measures, leaving n = **XX** "direct" effect sizes in our main analysis.
-To facilitate easy comparison, we present the new and old results below: one can see that nothing has changed (in terms of statistical significance).
-To avoid reader fatigue in our manuscript (since we already chop and change the dataset in many different ways), we have changed this analysis to include only the "direct" measures, i.e.
-the graph on the right, and the table below, rather than presenting both versions.
+In the manuscript, we culled the dataset to only include the "direct" and "indirect" measures of popualtion fitness (this decision was taken to maximise the use of the data).
+If we were to eliminate indirect measures, it would leave us with n = **XX** "direct" effect sizes in our main analysis.
+To facilitate easy comparison, we present the new and old results below: one can see that two things have changed (in terms of statistical significance).
+Firstly, for the "direct only" model the predicted effect size for males in stressful environments is now significantly negative (*Hedges' g* = -0.45; 95 % CIs = -0.70 to -0.19).
+However, because in the revised dataset we have reclassified male reproductive success as an ambiguous measure of fitness, there are only two effect sizes for males in stressful environments; making any conclusions drawn from this finding problematic.
+Secondly, the predicted effect size for females in benign environments in the "direct only model" are non-significantly positive, unlike the "direct and indirect" model, however, in both cases the positive effect of sexual selection on fitness is magnified for females in stressful environments.
+To avoid reader fatigue in our manuscript (since we already chop and change the dataset in many different ways), we have retained the analysis to include both the "indirect and direct" measures.
+The graph on the right, and the table below show the main results recovered from only "direct" measurements for reference.
+
+**Luke: Might need to argue use of both indirect and direct more. Basically the results **
 
@@
   scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
-  scale_x_continuous(limits = c(-0.75, 1.5), breaks = c(-1, -.5, 0, 0.5, 1, 1.5))+
+  scale_x_continuous(limits = c(-1.25, 1.25), breaks = c(-1, -.5, 0, 0.5, 1))+
 
@@
              nrow = 1, 
-             widths = c(3,4))
+             widths = c(3,3.5))
 ```
@@
 We find no effect of manipulation type on effect size, suggestion that both ways of removing sexual selection had a similar effect on population fitness traits.
-**See the revised Table SX.**
+**See the revised Table S10.**
 
@@
 
-After reading htose references, we agree that Hedges' *g* is imperfect, and so we checked the robustness of our meta-analysis using two alternative measures of effect size.
+After reading those references, we agree that Hedges' *g* is imperfect, and so we checked the robustness of our meta-analysis using two alternative measures of effect size.
 Firstly, we present the log response ratio (*lnRR*) as suggested by this reviewer.
@@
 
-We agree, and we have changed the title to "Sexual selection improves population fitness: a systematic review and meta-analysis".  **DO THIS**
+We agree, and we have changed the title to "Sexual selection improves population fitness: a systematic review and meta-analysis".
 
@@
 
-**This manuscript addresses the question of whether, on average, sexual selection has a net beneficial or detrimental effect on population fitness, using a meta-analysis of experimental evolution studies comparing the fitness of populations under different intensities of sexual selection.
+>*This manuscript addresses the question of whether, on average, sexual selection has a net beneficial or detrimental effect on population fitness, using a meta-analysis of experimental evolution studies comparing the fitness of populations under different intensities of sexual selection.
 The analyses consider the effects of sexual selection on both the mean and variance of population fitness, and test whether these effects differ for stressful vs.
-benign environments, or depend on the measure of population fitness.**
+benign environments, or depend on the measure of population fitness.*
 
-**These are issues of longstanding interest, and as there is now quite a wealth of experimental evolution studies addressing these questions a meta-analysis synthesising their findings is timely.**
+>*These are issues of longstanding interest, and as there is now quite a wealth of experimental evolution studies addressing these questions a meta-analysis synthesising their findings is timely.*
 
@@
 
+Yes, we now also stress that we consider sexual selection on males, as suggested (changes are made throughout the manuscript).
+
 >*Experiments manipulating the sex ratio to alter sexual selection might simultaneously decrease sexual selection on males while increasing sexual selection on females.
@@
 For the latter type, we considered the strength of sexual selection on males to be variable of interest, though it is confounded with the strength of sexual seleciton on females.
-To test if there was any difference in the effect sizes induced by these two types of manipulation, we now include "manipulation type" as a moderator variable: there was no effect (see above comment to Reviewer 1).
-**We now also stress that we consider sexual selection on males, as suggested.**
+To test if there was any difference in the effect sizes induced by these two types of manipulation, we now include 'manipulation type' (named "Enforced.Monogamy" in the Supplementary Material and R code) as a moderator variable: there was no effect in our preliminary model (**see above comment to Reviewer 1 and the revised Table S10**).
 
@@
 
+The results are odd, however to the best of our knowledge they are accurate.
+The REML model estimates the variance component ($\sigma^2$) of the "taxon" random effect as very low (3.38e-09), compared to the other random effects ("Study ID"" = 1.93e-01 and "fitness component" = 1.28e-01).
+A low value for $\sigma^2$ is the reason $I^2$ is estimated as zero.
+A potential reason for low heterogeneity is that there are only six taxon levels (campared to 53 studies and 13 fitness components).
+
 **Check this please Justin - I could not see what you changed in the R script**
+**Luke: I think the function was still in dev when i forked it and there was a bug that stopped in allowing me to get I2 for all three random effects (only last two), I changed the code so it recognised all three random effects.
+Not sure if the answer I provided makes sense**
 
@@
 
-**We now clarify this as suggested.**
+We now clarify this as suggested.
 
@@
 
-**We now clarify this as suggested.**
+We now clarify the confidence intervals on the funnel plot as suggested.
 
@@
 
-**Please check and answer this Justin**
+The revised manuscript no longer has this disparity between REML and Bayesian estimates.
+However we noticed that Bayesian estimates had slightly wider confidence intervals than REML models leading to differences in statistical significance (e.g.
+Table S6).
 

### 2019-01-03 Manuscripts/Manuscript_MetaAnalysis.Rmd
updated supp info

@@
 ---
-title: '\huge{Sexual selection improves population fitness: a meta-analysis}'
+title: '\huge{Sexual selection improves population fitness: a systematic review and meta-analysis}'
 author: 
@@
 Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis.
-We find that sexual selection tends to elevate the mean and reduce the variance for many fitness traits, especially in females, and for populations evolving under stressful conditions.
+We find that sexual selection **on males** tends to elevate the mean and reduce the variance for many fitness traits, especially in females, and for populations evolving under stressful conditions.
 We conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
@@
 Here, we synthesise the empirical literature on sexual selection and population fitness using formal meta-analysis.
-We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection, and then measured some fitness component, since these provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations.
+We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection **on males**, and then measured some fitness component, since these provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations.
 Our principle aims were to measure the average net effect of sexual selection on the population-level mean and variance for various fitness components, to test whether this effect varies between stressful and benign environments, and identify key moderators of the effect size of sexual selection treatment.
@@
 
-The grand mean for all effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.25, 95% CIs: 0.06 to 0.43, $p$ = 0.008; Bayesian $\beta$ = 0.25, 95% CIs: -0.02 to 0.52, $BF_{>0}$ = 32), indicating that sexual selection typically had a net positive effect on the majority of populations and fitness components so far studied.
+The grand mean for all effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.25, 95% CIs: 0.06 to 0.43, $p$ = 0.008; Bayesian $\beta$ = 0.25, 95% CIs: -0.02 to 0.52, $BF_{>0}$ = 32), indicating that sexual selection **on males** typically had a net positive effect on the majority of populations and fitness components so far studied.
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
@@
 We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect fitness (\hyperlink{page.18}{Table 1, 2}).
-Sexual selection significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
+Sexual selection **on males** significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
 Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
@@
 
-Our meta-analysis revealed that populations evolving under sexual selection often have higher values for multiple fitness traits, relative to populations where sexual selection was experimentally removed or weakened.
+Our meta-analysis revealed that populations evolving under sexual selection often have higher values for multiple fitness traits, relative to populations where sexual selection **on males** was experimentally removed or weakened.
 **Sexual selection had beneficial effects for traits that were ambiguously or indirectly related to fitness, but had smaller, variable effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced) and the proportion of viable offspring**.
@@
 
-The results of the meta-analysis support predictions that sexual selection can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
+The results of the meta-analysis support predictions that sexual selection **on males** can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
 Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles through selection on males [@RN94; @RN198; @RN95].
@@
 From each paper, we first attempted to extract the arithmetic means, standard deviations and sample sizes of each of the different treatment groups, which facilitate calculation of effect size (see below).
-Typically, there were two or three treatments, which varied in the strength of sexual selection.
+Typically, there were two or three treatments, which varied in the strength of sexual selection **on males through manipulations to the adult sex ratio, in these cases we considered treatments with the greater male to female ratio to be the high sexual selection treatment group**.
 For some papers, summary statistics were not written down, but were presented in a figure such as a bar chart: in these cases, we extracted the data using *WebPlotDigitizer* v.3.12 [@RN195].
@@
 
-For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177].**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (FIG SXX).
+For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$ .**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S6).
 As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 352 of 459 comparisons.
@@
 For (**b**) and (**c**) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).
-Grey envelopes in (**b**) and (**c**) represent the 95 % CI of the linear regression.\label{publication_bias}](Figures/publicationbias.pdf)
+For (**a**), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99 % CIs for the dataset.
+The Grey envelopes in (**b**) and (**c**) represent the 95 % CI of the linear regression.\label{publication_bias}](Figures/publicationbias.pdf)
 

### 2019-01-03 meta_analysis_sexual_selection_pop_fitness.Rmd
updated supp info

@@
 ---
-title: 'Sexual selection improves population fitness: a meta-analysis'
+title: 'Sexual selection improves population fitness: a systematic review and meta-analysis'
 author: "Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
@@
                           cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
-                          control = list(adapt_delta = 0.9999, max_treedepth = 15),
+                          control = list(adapt_delta = 0.999, max_treedepth = 15),
                           data = full_dataset %>% mutate(SE = sqrt(var.g)))
@@
 ```{r, message=FALSE, error = FALSE, warning=FALSE}
+strict_dataset <- full_dataset %>%
+  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>%
+  mutate(Sex = relevel(Sex, ref = "M"),
+         Environment = relevel(factor(Environment), ref = "Unstressed"),
+         Taxon = relevel(factor(Taxon), ref = "Beetle"))
+
 # strict_dataset <- full_dataset %>% 
-#   filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated")  %>% 
+#   filter(Outcome.Class == "Direct" & Environment != "Not Stated")  %>% 
 #   mutate(Sex = relevel(Sex, ref = "M"),
@@
 
-strict_dataset <- full_dataset %>% 
-  filter(Outcome.Class == "Direct" & Environment != "Not Stated")  %>% 
-  mutate(Sex = relevel(Sex, ref = "M"),
-         Environment = relevel(factor(Environment), ref = "Unstressed"),
-         Taxon = relevel(factor(Taxon), ref = "Beetle"))
-
 model.complete <- rma.mv(g, V = var.g, 
-                         mods = ~ 1 + Sex * Environment + Taxon + Enforced.Monogamy, 
+                         mods = ~ 1 + Sex * Environment + Taxon, 
                          random = list(~ 1 | Study.ID, 
@@
 get.predictions.complete <- function(newdata){
-  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0; interaction3<-0
+  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0;
   if(newdata[1] == "B") B<-1 
@@
   if(newdata[2] == "Stressed") Stressed<-1
-  if(newdata[3] == "Cricket") Cricket<-1
+  if(newdata[2] == "Cricket") Cricket<-1
   if(newdata[3] == "Fly") Fly<-1
@@
 
-  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, 1, interaction1, interaction2))
+  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, interaction1, interaction2))
 }
@@
                         cores = 4, chains = 4, iter = 4000, 
-                        control = list(adapt_delta = 0.9999, max_treedepth = 15),
+                        control = list(adapt_delta = 0.999, max_treedepth = 15),
                         data = strict_dataset %>% mutate(SE = sqrt(var.g)))
@@
                         cores = 4, chains = 4, iter = 4000, 
-                        control = list(adapt_delta = 0.9999, max_treedepth = 15),
+                        control = list(adapt_delta = 0.999, max_treedepth = 15),
                         data = lnRR.data %>% mutate(SE = sqrt(lnRR_var)) %>% 

### 2019-01-03 I2_function.R

@@ -56,7 +56,7 @@ I2 <- function(model, v, ME = FALSE, sims = 1500, phylo = FALSE){
     colnames(sigma2) <- model$s.names
     sigmaN <- model$s.nlevels
     
-    if("Study.ID" %in% colnames(sigma2) == FALSE){
+    if(model[["s.names"]][1] %in% colnames(sigma2) == FALSE){
       stop("The metafor object does not contain a residual variance estimate. Please include an observation-level random effect (~1|obs) when fitting model")
     }
     

### 2019-01-06 Response_to_Nature_Comms.Rmd
Fixed figures etc

@@
 
-Effect on the results...
+As one can see, this reclassification had minimal impact on the main findings of the study.
+And the results that the predicted effect size for female reproductive success is significantly positive, while non-significantly positive also align with our main findings that sexual selection on males leads to incrtease in female fitness components.
 
@@
 left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component") %>% 
-  filter(`Fitness Component` == "Male Attractiveness") %>% pander(split.table = Inf, digits = 2)
+  filter(`Fitness Component` == "Male Attractiveness") %>% pander(split.table = Inf, digits = 2, caption = "Model predictions for Male Attractiveness")
 ```
@@
 
+To clarify the effects of sexual selection on ambiguous, indirect and direct fitness-related traits we have changed Figure 1 to a simpler style forest plot, with the forest plot now only found within the Supplementary Material (Fig.
+S1).
+
 >*Thirdly, type of trait measured explained 35% variance, but the authors do not explore this any further.
@@
 In the manuscript, we culled the dataset to only include the "direct" and "indirect" measures of popualtion fitness (this decision was taken to maximise the use of the data).
-If we were to eliminate indirect measures, it would leave us with n = **XX** "direct" effect sizes in our main analysis.
+If we were to eliminate indirect measures, it would leave us with approximately half the number of "direct" effect sizes in our main analysis (n = 159 vs n = 289).
 To facilitate easy comparison, we present the new and old results below: one can see that two things have changed (in terms of statistical significance).
@@
 Secondly, the predicted effect size for females in benign environments in the "direct only model" are non-significantly positive, unlike the "direct and indirect" model, however, in both cases the positive effect of sexual selection on fitness is magnified for females in stressful environments.
-To avoid reader fatigue in our manuscript (since we already chop and change the dataset in many different ways), we have retained the analysis to include both the "indirect and direct" measures.
+To avoid reader fatigue and low-powered predictions in our manuscript (we already chop and change the dataset in many different ways), we have retained the analysis to include both the "indirect and direct" measures.
 The graph on the right, and the table below show the main results recovered from only "direct" measurements for reference.
 
-**Luke: Might need to argue use of both indirect and direct more. Basically the results **
+**Luke: Might need to argue use of both indirect and direct more.**
 
@@
 ```{r, warning=FALSE}
-predictions.direct %>% pander(caption = "Model using only direct measures of fitness")
+predictions.direct %>% pander(caption = "Model predictions using only direct measures of fitness")
 ```
@@
 
-We agree that this section could have been much clearer, and have made some changes in light of this comment to clarify what we meant.
+**Luke: Need to highlight in discussion where we put this in**
+
+We agree that this section could have been much clearer, **and have made some changes in light of this comment to clarify what we meant**.
 We believe that experiments that manipuate sexual selection on males will alter female fitness traits, even in species where females experience no sexual selection, because of mechanisms such as intra- and inter-locus sexual conflict.
@@
 We find no effect of manipulation type on effect size, suggestion that both ways of removing sexual selection had a similar effect on population fitness traits.
-**See the revised Table S10.**
+See the revised Table S10.
 
@@
 For relevant results, please see the section of the results that reads "Other moderator variables that we examined had minimal impacts on effect size (Figure S2, Table S10).
-Specifically, effect size did not depend on whether or not the study was conducted blind (Figure S9), nor on the number of generations for which the experimental evolution study was run (Figure S10, S11)." In the methods, we wrote "Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), blinding of researchers to treatments and number of generations a treatment group underwent experimentally evolution."
+Specifically, effect size did not depend on whether or not the study was conducted blind (Figure S6), nor on the number of generations for which the experimental evolution study was run (Figure S7, S8)." In the methods, we wrote "Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), blinding of researchers to treatments and number of generations a treatment group underwent experimentally evolution."
 
@@
 We have changed the numbering of the supplementary figures, so that e.g.
-Figure 2 in the HTML supplement is correctly labelled as Figure 2 and not as Fig.
+Figure 1 in the HTML supplement is correctly labelled as Figure 1 and not as Fig.
 S1, to make it clear that it is the same figure.
-**A JOB FOR JUSTIN HERE**
 
@@
 Although we think that *lnVR* is not preferable due to this positive relationship, we ran our meta-analyses using *lnVR* in the interests of completeness.
-**We present this new result in the supplementary material and briefly discuss it in the manuscript**.
-To summarise, we found very similar patterns, although the statistical significance of one of the results disappeared; see the following figure:
+We present this new result in the supplementary material and briefly discuss it in the manuscript.
+To summarise, we found very similar patterns, although the statistical significance some of the results have changed; see the following figure:
 
@@
 
-Many thanks for this feedback -- we have **incorporated all these suggestions in the Methods section**.
+Many thanks for this feedback -- we have incorporated all these suggestions in the Methods section.
 
@@
 
-Thanks -- we now **remind the reader that funnel plot asymmetry is not decisive evidence** for publication bias, because it can also result from unexplained heterogeneity in the original effect sizes.
+Thanks -- we now remind the reader that funnel plot asymmetry is not decisive evidence for publication bias, because it can also result from unexplained heterogeneity in the original effect sizes.
 We have elected not to implement trim-and-fill since the method seems to have fallen into disfavour among many readers, and because we are unsure how to correctly implement it using the REML- and Bayesian methods we used.

### 2019-01-06 Manuscripts/Manuscript_MetaAnalysis.Rmd
Fixed figures etc

@@
 Most effect sizes in our dataset came from studies that manipulated sexual selection by completely removing it in one treatment via enforced random monogamy ($n$ = 241); other effect sizes ($n$ = 218) derived from alternative manipulations, such as changing the adult sex ratio.
-In total, we obtained effect sizes for 20 different fitness traits, with reproductive success ($n$ = 156) and offspring viability ($n$ = 56) being the most commonly-measured traits.
-We classified **216 effect sizes as direct measures of fitness, 141 as indirect, and the remaining 102 effect sizes as ambiguous** (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
-Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, reproductive success, offspring viability, and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, and early fecundity).
+In total, we obtained effect sizes for 22 different fitness traits, with female reproductive success ($n$ = 102) and offspring viability ($n$ = 56) being the most commonly-measured traits.
+We classified **171 effect sizes as direct measures of fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous** (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
+Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, female reproductive success, offspring viability, and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, male reproductive success, and early fecundity).
 \href{https://justincally.github.io/SexualSelection/#tables_of_sample_sizes}{Tables S4-S5} give a detailed description of our dataset.\phantomsection
@@
 
-The grand mean for all effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.25, 95% CIs: 0.06 to 0.43, $p$ = 0.008; Bayesian $\beta$ = 0.25, 95% CIs: -0.02 to 0.52, $BF_{>0}$ = 32), indicating that sexual selection **on males** typically had a net positive effect on the majority of populations and fitness components so far studied.
+The grand mean for all effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.24, 95% CIs: 0.055 to 0.43, $p$ = 0.011; Bayesian $\beta$ = 0.25, 95% CIs: -0.0074 to 0.51, $BF_{>0}$ = 35), indicating that sexual selection **on males** typically had a net positive effect on the majority of populations and fitness components so far studied.
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
 Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6}).
-**Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.23, 95% CIs: 0.12 to 0.35; Bayesian $\beta$ = 0.23, 95% CIs: 0.03 to 0.41, $BF_{>0}$ = 55, $n$ = 102) and an indirect relationship to fitness (REML $\beta$ = 0.25, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.04 to 0.42, $BF_{>0}$ = 68, $n$ = 141).
-Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.02 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.07 to 0.3, $BF_{>0}$ = 14, $n$ = 216).
+**Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.21, 95% CIs: 0.058 to 0.093; Bayesian $\beta$ = 0.20, 95% CIs: -0.0016 to	0.39, $BF_{>0}$ = 38, $n$ = 144) and an indirect relationship to fitness (REML $\beta$ = 0.24, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.033 to 0.43, $BF_{>0}$ = 59, $n$ = 141).
+Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174).
 An extensive forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed in model prediction and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
-Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.16, $BF_{>0}$ = 0.0021; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.8 to -0.61, $BF_{>0}$ = 0.00013, $n$ = 1).
+Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).
 \phantomsection
@@
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
-**When the lnRR (log Response Ratio) effect size was used to conduct the meta-analysis investigating the impact of sex and environment, the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S4 and Table S16).**
+**When the lnRR (log Response Ratio) effect size was used to conduct the meta-analysis investigating the impact of sex and environment, the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S3 and Table S16).**
 
 Other moderator variables that we examined had minimal impacts on effect size (\href{https://justincally.github.io/SexualSelection/#meta-analyses_including_many_moderator_variables}{Figure S2, Table S10}).
-Specifically, effect size did not depend on whether or not the study was conducted blind (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S9}), nor on the number of generations for which the experimental evolution study was run (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S10, S11}).
+Specifically, effect size did not depend on whether or not the study was conducted blind (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S6}), nor on the number of generations for which the experimental evolution study was run (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S7, S8}).
 
-The effect size estimates we recovered were highly heterogeneous ($I^2$ = 94.7%, 95% CIs: 92.4-96.4%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016].
-Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 57.4%, 95% CIs: 38.1-76.5%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 37.4%, 95% CIs: 16.9-57.6%).
-The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model **suggested a probable non-zero effect** ($\sigma^2$ = 0.13 [0-0.46]).
+The effect size estimates we recovered were highly heterogeneous ($I^2$ = 95.4%, 95% CIs: 93.5-96.8%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016].
+Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 57.9%, 95% CIs: 38.8-76.7%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 37.2%, 95% CIs: 18.2-57.2%).
+The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model **suggested a probable non-zero effect** ($\sigma^2$ = 0.15 [0-0.54]).
 Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
@@
 By applying meta-analysis to log coefficient of variation ratios [*lnCVR*; @RN177], we found evidence that sexual selection reduces phenotypic variation under certain conditions (\autoref{env_sex}b).
-Specifically, phenotypic variance was significantly reduced by sexual selection for fitness components measured in females under stressful conditions (*lnCVR* = -0.75, 95% CIs: -1.13 to -0.36).
+Specifically, phenotypic variance was significantly reduced by sexual selection for fitness components measured in females under stressful conditions (*lnCVR* = -0.78, 95% CIs: -1.23 to -0.34, $n$ = 27).
 By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (\autoref{env_sex}b; \href{https://justincally.github.io/SexualSelection/#obtaining_lncvr_and_meta-analysis_models}{Tables S13-S16}).
-However, similar to the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.77, 95% CIs: -1.16 to -0.38; \autoref{env_sex}b).
+However, similar to the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.76, 95% CIs: -1.22 to -0.31; \autoref{env_sex}b).
+**A meta-analysis using the log variability ratio (lnVR), which does not account for the mean-variance relationship present in the dataset (Figure S4), suggested sexual selection reduces variance for mixed-sex samples in stressful conditions, but not females, results of this meta-analysis can be found in the Supplementary Material (Figure S5 and Table S21)**.
 
-As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 99.2%, 95% CIs: 98.8-99.6%).
-Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 36.1 %, 95% CIs: 19.3 % to 59 %), fitness components ($I^2_{fitness\:components}$ = 50.4%, 95% CIs: 24.2-72.1%) and taxon ($I^2_{taxon}$ = 12.7, 95% CIs: 2.14-31%).
+As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 99.3%, 95% CIs: 98.7-99.6%).
+Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 16 %, 95% CIs: 7.21 % to 30 %), fitness components ($I^2_{fitness\:components}$ = 51.6%, 95% CIs: 22.4 to 77.6%) and taxon ($I^2_{taxon}$ = 31.7, 95% CIs: 6.97 to 62.3%).
 \phantomsection
@@
 Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection.
+**However, funnel plot asymmetry can arise due to between-study heterogeneity (which high $I^2$ imply) and are not decisive tests of publication bias [@RN215]**.
 There was no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.23) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.2, $p$ = 0.24); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
@@
 We categorised the fitness outcomes into three categories: ambiguous, indirect and direct (detailed in \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
-Briefly, ambiguous measures of fitness were those that are reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration and early fecundity).
+Briefly, ambiguous measures of fitness were those that are reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, early fecundity and male reproductive success).
 Indirect fitness components were those that are often used as a proxy of fitness but do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production).
-Finally, direct measures of fitness (reproductive success, offspring viability and extinction rate) are those that measure fitness through components of reproduction or long-term viability.
+Finally, direct measures of fitness (female/mixed sex reproductive success, offspring viability and extinction rate) are those that measure fitness through components of reproduction or long-term viability.
 The ESM describes why specific papers recovered in the literature search were included or excluded (\href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S2}).
@@
 
-**Additionally, using studies that presented means, standard deviations and sample sizes (n = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) CITE.
-The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that
+**Additionally, using studies that presented means, standard deviations and sample sizes (n = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) [@Hedges_1999; @Osenberg_1997] The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that
 
-For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$ .**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S6).
+For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$ .**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4).
 As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 352 of 459 comparisons.
@@
 Firstly, we obtained a weighted mean effect size (Hedges’ *g*) for the entire dataset, using both Bayesian and restricted maximum likelihood (REML) approaches for completeness.
-The weighted mean was obtained by fitting a model with no moderator variables (*i.e.* fixed effects), but fitness component (*e.g.*, body size, female fecundity), study ID, and taxon as random/group-level effects.
+The weighted mean was obtained by fitting a model with no moderator variables (*i.e.* fixed effects), but fitness component (*e.g.*, body size, female reproductive success), study ID, and taxon as random/group-level effects.
 That is, we separately model correlations between different effect sizes sourced from the same study, taxon, or pertaining to the same fitness component, and account for these interdependencies when estimating the overall effect.
@@
 **Secondly, we fixed the relationship to fitness class (Ambiguous, Indirect or Direct) as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the three fitness-relationship classes, using the relevant ``predict`` functions for each of the ``R`` packages used (see below).
-This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and reproductive success); predictions for this model on the 20 fitness components were derived as above.
+This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and female reproductive success); predictions for this model on the 22 fitness components were derived as above.
 Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (n = 16); subset for each fitness trait with more than three effect sizes.

### 2019-01-06 meta_analysis_sexual_selection_pop_fitness.Rmd
Fixed figures etc

@@
                           cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
-                          control = list(adapt_delta = 0.999, max_treedepth = 15),
+                          control = list(adapt_delta = 0.9999, max_treedepth = 15),
                           data = full_dataset %>% mutate(SE = sqrt(var.g)))
@@
 av.se.g.class <- full_dataset %>% group_by(Outcome.Class) %>% summarise(mean = mean(sqrt(var.g)))
-brms.newdata.class$SE <- av.se.g.class$mean
+brms.newdata.class <- left_join(av.se.g.class %>% rename(SE = mean), brms.newdata.class)
 
@@
 
-```{r, include = FALSE}
+```{r, fig.width = 8, fig.height = 4}
 pd <- position_dodge(0.3)
@@
   coord_flip()
-```
+
+forest.plot.class
+```
+
+**Figure 1** The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness.
+Overall, effect sizes were more often positive than negative.
+Predicted average values are presented as a diamond for each fitness-relationship category.
+The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line.
+Predictions from both Bayesian and REML models can be found in Table S7.
 
@@
 
-#knitr::include_graphics(path = "figures/ForestPlot_size_reduced.png") 
+knitr::include_graphics(path = "figures/ForestPlot_size_reduced.png") 
 ```
@@
 
-**Table S8** Summary of model predictions for 20 fitness components.
-In Figure S1 these values are presented as a text overlay on Figure 1 (Forest Plot) using the Bayesian values.
+**Table S8** Summary of model predictions for 22 fitness components.
+In Figure S1 these values are presented as a text overlay using the Bayesian values.
 Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0.
@@
   `Body Condition`<-0; `Body Size`<-0; `Development Rate`<-0; `Early Fecundity`<-0; `Ejaculate Quality and Production`<-0; `Extinction Rate`<-0; `Fitness Senescence`<-0; Immunity<-0; Lifespan<-0; `Male Attractiveness`<-0; `Male Reproductive Success`<-0; `Mating Duration`<-0; `Mating Frequency`<-0; `Mating Latency`<-0; `Mating Success`<-0; `Mutant Frequency`<-0; `Offspring Viability`<-0; `Pesticide Resistance`<-0; `Female Reproductive Success`<-0; `Both Reproductive Success`<-0; Strength<-0
+
+  if(newdata[1] == 'Body Condition')`Body Condition`<-1
   if(newdata[1] == 'Body Size') `Body Size`<-1
+  if(newdata[1] == 'Both Reproductive Success') `Both Reproductive Success`<-1
   if(newdata[1] == 'Development Rate') `Development Rate`<-1
   if(newdata[1] == 'Early Fecundity') `Early Fecundity`<-1
+  if(newdata[1] == 'Ejaculate Quality and Production')`Ejaculate Quality and Production`<-1
+  if(newdata[1] == 'Extinction Rate')`Extinction Rate`<-1
+  if(newdata[1] == 'Female Reproductive Success')`Female Reproductive Success`<-1
+  if(newdata[1] == 'Fitness Senescence')`Fitness Senescence`<-1
   if(newdata[1] == 'Immunity')Immunity<-1
-  if(newdata[1] == 'Mating Duration')`Mating Duration`<-1
-  if(newdata[1] == 'Pesticide Resistance')`Pesticide Resistance`<-1
-  if(newdata[1] == 'Mutant Frequency')`Mutant Frequency`<-1
-  if(newdata[1] == 'Body Condition')`Body Condition`<-1
-  if(newdata[1] == 'Fitness Senescence')`Fitness Senescence`<-1
   if(newdata[1] == 'Lifespan')Lifespan<-1
@@
   if(newdata[1] == 'Male Reproductive Success')`Male Reproductive Success`<-1
+  if(newdata[1] == 'Mating Duration')`Mating Duration`<-1
   if(newdata[1] == 'Mating Frequency')`Mating Frequency`<-1
@@
   if(newdata[1] == 'Mating Success')`Mating Success`<-1
+  if(newdata[1] == 'Mutant Frequency')`Mutant Frequency`<-1
+  if(newdata[1] == 'Offspring Viability')`Offspring Viability`<-1
+  if(newdata[1] == 'Pesticide Resistance')`Pesticide Resistance`<-1
   if(newdata[1] == 'Strength')Strength<-1
-  if(newdata[1] == 'Ejaculate Quality and Production')`Ejaculate Quality and Production`<-1
-  if(newdata[1] == 'Extinction Rate')`Extinction Rate`<-1
-  if(newdata[1] == 'Offspring Viability')`Offspring Viability`<-1
-  if(newdata[1] == 'Female Reproductive Success')`Female Reproductive Success`<-1
-  if(newdata[1] == 'Both Reproductive Success')`Both Reproductive Success`<-1
-
-  predict(model.fitness.components.REML, newmods=c(`Body Condition`, `Body Size`, `Development Rate`, `Early Fecundity`, `Ejaculate Quality and Production`, `Extinction Rate`, `Fitness Senescence`, Immunity, Lifespan, `Male Attractiveness`, `Male Reproductive Success`, `Mating Duration`, `Mating Frequency`, `Mating Latency`, `Mating Success`, `Mutant Frequency`, `Offspring Viability`, `Pesticide Resistance`, `Female Reproductive Success`, `Both Reproductive Success`, Strength))
+
+  predict(model.fitness.components.REML, newmods=c(`Body Condition`,`Body Size`,`Both Reproductive Success`,`Development Rate`,`Early Fecundity`,`Ejaculate Quality and Production`,`Extinction Rate`,`Female Reproductive Success`,`Fitness Senescence`,`Immunity`,`Lifespan`,`Male Attractiveness`,`Male Reproductive Success`,`Mating Duration`,`Mating Frequency`,`Mating Latency`,`Mating Success`,`Mutant Frequency`,`Offspring Viability`,`Pesticide Resistance`,`Strength`))
 }
+
+outcome.list.model.levels <- c('Behavioural Plasticity' ,'Body Condition','Body Size','Both Reproductive Success','Development Rate','Early Fecundity','Ejaculate Quality and Production','Extinction Rate','Female Reproductive Success','Fitness Senescence','Immunity','Lifespan','Male Attractiveness','Male Reproductive Success','Mating Duration','Mating Frequency','Mating Latency','Mating Success','Mutant Frequency','Offspring Viability','Pesticide Resistance','Strength')
+
 # Get the predictions for each combination of moderators
-predictions.outcomes <- as.data.frame(expand.grid(Outcome = outcome.list.factor))
+predictions.outcomes <- as.data.frame(expand.grid(Outcome = outcome.list.model.levels))
 predictions.outcomes <- cbind(predictions.outcomes, do.call("rbind", apply(predictions.outcomes, 1, get.predictions.outcomes))) %>%
@@
 ```
+
 <br></br>
-**Figure S3:** Sexual selection generally increases population fitness, especially for females under stressful conditions.
+**Figure 2a:** Sexual selection generally increases population fitness, especially for females under stressful conditions.
 The benefits of sexual selection on fitness for females under stressful conditions are small-medium according to Cohen's interperetation of effect sizes.
@@
 
-**Figure S4:** Using an alternative effect size (lnRR) sexual selection also increases population fitness.
+**Figure S3:** Using an alternative effect size (lnRR) sexual selection also increases population fitness.
 Circle size is proportional to sample size (shown below).
@@
 variance.model <- rma.mv(lnCVr, V = var.lnCVr, mods = ~ 1 + Sex*Environment, 
-                          random = list(~ 1 | Taxon,
-                                        ~ 1 | Study.ID,
+                          random = list(~ 1 | Study.ID,
+                                        ~ 1 | Taxon,
                                         ~ 1 | Outcome), 
@@
 <br></br>
-**Figure S5:** Phenotypic variation changes under sexual selection in stressful environments.
+**Figure 2b:** Phenotypic variation changes under sexual selection in stressful environments.
 For females under stressful conditions phenotypic variation decreases (narrows).
@@
 
-**Figure S6** The use of lnCVR (as opposed to lnVR) is justified in this meta-analysis due to the strong mean-variance relationship.
+**Figure S4** The use of lnCVR (as opposed to lnVR) is justified in this meta-analysis due to the strong mean-variance relationship.
 In this case the standard deviation from the treatment group is compared to the means of the treatment group on a log-scale.
@@
 
-**Figure S7:** The effects of sexual selection on the log-variance ratio (lnVR).
+**Figure S5:** The effects of sexual selection on the log-variance ratio (lnVR).
 Without accounting for the mean variance relationship (lnCVR) sexual selection has different effects on the variance measure.
@@
 <br></br>
-**Figure S8:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001).
+**Figure 3a:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001).
 The asymmetry appears to come from a spread of positive effect sizes outside the funnel and of varying degrees of precision.
@@
 <br></br>
-**Figure S9:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
+**Figure 3a:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
 
@@
 <br></br>
-**Figure S10:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
+**Figure 3b:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
 Point size is proportional to the precision of the effect size.
@@
 <br></br>
-**Figure S11:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
+**Figure S6:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
 However, this should not be viewed as evidence against the validity of blinding as a research method.
@@
 <br></br>
-**Figure S12:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
+**Figure S7:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
 
@@
 <br></br>
-**Figure S13:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
+**Figure S8:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
 

### 2019-01-16 Response_to_Nature_Comms.Rmd
Changes after Devi comments

@@
 
-Many thanks for your time, and for the very helpful comments on our manuscript.
-We have made many changes in light of the three reviewers' detailed feedback, and we feel that the manuscript has been greatly improved.
-Please see the letter below for our detailed responses to each of the reviewers' points.
+We appreciate the insightful comments provided by the Associate Editor and reviewers.
+We have made the suggested changes and clarifications, detailed below.
 In addition to the revised manuscript and revised supplementary material, we attach a copy of the revised manuscript in which the significant changes and additions have been highlighted.
@@
 
-We completely agree that male attractiveness does not affect population fitness directly, and it is important to separate this trait from the "true" measures of population fitness in the meta-analysis.
-We do this more carefully in the revised meta-analysis.
-Specifically, in the original study, we classified male attractiveness as having an "indirect" relationship with population fitness (this is also how we classified traits such as body condition and life span; see Table S1 for a full breakdown).
-However on reflection, we think that attractiveness is only tenuously linked to population fitness, and so we have re-classified its relationship with population fitness as "ambiguous", along with traits like "Immunity" and "Development rate".
-Our main analysis excludes all of the ambiguous traits, and so our main results are now not derived from any effect sizes relating to male attractiveness.
-The exclusion of the n = 6 attractiveness effect sizes did not qualitatively change the results.
+We appreciate the reviewer's point that distinguishing between traits that are direct targets of sexual selection, versus those that respond more indirectly, could be revealing.
+For this reason, we present separate meta-analytical measurements for the effects of sexual selection on each of the various fitness components in the supplementary material.
+This enables the reader to gauge the effect of sexual selection each of the fitness components, e.g.
+to test whether direct targets of sexual selection (such as attractiveness) respond more strongly to sexual selection than traits such as immunity or longevity with a more indirect link to reproduction.
 
-Additionally, we have split the trait "Reproductive success" into "Female Reproductive Success", "Male Reproductive Success" and "Both Reproductive Success", the latter from studies where offspring number was measured from a given male-female pair interaction.
-We have made this reclassification in recognition of the facts that these two fitness components are maximised very differently, and are likely to have differentially related to population fitness.
-Specifically, we maintain "Female Reproductive Success" and "Both Reproductive Success" as direct measures of fitness but class "Male Reproductive Success" as an ambiguous measure of fitness.
+However, because the subject of our study is population fitness, we classified fitness components according to their relationship to population fitness, rather than their relationship with sexual selection.
+We took this decision because the relationship between sexual selection and population fitness is contentious, while there is no controversy over how sexual selection should affect traits like attractiveness (almost by definition, individuals born under sexual selection should be more attractive whenever attractiveness is hereditary).
 
-As one can see, this reclassification had minimal impact on the main findings of the study.
-And the results that the predicted effect size for female reproductive success is significantly positive, while non-significantly positive also align with our main findings that sexual selection on males leads to incrtease in female fitness components.
+In the revision, we have slightly altered which traits were classified as having a "direct", "indirect", or "ambiguous" relationship with population fitness, in light of the reviewer's feedback (see Table S1 for a breakdown of how all the traits were classified).
+Because we think that attractiveness is only tenuously linked to population fitness, and we have re-classified its relationship with population fitness as "ambiguous" (as opposed to "indirect" in the original manuscript).
+Additionally, we have split the trait "Reproductive success" by sex, in light of the fact that male and female fitness are maximised in differenet ways and are likely to have differentially related to population fitness.
+The revised manuscript and its main figures show that this reclassification had little impact on our main conclusions.
 
@@
 
-We agree that alone, these 6 studies do not provide strong evidence the mean is positive, although we note that some of the precisely measured effect sizes, and one of the imprecise ones, are positive, so this borderline significant result is not too anomalous.
+We agree that alone, these 6 effect sizes do not provide strong evidence that the true mean effect size is positive.
+But given that all but two of the effect sizes are positive, and some of them are very precisely measured, this only-just-significant result does not seem incorrect.
 
-Secondly, the effect size predictions were made using a single model that incorporated hundreds of other effect sizes, which allows the model is allowed to 'share information' between the different fitness measures.
-For example, if the overall mean effect size is positive, then smaller subsets of the dataset (like the attractiveness subset, with n = 6 studies) will tend to be made slightly more positive.
-That is, in the absence of precise information about the true average effect size for studies of attractiveness, the model uses some information provided by the global average.
+We thought about the reviewer's comment regarding random slopes, and it's not clear what revised model he is proposing. The current model has the following attributes:
 
-To clarify the effects of sexual selection on ambiguous, indirect and direct fitness-related traits we have changed Figure 1 to a simpler style forest plot, with the forest plot now only found within the Supplementary Material (Fig.
+- *Effect size* (i.e. the effect of sexual selection treatment on some fitness component) as the response variable, weighted by the associated standard error
+- The *type of fitness trait* (e.g. fecundity, lifespan, attractiveness) as a fixed factor or 'moderator vairable'
+- The *Study ID* as a random intercept (to model the similarity among effect sizes derived from the same study)
+- The *Taxon* as a random intercept (to model the similarity among effect sizes pertaining to the same taxon)
+
+So, is the reviewer proposing to add the fixed factor *type of fitness trait* as a random slope?
+If we understand correctly, this would allow each different fitness trait to differ in the amount of variance explained by study or taxon.
+We suspect that such a model would be overly-complex given the structure and size of our dataset, and it is unlikely to provide a statistically significantly better fit than the more parsimonious model that we currently use.
+Rather few studies measured multiple traits, and there are several taxa in which only one or two trait types have been measured, so there would be many components of the model that could not be estimated.
+
+Alternatively, it is possible that the reviewer meant for us to build a model that allows the response to sexual selection treatment to differ among the fitness traits.
+In pseudocode, this would look something like `Trait_value ~ Sexual_selection_treatment * Type_of_trait`.
+However, this would represent a misunderstanding of meta-analysis: we do not analyse the raw trait values from the original studies, but rather collect their effect sizes and combine them to estimate the average effect size for each of the different fitness traits.
+Our present analysis already allows for the possibility that the response to sexual selection differs between the different types of fitness trait.
+Apologies in advance if we have missed the point you were making, and thank you for this thought-provoking feedback.
+
+In light of this comment, we have changed our main figure for greater clarity and simplicity (we now group the traits by their relationship to population fitness, as opposed to the numerous individual types of types).
+Specifically we have changed Figure 1 to a simpler style of forest plot, with the big forest plot that was formerly Figure 1 now moved to the Supplementary Material (Fig.
 S1).

### 2019-01-16 Response_to_Nature_Comms.Rmd
edits to letter after Devi

@@
 We agree that alone, these 6 effect sizes do not provide strong evidence that the true mean effect size is positive.
-But given that all but two of the effect sizes are positive, and some of them are very precisely measured, this only-just-significant result does not seem incorrect.
+But given that 4/6 of the effect sizes are positive, and these were all either precisely measured or quite large, the model's conclusion that there is very weak evidence for a positive effect seems correct.
 
-We thought about the reviewer's comment regarding random slopes, and it's not clear what revised model he is proposing. The current model has the following attributes:
+Additionally, regarding the comment about random slopes, we were not sure what revised model the reviewer is proposing.
+To clarify things, we first note that the current model has the following attributes:
 
@@
 
-So, is the reviewer proposing to add the fixed factor *type of fitness trait* as a random slope?
-If we understand correctly, this would allow each different fitness trait to differ in the amount of variance explained by study or taxon.
-We suspect that such a model would be overly-complex given the structure and size of our dataset, and it is unlikely to provide a statistically significantly better fit than the more parsimonious model that we currently use.
-Rather few studies measured multiple traits, and there are several taxa in which only one or two trait types have been measured, so there would be many components of the model that could not be estimated.
+Given this, we suppose that the reviewer was proposing to add add the fixed factor *type of fitness trait* as a random slope to one or both of the two random intercept terms.
+This would allow each fitness trait to show a different amount of inter-study and inter-taxon variation.
+We suspect that such a model would be overly-complex given tour dataset, and it is unlikely to provide a statistically significantly better fit than the more parsimonious model that we currently use.
+Rather few studies in our dataset measured multiple traits, and there are several taxa in which only one or two trait types have been measured, meaning that the model would not be able to accurately measure the variance explained by the proposed random slopes.
 
 Alternatively, it is possible that the reviewer meant for us to build a model that allows the response to sexual selection treatment to differ among the fitness traits.
-In pseudocode, this would look something like `Trait_value ~ Sexual_selection_treatment * Type_of_trait`.
-However, this would represent a misunderstanding of meta-analysis: we do not analyse the raw trait values from the original studies, but rather collect their effect sizes and combine them to estimate the average effect size for each of the different fitness traits.
-Our present analysis already allows for the possibility that the response to sexual selection differs between the different types of fitness trait.
-Apologies in advance if we have missed the point you were making, and thank you for this thought-provoking feedback.
+In pseudocode, this model would look something like `Trait_value ~ Sexual_selection_treatment * Type_of_trait`.
+However, this would represent a misunderstanding: we did not analyse the raw trait values from the original studies, but rather we collected their effect sizes and combined them to estimate the average effect size for each of the different fitness traits.
+Our present analysis already allows for the possibility that the response to sexual selection is different for different types of fitness trait.
+Apologies in advance if we have missed the point you were making.
 
@@
 
-In the manuscript, we culled the dataset to only include the "direct" and "indirect" measures of popualtion fitness (this decision was taken to maximise the use of the data).
-If we were to eliminate indirect measures, it would leave us with approximately half the number of "direct" effect sizes in our main analysis (n = 159 vs n = 289).
-To facilitate easy comparison, we present the new and old results below: one can see that two things have changed (in terms of statistical significance).
-Firstly, for the "direct only" model the predicted effect size for males in stressful environments is now significantly negative (*Hedges' g* = -0.45; 95 % CIs = -0.70 to -0.19).
-However, because in the revised dataset we have reclassified male reproductive success as an ambiguous measure of fitness, there are only two effect sizes for males in stressful environments; making any conclusions drawn from this finding problematic.
-Secondly, the predicted effect size for females in benign environments in the "direct only model" are non-significantly positive, unlike the "direct and indirect" model, however, in both cases the positive effect of sexual selection on fitness is magnified for females in stressful environments.
-To avoid reader fatigue and low-powered predictions in our manuscript (we already chop and change the dataset in many different ways), we have retained the analysis to include both the "indirect and direct" measures.
-The graph on the right, and the table below show the main results recovered from only "direct" measurements for reference.
+We followed this suggestion and re-ran the model on 'direct only' and compared this to our previous results (both are presented below for comparison).
+The main result remains the same: the positive effect of sexual selection on fitness is magnified for females in stressful environments.
+However, two things have changed in terms of statistical significance.
 
-**Luke: Might need to argue use of both indirect and direct more.**
+Firstly, for the 'direct only' model the predicted effect size for males in stressful environments is now significantly negative (*Hedges' g*= -0.45; 95 % CIs = -0.70 to -0.19) as opposed to showing no difference.
+However, there are only two effect sizes for males in stressful environments using the 'direct only' subset of the data, so this is not very strong evidence that the direct and indirect measures differ considerably.
 
-<!-- **Add more in discussion about the variability amongst traits and why some might be subject to trade offs (e.g.
-immunity): We do kind of talk about this and an earlier draft had some of Jaceks work with regards to sexual conflict maintaining genetic variance through trade-offs.
-Should we add this back in?** -->
+Secondly, the predicted effect size for females in benign environments in the 'direct only' model are non-significantly positive, unlike the “direct and indirect” model where this result was statistically significant.
 
-<!-- The reviewer provides an accurate shortcoming of discussion on the observed heterogeneity between fitness components.
-The sixth paragraph of our discussion is raises some potential reasons why heterogeneity may be high within our meta-analysis.
-Additionally, it may please the reviewer to find an addition to our Supplementary Material (Table S9), now conducts independent meta-analyses and obtains $I^2$ for each of these traits.
-Even when metanalyses are conducted on a single trait, heterogeneity ($I^2$) is still high > 90 %.
--->
-
-<!-- In regards to conducting a meta-analysis on just direct fitness components, the reviewer provides a valid question of our use of direct **and** indirect fitness components for the meta-analysis investigating the effects of sex and stress.
-Based on the question we asked we were interested in the effect of sexual selection on many components of fitness.
--->
-
-<!-- Nevertheless, we conducted our analysis using just direct fitness measures.
-We find the same key associations; that sexual selection generally elevates fitness, especially for females, with the effect magnified in stressful environments.
-Below we present the findings.
--->
-<!-- **should we put this in the supp?** -->
-
-<!-- Additionally, in order to further distinguish the effects of sexual selection on ambiguous, indirect and direct fitness components, we have structured the second paragraph of the results to more consistently reflect our classification system.
--->
+**We now include the results recovered of the 'direct only' model in the supplementary material, and mention them in the main manuscript.
+We have left the 'direct plus indirect' model as our main focus, because its sample size and thus statistical power is much higher than the 'direct only' model (n = 289 vs n = 159 effect sizes).**
 
@@
 
-We agree that this section could have been much clearer, **and have made some changes in light of this comment to clarify what we meant**.
+We agree that this section could have been much clearer, **and have made changes in light of this comment to clarify what we meant**.
 We believe that experiments that manipuate sexual selection on males will alter female fitness traits, even in species where females experience no sexual selection, because of mechanisms such as intra- and inter-locus sexual conflict.
 That is, evolution in males will almost always have pleiotropic consequences for females, or change how males males affect females (i.e.
-sexual selection on males causes of evolution of males' indirect genetic effects on females).
+sexual selection on males causes evolution of males’ indirect genetic effects on females).
 
@@
 We thus might predict that females would adapt even more than males if female traits have more genetic variation, or if selection is 'harder' on females than males.
-These explanations are speculative and _post hoc_, and so in the revision we are careful to identify them as such.
-Our result is arguably opposite to what one would predict, because naively one would expect sexual selection to have greater effects on the phenotype of males, and we now spell this out as well.
+**These explanations are speculative and _post hoc_, and so in the revision we are careful to identify them as such.
+Our result is arguably opposite to what one would predict, because naively one would expect sexual selection to have greater effects on the phenotype of males, and we now spell this out as well.**
 
@@
 3 males 1 female, 2 of each, or 3 females 1 male).
-In the revised manuscript we now included "manipulation type" as a two-level moderator.
-We find no effect of manipulation type on effect size, suggestion that both ways of removing sexual selection had a similar effect on population fitness traits.
-See the revised Table S10.
+In the revised manuscript we now included "manipulation type" as a two-level moderator variable.
+We find no effect of manipulation type on effect size, suggesting that both ways of removing sexual selection had a similar effect on population fitness traits.
+This result can be found in the revised Table S10.
 
@@
 
-Our supplementary material does indeed contain all of our main figures, in order to show the data and code used to generate them.
+Our supplementary material contains all of our main figures (such as Figure 2), in order to show the data and the code that was used to generate them.
 We have changed the numbering of the supplementary figures, so that e.g.
 Figure 1 in the HTML supplement is correctly labelled as Figure 1 and not as Fig.
-S1, to make it clear that it is the same figure.
+S1, to make it clearer which are the same.
 
@@
 
-After reading those references, we agree that Hedges' *g* is imperfect, and so we checked the robustness of our meta-analysis using two alternative measures of effect size.
+After reading those papers, we agree that Hedges' *g* is imperfect, and so we checked the robustness of our meta-analysis using two alternative measures of effect size.
 Firstly, we present the log response ratio (*lnRR*) as suggested by this reviewer.
-Secondly, we present a modified version of Hedges' *g* that attempts to account for this heterogeneity issue [@bonett2009meta], named SMDH (standardized mean difference with heteroscedastic population variances in the two groups).
-There are several key findings from our new analyses using lnRR and SMDH:
+Secondly, we present a modified version of Hedges' *g* that attempts to account for the heterogeneity issue [@bonett2009meta], named SMDH (standardized mean difference with heteroscedastic population variances in the two groups).
+Here are the findings from our new analyses using lnRR and SMDH:
 
-*Firstly*, we found that Hedges' *g* and SMDH are highly correlated (in means and variance).
-This suggests that unequal variance between the treatment and control groups (heteroscedasticity) in the primary studies we examined is probably too small to greatly influence Hedges' *g*, which is interesting for the interpretation of earlier meta-analyses using Hedges' *g*.
+Firstly, we found that Hedges' *g* and SMDH are highly correlated (in means and variance).
+This is reassuring because it suggests that analyses based on *g* and SMDH are likely to yield the same results.
 
@@
 
-*Secondly*, we note that lnRR and SMDH can only be calculated in cases where the primary study reported means, standard deviations and sample sizes (352 out of 459 primary effect sizes).
+Secondly, we note that lnRR and SMDH can only be calculated in cases where the primary study reported means, standard deviations and sample sizes (352 out of 459 primary effect sizes).
 This is a limitation of lnRR and SMDH, as we must discard roughly 25% of the data in order to use them instead of Hedges' *g*.
@@
 
-*Thirdly*, if we conduct a meta-analysis using lnRR as the effect size we obtain very similar results with all our main conclusions unchanged, keeping in mind that lnRR and Hedge's are on different scales (see the revised Supplementary Material).
+Thirdly, if we conduct a meta-analysis using lnRR as the effect size we obtain very similar results with all our main conclusions unchanged, keeping in mind that lnRR and Hedge's *g* are on different scales (see the revised Supplementary Material).
 Specifically,
-+ The effect of sexual selection on population fitness is generally positive.
++ The effect of sexual selection on population fitness tends to be positive.
 + This effect is magnified for females in stressful environments with a significantly positive interaction term (stress*females).
@@
 
-*Fourthly*, the distribution of the lnRR effect sizes is non-normal (notably moreso than the distribution of Hedges' *g*), perhaps because one can get extreme values when taking a ratio (e.g.
-if the denominator is close to zero).
-Accordingly, @Lajeunesse_2015 showed that *lnRR* is problematic when quantifying the outcome of primary studies with small sample sizes, and can yield unsuitable variance estimates when the parameter scale of the study are close to zero.
+Fourthly, the distribution of the lnRR effect sizes is non-normal (notably moreso than the distribution of Hedges' *g*), perhaps because one can get extreme values when taking a ratio (e.g.
+if the denominator is close to zero, the ratio can be very large).
+Accordingly, @Lajeunesse_2015 showed that *lnRR* is problematic when quantifying the outcome of primary studies with small sample sizes, and can yield unsuitable variance in some cases.
 So, Hedges' *g* has the possible practical advantage of increasing model fit in our meta-analysis.
@@
 
-Many thanks -- we have now also present a meta-analysis of variation using lnVR in addition to one using lnCVR. We have the following comments on this new analysis:
+Many thanks -- we now also present a meta-analysis of variation using lnVR in addition to one using lnCVR. We have the following comments on this new analysis:
 
-*Firstly*, as the reviewer suggested, we now justify our use of lnCVR as opposed to lnVR, by assessing the mean-variance relationship in our data.
+Firstly, as the reviewer suggested, we now justify our use of lnCVR (as opposed to lnVR) by assessing the mean-variance relationship in our data.
 The major limitation of lnVR is that it does not account for the mean-variance relationship; indeed this is why lnCVR has been recommended over lnVR [@RN177].
-We indeed found a strong positive correlation between mean and variance, suggesting that we should indeed lnCVR and not lnVR.
+We indeed found a strong positive correlation between mean and variance, suggesting that we should favour lnCVR over lnVR.
 
@@
 We present this new result in the supplementary material and briefly discuss it in the manuscript.
-To summarise, we found very similar patterns, although the statistical significance some of the results have changed; see the following figure:
+To summarise, we found very similar patterns, although the statistical significance of some of the results has changed; see the following figure:
 
@@
 Thanks -- we now remind the reader that funnel plot asymmetry is not decisive evidence for publication bias, because it can also result from unexplained heterogeneity in the original effect sizes.
-We have elected not to implement trim-and-fill since the method seems to have fallen into disfavour among many readers, and because we are unsure how to correctly implement it using the REML- and Bayesian methods we used.
+We have elected not to implement trim-and-fill since the method seems to have fallen into disfavour, and because we are unsure how to correctly implement it using the REML- and Bayesian methods we used.
 NB that there is no method for trim-and-fill in mixed meta-analysis in the popular R package `metafor` (which we used), suggesting the method is not simple to implement.
@@
 
-Yes, and we have now included this information in the figure caption. Thank you for highlighting this.
+Yes -- we have now included this information in the figure caption.
 
@@
 
-It is possible that sexual selection on females on affects population fitness, although to our knowledge no-one has considered or modelled this before.
+It is possible that sexual selection on females affects population fitness, although to our knowledge no-one has considered or modelled this before.
 Also, we are not a aware of any experiments that have manipulated the opportunity for sexual selection on females independently of any other factors (e.g.
@@
 
-The results are odd, however to the best of our knowledge they are accurate.
-The REML model estimates the variance component ($\sigma^2$) of the "taxon" random effect as very low (3.38e-09), compared to the other random effects ("Study ID"" = 1.93e-01 and "fitness component" = 1.28e-01).
+**Luke says: I sent Justin an email about how to fix this on January 16th**
+
+The results are accurate to the best of our knowledge.
+The REML model estimates the variance component ($\sigma^2$) of the "taxon" random effect to be very low (3.38e-09), compared to the other random effects ("Study ID"" = 1.93e-01 and "fitness component" = 1.28e-01).
 A low value for $\sigma^2$ is the reason $I^2$ is estimated as zero.
 A potential reason for low heterogeneity is that there are only six taxon levels (campared to 53 studies and 13 fitness components).
-
-**Check this please Justin - I could not see what you changed in the R script**
-**Luke: I think the function was still in dev when i forked it and there was a bug that stopped in allowing me to get I2 for all three random effects (only last two), I changed the code so it recognised all three random effects.
-Not sure if the answer I provided makes sense**
 

### 2019-01-22 Response_to_Nature_Comms.Rmd
Changes to manuscript, I2, letter and supp Material

@@
 
-**We now include the results recovered of the 'direct only' model in the supplementary material, and mention them in the main manuscript.
-We have left the 'direct plus indirect' model as our main focus, because its sample size and thus statistical power is much higher than the 'direct only' model (n = 289 vs n = 159 effect sizes).**
+We now include the results recovered of the 'direct only' model in the supplementary material, and mention them in the main manuscript.
+We have left the 'direct plus indirect' model as our main focus, because its sample size and thus statistical power is much higher than the 'direct only' model (n = 289 vs n = 159 effect sizes).
+
+*N.B.* Using the corrected $I^2$ formula (see reviewer 3 comments) the type of trait measured only accounts for ~ 0.5 % of the total heterogeneity (for Hedges' g) and thus we have not added further discussion.
 
@@
 
-**Luke: Need to highlight in discussion where we put this in**
-
-We agree that this section could have been much clearer, **and have made changes in light of this comment to clarify what we meant**.
+We agree that this section could have been much clearer, and have made changes in light of this comment to clarify what we meant.
 We believe that experiments that manipuate sexual selection on males will alter female fitness traits, even in species where females experience no sexual selection, because of mechanisms such as intra- and inter-locus sexual conflict.
@@
 We thus might predict that females would adapt even more than males if female traits have more genetic variation, or if selection is 'harder' on females than males.
-**These explanations are speculative and _post hoc_, and so in the revision we are careful to identify them as such.
-Our result is arguably opposite to what one would predict, because naively one would expect sexual selection to have greater effects on the phenotype of males, and we now spell this out as well.**
+These explanations are speculative and _post hoc_, and so in the revision we are careful to identify them as such.
+Our result is arguably opposite to what one would predict, because naively one would expect sexual selection to have greater effects on the phenotype of males, and we now spell this out as well.
 
@@
 3 males 1 female, 2 of each, or 3 females 1 male).
-In the revised manuscript we now included "manipulation type" as a two-level moderator variable.
+In the revised Supplementary Material we now included "manipulation type" as a two-level moderator variable.
 We find no effect of manipulation type on effect size, suggesting that both ways of removing sexual selection had a similar effect on population fitness traits.
-This result can be found in the revised Table S10.
+This result can be found in the revised Table S10 (moderator labelled as Enforced MonogamyYES).
 
@@
 Specifically,
+
 + The effect of sexual selection on population fitness tends to be positive.
@@
 For the latter type, we considered the strength of sexual selection on males to be variable of interest, though it is confounded with the strength of sexual seleciton on females.
-To test if there was any difference in the effect sizes induced by these two types of manipulation, we now include 'manipulation type' (named "Enforced.Monogamy" in the Supplementary Material and R code) as a moderator variable: there was no effect in our preliminary model (**see above comment to Reviewer 1 and the revised Table S10**).
+To test if there was any difference in the effect sizes induced by these two types of manipulation, we now include 'manipulation type' (named "Enforced.Monogamy" in the Supplementary Material and R code) as a moderator variable: there was no effect in our preliminary model (see above comment to Reviewer 1 and the revised Table S10).
 
@@
 
-**Luke says: I sent Justin an email about how to fix this on January 16th**
-
-The results are accurate to the best of our knowledge.
-The REML model estimates the variance component ($\sigma^2$) of the "taxon" random effect to be very low (3.38e-09), compared to the other random effects ("Study ID"" = 1.93e-01 and "fitness component" = 1.28e-01).
-A low value for $\sigma^2$ is the reason $I^2$ is estimated as zero.
-A potential reason for low heterogeneity is that there are only six taxon levels (campared to 53 studies and 13 fitness components).
+Many thanks for raising this.
+The original $I^2$ mistakingly did not include residual heterogeneity in the denominator when calculating proportion of heterogeneity for each random effect.
+The supplementary material has now been changed, with correctly derived $I^2$ values included in the revised manuscript.
 

### 2019-01-22 Manuscripts/Manuscript_MetaAnalysis.Rmd
Changes to manuscript, I2, letter and supp Material

@@
 Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174).
-An extensive forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed in model prediction and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
+An extensive forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
 Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).
@@
 
-The effect size estimates we recovered were highly heterogeneous ($I^2$ = 95.4%, 95% CIs: 93.5-96.8%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016].
-Most of the observed heterogeneity stemmed from between-study differences ($I^2_{study}$ = 57.9%, 95% CIs: 38.8-76.7%), with variation between fitness components accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 37.2%, 95% CIs: 18.2-57.2%).
-The effect of taxon varied between REML and Bayesian models: the REML model suggested no effect ($I^2_{taxon}$ = 0), while the Bayesian model **suggested a probable non-zero effect** ($\sigma^2$ = 0.15 [0-0.54]).
-Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
+The effect size estimates we recovered were highly heterogeneous **($I^2$ = 95.2%, 95% CIs: 94.4% to 95.9%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016].
+Heterogeneity stemmed from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%), with variation between fitness components and taxon accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%,  95% CIs: 0.2% to 3.5%).** Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
 \phantomsection
@@
 
-As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 99.3%, 95% CIs: 98.7-99.6%).
-Heterogeneity in the dataset was due to variability between studies ($I^2_{study}$ = 16 %, 95% CIs: 7.21 % to 30 %), fitness components ($I^2_{fitness\:components}$ = 51.6%, 95% CIs: 22.4 to 77.6%) and taxon ($I^2_{taxon}$ = 31.7, 95% CIs: 6.97 to 62.3%).
-\phantomsection
+As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 98.9%, 95% CIs: 98.7% to 99.1%).
+**Heterogeneity in the dataset was due to variability between studies fitness components ($I^2_{fitness\:components}$ = 12.7%, 95% CIs: 4.5% to 23.1%) and taxon ($I^2_{taxon}$ = 7.7%, 95% CIs: 1.3% to 18.4%), as well as large amounts of residual heterogeneity (78.6 %, 95 % CIs: 65.9% to 89%).
+Using the REML approach variance associated with the Study ID random effect was estimated at zero ($I^2_{study}$ = 0 %), however Bayesian methods suggest this value may be zero or small ($sd_{study}$ = 0.07, 95 % CIs: 0 to 0.19).**  \phantomsection
 
@@
 The results of the meta-analysis support predictions that sexual selection **on males** can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
-Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles through selection on males [@RN94; @RN198; @RN95].
+Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles **through sexual selection on males** [@RN94; @RN198; @RN95].
 What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest).
-Below we discuss possible explanations for this result, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].
+**Below we discuss possible explanations for indirect fitness effects on females through sexual selection on males**, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].
+**However, these explanations are speculative and _post hoc_ as the result is arguably opposite to what one would predict, (*i.e.* sexual selection should have greater effects on the phenotype of males)**.
 
@@
 Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as commonly is the case for studies in ecology and evolution [@RN208].
-Most of the heterogeneity was explained by study and the fitness component that was measured, while the taxon, number of generations of evolution, and use of blinding showed less impact on effect size.
+Most of the heterogeneity was explained by study identification, while the taxon, number of generations of evolution, and use of blinding showed less impact on effect size.
 Taxonomic diversity is limited in experimental evolution studies, which mostly use lab-suitable invertebrates with similar mating systems and sex determination.
@@
 
-**Additionally, using studies that presented means, standard deviations and sample sizes (n = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) [@Hedges_1999; @Osenberg_1997] The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that
+**Additionally, using studies that presented means, standard deviations and sample sizes (_n_ = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) [@Hedges_1999; @Osenberg_1997] The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that
 
-For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$ .**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4).
-As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 352 of 459 comparisons.
+For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$.
+**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4).
+As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 354 of 459 comparisons.
 \phantomsection
@@
 This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and female reproductive success); predictions for this model on the 22 fitness components were derived as above.
-Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (n = 16); subset for each fitness trait with more than three effect sizes.
+Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (_n_ = 16); subset for each fitness trait with more than three effect sizes.
 These models were were intercept only REML models with study and taxon as group-level effects**.
@@
 
-The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (**link hidden for double bind review**).
-The repository (**link hidden for double bind review**) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results.
+The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (**link hidden for double blind review**).
+The repository (**link hidden for double blind review**) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results.
 \phantomsection
@@
 Overall, effect sizes were more often positive than negative.
-Predicted average values are presented as a diamond for each fitness-relationship category.
+Predicted average values are presented as a diamond with 95 % CIs for each fitness-relationship category.
 The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line.

### 2019-01-22 meta_analysis_sexual_selection_pop_fitness.Rmd
Changes to manuscript, I2, letter and supp Material

@@
 
-Using an adapted function from https://github.com/daniel1noble/metaAidR we can obtain confidence intervals for total _I^2^_ and the individual components of the random effects.
+Using a function from https://github.com/daniel1noble/metaAidR we can obtain confidence intervals for total _I^2^_ and the individual components of the random effects.
 There are different methods to obtain estimates of _I^2^_.
@@
 ```{r warning=FALSE}
-I2(model.complete2, strict_dataset$var.g) %>% pander(digits = 3)
-```
-These values indicate that 57.4 % of total heterogeneity is due to the **between study** heterogeneity and 37.4 % for **between outcome** heterogeneity between different outcomes.
-The total _I^2^_  is 94.7 %, a reasonably high _I^2^_ value.
+I2.model.g <- rma.mv(g, V = var.g, 
+                          mods = ~ 1 + Sex * Environment, 
+                          random = list(~ 1 | Observation.level, 
+                                        ~ 1 | Study.ID, 
+                                        ~ 1 | Outcome,
+                                        ~ 1 | Taxon), 
+                          method = "REML", 
+                          data = strict_dataset %>% mutate(Observation.level = 1:n()))
+
+I2(I2.model.g, strict_dataset$var.g) %>% pander(digits = 3)
+```
+These values indicate that 36 % of total heterogeneity is due to the **between study**.
+The total _I^2^_  is 95.2 %, a reasonably high _I^2^_ value.
 However this is relatively common in Ecology and Evolution total [@Senior_I2_2016].
@@
 Similar to the meta-analysis on Hedges' g we can obtain _I^2^_ for lnCVR REML model.
-In this case (compared to Hedges' g) we see Taxon has more of a variable effect on overall _I^2^_ estimates and the total _I^2^_ is larger.
-
-```{r}
-I2(variance.model, na.omit(strict_dataset$var.lnCVr)) %>% pander(digits = 3)
-```
+In this case (compared to Hedges' g) we see Taxon has more of a variable effect on overall _I^2^_ estimates and Study.ID has the variance component ($\sigma^2$) esgtimated at zero.
+
+```{r}
+I2.model.lnCVr <- rma.mv(lnCVr, V = var.lnCVr, 
+                          mods = ~ 1 + Sex * Environment, 
+                          random = list(~ 1 | Study.ID,
+                                        ~ 1 | Outcome,
+                                        ~ 1 | Taxon,
+                                        ~ 1 | Observation.level), 
+                          method = "REML", 
+                          data = strict_dataset %>% mutate(Observation.level = 1:n()))
+
+I2(I2.model.lnCVr, na.omit(strict_dataset$var.lnCVr)) %>% pander(digits = 3)
+```
+
+**Disclaimer**: Noticeabley, the Study.ID $I^2$ is estimated at zero with no CIs.
+This result is sourced from the variance component for Study.ID ($\sigma_2$) being estimated at zero with a standard error of zero.
+This result is questionable, thus we run the above model using ``brms`` and find the variance of the Study.ID group-level effect to be non-zero with confidence intervals including zero (see below).
+This is potential advantage of the Bayesian approach.
+
+```{r}
+if(!file.exists("data/I2.variance.brms.rds")){
+
+I2.variance.brms <- brm(lnCVr| se(SE.v)  ~ 1 + Sex * Environment 
+                + (1|Taxon) 
+                + (1|Study.ID)
+                + (1|Outcome) 
+                + (1|Observation.level),
+                family = "gaussian", 
+                seed = 1,
+                cores = 4, chains = 4, iter = 4000, 
+                control = list(adapt_delta = 0.999, max_treedepth = 15),
+                data = strict_dataset %>% mutate(SE.v = sqrt(var.lnCVr)) %>% mutate(Observation.level = 1:n()))
+  saveRDS(I2.variance.brms, "data/I2.variance.brms.rds")
+
+}
+I2.variance.brms <- readRDS(file = "data/I2.variance.brms.rds") #Avoid re-running model above
+
+I2.variance.brms
+```
+
 _________

### 2019-01-22 I2_function.R

@@ -56,7 +56,7 @@ I2 <- function(model, v, ME = FALSE, sims = 1500, phylo = FALSE){
     colnames(sigma2) <- model$s.names
     sigmaN <- model$s.nlevels
     
-    if(model[["s.names"]][1] %in% colnames(sigma2) == FALSE){
+    if("Observation.level" %in% colnames(sigma2) == FALSE){
       stop("The metafor object does not contain a residual variance estimate. Please include an observation-level random effect (~1|obs) when fitting model")
     }
     

### 2019-01-22 Manuscripts/Manuscript_MetaAnalysis.Rmd
Luke edits

@@
 Here, we synthesise the empirical literature on sexual selection and population fitness using formal meta-analysis.
-We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection **on males**, and then measured some fitness component, since these provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations.
+We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection **on males**, and then measured some fitness component, since experiments provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations.
 Our principle aims were to measure the average net effect of sexual selection on the population-level mean and variance for various fitness components, to test whether this effect varies between stressful and benign environments, and identify key moderators of the effect size of sexual selection treatment.
@@
 In total, we obtained effect sizes for 22 different fitness traits, with female reproductive success ($n$ = 102) and offspring viability ($n$ = 56) being the most commonly-measured traits.
-We classified **171 effect sizes as direct measures of fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous** (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
-Specifically, direct measures were components of reproduction or long-term viability (*e.g.*, female reproductive success, offspring viability, and extinction rate), indirect measures were traits often used as a proxy of fitness but that do not directly measure aspects of success in reproduction or population viability (*e.g.*, lifespan, mating success and ejaculate quality/production); and ambiguous measures were those reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, male reproductive success, and early fecundity).
+We classified **171 effect sizes as direct measures of population fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous** (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
+Specifically, **we scored traits that are likely to correlate with population growth and persistence as direct** (*e.g.*, female reproductive success, offspring viability, and extinction rate), **those which are not necessarily correlated with population fitness but which do measure individual fitness as indirect** (*e.g.*, lifespan, male mating success and ejaculate quality/production); and **those for which the relationship to population fitness is unclear as ambiguous** (*e.g.*, body size, mating duration, male reproductive success, and early fecundity).
 \href{https://justincally.github.io/SexualSelection/#tables_of_sample_sizes}{Tables S4-S5} give a detailed description of our dataset.\phantomsection
@@
 
-The grand mean for all effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.24, 95% CIs: 0.055 to 0.43, $p$ = 0.011; Bayesian $\beta$ = 0.25, 95% CIs: -0.0074 to 0.51, $BF_{>0}$ = 35), indicating that sexual selection **on males** typically had a net positive effect on the majority of populations and fitness components so far studied.
+The grand mean across all types of effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.24, 95% CIs: 0.055 to 0.43, $p$ = 0.011; Bayesian $\beta$ = 0.25, 95% CIs: -0.0074 to 0.51, $BF_{>0}$ = 35), indicating that sexual selection **on males** typically had a net positive effect on the majority of populations and fitness components so far studied.
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
@@
 Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174).
-An extensive forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
+An large forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
 Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).
@@
 
-We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect fitness (\hyperlink{page.18}{Table 1, 2}).
+We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect the relationship between sexual selection and fitness (\hyperlink{page.18}{Table 1, 2}).
 Sexual selection **on males** significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
@@
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
-**When the lnRR (log Response Ratio) effect size was used to conduct the meta-analysis investigating the impact of sex and environment, the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S3 and Table S16).**
+**When we used an alternative measure of effect size (log Response Ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S3 and Table S16).**
 
@@
 The effect size estimates we recovered were highly heterogeneous **($I^2$ = 95.2%, 95% CIs: 94.4% to 95.9%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016].
-Heterogeneity stemmed from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%), with variation between fitness components and taxon accounting for comparatively less heterogeneity ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%,  95% CIs: 0.2% to 3.5%).** Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
+Heterogeneity stemmed mostly from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%) rather than differences between fitness components and taxon ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%, 95% CIs: 0.2% to 3.5%).** Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
 \phantomsection
@@
 The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (\autoref{publication_bias}a; Egger’s test: *z* = 5.9, $p$ < 0.0001).
-Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection.
-**However, funnel plot asymmetry can arise due to between-study heterogeneity (which high $I^2$ imply) and are not decisive tests of publication bias [@RN215]**.
+Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection **(though funnel plots are not a decisive evidence of publication bias[@RN215])**.
 There was no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.23) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.2, $p$ = 0.24); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
@@
 Furthermore, the overall benefit of sexual selection was greater for females than males, and this sex difference was magnified in stressful environments.
-Consistent with stronger selection on female fitness under stress, **female and mixed-sex samples showed substantially reduced phenotypic variance** when sexual selection was applied under stressful as opposed to benign conditions.
+Consistent with stronger selection on female fitness under stress, **female and mixed-sex samples showed reduced phenotypic variance** when sexual selection was applied under stressful as opposed to benign conditions.
 These results suggest that sexual selection may contribute to population persistence under stressful conditions, such as fluctuating environmental change [@RN173] or spatial variability [@RN189], particularly since female reproductive output is often a limiting factor in population growth [@RN188].
@@
 What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest).
-**Below we discuss possible explanations for indirect fitness effects on females through sexual selection on males**, in light of the core principle that the speed and magnitude of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].
-**However, these explanations are speculative and _post hoc_ as the result is arguably opposite to what one would predict, (*i.e.* sexual selection should have greater effects on the phenotype of males)**.
+**Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].** However, these explanations are speculative and _post hoc_, as the result is arguably opposite to what one would predict, (*i.e.* that manipulating sexual selection on males should affect the phenotype of males more than females)**.
 
 Firstly, the response of male fitness to sexual selection may be constrained in species where the heritability of male fitness is influenced by the sex determination system.
-Males are heterogametic in many of the species in our sample (*e.g.* in species with XY or XO sex determination systems); this can reduce father-to-son heritability relative to mother-to-daughter, since sons never inherit the larger sex chromosome from their fathers [@RN340; @RN262; @RN147; @RN263], which might slow adaptation in male relative to female traits [@RN263; @RN259].
+Males are heterogametic in many of the species in our sample (*e.g.* due to XY or XO sex determination); this can reduce father-to-son heritability relative to mother-to-daughter, since sons never inherit the larger sex chromosome from their fathers [@RN340; @RN262; @RN147; @RN263], which might slow adaptation in male relative to female traits [@RN263; @RN259].
 However, X-linkage is also likely to inflate the contribution of X-linked genes to fitness variance in the heterogametic sex.
-Under this view, X-linkage facilitates adaptation by increasing the efficacy of selection against recessive deleterious alleles and selection for rare (and recessive) beneficial alleles  [@RN341; @RN339].
+Under this view, X-linkage facilitates adaptation by increasing the efficacy of selection against recessive deleterious alleles and selection for recessive beneficial alleles [@RN341; @RN339].
 Perhaps as a result of these conflicting predictions, there seems to be no clear consensus regarding sex-based differences in heritability.
@@
 
-Secondly, selection on males might be weaker than selection on females, resulting in slower adaptation following experimental manipulation of sexual selection.
-This explanation may initially seem implausible, because net selection on males is generally assumed to be stronger than on females, due to the (actual or hypothesised) sex difference in sexual selection strength and inter-individual variance in fitness [@RN304; @RN303; @RN337; @RN338].
+Secondly, selection on males might be weaker than selection on females, resulting in slower adaptation following the experimental manipulation of sexual selection.
+This explanation may initially seem implausible, because net selection on males is generally assumed to be stronger than on females, due to (actual or hypothesised) sex differences in sexual selection and inter-individual variance in fitness [@RN304; @RN303; @RN337; @RN338].
 However, an oft-overlooked aspect is that selection might frequently be ‘softer’ on males and ‘harder’ on females [@RN319], because the local competitive environment is usually more important for males than it is for females.
@@
 Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the nature of selection, relative to expectations for large, natural populations [@RN322; @RN277; @RN112].
-For example, many studies [@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then mixed and randomly sampled to create the next generation; this design ensures that successful males simply needed to outcompete their rival(s) in the same sub-population, while each female's reproductive output is measured against the entire female population.
+For example, many studies [@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then mixed and randomly sampled to create the next generation; this design ensures that successful males simply needed to outcompete their rival(s) in the same sub-population (soft selection), while each female's reproductive output is measured against the entire female population (hard selection).
 
@@
 Recent work has emphasised that environmental stress should reduce the strength of sexually antagonistic selection relative to selection that is concordant between sexes.
-Theoretical models reaching this conclusion [@RN67; @RN173] have been supported by empirical studies [@RN187; @RN74; @RN243]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress [@RN74].
+Theoretical models reaching this conclusion [@RN67; @RN173] have been supported by some empirical work [@RN187; @RN74; @RN243]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress [@RN74].
 However, other quantitative genetic studies have shown that stressful conditions do not always reduce sexual antagonism [@RN297; @RN200; @RN257].
@@
 
-Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as commonly is the case for studies in ecology and evolution [@RN208].
-Most of the heterogeneity was explained by study identification, while the taxon, number of generations of evolution, and use of blinding showed less impact on effect size.
-Taxonomic diversity is limited in experimental evolution studies, which mostly use lab-suitable invertebrates with similar mating systems and sex determination.
-However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates [fish, insects, birds, spiders, reptiles, mammals; @RN165].
-Despite this, taxonomic differences in the effects of sexual selection on fitness or patterns of diversity are often expected due to differences in mating systems [@RN277] and sex-determination systems [@RN262].
-For example, mate choice is thought to be more prevalent in taxa with well-developed parental care [@RN196], affecting the strength and nature of sexual selection.
-Furthermore, male heterogametic taxa, including those commonly used in experimental evolution such as flies (Diptera), beetles (Coleoptera) and mice (Mammalia), are likely to have higher heritability of fitness from mothers to daughters.
-Our results -- which show greater fitness effects accruing to females -- align with this hypothesis.
+Although our meta-analysis revealed an overall positive effect of sexual selection, the variation in effect size across the dataset is high, as is often the case for studies in ecology and evolution [@RN208].
+Most of the heterogeneity was between studies (potentially due to differences between study designs and populations), while the taxon, number of generations of evolution, and use of blinding had less impact on effect size.
+Experimental evolution studies cover relatively few taxa, and most focus on easy-to-culture invertebrates with similar mating systems and sex determination.
+However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates [fish, insects, birds, spiders, reptiles, mammals; @RN165], perhaps suggesting that our results would generalise to other taxa.
+On the other hand, biological differences between taxa could change the relationship between sexual selection and population fitness.
+For example, species where males and females have radically different morphology might have a reduced inter-sexual genetic correlation for fitness, such that sexual selection has fewer pleiotropic benefits for females, while for species with sexually-selected male parental care, sexual selection might help the population by conferring high fitness to caring fathers.
 
 Our findings have implications for fundamental and applied research.
-For example, the beneficial population-level consequences of sexual selection have been proposed as one possible resolution to the long-standing evolutionary puzzle presented by sexual reproduction [@RN309].
-If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants that arise in their midst [@RN94; @RN308; @RN198].
+For example, the beneficial population-level consequences of sexual selection have been proposed as one possible resolution to the long-standing evolutionary puzzle regarding sexual reproduction [@RN309].
+If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants [@RN94; @RN308; @RN198].
 Sexual selection is also important for conservation [@RN25] and captive breeding programs [@RN117].
@@
 After removing duplicates, we read the titles and abstracts of the remaining 1,015 papers and removed those that did not fit our inclusion criteria (typically because they did not present primary experimental evolution data).
-This left 130 papers, for which we read the full text and applied the inclusion criteria outlined in the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) diagram (\autoref{prisma_flow}).
-Briefly, we included studies that 1) were conducted in a dioecious animal species, 2) experimentally manipulated the strength of sexual selection (*e.g.*, via experimentally-enforced random monogamy or an altered sex ratio) for at least one generation, and 3) measured a trait that we judged to be a potential correlate of population fitness.
+This left 130 papers, for which we read the full text and applied the inclusion criteria outlined in the PRISMA diagram (\autoref{prisma_flow}).
+Briefly, we included studies that 1) were conducted in a dioecious animal, 2) experimentally manipulated the strength of sexual selection (*e.g.*, via experimentally-enforced random monogamy or an altered sex ratio) for at least one generation, and 3) measured a trait that we judged to be a potential correlate of population fitness.
 This third criterion is the most subjective, because there is rarely enough data to determine whether a particular trait is (or is not) correlated with population fitness.
@@
 Finally, direct measures of fitness (female/mixed sex reproductive success, offspring viability and extinction rate) are those that measure fitness through components of reproduction or long-term viability.
-The ESM describes why specific papers recovered in the literature search were included or excluded (\href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S2}).
+The ESM describes why each of the 130 papers was included or excluded (\href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S2}).
 
-Of the 130 papers subjected to detailed screening, 62 were excluded based on the PRISMA criteria (\autoref{prisma_flow}).
+Of these 130 papers, 62 were excluded based on the PRISMA criteria (\autoref{prisma_flow}).
 Additionally, three papers presented insufficient information to calculate effect size.
 In these cases, we contacted the authors and attempted to obtain the missing data, with partial success.
-The final meta-analysis covered data from 65 papers.
+The final meta-analysis included data from 65 papers.
 
@@
 A key moderator was whether the environmental conditions that a population evolved under were stressful (*e.g.*, elevated mutation load, novel/sub-optimal food source, increased sub-lethal temperatures).
-Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), blinding of researchers to treatments and number of generations a treatment group underwent experimentally evolution.
+Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), the presence/absence of blind methodology, and number of generations a treatment group underwent experimental evolution.
 In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the ESM (\href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{Table S3}).
@@
 
-**Additionally, using studies that presented means, standard deviations and sample sizes (_n_ = 352) we were able to calculate an alternative effect size: the log-response ratio (lnRR) [@Hedges_1999; @Osenberg_1997] The lnRR was used as a supplement to Hedges' g as it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that
+**Additionally, using studies that presented means, standard deviations and sample sizes (_n_ = 352) we were able to calculate an alternative measure of effect size: the log-response ratio (lnRR) [@Hedges_1999; @Osenberg_1997].
+The lnRR was used as a supplement to Hedges' g because it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that
 
@@
 
-**For our meta-analysis investigating the effects of environment and sex on the magnitude and variance of fitness-related traits (*Hedges' g* and *lnCVR*) we provide estimates of heterogenity present in the dataset.
-We use the $I^2$ statistic as an estimate of the proportion of total variation in study estimates that is due to heterogeneity [@Higgins_2002].
-$I^2$ is prefered over other statistics as it is independent of sample size, is easily interperatable (pecentage) and can be partitioned between random effects [@RN208].
-Within ecology and evolution heterogeneity in datasets is often high, with the mean $I^2$ from 86 studies above 90 % [@Senior_I2_2016].**
+**For our meta-analyses investigating the effects of environment and sex on the magnitude and variance of fitness-related traits we provide estimates of heterogenity present in the dataset.
+We use the statistic $I^2$ as an estimate of the proportion of variance in effect size that is due to differences between studies [@Higgins_2002].
+$I^2$ is prefered over other statistics as it is independent of sample size, is easily interperatable, and can be partitioned between random effects [@RN208].
+Within ecology and evolution heterogeneity in datasets is often high, with the mean $I^2$ from 86 studies above 90% [@Senior_I2_2016].**
 
 Meta-analyses fit by REML were implemented in the *metafor* ``R`` package [v.
-2.0; @RN212], while their Bayesian equivalents used the *brms* ``R`` package [v.
-2.3.1; @RN290] to specify and run models in the Stan programming language.
-\phantomsection
+2.0; @RN212], while their Bayesian equivalents used the ``R`` package *brms* to run models in Stan[v.
+2.3.1; @RN290].\phantomsection
 
@@
 We tested for publication bias via funnel plots, using Egger’s test to quantify plot asymmetry [@RN213; @RN214].
-However, funnel plot asymmetry does not necessarily indicate publication bias; asymmetry can arise simply through between-study heterogeneity [@RN215].
-Thus, we utilised several other methods for checking publication bias.
-We investigated whether the time-lag bias [@RN216] – where effect size magnitudes decrease over successive years – is present.
-Additionally, we assessed a potential source of publication bias through the correlation between effect size and journal impact factor [@RN217], which can arise if null or countervailing results are more difficult to publish.
-The journal impact factor for each effect size at the time of publication was obtained using *InCites Journal Citation Reports*.\phantomsection
+Additionally, we tested for time-lag bias [@RN216], in which effect size magnitudes decline over time as more data are collected.
+Additionally, we assessed a potential source of publication bias through the correlation between effect size and journal impact factor [@RN217], which can arise if null or countervailing results are more difficult to publish (impact factors were from *InCites Journal Citation Reports*).\phantomsection
 

### 2019-01-22 Manuscripts/Manuscript_MetaAnalysis.Rmd
Final changes before submission

@@
 Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174).
-An large forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
+A large forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
 Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).
@@
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
-**When we used an alternative measure of effect size (log Response Ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S3 and Table S16).**
+**When we used an alternative measure of effect size (log response ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S3 and Table S16).**
 
@@
 **Heterogeneity in the dataset was due to variability between studies fitness components ($I^2_{fitness\:components}$ = 12.7%, 95% CIs: 4.5% to 23.1%) and taxon ($I^2_{taxon}$ = 7.7%, 95% CIs: 1.3% to 18.4%), as well as large amounts of residual heterogeneity (78.6 %, 95 % CIs: 65.9% to 89%).
-Using the REML approach variance associated with the Study ID random effect was estimated at zero ($I^2_{study}$ = 0 %), however Bayesian methods suggest this value may be zero or small ($sd_{study}$ = 0.07, 95 % CIs: 0 to 0.19).**  \phantomsection
+Using the REML approach heterogeneity associated with the Study ID random effect was estimated at zero ($I^2_{study}$ = 0 %), however the Bayesian approach suggests heterogeneity between studies may be zero or small ($sd_{study}$ = 0.07, 95 % CIs: 0 to 0.19).**  \phantomsection
 
@@
 What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest).
-**Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].** However, these explanations are speculative and _post hoc_, as the result is arguably opposite to what one would predict, (*i.e.* that manipulating sexual selection on males should affect the phenotype of males more than females)**.
+**Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].
+However, these explanations are speculative and _post hoc_, as the result is arguably opposite to what one would predict, (*i.e.* that manipulating sexual selection on males should affect the phenotype of males more than females)**.
 
@@
 Variation in effects of sexual selection in stressful environments may be due to potentially variable responses amongst taxa [@RN298] and environments.
-Notably, @RN173 predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it.
+Notably, Connallon & Hall [@RN173] predict that the dynamics of environmental change alter the strength of sexual antagonism; for instance, gradual directional selection may facilitate indefinite sexual antagonism, while rapid cyclical change can swiftly remove it.
 Our meta-analysis suggests that under directional selection imposed by environmental stress, sexual antagonism is likely dampened; allowing sexual selection to facilitate adaptation and persistence.
@@
 Experimental evolution studies cover relatively few taxa, and most focus on easy-to-culture invertebrates with similar mating systems and sex determination.
-However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates [fish, insects, birds, spiders, reptiles, mammals; @RN165], perhaps suggesting that our results would generalise to other taxa.
+However, a meta-analysis of macroevolutionary studies on sexual selection and speciation rate found no significant taxon-based differences across a diverse sample of vertebrates and invertebrates (fish, insects, birds, spiders, reptiles, mammals) [@RN165], perhaps suggesting that our results would generalise to other taxa.
 On the other hand, biological differences between taxa could change the relationship between sexual selection and population fitness.
@@
 
-**Additionally, using studies that presented means, standard deviations and sample sizes (_n_ = 352) we were able to calculate an alternative measure of effect size: the log-response ratio (lnRR) [@Hedges_1999; @Osenberg_1997].
-The lnRR was used as a supplement to Hedges' g because it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).** However, lnRR was not able to be calculated from studies that
+**Additionally, using studies that presented means, standard deviations and sample sizes (_n_ = 352) we were able to calculate an alternative measure of effect size: the log response ratio (_lnRR_) [@Hedges_1999; @Osenberg_1997].
+The _lnRR_ was used as a supplement to Hedges' _g_ because it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).**
 
@@
 **The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4).
-As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* for 354 of 459 comparisons.
+As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* and *lnVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* and *lnVR* for 354 of 459 comparisons.
 \phantomsection
@@
 This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and female reproductive success); predictions for this model on the 22 fitness components were derived as above.
-Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (_n_ = 16); subset for each fitness trait with more than three effect sizes.
+Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (_n_ = 18); subset for each fitness trait with more than three effect sizes.
 These models were were intercept only REML models with study and taxon as group-level effects**.
@@
 **For our meta-analyses investigating the effects of environment and sex on the magnitude and variance of fitness-related traits we provide estimates of heterogenity present in the dataset.
-We use the statistic $I^2$ as an estimate of the proportion of variance in effect size that is due to differences between studies [@Higgins_2002].
+We use the statistic $I^2$ as an estimate of the proportion of variance in effect size that is due to differences between levels of a random effect (*e.g.* studies) [@Higgins_2002].
 $I^2$ is prefered over other statistics as it is independent of sample size, is easily interperatable, and can be partitioned between random effects [@RN208].
@@
 
-The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (**link hidden for double blind review**).
-The repository (**link hidden for double blind review**) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results.
+The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (https://justincally.github.io/SexualSelection/).
+The repository (https://github.com/JustinCally/SexualSelection) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results.
 \phantomsection

### 2019-03-07 Response_to_editorial_requests.Rmd
Addition of editorial requests letter

---
title: 'Sexual selection improves population fitness: a systematic review and meta-analysis'
output:
  pdf_document: default
subtitle: Response to Editorial Requests
bibliography: Manuscripts/Bibliography/Bibliography.bib
header-includes: 
- \usepackage{hyperref}\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue} 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Dear Dr. Jones and colleagues,

We are delighted to provide a revised manuscript for publication in \textit{Nature Communications}. Below we provide a point-by-point response to the editorial requests as well as a response to comments by Prof. Jacek Radwan.

## Editorial Requests

\begin{enumerate}
  \item \textit{Please supply the main manuscript file in Microsoft Word or LaTeX format. Please supply a Supplementary Information file in PDF format.} \\ 
  The main manuscript is provided in LaTeX format (.tex) and the Supplementary Information is now in pdf format. However, we retain the HTML formatting for the Supplementary Information hosted on \hyperlink{https://justincally.github.io/SexualSelection/}{Github}.

  \item \textit{Please edit the title so that it is 15 words or fewer and does not include punctuation} \\
  <!-- Sexual selection improves population fitness based on a systematic review and meta-analysis -->

  \item \textit{The final paragraph of the Introduction should summarise the major results and conclusions of this manuscript, in the present tense.} \\
  <!-- We had previously included this in an earlier draft and cut it. Can add it back  -->

  \item \textit{Please shorten all subheadings in the Results section to fewer than 60 characters including spaces.} \\
  Sexual selection is associated with higher mean values for most fitness components \textbbf{to} Sexual selection improves average fitness for most traits. \\
  Sexual selection reduces phenotypic variance, for female traits in stressful environments \textbbf{to} Effects of sexual selection on phenotypic variance

  \item \textit{Please do not use italics or bold font to convey emphasis (in both the main text and the display items).} \\
  Is this the latin? (e.g. /Prima facie / Tabbles have bold, figures have bold...)

  \item \texit{Please avoid using speech marks around words or phrases. In most cases they are unnecessary.} \\
  Speech marks around the following words/phrases have now been removed: population fitness (l.21), purged (l.175), softer (l.199), harder (l.199), 'good genes' (l.243), attractive (l.244), unambiguous (l.359).

  \item \textit{Please make sure that mathematical terms throughout your manuscript and Supplementary Information (including in figures, figure axes, and legends) conform strictly to the guidelines} \\
  Not sure where we went wrong here?

  \item \textit{Wherever p-values are stated in the text and figure legends, please also state the name of the statistical test.} \\
  A couple of linear models in the publication bias section have p values without stating it is a linear regression.  Otherwise we dont have that many p values and it is described in the table as from a multilevel meta-analysis model.

  \item \textit{Please provide a full Methods section in the main manuscript file. Please note that there are no word limits to the Methods section. The Methods section must include subheadings of fewer than 60 characters including spaces. There is no word limit for the Methods section, so we recommend against splitting the methods description between the main text and Supplementary Information.}

  All headings are under 60 characters in length, we have some additional Supp Methods in the Supp info but it is more or an appendage to the Supp tables and search terms (which would not nicely format in the main text)

  \item \textit{Please rename the Methods section as "Methods".} \\

  Done

  \item \textit

\end{enumerate}

## Response to Prof. Jacek Radwan

### 2019-03-07 Manuscripts/Manuscript_MetaAnalysis.Rmd
Addition of editorial requests letter

@@
 Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis.
-We find that sexual selection **on males** tends to elevate the mean and reduce the variance for many fitness traits, especially in females, and for populations evolving under stressful conditions.
+We find that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females, and for populations evolving under stressful conditions.
 We conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
@@
 
-Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus **sexual conflict [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014]**.
+Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus sexual conflict [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014].
 Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males [@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care: \textit{inter}locus sexual conflict [@RN314; @RN276; @RN315].
@@
 Here, we synthesise the empirical literature on sexual selection and population fitness using formal meta-analysis.
-We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection **on males**, and then measured some fitness component, since experiments provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations.
+We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection on males, and then measured some fitness component, since experiments provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations.
 Our principle aims were to measure the average net effect of sexual selection on the population-level mean and variance for various fitness components, to test whether this effect varies between stressful and benign environments, and identify key moderators of the effect size of sexual selection treatment.
@@
 In total, we obtained effect sizes for 22 different fitness traits, with female reproductive success ($n$ = 102) and offspring viability ($n$ = 56) being the most commonly-measured traits.
-We classified **171 effect sizes as direct measures of population fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous** (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
-Specifically, **we scored traits that are likely to correlate with population growth and persistence as direct** (*e.g.*, female reproductive success, offspring viability, and extinction rate), **those which are not necessarily correlated with population fitness but which do measure individual fitness as indirect** (*e.g.*, lifespan, male mating success and ejaculate quality/production); and **those for which the relationship to population fitness is unclear as ambiguous** (*e.g.*, body size, mating duration, male reproductive success, and early fecundity).
+We classified 171 effect sizes as direct measures of population fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
+Specifically, we scored traits that are likely to correlate with population growth and persistence as direct (*e.g.*, female reproductive success, offspring viability, and extinction rate), those which are not necessarily correlated with population fitness but which do measure individual fitness as indirect (*e.g.*, lifespan, male mating success and ejaculate quality/production); and those for which the relationship to population fitness is unclear as ambiguous (*e.g.*, body size, mating duration, male reproductive success, and early fecundity).
 \href{https://justincally.github.io/SexualSelection/#tables_of_sample_sizes}{Tables S4-S5} give a detailed description of our dataset.\phantomsection
@@
 
-The grand mean across all types of effect sizes (**direct, indirect and ambiguous**) was positive (REML $\beta$ = 0.24, 95% CIs: 0.055 to 0.43, $p$ = 0.011; Bayesian $\beta$ = 0.25, 95% CIs: -0.0074 to 0.51, $BF_{>0}$ = 35), indicating that sexual selection **on males** typically had a net positive effect on the majority of populations and fitness components so far studied.
+The grand mean across all types of effect sizes (direct, indirect and ambiguous) was positive (REML $\beta$ = 0.24, 95% CIs: 0.055 to 0.43, $p$ = 0.011; Bayesian $\beta$ = 0.25, 95% CIs: -0.0074 to 0.51, $BF_{>0}$ = 35), indicating that sexual selection on males typically had a net positive effect on the majority of populations and fitness components so far studied.
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
 Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6}).
-**Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.21, 95% CIs: 0.058 to 0.093; Bayesian $\beta$ = 0.20, 95% CIs: -0.0016 to	0.39, $BF_{>0}$ = 38, $n$ = 144) and an indirect relationship to fitness (REML $\beta$ = 0.24, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.033 to 0.43, $BF_{>0}$ = 59, $n$ = 141).
+Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.21, 95% CIs: 0.058 to 0.093; Bayesian $\beta$ = 0.20, 95% CIs: -0.0016 to	0.39, $BF_{>0}$ = 38, $n$ = 144) and an indirect relationship to fitness (REML $\beta$ = 0.24, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.033 to 0.43, $BF_{>0}$ = 59, $n$ = 141).
 Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174).
-A large forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in** \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
+A large forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
 Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).
@@
 We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect the relationship between sexual selection and fitness (\hyperlink{page.18}{Table 1, 2}).
-Sexual selection **on males** significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
+Sexual selection on males significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
 Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
@@
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
-**When we used an alternative measure of effect size (log response ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S3 and Table S16).**
+When we used an alternative measure of effect size (log response ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S3 and Table S16).
 
@@
 
-The effect size estimates we recovered were highly heterogeneous **($I^2$ = 95.2%, 95% CIs: 94.4% to 95.9%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016].
-Heterogeneity stemmed mostly from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%) rather than differences between fitness components and taxon ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%, 95% CIs: 0.2% to 3.5%).** Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
+The effect size estimates we recovered were highly heterogeneous ($I^2$ = 95.2%, 95% CIs: 94.4% to 95.9%), reflecting the large differences in experimental procedures, study species, and fitness components included in our meta-analysis [@RN208; @Senior_I2_2016].
+Heterogeneity stemmed mostly from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%) rather than differences between fitness components and taxon ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%, 95% CIs: 0.2% to 3.5%).
+Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
 \phantomsection
@@
 However, similar to the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.76, 95% CIs: -1.22 to -0.31; \autoref{env_sex}b).
-**A meta-analysis using the log variability ratio (lnVR), which does not account for the mean-variance relationship present in the dataset (Figure S4), suggested sexual selection reduces variance for mixed-sex samples in stressful conditions, but not females, results of this meta-analysis can be found in the Supplementary Material (Figure S5 and Table S21)**.
+A meta-analysis using the log variability ratio (lnVR), which does not account for the mean-variance relationship present in the dataset (Figure S4), suggested sexual selection reduces variance for mixed-sex samples in stressful conditions, but not females, results of this meta-analysis can be found in the Supplementary Material (Figure S5 and Table S21).
 
 As in the meta-analysis of trait means, there was high heterogeneity in the estimates of *lnCVR* ($I^2$ = 98.9%, 95% CIs: 98.7% to 99.1%).
-**Heterogeneity in the dataset was due to variability between studies fitness components ($I^2_{fitness\:components}$ = 12.7%, 95% CIs: 4.5% to 23.1%) and taxon ($I^2_{taxon}$ = 7.7%, 95% CIs: 1.3% to 18.4%), as well as large amounts of residual heterogeneity (78.6 %, 95 % CIs: 65.9% to 89%).
-Using the REML approach heterogeneity associated with the Study ID random effect was estimated at zero ($I^2_{study}$ = 0 %), however the Bayesian approach suggests heterogeneity between studies may be zero or small ($sd_{study}$ = 0.07, 95 % CIs: 0 to 0.19).**  \phantomsection
+Heterogeneity in the dataset was due to variability between studies fitness components ($I^2_{fitness\:components}$ = 12.7%, 95% CIs: 4.5% to 23.1%) and taxon ($I^2_{taxon}$ = 7.7%, 95% CIs: 1.3% to 18.4%), as well as large amounts of residual heterogeneity (78.6 %, 95 % CIs: 65.9% to 89%).
+Using the REML approach heterogeneity associated with the Study ID random effect was estimated at zero ($I^2_{study}$ = 0 %), however the Bayesian approach suggests heterogeneity between studies may be zero or small ($sd_{study}$ = 0.07, 95 % CIs: 0 to 0.19).
+\phantomsection
 
@@
 The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (\autoref{publication_bias}a; Egger’s test: *z* = 5.9, $p$ < 0.0001).
-Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection **(though funnel plots are not a decisive evidence of publication bias[@RN215])**.
+Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection (though funnel plots are not a decisive evidence of publication bias[@RN215]).
 There was no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.23) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.2, $p$ = 0.24); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
@@
 
-Our meta-analysis revealed that populations evolving under sexual selection often have higher values for multiple fitness traits, relative to populations where sexual selection **on males** was experimentally removed or weakened.
-**Sexual selection had beneficial effects for traits that were ambiguously or indirectly related to fitness, but had smaller, variable effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced) and the proportion of viable offspring**.
+Our meta-analysis revealed that populations evolving under sexual selection often have higher values for multiple fitness traits, relative to populations where sexual selection on males was experimentally removed or weakened.
+Sexual selection had beneficial effects for traits that were ambiguously or indirectly related to fitness, but had smaller, variable effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced) and the proportion of viable offspring.
 Fitness traits related to immunocompetence were an exception: sexual selection typically resulted in weaker immunity.
@@
 Furthermore, the overall benefit of sexual selection was greater for females than males, and this sex difference was magnified in stressful environments.
-Consistent with stronger selection on female fitness under stress, **female and mixed-sex samples showed reduced phenotypic variance** when sexual selection was applied under stressful as opposed to benign conditions.
+Consistent with stronger selection on female fitness under stress, female and mixed-sex samples showed reduced phenotypic variance when sexual selection was applied under stressful as opposed to benign conditions.
 These results suggest that sexual selection may contribute to population persistence under stressful conditions, such as fluctuating environmental change [@RN173] or spatial variability [@RN189], particularly since female reproductive output is often a limiting factor in population growth [@RN188].
 
-The results of the meta-analysis support predictions that sexual selection **on males** can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
-Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles **through sexual selection on males** [@RN94; @RN198; @RN95].
+The results of the meta-analysis support predictions that sexual selection on males can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
+Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles through sexual selection on males [@RN94; @RN198; @RN95].
 What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest).
-**Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].
-However, these explanations are speculative and _post hoc_, as the result is arguably opposite to what one would predict, (*i.e.* that manipulating sexual selection on males should affect the phenotype of males more than females)**.
+Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].
+However, these explanations are speculative and _post hoc_, as the result is arguably opposite to what one would predict, (*i.e.* that manipulating sexual selection on males should affect the phenotype of males more than females).
 
@@
 
-#Materials and methods
+#Methods
 \phantomsection
@@
 From each paper, we first attempted to extract the arithmetic means, standard deviations and sample sizes of each of the different treatment groups, which facilitate calculation of effect size (see below).
-Typically, there were two or three treatments, which varied in the strength of sexual selection **on males through manipulations to the adult sex ratio, in these cases we considered treatments with the greater male to female ratio to be the high sexual selection treatment group**.
+Typically, there were two or three treatments, which varied in the strength of sexual selection on males through manipulations to the adult sex ratio, in these cases we considered treatments with the greater male to female ratio to be the high sexual selection treatment group.
 For some papers, summary statistics were not written down, but were presented in a figure such as a bar chart: in these cases, we extracted the data using *WebPlotDigitizer* v.3.12 [@RN195].
@@
 In all cases, we selected a direction for the effect size calculation such that in our meta-analysis, negative effect sizes indicate that the removal of sexual selection was associated with higher fitness trait values, and positive effect sizes indicate higher fitness when sexual selection was elevated or left intact.
-We also inverted the sign of effect sizes pertaining to measurements that are expected to be negatively related to population fitness **(*e.g.*, parasite load, mutation load, extinction risk/rate, mating latency (males), and rate of senescence)**.
+We also inverted the sign of effect sizes pertaining to measurements that are expected to be negatively related to population fitness (*e.g.*, parasite load, mutation load, extinction risk/rate, mating latency (males), and rate of senescence).
 Because many of our 65 papers measured multiple fitness outcomes, studied multiple replicate populations, or had three or more sexual selection treatments, we calculated a total of 459 effect sizes.
 
-**Additionally, using studies that presented means, standard deviations and sample sizes (_n_ = 352) we were able to calculate an alternative measure of effect size: the log response ratio (_lnRR_) [@Hedges_1999; @Osenberg_1997].
-The _lnRR_ was used as a supplement to Hedges' _g_ because it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).**
+Additionally, using studies that presented means, standard deviations and sample sizes (_n_ = 352) we were able to calculate an alternative measure of effect size: the log response ratio (_lnRR_) [@Hedges_1999; @Osenberg_1997].
+The _lnRR_ was used as a supplement to Hedges' _g_ because it relaxes the assumption in equal variances between control and treatment groups (homoscedasticity).
 
 For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$.
-**The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4).
-As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].** The calculation of *lnCVR* and *lnVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* and *lnVR* for 354 of 459 comparisons.
+The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4).
+As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].
+The calculation of *lnCVR* and *lnVR* relies on the availability of arithmetic means, standard deviations and sample sizes for the two treatment groups [@RN177; @RN190], and so we were only able to calculate *lnCVR* and *lnVR* for 354 of 459 comparisons.
 \phantomsection
@@
 Given the small number of phylogenetically diverse species, we did not utilise phylogenetic corrections within the models.
-**In our meta-analyses we report Bayes Factors ($BF$), giving the likelihood ratio that the focal effect size differs from zero $BF_{>0}$.**
+In our meta-analyses we report Bayes Factors ($BF$), giving the likelihood ratio that the focal effect size differs from zero $BF_{>0}$.
 
-**Secondly, we fixed the relationship to fitness class (Ambiguous, Indirect or Direct) as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the three fitness-relationship classes, using the relevant ``predict`` functions for each of the ``R`` packages used (see below).
+Secondly, we fixed the relationship to fitness class (Ambiguous, Indirect or Direct) as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the three fitness-relationship classes, using the relevant ``predict`` functions for each of the ``R`` packages used (see below).
 This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and female reproductive success); predictions for this model on the 22 fitness components were derived as above.
 Alternatively, to assess the impact of sexual selection on each fitness component independently of one another we conducted seperate meta-analyses (_n_ = 18); subset for each fitness trait with more than three effect sizes.
-These models were were intercept only REML models with study and taxon as group-level effects**.
+These models were were intercept only REML models with study and taxon as group-level effects.
 Further details on model parameters can be found within the ESM.
 
-Thirdly, we measured the impact of environment, sex and their interaction on the effect size **(Hedges’ *g*, *lnRR*, *lnCVR* and *lnVR* in the ESM)** associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
-These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign **(Hedges' *g*: *n* = 330; *lnRR*, *lnCVR* & *lnVR*: *n* = 269)**.
+Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g*, *lnRR*, *lnCVR* and *lnVR* in the ESM) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
+These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g*: *n* = 330; *lnRR*, *lnCVR* & *lnVR*: *n* = 269).
 We again fit study ID, fitness component, and taxon as random/group level effects.
@@
 
-**For our meta-analyses investigating the effects of environment and sex on the magnitude and variance of fitness-related traits we provide estimates of heterogenity present in the dataset.
+For our meta-analyses investigating the effects of environment and sex on the magnitude and variance of fitness-related traits we provide estimates of heterogenity present in the dataset.
 We use the statistic $I^2$ as an estimate of the proportion of variance in effect size that is due to differences between levels of a random effect (*e.g.* studies) [@Higgins_2002].
 $I^2$ is prefered over other statistics as it is independent of sample size, is easily interperatable, and can be partitioned between random effects [@RN208].
-Within ecology and evolution heterogeneity in datasets is often high, with the mean $I^2$ from 86 studies above 90% [@Senior_I2_2016].**
+Within ecology and evolution heterogeneity in datasets is often high, with the mean $I^2$ from 86 studies above 90% [@Senior_I2_2016].
 
@@
 
-**Table 1:** Results for the multilevel meta-analysis model testing the effects of sexual selection on fitness (**measured by Hedges' _g_**) in different environments and between sexes.
+Table 1: Results for the multilevel meta-analysis model testing the effects of sexual selection on fitness (measured by Hedges' _g_) in different environments and between sexes.
 Moderator variables whose 95% confidence intervals do not cross zero are shown in bold.
@@
 
-**Table 2:** Hypothesis tests using restricted maximum likelihood (REML) or Bayesian methods, illustrating how sex and environmental stress interact to modulate effect size.
+Table 2: Hypothesis tests using restricted maximum likelihood (REML) or Bayesian methods, illustrating how sex and environmental stress interact to modulate effect size.
 Tests whose 95% confidence intervals do not cross zero are shown in bold.
@@
 
-![(**a**) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
-(**b**) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals.
+![(a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
+(b) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals.
 The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Table S12 and S14).
@@
 ![Tests of publication bias are mixed and suggest publication bias may be present.
-(**a**) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies.
-(**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias.
-For (**b**) and (**c**) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).
-For (**a**), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99 % CIs for the dataset.
-The Grey envelopes in (**b**) and (**c**) represent the 95 % CI of the linear regression.\label{publication_bias}](Figures/publicationbias.pdf)
+(a) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies.
+(b) No significant correlation exists between journal impact factor and effect size, (c) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias.
+For (b) and (c) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).
+For (a), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99 % CIs for the dataset.
+The Grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.\label{publication_bias}](Figures/publicationbias.pdf)
 

### 2019-03-08 Response_to_editorial_requests.Rmd
organising repo

@@
   <!-- Sexual selection improves population fitness based on a systematic review and meta-analysis -->
+  We have changed our title to: Meta-analytic evidence that sexual selection improves population fitness
 
@@
   \item \textit{Please shorten all subheadings in the Results section to fewer than 60 characters including spaces.} \\
-  Sexual selection is associated with higher mean values for most fitness components \textbbf{to} Sexual selection improves average fitness for most traits. \\
-  Sexual selection reduces phenotypic variance, for female traits in stressful environments \textbbf{to} Effects of sexual selection on phenotypic variance
+  Sexual selection is associated with higher mean values for most fitness components \textbf{to} Sexual selection improves average fitness for most traits. \\
+  Sexual selection reduces phenotypic variance, for female traits in stressful environments \textbf{to} Effects of sexual selection on phenotypic variance
 
@@
 
-  \item \texit{Please avoid using speech marks around words or phrases. In most cases they are unnecessary.} \\
+  \item \textit{Please avoid using speech marks around words or phrases. In most cases they are unnecessary.} \\
   Speech marks around the following words/phrases have now been removed: population fitness (l.21), purged (l.175), softer (l.199), harder (l.199), 'good genes' (l.243), attractive (l.244), unambiguous (l.359).
+
+  Single quotes for technical terms
 
@@
 
-  \item \textit
+  \item \textit{All Nature Communications manuscripts must include a section titled "Data Availability" as a separate section after the Methods section and before the References.}
 

### 2019-03-08 Manuscripts/Manuscript_MetaAnalysis.Rmd
organising repo

@@
 
-##Code and data availability
+##Code availability
 
-The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (https://justincally.github.io/SexualSelection/).
+The code used to perform this meta-analysis is available on Github (https://justincally.github.io/SexualSelection/).
 The repository (https://github.com/JustinCally/SexualSelection) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results.
 \phantomsection
+
+##Data availability
+
+All data are available on Github (https://github.com/JustinCally/SexualSelection).
 

### 2019-03-08 meta_analysis_sexual_selection_pop_fitness.Rmd
organising repo

@@
 ```{r}
-read.csv('data/Eligibility Workbook(22.02).csv', fileEncoding="UTF-8") %>%
+read.csv('data/Eligibility Workbook.csv', fileEncoding="UTF-8") %>%
   kable("html") %>% kable_styling() %>%
@@
 
-knitr::include_graphics(path = "figures/ForestPlot_size_reduced.png") 
+knitr::include_graphics(path = "figures/ForestPlot_large.png") 
 ```
@@
 
-ggsave(plot = funnel.plot, filename = "figures/funnel_plot.eps", height = 7.5, width = 10)
+#ggsave(plot = funnel.plot, filename = "figures/funnel_plot.eps", height = 7.5, width = 10)
 funnel.plot

### 2019-03-09 Response_to_editorial_requests.Rmd
Changes to bib, response to editor and manuscript

@@
 
-  \item \textit{All Nature Communications manuscripts must include a section titled "Data Availability" as a separate section after the Methods section and before the References.}
+  \item \textit{All Nature Communications manuscripts must include a section titled "Data Availability" as a separate section after the Methods section and before the References.} \\
+
+  We have now ammended this section of the manuscript by seperating data availability and code availability as well as providing the relevent links to the data sources hosted on github.
+
+  \item \textit{We strongly encourage authors to deposit all new data associated with the paper in a persistent repository where they can be freely and enduringly accessed.} \\
+
+  We have chosen to host our data on a github repository alongside all our code and a neatly formatted html with supplementary information in an effort to maximise transparency of our analysis as well as allowing for the data and code to be easily reproduced and built upon by future studies.
+
+  \item \textit{For all studies developing new software or using custom code in the generation or processing of datasets, a statement must be included in the Methods section, under the subheading "Code Availability", indicating whether and how the code can be accessed, including any restrictions to access.
+This section should also include information on the versions of any software used, if relevant, and any specific variables or parameters used to generate, test, or process the current dataset.} \\
+
+  Done. The Supplementary information has a section at the end with `R Session Information`, which provides details of the attached packages and parameters of the operating system.
+
+  \item \textit{Please add a reference to the source data file in the "Data Availability" section} \\
+
+  Done. The repository now also contains a more extensive 'READ ME', with a description of the repository organisation.
+
+  \item \textit{End notes} \\
+
+  Acknowledgements, Author Contributions and Competing Interests are now found after the references.
+
+  \item \textit{Please update any preprints in the reference list with details of the published paper, if possible.} \\
+
+  We have changed one reference that was a preprint and is now published (Li and Holman 2018).
+
+  \item \textit{Please check whether your manuscript or Supplementary Information contain third-party images, such as figures from the literature, stock photos, clip art or commercial satellite and map data.} \\
+
+  No third-party images are included in the display items.
+
+  \item \textit{Please include a brief title for all figure legends that summarises the whole figure and does not refer to specific panels and Please ensure that figure legend titles are brief - they should not occupy more than one line in the final proof.} \\
+
+  Figure titles are now included and illustrated in bold at the start of the figure legend. They do not occupy more than one line.
+
+  \item \textit{Please include figure legends of up to 350 words, referring to all panels within the figure.} \\
+
+  No figure legends are above 350 words and in all cases all panels are referred to in the legend.
+
+  \item \textit{Data in tables must be free from bold/italic formatting unless this has been clearly defined in the footnote.
+Tables need to be black and white, fit onto a single A4 portrait page and can contain only one row of column titles.
+Finally, we are unable to merge cells or include vertical dividing lines or diagonal lines.
+Please format your tables accordingly.} \\
+
+  Bolding in tables are now clearly defined in the footnotes, the tables are formatted in latex, contain one row of column titles and are in black and white.
+
+  \item \textit{Please ensure that table titles are brief - they should not occupy more than one line in the final proof.} \\
+
+  Done
 

### 2019-03-09 Manuscripts/Manuscript_MetaAnalysis.Rmd
Changes to bib, response to editor and manuscript

@@
 
-The code used to perform this meta-analysis is available on Github (https://justincally.github.io/SexualSelection/).
-The repository (https://github.com/JustinCally/SexualSelection) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results.
+The code used to perform this meta-analysis is freely available on Github (https://justincally.github.io/SexualSelection/).
+Here the code is available through a neatly compiled html, with the R Markdown file found within the corresponding github repository:  (https://github.com/JustinCally/SexualSelection).
 \phantomsection
@@
 
-All data are available on Github (https://github.com/JustinCally/SexualSelection).
-
-#Acknowledgements
-We are very grateful to Paco Garcia-Gonzalez for sharing a collection of literature that helped to guide our study, and to Tim Connallon for comments on the manuscript.
+All data are freely available on Github (https://github.com/JustinCally/SexualSelection).
+The repository provides a source data file that was used to create all results, tables and figures.
+\phantomsection
 
@@
 \phantomsection
+
+#Acknowledgements
+We are very grateful to Paco Garcia-Gonzalez for sharing a collection of literature that helped to guide our study, and to Tim Connallon for comments on the manuscript.  \phantomsection
+
+#Author contributions  
+All authors designed the study; JGC collected the data; JGC and LH conducted the meta-analyses; JGC wrote the first draft of the manuscript; and all authors contributed substantially to all further revisions.
+\phantomsection
+
+#Competing interests  
+The authors declare no competing interests.
+
+\newpage
+\phantomsection
 \nolinenumbers
@@
 #Tables and Figures
-
-Table 1: Results for the multilevel meta-analysis model testing the effects of sexual selection on fitness (measured by Hedges' _g_) in different environments and between sexes.
-Moderator variables whose 95% confidence intervals do not cross zero are shown in bold.
 
@@
 
-kable(table1, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
-  kable_styling(latex_options = c("scale_down", "striped"), full_width = F) %>%
+kable(table1, format = "latex", booktabs = T, digits = 2, escape = F, 
+      caption = "Multilevel meta-analysis model results") %>% 
+  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
   row_spec(0, bold = TRUE) %>%
   group_rows("REML Model", 1, 6) %>%
-  group_rows("Bayesian Model", 7, 12)
+  group_rows("Bayesian Model", 7, 12) %>% 
+  footnote(symbol_title = "", 
+           symbol = c("Moderator variables whose 95\\\\% confidence intervals do not cross zero are shown in bold.", 
+                       "Hedges' \\\\textit{g} is the response variable for this model"), 
+           threeparttable = T, 
+           escape = F)
 ```
 
-\vspace{0.75 cm}
-
-Table 2: Hypothesis tests using restricted maximum likelihood (REML) or Bayesian methods, illustrating how sex and environmental stress interact to modulate effect size.
-Tests whose 95% confidence intervals do not cross zero are shown in bold.
+\vspace{0.5 cm}
 
@@
 
-kable(table2, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
-  kable_styling(latex_options = c("scale_down"), full_width = F) %>%
+kable(table2, format = "latex", booktabs = T, digits = 2, escape = F, 
+      caption = "Hypothesis tests showing how sex and environmental stress interact to modulate effect size") %>% 
+  kable_styling(latex_options = c("hold_position"), full_width = F) %>%
   row_spec(0, bold = TRUE) %>%
-  collapse_rows(columns = 1:2, latex_hline = "major")
+  collapse_rows(columns = 1:2, latex_hline = "major") %>%
+  footnote(symbol_title = "", 
+         symbol = c("Moderator variables whose 95\\\\% confidence intervals do not cross zero are shown in bold.", 
+                     "Hedges' \\\\textit{g} is the response variable for this model"), 
+         threeparttable = T, 
+         escape = F)
 ```
@@
 
-![The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness.
+![\textbf{The effect of sexual selection on direct, indirect and ambiguous fitness components.} The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness.
 Overall, effect sizes were more often positive than negative.
@@
 
-![(a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
+![\textbf{The roles of environmental stress and sex.} (a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
 (b) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals.
@@
 
-![Tests of publication bias are mixed and suggest publication bias may be present.
+![\textbf{Tests for publication bias in the dataset.} Tests of publication bias are mixed and suggest publication bias may be present.
 (a) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies.
@@
 
-![Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.\label{prisma_flow}](Figures/PRISMA\ Chart.pdf)
+![\textbf{PRISMA diagram.} Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.\label{prisma_flow}](Figures/PRISMA\ Chart.pdf)

### 2019-03-15 Response_to_editorial_requests.Rmd
Updates on response to editorial requests

--- 2019-03-08 Response_to_editorial_requests.Rmd
@@
 ---
-title: 'Sexual selection improves population fitness: a systematic review and meta-analysis'
+title: 'Meta-analytic evidence that sexual selection improves population fitness'
 output:
   pdf_document: default
-subtitle: Response to Editorial Requests
+subtitle: Response to Editorial Requests and Reviewer 1
 bibliography: Manuscripts/Bibliography/Bibliography.bib
@@
   \item \textit{Please edit the title so that it is 15 words or fewer and does not include punctuation} \\
-  <!-- Sexual selection improves population fitness based on a systematic review and meta-analysis -->
   We have changed our title to: Meta-analytic evidence that sexual selection improves population fitness
@@
   \item \textit{The final paragraph of the Introduction should summarise the major results and conclusions of this manuscript, in the present tense.} \\
-  <!-- We had previously included this in an earlier draft and cut it. Can add it back  -->
+  We have now replaced our aims in the last paragraph of the last paragraph of the introduction with a summary of the major results and colnclusions of the study.
 
@@
   \item \textit{Please do not use italics or bold font to convey emphasis (in both the main text and the display items).} \\
-  Is this the latin? (e.g. /Prima facie / Tabbles have bold, figures have bold...)
+  We only use italics for latin words or abbreviations (\textit{e.g., i.e., Prima facie}) and not for emphasis.
 
   \item \textit{Please avoid using speech marks around words or phrases. In most cases they are unnecessary.} \\
-  Speech marks around the following words/phrases have now been removed: population fitness (l.21), purged (l.175), softer (l.199), harder (l.199), 'good genes' (l.243), attractive (l.244), unambiguous (l.359).
-
-  Single quotes for technical terms
+  Speech marks around the following words/phrases have now been removed: purged (l.175), softer (l.199), harder (l.199),  attractive (l.244), unambiguous (l.359).  \\
+  However, we have retained single quotation marks for the following terms as they recall technical terms: 'population fitness' (l.21), 'good genes' (l.243).
 
   \item \textit{Please make sure that mathematical terms throughout your manuscript and Supplementary Information (including in figures, figure axes, and legends) conform strictly to the guidelines} \\
-  Not sure where we went wrong here?
+  The mathematical and greek letter symbols (\textit{e.g.} $\beta$) are formatted as mathematical symbols in the submitted latex manuscript.
 
   \item \textit{Wherever p-values are stated in the text and figure legends, please also state the name of the statistical test.} \\
-  A couple of linear models in the publication bias section have p values without stating it is a linear regression.
-Otherwise we dont have that many p values and it is described in the table as from a multilevel meta-analysis model.
+  The p-values presented in the publication bias section now clearly state that they were obtained from a linear regression model.
+The p-values in Table 1 are clearly stated to be coming from a multilevel meta-analysis model with a corresponding z-value.
 
@@
 The Methods section must include subheadings of fewer than 60 characters including spaces.
-There is no word limit for the Methods section, so we recommend against splitting the methods description between the main text and Supplementary Information.}
-
-  All headings are under 60 characters in length, we have some additional Supp Methods in the Supp info but it is more or an appendage to the Supp tables and search terms (which would not nicely format in the main text)
+There is no word limit for the Methods section, so we recommend against splitting the methods description between the main text and Supplementary Information.} \\
+  All headings are under 60 characters in length, we have some additional Supplementary Methods in the Supplementary Information but it is an appendage to the Supplementary Tables 1-3 and search terms (which would not nicely format in the main text).
 
   \item \textit{Please rename the Methods section as "Methods".} \\
-
   Done
 
-  \item \textit{All Nature Communications manuscripts must include a section titled "Data Availability" as a separate section after the Methods section and before the References.}
+  \item \textit{All Nature Communications manuscripts must include a section titled "Data Availability" as a separate section after the Methods section and before the References.} \\
+  We have now ammended this section of the manuscript by seperating data availability and code availability as well as providing the relevent links to the data sources hosted on Github.
+
+  \item \textit{We strongly encourage authors to deposit all new data associated with the paper in a persistent repository where they can be freely and enduringly accessed.} \\
+  We have chosen to host our data on a Github repository alongside all our code and a neatly formatted html with supplementary information in an effort to maximise transparency of our analysis as well as allowing for the data and code to be easily reproduced and built upon by future studies.
+
+  \item \textit{For all studies developing new software or using custom code in the generation or processing of datasets, a statement must be included in the Methods section, under the subheading "Code Availability", indicating whether and how the code can be accessed, including any restrictions to access.
+This section should also include information on the versions of any software used, if relevant, and any specific variables or parameters used to generate, test, or process the current dataset.} \\
+  Done. The Supplementary Information has a section at the end with `R Session Information`, which provides details of the attached packages and parameters of the operating system.
+
+  \item \textit{Please add a reference to the source data file in the "Data Availability" section} \\
+  Done. The github repository now also contains a more extensive 'READ ME', with a description of the repository organisation.  
+  \item \textit{End notes} \\
+  Acknowledgements, Author Contributions and Competing Interests are now found after the references.
+
+  \item \textit{Please update any preprints in the reference list with details of the published paper, if possible.} \\
+  We have changed one reference that was a preprint and is now published (Li and Holman 2018).
+
+  \item \textit{Please check whether your manuscript or Supplementary Information contain third-party images, such as figures from the literature, stock photos, clip art or commercial satellite and map data.} \\
+  No third-party images are included in the display items.
+
+  \item \textit{Please include a brief title for all figure legends that summarises the whole figure and does not refer to specific panels and Please ensure that figure legend titles are brief - they should not occupy more than one line in the final proof.} \\
+  Figure titles are now included and illustrated in bold at the start of the figure legend. They do not occupy more than one line.
+
+  \item \textit{Please include figure legends of up to 350 words, referring to all panels within the figure.} \\
+  No figure legends are above 350 words and in all cases all panels are referred to in the legend.
+
+  \item \textit{Data in tables must be free from bold/italic formatting unless this has been clearly defined in the footnote.
+Tables need to be black and white, fit onto a single A4 portrait page and can contain only one row of column titles.
+Finally, we are unable to merge cells or include vertical dividing lines or diagonal lines.
+Please format your tables accordingly.} \\
+  Bolding in tables are now clearly defined in the footnotes, the tables are formatted in latex, contain one row of column titles and are in black and white.
+
+  \item \textit{Please ensure that table titles are brief - they should not occupy more than one line in the final proof.} \\
+  Done
+
+  \item \textit{Please define any new abbreviations, symbols or colours present in your figures in the associated legends.
+Please do not use symbols in your legend, instead please write out the symbols in words (blue circles, red dashed line, etc.)} \\
+  We include text descriptions in our figure legends. With figure 2 we have used an in-figure guide to allow the reader to easily distinguish the statistical approach used and the sex of the group.
+
+  \item \textit{In each figure and supplementary figure where error bars are used, they must be defined.
+One statement at the end of each figure is sufficient if the error bars are equivalent throughout the figure.} \\
+  Error bars are described in the figure legends for all appropriate figures (1,2,3).
+
+  \item \textit{The only section headings permitted in the Supplementary Information are Supplementary Figures, Supplementary Tables, Supplementary Methods (although this is discouraged), Supplementary Notes, Supplementary Discussion, Supplementary References.
+All other section headings and numbering should be removed or relabelled.} \\
+  We have a section with Supplementary Methods that details the search terms and inclusion/exclusion process.
+Because many of the Supplementary Tables are in reference to Supplementary Figures (i.e.
+contains the numerical values shown in the plot) we did not split Supplementary Figures and Supplementary Tables.
+
+  \item \textit{In the Supplementary Information file and the main manuscript text, supplementary items must be labelled and cited using only the following formats: Supplementary Figure 1, Supplementary Table 1, Supplementary Methods, Supplementary Note 1, Supplementary Discussion, and Supplementary References.
+Please note the use of "Supplementary" and that we do not use the "S" prefix.}\\
+  This has now been changed.
+
+  \item \textit{Please replace general citations to the Supplementary Information (e.g. "see Supplementary Information") with specific citations (e.g. "See Supplementary Figure 1", etc.).}
+  We have now updated the references to the Supplementary Information with specific tables/figures.
+Additionally, as per Prof.
+Jacek Radwan's comment "I hope supplementary figures will be linked to the main text, as it is somewhat difficult to find them by the number in the supplement deposited in a repository" we have created hyperlinks to the section of the Supplementary Information (the HTML version hosted on github) with the relevent table/figure.
+
+  \item \textit{Supplementary References should appear at the end of the Supplementary Information file, and should be self-contained and numbered from 1.
+References mentioned in both the main text and the Supplementary Information should be part of both reference lists so that the Supplementary Information does not refer to the reference list in the main paper and vice versa.}\\
+  The Supplementary References are formatted in the style of Nature Communications (numbered) and are seperate from the main manuscript.
+
+  \item\textit{Please supply Supplementary Software as a ZIP file and provide a legend for it in your cover letter (not in the Supplementary Information file).}\\
+  Not applicable for our manuscript.
+
+  \item \textit{Within the Source Data file, each figure or table (in the main manuscript and in the Supplementary Information) containing relevant data should be represented by a single sheet in an Excel document, or a single .txt file or other file type in a zipped folder.
+Blot and gel images should be pasted in and labelled with the relevant panel and identifying information such as the antibody used.}\\
+  Source data are formatted as a single csv file. Figures 1-3 now provide the url of the repository with the source data.
+
+  \item \textit{Nature Communications uses a transparent peer review system, where for manuscripts submitted from January 2016 we are publishing the reviewer comments to the authors and author rebuttal letters of our research articles online as a supplementary peer review file.
+Please indicate in your cover letter when submitting the final version of your manuscript whether you wish to opt out of this scheme or not.}\\
+  We are happy for peer reviews to be published.
+
+  \item \textit{An updated editorial policy checklist that verifies compliance with all required editorial policies must be completed and uploaded with the revised manuscript.
+All points on the policy checklist must be addressed; if needed, please revise your manuscript in response to these points.
+Please note that this form is a dynamic "smart pdf" and must therefore be downloaded and completed in Adobe Reader, instead of opening it in a web browser.
+Editorial policy checklist: https://www.nature.com/authors/policies/Policy.pdf} \\
+  We provide an updated copy of this checklist.
+
+  \item \textit{An updated reporting summary must be completed and uploaded with the revised manuscript.
+All points on the reporting summary must be addressed; if needed, please revise your manuscript in response to these points.
+Please note that this form is a dynamic ""smart pdf"" and must therefore be downloaded and completed in Adobe Reader, instead of opening it in a web browser.
+Reporting summary: https://www.nature.com/authors/policies/ReportingSummary.pdf} \\
+  We provide an updated copy of this reporting summary.
+
+  \item \textit{Your paper will be accompanied by a two-sentence Editor's summary, of between 250-300 characters including spaces, when it is published on our homepage.
+Could you please approve the draft summary below or provide us with a suitably edited version.
+\\"Sexual selection has the potential to either increase or decrease absolute fitness.
+Here, Cally et al.
+perform a meta-analysis of 65 experimental evolution studies and find that sexual selection on males tends to increase fitness, especially in females and under stressful conditions."} \\
+We wish to make a small change to the last sentence of the above summary:
+
+"Sexual selection has the potential to either increase or decrease absolute fitness.
+Here, Cally et al.
+perform a meta-analysis of 65 experimental evolution studies and find that sexual selection on males tends to increase fitness, especially in females evolving under stressful conditions."
+
+  \item \textit{As part of our efforts to communicate our content to a wider audience, we endeavour to highlight papers published in Nature Communications on the journal’s Twitter account (@NatureComms).
+If you would like us to mention authors, institutions or lab groups in these tweets, please provide the relevant twitter handles in your cover letter upon resubmission.}\\
+  Luke and my handles are now included in the cover letter.
+
+  \item \textit{If you opted into the journal hosting details of a preprint version of your manuscript via a link on our dedicated website (https://nature-research-under-consideration.nature.com), it will remain on this site while you are revising your manuscript, as we consider the file to remain active.
+Should you wish to remove these details, please email naturecommunications@nature.com indicating your manuscript number and the link on our website that was previously sent to you.
+Please see our pre-publicity policy at http://www.nature.com/authors/policies/confidentiality.html For more information, please refer to our FAQ page at https://nature-research-under-consideration.nature.com/posts/19641-frequently-asked-questions} \\
+  Not applicable to our manuscript.
 
@@
 ## Response to Prof. Jacek Radwan
+
+\begin{enumerate}
+  \item \textit{The authors made a good effort to address my concerns.
+In particular, they now report a separate analysis addressing the effect of sexual selection manipulation on traits with direct effect on population fitness, which is the most relevant analysis for the question being asked.
+This effect has proved ambiguous (significant with REML, but with 95\%Cis overlapping zero with Bayesian analysis), which, coupled with some evidence for publication bias (lines 147-151) , makes the main conclusion of positive effect of selection on population fitness rather tentative.
+This interpretational uncertainty, however, is not properly reflected in the revised manuscript, eg.
+in the abstract (l.
+12-13 ) and discussion (172-175; 249-251).
+Furthermore, recommendations for conservation biology seem premature in this context.}\\
+  We have modified the title and abstract of the paper, and made it clear which conclusions are supported unambiguously and which are more tentative. For example…. [provide a quote or two].
+
+  \item \textit{Sorry for not being clear with my point on random slopes, I meant the first option the authors identified, but (as I already indicated in my original review) I appreciate that dataset at hand may make this difficult.
+I’m OK with the way this comment was taken into account.}\\
+  We are glad that the reviewer found the modifications we made satisfactory.
+
+  \item \textit{I appreciate the added text explaining that stronger response in females is counterintuitive (l.
+195-222).
+However, it is still not clear what the authors mean to say about the nature of selection on females.
+I can see two options (which the authors also identify in their response to my question) (i) stronger correlated response in females to selection on males, compared to response in males themselves and (ii) direct effect of sexual selection manipulation on female fitness, e.g.
+due to increased male harassment.
+These two mechanisms should be clearly separated and discussed, they can have different consequences for interpretations of the results, but also on recommendations about allowing for “good genes” sexual selection in endangered species (eg.
+line 243).}\\
+  We agree that this section of the discussion can be clearer and have modified the two paragraphs in question.
+
+The section in questions rests upon the fundamental premise that the response to selection depends on A) genetic variance, and B) the strength of selection.
+This fact is captured in the Breeder’s equation, $R = h^2s$, where $R$ is the response to selection, $h^2$ is the narrow-sense heritability of the trait, and s is the selection differential.
+Because females responded more strongly than males did (bigger $R$ for females), our argument is that $h^2$ and/or $s$ must be bigger for females.
+We then list a number of mechanisms that might make $h^2$ or $s$ bigger for females.
+
+Here are the revised paragraphs:
+
+\subsection {Other Comments}
+
+  \item \textit{l.
+21: I wonder if defining population fitness as an average (presumably in both sexes) makes sense?
+As the authors state later in abstract, what really matters is fitness of demographically-limiting sex (and the traits which affect the demography).}\\
+  We have not made a change here, for two reasons.
+
+Firstly, it usually makes no difference if one thinks of population fitness as an average across all the females, or an average across both sexes.
+This is because the average fitness of males is always equal to the average fitness of females, assuming the population has obligate sexual reproduction and a 50:50 primary sex ratio (as most species in our meta-analysis do), because every offspring has one genetic mother and one genetic father.
+For example, if the average fitness across all the females is 1.1, the average fitness of all the males must be 1.1 as well, so one gets the same answer when averaging over females only, or the whole population.
+
+Secondly, ‘population fitness’ has a prominent technical definition that has been used by eminent figures in population geneticists (e.g.
+Wright, Fisher and Kimura), i.e.
+the average across the whole population.
+However, many of these classic models implicitly ignored males (e.g.
+by assuming isogamous sexual reproduction) for reasons of mathematical tractability.
+Later ecological and evolutionary models have incorporated the sexes explicitly, and unsurprisingly found that adaptation in males and females has different effects on the growth rate of the population (confusingly, the growth rate of the population is also called ‘population fitness’ by many ecologists).
+We believe that a clear, inclusive, and universally satisfying definition of population fitness is currently missing, but it is beyond the scope of this paper – instead, we use the standard definition.
+
+\end{enumerate}

### 2019-03-15 Manuscripts/Manuscript_MetaAnalysis.Rmd
Updates on response to editorial requests

@@
 ---
-title: '\huge{Sexual selection improves population fitness: a systematic review and meta-analysis}'
+title: '\huge{Meta-analytic evidence that sexual selection improves population fitness}'
 author: 
@@
 subparagraph: yes
+urlcolor: blue
 csl: Bibliography/NComms.csl
@@
     \usepackage{titlesec} \titleformat{\section}{\normalfont\scshape\LARGE}{\thesection}{1em}{} \titleformat{\subsection}{\normalfont\Large}{\thesubsection}{1em}{} \titleformat{\subsubsection}{\normalfont\large}{\thesubsubsection}{1em}{} \usepackage{abstract} \renewcommand{\abstractnamefont}{\normalfont\Large}
-    \usepackage{hyperref}\hypersetup{colorlinks=false, linkcolor=blue, filecolor=blue, urlcolor=blue} 
+    \usepackage{hyperref}\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue} 
     \usepackage{color,soul}
@@
 Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis.
-We find that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females, and for populations evolving under stressful conditions.
+We find that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females evolving under stressful conditions.
 We conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
@@
 We focus exclusively on experimental evolution studies that manipulated the presence or strength of sexual selection on males, and then measured some fitness component, since experiments provide a particularly strong test of the hypothesis that sexual selection affects the average fitness of populations.
-Our principle aims were to measure the average net effect of sexual selection on the population-level mean and variance for various fitness components, to test whether this effect varies between stressful and benign environments, and identify key moderators of the effect size of sexual selection treatment.
+We find that sexual selection tends to improve population fitness; especially when fitness components were measured in females experiencing stressful rather than benign conditions.
+Additionally, we show that sexual selection tends to narrow phenotypic variance of fitness-related traits for females and mixed-sex samples in stressful conditions.
+These results suggest that sexual selection may be especially important for populations adapting to changing environments.
 \phantomsection
@@
 In total, we obtained effect sizes for 22 different fitness traits, with female reproductive success ($n$ = 102) and offspring viability ($n$ = 56) being the most commonly-measured traits.
-We classified 171 effect sizes as direct measures of population fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
+We classified 171 effect sizes as direct measures of population fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Supplementary Table 1}).
 Specifically, we scored traits that are likely to correlate with population growth and persistence as direct (*e.g.*, female reproductive success, offspring viability, and extinction rate), those which are not necessarily correlated with population fitness but which do measure individual fitness as indirect (*e.g.*, lifespan, male mating success and ejaculate quality/production); and those for which the relationship to population fitness is unclear as ambiguous (*e.g.*, body size, mating duration, male reproductive success, and early fecundity).
-\href{https://justincally.github.io/SexualSelection/#tables_of_sample_sizes}{Tables S4-S5} give a detailed description of our dataset.\phantomsection
+\href{https://justincally.github.io/SexualSelection/#tables_of_sample_sizes}{Supplementary Tables 3,4} give a detailed description of our dataset.\phantomsection
 
@@
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
-Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S6}).
+Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_on_direct,_indirect_and_ambiguous_measures_of_fitness}{Supplementary Table 6}).
 Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.21, 95% CIs: 0.058 to 0.093; Bayesian $\beta$ = 0.20, 95% CIs: -0.0016 to	0.39, $BF_{>0}$ = 38, $n$ = 144) and an indirect relationship to fitness (REML $\beta$ = 0.24, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.033 to 0.43, $BF_{>0}$ = 59, $n$ = 141).
 Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174).
-A large forest plot with predicted effect sizes for each fitness component is presented in Figure S1 and further detailed with model predictions and individual meta-analyses in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Table S8 and S9}.
+A large forest plot with predicted effect sizes for each fitness component is presented in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Figure 1} and further detailed with model predictions and individual meta-analyses in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Table 8,9}.
 Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).
@@
 
-We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect the relationship between sexual selection and fitness (\hyperlink{page.18}{Table 1, 2}).
-Sexual selection on males significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
-Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, \hyperlink{page.18}{Table 2}).
-Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (\autoref{env_sex}a, \hyperlink{page.13}{Table 2}).
+We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect the relationship between sexual selection and fitness (Table 1,2).
+Sexual selection on males significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, Table 2).
+Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, Table 2).
+Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (\autoref{env_sex}a, Table 2).
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
-When we used an alternative measure of effect size (log response ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (Figure S3 and Table S16).
+When we used an alternative measure of effect size (log response ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (\href{https://justincally.github.io/SexualSelection/#meta-analysis_using_lnrr}{Supplementary Figure 4 and Supplementary Table 16}).
 
-Other moderator variables that we examined had minimal impacts on effect size (\href{https://justincally.github.io/SexualSelection/#meta-analyses_including_many_moderator_variables}{Figure S2, Table S10}).
-Specifically, effect size did not depend on whether or not the study was conducted blind (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S6}), nor on the number of generations for which the experimental evolution study was run (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Figure S7, S8}).
+Other moderator variables that we examined had minimal impacts on effect size (\href{https://justincally.github.io/SexualSelection/#meta-analyses_including_many_moderator_variables}{Supplementary Table 9}).
+Specifically, effect size did not depend on whether or not the study was conducted blind (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Supplementary Figure 7}), nor on the number of generations for which the experimental evolution study was run (\href{https://justincally.github.io/SexualSelection/#other_moderators}{Supplementary Figure 8,9}).
 
@@
 Heterogeneity stemmed mostly from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%) rather than differences between fitness components and taxon ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%, 95% CIs: 0.2% to 3.5%).
-Variation among taxa is explored further in the ESM (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_to_just_the_higher-quality_data}{Figure S2, Table S11}).
+Variation among taxa is explored further in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_of_just_the_higher-quality_data}{Supplementary Figure 2, Supplementary Table 10}).
 \phantomsection
@@
 Specifically, phenotypic variance was significantly reduced by sexual selection for fitness components measured in females under stressful conditions (*lnCVR* = -0.78, 95% CIs: -1.23 to -0.34, $n$ = 27).
-By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (\autoref{env_sex}b; \href{https://justincally.github.io/SexualSelection/#obtaining_lncvr_and_meta-analysis_models}{Tables S13-S16}).
+By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (\autoref{env_sex}b; \href{https://justincally.github.io/SexualSelection/#meta-analysis_on_variance}{Supplementary Tables 17-20}).
 However, similar to the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.76, 95% CIs: -1.22 to -0.31; \autoref{env_sex}b).
-A meta-analysis using the log variability ratio (lnVR), which does not account for the mean-variance relationship present in the dataset (Figure S4), suggested sexual selection reduces variance for mixed-sex samples in stressful conditions, but not females, results of this meta-analysis can be found in the Supplementary Material (Figure S5 and Table S21).
+A meta-analysis using the log variability ratio (lnVR), which does not account for the mean-variance relationship present in the dataset (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 5}), suggested sexual selection reduces variance for mixed-sex samples in stressful conditions, but not females, results of this meta-analysis can be found in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 6 and Supplementary Table 21}).
 
@@
 Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection (though funnel plots are not a decisive evidence of publication bias[@RN215]).
-There was no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.23) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.2, $p$ = 0.24); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
+Linear regressions show no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.23) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.2, $p$ = 0.24); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
 
@@
 The results of the meta-analysis support predictions that sexual selection on males can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
-Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been 'purged' of deleterious alleles through sexual selection on males [@RN94; @RN198; @RN95].
+Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been purged of deleterious alleles through sexual selection on males [@RN94; @RN198; @RN95].
 What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest).
@@
 This explanation may initially seem implausible, because net selection on males is generally assumed to be stronger than on females, due to (actual or hypothesised) sex differences in sexual selection and inter-individual variance in fitness [@RN304; @RN303; @RN337; @RN338].
-However, an oft-overlooked aspect is that selection might frequently be ‘softer’ on males and ‘harder’ on females [@RN319], because the local competitive environment is usually more important for males than it is for females.
+However, an oft-overlooked aspect is that selection might frequently be softer on males and harder on females [@RN319], because the local competitive environment is usually more important for males than it is for females.
 For instance, a mediocre male genotype can have high fitness provided it outcompetes its local rivals, while low-fitness female genotypes are likely to produce few offspring even when competing with other low-fitness females.
@@
 Within captive breeding programs, genetic diversity is often managed through the enforced monogamy of a strategically selected (genetically diverse) breeding pair [@RN117].
-Captive breeding programs may benefit from allowing sexual selection of 'good genes' or more compatible genes [@RN294], or by increasing maternal investment by females paired with 'attractive' males [@RN291; @RN292; @RN293].
+Captive breeding programs may benefit from allowing sexual selection of 'good genes' or more compatible genes [@RN294], or by increasing maternal investment by females paired with attractive males [@RN291; @RN292; @RN293].
 Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution, could reduce the genetic quality of the population, and potentially compromise its long-term persistence [@RN332; @RN331; @RN47; @RN333; @RN330].
@@
 We searched *ISI Web of Science* and *Scopus* on 9^th^ June 2017 for peer-reviewed, English language studies that manipulated the presence or strength of sexual selection using experimental evolution, and then measured some proxy of population fitness.
-A detailed list of search terms is given in the Electronic Supplementary Material (\href{https://justincally.github.io/SexualSelection/}{ESM}).
+A detailed list of search terms is given in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/}{see Supplementary Methods}).
 
@@
 We therefore relied on our best judgement when deciding what outcomes were correlated with population fitness.
-We categorised the fitness outcomes into three categories: ambiguous, indirect and direct (detailed in \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S1}).
+We categorised the fitness outcomes into three categories: ambiguous, indirect and direct (detailed in \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Supplementary Table 1}).
 Briefly, ambiguous measures of fitness were those that are reported to have an unclear or variable association with fitness (*e.g.*, body size, mating duration, early fecundity and male reproductive success).
@@
 Finally, direct measures of fitness (female/mixed sex reproductive success, offspring viability and extinction rate) are those that measure fitness through components of reproduction or long-term viability.
-The ESM describes why each of the 130 papers was included or excluded (\href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Table S2}).
+The Supplementary Methods describe why each of the 130 papers was included or excluded (\href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Supplementary Table 2}).
 
@@
 
-In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see \href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{Table S3} and associated ESM).
+In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see \href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{the source data} and associated Supplementary Information).
 The moderators were selected due to their ready availability, and because we hypothesised that they might explain some of the observed heterogeneity in effect size.
@@
 Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), the presence/absence of blind methodology, and number of generations a treatment group underwent experimental evolution.
-In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the ESM (\href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{Table S3}).
+In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{the source data}).
 \phantomsection
@@
 For the meta-analysis testing whether sexual selection affects phenotypic variance (as opposed to the mean), we estimated the difference in variance between each pair of treatments using the natural logarithm of the ratio between the coefficient of variation for each group (termed *lnCVR*) [@RN177]: $ln(CVfitness_{SS\ high}/CVfitness_{SS\ low})$.
-The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (Figure S4).
+The use of _lnCVR_ allows us to determine the effects of sexual selection on phenotypic variance, with the coefficient of variation implicitly controlling for the mean-variance relationship seen in the dataset (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 5}).
 As a supplement, we also calculated the natural logarithm of the absolute ratio between the absolute variation for each group (_lnVR_) in order to assess the impact of sexual selection on trait variance, irrespective of their magnitudes [@RN177].
@@
 These models were were intercept only REML models with study and taxon as group-level effects.
-Further details on model parameters can be found within the ESM.
+Further details on model parameters can be found by accessing the \href{https://justincally.github.io/SexualSelection/#meta-analysis}{``R`` code}.
 
-Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g*, *lnRR*, *lnCVR* and *lnVR* in the ESM) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
-These meta-analyses were restricted to effect sizes calculated from ‘unambiguous’ outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g*: *n* = 330; *lnRR*, *lnCVR* & *lnVR*: *n* = 269).
+Thirdly, we measured the impact of environment, sex and their interaction on the effect size (Hedges’ *g*, *lnRR*, *lnCVR* and *lnVR* ) associated with the manipulation of sexual selection, by fitting these predictors as moderators in a pair of separate mixed-effects meta-analyses.
+These meta-analyses were restricted to effect sizes calculated from unambiguous outcomes (*i.e.* those scored as being directly or indirectly related to population fitness), as well as those where we were able to define the environmental conditions as either stressful or benign (Hedges' *g*: *n* = 330; *lnRR*, *lnCVR* & *lnVR*: *n* = 269).
 We again fit study ID, fitness component, and taxon as random/group level effects.
-Models investigating other moderators such as number of generations and blinding are presented in the \href{https://justincally.github.io/SexualSelection/}{ESM}.
+Models investigating other moderators such as number of generations and blinding are presented in  \href{https://justincally.github.io/SexualSelection/#meta-analyses_including_many_moderator_variables}{Supplementary Table 9}.
 
@@
 The code used to perform this meta-analysis is freely available on Github (https://justincally.github.io/SexualSelection/).
-Here the code is available through a neatly compiled html, with the R Markdown file found within the corresponding github repository:  (https://github.com/JustinCally/SexualSelection).
+Here the code is available through a neatly compiled html, with the R Markdown file found within the corresponding Github repository:  (https://github.com/JustinCally/SexualSelection).
 \phantomsection
@@
 
-#Tables and Figures
+#Tables and Figure Legends
 
@@
       caption = "Multilevel meta-analysis model results") %>% 
-  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
+  kable_styling(latex_options = c("hold_position"), full_width = F) %>%
   row_spec(0, bold = TRUE) %>%
@@
 The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line.
-Predictions from both Bayesian and REML models can be found in Table S7).\label{forest_plot}](Figures/forest.plot.class.pdf)
+Predictions from both Bayesian and REML models can be found in Supplementary Table 6 and source data are provided at \url{https://github.com/JustinCally/SexualSelection}.\label{forest_plot}](Figures/forest.plot.class.pdf)
 
@@
 (b) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals.
-The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Table S12 and S14).
-Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.\label{env_sex}](Figures/environment_variance_edit5.pdf)
+The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Supplementary Tables 14,18).
+Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.
+Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.\label{env_sex}](Figures/environment_variance_edit5.pdf)
 
@@
 For (b) and (c) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance).
-For (a), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99 % CIs for the dataset.
-The Grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.\label{publication_bias}](Figures/publicationbias.pdf)
+For (a), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99.8 % CIs for the dataset.
+The Grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.
+Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.\label{publication_bias}](Figures/publicationbias.pdf)
 

### 2019-03-15 meta_analysis_sexual_selection_pop_fitness.Rmd
Updates on response to editorial requests

@@
 ---
-title: 'Sexual selection improves population fitness: a systematic review and meta-analysis'
+title: 'Meta-analytic evidence that sexual selection improves population fitness'
 author: "Justin G. Cally^1^, Devi Stuart-Fox^1^ and Luke Holman^1^ <br></br> <br></br> ^1^The University of Melbourne"
-subtitle: Supplementary Material
+subtitle: Supplementary Information
 bibliography: bibliography_meta_analysis.bib
@@
 Criterion 4 is somewhat subjective, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness.
-We therefore relied on our best judgement when deciding which studies to exclude (see **Table S1**).
-The inclusion/exlusion critera as applied to each study are detailed in **Table S2**.
-
-**Table S1:** We classified each of the twenty fitness outcomes into three broad groups -- direct, indirect and ambiguous -- based on the established link with population fitness, the directionality of the measure.
+We therefore relied on our best judgement when deciding which studies to exclude (see **Supplementary Table 1**).
+The inclusion/exlusion critera as applied to each study are detailed in **Supplementary Table 2**.
+
+**Supplementary Table 1:** We classified each of the twenty fitness outcomes into three broad groups -- direct, indirect and ambiguous -- based on the established link with population fitness, the directionality of the measure.
 Here we detailed how these outcomes were measured in the primary studies.
@@
 
-#### References for Table S1
+#### References for Supplementary Table 1
 ```{r, warning=FALSE}
@@
 
-**Table S2:** A study was deemed eligible for inclusion in the meta-analysis if it met all four criteria discussed above (referred to by their numbers, 1-4, in this table).
+**Supplementary Table 2:** A study was deemed eligible for inclusion in the meta-analysis if it met all four criteria discussed above (referred to by their numbers, 1-4, in this table).
 We went through these four criteria in a step-wise fashion, for each of the 130 studies for which we read the full text, and noted the first criterion that was failed (if any).
@@
 
-4. We also collected various covariates for some of the studies (**Table S3**), which are discussed later.
+4. We also collected various covariates for some of the studies (**see source data**), which are discussed later.
 
@@
 
-**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
+**Source Data:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
  <br/><br/> 
@@
 **Outcome**: The fitness related outcome that was measured, e.g.
-fecundity, survival, or mating success (see Table S1 for all 20 categories).
+fecundity, survival, or mating success (see Supplementary Table 1 for all 20 categories).
 We applied our own classifications rather than relying on those provided by the authors, because different papers sometimes used different names for the same trait.
 
-**Outcome Class**: To help guide analysis the outcomes were classed into three categories; ambiguous, indirect and direct (see Table S1).
+**Outcome Class**: To help guide analysis the outcomes were classed into three categories; ambiguous, indirect and direct (see Supplementary Table 1).
 
@@
 
-**Table S4:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
+**Supplementary Table 3:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
 ```{r message=FALSE, warning=FALSE}
@@
 
-**Table S5:** Table of fitness outcomes included in our meta-analysis by sex.
+**Supplementary Table 4:** Table of fitness outcomes included in our meta-analysis by sex.
 ```{r}
@@
 
-**Table S6**
+**Supplementary Table 5:**
 These estimates are presented in the text of the Results section. The test statistic is either the p-value (REML) or Bayes factor (BF) comparing the effect size to zero (Bayesian).
@@
 
-**Table S7** The predicted effect size for each of the three fitness trait classes (Ambiguous, Indirect and Direct) that are presented in Figure 1 in the manuscript.
+**Supplementary Table 6:** The predicted effect size for each of the three fitness trait classes (Ambiguous, Indirect and Direct) that are presented in Figure 1 in the manuscript.
 This table presents both Bayesian and REML predictions with some discrepencies in the estimated error margins.
@@
 
-**Figure 1** The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness.
+**Figure 1:** The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness.
 Overall, effect sizes were more often positive than negative.
@@
 The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line.
-Predictions from both Bayesian and REML models can be found in Table S7.
+Predictions from both Bayesian and REML models can be found in Supplementary Table 6.
 
@@
 
-**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
+**Supplementary Figure 1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together).
 Rows with multiple data points denote studies that provided multiple effect sizes.
@@
 
-**Table S8** Summary of model predictions for 22 fitness components.
-In Figure S1 these values are presented as a text overlay using the Bayesian values.
+**Supplementary Table 7:** Summary of model predictions for 22 fitness components.
+In Supplementary Figure 1 these values are presented as a text overlay using the Bayesian values.
 Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0.
@@
 left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component") %>% pander(split.table = Inf, digits = 2)
-```
-
-**Table S9** In some instances it may be beneficial to the reader to obtain average effect sizes of each fitness trait **entirely independently** of other traits.
+
+# saveRDS(left_join(fitness.component.predictions, predictions.outcomes, by = "Fitness Component"), "PDF_RDS_files/ST7.rds")
+```
+
+**Supplementary Table 8:** In some instances it may be beneficial to the reader to obtain average effect sizes of each fitness trait **entirely independently** of other traits.
 For this reason we present a summary of independent model estimates for 16 fitness components with a sample size greater than 3 effect sizes (n>3).
@@
 outcome.frame %>% rename(beta = b, n = k) %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)
+
+# saveRDS(outcome.frame %>% rename(beta = b, n = k) %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength"), "PDF_RDS_files/ST8.rds")
 ```
@@
 
-**Table S10:** Bayesian model results for a preliminary model that explores many covariates collected in the dataset.
+**Supplementary Table 9:** Bayesian model results for a preliminary model that explores many covariates collected in the dataset.
 
@@
 We also focus on the model containing the fixed effects Sex, Environment, Taxon and the interaction between sex and environment, as these are key to our research question.
-
-<!-- Note to Justin: here, I changed to just the 'direct' measures, and added the "Enforced Monogamy" predictor.
-You'll need to add the Bayesian equivalent, and alter the code for the figure etc.
-I think it's better this way, and the results don't appear to change in any major way -->
 
@@
 
-#ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.svg", height = 8, width = 8)
+#ggsave(plot = Taxon.metaanlysis, filename = "PDF_RDS_files/SF2.pdf", height = 8, width = 8)
 Taxon.metaanlysis
+
+#saveRDS(Taxon.metaanlysis, "PDF_RDS_files/SF2.rds")
 ```
 <br></br>
-**Figure S2:** The predictions from this model indicate some heterogeneity between taxon.
+**Supplementary Figure 2:** The predictions from this model indicate some heterogeneity between taxon.
 However, the most apparent difference between taxa is that confidence bands increase for taxa with low sample size.
@@
 
-**Table S11** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.
+**Supplementary Table 10:** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.
 
@@
 predictions.complete %>% pander()
-```
-
-Given that none of the levels of `Taxon` have a particularly strong impact on effect size, and many categories are incompletely sampled with regards to Sex and Environment (Table S11), we elected to treat `Taxon` as a random/group level effect in all subsequent models.
+
+#saveRDS(predictions.complete, "PDF_RDS_files/ST10.rds")
+```
+
+Given that none of the levels of `Taxon` have a particularly strong impact on effect size, and many categories are incompletely sampled with regards to Sex and Environment (Supplementary Table 10), we elected to treat `Taxon` as a random/group level effect in all subsequent models.
 
@@
 
-**Table S12** Using the ``anova.rma`` function we can conduct hypothesis tests between two categorical groups in the model.
+**Supplementary Table 11:** Using the ``anova.rma`` function we can conduct hypothesis tests between two categorical groups in the model.
 Here we conduct 5 tests comparing the relative effect of sexual selection between the sexes, and in different environments.
@@
 anova.frame %>% pander(split.table = Inf)
+
+#saveRDS(anova.frame, "PDF_RDS_files/ST11.rds")
 ```
@@
 
-**Table S13** Model estimate summary table for the Bayesian model investigating the effect of environment and sex (alongside sexual selection) on fitness. 
+**Supplementary Table 12:** Model estimate summary table for the Bayesian model investigating the effect of environment and sex (alongside sexual selection) on fitness. 
 ```{r}
@@
 
-**Table S14** Hypothesis tests for the Bayesian model are similar to the REML model (Table S9), with slight differences to CIs.
+**Supplementary Table 13:** Hypothesis tests for the Bayesian model are similar to the REML model (Supplementary Table 8), with slight differences to CIs.
+
 ```{r}
@@
 
-**Table S15** The REML predictions in the plot above use the following dataframe
+**Supplementary Table 14:** The REML predictions in the plot above use the following dataframe
+
 ```{r}
@@
 predictions.complete2 %>% pander()
+
+#saveRDS(predictions.complete2, "PDF_RDS_files/ST14.rds")
+```
+
+##Effects of environment and sex on direct fitness components
+
+```{r, warning=FALSE, message=FALSE, error = FALSE, fig.align='center', fig.width = 10, fig.height=6}
+model.direct.only <- rma.mv(g, V = var.g, 
+                          mods = ~ 1 + Sex * Environment, 
+                          random = list(~ 1 | Study.ID, 
+                                       ~ 1 | Outcome,
+                                       ~ 1 | Taxon), 
+                          method = "REML", 
+                          data = strict_dataset %>% filter(Outcome.Class == "Direct"))
+
+#Generate predictions without taxon utilising the previously described function
+get.predictions.direct <- function(newdata){
+  B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0
+  if(newdata[1] == "B") B<-1 
+  if(newdata[1] == "F") F<-1 
+  if(newdata[2] == "Stressed") Stressed<-1
+  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
+  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1
+
+  predict(model.direct.only, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2))
+}
+
+# Get the predictions for each combination of moderators
+predictions.direct <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
+                           Environment = c("Unstressed", "Stressed")))
+predictions.direct <- cbind(predictions.direct, do.call("rbind", apply(predictions.direct, 1, get.predictions.direct))) %>%
+  select(Sex, Environment, pred, se, ci.lb, ci.ub) 
+for(i in 3:6) predictions.direct[,i] <- unlist(predictions.direct[,i])
+
+countpred <- count_(strict_dataset %>% filter(Outcome.Class == "Direct"), c("Sex", "Environment"))
+
+predictions.direct <- left_join(predictions.direct, countpred, by = c("Sex", "Environment"))
+colnames(predictions.direct) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
+predictions.direct <- predictions.direct %>%
+      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
+         Sex = replace(Sex, Sex == "M", "Male"),
+         Sex = replace(Sex, Sex == "F", "Female"),
+         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
+         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
+         Sex = factor(Sex, levels = c("Male", "Both", "Female")))
+
+predictions.direct <- format(predictions.direct, digits = 2)
+predictions.direct$Prediction = as.numeric(predictions.direct$Prediction)
+predictions.direct$CI.lb = as.numeric(predictions.direct$CI.lb)
+predictions.direct$CI.ub = as.numeric(predictions.direct$CI.ub)
+predictions.direct$n = as.numeric(predictions.direct$n)
+
+if(!file.exists("data/brms.direct.rds")){
+  brms.direct <- brm(g | se(SE)  ~ 1 + Sex * Environment 
+                        + (1|Taxon) 
+                        + (1|Study.ID) 
+                        + (1|Outcome), 
+                        family = "gaussian", 
+                        seed = 1,
+                        cores = 4, chains = 4, iter = 4000, 
+                        control = list(adapt_delta = 0.9999, max_treedepth = 15),
+                        data = strict_dataset %>% 
+                          filter(Outcome.Class == "Direct") %>% 
+                          mutate(SE = sqrt(var.g)))
+  saveRDS(brms.direct, file = "data/brms.direct.rds")
+}
+brms.direct <- readRDS(file = "data/brms.direct.rds")
+
+# lternatively you can obtain posterior samples manually.
+post.direct <- (posterior_samples(brms.direct, 
+                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
+                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
+                                    "b_SexF:EnvironmentStressed")) %>%
+           mutate(both_benign = b_Intercept + b_SexB,
+                  both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed`,
+                  male_benign = b_Intercept,
+                  male_stressful = b_Intercept + b_EnvironmentStressed,
+                  female_benign = b_Intercept + b_SexF,
+                  female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed`))[,-(1:6)]
+
+# Add columns for Environment and Sex
+post.direct <- as.data.frame(t(post.direct))
+post.direct$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
+post.direct$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")
+
+#Clean up dataframe
+post.direct <- melt(post.direct, id = c("Sex", "Environment"))
+post.direct$variable <- NULL
+
+#Plot the posterior values from the Bayesian model as density ridges
+pd <- position_dodgev(height = 0.3)
+posterior.direct.plot <- post.direct %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>% ggplot()+
+  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.65, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
+  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
+  ylab("Environment\n")+
+  xlab("\nEffect Size (Hedges' g)")+
+  # scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  # scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
+  scale_fill_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+  scale_color_manual(values = c("Male" = "#ff7f00", "Female" = "#984ea3", "Both" = "#4daf4a"))+
+  scale_x_continuous(limits = c(-1.25, 1.25), breaks = c(-1, -.5, 0, 0.5, 1))+
+
+  theme_bw()+
+
+  theme(panel.spacing = unit(0.1, "lines"),
+        text = element_text(size=16),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.text = element_text(size=16), 
+        legend.title=element_text(size=16, face = "bold"),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+        axis.title.y = element_text(size = 16, hjust = 0.35, margin = margin(r=-10)),
+        axis.text.y = element_text(angle = 0),
+        plot.title = element_text(size = 16))
+
+#Add the REML predictions as circles with error bars
+both.direct.plots <- posterior.direct.plot + 
+  geom_errorbarh(data = predictions.direct %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+                 aes(xmin = predictions.direct$CI.lb,
+                     xmax = predictions.direct$CI.ub, y = Environment,
+                     color = Sex), 
+                 height = 0, show.legend = F, position = pd)+
+
+  geom_point(data = predictions.direct %>% mutate(Sex = factor(Sex, levels = c("Male", "Both", "Female"))), 
+             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
+             shape=21, color = "grey20", position = pd) +
+
+    guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
+    scale_size(guide = 'none')+
+
+  scale_y_discrete(expand=c(0.075, 0))
+
+#pdf("PDF_RDS_files/SF3.pdf", width = 10, height = 6)
+grid.arrange(both.plots + 
+               guides(fill = FALSE)+
+               ggtitle("Indirect And Direct\n")+ theme(plot.title = element_text(size = 18, face = "bold", colour = "Red")),
+             both.direct.plots + ggtitle("Direct Only\n")+
+               theme(axis.title.y = element_blank(), 
+                     plot.title = element_text(size = 18, face = "bold", colour = "Red")), 
+             nrow = 1, 
+             widths = c(3,3.5))
+#dev.off
+```
+
+**Supplementary Figure 3:** The comparison of model predictions between models that use a dataset compiled from direct **and** indirect fitness components against a model that only uses direct fitness components.
+Notably, in both cases there is a significant positive effect of sexual selection on fitness for females evolving in stressful conditions.
+Bayesian predictions are depicted by a density curve while REML predictions are depicted with a circle (size corresponds to _n_) and 95 % CIs.
+
+**Supplementary Table 15:** The REML predictions for the 'direct model' in the plot above use the following dataframe.
+
+```{r, warning=FALSE}
+predictions.direct %>% pander()
+
+#saveRDS(predictions.direct, "PDF_RDS_files/ST15.rds")
 ```
@@
 
-###Estimating Hedges' g Heterogeneity Using _I^2^_
+###Estimating Hedges' g heterogeneity using _I^2^_
 
@@
 
+#pdf("PDF_RDS_files/SF4.pdf", width = 6, height = 6)
 lnRR.plots
-```
-
-**Figure S3:** Using an alternative effect size (lnRR) sexual selection also increases population fitness.
+#dev.off()
+```
+
+**Supplementary Figure 4:** Using an alternative effect size (lnRR) sexual selection also increases population fitness.
 Circle size is proportional to sample size (shown below).
@@
 
-**Table S16** The REML predictions for the meta-analysis using lnRR (plotted above) are formulated from the following model and predictions.
+**Supplementary Table 16:** The REML predictions for the meta-analysis using lnRR (plotted above) are formulated from the following model and predictions.
 
@@
 predictions.lnRR %>% pander()
+
+#saveRDS(predictions.lnRR, "PDF_RDS_files/ST16.rds")
 ```
@@
 
-**Table S17** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
+**Supplementary Table 17:** Model estimates, including random effect sigma value for the model of phenotypic variance (lnCVR)
 ```{r}
@@
 
-**Table S18** The REML predictions in the plot above use the following dataframe.
+**Supplementary Table 18:** The REML predictions in the plot above use the following dataframe.
 ```{r}
@@
 predictions.variance %>% pander(digits = 2)
+
+#saveRDS(predictions.variance, "PDF_RDS_files/ST18.rds")
 ```
@@
 
-**Table S19** Bayesian hypothesis tests between categorical groups for phenotypic variation (lnCVR)
+**Supplementary Table 19:** Bayesian hypothesis tests between categorical groups for phenotypic variation (lnCVR)
 ```{r}
@@
 
-**Table S20** REML hypothesis tests between categorical groups for phenotypic variation (lnCVR)
+**Supplementary Table 20:** REML hypothesis tests between categorical groups for phenotypic variation (lnCVR)
 ```{r}
@@
 anova.frame.var %>% pander(split.table = Inf)
+
+#saveRDS(anova.frame.var, "PDF_RDS_files/ST20.rds")
 ```
@@
 
-**Figure S4** The use of lnCVR (as opposed to lnVR) is justified in this meta-analysis due to the strong mean-variance relationship.
+**Supplementary Figure 5:** The use of lnCVR (as opposed to lnVR) is justified in this meta-analysis due to the strong mean-variance relationship.
 In this case the standard deviation from the treatment group is compared to the means of the treatment group on a log-scale.
@@
 
+#pdf("PDF_RDS_files/SF6.pdf", width =6, height = 6)
 both.lnVR.plots
-```
-
-**Figure S5:** The effects of sexual selection on the log-variance ratio (lnVR).
+#dev.off()
+```
+
+**Supplementary Figure 6:** The effects of sexual selection on the log-variance ratio (lnVR).
 Without accounting for the mean variance relationship (lnCVR) sexual selection has different effects on the variance measure.
 
-**Table S21** The points in the above plot are based on the following REML model and predictions.
+**Supplementary Table 21:** The points in the above plot are based on the following REML model and predictions.
 While the predicted effects of sexual selection on lnVR in stressful conditions is non-significantly negative, there is still a negative significant interaction between stressful environments and the female sex.
@@
 predictions.lnVR %>% pander(digits = 2) 
+#saveRDS(predictions.lnVR, "PDF_RDS_files/ST21.rds")
 ```
@@
 <br></br>
-**Figure 3a:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
+**Figure 3b:** Journal impact factor is not correlated with effect size. Point size is proportional to the precision of the effect size.
 
@@
 <br></br>
-**Figure 3b:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
+**Figure 3c:** The effect size dataset shows little to no signs of the time-lag bias: the average effect size from published studies has remained consistent across the two previous decades.
 Point size is proportional to the precision of the effect size.
@@
 
-# ggsave(plot = blind.plot, filename = "figures/blind_plot.eps", height = 6, width = 8)
+#ggsave(plot = blind.plot, filename = "PDF_RDS_files/blind_plot.pdf", height = 6, width = 8)
 blind.plot
@@
 <br></br>
-**Figure S6:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
+**Supplementary Figure 7:** Blinding does not appear to alter the magnitude or direction of effect sizes for the studies used in this meta-analysis.
 However, this should not be viewed as evidence against the validity of blinding as a research method.
@@
 
-#ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
+#ggsave(plot = generations.plot, filename = "PDF_RDS_files/generations_plot.pdf", height = 7.5, width = 10)
 
@@
 <br></br>
-**Figure S7:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
+**Supplementary Figure 8:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.
 
@@
 
-# ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
+#ggsave(plot = generations.plot.var, filename = "PDF_RDS_files/generations_plot_var.pdf", height = 7.5, width = 10)
 generations.plot.var
@@
 <br></br>
-**Figure S8:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
+**Supplementary Figure 9:** Phenotypic variation (lnCVR) is not affected by the number of generations an experiment is ran for.
 

### 2019-03-27 Response_to_editorial_requests.Rmd
minor changes to manuscript and response to editor

@@
 title: 'Meta-analytic evidence that sexual selection improves population fitness'
+author: 
+- Justin G. Cally, Devi Stuart-Fox and Luke Holman
 output:
   pdf_document: default
-subtitle: Response to Editorial Requests and Reviewer 1
+subtitle: Response to Editorial Requests and Reviewer
 bibliography: Manuscripts/Bibliography/Bibliography.bib
+csl: Manuscripts/Bibliography/NComms.csl
 header-includes: 
@@
   The main manuscript is provided in LaTeX format (.tex) and the Supplementary Information is now in pdf format.
-However, we retain the HTML formatting for the Supplementary Information hosted on \hyperlink{https://justincally.github.io/SexualSelection/}{Github}.
+However, we retain the HTML formatting for the Supplementary Information hosted on \href{https://justincally.github.io/SexualSelection/}{Github}.
 
   \item \textit{Please edit the title so that it is 15 words or fewer and does not include punctuation} \\
-  We have changed our title to: Meta-analytic evidence that sexual selection improves population fitness
+  We have changed our title to: Meta-analytic evidence that sexual selection improves population fitness.
 
@@
   \item \textit{Please do not use italics or bold font to convey emphasis (in both the main text and the display items).} \\
-  We only use italics for latin words or abbreviations (\textit{e.g., i.e., Prima facie}) and not for emphasis.
+  We only use italics for phrases or abbreviations in Latin (\textit{e.g., i.e., Prima facie}) and not for emphasis.
 
@@
   \item \textit{We strongly encourage authors to deposit all new data associated with the paper in a persistent repository where they can be freely and enduringly accessed.} \\
-  We have chosen to host our data on a Github repository alongside all our code and a neatly formatted html with supplementary information in an effort to maximise transparency of our analysis as well as allowing for the data and code to be easily reproduced and built upon by future studies.
+  We have chosen to host our data on a Github repository alongside all our code and a neatly formatted HTML with supplementary information in an effort to maximise transparency of our analysis as well as allowing for the data and code to be easily reproduced and built upon by future studies.
 
@@
 Furthermore, recommendations for conservation biology seem premature in this context.}\\
-  We have modified the title and abstract of the paper, and made it clear which conclusions are supported unambiguously and which are more tentative. For example…. [provide a quote or two].
+  We have modified the title and abstract of the paper, and made it clear which conclusions are supported unambiguously and which are more tentative. For example…
+
+\begin{itemize}
+
+\item The title is now \textit{Meta-analytic evidence that sexual selection improves population fitness}.
+
+\item In the abstract we include: \textbf{We find evidence} that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits.
+
+\item In the abstract we include: However, sexual selection had comparatively less positive effects on traits directly related to fitness than those with indirect or ambiguous relationships.
+
+\item We have modified the 2nd, 3rd and 4th paragraphs of the discussion and take a more tentative approach in drawing conclusions (see following comments).
+
+\end{itemize}
 
@@
 
+\end{enumerate}
 Here are the revised paragraphs:
+
+The results of the meta-analysis support predictions that sexual selection on males can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
+One possible mechanism is that male mating success is positively genetically correlated with traits that contribute to population fitness, allowing females to benefit from a genome that has been purged of deleterious alleles through competition between males [@RN94; @RN198; @RN95].
+A second (non-exclusive) mechanism is that experimental manipulation of sexual selection on males might directly alter the selective pressures acting on females, causing female traits to evolve.
+For example, removing sexual selection via enforced monogamy probably alters selection on females, because it alters the frequency of interactions with males (as well as the evolved genotype of those males).
+What is less clear is why the manipulation of sexual selection had a larger effect on female trait means and variances as opposed to males -- this result is arguably the opposite of what one would expect, since it is males that experience stronger sexual selection.
+Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic (co)variance and the strength of selection [@RN317; @RN318].
+
+Firstly, it is possible that female traits show more additive genetic variation than male traits, causing female traits to respond more strongly to a change in selection.
+This hypothesis is plausible because males frequently do experience stronger selection than females [@Singh2018], and sustained strong selection reduces heritability.
+A systematic review found no overall difference in mean heritability between male and female traits [@RN342], but did record numerous instances in which trait heritability was higher for females than males [@RN342].
+The sex chromosomes provide another reason for sex-specific heritability.
+Males are heterogametic in most of the species in our sample (*i.e.* the species with XY or XO sex determination), which can reduce father-to-son heritability relative to mother-to-daughter, since sons do not inherit the larger sex chromosome from their fathers [@RN340; @RN262; @RN147; @RN263], potentially slowing the adaptation of male traits [@RN263; @RN259].
+
+Secondly, selection on males might be weaker than selection on females, resulting in slower adaptation following the experimental manipulation of sexual selection.
+This explanation may initially seem implausible, because net selection on males is often stronger than on females [@Singh2018], due in part to the elevated importance of sexual selection in males as opposed to females [@RN304; @RN303; @RN337; @RN338].
+However, an oft-overlooked aspect is that selection might frequently be softer on males and harder on females [@RN319], because the local competitive environment is usually more important for males than it is for females.
+For instance, a mediocre male genotype can have high fitness provided it outcompetes its local rivals, while low-fitness female genotypes might produce few offspring even when competing with other low-fitness females.
+Therefore, improvements in genetic quality might have stronger diminishing returns in males, possibly contributing to our finding that the genetic consequences of sexual selection lead to greater fitness benefits for females.
+Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the softness of selection, relative to expectations for large, natural populations [@RN322; @RN277; @RN112].
+For example, many studies [@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then mixed and randomly sampled to create the next generation; this design ensures that successful males simply needed to outcompete their rival(s) in the same sub-population (soft selection), while each female's reproductive output is measured against the entire female population (hard selection).
 
@@
 
+\begin{enumerate}
+\setcounter{enumi}{3}
   \item \textit{l.
@@
 
+  \item \textit{l.
+162: low effect on sexual selection manipulation on traits like viability or female fecundity, compared to “indirect effect traits” which including male mating success, align with findings of meta-analysis of Prokop et al.
+2012 – it would be appropriate to mention this consistency here.}\\
+Thank you – we have now added this reference to the sentence in question.
+
+  \item \textit{l. 165: but see recent metaanalysis by Kelly et al. (2018) showing no sex effect on immunity}\\
+This study is interesting, but ultimately we don’t think it is sufficiently relevant to cite here.
+Our results found evidence that the experimental manipulation of sexual selection causes immunocompetence to evolve, while Kelly et al.
+(2018) examined whether males and females are differently defended against pathogens.
+
+  \item \textit{I hope supplementary figures will be linked to the main text, as it is somewhat difficult to find them by the number in the supplement deposited in a repository.}\\
+In the revision, we have provided a more traditional PDF version of the supplementary material, which is a simple list of all the supplementary figures and tables (this was also added to conform to Nature Communications style).
+For the submitted version of the manuscript we have hyperlinked the Supplementary Figure/Table to the relevant section of the Github page.
+One can also find a particular figure in the HTML version using Ctrl + F to search for the figure by name.
+
 \end{enumerate}
+
+\newpage
+
+# References
+<div id="refs"></div>

### 2019-03-27 Manuscripts/Manuscript_MetaAnalysis.Rmd
minor changes to manuscript and response to editor

@@
 - Justin G. Cally\textsuperscript{§*}, Devi Stuart-Fox\textsuperscript{§} and Luke Holman\textsuperscript{§}
-- 
+- '\textsuperscript{§}School of BioSciences, The University of Melbourne, Parkville, VIC, 3052, Australia'
 - '\textsuperscript{*}\textit{justin.g.cally@gmail.com}'
@@
 Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis.
-We find that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females evolving under stressful conditions.
-We conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
+We find evidence that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females evolving under stressful conditions.
+However, sexual selection had comparatively less positive effects on traits directly related to fitness than those with indirect or ambiguous relationships.
+Ultimately, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
 We discuss the implications of these results for conservation and evolutionary biology.
-\vspace{5mm} \par\noindent \textbf{Keywords:} Adaptation, Gender load, Monogamy, Mutation load, Sexual conflict.
 ---
-\maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.}
+\pagestyle{plain}
 
@@
 Our meta-analysis revealed that populations evolving under sexual selection often have higher values for multiple fitness traits, relative to populations where sexual selection on males was experimentally removed or weakened.
-Sexual selection had beneficial effects for traits that were ambiguously or indirectly related to fitness, but had smaller, variable effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced) and the proportion of viable offspring.
+Sexual selection had beneficial effects for traits that were ambiguously or indirectly related to fitness, but had smaller and variable effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced), and the proportion of viable offspring (similar to the results of another meta-analysis [@Prokop_2012]).
 Fitness traits related to immunocompetence were an exception: sexual selection typically resulted in weaker immunity.
@@
 The results of the meta-analysis support predictions that sexual selection on males can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
-Specifically, our results support arguments that positive genetic correlations between male mating success and female non-sexual traits are common, allowing females to benefit from a genome that has been purged of deleterious alleles through sexual selection on males [@RN94; @RN198; @RN95].
-What is less clear is why sexual selection had a larger effect on female trait means and variances as opposed to males (the sex in which sexual selection is typically strongest).
-Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic variance, the structure of genetic covariance, and the strength of selection [@RN317; @RN318].
-However, these explanations are speculative and _post hoc_, as the result is arguably opposite to what one would predict, (*i.e.* that manipulating sexual selection on males should affect the phenotype of males more than females).
+One possible mechanism is that male mating success is positively genetically correlated with traits that contribute to population fitness, allowing females to benefit from a genome that has been purged of deleterious alleles through competition between males [@RN94; @RN198; @RN95].
+A second (non-exclusive) mechanism is that experimental manipulation of sexual selection on males might directly alter the selective pressures acting on females, causing female traits to evolve.
+For example, removing sexual selection via enforced monogamy probably alters selection on females, because it alters the frequency of interactions with males (as well as the evolved genotype of those males).
+What is less clear is why the manipulation of sexual selection had a larger effect on female trait means and variances as opposed to males -- this result is arguably the opposite of what one would expect, since it is males that experience stronger sexual selection.
+Below we discuss possible explanations for this result, in light of the core principle that the extent of adaptation depends on additive genetic (co)variance and the strength of selection [@RN317; @RN318].
 
-Firstly, the response of male fitness to sexual selection may be constrained in species where the heritability of male fitness is influenced by the sex determination system.
-Males are heterogametic in many of the species in our sample (*e.g.* due to XY or XO sex determination); this can reduce father-to-son heritability relative to mother-to-daughter, since sons never inherit the larger sex chromosome from their fathers [@RN340; @RN262; @RN147; @RN263], which might slow adaptation in male relative to female traits [@RN263; @RN259].
-However, X-linkage is also likely to inflate the contribution of X-linked genes to fitness variance in the heterogametic sex.
-Under this view, X-linkage facilitates adaptation by increasing the efficacy of selection against recessive deleterious alleles and selection for recessive beneficial alleles [@RN341; @RN339].
-Perhaps as a result of these conflicting predictions, there seems to be no clear consensus regarding sex-based differences in heritability.
-For instance, a systematic review found no difference in mean heritability between male and female traits, although there was a male-biased skew in heritability of reproductive traits [@RN342].
-Conversely, a recent association study in humans found a number of traits showing higher heritability in females than males [@RN325].
+Firstly, it is possible that female traits show more additive genetic variation than male traits, causing female traits to respond more strongly to a change in selection.
+This hypothesis is plausible because males frequently do experience stronger selection than females [@Singh2018], and sustained strong selection reduces heritability.
+A systematic review found no overall difference in mean heritability between male and female traits [@RN342], but did record numerous instances in which trait heritability was higher for females than males [@RN342].
+The sex chromosomes provide another reason for sex-specific heritability.
+Males are heterogametic in most of the species in our sample (*i.e.* the species with XY or XO sex determination), which can reduce father-to-son heritability relative to mother-to-daughter, since sons do not inherit the larger sex chromosome from their fathers [@RN340; @RN262; @RN147; @RN263], potentially slowing the adaptation of male traits [@RN263; @RN259].
 
 Secondly, selection on males might be weaker than selection on females, resulting in slower adaptation following the experimental manipulation of sexual selection.
-This explanation may initially seem implausible, because net selection on males is generally assumed to be stronger than on females, due to (actual or hypothesised) sex differences in sexual selection and inter-individual variance in fitness [@RN304; @RN303; @RN337; @RN338].
+This explanation may initially seem implausible, because net selection on males is often stronger than on females [@Singh2018], due in part to the elevated importance of sexual selection in males as opposed to females [@RN304; @RN303; @RN337; @RN338].
 However, an oft-overlooked aspect is that selection might frequently be softer on males and harder on females [@RN319], because the local competitive environment is usually more important for males than it is for females.
-For instance, a mediocre male genotype can have high fitness provided it outcompetes its local rivals, while low-fitness female genotypes are likely to produce few offspring even when competing with other low-fitness females.
-Therefore, improvements in genetic quality should have stronger diminishing returns in males, possibly contributing to our finding that the genetic consequences of sexual selection lead to greater fitness benefits for females.
-Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the nature of selection, relative to expectations for large, natural populations [@RN322; @RN277; @RN112].
+For instance, a mediocre male genotype can have high fitness provided it outcompetes its local rivals, while low-fitness female genotypes might produce few offspring even when competing with other low-fitness females.
+Therefore, improvements in genetic quality might have stronger diminishing returns in males, possibly contributing to our finding that the genetic consequences of sexual selection lead to greater fitness benefits for females.
+Though this argument is speculative, we note that many experimental evolution designs exaggerate the sex difference in the softness of selection, relative to expectations for large, natural populations [@RN322; @RN277; @RN112].
 For example, many studies [@RN110; @RN326; @RN300; @RN111; @RN227] have evolved insects in small sub-populations, each containing one female and multiple males, whose progeny are then mixed and randomly sampled to create the next generation; this design ensures that successful males simply needed to outcompete their rival(s) in the same sub-population (soft selection), while each female's reproductive output is measured against the entire female population (hard selection).
@@
 For (a), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99.8 % CIs for the dataset.
-The Grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.
+The grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.
 Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.\label{publication_bias}](Figures/publicationbias.pdf)

### 2019-03-28 Manuscripts/Manuscript_MetaAnalysis.Rmd
Manuscript updates

@@
 In total, we obtained effect sizes for 22 different fitness traits, with female reproductive success ($n$ = 102) and offspring viability ($n$ = 56) being the most commonly-measured traits.
-We classified 171 effect sizes as direct measures of population fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous (see Methods, \autoref{forest_plot} and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Supplementary Table 1}).
+We classified 171 effect sizes as direct measures of population fitness, 141 as indirect, and the remaining 144 effect sizes as ambiguous (see Methods, Figure 1 and \href{https://justincally.github.io/SexualSelection/#inclusionexclusion_criteria}{Supplementary Table 1}).
 Specifically, we scored traits that are likely to correlate with population growth and persistence as direct (*e.g.*, female reproductive success, offspring viability, and extinction rate), those which are not necessarily correlated with population fitness but which do measure individual fitness as indirect (*e.g.*, lifespan, male mating success and ejaculate quality/production); and those for which the relationship to population fitness is unclear as ambiguous (*e.g.*, body size, mating duration, male reproductive success, and early fecundity).
@@
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
-Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness \autoref{forest_plot}; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_on_direct,_indirect_and_ambiguous_measures_of_fitness}{Supplementary Table 6}).
+Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness (Figure 1; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_on_direct,_indirect_and_ambiguous_measures_of_fitness}{Supplementary Table 6}).
 Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.21, 95% CIs: 0.058 to 0.093; Bayesian $\beta$ = 0.20, 95% CIs: -0.0016 to	0.39, $BF_{>0}$ = 38, $n$ = 144) and an indirect relationship to fitness (REML $\beta$ = 0.24, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.033 to 0.43, $BF_{>0}$ = 59, $n$ = 141).
@@
 We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect the relationship between sexual selection and fitness (Table 1,2).
-Sexual selection on males significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (\autoref{env_sex}a, Table 2).
-Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (\autoref{env_sex}a, Table 2).
-Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (\autoref{env_sex}a, Table 2).
+Sexual selection on males significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (Figure 2a, Table 2).
+Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (Figure 2a, Table 2).
+Consistent with the different consequences of sexual selection for female and male fitness, the mean effect size in mixed-sex samples was non-significantly positive, and there was no significant difference between benign versus stressful conditions (Figure 2a, Table 2).
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
@@
 
-By applying meta-analysis to log coefficient of variation ratios [*lnCVR*; @RN177], we found evidence that sexual selection reduces phenotypic variation under certain conditions (\autoref{env_sex}b).
+By applying meta-analysis to log coefficient of variation ratios [*lnCVR*; @RN177], we found evidence that sexual selection reduces phenotypic variation under certain conditions (Figure 2b).
 Specifically, phenotypic variance was significantly reduced by sexual selection for fitness components measured in females under stressful conditions (*lnCVR* = -0.78, 95% CIs: -1.23 to -0.34, $n$ = 27).
-By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (\autoref{env_sex}b; \href{https://justincally.github.io/SexualSelection/#meta-analysis_on_variance}{Supplementary Tables 17-20}).
-However, similar to the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.76, 95% CIs: -1.22 to -0.31; \autoref{env_sex}b).
+By contrast, we found no significant effect of sexual selection on phenotypic variance in males, or for either sex under benign conditions (Figure 2b; \href{https://justincally.github.io/SexualSelection/#meta-analysis_on_variance}{Supplementary Tables 17-20}).
+However, similar to the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.76, 95% CIs: -1.22 to -0.31; Figure 2b).
 A meta-analysis using the log variability ratio (lnVR), which does not account for the mean-variance relationship present in the dataset (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 5}), suggested sexual selection reduces variance for mixed-sex samples in stressful conditions, but not females, results of this meta-analysis can be found in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 6 and Supplementary Table 21}).
@@
 
-The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (\autoref{publication_bias}a; Egger’s test: *z* = 5.9, $p$ < 0.0001).
+The funnel plot of effect sizes was asymmetrical, suggesting that some publication bias might be present (Figure 3a; Egger’s test: *z* = 5.9, $p$ < 0.0001).
 Specifically, there was a moderate excess of low-powered studies in which sexual selection had a more positive effect on the fitness component than average, implying that low-powered studies are more likely to be published if they report statistically significant fitness benefits of sexual selection (though funnel plots are not a decisive evidence of publication bias[@RN215]).
-Linear regressions show no significant relationship between effect size and journal impact factor (\autoref{publication_bias}b; $t_{437}$ = 1.2, $p$ = 0.23) or year of publication (\autoref{publication_bias}c; $t_{437}$ = -1.2, $p$ = 0.24); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
+Linear regressions show no significant relationship between effect size and journal impact factor (Figure 3b; $t_{437}$ = 1.2, $p$ = 0.23) or year of publication (Figure 3c; $t_{437}$ = -1.2, $p$ = 0.24); thus, we found no evidence that effect size dictates the likelihood of publication in high-profile journals, or that effect sizes have diminished as the field has matured [@RN216; @RN217].
 
@@
 After removing duplicates, we read the titles and abstracts of the remaining 1,015 papers and removed those that did not fit our inclusion criteria (typically because they did not present primary experimental evolution data).
-This left 130 papers, for which we read the full text and applied the inclusion criteria outlined in the PRISMA diagram (\autoref{prisma_flow}).
+This left 130 papers, for which we read the full text and applied the inclusion criteria outlined in the PRISMA diagram (Figure 4).
 Briefly, we included studies that 1) were conducted in a dioecious animal, 2) experimentally manipulated the strength of sexual selection (*e.g.*, via experimentally-enforced random monogamy or an altered sex ratio) for at least one generation, and 3) measured a trait that we judged to be a potential correlate of population fitness.
@@
 
-Of these 130 papers, 62 were excluded based on the PRISMA criteria (\autoref{prisma_flow}).
+Of these 130 papers, 62 were excluded based on the PRISMA criteria (Figure 4).
 Additionally, three papers presented insufficient information to calculate effect size.
@@
 
-![\textbf{The effect of sexual selection on direct, indirect and ambiguous fitness components.} The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness.
+\textbf{Figure 1: The effect of sexual selection on direct, indirect and ambiguous fitness components.} The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness.
 Overall, effect sizes were more often positive than negative.
@@
 The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line.
-Predictions from both Bayesian and REML models can be found in Supplementary Table 6 and source data are provided at \url{https://github.com/JustinCally/SexualSelection}.\label{forest_plot}](Figures/forest.plot.class.pdf)
+Predictions from both Bayesian and REML models can be found in Supplementary Table 6 and source data are provided at \url{https://github.com/JustinCally/SexualSelection}.
 
-![\textbf{The roles of environmental stress and sex.} (a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
+\textbf{Figure 2: The roles of environmental stress and sex.} (a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions.
 (b) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals.
@@
 Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.
-Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.\label{env_sex}](Figures/environment_variance_edit5.pdf)
+Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.
 
-![\textbf{Tests for publication bias in the dataset.} Tests of publication bias are mixed and suggest publication bias may be present.
+\textbf{Figure 3: Tests for publication bias in the dataset.} Tests of publication bias are mixed and suggest publication bias may be present.
 (a) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies.
@@
 The grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.
-Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.\label{publication_bias}](Figures/publicationbias.pdf)
+Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.
 
-![\textbf{PRISMA diagram.} Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.\label{prisma_flow}](Figures/PRISMA\ Chart.pdf)
+\textbf{Figure 4: PRISMA diagram.} Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.

### 2019-03-28 meta_analysis_sexual_selection_pop_fitness.Rmd
Source data title

@@
 
-**Source Data:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
- <br/><br/> 
+**Source Data** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
+
 ```{r}

### 2019-04-05 Response_to_editorial_requests.Rmd
Minor tweaks

@@
 
-\item In the abstract we include: However, sexual selection had comparatively less positive effects on traits directly related to fitness than those with indirect or ambiguous relationships.
+\item In the abstract we include: However, sexual selection had weaker positive effects on direct measures of population fitness, such as extinction rate and proportion of viable offspring, than on individual fitness measures with indirect or less clear relationships to population fitness.
 
-\item We have modified the 2nd, 3rd and 4th paragraphs of the discussion and take a more tentative approach in drawing conclusions (see following comments).
+\item We have modified the 1st paragraph of the discussion and make it clear which conclusions are more or less strongly supported by the data (see also following comments for additional changes to improve clarity of interpretation).
 

### 2019-04-05 Manuscripts/Manuscript_MetaAnalysis.Rmd
Minor tweaks

@@
 We find evidence that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females evolving under stressful conditions.
-However, sexual selection had comparatively less positive effects on traits directly related to fitness than those with indirect or ambiguous relationships.
-Ultimately, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
+However, sexual selection had weaker positive effects on direct measures of population fitness, such as extinction rate and proportion of viable offspring, than on individual fitness measures with indirect or less clear relationships to population fitness.
+Overall, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
 We discuss the implications of these results for conservation and evolutionary biology.
@@
 Moreover, the effect sizes associated with the manipulation of sexual selection varied between different fitness traits.
-Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness (Figure 1; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_on_direct,_indirect_and_ambiguous_measures_of_fitness}{Supplementary Table 6}).
+Sexual selection had a beneficial effect on most fitness traits, but varied across the three relationships to fitness (Figure 1; \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_on_direct,_indirect_and_ambiguous_measures_of_fitness}{Supplementary Tables 5,6}).
 Sexual selection elevated fitness for traits that shared an ambiguous relationship to fitness (REML $\beta$ = 0.21, 95% CIs: 0.058 to 0.093; Bayesian $\beta$ = 0.20, 95% CIs: -0.0016 to	0.39, $BF_{>0}$ = 38, $n$ = 144) and an indirect relationship to fitness (REML $\beta$ = 0.24, 95% CIs: 0.13 to 0.36; Bayesian $\beta$ = 0.24, 95% CIs: 0.033 to 0.43, $BF_{>0}$ = 59, $n$ = 141).
 Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174).
-A large forest plot with predicted effect sizes for each fitness component is presented in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Figure 1} and further detailed with model predictions and individual meta-analyses in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Table 8,9}.
+A large forest plot with predicted effect sizes for each fitness component is presented in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Figure 1, Supplementary Table 7} and further detailed with model predictions and individual meta-analyses in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Table 8,9}.
 Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).
@@
 
-We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect the relationship between sexual selection and fitness (Table 1,2).
-Sexual selection on males significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (Figure 2a, Table 2).
+We found that the sex of the individuals measured (male, female, or a mixture), and the conditions under which the population evolved (stressful or benign) interacted to affect the relationship between sexual selection and fitness (Table 1,2 and \href{https://justincally.github.io/SexualSelection/#bayesian_model:_effects_of_environment_and_sex}{Supplementary Tables 11-13}).
+Sexual selection on males significantly improved female fitness, and the beneficial effect of sexual selection was significantly stronger for females from populations evolving under stressful conditions (*e.g.* a food source to which they were not well-adapted) than under benign conditions (Figure 2a, Table 2, \href{https://justincally.github.io/SexualSelection/#bayesian_model:_effects_of_environment_and_sex}{Supplementary Table 14}).
 Sexual selection had a positive but non-significant effect on male fitness, and in contrast to females, fitness benefits were significantly weaker in stressful than benign environments (Figure 2a, Table 2).
@@
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
-When we used an alternative measure of effect size (log response ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (\href{https://justincally.github.io/SexualSelection/#meta-analysis_using_lnrr}{Supplementary Figure 4 and Supplementary Table 16}).
+When only fitness components directly related to fitness were used in the mixed-effects model the benefits of sexual selection were magnified in females evolving under stressful conditions (\href{https://justincally.github.io/SexualSelection/#effects_of_environment_and_sex_on_direct_fitness_components}{Supplementary Figure 3 and Supplementary Table 15}).
+Similarly, when we used an alternative measure of effect size (log response ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (\href{https://justincally.github.io/SexualSelection/#meta-analysis_using_lnrr}{Supplementary Figure 4 and Supplementary Table 16}).
 
@@
 However, similar to the results in females, there was a non-significant trend for a reduction in phenotypic variance in mixed-sex samples measured under stressful conditions (*lnCVR* = -0.76, 95% CIs: -1.22 to -0.31; Figure 2b).
-A meta-analysis using the log variability ratio (lnVR), which does not account for the mean-variance relationship present in the dataset (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 5}), suggested sexual selection reduces variance for mixed-sex samples in stressful conditions, but not females, results of this meta-analysis can be found in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 6 and Supplementary Table 21}).
+A meta-analysis using the log variability ratio (lnVR), which does not account for the mean-variance relationship present in the dataset (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 5}), suggested sexual selection reduces variance for mixed-sex samples in stressful conditions, but not females.
+Results of this meta-analysis can be found in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#lnvr_effect_size_of_variance}{Supplementary Figure 6 and Supplementary Table 21}).
 
@@
 Our meta-analysis revealed that populations evolving under sexual selection often have higher values for multiple fitness traits, relative to populations where sexual selection on males was experimentally removed or weakened.
-Sexual selection had beneficial effects for traits that were ambiguously or indirectly related to fitness, but had smaller and variable effects on direct measures of fitness such as extinction rate, reproductive success (defined as the number of offspring produced), and the proportion of viable offspring (similar to the results of another meta-analysis [@Prokop_2012]).
+Sexual selection had beneficial effects on the majority of commonly measured individual fitness traits, which have indirect or unclear relationships to population fitness.
+Effects of sexual selection on direct measures of population fitness such as extinction rate, reproductive success (defined as the number of offspring produced), and the proportion of viable offspring, were smaller and variable (similar to the results of another meta-analysis [@Prokop_2012]), but nonetheless tended to be positive.
 Fitness traits related to immunocompetence were an exception: sexual selection typically resulted in weaker immunity.

### 2019-04-05 Manuscripts/Manuscript_MetaAnalysis.Rmd
Spelling tweaks

@@
 Additionally, sexual selection elevated fitness components directly related to fitness, albeit at a lower magnitude (REML $\beta$ = 0.13, 95% CIs: 0.019 to 0.24; Bayesian $\beta$ = 0.13, 95% CIs: -0.079 to 0.31, $BF_{>0}$ = 11, $n$ = 174).
-A large forest plot with predicted effect sizes for each fitness component is presented in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Figure 1, Supplementary Table 7} and further detailed with model predictions and individual meta-analyses in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Table 8,9}.
+A large forest plot with predicted effect sizes for each fitness component is presented in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Figure 1} and further detailed with model predictions and individual meta-analyses in \href{https://justincally.github.io/SexualSelection/#effect_of_sexual_selection_for_different_fitness_components}{Supplementary Tables 7,8}.
 Sexual selection significantly reduced two fitness components, namely immunity (REML $\beta$ = -0.42, 95% CIs: -0.64 to -0.20; Bayesian $\beta$ = -0.43, 95% CIs: -0.70 to -0.15, $BF_{>0}$ = 0.0026; $n$ = 35) and body condition (REML $\beta$ = -1.2, 95% CIs: -1.8 to -0.63; Bayesian $\beta$ = -1.2, 95% CIs: -1.9 to -0.63, $BF_{>0}$ < 0.0001, $n$ = 1).
@@
 Overall, our results indicate that the positive effect of sexual selection on fitness is greater for females than males, and the difference between the sexes is magnified in stressful environments.
-When only fitness components directly related to fitness were used in the mixed-effects model the benefits of sexual selection were magnified in females evolving under stressful conditions (\href{https://justincally.github.io/SexualSelection/#effects_of_environment_and_sex_on_direct_fitness_components}{Supplementary Figure 3 and Supplementary Table 15}).
+When only fitness components directly related to fitness were used in the mixed-effects model the benefits of sexual selection were still magnified in females evolving under stressful conditions (\href{https://justincally.github.io/SexualSelection/#effects_of_environment_and_sex_on_direct_fitness_components}{Supplementary Figure 3 and Supplementary Table 15}).
 Similarly, when we used an alternative measure of effect size (log response ratio or lnRR), the results aligned with those of Hedges' g in that sexual selection elevates population fitness, with its effect magnified for females evolving in stressful environments (\href{https://justincally.github.io/SexualSelection/#meta-analysis_using_lnrr}{Supplementary Figure 4 and Supplementary Table 16}).
@@
 
-Secondly, we fixed the relationship to fitness class (Ambiguous, Indirect or Direct) as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the three fitness-relationship classes, using the relevant ``predict`` functions for each of the ``R`` packages used (see below).
+Secondly, we fixed the relationship to fitness class (Ambiguous, Indirect or Direct) as a moderator variable in Bayesian and REML models (whilst maintaining study and taxon as group-level effects) to derive predictions for effect size within each of the three fitness-relationship classes, using the relevant ``predict`` functions for each of the R packages used (see below).
 This meta-analysis was then supplemented by another model where we fixed fitness component as a moderator variable (_e.g._, immunity, lifespan, offspring viability and female reproductive success); predictions for this model on the 22 fitness components were derived as above.
@@
 These models were were intercept only REML models with study and taxon as group-level effects.
-Further details on model parameters can be found by accessing the \href{https://justincally.github.io/SexualSelection/#meta-analysis}{``R`` code}.
+Further details on model parameters can be found by accessing the \href{https://justincally.github.io/SexualSelection/#meta-analysis}{R code}.
 
@@
 
-Meta-analyses fit by REML were implemented in the *metafor* ``R`` package [v.
-2.0; @RN212], while their Bayesian equivalents used the ``R`` package *brms* to run models in Stan[v.
+Meta-analyses fit by REML were implemented in the *metafor* R package [v.
+2.0; @RN212], while their Bayesian equivalents used the R package *brms* to run models in Stan[v.
 2.3.1; @RN290].\phantomsection

### 2019-04-05 Manuscripts/Manuscript_MetaAnalysis.Rmd
keep tex

@@
   pdf_document: default
-  html_document: default
-  word_document:
-      pandoc_args: ["--smart"]
+  keep_tex: yes 
 bibliography: Bibliography/Bibliography.bib

### 2019-04-05 Manuscripts/Manuscript_MetaAnalysis.Rmd
teep tex

@@
 output:
-  pdf_document: default
-  keep_tex: yes 
+  pdf_document:
+    keep_tex: true
 bibliography: Bibliography/Bibliography.bib

### 2019-04-06 Manuscripts/Manuscript_MetaAnalysis.Rmd
Author Contributions changed

@@
 #Author contributions  
-All authors designed the study; JGC collected the data; JGC and LH conducted the meta-analyses; JGC wrote the first draft of the manuscript; and all authors contributed substantially to all further revisions.
+JGC, DSF and LH designed the study; JGC collected the data; JGC and LH conducted the meta-analyses; JGC wrote the first draft of the manuscript; JGC, DSF and LH contributed substantially to all further revisions.
 \phantomsection

### 2019-04-12 Manuscripts/Manuscript_MetaAnalysis.Rmd
Editorial changes the SI formatting, citations and abstract now 150 words

@@
     \raggedbottom    
-abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict from first principles.
-Instead, one can empirically determine whether sexual selection increases or decreases population fitness by manipulating the opportunity for sexual selection in replicate populations, allow evolution to proceed, and then compare the evolved average fitness between the treatment groups.
-Here, we synthesise 459 effect sizes from 65 pertinent experimental evolution studies using meta-analysis.
-We find evidence that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females evolving under stressful conditions.
-However, sexual selection had weaker positive effects on direct measures of population fitness, such as extinction rate and proportion of viable offspring, than on individual fitness measures with indirect or less clear relationships to population fitness.
-Overall, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection on total selection, genetic variance, and/or evolvability can differ markedly between sexes and environments.
+abstract: Sexual selection has manifold ecological and evolutionary consequences, making its net effect on population fitness difficult to predict.
+A powerful empirical test is to experimentally manipulate sexual selection and then determine how population fitness evolves.
+Here, we synthesise 459 effect sizes from 65 experimental evolution studies using meta-analysis.
+We find that sexual selection on males tends to elevate the mean and reduce the variance for many fitness traits, especially in females and in populations evolving under stressful conditions.
+Sexual selection had weaker effects on direct measures of population fitness such as extinction rate and proportion of viable offspring, relative to traits that are less closely linked to population fitness.
+Overall, we conclude that the beneficial population-level consequences of sexual selection typically outweigh the harmful ones and that the effects of sexual selection can differ between sexes and environments.
 We discuss the implications of these results for conservation and evolutionary biology.
@@
 Sexual selection, defined as selection resulting from competition for mates or their gametes [@RN139], is a ubiquitous evolutionary force that has profoundly shaped the natural world.
-As far back as Darwin [@RN310], researchers have theorised that sexual selection can change the average absolute fitness of individuals in a population, henceforth termed ‘population fitness’ [@RN269; @RN268].
+As far back as Darwin [@RN310], researchers have theorised that sexual selection can change the average absolute fitness of individuals in a population, henceforth termed ‘population fitness’ [@RN269].
 However, opinion is divided over whether the net effect on population fitness is positive or negative [@RN42; @RN25; @RN116; @RN95].
@@
 
-Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus sexual conflict [@RN187; @RN146; @RN237; @RN147; @Harano_2010; @Plesnar_2014].
-Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males [@RN6; @RN267; @RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care: \textit{inter}locus sexual conflict [@RN314; @RN276; @RN315].
+Conversely, sexual selection can decrease population fitness if male sexually-selected traits are negatively genetically correlated with female fitness, producing intralocus sexual conflict [@RN187; @RN146; @RN147; @Harano_2010; @Plesnar_2014].
+Additionally, sexual selection frequently favours phenotypes that reduce population fitness but benefit the individuals expressing them, such as harassment or infanticide by mate-seeking males [@RN37], as well as investment in costly sexual signals and weaponry at the expense of parental care: \textit{inter}locus sexual conflict [@RN276; @RN315].
 Given these conflicting theoretical expectations and empirical results, it remains unclear whether sexual selection tends to have a net benefit or cost to population fitness [@RN42; @RN25; @RN116; @RN95].
@@
 Heterogeneity stemmed mostly from between-study differences ($I^2_{study}$ = 36%, 95% CIs: 26.5% to 45.4%) rather than differences between fitness components and taxon ($I^2_{fitness\:components}$ = 0.4%, 95% CIs: 0.2% to 0.9%; $I^2_{taxon}$ = 1.4%, 95% CIs: 0.2% to 3.5%).
-Variation among taxa is explored further in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_of_just_the_higher-quality_data}{Supplementary Figure 2, Supplementary Table 10}).
+Variation among taxa is explored further in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#restricted_analysis_of_just_the_higher-quality_data}{Supplementary Figure 2 and Supplementary Table 10}).
 \phantomsection
@@
 
-The results of the meta-analysis support predictions that sexual selection on males can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN141; @RN230; @RN198; @RN58].
+The results of the meta-analysis support predictions that sexual selection on males can improve population fitness and accelerate adaptation [@RN94; @RN173; @RN54; @RN230; @RN198; @RN58].
 One possible mechanism is that male mating success is positively genetically correlated with traits that contribute to population fitness, allowing females to benefit from a genome that has been purged of deleterious alleles through competition between males [@RN94; @RN198; @RN95].
@@
 Recent work has emphasised that environmental stress should reduce the strength of sexually antagonistic selection relative to selection that is concordant between sexes.
-Theoretical models reaching this conclusion [@RN67; @RN173] have been supported by some empirical work [@RN187; @RN74; @RN243]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress [@RN74].
-However, other quantitative genetic studies have shown that stressful conditions do not always reduce sexual antagonism [@RN297; @RN200; @RN257].
+Theoretical models reaching this conclusion [@RN67; @RN173] have been supported by some empirical work [@RN187; @RN74]; for example, one study found that high fitness males produced low fitness daughters under benign conditions but high fitness daughters under stress [@RN74].
+However, other quantitative genetic studies have shown that stressful conditions do not always reduce sexual antagonism [@RN200; @RN257].
 Variation in effects of sexual selection in stressful environments may be due to potentially variable responses amongst taxa [@RN298] and environments.
@@
 For example, the beneficial population-level consequences of sexual selection have been proposed as one possible resolution to the long-standing evolutionary puzzle regarding sexual reproduction [@RN309].
-If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants [@RN94; @RN308; @RN198].
+If sufficiently strong, these benefits can more than compensate for the costs of sexual reproduction, and prevent sexual populations from being outcompeted by asexual mutants [@RN94; @RN198].
 Sexual selection is also important for conservation [@RN25] and captive breeding programs [@RN117].
@@
 Captive breeding programs may benefit from allowing sexual selection of 'good genes' or more compatible genes [@RN294], or by increasing maternal investment by females paired with attractive males [@RN291; @RN292; @RN293].
-Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution, could reduce the genetic quality of the population, and potentially compromise its long-term persistence [@RN332; @RN331; @RN47; @RN333; @RN330].
+Additionally, our findings imply that anthropogenic environmental changes that reduce the opportunity for sexual selection, such as eutrophication, pesticides, artificial light and noise pollution, could reduce the genetic quality of the population, and potentially compromise its long-term persistence [@RN332; @RN331; @RN47; @RN333].
 Equally, our results support recent evidence that human activities that directly counteract sexual selection, such as selective harvesting of the largest or most ornamented males, can lower population fitness [@RN334].
@@
 
-In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see \href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{the source data} and associated Supplementary Information).
+In addition to the data used to calculate effect size, we collected a set of moderator variables for each paper (see the Source Data file and associated Supplementary Information).
 The moderators were selected due to their ready availability, and because we hypothesised that they might explain some of the observed heterogeneity in effect size.
@@
 Additionally, we collected details for each effect size on: sex (male, female or a mixed sample of both), taxon (flies, beetles, mice, nematodes, mites, crickets and guppies), the presence/absence of blind methodology, and number of generations a treatment group underwent experimental evolution.
-In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the Supplementary Information (\href{https://justincally.github.io/SexualSelection/#data_extraction_and_effect_size_calculation}{the source data}).
+In the interests of creating a useful data resource, we also recorded details about each experiment that were not formally analysed due to a shortage of data, such as the type of sexual selection that was manipulated (pre-copulatory, post-copulatory, or both) and the male to female ratio, which is included in the Source Data file.
 \phantomsection
@@
 
-We tested for publication bias via funnel plots, using Egger’s test to quantify plot asymmetry [@RN213; @RN214].
+We tested for publication bias via funnel plots, using Egger’s test to quantify plot asymmetry [@RN213].
 Additionally, we tested for time-lag bias [@RN216], in which effect size magnitudes decline over time as more data are collected.
@@
 All data are freely available on Github (https://github.com/JustinCally/SexualSelection).
-The repository provides a source data file that was used to create all results, tables and figures.
+Additionally, the source data used in this meta-analysis is provided as a Source Data file alongside this manuscript.
 \phantomsection
@@
 The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line.
-Predictions from both Bayesian and REML models can be found in Supplementary Table 6 and source data are provided at \url{https://github.com/JustinCally/SexualSelection}.
+Predictions from both Bayesian and REML models can be found in Supplementary Table 6.
+Data used for generating this figure are available in the Source Data file.
 
@@
 Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.
-Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.
+Data used for generating this figure are available in the Source Data file.
 
@@
 The grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.
-Source data are provided at \url{https://github.com/JustinCally/SexualSelection}.
+Data used for generating this figure are available in the Source Data file.
 

### 2019-04-12 meta_analysis_sexual_selection_pop_fitness.Rmd
Minor tweaks
Editorial changes the SI formatting, citations and abstract now 150 words

@@
 ```{r, warning=FALSE}
-read.csv('data/outcome.descriptions.csv', fileEncoding="UTF-8") %>%
+read.csv('data/outcome.descriptions.csv', fileEncoding="UTF-8") %>% select(-Examples) %>%
   kable("html") %>% kable_styling() %>%
   scroll_box(width = "100%", height = "500px")
-```
-<br></br>
-
-#### References for Supplementary Table 1
-```{r, warning=FALSE}
-read.csv('data/references.tableS1.csv', fileEncoding="UTF-8") %>%
-  kable("html") %>% kable_styling() %>%
-  scroll_box(width = "100%", height = "250px")
 ```
@@
 read.csv('data/Eligibility Workbook.csv', fileEncoding="UTF-8") %>% 
+  mutate(Citation = paste0('[@',Citation,']')) %>%
   kable("html") %>% kable_styling() %>%
@@
 
-**Supplementary Table 13:** Hypothesis tests for the Bayesian model are similar to the REML model (Supplementary Table 8), with slight differences to CIs.
+**Supplementary Table 13:** Hypothesis tests for the Bayesian model are similar to the REML model, with slight differences to CIs.
 
@@
 
-##Effects of environment and sex on direct fitness components
+###Effects of environment and sex on direct fitness components
 
